---
title: "Thermal Time Calculation Iversen 2 Weather data using hourly data from Novemer and December 2017"
author: "CT"
date: "07.01.2018"
output: html_document
---
##Thrs script calculates the TT for seed development experiment druing November and December 2017 in Iversen 2 . It uses air and soil tempertaure (Lumet data)

```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```



## Define Tt cardinal temperatures

Considered an overall average the following references:
Tb: 0.0
Top range:18-25
Tmax: 40
REFS: MonksEtAl2009	,LonatiEtAl2009	,MootEtal2003, SilsburyetAl1984. 
							
```{r}

#Create Thermal time cardinal temperatures need REF! 

tt_card <- data.frame(temp=c(0,15,22,35),TT=c(0,15,15,0))

tt_card %>%
  ggplot(aes(x=temp, y=TT))+
  labs(x="Temperature (degree Celsius)")+
  labs(y="Thermal Time (degree days)") +
  theme_bw()+
  geom_line()
  
```

```{r}

#Create and test interpolation function - Test if works 

temp_ref  <- 25 # x-axes reference
x_temp <- tt_card$temp # x-axes
y_TT <- tt_card$TT # y-axes


int_func <- function(temp,TT,temp_ref){

  # if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   out <- TT[length(TT)] 
   # FIXME: approx functions seems to do that - need param
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
   # else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  
int_func(x_temp,y_TT,temp_ref)


```

```{r readData}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedDevelopIv2")
getwd()

#create file
df_W_raw <- read.table("IvTempHour.txt",header=TRUE)

#head(df_We)

summary(df_W_raw)
```

Calculate the TThour, then transform to TT day and accumulate the Thermal time to make the TTSUM Air. 

```{r changeformat, echo=FALSE, warning=FALSE}

df_W <- df_W_raw %>%
  dplyr::select(Date:AirTemp) %>%
  mutate(Date=dmy(Date)) %>%
  rowwise() %>%
  mutate(TThour=int_func(x_temp, y_TT,AirTemp)) %>%
  group_by(Date) %>%
  summarise(TTday=mean(TThour)) %>%
  mutate(SumTTday = cumsum(TTday))

summary(df_W)

```

Now calculate the SumTT with the soil temperature 


```{r}
df_S <- df_W_raw %>%
  dplyr::select(-AirTemp) %>%
  mutate(Date=dmy(Date)) %>%
  rowwise() %>%
  mutate(TThour=int_func(x_temp, y_TT,SoilTemp10mm)) %>%
  group_by(Date) %>%
  summarise(TTdaysoil=mean(TThour)) %>%
  mutate(SumTTdaysoil = cumsum(TTdaysoil))

summary(df_S)
```



the formula and the hourly records correlate well ~12.5.. 


```{r}

write.table(df_W, "df_CumTTiv_air.txt")
write.table(df_S, "df_CumTTiv_soil.txt")
```

