---
title: "Seed Development  6CV"
author: "CT"
date: "05.01.2015"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
Aim: to calculate the seed development from bur 2 to bur 4 ....physiological maturity when inflorescences reach maximum dry weight. 



```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```
Read file and adjust formats 

```{r loadFile}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedDevelopIv2")

getwd()

#create file
df_develop <- read.table("SeedDevelop.txt",header=TRUE)


```


Check data 
```{r}
summary(df_develop)
```


```{r}


#select columns of interest 
df_develop2 <-df_develop %>%
  select(Date:Cultivar,DOT,Variable,BurrDryWg,MoistureContentPerc,IndividualDrySeedWeig)%>%
  mutate(Date=as.Date(Date))
  
  
str(df_develop2)
  
```


#data visualisation moisture content

```{r GraphBoxPlotBud, fig.height= 5, fig.width= 8}

 df_develop2 %>%
  filter(Variable != "B1") %>%
  group_by(DOT,Date,Cultivar,Variable)%>%
  dplyr::select(MoistureContentPerc)%>%
  summarise_each(funs(mean)) %>%
  #select(Variable,Percent,Cultivar,Date,SowTreat)%>%
  
  ggplot(aes(x=DOT, y=MoistureContentPerc)) + 
  geom_point(aes(colour=Cultivar, shape=Cultivar)) +
  #facet_grid(SowTreat~Cultivar, scales = "free")+
  #facet_grid(Cultivar~., scales = "free")+
  geom_abline(intercept = 0.5, slope = 0) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 0, hjust = 1))


```




```{r}

df_develop2 %>%
  filter(Variable != "B1") %>%
  group_by(DOT,Date,Cultivar,Variable)%>%
  dplyr::select(BurrDryWg)%>%
  summarise_each(funs(mean)) %>%
  #select(Variable,Percent,Cultivar,Date,SowTreat)%>%
  
  ggplot(aes(x=DOT, y=BurrDryWg)) + 
  geom_point(aes(colour=Cultivar, shape=Cultivar)) +
  #facet_grid(SowTreat~Cultivar, scales = "free")+
  #facet_grid(Cultivar~., scales = "free")+
  #geom_abline(intercept = 0.5, slope = 0) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 0, hjust = 1))

```


Then include the TT calculated !!! TT cum 


```{r ReadThermalSumData}
# read raw data

#The df_CumTTiv_air.txt  is created in script 1. 

#the file df_CumTTiv_air .txt contains the thermal sum hourly from Iversen.  
 
df_TTSum <- read.table("df_CumTTiv_air.txt",header=TRUE)

# remove extra columns
df_TTSum <- df_TTSum %>%
dplyr::select(Date,SumTTday) %>%
  mutate(Date = ymd(Date))%>%
  mutate(SumTTday=round(SumTTday, digits=2))
  
 
#check
head(df_TTSum)

```
Check data 
```{r}
summary(df_TTSum)
```

Merge dfs TTSum at Measurement and Sowing Date into Flowering df
```{r}

# Add Tt at measurement date
df_seed <- merge(df_develop2,df_TTSum, by="Date")
  

summary(df_seed)

```

Now calculate the TT starting from 2017-11-24 (DOT=0 or SumTTday=125.7).
Creted a column with the value 125.7 and subtract from SumTTday colum to get the value of TT.

```{r}


# change name SumTTday to TT at measurement used mutate 1 x cause rename did not work 
df_seed2 <- df_seed %>%
mutate(AccumTT = SumTTday-125.75)
#check the data 
str(df_seed2)


```
Need to modify the column name to be able to merge 
```{r}

 df_seed2 %>%
  filter(Variable != "B1") %>%
  group_by(Cultivar,Variable,Date, AccumTT)%>%
  dplyr::select(BurrDryWg)%>%
  summarise_all(funs(mean,sd)) %>%
  #select(Variable,Percent,Cultivar,Date,SowTreat)%>%
  
  ggplot(aes(x=AccumTT, y=mean)) + 
  geom_point(aes(colour=Cultivar, shape=Cultivar),size=3) +
  #facet_grid(SowTreat~Cultivar, scales = "free")+
  #facet_grid(Cultivar~., scales = "free")+
  #geom_abline(intercept = 0.5, slope = 0) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 0, hjust = 1))

```

Explore values for Narrikup  
```{r}
df_seed3<-df_seed2 %>%
  filter(Variable != "B1") %>%
  filter(Cultivar=="Narrikup")%>%
  group_by(Cultivar,Variable,Date, AccumTT)%>%
  dplyr::select(BurrDryWg)%>%
  summarise_all(funs(mean,sd))%>%
  mutate(SE=sd/1.73)





```


end of this script.