---
title: "Flowering 6CV"
author: "CT"
date: "31.12.2015"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
Aim: to calculate the percent of plants in specific reproductive phases : Bud, Early, Open, Petal, Bur1 _Bur4.

ATTENTION : this script has to run as continuous as the final dataframe generated (df_flower) is saved for further analysis and other scripts 

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```
Read file and adjust formats 

```{r loadFile}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")

getwd()

#create file
df_flower <- read.table("df_flower.txt",header=TRUE)



str(df_flower)

```

Check data 
```{r}
df_flower<-df_flower %>% 
 
mutate(Date=ymd(Date),SowingD=ymd(SowingD)) %>%
mutate(Percent=as.numeric(Percent))%>%
mutate(SimpleCat_Perc=as.numeric(Percent))
  
  
```

Analysis of sowing date and cultivars for Bud considering Date 

```{r }
df_flower%>%
dplyr::select(SowingD:Variable,TTAS:SimpleCat_Perc) %>%
  group_by(SowingD, Date, Cultivar,SowTreat,Block, Plot,Variable) %>%
  na.omit() %>%
  summarise_all(funs(max)) %>% # avoids repeated records FIXME: how to better do it?
  ungroup()
  
#functions use
str(df_flower)

 
```

 - Here blocks and plots are kept and repeated rows will be removed (unique).

- Find 50 Percent of each variable for cultivar and sowtreat.  
      DAS_50p_flow 
      tt_50p_flow 
- Need to inform the loop to interpolate in the first 50% reached (curve ascend, before the max Percent) to avoid getting values in descend curve.  

- Interpolate at 50% Flowering with function approx  REF: (Soetaert, Cash and Mazzia, 2012) 



```{r}

df_50_P <- df_flower


#Loop each plot to make it simple
var <- unique(df_50_P$Variable    )
plots <- unique(df_50_P$Plot)


# create empty df
df_tt_50p_flow <- data.frame(Variable = NULL,
                             Cultivar = NULL,
                             SowTreat = NULL,
                             SowingD = NULL,
                             Block=NULL,
                             Plot=NULL,
                             DAS= NULL,
                             TT50F = NULL)

#i=p=1
# 
# #loop trough each combination of factor levels
  for(j in 1:length(var)){
      for(p in 1:length(plots)){

      # clean value holders
      DAS_50p_flow <- 0
      tt_50p_flow <- 0
      
      #print(paste0(cv[i]," ",var[j]," ", sow[k], " B", block[b]))
  
  # filter for each combination
  df_sub <- df_50_P %>%
    filter(Plot == as.character(plots[p]) &
    Variable == as.character(var[j]))

  summary(df_sub)

  # create percentage with maximum value recorded
  # to avoid crossing the 50% line twice when flowering decreassed
  df_sub$av_Perc_max <- 0 # create new col

  for(z in 1:nrow(df_sub)) {

    df_sub$av_Perc_max[z] <- max(df_sub$SimpleCat_Perc[z],
                                 df_sub$av_Perc_max[z-1]) # keeps the highest value found

  }

 # df_sub
 # head(df_sub)
 # tail(df_sub)
# 
  # Interpolate
  y_ref <- 50 # y value where we want to find x by interpolation

  # interpolate
  #find DAS at 50 Pecent Flower

  tryCatch(
  DAS_50p_flow <- approx(df_sub$SimpleCat_Perc,
  df_sub$DAS , xout = y_ref, rule = 1)$y,
  error = function(e)
  {
  DAS_50p_flow <- NA
  }
)
  #find TT at 50 Pecent Flower
  tryCatch(
  tt_50p_flow <- approx(df_sub$SimpleCat_Perc,
  df_sub$TTAS , xout = y_ref, rule = 1)$y,
  error = function(e)
  {
  tt_50p_flow <- NA
  }
)

  df_temp <- NULL
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             Variable = df_sub$Variable[1],
                             SowTreat = df_sub$SowTreat[1],
                             SowingD = df_sub$SowingD[1],
                             Block = df_sub$Block[1],
                             Plot = df_sub$Plot[1],
                             DAS50F = DAS_50p_flow,
                             TT50F = tt_50p_flow)


  df_tt_50p_flow<- rbind(df_tt_50p_flow,df_temp)

      }
    }
  
summary(df_tt_50p_flow)

```



select only Denmark 

```{r}

# df_D <-df_tt_50p_flow %>%
#   filter(Cultivar=="Denmark")%>%
# filter(SowTreat=="S8") 
#     
#    ##get the mean and SE
# #get the mean and SE
# df_D1 <-df_D %>%
#   group_by(Variable) %>%
#   dplyr::select(DAS50F,TT50F)%>%
# summarise_all(funs(mean, sd))
  

  

```

Now select Narrikup

```{r}


df_N <-df_tt_50p_flow %>%
  filter(Cultivar=="Narrikup")%>%
filter(SowTreat=="S6"|SowTreat=="S7"|SowTreat=="S8") 
    
   ##get the mean and SE
#get the mean and SE
df_N1 <-df_N %>%
  group_by(Variable) %>%
  dplyr::select(DAS50F,TT50F)%>%
summarise_all(funs(mean, sd))%>%
  mutate(DASSE= DAS50F_sd/1.73, TT50SE=TT50F_sd/1.73)%>%
  select(-DAS50F_sd, -TT50F_sd)




```

then need to calculate the period Days and TT for each phase
bud to open
open to petal
petal -bur3
bur 3 - bur 4 
Calculate first duration in days 
```{r}

df_N2<-df_N %>%
  select(Cultivar:DAS50F)%>%
  spread(Variable,DAS50F)%>%
  mutate(BudOpen=Open-Bud, 
         OpenPetal=Petal-Open,
         PetalBur3=Bur3-Petal,
         Bur3Bur4=Bur4-Bur3)%>%
  select(-Bud,-Early, -Open, -Petal, -Bur1, -Bur2, -Bur3, -Bur4)%>%
  group_by(SowTreat)%>%
        summarise_all(funs(mean, sd))
   

write.table(df_N2, "Narrikup_DurationDays.txt")

```

Now calculate for duration in  TT 

```{r}

df_N3<-df_N %>%
  select(Cultivar:Plot, TT50F)%>% 
  spread(Variable,TT50F)%>%
  mutate(BudOpen=Open-Bud, 
         OpenPetal=Petal-Open,
         PetalBur3=Bur3-Petal,
         Bur3Bur4=Bur4-Bur3)%>%
  select(-Bud,-Early, -Open, -Petal, -Bur1, -Bur2, -Bur3, -Bur4)%>%
  group_by(SowTreat)%>%
        summarise_all(funs(mean, sd))
   
write.table(df_N3, "Narrikup_DurationTT.txt")


```



