---
title: "Flowering in Iversen 2 similar to ReAnalysis Table"
author: "CT"
date: "11.07.2018"
output:
  pdf_document: default
  html_document: default
  word_document: default
note: include Pp analysis using selected datasets from Reanalysis scripts but use
  Iversen 2 collected data. This is for DAS and TT from sowing to flowering . 
---

```{r loadLibraries, echo=FALSE, include=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library (segmented)
library(hydroGOF)
library (markdown)
library (knitr)

```
 
AIM:
- Estimate TT to 50% flowering in relation to Pp
- Find "when"" Pp has to be considered (i.e. Pp @ Tt between sowing till flowering)
- Do this by looking at figuest R2 fot Tt50 x Pp

```{r   loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")

getwd()


```
 
```{r}
#get dataframe created similar to ReAnalysis4 which is Rea6 - use Iversen DAS50Flwoering data
df_tt_flow <- read.table("df_tt_50p_flow.txt",header=TRUE) 

# force date format
df_tt_flow$SowingD <- ymd(df_tt_flow$SowingD)

str(df_tt_flow)


```

```{r}
summary(df_tt_flow)
```




##Here insert the dataframe with the Emergence data (DAS50E and TT50E)


##Insert here the dataframe with the DAS50E and TT50E 

```{r}

##Bring the table df_tt_50p_emerg

# Get dataframe 1 with the soil Temp in another folder 
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergenceIv2")
getwd()


df_Emergence <- read.table("df_tt_50p_emerg.txt",header=TRUE)

df_Emergence<-df_Emergence%>%
  dplyr::select(Plot, DAS50E,TT50E)


str(df_Emergence)
head(df_Emergence)



```



##to merge with the dataframe with the flower values (df_tt_flow) 

```{r}
df_mergedFloEmerg <- merge(df_tt_flow,df_Emergence, by="Plot") 
  #mutate(soilTempAcc_sow = SumTTday) %>%
  #dplyr::select(-SumTTday)
 # filter(Cultivar=="Antas")

str(df_mergedFloEmerg)
```


Cool! Now subtract DASF - DASE and TT50E - SummTTTrifo to get the values from emergence 


```{r}

#str(df_mergedFiveTrifo)

df_mergedFloEmerg <-df_mergedFloEmerg%>%
mutate(DAS50FFromEmerg=DAS50F-DAS50E,
       TT50FromEmerg= TT50F-TT50E)

str(df_mergedFloEmerg)

```

write a table with this dataset!!! 


```{r}

#write.table(df_mergedFiveTrifo, "C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifoCountsI2/DaysTT1TFromEmergence.txt")

write.table(df_mergedFloEmerg, "C:/GitHubRepos/SubCloverPhD/SubClover/FlowIv2/DaysTTToFlowerTFromEmergence.txt")

```


Inspect values and means 
 
 
 
```{r}

df_meanFlo <-df_mergedFloEmerg %>%
  dplyr:: select(Plot:Block,DAS50F,  TT50F ,DAS50FFromEmerg,TT50FromEmerg )%>%

  #group_by(Cultivar,SowTreat) %>%
  group_by(SowTreat) %>%
  # dplyr::select(SummTT5Trifo)%>%
  # summarise_all(funs(mean,sd))%>%
  #   mutate(SE=sd/1.73)
  
  summarise_at(c( "TT50F", "TT50FromEmerg"), mean, na.rm = TRUE)
  #summarise_at(c( "DAS50F", "DAS50FFromEmerg"), mean, na.rm = TRUE)


```



Bring weather dataset which is in df_CumTTIv.txt

```{r}

df_weather <- read.table("df_CumTTIv.txt",header=TRUE) %>%
  mutate(Date=ymd(Date)) %>%
  dplyr::select(-LocationYear,-Country) %>%
  dplyr::select(Date, SumTTday,Pp) # FIXME: this is also run Tt - change name to SumTTday_run?

  summary(df_weather)

```

Merge and calculate the two datasets 

- SumTT is value at sowing from 24 Jun 2015 
- TT50F_run (at flowering time) sets a limit for juvenile period (?) 

```{r}
# get TTsum at sowing
# estimates Tt with running TT sum from weather file
df_Iv <- merge(df_mergedFloEmerg, df_weather,
               by.x=c("SowingD"), 
               by.y=c("Date")) %>%
  ungroup()%>%
 # na.omit() %>%
  mutate(Pp_sow = Pp) %>%
  mutate(TtAtSowing_run = SumTTday) %>%
  dplyr::select(-SumTTday, -Pp) %>%
  mutate(TT50F_run = TT50F + TtAtSowing_run) %>% # Tt running at flowering
  mutate(cv_block_index = as.factor(paste0(Cultivar,"_",Block)))  %>%
  mutate(SowingD=ymd(SowingD))
 
str(df_Iv)

```

## Warning : negative values refer to S5 Denmark and Leura ... need to remove that 
```{r}
summary(df_Iv)
```


# Plot Tt50 vs Pp at sowing


```{r, fig.width=12}

df_Iv %>%
  na.omit() %>%
  #remove data from S5 Denmark and Leura 
  subset(DAS50FFromEmerg>0.05)%>%
  dplyr::select(Cultivar, SowTreat, Variable, TT50FromEmerg, Pp_sow) %>%
  group_by(Cultivar, SowTreat, Variable) %>%
  summarise_all(funs(mean,sd)) %>%
  ggplot(aes(x=Pp_sow_mean,y=TT50FromEmerg_mean, colour=Cultivar)) +
  theme_bw()+
  geom_point(size=4)+
  geom_line()+
  facet_grid(Variable~.)

#FIME: Why 0 for Leura & xxxx? Should be NA? when no flowerng

```


##Now include Pp function with target thermal time using the dataframe with days and TT from emergence 


Now assemble the Pp targets !!! 

##These chunks below need revision !!! why TT 50 run is added not sure if it is necessary now (26.06.2018) ? That is fixed now (01.07)


## calc

Find running sumTT for each sowing date at sowing

- only to have a small df for function below

- Obs: lebel tt as "_run" when using running sum of Tt across all sow dates

```{r}
sumTTatSow <- df_Iv %>%
  dplyr::select(SowTreat, TtAtSowing_run) %>%
  unique() %>%
  as.data.frame()

head(sumTTatSow)

```

Create function for retrieving photoperiod as a function of TT after sowing and Sowing date  treatment

- finds running TT at sowiong
- adds target to that and finds pp at that TT momrent
- tt_target is oCd after sowing when Pp is retrieved
- sowT is the sowing treatment (S1...)

```{r}

Pp_finder_func <- function(sowT, tt_target){
  
  #isolate the experiment and cultivar 
   sTT <- sumTTatSow %>% dplyr::filter(SowTreat == sowT) %>% dplyr::select(TtAtSowing_run)
   
   # sum target to sumTT at time of sowing for this specific sd
   tt_target_adj <- tt_target + sTT 
   
  # lookup for Pp at new tt sum in weather file
  tryCatch(  
  Pp_target <- approx(df_weather$SumTTday, 
  df_weather$Pp, xout = tt_target_adj, rule = 1)$y,
  error = function(e) 
  {
  Pp_target <- NA
  }
)
 
  return(Pp_target)
  
}

```

## Test function

```{r}
st <- "S5"

#test
tt_target <- 0 
#TTsum estimated to reach 1st trifoliate 

#test if function is working : example : 
Pp_finder_func(st, tt_target)
```

# Find Pp at a given Tt sum after EMERGENCE ! (not sowing) Use variable : TT50FromEmerg
- Sums ftxed Tt to sowing Tt and see what Pp is there
- Plots this Pp against TT to flowering
- See if there is a stronger relationship beteen Pp and Tt

## Segment df by Cv and block 
-Note that this one is the TT target from Emergence!! 

```{r}

# FIXME: This logic is corrupted as graph for target ==0 is not as above. Yes that is sure thing !!!! 

cv_block <- (unique(df_Iv$cv_block_index))

df_Iv_flow <- df_Iv %>% 
  dplyr::filter(Variable=="Flowering") %>%
  subset(TT50FromEmerg>0.5)
#na.omit()
  #Need to remove Denmark and Leura S5 ! no flowering 
  

# Loop 
df_pp_allEmer <- data.frame()

for(p in 1:length(cv_block)) {
  
  CBI <- cv_block[p]
  
  # segment plot of interesst
  df_sub <- df_Iv_flow %>% 
    dplyr::filter(cv_block_index==cv_block[p])
  
  # loop through Tt chuncks after sowing
  # t is tt from sowing to the point where Pp is retrieved
   # for(t in seq(from=0, to=min(df_sub$TT50F), by=100)){
     for(t in seq(from=0, to=min(df_sub$TT50FromEmerg), by=100)){
 #   TT_target <- t # tt from sowing to the point where Pp is retrieved
  
    # Calculate Pp at this Tt sum after sowing
    df_sub_pp <- df_sub %>%
    rowwise() %>%
    mutate(TT_target = t)  %>%
    mutate(Pp_target=Pp_finder_func(SowTreat,TT_target))
    
    # Bind all results
    df_pp_allEmer <- rbind(df_pp_allEmer,df_sub_pp)
   
    }
}

summary(df_pp_allEmer)

# FIXME: The extreme value of Tt target goes beyond current weather, need to expand it a bit

```

Check photoperiod direction 


```{r, fig.width=12}
df_pp_allEmer %>%
  ggplot(aes(y=TT_target,x=Pp_target)) +
  geom_point(size=3.5) + 
  #geom_line() + 
  facet_grid(Cultivar~SowTreat)+
  theme_bw(base_size=18) +
  ylab(expression(Mean~Thermal~time~target~"("^"o"*"Cd)")) + 
  #xlab(expression(Photoperiod~at~Thermal~time~Flowering~"("^"o"*"Cd)")) +
  xlab(" Photoperiod target (hours)") +
  ylim(0,1000)
  
  
```




Yes!! Now all these graphs contain the TT target refering to the TTfrom emergence (TT50FromEmerg) !!! 


```{r, fig.width=15, fig.height=6}

#str(df_pp_all)

df_pp_all_mean <- df_pp_allEmer %>%
  
    dplyr::select(Cultivar,Variable,SowTreat,TT50FromEmerg,TT_target,Pp_target)%>%
    group_by(Cultivar,SowTreat, Variable,TT_target)  %>%
    filter(Variable=="Flowering") %>%
    summarise_all(funs(mean))


#summary(df_pp_all_mean)


df_pp_all_mean$Cult_TtT <- paste0(df_pp_all_mean$Cultivar,"_",round(df_pp_all_mean$TT_target,0))

indexTT <- unique(round(df_pp_all_mean$TT_target,0))
indexCT <- unique(df_pp_all_mean$Cult_TtT)
indexCV <- unique(df_pp_all_mean$Cultivar)

for (i in 1:length(indexCV)) {
  
  df <- df_pp_all_mean%>%subset(Cultivar==indexCV[i])
  
  g <- df %>%
  ungroup() %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May")))%>%
  ggplot(aes(x=Pp_target,y=TT50FromEmerg))   +
  geom_text(aes(label=SowTreat, colour=Cultivar),hjust=0, vjust=0,size=4) +
    scale_colour_manual(values=c("#000000" )) +
  #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  theme_bw() +
  ylab(expression(Mean~Thermal~time~Flowering~"("^"o"*"Cd)")) + 
  #xlab(expression(Photoperiod~at~Thermal~time~Flowering~"("^"o"*"Cd)")) +
  xlab(" Photoperiod at Target Thermal times (hours) ") +
 #facet_grid(.~Cultivar, scales="free")+
  facet_wrap(~TT_target, scales="free",ncol=6)+
  # facet_grid(TT_target~., scales="free")+
  theme(text = element_text(size=16))+
    xlim(9,20)+
    ylim(0,2500)+
    ##FIXME here geom smooth : method ='lm' not stat = 'lm' 
     geom_smooth(method ='lm') +
  #  geom_smooth(alpha=0.2, fill='blue', aes(stat ='lm')) + 
    geom_point(size=2,alpha=0.5)
  
  
  
  print(g)
  
}

```


get all graphs in appendix then. 


## Check data

```{r, fig.height= 10 , fig.width=15}

df_pp_allEmer %>%
  filter(TT_target==500) %>%
  ggplot(aes(x=Pp_target,y=TT50FromEmerg,colour=factor(Cultivar),shape=factor(SowTreat) )) +
  theme_bw()+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  geom_point(size=6) + geom_line() +facet_grid(Cultivar~.)

```

##Now write a table to use to calculte the Photothermal time and continue in script 7 


```{r, fig.height= 5 , fig.width=10}

#str(df_pp_allEmer)
#format Block as factor here already 
df_pp_allEmer$Block <- as.factor(df_pp_allEmer$Block)


  
str(df_pp_allEmer)

#Save as table 
write.table(df_pp_allEmer, "df_Pptargets_TT50FFromEmergence.txt")

```

Cool now proceed with the next ones 
End of this script 
