---
title: "ReAnalysis Table"
author: "CT"
date: "24.04.2017"
output:
  word_document: default
  html_document: default
note: include Pp analysis using selected datasets from Reanalysis scripts but use Iversen 2 collected data  
---

```{r loadLibraries, echo=FALSE, include=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library (segmented)
library(hydroGOF)

```
 
AIM:
- Estimate TT to 50% flowering in relation to Pp
- Find "when"" Pp has to be considered (i.e. Pp @ Tt between sowing till flowering)
- Do this by looking at figuest R2 fot Tt50 x Pp

```{r   loadFile}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\FlowIv2")

getwd()


```

```{r}
#get dataframe created similar to ReAnalysis4 which is Rea6 - use Iversen DAS50Flwoering data
df_t <- read.table("df_tt_50p_flow.txt",header=TRUE) 

summary(df_t)
```

Bring weather dataset which is in df_CumTTIv.txt

```{r}

df_CumTT <- read.table("df_CumTTIv.txt",header=TRUE) %>%
  mutate(Date=ymd(Date)) %>%
  dplyr::select(-LocationYear,-Country)

summary(df_CumTT)

```

Then select just columns of interest 
```{r}

df_weather <- df_CumTT %>%
    dplyr::select(Date, SumTTday,Pp)

#  summary(df_CumTT2)
  summary(df_weather)

```

Merge the two datasets 

```{r, fig.width= 12,fig.height=5, warning=FALSE}

# force date format
df_t$SowingD <- ymd(df_t$SowingD)
str(df_t)

```

- Sum TT is from 24 Jun 2015

```{r}
# get TTsum at sowing
df_Iv <- merge(df_t, df_weather,
               by.x=c("SowingD"), 
               by.y=c("Date")) %>%
  mutate(ttJuvMax = TT50F+SumTTday)

# df_Iv$TTSumAtSow <- df_Iv$SumTTday
# 
# #df_Iv$Index <- as.factor(paste0(df_Iv$SowTreat,"_",df_Iv$Treatcultivar)) # used for loop later
# 
# df_Iv$SumTTday <- NULL

str(df_Iv)
```


```{r}
summary(df_Iv)
```

# Plot Tt50 vs Pp at sowing

```{r}

df_Iv %>%
  dplyr::select(Cultivar, SowTreat, Variable, TT50F, Pp) %>%
  group_by(Cultivar, SowTreat, Variable) %>%
  summarise_each(funs(mean,sd)) %>%
#  na.omit() %>%
  ggplot(aes(x=Pp_mean,y=TT50F_mean, colour=Cultivar)) +
  geom_point()+
  geom_line()+
  facet_grid(Variable~.)

```

## Select weather fields needed

- SumTTday is running sum from 24 Jun 2015

```{r}

# Select columns of interest 
# df_weather <- df_CumTT2 %>%
# dplyr::select(LocationYear,Date, Pp, SumTTday)
# 
# str(df_weather)

```

Note that SumTTday does not zero at sowing, keeps going 

```{r}
#summary(df_weather)
```

find running sumTT for each sowing date at sowing

- only to have a small df for function below

```{r}
sumTTatSow <- df_Iv %>%
  dplyr::select(SowTreat, SumTTday) %>%
  unique() %>%
  as.data.frame()

head(sumTTatSow)

```

Create function for retrieving photoperiod as a function of TT after sowing and SD treatment

- finds running TT at sowiong
- adds target to that and finds pp at that TT momrent
- tt_target is oCd after sowing when Pp is retrieved
- sowT is the sowing treatment (S1...)

```{r}

Pp_finder_func <- function(sowT, tt_target){
  
  #isolate the experiment and cultivar 
   df_temp_wea <- df_weather 
   sTT <- sumTTatSow %>% dplyr::filter(SowTreat == sowT) %>% dplyr::select(SumTTday)
   
   # sum target to sumTT at time of sowing for this spesific sd
   tt_target_adj <- tt_target + sTT 
   
  # lookup for Pp at new tt sum in weather file
  tryCatch(  
  Pp_target <- approx(df_temp_wea$SumTTday, 
  df_temp_wea$Pp, xout = tt_target_adj, rule = 1)$y,
  error = function(e) 
  {
  Pp_target <- NA
  }
)
 
  return(Pp_target)
  
}

```

## Test function

```{r}
st <- "S1"

#test
tt_target <- 300
#TTsum estimated to reach 1st trifoliate 

#test if function is working : example : 
Pp_finder_func(st, tt_target)
```

Create the loop to identify each combination of cultivars - isolate and calculate stats for each Pp target.
maybe use concatenate fro sowing date treatment and cultivar


```{r}
#FIXME: use RMSE instrad of R2 to find best fit

#Flowering reference = flowRefPerc
#flowRefPerc <- 50

#TTpercflo <- 2.6 # degree days from 5 to full (100) flowering 
# #value calculated from DearEtAL1993_Reanalysis3 script
# 
# # # find max value of TTjuv possible per  group (i.e. Tt at slowering time)
# #  ttJuvMax <- df_Iv %>%
# #    filter(Variable=="Flowering") %>%
# #  #  group_by(SowTreat,Cultivar,Block) %>%
# #    rowwise() %>%
# #   mutate(ttJuvMax = TT50F+SumTTday)
# 
# #loop
# cvGroup <- unique(df_Iv$Treatcultivar)
# vc_temp <- vector()
# vc_all <- vector()
# 
# #i=t=1
# 
# summary(ttJuvMax)


```

Stopped here .. check repeated values


```{r}

plots <- unique(df_Iv$Plot)

df_Iv_flow <- df_Iv %>% dplyr::filter(Variable=="Flowering") %>%  na.omit()

#p=1

for(p in 1:length(plots)) {
  
  # segment plot of interesst
  df_sub <- df_Iv_flow %>% dplyr::filter(Plot==plots[p])
  
  # loop through Tt chuncks after sowing
    for(t in seq(0,min(df_sub$ttJuvMax), by=100)){
      
     if(t > ttJuvMax$ttJuvMax) {
     
     break # do not allow TTjuv > min of TT to flower
     
     }
      
      
      
      print(t)
      
    }
}

summary(df_sub)

```







```{r, warning=FALSE}

for(i in 1:length(cvGroup)){
  
  for(t in seq(0,max(ttJuvMax$ttJuvMax), by=100)){
    
 #  if(t > ttJuvMax$ttJuvMax[ttJuvMax$ttJuvMax==cvGroup[i]]) {
     if(t > ttJuvMax$ttJuvMax) {
     
     break # do not allow TTjuv > min of TT to flower
     
     }
    
   #print(t)
  #print(i)
 
  cvG <- cvGroup[i]
  
  #print(s) 
  
  df_s <- df_Iv %>%
    dplyr::filter(Treatcultivar == cvG) %>%
    filter(Variable=="TTtoFlower") %>%
    mutate(ttFlowZero = Value - (flowRefPerc*TTpercflo)) %>% 
    mutate(z = TTSumAtSow + t) %>% #define multiple tt after sowing for which Pp needs to be retrieved 
    mutate(TT_target= ifelse (z > ttFlowZero,
                             ttFlowZero,
                             z)) %>%
    #mutate(z=TTSumSow + t) %>% #testing Pp even if Pp greater than experienced by crop
    rowwise() %>%
    #mutate(Pp_target=Pp_finder_func(TT_target)) # functions gets a charater therefore format changes
     mutate(Pp_target=Pp_finder_func(SowTreat,TT_target))
    #print(unique(df_s$indexLocCult))
    
    x <- as.numeric(df_s$Pp_target)
    y <- as.numeric(df_s$Value)
  
  # test alternative functions - all gave highest first R2 at ~ 600oCd - Not resolved
 #  polyM <- lm(formula = y ~ poly(x, 3)) # testing simple polinomial
 #  expM <- lm(log(y)~ x)
 #  print(t)
 #  print( summary(polyM)$r.squared*100)
 #  summary(polyM)
  # -------
  
  out.lm <-lm(Value~Pp_target,data=df_s)
  
    # way to get eq coeff  
  summary(out.lm) 
  intT <- out.lm$coefficients[1]
  slopeT<- out.lm$coefficients[2]
  
  tryCatch(  
  o <- segmented(out.lm,seg.Z=~Pp_target,psi=list(Pp_target=13),
                   control=seg.control(display=FALSE)),
  
  error = function(e) 
  {
  o <- NA
  }
)
  
  
  # test plot FIXME: Does not display what we expected?
  print(t)
  plot(x,y, pch=16)
  plot(o, add=T, link=TRUE)
  
      
  
  # find stats
      s <- slope(o)$Pp[,1]    
      interc <- intercept(o)
    
    #  r2 <- round(summary.segmented(o)$adj.r.squared*100,digits=5)
      r2 <- round(summary.segmented(o)$r.squared*100,digits=5)
      slope1 <- round(s[1], digits = 4)
      slope2 <- round(s[2], digits = 4)
      pVs1 <- summary.segmented(o)$coefficients[14]#pvalue slope1
      pVs2 <-summary.segmented(o)$coefficients[15]#pvalue slope2
      
      # find breaks
      b = o$psi[,2]
      
      vc_temp <- c(as.character(cvG),t, r2,slope1,slope2,pVs1,pVs2,b)
      vc_all <- rbind(vc_all,vc_temp)
      # show slopes and breakpoints
      #print(paste0(" slope: ",s, " break: ", b))
      
      print(r2)
      r2 <-NA
      slope1 <- NA
      slope2 <- NA
      pVs1 <- NA
      pVs2 <-NA
     # print(summary(o))
  
    }  #this ends the loop of multiple thermal time
vc_temp <-NULL

 } #end loop group
  
 #Here need to include sowing date
 df_all <-data.frame(vc_all)
 colnames(df_all) <-c("CvGroup","TTjuv", "r2","slope1","slope2","pVs1","pVs2","b")
 
 # FIXME: The resulting model does not align with the best "visual" fit at 900oCd Tt juveline
```



```{r, fig.height=5, fig.width=12 }
#Graph : FIX ME why the R2 is the same in some of the TT?

#graph it 

df_all %>%
  #filter(CvGroup == "Antas")%>%
   ggplot(aes(x=as.numeric(as.character(TTjuv)),
              y=as.numeric(as.character(r2)), colour=CvGroup)) +
  labs(x="Thermal Time target after sowing (oCd)", y="R2")+
  theme_bw()+
  geom_point() +
  geom_line()+
   facet_wrap(~CvGroup,ncol=3)+
  ylim(0,100)
  
```

gfhgfhgfhgfhgfhgf
```{r , warning = FALSE}

# find highest r2

#graph PPat 1000TTjuv 
df_opt <- df_all %>%
group_by(CvGroup) %>%
filter(r2==max(as.numeric(as.character(r2))))

#tt_extra_opt <- 700

#for(gg in 1:length(ggg)) {
# for(tte in 1:length(tt_extra_opt)) {
  
   dt1 <- df_Iv %>%
     rowwise() %>%
     filter(Variable == "TTtoFlower") %>%
     mutate(tt_extra_opt = 700) %>%
     mutate(TT_target = TTSumAtSow + tt_extra_opt) %>% #define multiple thermal time after sowing for which photoperiod needs to be retrieved 
    mutate(Pp_target = Pp_finder_func("S1",TT_target)) %>%
    mutate(tt_juv_toflower=Value-tt_extra_opt)
   
   
  # 
  # 
 
  
   

  
# }
# 
# }

# loop acros multiple TT extras
# select best stats or simply store all (better I think) and test in next chunck
   

```



```{r}
   
  g <- dt1 %>%
    ggplot(aes(x=Pp_target,y=Value)) +
     #ggplot(aes(x=Pp_target,y=tt_juv_toflower)) + #test Pp versus the TTdiferential form Juvenile to    flower
    geom_point(aes(colour=(SowTreat))) +
    # stat_smooth(method = "lm", formula = y ~ x + I(x^2), size = 1) + 
     stat_smooth(method = "lm", formula = y ~ poly(x, 2), size = 1)+
     geom_vline(xintercept = 14, linetype=2)+
     labs(x="Photoperiod at inductive phase (hours)", y="Thermal Time to flower (degree days)")+
     facet_wrap(~Treatcultivar)+
     theme(legend.position="top") +
    labs(shape="SowTreat", colour="SowingDate")

   
   print(g)
```


Stopped here.... why don;t see all 8 sowing dates above ?

