 ---
title: "Flowering 6CV - calculation 50 Percent Flowering"
author: "CT"
date: "30.02.2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Aim: Calculate Tt at 50% Bud, flowering or Bur classes for each plot

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
```


```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")
getwd()

#create file: this file was generated in the previous script FlowerProject2
```

- Here create a df for calculation of 50 Percent Bud, Flower and Bur
- Read the dataframe created in the previous script (FlowerProject2)
- Create a column that contains the percentage for each simple category (SimpleCat_Perc) 
```{r}
df_bud_flow_bur_simple <- read.table("df_bud_flow_bur_simple.txt",header=TRUE)


# change formats
df_bud_flow_bur_simple <- df_bud_flow_bur_simple %>%
mutate(Date=ymd(Date),SowingD=ymd(SowingD)) %>%
mutate(Percent=as.numeric(Percent))%>%
mutate(SimpleCat_Perc=as.numeric(Percent))
summary(df_bud_flow_bur_simple)
```

- Select needed columns
- note that there will repeated values in df_50_P because of the merge variables. The dataframe will contain one unique value for Bud (as Bud) but 3 values (rows) for flowering and two row-values for Bur. 
- Troubleshooting the repeated values was removed  by the function max in the chunk below. 

```{r}

df_50_P <- df_bud_flow_bur_simple %>%
dplyr::select(SowingD:Variable,TTAS:SimpleCat_Perc) %>%
  group_by(SowingD, Date, Cultivar,SowTreat,Block, Plot,Variable) %>%
  na.omit() %>%
  summarise_all(funs(max)) %>% # avoids repeated records FIXME: how to better do it?
  ungroup()
  
#functions use
str(df_50_P)

```



```{r}
summary(df_50_P)

#write.table(df_50_Perc, "df_50_Perc.txt")
```
- Here blocks and plots are kept and repeated rows will be removed (unique).

- Find 50 Percent of each variable for cultivar and sowtreat.  
      DAS_50p_flow 
      tt_50p_flow 
- Need to inform the loop to interpolate in the first 50% reached (curve ascend, before the max Percent) to avoid getting values in descend curve.  

- Interpolate at 50% Flowering with function approx  REF: (Soetaert, Cash and Mazzia, 2012) 


Fix me here: how to loop unique variable and plot number ? It is producing dataframe with no values! 

Check data plot 2 Monti in S1 . right order? 

```{r}

#Loop each plot to make it simple
var <- unique(df_50_P$Variable    )
plots <- unique(df_50_P$Plot)


# create empty df
df_tt_50p_flow <- data.frame(Variable = NULL,
                             Cultivar = NULL,
                             SowTreat = NULL,
                             SowingD = NULL,
                             Block=NULL,
                             Plot=NULL,
                             DAS= NULL,
                             TT50F = NULL)

#i=p=1
# 
# #loop trough each combination of factor levels
  for(j in 1:length(var)){
      for(p in 1:length(plots)){

      # clean value holders
      DAS_50p_flow <- 0
      tt_50p_flow <- 0
      
      #print(paste0(cv[i]," ",var[j]," ", sow[k], " B", block[b]))
  
  # filter for each combination
  df_sub <- df_50_P %>%
    filter(Plot == as.character(plots[p]) &
    Variable == as.character(var[j]))

  summary(df_sub)

  # create percentage with maximum value recorded
  # to avoid crossing the 50% line twice when flowering decreassed
  df_sub$av_Perc_max <- 0 # create new col

  for(z in 1:nrow(df_sub)) {

    df_sub$av_Perc_max[z] <- max(df_sub$SimpleCat_Perc[z],
                                 df_sub$av_Perc_max[z-1]) # keeps the highest value found

  }

 # df_sub
 # head(df_sub)
 # tail(df_sub)
# 
  # Interpolate
  y_ref <- 2#0 # y value where we want to find x by interpolation

  # interpolate
  #find DAS at 50 Pecent Flower

  tryCatch(
  DAS_50p_flow <- approx(df_sub$SimpleCat_Perc,
  df_sub$DAS , xout = y_ref, rule = 1)$y,
  error = function(e)
  {
  DAS_50p_flow <- NA
  }
)
  #find TT at 50 Pecent Flower
  tryCatch(
  tt_50p_flow <- approx(df_sub$SimpleCat_Perc,
  df_sub$TTAS , xout = y_ref, rule = 1)$y,
  error = function(e)
  {
  tt_50p_flow <- NA
  }
)

  df_temp <- NULL
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             Variable = df_sub$Variable[1],
                             SowTreat = df_sub$SowTreat[1],
                             SowingD = df_sub$SowingD[1],
                             Block = df_sub$Block[1],
                             Plot = df_sub$Plot[1],
                             DAS50F = DAS_50p_flow,
                             TT50F = tt_50p_flow)


  df_tt_50p_flow <- rbind(df_tt_50p_flow,df_temp)

      }
    }
  
summary(df_tt_50p_flow)
```
check graphically

```{r, fig.width= 12, fig.height=10}
df_tt_50p_flow %>%
  mutate(TT50F=ifelse(TT50F==0,NA,as.numeric(TT50F))) %>%
  na.omit() %>%
  ggplot(aes(x=SowingD,y=TT50F, linetype=factor(Block), colour=factor(Block))) +
  geom_point() +
  geom_line() +
  theme_bw()+
  facet_grid(Variable~Cultivar)

```


get means and SE 

```{r}
dfMean20 <-df_tt_50p_flow %>%
  group_by(SowTreat, Cultivar,Variable)%>%
  dplyr::select(TT50F)%>%
  summarise_all(funs(mean,sd))%>%
  filter(SowTreat=="S7")




```





```{r Calc50PercFlower}



# #Loop each plot to make it simple
# 
# #  loop to calculate tt_50p_flow for each var x sd x cv x block
# # cv <- unique(df_50_P$Cultivar)
# var <- unique(df_50_P$Variable)
# #sow <- unique(df_50_P$SowTreat)
# #sowd <- unique(df_50_P$SowingD)
# #block <- unique(df_50_P$Block)
# plots <- unique(df_50_P$Plot)
# 
# 
# # create empty df
# df_tt_50p_flow <- data.frame(Variable = NULL,
# #                              Cultivar = NULL,
# #                              SowTreat = NULL,
# #                              SowingD = NULL,
# #                              Block=NULL,
#                              Plot=NULL)
# #                              DAS= NULL,
# #                              TT50F = NULL)
# 
# #i=j=k=b=1
# # 
# # #loop trough each combination of factor levels
# # 
# # #for(i in 1:length(cv)){
#   for(j in 1:length(var)){
# #     #for(k in 1:length(sow)){
#       for(p in 1:length(plots)){
# 
#       # clean value holders
#       DAS_50p_flow <- 0
#       tt_50p_flow <- 0
# 
# 
#       #print(paste0(cv[i]," ",var[j]," ", sow[k], " B", block[b]))
#       # filter for each combination
# 
#   df_sub <- df_50_P %>%
#     subset(Plot == as.character(plots[p])) &
#     #Block == as.character(block[b]) &
#     Variable == as.character(var[j])
#     #SowTreat == as.character(sow[k]))
# 
#   summary(df_sub)
# 
#   # create percentage with maximum value recorded
#   # to avoid crossing the 50% line twice when flowering decreassed
# 
#   df_sub$av_Perc_max <- 0 # create new col
# 
#   for(z in 1:nrow(df_sub)) {
# 
#     df_sub$SimpleCat_Perc_max[z] <- max(df_sub$SimpleCat_Perc[z],
#                                  df_sub$SimpleCat_Perc_max[z-1])
# 
#   }
# 
#  # df_sub
#  # head(df_sub)
#  # tail(df_sub)
# # 
#   # Interpolate
#   y_ref <- 50 # y value where we want to find x by interpolation
# 
#   # interpolate
#   #find DAS at 50 Pecent Flower
# 
#   tryCatch(
#   DAS_50p_flow <- approx(df_sub$SimpleCat_Perc_max,
#   df_sub$av_DAS , xout = y_ref, rule = 1)$y,
#   error = function(e)
#   {
#   DAS_50p_flow <- NA
#   }
# )
#   #find TT at 50 Pecent Flower
#   tryCatch(
#   tt_50p_flow <- approx(df_sub$SimpleCat_Perc_max,
#   df_sub$av_TT , xout = y_ref, rule = 1)$y,
#   error = function(e)
#   {
#   tt_50p_flow <- NA
#   }
# )
# 
#   df_temp <- NULL
#   df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
#                              Variable = df_sub$Variable[1],
#                              SowTreat = df_sub$SowTreat[1],
#                              SowingD = df_sub$SowingD[1],
#                              Block = df_sub$Block[1],
#                              #Plot = df_sub$Plot[1],
#                              DAS50F = DAS_50p_flow,
#                              TT50F = tt_50p_flow)
# 
# 
#   df_tt_50p_flow <- rbind(df_tt_50p_flow,df_temp)
# 
#       }
#     }
#   
#  
# 
# # 
# # summary(df_tt_50p_flow)




```


-This new dataframe  contains the values of Days and thermal time for 50% of Bud, Flowering and Bur classes 
- Repeated values were removed. Dataframe df_tt_50p_flow contains: 144 plots x 3 classes = 432 rows.

- Save dataframe for next calculations in script 4 
```{r}

#write.table(df_tt_50p_flow,"df_tt_50p_flow.txt")

#summary(df_tt_50p_flow)
```

- Main graphs are produced in next script (3_1 Graphs )
- End of this script. Script 4 continues with graphics using df_tt_50p_flow.txt.



