---
title: "Flowering 6CV"
author: "CT"
date: "02.03.2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```
This script produces the rate of flowering develop 1/DAS and 1/TT50F

```{r loadFile}

setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\FlowIv2")

getwd()

#create file
df_flower <- read.table("df_tt_50p_flow.txt",header=TRUE)



# convert to date format
df_f <- df_flower %>%
  mutate(TT50F=ifelse(TT50F==0,NA,as.numeric(TT50F)))%>%
  mutate(DAS50F=ifelse(DAS50F==0,NA,as.numeric(DAS50F)))%>%
  
  mutate(SowingD=ymd(SowingD))%>%
  mutate(RateDAS50F=(1/DAS50F))%>%
  mutate(RateTT50F=(1/TT50F))


str(df_f)
head(df_f)
tail(df_f)
```

```{r}
summary(df_f)
```

Analysis of sowing date and cultivars for Bud considering Date 

```{r GraphBoxPlotBud, fig.height= 5, fig.width= 8}

 df_f %>%
  #use filter to check single variables -Bud, Flowering and Bur
  filter( Variable== "Bur") %>%
    tidyr::gather("Variable3","Value",RateDAS50F:RateTT50F) %>%
  mutate(Variable3=as.factor(Variable3))%>%

  ggplot(aes(x=SowingD,y=Value,colour=Cultivar, shape=Cultivar))+
  geom_point()+
  geom_line()+
  facet_grid(Variable3~., scales="free")+
  theme_bw()+
 # theme(axis.text.x = element_text(angle = 0, hjust = 1.5))+
  scale_x_date(date_breaks = "1 month",date_labels =  "%b")+
labs(x="Sowing Month")+
ylab(expression(1/Tt~"("^"o"*"Cd)"~~~~~~~~~~~~~~~~~~~~~~1/Days))


```



Then include the mean Temperature !!! TT cum 




Read Thermal Sum data. Need to include  values before 30 06 : 

Country	LocationYear	Date	DOY	Tx	Tm	MeanTt	Pp
NZ	Iversen2_2015	24/06/2015	175	7.30	-1.80	2.75	10.03173957
NZ	Iversen2_2015	25/06/2015	176	6.90	-3.90	1.50	10.033705
NZ	Iversen2_2015	26/06/2015	177	12.80	-0.70	6.05	10.03668323
NZ	Iversen2_2015	27/06/2015	178	17.40	-1.30	8.05	10.04067231
NZ	Iversen2_2015	28/06/2015	179	10.30	-1.70	4.30	10.04566961
NZ	Iversen2_2015	29/06/2015	180	17.30	3.70	10.50	10.05167184
NZ	Iversen2_2015	30/06/2015	181	18.50	1.30	9.90	10.05867507
"

```{r ReadThermalSumData}
# read raw data

#Temperatures from 24 June to 29 June included from Broadfield Niwa in excel Datalogger folder  Thermal Sum is created  in the the Thermal time project_TTCalc (R script_file)

#The df_CumTTiv.txt comes from the TTCalc script in the main Gitsubclover folder! Need to produce the file and add to the FlowIv2 folder for calculations 
 
df_TTSum <- read.table("df_CumTTiv.txt",header=TRUE)

# remove extra columns
df_TTSum <- df_TTSum %>%
dplyr::select(Date,MeanTt,Pp) %>%
  mutate(Date = ymd(Date))
 
#check
head(df_TTSum)

```

```{r}
summary(df_TTSum)
```

Merge dfs TTSum at Measurement and Sowing Date into Flowering df
```{r}
#First need to rename SowingD column to Date to merge 
#But does make sense to plot Mean temperature at sowing date? would be necessary to make mean temperature of the whole period untill flowering? 

df_fa <- df_f %>%
rename( Date = SowingD)
str(df_fa)

# Add Tt at measurement date
df_flowera <- merge(df_fa,df_TTSum, by="Date")

summary(df_flowera)
```


```{r}


# grah rate versus mean Temperature 
df_flowera %>%
  #use filter to check single variables -Bud, Flowering and Bur
  filter( Variable== "Bud") %>%
  
  tidyr::gather("Variable3","Value",RateDAS50F:RateTT50F) %>%
  mutate(Variable3=as.factor(Variable3))%>%

  ggplot(aes(x=as.numeric(as.character(Pp)),y=Value,colour=Cultivar, shape=Cultivar))+
  geom_point()+
  geom_line()+
  facet_grid(Variable3~., scales="free")+
  theme_bw()+
  #theme(axis.text.x = element_text(angle = 0, hjust = 1.0))+
labs(x="PpSowing")+
ylab(expression(1/Tt~"("^"o"*"Cd)"~~~~~~~~~~~~~~1/Days))

```

