---
title: "Graphics for relationships rate of flowering, mean temperature and mean Pp  "
author: "CT"
date: "23.07.2018"
output:
  pdf_document: default
  html_document: default
  word_document: default

note: build linear relattionships between rate flowering , Temp and Pp as per Evans 1992 and Nori 2014.
  
 Grab dataframe from script 12
 Need library plot3D 
 
---

```{r loadLibraries, echo=FALSE, include=FALSE}
#1
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library (segmented)
library(hydroGOF)
library(plot3D)

```
 
AIM:
- Estimate build relationship between rate of  flowering (1/days)  in relation to mean temperature and mean Pp


```{r   loadFile}
#2
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")

getwd()


```
## Change formats 

```{r}
#3 get dataframe created similar to ReAnalysis4 which is Rea6 - use Iversen DAS50Flwoering data
df_TempPp <- read.table("df_MeanRateFlower50F_TempsPhotoperiod_.txt",header=TRUE) 


str(df_TempPp)
```

## Prep data frame make the basic graph first ; select Antas first 


```{r}

Antas <-df_TempPp %>%
   group_by(Cultivar,SowTreat)%>%
  summarise_all(funs(mean))%>%
  filter (Cultivar=='Antas')
 



```

## Isert Plot3D code 
##Info at  : http://www.sthda.com/english/wiki/impressive-package-for-3d-and-4d-graph-r-software-and-data-visualization

```{r}
#4
#attribute vectors 


##example 
# x, y and z coordinates
#x <- sep.l <- iris$Sepal.Length
#y <- pet.l <- iris$Petal.Length
#z <- sep.w <- iris$Sepal.Width


# x, y and z coordinates
x <- temp <- Antas$meanTempAir_50F
z <- rate <- Antas$RateFlow 
y <- Pp <- Antas$meanPp50F

#scatter3D(x, y, z, clab = c("Sepal", "Width (cm)")

#basic#  scatter3D(x, y, z, clab = c("SowTreat"),theta = 15, phi = 20)

scatter3D(x, y, z, phi = 0, bty = "g",
        pch = 20, cex = 3, ticktype = "detailed",
        xlab = "Temperature", ylab = "Photoperiod", zlab = "Rate")
#how to space the labels ??

##FIX ME How do I manage labels ? 

```

## Try a different format  use text3D (#still not working )

```{r}

#FIX ME still working here ...not ready
str(Antas)

#text3D(x, y, z, labels, ...)

# data(Antas)
# 
# with(Antas, text3D (meanTempAir_50F, meanPp50F, RateFlow ,
#   labels = rownames(Antas), colvar = SowTreat,
#   col = gg.col(100), theta = 60, phi = 20,
#   xlab = "Temperature", ylab = "Pp", zlab = "Rate",
#   main = "Antas Flowering", cex = 0.6,
#   bty = "g", ticktype = "detailed", d = 2,
#   clab = c("SowTreat"), adj = 0.5, font = 2))


```

#Run  linear model politype review coef number ??

##formula Evans et al : Rate = a +b*Temp + c*Pp
##FIX ME : is this correct?  


```{r}

str(Antas)

# get empirical coefficients of equation
  polyType <- 2 # two as we'll do quadratic

polFit_df <- Antas %>%
  #group_by() %>%
  ##FIX ME : quadratic with 3 coefficients
  
  do(fittedEq = lm(RateFlow ~ poly(meanTempAir_50F *   meanPp50F, polyType ,raw = TRUE), data = .)) # note that raw is TRUE not to get orthogonal coeff
# loop through results and get coefficients

# get size of loop
noFactors <- length(unique(Antas$Cultivar)) # how many factors?
noCoeff <-   polyType + 2 # how many coeficients (polynomial no + 1 intercept)

# loop and print each coeff
for (f in 1:noFactors) {
  
  print("-----------------------------------------")
  print(Antas$Cultivar[f])
  
  
  for (c in 1:noCoeff) {
    
    print(paste0("Coeff_",c,": ",unname(polFit_df$fittedEq[[f]]$coefficients[c]) ))# remove coeff names
  }
  print(paste0("R2: ",(summary(polFit_df$fittedEq[[f]])$r.squared))) 
  print(paste0("R2 adjusted: ",(summary(polFit_df$fittedEq[[f]])$adj.r.squared)))
}

```



##formula Evans et al : Rate = a +b*Temp + c*Pp

```{r}


# NON-linear MULTIPLE regression

library(nls2)
# data for Rate 
# 0.008
# 0.009
# 0.009
# 0.011

data for Temperature 








mydf <- data.frame(flower=c(0.008, 0.009, 0.009, 0.011), PP=c(1,2,3,4,5,6), Temp= c(1,2,3,4,5,6))
fit <- nls(flower ~ a + b*PP + c*(Temp^2), data=mydf, start = list(a=exp(9.947),b=-2.011, c=2))
predict(newMod, newdata = data.frame(PP=c(1,2,3,4,5,6),Temp= c(1,2,3,4,5,6)))
coefficients(fit) 
confint(fit, level=0.95) # CIs for model parameters
fitted(fit) # predicted values
residuals(fit) # residuals
vcov(fit) # covariance matrix for model parameters 





```






##Now Add the accumulation of of soil temperatures to calculate the average temperature during the desired process (here 50% plants with first runner ). 

```{r}
#cumulate air
df_B <- df_A %>%
  mutate(SumAir = cumsum(AirTt)) %>%
  mutate(Date=dmy(Date))%>%
  dplyr::select(-AirTt)

#cumulate soil

df_Soil1 <- df_Soil %>%
  mutate(SumTempSo = cumsum(TempSoil10mm)) %>%
  #mutate(Date=dmy(Date))%>%
  dplyr::select(-TempSoil10mm)


```

check data with graph

```{r}
df_Soil1 %>%
  ggplot(aes(x=Date,y=SumTempSo)) +
  geom_point()

df_B%>%
  ggplot(aes(x=Date,y=SumAir)) +
  geom_point()

```


Merge dataframes by date

```{r}

# first merge the soil and air temperature dataframes 




df_Temp <- merge(df_Soil1,df_B,by="Date") 
str(df_Temp)

#Merge the two dataframes by Date
df1 <- merge(df_Prep,df_Temp, by.x="SowingD",by.y="Date") %>%
  mutate(soilTempAcc_sow = SumTempSo) %>% 
  mutate(airTempAcc_sow=SumAir)%>%
dplyr::select(-SumTempSo,-SumAir)

str(df1)



```

Need to force a date for 50 % of plants with runners  (round) to calculate the average temperature during this phase  

Save dataframe as txt file


```{r}


# force formats of dates
df1$Date <- round(df1$Date50FF,0)
df_Temp$Date <- round(df_Temp$Date,0)

#then repeat same procedure done for the sowing date but use the date for Flowering 
  df_merge <- merge(df1, df_Temp, by="Date") %>%
  mutate(soilTempAcc_50F = SumTempSo) %>%
  mutate(airTempAcc_50F=SumAir)%>%
  dplyr::select(-SumTempSo, -SumAir) %>%
 
    #str(df_merge )
  
  
#subtract accumulate temperature das1T from sowing 
  mutate(meanTempSoil_50F = (soilTempAcc_50F-soilTempAcc_sow)/DAS50F) %>% 
  mutate(meanTempAir_50F = (airTempAcc_50F-airTempAcc_sow)/DAS50F)
  
  summary(df_merge)

  ##Use this dataframe to build graph in script 4 
write.table(df_merge, "df_MeanTempTo50Flower.txt") 



```

#Incorporate the mean Pp as well 


## Read the daily Pp and  adjust formats 

```{r}

#create file
df_P <- read.table("df_CumTTiv.txt",header=TRUE)

#
str(df_P)
df_P$Date<-as.Date(df_P$Date)
str(df_P)

#adjust formats
df_P<-df_P%>%
 #mutate(Date=dmy(Date))%>%
  select(Date,Pp)

str(df_P)

```

# Now need to calculate the mean Pp

#FIX ME HERE ! why Pp> 20 hs??? find a better way! 


#Till here all good ! 

Need to force a date for 50 % of plants with flowers  (round) to calculate the average Pp during this phase  

Save dataframe as txt file.


```{r}


# force formats of dates
df_merge$Date <- round(df_merge$Date50FF ,0)
df_P$Date <- round(df_P $Date,0)

#then repeat same procedure done for the soing date but use the dat for 1 Trifoliate
  df_mergePp <- merge(df_merge, df_P, by="Date") 
  
  str(df_mergePp)


```


Calculate the mean photoperiod for the flowering period

```{r}


  df_Pp50FmeanTPp <-df_mergePp %>%
    mutate(meanPp50F = (Pp+Pp_sow)/2) %>%
  ##calculate the rate to Flowering 1/DAS50FFromEmerg
  mutate(RateFlow= 1/DAS50FFromEmerg)

str(df_Pp50FmeanTPp)

```

then select columns of interest and clean data frame for just 144 plots dataset  

```{r}

a <-df_Pp50FmeanTPp %>%
  select(SowingD:Block,meanTempSoil_50F,meanTempAir_50F,meanPp50F,RateFlow  )%>%
  group_by(SowTreat,Plot,Cultivar,Block)%>%
  dplyr::select(meanPp50F, meanTempAir_50F,meanTempSoil_50F,RateFlow)%>%
  summarise_all(funs(mean))
  

```

##That's Super  store this dataframe as txt table 
```{r}


#Save as table 
write.table(a, "df_MeanRateFlower50F_TempsPhotoperiod_.txt")


```



End of this script  (move for graphs  in script 13) 
