 ---
title: "Flowering 6CV - calculation Bud production period - duration"
author: "CT"
date: "30.02.2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Aim: Calculate Tt and Days for bud duration ...for how long subclovers keep producing buds? 

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
```


```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")
getwd()

#create file: this file was generated in the previous script FlowerProject2
```

- Here theaim is to calculate the period of bud production
- Read the dataframe created : df_Bud_Duration.txt
- analyse ANOVA 

```{r}
df_bud_duration <- read.table("df_Bud_Duration.txt",header=TRUE)


str(df_bud_duration)

# change formats
df_bud_duration <- df_bud_duration %>%
mutate(SowingD=dmy(SowingD)) %>%
mutate(DaysBudDuration=as.numeric(DaysBudDuration))

```


## create an average table Days of bud duration to compare with the hardseededness data 



```{r}

AverageBudDuration<-df_bud_duration %>%
  group_by(Cultivar, SowTreat)%>%
  dplyr::select(DaysBudDuration)%>%
  summarise_all(funs(mean))

write.table(AverageBudDuration, "AverageBudDuration.txt") 
##this will be used in scripts dealing with seedhardness....investigate trade offs phenology and hardseeds  

```


Run ANOVA for DAysBud Duration 


##stats for the number of days for bud duration 
##general use Sow Treat as Factor 

```{r}
 
str(df_bud_duration)

file <- df_bud_duration

file.subs <- file 

head(file.subs)
summary(file.subs)

#ANOVA

my.anova <- aov(DaysBudDuration ~ Cultivar*SowTreat+ Block, data = file.subs)
summary(my.anova)

```


There was an interaction between Cultivar and sowing date (P<0.001).


```{r}
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))

```

In S6 and S7 Monti and Narrikup had the longest period of blossom (mean of 106 days). 
The shortest bud duration occurred in S1,S2, S4 and S5 (mean of 33).
Among the cultivars Narrikup had the longest period of bud production (60) in contrast to Denmark and antas which had 43.5 days.  



## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(df_bud_duration$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```

## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_bud_duration %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(DaysBudDuration ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```

Cultivar differed only in S1, S3 and S6. 

##Perform ANOVA TT duration 


```{r}
 
str(df_bud_duration)

file <- df_bud_duration

file.subs <- file 

head(file.subs)
summary(file.subs)

#ANOVA

my.anova <- aov(TTBudDuration  ~ Cultivar*SowTreat+ Block, data = file.subs)
summary(my.anova)

```

```{r}

#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 

```







```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(df_bud_duration$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```

## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_bud_duration %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(TTBudDuration ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```





```{r}




```





- Main graphs are produced in next script (3_1 Graphs )
- End of this script. Script 4 continues with graphics using df_tt_50p_flow.txt.



