---
title: "Fitting Photothermal time relationship - increase decrease Pp "
author: "CT"
date: "12.07.2018"
output:
  pdf_document: default
  html_document: default
  word_document: default

note: include Pp analysis using selected datasets from Reanalysis scripts but use
  Iversen 2 collected data; this script is a continuation of script 9 and 10 and estimate linear fits for 
  
  y = Photorhemal time to Varialbe == flowering .
  x= Photoperiod target 
  
   (after Nori et al 2014)
  
  This script use the thermal time from first trifo (TT50F1T)
  
! 
---

```{r loadLibraries, echo=FALSE, include=FALSE}
#1
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library (segmented)
library(hydroGOF)


```
 
AIM:
- Estimate photothermal time to flowering TT to 50% flowering in relation to Pp


```{r   loadFile}
#2
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")

getwd()


```
## Change formats 

```{r}
#3 get dataframe with TTFlo1T
df_Flo1T <- read.table("DASTTToFloweringFromFirstTRif_MeanPp.txt",header=TRUE) 

#get the photperiods at phenophses 
df_tt_Pp <- read.table("PpSowEmer1TrifoRunner.txt",header=TRUE)



str(df_Flo1T )
str(df_tt_Pp)






```

## Yes, That's the dataframe ! ! 

```{r}
# Merge by plot


df_All <- merge(df_Flo1T, df_tt_Pp, by="Plot")
# force date format
df_All$SowingD <- dmy(df_All$SowingD)


```
##Calculate the photoperiod factor, Here consists of getting the  Pp_target - 10 / (16.7-10) and calculate Photothermal time 

```{r}

#5Tidy up data frame

str(df_All)

df_worked <-df_All%>%
dplyr::select(Plot, Cultivar,SowTreat, Variable,TTFlo1T,Pp1Trifo,PpEmerg, meanPp50F , PpRunner,SowingD )

```

## Prepare dataframe to fit linear equations in increasing and decreasing Pp ...

Photothermal is (Ppemerg-10/16.7-10) =PpEmerg-


```{r}
##empty 

df_worked 
## create indexes for increase Pp (ipp) and decrease Pp (dpp)
ipp <- c("S1","S2","S3", "S4", "S5")
dpp <- c("S6", "S7","S8")

##create indexes for the maturity or sensgroup: early or late as per rea nalysis 
early <- c("Monti","Narrikup")
late <-  c("Antas", "Denmark","Leura","Woogenellup")


##Include indexes

df_worked_A<-df_worked%>%
 mutate(Pp_dir = ifelse(SowTreat %in% ipp, "IncreasingPp", "DecreasingPp")) %>%
mutate(Pp_dir = as.factor(Pp_dir))%>%
  mutate(Pp_dir = ifelse(SowTreat %in% ipp, "IncreasingPp", "DecreasingPp")) %>%
mutate(Pp_dir = as.factor(Pp_dir))%>%
   mutate(Group = ifelse(Cultivar %in% early, "Early", "Late")) %>%
  mutate(Group = as.factor(Group))%>%
##Calculate PhotothermalTime
  mutate(PhoTherm=((PpEmerg-10)/6.7)*TTFlo1T)



```


Here graph PT against months the means 

```{r}

MeanData<-df_worked_A%>%
  ##remove the NA from Denmark and Leura 
  subset(TTFlo1T>1) %>%
  dplyr::select(Plot,Cultivar,SowTreat,SowingD, PpEmerg,Pp1Trifo, meanPp50F,PhoTherm,TTFlo1T,Pp_dir,Group)%>%
  group_by(Cultivar,SowTreat,Pp_dir,SowingD,Group)%>%
  dplyr::select(PpEmerg,TTFlo1T,meanPp50F,PhoTherm,Pp1Trifo)%>%
  summarise_all(funs(mean,sd))

```




```{r, fig.width=12, fig.height=7}


str(MeanData)

MeanData %>%
      ggplot(aes(x=SowingD, y= PhoTherm_mean, 
             colour=Group,
             linetype=Cultivar,
             fill=Group)) +
    geom_point(aes(shape = Cultivar),size=8, stroke=1.5) +
    theme_bw(base_size = 18) +
    #geom_smooth(method='lm',se=TRUE)+
    geom_line(aes())  +
    labs(x="Sowing Month") +
    ylab(expression(Mean~Photothermal~time~to~Flowering~"("^"o"*"Cd)")) + 
    scale_x_date(date_breaks = "months" , date_labels = "%b")+
    #facet_grid(VariableName~.,scales ="free") +
  
  theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 22))+
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 22))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 22))+
  theme(axis.title.y=element_text(angle = 90, hjust = 0.5, size= 22))+
  ylim(0,2000)+
  
    #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11)) +
    scale_shape_manual(values = c(1,2,0,4,7,8)) + 
#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+

 ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2)) +
    
# theme(strip.text = element_text(face="bold", size=9))+
   
  #label sizes 
theme(text = element_text(size = 24))

ggsave("plot_Prj11_PT_VsSowingMonth_AllCvs.tiff", width=14, height=8, dpi=600)
  
```



Here Graph the Photothermal time against Pp emergence for all cultivars 

use this (°Cd) 



```{r, fig.height=8, fig.width=15}



MeanData<-df_worked_A%>%
  ##remove the NA from Denmark and Leura 
  subset(TTFlo1T>1) %>%
  dplyr::select(Plot,Cultivar,SowTreat,PpEmerg,Pp1Trifo, meanPp50F,PhoTherm,TTFlo1T,Pp_dir,Group)%>%
  group_by(Cultivar,SowTreat,Pp_dir,Group)%>%
  dplyr::select(PpEmerg,TTFlo1T,meanPp50F,PhoTherm,Pp1Trifo)%>%
  summarise_all(funs(mean,sd))
  
  
##Create datapoint for error bar 
dfError<- MeanData %>%
  group_by(Cultivar)%>%
  summarise(SE=max(PhoTherm_sd)/1.73)%>%
 # mutate(PpEmerg_mean=18,PhoTherm_mean=1000) %>%
   mutate(Pp1Trifo_mean=17.5,PhoTherm_mean=1300) %>%
  ungroup()


str(MeanData)
g1 <-MeanData %>%
  ungroup() %>%
  #mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4","S5", "S6","S7","S8"),labels=c("June", #"July", "September", "November","December", "February","March","May")))%>%
  mutate(SowMonth= factor(SowTreat, 
                           levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
                           labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May"))) %>%
  #left_join(df_Photo_dir, by="SowTreat") %>%
  ##For Ppemergence
  #ggplot(aes(x=meanPp50F_mean, y= PhoTherm_mean))  +
  
  ##for fristtrifo (Pp1Trifo_mean)
 ggplot(aes(x=Pp1Trifo_mean, y= PhoTherm_mean))  +
  geom_point(colour= "black", alpha=0.5) +
  geom_point(aes(shape=SowMonth, colour=Group),size=6, stroke=1.5)+
  scale_shape_manual(values = c(1,2,3,4,5,6,7,8)) +
  #geom_text(aes(label=SowMonth),hjust=0, vjust=0,size=7) +
  #geom_errorbar(aes(ymin=PhylC_mean-PhylC_sd/2,
                    #ymax=PhylC_mean+PhylC_sd/2), width=1.5)+
  geom_errorbar(data=dfError, aes(ymin=PhoTherm_mean-SE,ymax=PhoTherm_mean+SE), width=.9)+
 
  #geom_smooth(method='lm',formula=y~x,alpha=0.01, aes(linetype=Pp_dir,fill = Pp_dir, colour="black"))+
    geom_smooth(method='lm',formula=y~x,alpha=0.01, aes(linetype=Pp_dir,fill = Pp_dir),colour="black")+
  #geom_smooth(method='lm',formula=y~x,alpha=0.1,  linetype = "dashed", colour= "grey")+
  
  theme_bw() +
  xlab(expression(Photoperiod~"("*"hours"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  ylab(expression(Mean~Photothermal~time~"("^"o"*"Cd)")) +
  theme(text = element_text(size=24))+
  facet_wrap(~Cultivar)+
  xlim(9,18)+
  ylim(0,2000)+
 #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   
  #label sizes 
theme(text = element_text(size = 24))
  

#grid.arrange(g1, g2, g3,g4,g41)
grid.arrange(g1)
# Save
ggsave("plot_Prjt11_PhotoThermalTime_Pp1Trifo.tiff", width=12, height=6, dpi=400)
#ggsave("plot_Prjt10_Phyllochron_PpFirstTrifo.tiff", width=12, height=6, dpi=400)

```





Then fit PhotothermalTime against Pp First Trifo


# Get linear coefficients of equations above
##check what are these P values lonly for the decreasing Photoperiod 

```{r}
library(broom)
options(scipen=999)

#Select the Pp you want to regress against PT50


# create the linear fits by groups o variables
#dfregInc <- df_worked_A %>% group_by(Cultivar, Pp_dir) %>%
 dfregCv <- df_worked_A %>% group_by(Cultivar) %>%
 # dfregGroup <- df_worked_A %>% group_by(Group) %>%
##For emergence use PpEmerg,
  ##do(fitreg = lm(PhoTherm ~ meanPp50F, data = .))
  do(fitreg = lm(PhoTherm ~ PpRunner, data = .))
  ##do(fitreg = lm(PhoTherm ~ Pp1Trifo, data = .))
  
  ##For First Trifo use  Pp1Trifo_mean
 #do(fitreg = lm(PhylC_mean ~ Pp1Trifo_mean, data = .))

# get the linear coefficients by group in a tidy data_frame
dfCoef <- tidy(dfregCv, fitreg)
dfCoef

#write.table(dfCoefInc, "CoefficientsregressionPT50AgainstPp1Trifo.csv")

```



```{r}


dfCoefInc = glance(dfregCv, fitreg)
dfCoefInc




```


