---
title: "Photothermal time "
author: "CT"
date: "09.07.2018"
output:
  pdf_document: default
  html_document: default
  word_document: default

note: include Pp analysis using selected datasets from Reanalysis scripts but use
  Iversen 2 collected data; this script is a continuation of script 8 and calculates the equations from Weir et al 1984.
  This script use the thermal time from emergence (TT50FromEmerg)
  
  
  Pt=FP x Tt 0<1 
  
  Tt target here 
  
  
  FP = (Pp -Pbase/Popt-Pbase)
  
  
  
  Set as default : Pbase = 10; Popt =16.7 (after Nori et al 2014)
---

```{r loadLibraries, echo=FALSE, include=FALSE}
#1
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library (segmented)
library(hydroGOF)


```
 
AIM:
- Estimate photothermal time to flowering TT to 50% flowering in relation to Pp


```{r   loadFile}
#2
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")

getwd()


```
## Change formats 

```{r}
#3 get dataframe created similar to ReAnalysis4 which is Rea6 - use Iversen DAS50Flwoering data
df_tt_Pp <- read.table("df_Pptargets_TT50F.txt",header=TRUE) 

#df_Pptargets_TT50FFromEmergence
df_tt_Pp <- read.table("df_Pptargets_TT50FFromEmergence.txt",header=TRUE)

# force date format
df_tt_Pp$SowingD <- ymd(df_tt_Pp$SowingD)
str(df_tt_Pp)


```

```{r}
#4

summary(df_tt_Pp)
```
##Calculate the photoperiod factor, Here consists of getting the  Pp_target - 10 / (16.7-10) and calculate Photothermal time 

```{r}

#5
df_FP <- df_tt_Pp %>%
  mutate(FP = as.numeric(Pp_target-10)/6.7 ) %>%
  mutate (Photo =FP*TT50F)

##Remember that TTtarget =0 is the sowing PP!! 

```

##Plot the Photohermal in Y against Photoperiod target 


```{r}
##empty

```


```{r}
str(df_FP)

```

# Plot Tt50 vs Pp at sowing overall mean selecting a TT_target of :
## 190 (nearly the first trifoliate phase )
## nearly 5 Trifoliate = 430
## nearly 9 Trifoliate = 460
## nearly Runner initiation = 600
## nearly flowering = 

## Need to filter the variable to graph : choose flowering 

```{r, fig.height=6, fig.width= 12}
str(df_FP)

 dfGraph1 <- df_FP %>% 
  dplyr::select(SowingD:Block, Photo , TT50FromEmerg, Pp_target , TT_target)%>%
  filter(TT_target!=1900)%>%

  group_by(Cultivar,SowingD,SowTreat,Variable) %>%
  #select variables to average 
  select(Cultivar,SowingD,SowTreat, Photo , TT50FromEmerg, Pp_target)%>%
  summarise_all(funs(mean))


#Remember that S5 A,D,W = no flowering 
 
dfGraph1 %>%
  filter(Variable=="Flowering") %>%
  ggplot(aes(x=Pp_target,y=Photo,colour=factor(Cultivar))) +
  geom_point(aes(shape= SowTreat), size=4)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  geom_point(size=5) +
  #geom_line() + 
  facet_grid(.~Cultivar)+
  theme_bw()+
    ylim(0,1500) + geom_smooth(stat='lm', fill='blue', alpha=0.2, stat = "identity") + geom_point(size=2,alpha=0.5,stat = "identity")
  

```

Just change the labels in graph to visualise the sowing date   


```{r, fig.height=5, fig.width=15}


dfGraph1 %>%
  ungroup()%>%
mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May")))%>%
   #filter(Cultivar=="Monti"| Cultivar=="Antas")%>%
  #filter (SowTreat== "S3"| SowTreat== "S4"|SowTreat== "S5"|SowTreat== "S6")%>%
  #ggplot(aes(x=Pp_sow,y=TT50F,colour=factor(Cultivar)))   +
   ggplot(aes(x=Pp_target,y=Photo,colour=factor(Cultivar))) +

  #  geom_point(aes(shape= SowTreat), size=4)+
  
  geom_text(aes(label=SowTreat),hjust=0, vjust=0,size=6) +
  theme_bw()+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
  ylab(expression(Mean~PhotoThermal~time~Flowering~"("^"o"*"Cd)")) + 
  xlab(" Photoperiod at First Trifoliate leaf (hours) ") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=18))+
 scale_x_continuous(limits = c(9,20))+
  scale_y_continuous(limits = c(0,1800)) + geom_smooth(stat='lm', fill='blue', alpha=0.2) + geom_point(size=2,alpha=0.5)
  
#theme(axis.title.y = element_text(face="bold", size=16))+
   

#ggsave("plot_Photoperioxxxx.png", width=16, height=6, dpi=400)

```



```{r}

#str(df_pp_all)

df_FP_all_mean <- df_FP %>%
  
    dplyr::select(Cultivar,Variable,SowTreat,Photo, TT50FromEmerg, TT_target,Pp_target)%>%
    group_by(Cultivar,SowTreat, Variable,TT_target)  %>%
    #filter(Variable=="Flowering") %>%
    summarise_all(funs(mean))

#str(df_FP_all_mean)

#summary (df_FP_all_mean)

```


get graph for antas 


```{r, fig.width=15, fig.height=6}

#str(df_pp_all)

  
   df_FP_all_mean  %>%
  ungroup() %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May")))%>%
  filter (Cultivar=="Woogenellup")%>%
  ggplot(aes(x=Pp_target,y=Photo))   +
  geom_text(aes(label=SowTreat, colour=Cultivar),hjust=0, vjust=0,size=4) +
    scale_colour_manual(values=c("#000000" ))+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  theme_bw() +
  ylab(expression(Mean~PhotoThermal~time~Flowering~"("^"o"*"Cd)")) + 
  #xlab(expression(Photoperiod~at~Thermal~time~Flowering~"("^"o"*"Cd)")) +
  xlab(" Photoperiod at Target Thermal times") +
 #facet_grid(.~Cultivar, scales="free")+
  
     
  facet_wrap(~TT_target, scales="free",ncol=6)+
     
   #facet_grid(TT_target~., scales="free")+
  theme(text = element_text(size=16))+
    xlim(9,20)+
    ylim(0,2000)+
#geom_smooth(stat='lm', fill='blue', alpha=0.2) + geom_point(size=2,alpha=0.5)
 geom_smooth(method='lm', fill='blue', alpha=0.2) + geom_point(size=2,alpha=0.5) 
  

```




plot...but this loop is now working : ) !!!!!!!

```{r, fig.width=15, fig.height=6}


indexCV <- unique(df_FP_all_mean$Cultivar)

 # 
 for (i in 1:length(indexCV)) {
#   
  # df <- df_pp_all_mean%>%subset(Cultivar==indexCV[i])
  
 
   #df <- df_FP_all_mean%>%subset(Cultivar==indexCV[i])
   df <- df_FP_all_mean%>%subset(Cultivar==indexCV[i])
   
  
    g <- df %>%
  ungroup() %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May")))%>%
  ggplot(aes(x=Pp_target,y=Photo))   +
  geom_text(aes(label=SowTreat, colour=Cultivar),hjust=0, vjust=0,size=5) +
    scale_colour_manual(values=c("#000000" ))+
      #geom_point()+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  theme_bw() +
  ylab(expression(Mean~PhotoThermal~time~Flowering~"("^"o"*"Cd)")) + 
  #xlab(expression(Photoperiod~at~Thermal~time~Flowering~"("^"o"*"Cd)")) +
  xlab(" Photoperiod at Target Thermal times") +
 #facet_grid(.~Cultivar, scales="free")+
  facet_wrap(~TT_target, scales="free",ncol=4)+
   #facet_grid(TT_target~., scales="free")+
  theme(text = element_text(size=16))+
    xlim(9,20)+
    ylim(0,2000) + geom_smooth(stat='lm', fill='blue', alpha=0.2) + geom_point(size=2,alpha=0.5)
  
  
  
  print(g)
  
  
}

```


get graph for antas 


```{r, fig.width=15, fig.height=6}

#str(df_pp_all)

  
   df_FP_all_mean  %>%
  ungroup() %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May")))%>%
  filter (Cultivar=="Antas")%>%
  ggplot(aes(x=Pp_target,y=Photo))   +
  geom_text(aes(label=SowTreat, colour=Cultivar),hjust=0, vjust=0,size=4) +
    scale_colour_manual(values=c("#000000" ))+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  theme_bw() +
  ylab(expression(Mean~PhotoThermal~time~Flowering~"("^"o"*"Cd)")) + 
  #xlab(expression(Photoperiod~at~Thermal~time~Flowering~"("^"o"*"Cd)")) +
  xlab(" Photoperiod at Target Thermal times") +
 #facet_grid(.~Cultivar, scales="free")+
  
     
  facet_wrap(~TT_target, scales="free",ncol=6)+
     
   #facet_grid(TT_target~., scales="free")+
  theme(text = element_text(size=16))+
    xlim(9,20)+
    ylim(0,2000)
  

```



## Check data

```{r, fig.height= 10 , fig.width=15}

Means<-df_FP_all_mean %>%
  filter(TT_target==0) %>%
  group_by(SowTreat,Variable)%>%
  summarise_all(funs(mean))

  ggplot(aes(x=Pp_target,y=TT50FromEmerg,colour=factor(Cultivar),shape=factor(SowTreat),size=3 )) +
  geom_point() + geom_line() +facet_grid(Cultivar~.)+
  theme_bw()

```



End of this script  (move for stats in script 10) 
