---
title: "ReAnalysis Table"
author: "CT"
date: "24.04.2017"
output:
  word_document: default
  html_document: default
note: include Pp analysis using selected datasets from Reanalysis scripts but use Iversen 2 collected data  
---

```{r loadLibraries, echo=FALSE, include=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library (segmented)
library(hydroGOF)

```
 
AIM:
- Estimate TT to 50% flowering in relation to Pp
- Find "when"" Pp has to be considered (i.e. Pp @ Tt between sowing till flowering)
- Do this by looking at figuest R2 fot Tt50 x Pp

```{r   loadFile}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\FlowIv2")

getwd()


```

```{r}
#get dataframe created similar to ReAnalysis4 which is Rea6 - use Iversen DAS50Flwoering data
df_tt_flow <- read.table("df_tt_50p_flow.txt",header=TRUE) 

# force date format
df_tt_flow$SowingD <- ymd(df_tt_flow$SowingD)
str(df_tt_flow)


```

```{r}
summary(df_tt_flow)
```

Bring weather dataset which is in df_CumTTIv.txt

```{r}

df_CumTT <- read.table("df_CumTTIv.txt",header=TRUE) %>%
  mutate(Date=ymd(Date)) %>%
  dplyr::select(-LocationYear,-Country)

summary(df_CumTT)

```

Then select just columns of interest 
```{r}

df_weather <- df_CumTT %>%
    dplyr::select(Date, SumTTday,Pp)

#  summary(df_CumTT2)
  summary(df_weather)

```

Merge and calculate the two datasets 

- SumTT is value at sowing from 24 Jun 2015 
- ttJuvMax (at flowering time) sets a limit for juvenile period

```{r}
# get TTsum at sowing
# estimates Tt with running TT sum from weather file
df_Iv <- merge(df_tt_flow, df_weather,
               by.x=c("SowingD"), 
               by.y=c("Date")) %>%
  ungroup()%>%
 # na.omit() %>%
  mutate(SumTtAtSowing = SumTTday) %>%
  dplyr::select(-SumTTday) %>%
  mutate(ttJuvMax = TT50F + SumTtAtSowing) 

# df_Iv$TTSumAtSow <- df_Iv$SumTTday
# 
# #df_Iv$Index <- as.factor(paste0(df_Iv$SowTreat,"_",df_Iv$Treatcultivar)) # used for loop later
# 
# df_Iv$SumTTday <- NULL

str(df_Iv)
```


```{r}
summary(df_Iv)
```

# Plot Tt50 vs Pp at sowing

```{r}

df_Iv %>%
  dplyr::select(Cultivar, SowTreat, Variable, TT50F, Pp) %>%
  group_by(Cultivar, SowTreat, Variable) %>%
  summarise_each(funs(mean,sd)) %>%
#  na.omit() %>%
  ggplot(aes(x=Pp_mean,y=TT50F_mean, colour=Cultivar)) +
  geom_point()+
  geom_line()+
  facet_grid(Variable~.)

```

## calc

Find running sumTT for each sowing date at sowing

- only to have a small df for function below

```{r}
sumTTatSow <- df_Iv %>%
  dplyr::select(SowTreat, SumTtAtSowing) %>%
  unique() %>%
  as.data.frame()

head(sumTTatSow)

```

Create function for retrieving photoperiod as a function of TT after sowing and SD treatment

- finds running TT at sowiong
- adds target to that and finds pp at that TT momrent
- tt_target is oCd after sowing when Pp is retrieved
- sowT is the sowing treatment (S1...)

```{r}

Pp_finder_func <- function(sowT, tt_target){
  
  #isolate the experiment and cultivar 
   df_tt_flowemp_wea <- df_weather 
   sTT <- sumTTatSow %>% dplyr::filter(SowTreat == sowT) %>% dplyr::select(SumTtAtSowing)
   
   # sum target to sumTT at time of sowing for this spesific sd
   tt_target_adj <- tt_target + sTT 
   
  # lookup for Pp at new tt sum in weather file
  tryCatch(  
  Pp_target <- approx(df_tt_flowemp_wea$SumTTday, 
  df_tt_flowemp_wea$Pp, xout = tt_target_adj, rule = 1)$y,
  error = function(e) 
  {
  Pp_target <- NA
  }
)
 
  return(Pp_target)
  
}

```

## Test function

```{r}
st <- "S7"

-------#test
tt_target <- 3633
#TTsum estimated to reach 1st trifoliate 

#test if function is working : example : 
Pp_finder_func(st, tt_target)
```

# Find Pp at a given Tt sum after sowing

- Sums ftxed Tt to sowing Tt and see what Pp is there
- Plots this Pp against TT to flowering
- See if there is a stronger relationship beteen Pp and Tt


```{r}


#Create the loop to identify each combination of cultivars - isolate and calculate stats for each Pp target.
#maybe use concatenate fro sowing date treatment and cultivar
#FIXME: use RMSE instrad of R2 to find best fit

#Flowering reference = flowRefPerc
#flowRefPerc <- 50

#TTpercflo <- 2.6 # degree days from 5 to full (100) flowering 
# #value calculated from DearEtAL1993_Reanalysis3 script
# 
# # # find max value of TTjuv possible per  group (i.e. Tt at slowering time)
# #  ttJuvMax <- df_Iv %>%
# #    filter(Variable=="Flowering") %>%
# #  #  group_by(SowTreat,Cultivar,Block) %>%
# #    rowwise() %>%
# #   mutate(ttJuvMax = TT50F+SumTTday)
# 
# #loop
# cvGroup <- unique(df_Iv$Treatcultivar)
# vc_temp <- vector()
# vc_all <- vector()
# 
# #i=t=1
# 
# summary(ttJuvMax)


```

Stopped here .. check repeated values

```{r}
df_Iv$cv_block_index <- as.factor(paste0(df_Iv$Cultivar,"_",df_Iv$Block))

summary(df_Iv)
```

## Segment df by Cv and block 

```{r}

cv_block <- (unique(df_Iv$cv_block_index))

df_Iv_flow <- df_Iv %>% dplyr::filter(Variable=="Flowering") %>% na.omit()

# Loop 
df_pp_all <- data.frame()

for(p in 1:length(cv_block)) {
  
  CBI <- cv_block[p]
  
  # segment plot of interesst
  df_sub <- df_Iv_flow %>% 
    dplyr::filter(cv_block_index==cv_block[p]) %>%
    mutate(Tt_event=ttJuvMax-SumTtAtSowing) # value of Tt at Flowering or pheno phase selected
  
  # loop through Tt chuncks after sowing
  # t is tt from sowing to the point where Pp is retrieved
    for(t in seq(from=0, to=min(df_sub$Tt_event), by=100)){
    
    TT_target <- t # tt from sowing to the point where Pp is retrieved
  
    # Calculate Pp at this Tt sum after sowing
    df_sub_pp <- df_sub %>%
    rowwise() %>%
    mutate(TT_target = t)  %>%
    mutate(Pp_target=Pp_finder_func(SowTreat,SumTtAtSowing + TT_target))
    
    # Bind all results
    df_pp_all <- rbind(df_pp_all,df_sub_pp)
   
    }
}

summary(df_pp_all)

```

## Check data

```{r, fig.height=20}

df_pp_all %>%
  ggplot(aes(x=Pp_target,y=Tt_event,colour=factor(TT_target),shape=factor(Block))) +
  geom_point() + geom_line() +facet_grid(factor(TT_target)~Cultivar)

```

