---
title: "Fitting  relationships rate of flowering, mean temperature and mean Pp  "
author: "CT"
date: "22.07.2018"
output:
  pdf_document: default
  html_document: default
  word_document: default

note: build linear relattionships between rate flowering , Temp and Pp as per Evans 1992 and Nori 2014.
  
 Grab dataframe with TT to start 
 Need library plot3D 
 
---

```{r loadLibraries, echo=FALSE, include=FALSE}
#1
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library (segmented)
library(hydroGOF)
library(plot3D)

```
 
AIM:
- Estimate build relationship between rate of  flowering (1/days)  in relation to mean temperature and mean Pp


```{r   loadFile}
#2
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")

getwd()


```
## Change formats 

```{r}
#3 get dataframe created similar to ReAnalysis4 which is Rea6 - use Iversen DAS50Flwoering data
df_tt_Pp <- read.table("df_Pptargets_TT50F.txt",header=TRUE) 

#df_Pptargets_TT50FFromEmergence
df_tt_Pp <- read.table("df_Pptargets_TT50FFromEmergence.txt",header=TRUE)

# force date format
df_tt_Pp$SowingD <- ymd(df_tt_Pp$SowingD)
df_tt_Pp$Block <- as.factor(df_tt_Pp$Block)
df_tt_Pp$TT_target <- as.factor(df_tt_Pp$TT_target)

str(df_tt_Pp)


```


## Now prepare the data frame to include the date of flowering and the rate (1/days)
## consider DAE (after emergence) ! ! 

```{r}
#4
#select columns of interest 

df_Prep <- df_tt_Pp%>%
 dplyr:: select(SowingD:Block,DAS50F, DAS50FFromEmerg,Pp_sow)%>%
  #find the date when 50F occurred  
  mutate(Date50FF= ymd(SowingD+DAS50F))

##Note that this is a long dataframe because of the loop in previous script (that's why so many lines FIX ME ...make it only 144 lines)
```

## Read the soil Temp data and Air temp data and  adjust formats 

```{r}

#create file
df_A <- read.table("AirTemp.txt",header=TRUE)
df_Soil <-read.table("SoilTemp.txt",header=TRUE)

#adjust formats
df_A %>%
  mutate(Date=dmy(Date))

str(df_A)

#adjust formats
df_Soil <- df_Soil%>%
mutate(Date=dmy(Date))


```


##Now Add the accumulation of of soil temperatures to calculate the average temperature during the desired process (here 50% plants with first runner ). 

```{r}
#cumulate air
df_B <- df_A %>%
  mutate(SumAir = cumsum(AirTt)) %>%
  mutate(Date=dmy(Date))%>%
  dplyr::select(-AirTt)

#cumulate soil

df_Soil1 <- df_Soil %>%
  mutate(SumTempSo = cumsum(TempSoil10mm)) %>%
  #mutate(Date=dmy(Date))%>%
  dplyr::select(-TempSoil10mm)


```

check data with graph

```{r}
df_Soil1 %>%
  ggplot(aes(x=Date,y=SumTempSo)) +
  geom_point()

df_B%>%
  ggplot(aes(x=Date,y=SumAir)) +
  geom_point()

```


Merge dataframes by date

```{r}

# first merge the soil and air temperature dataframes 




df_Temp <- merge(df_Soil1,df_B,by="Date") 
str(df_Temp)

#Merge the two dataframes by Date
df1 <- merge(df_Prep,df_Temp, by.x="SowingD",by.y="Date") %>%
  mutate(soilTempAcc_sow = SumTempSo) %>% 
  mutate(airTempAcc_sow=SumAir)%>%
dplyr::select(-SumTempSo,-SumAir)

str(df1)



```

Need to force a date for 50 % of plants with runners  (round) to calculate the average temperature during this phase  

Save dataframe as txt file


```{r}


# force formats of dates
df1$Date <- round(df1$Date50FF,0)
df_Temp$Date <- round(df_Temp$Date,0)

#then repeat same procedure done for the sowing date but use the date for Flowering 
  df_merge <- merge(df1, df_Temp, by="Date") %>%
  mutate(soilTempAcc_50F = SumTempSo) %>%
  mutate(airTempAcc_50F=SumAir)%>%
  dplyr::select(-SumTempSo, -SumAir) %>%
 
    #str(df_merge )
  
  
#subtract accumulate temperature das1T from sowing 
  mutate(meanTempSoil_50F = (soilTempAcc_50F-soilTempAcc_sow)/DAS50F) %>% 
  mutate(meanTempAir_50F = (airTempAcc_50F-airTempAcc_sow)/DAS50F)
  
  summary(df_merge)

  ##Use this dataframe to build graph in script 4 
write.table(df_merge, "df_MeanTempTo50Flower.txt") 



```


##inspect means air temp in each sowing date 
```{r}
MeanAirTemp<- df_merge %>%
  group_by(SowTreat)%>%
 dplyr::select(meanTempAir_50F)%>%
  summarise_all(funs(mean))


```



#Incorporate the mean Pp as well 


## Read the daily Pp and  adjust formats 

```{r}

#create file
df_P <- read.table("df_CumTTiv.txt",header=TRUE)

#
str(df_P)
df_P$Date<-as.Date(df_P$Date)
str(df_P)

#adjust formats
df_P<-df_P%>%
 #mutate(Date=dmy(Date))%>%
  select(Date,Pp)

str(df_P)

```

# Now need to calculate the mean Pp


#Till here all good ! 

Need to force a date for 50 % of plants with flowers  (round) to calculate the average Pp during this phase  

Save dataframe as txt file.


```{r}


# force formats of dates
df_merge$Date <- round(df_merge$Date50FF ,0)
df_P$Date <- round(df_P $Date,0)

#then repeat same procedure done for the soing date but use the dat for 1 Trifoliate
  df_mergePp <- merge(df_merge, df_P, by="Date") 
  
  str(df_mergePp)


```


Calculate the mean photoperiod for the flowering period

```{r}


  df_Pp50FmeanTPp <-df_mergePp %>%
    mutate(meanPp50F = (Pp+Pp_sow)/2) %>%
  ##calculate the rate to Flowering 1/DAS50FFromEmerg
  mutate(RateFlow= 1/DAS50FFromEmerg)

str(df_Pp50FmeanTPp)

```

then select columns of interest and clean data frame for just 144 plots dataset  

```{r}

a <-df_Pp50FmeanTPp %>%
  select(SowingD:Block,meanTempSoil_50F,meanTempAir_50F,meanPp50F,RateFlow  )%>%
  group_by(SowTreat,Plot,Cultivar,Block)%>%
  dplyr::select(meanPp50F, meanTempAir_50F,meanTempSoil_50F,RateFlow)%>%
  summarise_all(funs(mean))
  

```

##That's Super  store this dataframe as txt table 
```{r}


#Save as table 
write.table(a, "df_MeanRateFlower50F_TempsPhotoperiod_.txt")


```



End of this script  (move for graphs  in script 13) 
