---
title: "Fitting Photothermal time relationship - increase decrease Pp "
author: "CT"
date: "12.07.2018"
output:
  pdf_document: default
  html_document: default
  word_document: default

note: include Pp analysis using selected datasets from Reanalysis scripts but use
  Iversen 2 collected data; this script is a continuation of script 9 and 10 and estimate linear fits for 
  
  y = Photorhemal time to Varialbe == flowering .
  x= Photoperiod target 
  
   (after Nori et al 2014)
  
  This script use the thermal time from emergence (TT50FromEmerg)
  
## Note this is similar to script 9 untill line 108 ...retrieve original data .... then comes novelty! 
---

```{r loadLibraries, echo=FALSE, include=FALSE}
#1
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library (segmented)
library(hydroGOF)


```
 
AIM:
- Estimate photothermal time to flowering TT to 50% flowering in relation to Pp


```{r   loadFile}
#2
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")

getwd()


```
## Change formats 

```{r}
#3 get dataframe created similar to ReAnalysis4 which is Rea6 - use Iversen DAS50Flwoering data
df_tt_Pp <- read.table("df_Pptargets_TT50F.txt",header=TRUE) 

#df_Pptargets_TT50FFromEmergence
df_tt_Pp <- read.table("df_Pptargets_TT50FFromEmergence.txt",header=TRUE)

# force date format
df_tt_Pp$SowingD <- ymd(df_tt_Pp$SowingD)
df_tt_Pp$Block <- as.factor(df_tt_Pp$Block)
df_tt_Pp$TT_target <- as.factor(df_tt_Pp$TT_target)

str(df_tt_Pp)


```

## Yes, That's the dataframe ! ! 

```{r}
#4

summary(df_tt_Pp)
```
##Calculate the photoperiod factor, Here consists of getting the  Pp_target - 10 / (16.7-10) and calculate Photothermal time 

```{r}

#5
df_FP <- df_tt_Pp %>%
  mutate(FP = as.numeric(Pp_target-10)/6.7 ) %>%
  mutate (Photo =FP*TT50F)

##Remember that TTtarget =0 is the sowing PP!! 

```

## Prepare dataframe to fit linear equations in increasing and decreasing Pp ...




```{r}
##empty 

str(df_FP)



```



# Get linear coefficients of equations above
##check what are these P values lonly for the decreasing Photoperiod 

```{r}
library(broom)
options(scipen=999)

IncreasePp <-df_FP%>%
  filter(SowTreat=="S1"| 
         SowTreat=="S2"| 
         SowTreat=="S3"|
         SowTreat=="S4")

str(IncreasePp)

# create the linear fits by groups o variables
dfregInc <- IncreasePp %>% group_by(Cultivar, TT_target) %>%
##For emergence use PpEmerg_mean,
  do(fitreg = lm(Photo ~ Pp_target, data = .))

  ##For First Trifo use  Pp1Trifo_mean
 #do(fitreg = lm(PhylC_mean ~ Pp1Trifo_mean, data = .))

# get the linear coefficients by group in a tidy data_frame
dfCoefInc <- tidy(dfregInc, fitreg)
dfCoefInc


```



```{r}


dfCoefInc = glance(dfregInc, fitreg)
dfCoefInc

```





----------------Started Increase Pp-------------------
##Create dataframe with increasing Pp (S1- S5)
## Prep dataframe with only 


```{r}

df_IncPp <-df_FP %>%
  filter(SowTreat =="S1"| SowTreat=="S2"| SowTreat =="S3" |SowTreat =="S4"|SowTreat =="S5")%>%
select(SowingD:Block, TT_target, Photo, Pp_target)

```

##Remember this key values!  :
## 190 (nearly the first trifoliate phase )
## nearly 5 Trifoliate = 430
## nearly 9 Trifoliate = 460
## nearly Runner initiation = 600
## nearly flowering = 


##Now fit linear regressions for each ! Do it first for Photothermal time (y) and Pp target (x) Loop by plot  

```{r}

str(df_IncPp)

```


##This code is similar to HardseedProjectLive_4Calc

```{r}

df_IncPp$LoopIndex <- as.factor(paste0(df_IncPp$Cultivar,"_",df_IncPp$TT_target)) # prepare for loop below

str(df_IncPp)

```



##then loop every plot and depth to find the linear equation and print a list of the coefficients and R2. 
```{r}
all.data<-data.frame()
counter<-0
 #plots<-unique(df_IncPp$Plot)
# depth<-unique(dfSubSet$Depth)

#li<- unique(dfSubSet$LoopIndex)
li<- unique(df_IncPp$LoopIndex)

#slopeType <- c("perDay","perTt")
 
slopeType <- c("perPhotoTT")

#length(plots)*length(depth)

#p=d=1
for(p in 1:length(slopeType)) {
  for(d in 1:length(li)) {
  df_sub <- data.frame()  
   # print(paste0(plots[p],"_",depth[d]))
  #  counter<-counter+1
    
 
 # df_sub <- dfSubSet %>% filter(LoopIndex==li[d])
   df_sub <- df_IncPp %>% filter(LoopIndex==li[d])
  
  ## Linear fit
  
# select type of slope calculated  
if(slopeType[p]=="Photo") {
  x <- df_sub$Pp_target
} else {
    x <- df_sub$Pp_target
}
  
 # x <- df_sub$Days
 # x <- df_sub$TtSum
  y <- df_sub$Photo
  
  #print(data.frame(x=x,y=y))
  
  fit <- NULL
  fit <- lm(y ~ x)
  
  intercept <- round(fit$coefficients[[1]],2)
  slope <- round(fit$coefficients[[2]],3)
  r2 <- round(summary(fit)$r.squared * 100,2)
  # summary(fit)$adj.r.squared
  cv <- as.character(df_sub$Cultivar[1])
  block <- as.character(df_sub$Block[1])
  sow <- as.character(df_sub$SowTreat[1])  
  sd <- dmy(df_sub$SowingD[1])
  slopeType <- factor(slopeType) 
  plot<- as.character(df_sub$Plot[1])
  TT<- as.character(df_sub$TT_target[1])
  
  
  buf <- data.frame(slopeType=slopeType[p], sow=sow,cv=cv, block=block, plot=plot, TT=TT, int=intercept, slope=slope, r2=r2, n=nrow(df_sub))
  
  all.data <- rbind(buf, all.data)
  
 # print(buf)
  
  #print(nrow(df_sub))
    
  #subset(dfSubSet, (dfSubSet$Plot==plots[p] & Depth == depth[d]))
    
  }
  
}

summary(all.data)

```

##Save data as table for Increase Pp



```{r, fig.width=15, fig.height=6}

df_FitIncPp<- all.data 

write.table(df_FitIncPp, "df_FitLinear_PhotoTherm_IncreasePp.txt")
  

```








----------------End of loop for Increased Pp----------

##Ok Now repeat the process for the decreasing Photoperiod 
##Select from  Feb (S6) to Jun (S1)



```{r}

df_DecPp <-df_FP %>%
  filter(SowTreat =="S6"| SowTreat=="S7"| SowTreat =="S8" |SowTreat =="S1")%>%
select(SowingD:Block, TT_target, Photo, Pp_target)

```

##Remember this key values!  :
## 190 (nearly the first trifoliate phase )
## nearly 5 Trifoliate = 430
## nearly 9 Trifoliate = 460
## nearly Runner initiation = 600
## nearly flowering = 


##Now fit linear regressions for each ! Do it first for Photothermal time (y) and Pp target (x) Loop by plot  

```{r}

str(df_DecPp)

```


##Prepare data frame for second loop 

```{r}

df_DecPp$LoopIndex <- as.factor(paste0(df_DecPp$Cultivar,"_",df_DecPp$TT_target)) # prepare for loop below

str(df_DecPp)

```



then loop every plot and depth to find the linear equation and print a list of the coefficients and R2. 
```{r}
all.data<-data.frame()
counter<-0
 #plots<-unique(df_IncPp$Plot)
# depth<-unique(dfSubSet$Depth)

#li<- unique(dfSubSet$LoopIndex)
li<- unique(df_DecPp$LoopIndex)

#slopeType <- c("perDay","perTt")
 
slopeType <- c("perPhotoTT")

#length(plots)*length(depth)

#p=d=1
for(p in 1:length(slopeType)) {
  for(d in 1:length(li)) {
  df_sub <- data.frame()  
   # print(paste0(plots[p],"_",depth[d]))
  #  counter<-counter+1
    
 
 # df_sub <- dfSubSet %>% filter(LoopIndex==li[d])
   df_sub <- df_DecPp %>% filter(LoopIndex==li[d])
  
  ## Linear fit
  
# select type of slope calculated  
if(slopeType[p]=="Photo") {
  x <- df_sub$Pp_target
} else {
    x <- df_sub$Pp_target
}
  
 # x <- df_sub$Days
 # x <- df_sub$TtSum
  y <- df_sub$Photo
  
  #print(data.frame(x=x,y=y))
  
  fit <- NULL
  fit <- lm(y ~ x)
  
  intercept <- round(fit$coefficients[[1]],2)
  slope <- round(fit$coefficients[[2]],3)
  r2 <- round(summary(fit)$r.squared * 100,2)
  # summary(fit)$adj.r.squared
  cv <- as.character(df_sub$Cultivar[1])
  block <- as.character(df_sub$Block[1])
  sow <- as.character(df_sub$SowTreat[1])  
  sd <- dmy(df_sub$SowingD[1])
  slopeType <- factor(slopeType) 
  plot<- as.character(df_sub$Plot[1])
  TT<- as.character(df_sub$TT_target[1])
  
  
  buf <- data.frame(slopeType=slopeType[p], sow=sow,cv=cv, block=block, plot=plot, TT=TT, int=intercept, slope=slope, r2=r2, n=nrow(df_sub))
  
  all.data <- rbind(buf, all.data)
  
 # print(buf)
  
  #print(nrow(df_sub))
    
  #subset(dfSubSet, (dfSubSet$Plot==plots[p] & Depth == depth[d]))
    
  }
  
}

summary(all.data)

```





```{r, fig.width=15, fig.height=6}

df_FitDecPp<- all.data 

write.table(df_FitDecPp, "df_FitLinear_PhotoTherm_DecreasePp.txt")
  

```

----------------End of loop for Decrease Pp----------




End of this script  (move for stats in script 10) 
