---
title: "thermal time to flower versus Mean Photoperiod analysis "
author: "CT"
date: "09.07.2018"
output:
  pdf_document: default
  html_document: default
  word_document: default

note: include Pp analysis using the mean photoperiod to compare with the results from the re analysis. 
  Iversen 2 collected data; this script is a continuation of script 9 .
  This script use the thermal time from emergence (TT50FromEmerg)
  
  Next scrip 8b contains all the Photoperiods!!! 
  
---

```{r loadLibraries, echo=FALSE, include=FALSE}
#1
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
#library (segmented)
#library(hydroGOF)


```
 
AIM:
- Plot the thermal time to flower against the mean photoperiod (as per Evans and re analysis)


```{r   loadFile}
#2
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")

getwd()


```
## Change formats

##file is : TT50FloAndMeanPhotoperiod 

```{r}
#3 get dataframe created similar to ReAnalysis4 which contains the mean photoperiod 
df_tt_MeanPp <- read.table("TT50FloAndMeanPhotoperiod .txt",header=TRUE) 

##bring file : Project1_Total_SeedYieldIv2.txt
df_SeedYield <- read.table("Project1_Total_SeedYieldIv2.txt",header=TRUE) 
#df_Pptargets_TT50FFromEmergence
#df_tt_Pp <- read.table("df_Pptargets_TT50FFromEmergence.txt",header=TRUE)

# force date format
df_tt_MeanPp$SowingD <- dmy(df_tt_MeanPp$SowingD)
str(df_tt_MeanPp)


```

```{r}
#4

summary(df_tt_MeanPp)
```


Insert total seed Yield values by plot 

```{r}
str(df_SeedYield)
 
A<-df_SeedYield%>%
  dplyr::select(Plot,Seedskg_ha)

FlowerSeedYield <-merge(df_tt_MeanPp,A, by="Plot")

```





simply plot the TT50FromEmerg in y and Mean Pp in x 



```{r}

## create indexes for increase Pp (ipp) and decrease Pp (dpp)
ipp <- c("S1","S2","S3", "S4", "S5")
dpp <- c("S6", "S7","S8")

##create indexes for the maturity or sensgroup: early or late as per rea nalysis 
early <- c("Monti","Narrikup")
late <-  c("Antas", "Denmark","Leura","Woogenellup")


df_FP_all_mean <- df_tt_MeanPp  %>%
    dplyr::select(Cultivar,Variable,SowTreat,TT50FromEmerg, meanPp50F,SowingD) %>%
    group_by(Cultivar,SowTreat, Variable) %>%
    summarise_all(funs(mean,sd))  %>%
  ungroup() %>%
  mutate(Pp_dir = ifelse(SowTreat %in% ipp, "IncreasingPp", "DecreasingPp")) %>%
  mutate(Pp_dir = as.factor(Pp_dir))%>%
  mutate(Group = ifelse(Cultivar %in% early, "Early", "Late")) %>%
  mutate(Group = as.factor(Group))

#str(df_FP_all_mean)

summary (df_FP_all_mean)

```





```{r, fig.width=15, fig.height=6}

#str(df_pp_all)

  
   df_FP_all_mean  %>%
  ungroup() %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May")))%>%
  filter (Cultivar=="Woogenellup")%>%
  ggplot(aes(x=meanPp50F_mean ,y=TT50FromEmerg_mean))   +
  geom_text(aes(label=SowTreat, colour=Cultivar),hjust=0, vjust=0,size=4) +
    scale_colour_manual(values=c("#000000" ))+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  theme_bw() +
  ylab(expression(Mean~Thermal~time~Flowering~"("^"o"*"Cd)")) + 
  #xlab(expression(Photoperiod~at~Thermal~time~Flowering~"("^"o"*"Cd)")) +
  xlab(" Mean Photoperiod") +
 #facet_grid(.~Cultivar, scales="free")+
  
     
  facet_wrap(~Cultivar, scales="free",ncol=6)+
     
   #facet_grid(TT_target~., scales="free")+
  theme(text = element_text(size=16))+
   # xlim(9,20)+
    ylim(0,2000)+
#geom_smooth(stat='lm', fill='blue', alpha=0.2) + geom_point(size=2,alpha=0.5)
 geom_smooth(method='lm', fill='blue', alpha=0.2) + geom_point(size=2,alpha=0.5) 
  

```




All togteher 

```{r, fig.width=15, fig.height=10}

  df_FP_all_mean %>%
  ungroup() %>%
    mutate (SowTreat= factor(SowTreat, 
    levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
    labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May"))) %>%
  ggplot(aes(x=meanPp50F_mean ,y=TT50FromEmerg_mean))   +
  geom_text(aes(label=SowTreat, colour=Cultivar),hjust=0, vjust=0,size=5) +
  ylab(expression(Mean~Thermal~time~Flowering~"("^"o"*"Cd)")) + 
  xlab(" Mean Photoperiod ") +
  facet_grid(Cultivar~., scales="free")+
  theme(text = element_text(size=16))+
  #xlim(9,20)+
  ylim(0,3000) #+ geom_smooth(stat='lm', fill='blue', alpha=0.2) 
 geom_point(size=2,alpha=0.5)
  
```

Make black and white graph 


```{r, fig.width=15, fig.height=10}
  df_FP_all_mean %>%
  ungroup() %>%
    mutate (SowTreat= factor(SowTreat, 
    levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
    labels=c("Jun", "Jul", "Sep", "Nov", "Dec", "Feb", "Mar", "May"))) %>%
  ggplot(aes(x=as.numeric(meanPp50F_mean),y=TT50FromEmerg_mean, 
             linetype= Pp_dir,
             colour=interaction(Group, Pp_dir),
             fill=interaction(Group, Pp_dir))) +
    geom_point(aes(shape = factor(Cultivar)), size=5) +
    geom_smooth(method='lm',se=TRUE, aes()) +
    labs(x="Mean photoperiod (hours)", y="Time to 50% flowering ") +
      scale_fill_manual(name="Interactions",
        values=c(Early.DecreasingPp="red", 
                 Late.DecreasingPp="blue", 
                 Late.IncreasingPp= "blue",
                 Early.IncreasingPp="red")) +
    scale_color_manual(name="Interactions",
        values=c(Early.DecreasingPp="red", 
                 Late.DecreasingPp="blue", 
                 Late.IncreasingPp= "blue",
                 Early.IncreasingPp="red"))
  
  
  
  
  
  
  # ylab(expression(Mean~thermal~time~flowering~"("^"o"*"Cd)")) + 
  # xlab(" Mean photoperiod (h) ") +
  # theme_bw()+
  # theme(text = element_text(size=18))+
  # ylim(0,3000) + 
  # geom_smooth(method='lm', aes(colour=interaction(Pp_dir)))+
  # geom_point(size=4,alpha=0.5,aes(shape=Cultivar))

```

```{r, fig.width=15, fig.height=10}
  
df_FP_all_mean %>%
  ungroup() %>%
    mutate (SowTreat= factor(SowTreat, 
    levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
    labels=c("Jun", "Jul", "Sep", "Nov", "Dec", "Feb", "Mar", "May"))) %>%
  ggplot(aes(x=as.numeric(meanPp50F_mean),y=TT50FromEmerg_mean)) +
  ylab(expression(Mean~thermal~time~flowering~"("^"o"*"Cd)")) +
  xlab(" Mean photoperiod (h) ") +
  theme_bw()  +
  ylim(0,3000) +
  geom_smooth(method='lm', aes( linetype=Pp_dir))+
  geom_point(size=5,alpha=0.5,aes(shape=Cultivar,colour=Group)) +
  theme(text = element_text(size=25)) +
    labs(linetype="Pp direction")

```


Insert graph here with das 





graph as sowing date in the X axis and thermal time at y axis  (parei aqui) 


```{r, fig.width=15, fig.height=10}

  df_FP_all_mean %>%
  ungroup() %>%
    mutate (SowTreat= factor(SowTreat, 
    levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
    #labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May"))) %>%
    labels=c("Jun", "Jul", "Sep", "Nov", "Dec", "Feb", "Mar", "May"))) %>%
  # ggplot(aes(x=as.numeric(month(SowingD)),y=TT50FromEmerg))   +
 ggplot(aes(x=SowingD_mean,y=TT50FromEmerg_mean, colour=Cultivar))   +
  #geom_text(aes(label=SowTreat),hjust=0, vjust=0,size=5) +
 # geom_text(aes(label=SowTreat),hjust=0, vjust=0,size=5) +
  ylab(expression(Thermal~time~flowering~"("^"o"*"Cd)")) + 
  xlab(" Sowing month ") +
 # facet_wrap(~Cultivar, scales="free", ncol=2)+
  theme_bw()+
  theme(text = element_text(size=18))+
 # theme(axis.text.x=element_text(angle = 90, hjust = 0.5))+
  scale_x_date(date_breaks = "3 month", 
                 labels=date_format("%b-%Y"),
                 limits = as.Date(c('2015-05-01','2016-08-01')))+
  #xlim(0,20)+
  ylim(0,3000) + 
  #geom_smooth(stat='lm', fill='grey', alpha=0.2) + 
#  geom_smooth(method ='lm', colour="black") +
  geom_point(size=2,alpha=0.5)+
  geom_line(aes(colour=Cultivar)) # +
#make sowing dates white  
  #  theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
  # #remove grid lines 
  #   theme(
  #    panel.border = element_rect(colour = "black", size = 3), 
  #    panel.grid.major = element_blank(),
  #    panel.grid.minor = element_blank(),
  #    axis.line = element_line(colour = "black"))
    
     #ggsave("plot_PhotoThermalTimeFloweringVsSowingMonth_AllCvs.tiff", width=16, height=14, dpi=600)

```

make a black and white graph

```{r, fig.width=15, fig.height=7 }

#then create the error bar position
#Here how to create the end error bar with max Sd 
# find size of bar per cultivar and temp
# find single position of x y to put the bar

#check name columns 

# str(df_FP_all_mean)
# 
# 
# #extraPos<- 1.10 # extra position for single error bar
# extraPos<- 1.1 # extra position for single error bar
# x_max<-max(df_FP_all_mean$SowingD_max)
# y_max<-max(df_FP_all_mean$TT50FromEmerg)
# 
# 
# sd_df <- df_FP_all_mean %>% 
#   group_by(Cultivar) %>%
#   dplyr::select(sd)%>%
#   summarise_all(funs(max))%>%
#   #summarise(max_sd = max(sd)) %>% 
#   ungroup() %>%
#   rowwise() %>%
#   mutate(ActTemp_max = x_max*extraPos, max = y_max*extraPos, max_sd=sd)
# 
# summary(sd_df)




  df_FP_all_mean %>%
  ungroup() %>%
    mutate (SowTreat= factor(SowTreat, 
    levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
    #labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May"))) %>%
    labels=c("Jun", "Jul", "Sep", "Nov", "Dec", "Feb", "Mar", "May"))) %>%
    ggplot(aes(x=SowingD_mean,y=TT50FromEmerg_mean, shape=Cultivar))   +
    ylab(expression(Thermal~time~flowering~"("^"o"*"Cd)")) + 
  xlab(" Sowing month ") +
 # facet_wrap(~Cultivar, scales="free", ncol=2)+
  theme_bw()+
  theme(text = element_text(size=26))+
 # theme(axis.text.x=element_text(angle = 90, hjust = 0.5))+
  scale_x_date(date_breaks = "3 month", 
                 labels=date_format("%b-%Y"),
                 limits = as.Date(c('2015-05-01','2016-08-01')))+
  #xlim(0,20)+
  ylim(0,3000) + 
  
  
  #geom_smooth(stat='lm', fill='grey', alpha=0.2) + 
#  geom_smooth(method ='lm', colour="black") +
  geom_point(size=8)+
  scale_shape_manual(values = c(1,2,0,4,7,8))+
  geom_line(aes(linetype_pal=Cultivar),colour="grey")  +


#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
   #  panel.grid.major = element_blank(),
   #  panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))

 ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
   
  #label sizes 
theme(text = element_text(size = 26))


    
     #ggsave("plot_ThermalTimeFlo_MeanPP_VsSowingMonth_AllCvs.tiff", width=14, height=8, dpi=600)

```

Do a graph with the days and TT 50 as per re analysis 

```{r}
##first gather variable TT50 and DAS50 in a column called Variable and value 
#str(df_tt_MeanPp)

df_Panel <- df_tt_MeanPp %>%
  dplyr::select(-Plot,-Variable,-Block)%>%
  gather(VariableName, VariableValue,DAS50FFromEmerg,TT50FromEmerg)%>%
  mutate(VariableName=as.factor(VariableName))

summary(df_Panel)


  
##now use df_Panelwork to build graph 

```

```{r}
## create indexes for increase Pp (ipp) and decrease Pp (dpp)
ipp <- c("S1","S2","S3", "S4", "S5")

##create indexes for the maturity or sensgroup: early or late as per rea nalysis 
early <- c("Monti","Narrikup")


df_Panelwork <- df_Panel %>%
 # dplyr::select(SowTreat,VariableValue, meanPp50F )%>%
  mutate(Pp_dir=factor(ifelse(SowTreat %in% ipp, "Increase","Decreasing"))) %>%
  mutate(Group=factor(ifelse(Cultivar %in% early, "Early","Late"))) %>%
  na.omit() %>%
  group_by(SowingD, Pp_dir, Group, Cultivar,SowTreat, VariableName) %>%
  summarise_all(funs(mean,sd)) %>%
  mutate(VariableName=factor(VariableName, 
                             level=c("DAS50FFromEmerg","TT50FromEmerg"),
                             labels=c("Days to flower","Thermal-time (degree days)"))) 

summary(df_Panelwork)
str(df_Panelwork)
```

Simple Graphs 

```{r, fig.width=15, fig.height=10 }


df_Panelwork %>%
  ggplot(aes(x=meanPp50F_mean,y=VariableValue_mean)) +
  geom_point()+
  facet_grid(VariableName~.,scales = 'free')

```



```{r, fig.width=15, fig.height=10 }


df_Panelwork %>%
  ggplot(aes(x=SowingD,y=VariableValue_mean)) +
  geom_point()+
  facet_grid(VariableName~.,scales = 'free')

```
 
 ##Now join comples aesthetics 



```{r, fig.width=12, fig.height=7}
  
str(df_Panelwork)

df_Panelwork %>%
  ggplot(aes(x=meanPp50F_mean,y=VariableValue_mean),
         linetype= Pp_dir,
             fill=interaction(Group, Pp_dir)) +
  
  #ylab(expression(Mean~thermal~time~flowering~"("^"o"*"Cd)")) +
  xlab(" Mean photoperiod (hours) ") +
  ylab(" Time to flowering ") +
  theme_bw() +
  geom_smooth(method='lm', aes( linetype=Pp_dir), colour="black")+
   
  facet_grid(VariableName~.,scales = 'free')+
  geom_point(size=8,alpha=0.99,aes(shape=Cultivar,colour=Group)) +
  scale_shape_manual(values = c(1,2,0,4,7,8))+
  theme(text = element_text(size=22)) +
    labs(linetype="Pp direction")+
  

 ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))+
 ##make sowing dates white  
  theme(strip.background = element_rect(colour = "black", fill = "white",size=2))


```



```{r, fig.width=12, fig.height=7}
  
str(df_Panelwork)

df_Panelwork %>%
  ggplot(aes(x=SowingD,y=VariableValue_mean)) +
  ylab(expression(Mean~thermal~time~flowering~"("^"o"*"Cd)")) +
  xlab("Sowing Month") +
   scale_x_date(date_breaks = "months" , date_labels = "%b")+
  ylab(" Time to flowering ") +
  theme_bw() +
  geom_smooth(method='lm', aes( linetype=Pp_dir), colour="black")+
  facet_grid(VariableName~.,scales = 'free')+
  geom_point(size=8,alpha=0.99,aes(shape=Cultivar,colour=Group)) +
  scale_shape_manual(values = c(1,2,0,4,7,8))+
  #theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 18))+
  theme(text = element_text(size=22)) +
    labs(linetype="Pp direction")+

 ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))+
 ##make sowing dates white  
  theme(strip.background = element_rect(colour = "black", fill = "white",size=2))


```

##Re graph as per re analyis Mena Pp in x axis


```{r, fig.width= 12,fig.height=10, warning=FALSE}

df_Panelwork %>%
  dplyr::rename(Pp_direction=Pp_dir) %>%
      ggplot(aes(x=meanPp50F_mean, y= VariableValue_mean, 
             colour=interaction(Group, Pp_direction),
             linetype= Pp_direction,
             fill=interaction(Group, Pp_direction))) +
    geom_point(size=5, aes(shape = Cultivar,)) +
    theme_bw(base_size = 18) +
    geom_smooth(method='lm',se=TRUE)+
    labs(x="Mean photoperiod (hours)", y="Time to 50% flowering ") +
    facet_grid(VariableName~.,scales ="free") +
    #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11)) +
    scale_shape_manual(values = c(1,2,0,4,7,8)) + 
    scale_fill_manual(name="Interactions",
        values=c(Early.Decreasing="black", 
                 Late.Decreasing="darkgrey", 
                 Late.Increase= "darkgrey",
                 Early.Increase="black")) +
    scale_color_manual(name="Interactions",
        values=c(Early.Decreasing="black", 
                 Late.Decreasing="darkgrey", 
                 Late.Increase= "darkgrey",
                 Early.Increase="black")) +
  ylim(0,NA)

#+ theme(legend.position = "top") 

ggsave("plot_Proj8a_Days_ThermalTimeFlo_vs_MeanPp_AllCvs.tiff", width=14, height=8, dpi=600)

```

##Re graph as per re analyis use Sowing Month in x axis; Do same graph per sowing month 



```{r, fig.width= 12,fig.height=8, warning=FALSE}

df_Panelwork %>%
      ggplot(aes(x=SowingD, y= VariableValue_mean, 
             colour=Group,
             linetype=Cultivar,
             fill=Group)) +
    geom_point(aes(shape = Cultivar),size=4) +
    theme_bw(base_size = 18) +
    #geom_smooth(method='lm',se=TRUE)+
    geom_line(aes())  +
    labs(x="Sowing Month", y="Time to 50% flowering ") +
    scale_x_date(date_breaks = "months" , date_labels = "%b")+
    facet_grid(VariableName~.,scales ="free") +
  
  #theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 22))+
  #theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 22))+
  #theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 22))+
  #theme(axis.title.y=element_text(angle = 90, hjust = 0.5, size= 22))+
  
    #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11)) +
    scale_shape_manual(values = c(1,2,0,4,7,8)) + 
#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
   #  panel.grid.major = element_blank(),
   #  panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))

 ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2)) +
    
# theme(strip.text = element_text(face="bold", size=9))+
   
  #label sizes 
theme(text = element_text(size = 20))

ggsave("plot_Days_ThermalTimeFlo_VsSowingMonth_AllCvs.tiff", width=14, height=8, dpi=600)
  
```



#do graph starting with y in zero  Days to Flower 

```{r, fig.width= 12,fig.height=6, warning=FALSE}

#str(df_Panelwork)


df_Panelwork %>%
  filter(VariableName =="Days to flower")%>%
      ggplot(aes(x=SowingD, y= VariableValue_mean, 
             colour=Group,
             linetype=Cultivar,
             fill=Group)) +
    geom_point(aes(shape = Cultivar),size=8) +
    theme_bw(base_size = 18) +
    #geom_smooth(method='lm',se=TRUE)+
    geom_line(aes())  +
    labs(x="Sowing Month", y="Number of days to 50% flowering ") +
    scale_x_date(date_breaks = "months" , date_labels = "%b")+
    #facet_grid(VariableName~.,scales ="free") +
  
  theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 22))+
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 22))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 22))+
  theme(axis.title.y=element_text(angle = 90, hjust = 0.5, size= 22))+
  ylim(0,300)+
  
    #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11)) +
    scale_shape_manual(values = c(1,2,0,4,7,8)) + 
#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
   #  panel.grid.major = element_blank(),
   #  panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+

 ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2)) +
    
# theme(strip.text = element_text(face="bold", size=9))+
   
  #label sizes 
theme(text = element_text(size = 24))

ggsave("plot_Prj8a_DAE50Flo_VsSowingMonth_AllCvs.tiff", width=14, height=8, dpi=600)
  
```

#do the graph now with Thermal time TT50 

```{r, fig.width= 12,fig.height=8, warning=FALSE}


df_Panelwork %>%
#  filter(VariableName =="Thermal-time (degree days)")%>%
      ggplot(aes(x=SowingD, y= VariableValue_mean, 
             colour=Group,
             linetype=Cultivar,
             fill=Group)) +
    geom_point(aes(shape = Cultivar),size=4) +
    theme_bw(base_size = 18) +
    #geom_smooth(method='lm',se=TRUE)+
    geom_line(aes())  +
    labs(x="Sowing Month") +
    ylab(expression(Mean~Thermal~time~Flowering~"("^"o"*"Cd)")) + 
    scale_x_date(date_breaks = "months" , date_labels = "%b")+
    #facet_grid(VariableName~.,scales ="free") +
  
 # theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 22))+
  #theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 22))+
  #theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 22))+
  #theme(axis.title.y=element_text(angle = 90, hjust = 0.5, size= 22))+
  ylim(0,NA)+
  
    #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11)) +
    scale_shape_manual(values = c(1,2,0,4,7,8)) + 
#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
   #  panel.grid.major = element_blank(),
   #  panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+

 ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2)) +
    
# theme(strip.text = element_text(face="bold", size=9))+
   
  #label sizes 
theme(text = element_text(size = 18)) +
        facet_grid(VariableName~., scales ='free')

ggsave("plot_Prjt8a_TT50Flo_VsSowingMonth_AllCvs.tiff", width=14, height=8, dpi=600)


```



#do graph with sowing month in X, flowering month in Y and seed yield as point size  

```{r, fig.width= 12,fig.height=6, warning=FALSE}

str(FlowerSeedYield)

FlowerSeedYieldWork<-FlowerSeedYield%>%
  dplyr::select(Plot,SowTreat, Cultivar,SowingD,DAS50F,Seedskg_ha)%>%
  group_by(Cultivar,SowTreat,SowingD)%>%
  dplyr::select(DAS50F,Seedskg_ha)%>%
  summarise_each(funs(mean,sd))%>%
  mutate(FlowerD=round(SowingD+DAS50F_mean,0))
  


#Graph it 
FlowerSeedYieldWork %>%
      ggplot(aes(x=SowingD, y= FlowerD, 
             colour=Cultivar)) +
    #geom_point(aes(shape=Cultivar))+
    geom_jitter(aes(size = (Seedskg_ha_mean), shape=Cultivar),stroke=1.7)+
    theme_bw(base_size = 18) +
    #geom_smooth(method='lm',se=TRUE)+
    #geom_line(aes())  +
    labs(x="Sowing Month", y="Flowering Month ") +
    scale_x_date(date_breaks = "months" , date_labels = "%b")+
    scale_y_date(date_breaks = "months" , date_labels = "%b")+
    scale_shape_manual(values = c(1,2,0,4,7,8)) + 
#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
   #  panel.grid.major = element_blank(),
   #  panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  ##Ablines
  geom_hline(yintercept=10, linetype="dashed", color = "black")+


 ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2)) +

   
  #label sizes 
theme(text = element_text(size = 24))

ggsave("plot_Prj8a_SowMonth_vs_FlowMonth_seedyield_AllCvs.tiff", width=14, height=8, dpi=600)
  
```






