---
title: "Flowering 6CV"
author: "CT"
date: "06.07.2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r loadLibraries, warning=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```
This script calculates the means of TTAS50Flo and perform the statistics 

```{r loadFile}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")

getwd()

#create file
df_raw <- read.table("df_tt_50p_flow.txt",header=TRUE)

head (df_raw)
```
check formats
```{r}

df_work<-df_raw %>%
  mutate(SowingD=ymd(SowingD)) %>%
  rename(PhenoStage=Variable)%>%
  mutate(Plot=factor(Plot), Block=factor(Block))
         
str(df_work)

```


Do Stats for DAS50F for Bud first 

```{r}
df_Bud <-df_work %>%
  filter(PhenoStage=="Bud")

```


Perform anova general using the TT50F 

```{r}


 file <- df_Bud
file.subs <- file 

head(file.subs)
summary(file.subs)

#ANOVA

my.anova <- aov(TT50F ~ SowTreat + Block, data = file.subs)
#my.anova <- aov(DAS50F ~ Cultivar + Block, data = file.subs)

summary(my.anova)
```

```{r}
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(df_Bud$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```

## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_Bud %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(DAS50F ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```



```{r}











```



Here only graph by month of sowing for report ; split in two graphs to be able to see cultivars. 

```{r, fig.height=6, fig.width=12}


  df_work_bud_mean <- df_work %>%
  tidyr::gather("Variable","Value",DAS50F:TT50F) %>%
  mutate(Variable=factor(Variable)) %>%
  dplyr::select(-Plot,-Block) %>%
  mutate(SowingD=factor(SowingD)) %>%
  group_by(Cultivar, SowTreat,SowingD,Variable,PhenoStage)%>%
  summarise_all(funs(mean,sd)) %>%
  ungroup() %>%
  mutate(SowingD=ymd(as.character(SowingD))) %>%
  rename(AvValue=mean)


summary(df_work_bud_mean)
  
  
  
```

here calculate max sd stopped here 

```{r}


df_work_bud_mean
#then create the error bar position
#Here how to create the end error bar with max Sd 
# find size of bar per cultivar and temp
# find single position of x y to put the bar

#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.1 # extra position for single error bar
x_max<-max(df_work_bud_mean$SowingD)
y_max<-max(df_work_bud_mean$AvValue)


sd_df <- df_work_bud_mean %>%
  na.omit() %>%
  dplyr::select(PhenoStage,Variable,sd) %>%
  group_by(PhenoStage,Variable) %>%
  summarise(max=max(sd),y_max=max(mean)) 
  

summary(sd_df)

```


graph DAS and TT 50Bud for all cultivars and sowing dates 

```{r, fig.height=6, fig.width=15}

df_work_bud_mean%>%
  
ggplot(aes(x=SowingD,y=mean, shape=Cultivar))+
  geom_point(aes(shape=Cultivar),size=5)+
    scale_shape_manual(values = c(1,2,0,4,7,8)) +
  facet_grid(Variable~PhenoStage, scales="free")+
  
    theme_grey(base_size = 16) +
    theme_bw()+
    geom_abline(intercept = 100, slope = 0, linetype=2)+
   
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
theme(text = element_text(size = 16))+
 # theme(axis.text.x = element_text(angle = 0, hjust = 1.5))+
  #scale_x_date(date_breaks = "1 month",date_labels =  "%b")+
labs(x="Sowing Month")+
    #limits = as.Date (c("2016"))
ylab(expression(Tt~"("^"o"*"Cd)"~~~~~~~~~~~~~~~~~~~~~~Days))
    
#ggsave("plot_xxx.png", width=12, height=6, dpi=400)
 summary(df_work_bud_mean)
```


here ho to calculate max se

```{r}





```



Make the mean and SE
`
```{r}

aMean <- a %>%
  tidyr::gather("Variable","Value",DAS50F:TT50F) %>%
  dplyr::select(SowingD,SowTreat, Variable, Value) %>%
  
  
  summarise_all(funs(max(PercGerm_cum), sd)) 
  summarise_all(funs)
  ggplot(aes(x=SowingD,y=Value, shape=Cultivar))+
    #scale_x_discrete(name="Mon")
  geom_point(aes(shape=Cultivar),size=5)+
    scale_shape_manual(values = c(1,2,0,4,7,8)) +
     #scale_shape_manual(values = c(1,2,0)) +
  #geom_line(aes(colour=Variable))+
  facet_grid(Variable3~., scales="free")+
  
    theme_grey(base_size = 16) +
    theme_bw()+
    geom_abline(intercept = 100, slope = 0, linetype=2)+
   
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
theme(text = element_text(size = 16))+
labs(x="Sowing Month")+
ylab(expression(Tt~"("^"o"*"Cd)"~~~~~~~~~~~~~~~~~~~~~~Days))
    



```





```{r}
write.table(a, "graph.txt")
```



Analysis of sowing date and cultivars for Bud considering Date 

```{r GraphBoxPlotBud}

 df_50Iv <- df_f %>%
  group_by(Cultivar,SowTreat,Variable)%>%
  filter (Variable=="Flowering"| Variable== "Bur")%>%
  summarise_each(funs(mean))

str(df_50Iv)

```

```{r}



df_50Iv %>%
  #use filter to check single variables -Bud, Flowering and Bur
  filter( Cultivar == "Monti") %>%
  tidyr::gather("Variable3","Value",DAS50F:TT50F) %>%
  mutate(Variable3=as.factor(Variable3))%>%
  ggplot(aes(x=SowTreat,y=Value,colour=Variable3, shape=Variable3))+
  geom_point()+
  geom_line()+
  facet_grid(Variable3~., scales="free")+
  theme_bw()+
 # theme(axis.text.x = element_text(angle = 0, hjust = 1.5))+
  #scale_x_date(date_breaks = "1 month",date_labels =  "%b")+
labs(x="SowTreat")+
ylab(expression(Tt~"("^"o"*"Cd)"~~~~~~~~~~~~~~~~~~~~~~1/Days))
```



Save df as a table to join with Reanalysis table  

```{r GraphSowingDateAndVariable,fig.width=10}

write.table(df_50Iv, "df_50Iv.txt")


```

Now do the same for Poukawa in another script within Folder is FlowPok


