---
title: "Flowering 6CV"
author: "CT"
date: "06.07.2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r loadLibraries, warning=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```
This script calculates the time from visible bud to petal (Reproductive 7) 

file is :TimeToPollination_BurMaturity (worked dataframe)

```{r loadFile}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")

getwd()

#create file
df_raw <- read.table("TimeToPollination_BurMaturity.txt",header=TRUE)

head (df_raw)
```
check formats
```{r}


  
  ##force format date 
  df_raw$SowingD <- dmy(df_raw$SowingD)
         
str(df_raw)

##remove the NA

subset<-df_raw %>%
  subset(TT_fromPetalToBur >1) ##eliminate the NA

```

Graph 



```{r}

#str(df_raw)



MeanData<-subset%>%
  dplyr::select(Plot:Block,TT_fromPetalToBur,SowingD)%>%
  group_by(Cultivar,SowTreat,SowingD)%>%
  dplyr::select(TT_fromPetalToBur)%>%
  summarise_all(funs(mean,sd))
  
  
  


```



```{r, fig.width=12, fig.height=7}


str(MeanData)

MeanData %>%
      ggplot(aes(x=SowingD, y= mean)) +
    geom_point(aes(shape = Cultivar),size=8, stroke=1.5) +
    theme_bw(base_size = 18) +
    #geom_smooth(method='lm',se=TRUE)+
    #geom_line(aes())  +
    labs(x="Sowing Month") +
    ylab(expression(Thermal~time~R6-R11~"("^"o"*"Cd)")) + 
    scale_x_date(date_breaks = "months" , date_labels = "%b")+
    #facet_grid(.~Cultivar,scales ="free") +
  
  theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 22))+
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 22))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 22))+
  theme(axis.title.y=element_text(angle = 90, hjust = 0.5, size= 22))+
  ylim(0,800)+
  
    #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11)) +
    scale_shape_manual(values = c(1,2,0,4,7,8)) + 
#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+

 ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2)) +
    
# theme(strip.text = element_text(face="bold", size=9))+
   
  #label sizes 
theme(text = element_text(size = 24))

ggsave("plot_Prj16_R6_R11_VsSowingMonth_AllCvs.tiff", width=14, height=8, dpi=600)
  
```



##Runa anova calendar Thermal time from visible bud to Petal (pollination)  

##DiffTT_BudToPetal that is the TT accumulated from Bud to Petal 




```{r}
 

df_work<-df_raw %>%
  #rename(PhenoStage=Variable)%>%
  mutate(Plot=factor(Plot), Block=factor(Block),Cultivar=factor(Cultivar))

  file <- df_work


file.subs <- file 

head(file.subs)
summary(file.subs)

#ANOVA

my.anova <- aov(DiffTT_BudToPetal  ~ SowTreat*Cultivar + Block, data = file.subs)
#my.anova <- aov(TT_fromPetalToBur  ~ SowTreat*Cultivar + Block, data = file.subs)
#my.anova <- aov(DAS9T ~ Cultivar + Block, data = file.subs)

summary(my.anova)

```


```{r}
#(LSD.test(my.anova, c("SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))

#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
```



## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(df_work$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```


## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_work %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(DiffTT_BudToPetal ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```

##ANOVA : the calendar days from bud to pollinated flower to bur PAREI AQUI



```{r}
str(df_work)


 file <- df_work


file.subs <- file 

head(file.subs)
summary(file.subs)

#ANOVA

#my.anova <- aov(DiffTT_BudToPetal  ~ SowTreat*Cultivar + Block, data = file.subs)
my.anova <- aov(TT_fromPetalToBur  ~ SowTreat*Cultivar + Block, data = file.subs)
#my.anova <- aov(DAS9T ~ Cultivar + Block, data = file.subs)

summary(my.anova)



```



```{r}
(LSD.test(my.anova, c("SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))

#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
```









## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_work %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(TT_fromPetalToBur ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```




```{r}
 
  file <- df_work


file.subs <- file 

head(file.subs)
summary(file.subs)

#ANOVA
##variable Days_fromPetalToBur
#my.anova <- aov(Days_fromPetalToBur  ~ SowTreat*Cultivar + Block, data = file.subs)
my.anova <- aov(TT_fromPetalToBur  ~ SowTreat*Cultivar + Block, data = file.subs)
#my.anova <- aov(DAS9T ~ Cultivar + Block, data = file.subs)

summary(my.anova)

```





```{r}
#(LSD.test(my.anova, c("SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))

(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))



```

