---
title: "similar to ReAnalysis Table"
author: "CT"
date: "24.04.2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
note: include Pp analysis using selected datasets from Reanalysis scripts but use Iversen 2 collected data  
---

```{r loadLibraries, echo=FALSE, include=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
#library (segmented)
library(hydroGOF)

```
 
AIM:
- Estimate temperature during flowering (form bud to bur 4) for individual sowing dates 

```{r   loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")

getwd()


```


Bring weather dataset which is in df_CumTTIv.txt

```{r}

df_weather <- read.table("df_CumTTIv.txt",header=TRUE) %>%
  mutate(Date=ymd(Date)) %>%
  dplyr::select(-LocationYear,-Country)
  #dplyr::select(Date, SumTTday,Pp) # FIXME: this is also run Tt - change name to SumTTday_run?

  summary(df_weather)

```

Get mean temperature during floweirng of S1 (24 June 2015 ) happened between 27 October  2015 and 15 December 2015 (mean flowering time 49 days)

```{r}
# determine the period and mean
S1 <-df_weather %>%
  subset(Date>"2015-10-27" & Date< "2015-12-15")%>%
  dplyr::select(MeanTt)%>%
  summarise_all(funs(mean))

 

```
Get mean temperature during flowering S2 (28 July 2015 ) happened between 5 November 2015 and 25 December 2015 (50 days)

```{r}
# determine the period and mean
S2 <-df_weather %>%
  subset(Date>"2015-11-05" & Date< "2015-12-25")%>%
  dplyr::select(MeanTt)%>%
  summarise_all(funs(mean))

```


Get mean temperature during flowering S3 (15 Sept 2015 ) happened between 29 November 2015 and 18 January 2016 (50 days)

```{r}
# determine the period and mean
S3 <-df_weather %>%
  subset(Date>"2015-11-29" & Date< "2016-01-18")%>%
  dplyr::select(MeanTt)%>%
  summarise_all(funs(mean))

```

Get mean temperature during flowering S4 (05 Nov 2015 ) happened between 25 December 2015 and 09 March 2016 (74 days)

```{r}
# determine the period and mean
S4 <-df_weather %>%
  subset(Date>"2015-12-25" & Date< "2016-03-09")%>%
  dplyr::select(MeanTt)%>%
  summarise_all(funs(mean))

```


