---
title: "Spectra of S2All FTIR test"
author: "CT"
date: "17.09.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default

This script runs anovas in specific bands (subset )
#here files have already been baselined corrected in OPUS. Raw data is on folder Bionami Matrix 25.04; worksheet Columns to R. In this script the analysis of wavenumber ranges and ANOVAS.

---


```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)
#library(hyperSpec)

```


```{r readData}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Spectra_S2_Anovas")
getwd()

info <- read.table ("S2All.txt",  header = TRUE)
##or launch the baselinedNormalised 


summary (info)

```
```{r}
str(info)
```


Adjust formats 

```{r}

info_av <- info %>%
  mutate(Plot=factor(Plot), Block=factor(Block), wavelength=factor(wavelength)) %>%
    dplyr::select(-Seed) %>%
  group_by(Plot, Cultivar,Block,wavelength) %>%
  summarise_all(funs(mean)) %>%
  mutate(wavelength=as.numeric(as.character(wavelength))) 

summary(info_av)

write.table(info_av, "Absorb_Per_WL.txt")

```

##Then transform spectra in Normalised spectra (used Mas. normalisation treatment on spectra )

##Keep columns names like that prior loop (easy) 


```{r}
info_av_norm <- info_av %>%
  mutate(AbsorbanceNorm=Absorbance/max(Absorbance)) %>%
  dplyr::select(-Hardness) %>%
  ungroup()
 
str(info_av_norm)

```
```{r}
summary(info_av_norm)
```


##Subset spectra for selected wavenumber 

```{r}




```




-------------------------ANOVAS -----------------------

# Region 3000 - 2800
##select band  of interest : in this case choose at 2930 cm-1 , which represents CH2 asymmetrical (lipids region) 



```{r}


##2930 cm-1
 # df_sp2930 <-info_av_norm %>%
 #   subset(wavelength  <2932 & wavelength  >2929)

##2855 cm-1
 # df_sp2855 <-info_av_norm %>%
 #   subset(wavelength  <2856 & wavelength  >2853)

##1745 cm-1
  # df_sp1745 <-info_av_norm %>%
  #   subset(wavelength  <1746 & wavelength  >1743)

##1732 cm-1
  #df_sp1732 <-info_av_norm %>%
    #subset(wavelength  <1733 & wavelength  >1731)

  
   # df_sp1610 <-info_av_norm %>%
   #   subset(wavelength  <1611 & wavelength  >1609)

#df_sp1441 <-info_av_norm %>%
     #subset(wavelength  <1442 & wavelength  >1440)

 #df_sp1425 <-info_av_norm %>%
     #subset(wavelength  <1426 & wavelength  >1424)

 #df_sp1377 <-info_av_norm %>%
     #subset(wavelength  <1378 & wavelength  >1376)

 #df_sp1337 <-info_av_norm %>%
    # subset(wavelength  <1339 & wavelength  >1336)

 #df_sp1250 <-info_av_norm %>%
     #subset(wavelength  <1251 & wavelength  >1249)

 #df_sp1150 <-info_av_norm %>%
     #subset(wavelength  <1153 & wavelength  >1149)

 #df_sp1100 <-info_av_norm %>%
     #subset(wavelength  <1102 & wavelength  >1099)

   #df_sp1025 <-info_av_norm %>%
       #subset(wavelength  <1027 & wavelength  >1024)

 df_sp897 <-info_av_norm %>%
      subset(wavelength  <898 & wavelength  >896)



```


check 

```{r}

#str(df_sp2930)
#str(df_sp2855)
#str(df_sp1745)
#str(df_sp1732)
#str(df_sp1610)
#str(df_sp1441)
#str(df_sp1425)
#str(df_sp1377)
#str(df_sp1337)
#str(df_sp1250)
#str(df_sp1150)
#str(df_sp1100)
#str(df_sp1025)
#str(df_sp897)

```



##- Now run anova in this band 
 
```{r, warning=FALSE }


##use dataframe = df_sp1745

#-------------------------------------------------

# Chosen transform log to do anova 

#file.subset <- df_sp2930 
#file.subset <- df_sp2855
#file.subset <- df_sp1745
#file.subset <- df_sp1732
#file.subset <- df_sp1610
#file.subset <- df_sp1441
#file.subset <- df_sp1425
#file.subset <- df_sp1377
#file.subset <- df_sp1337
#file.subset <- df_sp1250
#file.subset <- df_sp1150
#file.subset <- df_sp1100
#file.subset <- df_sp1025
file.subset <- df_sp897

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(AbsValue ~ Cultivar*IncubationDays, data = file.subset)
  my.anova <- aov(AbsorbanceNorm ~ Cultivar+Block, data = file.subset)               

    #-----------------------
summary(my.anova)

```



## Means separation with LSD (not using for while )

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```


##Using this : Tukey 

```{r}
#posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)
posthoc <- TukeyHSD(x=my.anova, "Cultivar", conf.level=0.95)
#posthoc <- TukeyHSD(x=my.anova, c("Cultivar","IncubationDays"), conf.level=0.95, TRUE)
posthoc



```




