---
title: "Framework for PCA analysis "
author: "CT"
date: "05.08.2017
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
- This script is the PCA analysis of the spectra of the S2 six cultivars from S2. 

-Used guidelines from : http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/118-principal-component-analysis-in-r-prcomp-vs-princomp/


```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)
library(calibrate)
library(factoextra)
```

# Get the segmented spectra  and continue here 
```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Spectra_S2_Anovas")
getwd()

df_G <- read.table("S2_BaselinedMaxNormBlock1And2.txt",header=TRUE)

str(df_G)
```

Here take the mean of each replicate !!Analyse at the replicate level!  To get the following treatment combinations : 
A01
A02
A03
M01
M02
M03
A841
A842
A843
M841
M842
M843


##Now you have the dataframe organized vertically: spread the wavenumber horizontally 



```{r}

#-------------here is just to produce a matrix to export to Unscrambleror PCA 
str(df_G)

dftemp <- df_G%>%
#filter(Wavenumber %in% 850:3599) %>% # select only wavelengths of interest
filter(Wavenumber %in% 1740:1750 | Wavenumber %in% 1240:1260)%>% 
  # select only wavelengths of interest
#filter(Wavenumber %in% 1600:1800) %>% # select only wavelengths of interest
mutate(Wavenumber=factor(Wavenumber), Block=as.factor(Block)) #

summary(dftemp)

df_U <- dftemp %>%
   tidyr::spread(Wavenumber, AbsorbanceNorm)# %>%
 #  mutate(RN=paste0(Cultivar,"_",Block))

#row.names(df_U) <-  df_U$RN    
```

```{r}
head(df_U)[,1:5]
```



## -------------here PCa starts

##Re label row names per replicate (or Block is the same)  

```{r readData}
# Transforming Cv to number
cv   <- as.vector(unique(df_U$Cultivar))
cv_n <- c(1,2,3,4,5,6)

#rownames(df_U) <- NULL

df_U_pca <- df_U %>%
  ungroup() %>%
  mutate(Cultivar = factor(Cultivar, levels=cv,labels=cv_n)) %>%
  mutate(Cultivar=as.numeric(as.character(Cultivar))) %>%
  mutate(Block=as.numeric(as.character(Block)))

head(df_U_pca)[,1:5]


```





```{r}


#Re label row names per cultivar and block (replicate to make graph)
 row.names (df_U_pca) <-c("A_1","A_2","A_3",
 "D_1","D_2","D_3",
 "L_1","L_2","L_3",
  "M_1","M_2","M_3",
  "N_1","N_2","N_3",
  "W_1","W_2","W_3")


#Re label row names per cultivar and block (replicate to make graph)
  # row.names (df_U_pca) <-c("A","A","A",
  # "D","D","D",
  # "L","L","L",
  #  "M","M","M",
  #  "N","N","N",
  #  "W","W","W")










```






```{r}
res.pca <- prcomp(df_U_pca, scale = TRUE)
summary(res.pca)
```

## Visualize eigenvalues (scree plot). Show the percentage of variances explained by each principal component. 

```{r, fig.height=5, fig.width=10}
 fviz_eig(res.pca)
```

```{r}
str(res.pca)

```

# loadings are rotation in pca object

##source: http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/118-principal-component-analysis-in-r-prcomp-vs-princomp/

```{r}
summary(res.pca$rotation)
```

Graph the loading of PC1 and PC2 

```{r, warning=FALSE}

LabelColumn<-row.names(res.pca$rotation)

load.graph <- res.pca$rotation %>%
  as.data.frame() %>%
  dplyr::select(PC1,PC2) %>%
  mutate(WaveLength=as.numeric(LabelColumn)) %>%
  na.omit() %>% # FIXME: Cultivar and block come with value ??????
  gather("PC","PC_Value",PC1:PC2) %>%
  mutate(PC=factor(PC))

summary(load.graph)

##remove data after 3050
B<-load.graph %>%
  subset(WaveLength<3050)

  
```


Loadings must fluctuate between 0 -1 !! 

```{r}



``` 


```{r}

```



```{r, fig.width=12}
B %>%
   
        mutate(Show_WL = ifelse(WaveLength <1799,"Region 2",
                          ifelse( WaveLength > 2802,"Region 1","NotShow"))) %>%
  
  filter(Show_WL != "NotShow") %>%
  ggplot(aes(x=WaveLength,y=PC_Value)) +
  geom_line() +
  geom_abline(slope=0,intercept=0, linetype=2, colout="darkgrey")+
  #xlab(expression(Wavenumber~"(cm"^"-1"*")"))+
  ylab("Loadings")+
  xlab("X-variables")+
   scale_x_reverse()+
  theme_bw() +
  facet_grid(PC~Show_WL, scale="free")+
  #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
  
  
   #remove grid lines 
    
    #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),

axis.line = element_line(colour = "black"))+
      #make panels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
  
theme(text = element_text(size = 26))+
theme(axis.text.y = element_text( size = 20))+
    theme(axis.title.y = element_text(face="bold", size=26))+
     #scale_y_continuous(breaks = c(seq(from = 0, to = 1.25, by = 0.01)))+
theme(axis.text.x=element_text(angle = 25, hjust=0.5,vjust=0,size = 22))+
theme(axis.title.x = element_text( size=26,face="bold"))+
  theme(axis.line.x = element_line(colour = 'black', size = 3))+
  theme(axis.line.y = element_line(colour = 'black', size = 3))+
  
   #margin y axis
  theme(axis.title.y = element_text(margin =margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.text.x = element_text(margin = margin(b=15)))+
  #tick labels 
  ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))
 

  
  
 ggsave("plot_LoadingsPC1PC2_S2_6Cv.tiff", width=20, height=10, dpi=400)
  
```


Separate the loading regions 


```{r, fig.width=10}


Region850_1800 <-load.graph %>%
   
    subset(WaveLength<2800)
  
min_x <- min(min(Region3600_2800$WaveLength))
max_x <- max(max(Region3600_2800$WaveLength))

  
  Region3600_2800  %>%
  ggplot(aes(x=WaveLength,y=PC_Value)) +
  geom_line() +
  geom_abline(slope=0,intercept=0, linetype=2, colour="darkgrey")+
  labs(x= "x variables ([PC1_59%] _ [PC2_20%])")+
   ylab(" Loadings ")+
  #scale_x_reverse()+
  #scale_x_continuous(breaks = c(seq(from = 1000, to = 1800, by = 100)))+
  
  theme_bw() +
  facet_grid(PC~., scale="free")+
   #facet_grid(PC~. )+
    scale_x_continuous(limits = c(min_x, max_x))+
    
  #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2)) +
  
  
   #remove grid lines 
    
    #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),

axis.line = element_line(colour = "black"))+
     #make panels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
  
theme(text = element_text(size = 26))+
theme(axis.text.y = element_text( size = 20))+
    theme(axis.title.y = element_text(face="bold", size=26))+
     #scale_y_continuous(breaks = c(seq(from = 0, to = 1.25, by = 0.01)))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 26))+
theme(axis.title.x = element_text( size=26,face="bold"))+
  theme(axis.line.x = element_line(colour = 'black', size = 3))+
  theme(axis.line.y = element_line(colour = 'black', size = 3))+
  
  #tick labels 
  ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))
  
  
  
  
  
 #ggsave("plot_SpectraS2_PCA2019.25.05_LoadingsPC1PC2_REgion850_1800_6Cv.tiff", width=20, height=10, dpi=400)
  
```

## get only the most important bands in each PC


```{r}

Selected <-load.graph%>%
  subset(PC_Value > 0.01)%>%
  mutate(Wavenumber=WaveLength)

```



##Graph of individuals. Individuals with a similar profile are grouped together. 

## Add PC1 = 57% and PC2= 28% in axis titles 


```{r}

fviz_pca_ind(res.pca,
             label = "all", invisible = "none", labelsize = 6,pointsize = 4,)+

  #xlim(-60, 60)+
  ylim(-30, 20)+
#if need the axes labels 
  xlab(expression(PC1~"(59%)"))+ 
  ylab(expression(PC2~"(21%)")) 



```




```{r}

summary (res.pca)




```





```{r, fig.height=5, fig.width=10}


str(res.pca$scale)

fviz_pca_ind(res.pca,
             #col.ind = "cos2", # Color by the quality of representation
             geom = c("point","text"),
             label = "all", invisible = "none", labelsize = 7,pointsize = 4,
             repel = TRUE     # Avoid text overlapping
             )+
             scale_color_gradient2(low="light green", mid="green",
      high="black", midpoint=0.6)+
   theme_bw()+
   theme(axis.text.y = element_text( size = 26))+
theme(axis.title.y = element_text(face="bold", size=26))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 26,face="bold"))+
theme(axis.title.x = element_text( face="bold", size=26))+
  
  
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
#if need the axes labels 
  xlab(expression(PC1~"(59%)"))+ 
  ylab(expression(PC2~"(21%)")) +
  xlim(-50, 50)+
  ylim(-30, 20)

   
 
```


##SAve the plot graph 

```{r}

#ggsave("S2_plot_PC1andPC2.png", width=14, height=7, dpi=500)

```

Clustering 


```{r}

#res.pca <- prcomp(df_sp.activeU ,scale = TRUE)

res.pca2 <-PCA(df_U_pca, ncp = 2, graph = FALSE)

res.hcpc <- HCPC(res.pca2, graph = FALSE)


fviz_cluster(res.hcpc,
             repel = TRUE,            # Avoid label overlapping
             show.clust.cent = TRUE, # Show cluster centers
             palette = "jco",         # Color palette see ?ggpubr::ggpar
             ggtheme = theme_minimal(),
             main = "Factor map"
             ) +
   theme_bw()+
   theme(axis.text.y = element_text( size = 24))+
theme(axis.title.y = element_text(face="bold", size=24))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 24,face="bold"))+
theme(axis.title.x = element_text( face="bold", size=24))+
  
  
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     #panel.grid.major = element_blank(),
     #panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
#if need the axes labels 
  xlab(expression(PC1~"(59%)"))+ 
  ylab(expression(PC2~"(21%)")) 
  #xlim(-50, 50)
  #ylim(-30, 20)




```





PC contributions 

```{r, fig.height=5 , fig.width=30}

# Contributions of variab

les to PC1
fviz_contrib(res.pca, choice = "var", axes = 1, top = 20)
# Contributions of variables to PC2
fviz_contrib(res.pca, choice = "var", axes = 2, top = 20)

```




## Graph of variables. Positive correlated variables point to the same side of the plot. Negative correlated variables point to opposite sides of the graph.

```{r, fig.height=5, fig.width=10}

fviz_pca_var(res.pca,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
             )



```

Biplot of individuals and variables 

```{r}

fviz_pca_biplot(res.pca, repel = TRUE,
                col.var = "#2E9FDF", # Variables color
                col.ind = "#696969"  # Individuals color
                )
```

Access to PCA results 

```{r}
library(factoextra)
# Eigenvalues
eig.val <- get_eigenvalue(res.pca)
eig.val
  
# Results for Variables
res.var <- get_pca_var(res.pca)
res.var$coord          # Coordinates
res.var$contrib        # Contributions to the PCs
res.var$cos2           # Quality of representation 
# Results for individuals
res.ind <- get_pca_ind(res.pca)
res.ind$coord          # Coordinates
res.ind$contrib        # Contributions to the PCs
res.ind$cos2           # Quality of representation 
   
  
```

################ Least discriminant analysis attempt ###########



```{r}


    LDA<-LDA <- merge( Selected, df_G , by="Wavenumber")%>%
    dplyr::select(-WaveLength, -PC_Value,-PC)

LDASpread<-LDA%>%
  group_by(Cultivar, Wavenumber,Block)%>%
  dplyr::select(AbsorbanceNorm)%>%
  summarise_all(funs(mean))%>%
tidyr::spread(Wavenumber, AbsorbanceNorm)%>%
  ungroup()%>%
  dplyr::select(-Block)

head(LDASpread)



```
Least Discriminatn analysis

source : https://rstudio-pubs-static.s3.amazonaws.com/35817_2552e05f1d4e4db8ba87b334101a43da.html

```{r}

library(MASS)
Cultivar.lda <- lda(Cultivar ~ ., data=LDASpread )

Cultivar.lda

str(Cultivar.lda)

```

Proportion of trace is the is the percentage separation achieved by each discriminant function. For example, for the cultivR data we get the same values as just calculated (53% and 31.%).


```{r, fig.height=6; fig.width=12}


Cultivar.lda.values <- predict(Cultivar.lda)
str(Cultivar.lda.values)

v<-as.vector(Cultivar.lda.values$class)

plot(Cultivar.lda.values$x[,1],Cultivar.lda.values$x[,2]) # make a scatterplot
text(Cultivar.lda.values$x[,1],Cultivar.lda.values$x[,2],v,cex=0.7,pos=4,col="red") # add labels


```

```{r, fig.width=15}

v <-as.vector(Cultivar.lda.values$class) # get labels
df <-as.data.frame(Cultivar.lda.values$x) # get data

# graph labels + data
df %>%
  mutate(Cultivars=v) %>%
  ggplot(aes(x=LD1,y=LD2)) +
  geom_point(aes(colour=Cultivars, shape=Cultivars), size=5) +
  geom_text(aes(label=Cultivars, colour=Cultivars),hjust=0, vjust=-2, size=8) +
  theme_bw()+
  #xlim(-10,10) +
  ylim(-8,8) +
  theme(text = element_text(size=20)) +
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  geom_abline(slope = 0)
  
  
```



################################################not using 
