---
title: "Framework for PCA analysis "
author: "CT"
date: "05.08.2017
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
- This script is the PCA analysis of the spectra of the S2 six cultivars from S2. 

-Used guidelines from : http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/118-principal-component-analysis-in-r-prcomp-vs-princomp/


```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)
library(calibrate)
library(factoextra)
library(FactoMineR)
```

# Get the segmented spectra  and continue here 
```{r}


setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Spectra_S2_Anovas")
getwd()

#create file using the data from: "s2_Segmented_BaselinedMaxNorm1And2.txt"

#this is the whole spectra :

#df_G <- read.table("S2All.txt",header=TRUE)
#this is the sniped  spectra :

df_G <- read.table("S2_BaselinedMaxNormBlock1And2.txt",header=TRUE)

str(df_G)
```

Here take the mean of each replicate !!Analyse at the replicate level!  To get the following treatment combinations : 
A01
A02
A03
M01
M02
M03
A841
A842
A843
M841
M842
M843


select columns of interest and Adjust formats 
```{r}

#change formats
df_G$Cultivar <- as.integer(df_G$Cultivar)
df_G$Block <- as.integer(df_G$Block)
#df_G$Wavenumber   <- as.factor(df_G$Wavenumber)
df_G$Wavenumber  <- as.numeric(df_G$Wavenumber)

#select columns and change name wavelenght for wavenumber (easy)
# df_G <-df_G %>%
#   mutate(Wavenumber = as.numeric(wavelength))%>%
#   dplyr:: select (-wavelength)

  #mutate_(Wavenumber=wavelength) 

#dplyr:: select(Plot,Block,Cultivar)


str(df_G)

# this is to "clean previous dfs : df_emerg4 <- NULL








```


##Now you have the dataframe organized vertically: spread the wavenumber horizontally 



```{r}

#-------------here is just to produce a matrix to export to Unscrambleror PCA 

#duplicated(df_G) 


 df_U <- df_G %>%
 mutate(Wavenumber=factor(Wavenumber)) %>%
 group_by(Cultivar,Block, Wavenumber) %>%
  summarise_all(funs(mean))  %>%
   dplyr::select(Cultivar,Block, Wavenumber,AbsorbanceNorm) %>%
   tidyr::spread(Wavenumber, AbsorbanceNorm)

```



## -------------here PCa starts

##Prepare dataframe

```{r}
df_spRep <- df_U%>%

#filter(Cultivar =="A")%>%
#filter(IncubationDays!="0")%>%
group_by(Cultivar,Block) %>%
summarise_all(funs(mean))%>%
dplyr::select(-Block)
  


```
Now you have the dataframe with the mean spectra values at replicate level! Then do the selection of columns of interest ...before re labelling of row names 

```{r}

df_spU <- df_spRep
#filter(Cultivar =="A")%>%
#filter(IncubationDays!="0")%>%
#dplyr::select( -Plot, -Seed)

#here define the wavenumbers ;set active row numbers and column of variables
#df_sp.activeU <- df_spU[,1:25, 2:1738 ]

#df_sp.activeU <- df_spU[,1:25, 2:908 ]
#str(df_sp.activeU[, 1:6])

df_sp.activeU <- df_spU[1:18, 1:907 ]
#str(df_sp.activeU[, 1:6])




head(df_sp.activeU[, 1:18])


```

##Re label row names per replicate (or Block is the same)  

```{r}

##attribute new labels 
# row.names (df_sp.activeU) <-c("A0_1","A84_2","M0_1","M84_2")
# # 
# head (df_sp.activeU)

#Re label row names per cultivar and block (replicate )
row.names (df_sp.activeU) <-c("A_1","A_2","A_3",
"D_1","D_2","D_3",
"L_1","L_2","L_3",
 "M_1","M_2","M_3",
 "N_1","N_2","N_3",
 "W_1","W_2","W_3")

#row.names (df_sp.activeU) <-c("A","D","L","M","N","W")




# 
 head (df_sp.activeU)

#df_sp.activeU$row.name<-as.numeric(df_sp.activeU$row.name)

```



```{r readData}


#Need to convert the cultivar names to numbers as numeric



#compute PCA
#res.pca <- prcomp (df_sp.active[,apply(df_sp.active, 2, var, na.rm=TRUE) != 0])

res.pca <- prcomp(df_sp.activeU ,scale = TRUE)


str(res.pca)

```


```{r}
summary(res.pca$rotation)

```


```{r}
str(res.pca)

```


## Visualize eigenvalues (scree plot). Show the percentage of variances explained by each principal component. 

```{r, fig.height=5, fig.width=10}

 

fviz_eig(res.pca)

#str(fviz_eig(res.pca))

```




##Graph of individuals. Individuals with a similar profile are grouped together. 

## Add PC1 = 57% and PC2= 28% in axis titles 


```{r, fig.height=5, fig.width=10}

# fviz_pca_ind(res.pca,
#              col.ind = "cos2", # Color by the quality of representation
#              #col.ind = "Cultivar", 
#              gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
#              #gradient.cols = c("#00AFBB", "#E7B800"),
#              geom="point",
#              
#              repel = TRUE     # Avoid text overlapping
#              )


fviz_pca_ind(res.pca,
            # col.ind = "cos2", # Color by the quality of representation
             #gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             geom = c("point", "text"),
             label = "all", invisible = "none", labelsize = 8,pointsize = 5,
             repel = TRUE     # Avoid text overlapping
             )+
             scale_color_gradient2(low="light green", mid="green",
      high="black", midpoint=0.6)+
   theme_bw()+
  # theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 20))+
  # theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 20))+
  theme(axis.text.y = element_text( size = 26))+
theme(axis.title.y = element_text(face="bold", size=26))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 26,face="bold"))+
theme(axis.title.x = element_text( face="bold", size=26))+
  
  
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
#if need the axes labels 
  xlab(expression(PC1~"(59%)"))+ 
  ylab(expression(PC2~"(21%)")) +
  xlim(-50, 50)+
  ylim(-50, 50)

   
 
```


##SAve the plot graph 

```{r}

#ggsave("S2_plot_PC1andPC2.png", width=14, height=7, dpi=500)

```


```{r}

#res.pca <- prcomp(df_sp.activeU ,scale = TRUE)

res.pca2 <-PCA(df_sp.activeU, ncp = 2, graph = FALSE)

res.hcpc <- HCPC(res.pca2, graph = FALSE)


fviz_cluster(res.hcpc,
             repel = TRUE,            # Avoid label overlapping
             show.clust.cent = TRUE, # Show cluster centers
             palette = "jco",         # Color palette see ?ggpubr::ggpar
             ggtheme = theme_minimal(),
             main = "Factor map"
             )




```



```{r}


# Principal components + tree
plot(res.hcpc, choice = "3D.map")+
  




```


```{r}


# Dendrogram
fviz_dend(res.hcpc, show_labels = FALSE)

# Individuals facor map
fviz_cluster(res.hcpc, geom = "point", main = "Factor map")

```




Graph the loading of PC1 and PC2 

```{r, warning=FALSE}

LabelColumn<-row.names(res.pca$rotation)

load.graph <- res.pca$rotation %>%
  as.data.frame() %>%
  dplyr::select(PC1,PC2) %>%
  mutate(WaveLength=as.numeric(LabelColumn)) %>%
  na.omit() %>% 
  gather("PC","PC_Value",PC1:PC2) %>%
  mutate(PC=factor(PC))

summary(load.graph)
  
```




```{r, fig.width=10}
load.graph %>%
  mutate(Show_WL = ifelse(WaveLength %in% c(1799:2802), "NotShow","Show")) %>%
   mutate(Show_WL = ifelse(WaveLength <1799,"Show1",
                          ifelse(WaveLength %in% c(1799:2802), "NotShow","Show2"))) %>%
     
  
  filter(Show_WL != "NotShow") %>%
  ggplot(aes(x=WaveLength,y=PC_Value, colour=PC)) +
  geom_line() +
  geom_abline(slope=0,intercept=0, linetupe=2, colout="darkgreey")+
  labs(x= "X variables ([PC1_59%] _ [PC2_21%])")+
   scale_x_reverse()+
  theme_bw() +
  facet_grid(PC~Show_WL, scale="free")+
  #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))
  

  
```




Separate by groups for Antas 

```{r, fig.height=6, fig.width=12}
fviz_pca_ind(res.pca, label="none", habillage=df_sp.activeU$Cultivar)
df_sp.activeU

# Add ellipses
p <- fviz_pca_ind(res.pca, label="none", habillage=df_sp.activeU$Cultivar,
             addEllipses=TRUE, ellipse.level=0.2, alpha=0.25)+
  #scale_color_brewer(palette="Set1") +
     theme_minimal()
print(p)
```


PC contributions 

```{r, fig.height=5 , fig.width=30}

# Contributions of variables to PC1
fviz_contrib(res.pca, choice = "var", axes = 1, top = 20)
# Contributions of variables to PC2
fviz_contrib(res.pca, choice = "var", axes = 2, top = 20)

```




## Graph of variables. Positive correlated variables point to the same side of the plot. Negative correlated variables point to opposite sides of the graph.

```{r, fig.height=5, fig.width=10}

fviz_pca_var(res.pca,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
             )



```

Biplot of individuals and variables 

```{r}

fviz_pca_biplot(res.pca, repel = TRUE,
                col.var = "#2E9FDF", # Variables color
                col.ind = "#696969"  # Individuals color
                )
```

Access to PCA results 

```{r}
library(factoextra)
# Eigenvalues
eig.val <- get_eigenvalue(res.pca)
eig.val
  
# Results for Variables
res.var <- get_pca_var(res.pca)
res.var$coord          # Coordinates
res.var$contrib        # Contributions to the PCs
res.var$cos2           # Quality of representation 
# Results for individuals
res.ind <- get_pca_ind(res.pca)
res.ind$coord          # Coordinates
res.ind$contrib        # Contributions to the PCs
res.ind$cos2           # Quality of representation 
   
  
```



############################################# ended here ###################################

Theory behind PCA results
PCA results for variables
Here we'll show how to calculate the PCA results for variables: coordinates, cos2 and contributions:

var.coord = loadings * the component standard deviations
var.cos2 = var.coord^2
var.contrib. The contribution of a variable to a given principal component is (in percentage) : (var.cos2 * 100) / (total cos2 of the component)


```{r}
# Helper function 
#::::::::::::::::::::::::::::::::::::::::
var_coord_func <- function(loadings, comp.sdev){
  loadings*comp.sdev
}
# Compute Coordinates
#::::::::::::::::::::::::::::::::::::::::
loadings <- res.pca$rotation
sdev <- res.pca$sdev
var.coord <- t(apply(loadings, 1, var_coord_func, sdev)) 
head(var.coord[, 1:4])
```


```{r}
# Compute Cos2
#::::::::::::::::::::::::::::::::::::::::
var.cos2 <- var.coord^2
head(var.cos2[, 1:4])
```


```{r}
# Compute contributions
#::::::::::::::::::::::::::::::::::::::::
comp.cos2 <- apply(var.cos2, 2, sum)
contrib <- function(var.cos2, comp.cos2){var.cos2*100/comp.cos2}
var.contrib <- t(apply(var.cos2,1, contrib, comp.cos2))
head(var.contrib[, 1:4])
```


PCA results for individuals
ind.coord = res.pca$x
Cos2 of individuals. Two steps:
Calculate the square distance between each individual and the PCA center of gravity: d2 = [(var1_ind_i - mean_var1)/sd_var1]^2 + .+ [(var10_ind_i - mean_var10)/sd_var10]^2 + .+..
Calculate the cos2 as ind.coord^2/d2
Contributions of individuals to the principal components: 100 * (1 / number_of_individuals)*(ind.coord^2 / comp_sdev^2). Note that the sum of all the contributions per column is 100


```{r}
# Coordinates of individuals
#::::::::::::::::::::::::::::::::::
ind.coord <- res.pca$x
head(ind.coord[, 1:4])
```


```{r}
# Cos2 of individuals
#:::::::::::::::::::::::::::::::::
# 1. square of the distance between an individual and the
# PCA center of gravity
center <- res.pca$center
scale<- res.pca$scale
getdistance <- function(ind_row, center, scale){
  return(sum(((ind_row-center)/scale)^2))
  }
d2 <- apply(decathlon2.active,1,getdistance, center, scale)
# 2. Compute the cos2. The sum of each row is 1
cos2 <- function(ind.coord, d2){return(ind.coord^2/d2)}
ind.cos2 <- apply(ind.coord, 2, cos2, d2)
head(ind.cos2[, 1:4])
```


```{r}
# Contributions of individuals
#:::::::::::::::::::::::::::::::
contrib <- function(ind.coord, comp.sdev, n.ind){
  100*(1/n.ind)*ind.coord^2/comp.sdev^2
}
ind.contrib <- t(apply(ind.coord, 1, contrib, 
                       res.pca$sdev, nrow(ind.coord)))
head(ind.contrib[, 1:4])
```


