---
title: "Explore segments of the Normalised spectra "
author: "CT"
date: "19.09.2017"
output: html_document
---
#This script explores the wavenumbers which had Pvalue < 0.05 and 0.01 from:  (fromfile:///C:/GitHubRepos/SubCloverPhD/SubClover/Spectra_S2_Anovas/Spectra_S2_LinearEq3.Rmd )




```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic) 
library(lattice)
library (gridExtra)
```

get file 

```{r loadFile}
# Get dataframe from previous script (written table )
#setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\Spectra_S2_Anovas")
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Spectra_S2_Anovas")
getwd()


#create file
#df_G <- read.table("S2All.txt",header=TRUE)

df_spSegment <- read.table("S2_Segmented_BaselinedMaxNorm1And2.txt",header=TRUE)

str(df_spSegment)

```

select columns of interest and Adjust formats 
```{r}

# #change formats
# df_G$Cultivar <- as.factor(df_G$Cultivar)
# df_G$Block <- as.factor(df_G$Block)
# df_G$Plot <- as.factor(df_G$Plot)
# df_G$wavelength <- as.numeric(df_G$wavelength)
# 
# #select columns and change name wavelenght for wavenumber (easy)
# df_G <-df_G %>%
#   mutate(Wavenumber = as.numeric(wavelength))%>%
#   dplyr:: select (-wavelength)
# 
#   #mutate_(Wavenumber=wavelength) 
# 
# 
# #dplyr:: select(Plot,Block,Cultivar)
# 
# 
# str(df_G)

# this is to "clean previous dfs : df_emerg4 <- NULL
```


format 


```{r, fig.height=5, fig.width=20}


#adjust format and follow the same original script 
df_spSegment2<-df_spSegment  %>%
 # mutate(Days= as.factor(IncubationDays))%>%
  mutate (SpectraPart= factor(SpectraPart, levels=c("3600-2800", "1800-850")))%>%
  mutate (Cultivar_f= factor(Cultivar, levels=c("Antas","Denmark", "Leura", "Monti", 'Narrikup', "Woogenellup"),labels=c("Antas","Denmark", "Leura", "Monti", 'Narrikup', "Woogenellup")))%>%
  mutate (SpectraPart_f = factor(SpectraPart, levels=c('3600-2800','1800-850')))
 
 str(df_spSegment2)
                       
  
```
##Now refine regions of the spectra (zoom wavenumber regions)


```{r, fig.height=10, fig.width=20}

df_spSegment2  %>%   
  subset(Wavenumber <3000 & Wavenumber >2800)%>%
    #force spectra order here                              
     # df_spSegment$SpectraPart_f = factor(df_spSegment$SpectraPart, levels=c('3700-2700','1800-850'))%>% 
  ggplot(aes(x=Wavenumber,y=AbsorbanceNorm))+
    #geom_line(aes(), colour=IncubationDays))+
  geom_line(aes(colour=Cultivar),size=2)+
    #scale_color_manual(values=c("blue", "darkred"))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
    #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  #facet_grid(Cultivar_f ~SpectraPart_f,scales="free") +
  facet_grid(.~SpectraPart_f,scales="free") +
  #facet_grid(Cultivar ~.) +
  scale_x_reverse()+
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  
  theme_bw(base_size=30)+
  theme(strip.text.x =  element_blank())+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.25)) +
    labs(y= " Absorbance ")+
    xlab(expression(Wavenumber~"(cm"^"-1"*")"))+
#theme(axis.text.y = element_text( size = 24))+
  #theme(axis.title.y = element_text(face="bold", size=14))+
#theme(axis.text.x=element_text(angle = 0, hjust=0.95,vjust=0.2,size = 28)) +
    
    #remove grid lines 
    
    #remove grid lines 
   theme(
     panel.border = element_rect(colour = "white", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),

axis.line = element_line(colour = "black"))+
     #make cultivars white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
    #increase font size panels
    #theme(strip.text.x = element_text(size = 30, colour = "orange", angle = 90))+
    
theme(text = element_text(size = 32))+
theme(axis.text.y = element_text( size = 32))+
    theme(axis.title.y = element_text(face="bold", size=32))+
     scale_y_continuous(breaks = c(seq(from = 0, to = 1.25, by = 0.1)))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 28))+
theme(axis.title.x = element_text( size=32,face="bold"))+
  theme(axis.line.x = element_line(colour = 'black', size = 3))+
  theme(axis.line.y = element_line(colour = 'black', size = 3))
  #axis line 
  #y.line = element_line(colour = 'black', size = 4)



   #Save graph 
 
 #ggsave("plot_spectraMaxNorm_S2_6Cv.png", width=20, height=10, dpi=400)






```

##---------------------------------

##Create a spectra per Block to run the PCA per block!!! Need to keep the block info and save to use in PCA script 


```{r}


##use this filter if need to select cultivars and calculate the means here to graph
df_sp4B <-df_sp3%>%
  group_by(Cultivar,Block, Wavenumber)%>%
  dplyr::select(AbsorbanceNorm)%>%
  summarise_all(funs(mean))


```



```{r}

##select only wavenumbers between 3700-2700, then 
df_spzoom1B <-df_sp4B %>%
    #filter(Cultivar!="N")%>%
  #test here subset(Wavenumber <1700 & Wavenumber >1600) 
   subset(Wavenumber <3600 & Wavenumber >2800)
  

df_spzoom1B %>%
   ggplot(aes(x=Wavenumber,y=AbsorbanceNorm))+
  geom_line(aes(colour=factor(Block)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) 
  #geom_abline(intercept = 0.1, slope = 0)
  
#write.table(df_sp33, "BaselinedMaxNorm1.txt") #this will be used to buil the graph (portion 1 of spectra)
write.table(df_spzoom1B, "S 2_BaselinedMaxNormBlock1.txt") #this will be used to buil the graph (portion 1 of spectra)

```


#then create the second segment :subset(Wavenumber <1800 & Wavenumber >850)


```{r}

##select only wavenumbers between 3700-2700, then 
df_spzoom2B <-df_sp4B %>%
    #filter(Cultivar!="N")%>%
  #test here subset(Wavenumber <1700 & Wavenumber >1600) 
   subset(Wavenumber <1800 & Wavenumber >850)
  
##graph if needed 
# df_spzoom2B %>%
#    ggplot(aes(x=Wavenumber,y=AbsorbanceNorm))+
#   geom_line(aes(colour=factor(Block)))+
#   theme_bw()+
#   #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
#   
#   #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
#   facet_grid(Cultivar ~.) +
#   #facet_grid(IncubationDays ~.) +
#   scale_x_reverse()+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#   expand_limits(y=c(0,0.2)) 
#   #geom_abline(intercept = 0.1, slope = 0)
  
#write.table(df_sp33, "BaselinedMaxNorm1.txt") #this will be used to buil the graph (portion 1 of spectra)
write.table(df_spzoom2B, "S 2_BaselinedMaxNormBlock2.txt") #this will be used to buil the graph (portion 1 of spectra)

```

Bind the two dataframes for analysis and bring the complete dataset 


```{r}


#total <- rbind(data frameA, data frameB)

df_spzoom_1And2 <-rbind (df_spzoom1B,df_spzoom2B)


#write.table(df_sp33, "BaselinedMaxNorm1.txt") #this will be used to buil the graph (portion 1 of spectra)
write.table(df_spzoom_1And2, "S2_BaselinedMaxNormBlock1And2.txt") #this will be used to run the PCA



```




now move o next script to run p values for each wavenumber 



End of this script
