---
title: "Linear Equations "
author: "CT"
date: "19.09.2017"
output: html_document
---


```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic) 
library(lattice)
library (gridExtra)
```

get file 

```{r loadFile}
# Get dataframe from previous script (written table )
#setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\Spectra_S2_Anovas")
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Spectra_S2_Anovas")
getwd()

#create file
df_G <- read.table("S2All.txt",header=TRUE)


str(df_G)

```

select columns of interest and Adjust formats 
```{r}

#change formats
df_G$Cultivar <- as.factor(df_G$Cultivar)
df_G$Block <- as.factor(df_G$Block)
df_G$Plot <- as.factor(df_G$Plot)
df_G$wavelength <- as.numeric(df_G$wavelength)

#select columns and change name wavelenght for wavenumber (easy)
df_G <-df_G %>%
  mutate(Wavenumber = as.numeric(wavelength))%>%
  dplyr:: select (-wavelength)

  #mutate_(Wavenumber=wavelength) 


#dplyr:: select(Plot,Block,Cultivar)


str(df_G)

# this is to "clean previous dfs : df_emerg4 <- NULL
```
Then spread to make the matrix for Unscrambler - Wavenumber as column; do with average per replicate first 

```{r}

#duplicated(df_G) 


df_U <- df_G %>%
  mutate(Wavenumber=factor(Wavenumber)) %>%
 group_by(Cultivar,Block, Plot,Wavenumber) %>%
  summarise_all(funs(mean))  %>%
  dplyr::select(Cultivar,Block, Plot, Wavenumber,Absorbance) %>%
  tidyr::spread(Wavenumber, Absorbance)



```

Here make it with values per seed (as Burgi suggested) 

```{r}
df_Us <- df_G %>%
  mutate(Wavenumber=factor(Wavenumber)) %>%
 group_by(Cultivar,Block,Plot,Wavenumber,Seed) %>%
  summarise_all(funs(mean))  %>%
  dplyr::select(Cultivar,Block, Plot, Wavenumber,Absorbance,Seed) %>%
  tidyr::spread(Wavenumber, Absorbance)



```

got the means here ... and graph it

```{r, fig.height=5, fig.width=10, echo = FALSE}



# 

```



here get the equations for the Antas subset (min to optimum)  

```{r, fig.height=5,fig.width=10}
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}

#use all datapoints 
df <- df_A2 %>%
  dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E, Location) %>%
  group_by(SowTreat,Cultivar, Location) %>%
  summarise_each(funs(mean)) %>%
  mutate(y=InvDAS50E,x=meanTemp_Em) %>%
  dplyr::select(-meanTemp_Em, -InvDAS50E)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_point(aes(colour = factor(Location)), size=5) + scale_shape(solid = FALSE)+ 
  
  theme_bw()+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.25))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE) + 
  facet_grid(Cultivar~.,scales="free")
  
p1
```


```{r}
#get statistical summary here 
summary(lm(y ~ x, df))
```



End of this script
next script generate equations for each cultivar separately from 5 to 15.4-5 degrees. 