---
title: "analysis of the Different cultivar spectra of S2  "
author: "CT"
date: "19.09.2017_ last reivew in 11.09.2018"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---


```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic) 
library(lattice)
library (gridExtra)
```

get file 

```{r loadFile}
# Get dataframe from previous script (written table )
#setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\Spectra_S2_Anovas")
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Spectra_S2_Anovas")
getwd()

#create file
df_G <- read.table("S2All.txt",header=TRUE)


str(df_G)

```

select columns of interest and Adjust formats 
```{r}

#change formats
df_G$Cultivar <- as.factor(df_G$Cultivar)
df_G$Block <- as.factor(df_G$Block)
df_G$Plot <- as.factor(df_G$Plot)
df_G$wavelength <- as.numeric(df_G$wavelength)

#select columns and change name wavelenght for wavenumber (easy)
df_G <-df_G %>%
  mutate(Wavenumber = as.numeric(wavelength))%>%
  dplyr:: select (-wavelength)

  #mutate_(Wavenumber=wavelength) 


#dplyr:: select(Plot,Block,Cultivar)


str(df_G)

# this is to "clean previous dfs : df_emerg4 <- NULL
```

#This chunk was included just to load Unscrambler eralier (keep it here but leave as commented out)
##Then spread to make the matrix for Unscrambler - Wavenumber as column; do with average per replicate first 
## This data is then used for the PCA analysis. 


```{r}

#-------------here is just to produce a matrix to export to Unscrambler or PCA analysis 

#duplicated(df_G) 


# df_U <- df_G %>%
#   mutate(Wavenumber=factor(Wavenumber)) %>%
#  group_by(Cultivar,Block, Plot,Wavenumber) %>%
#   summarise_all(funs(mean))  %>%
#   dplyr::select(Cultivar,Block, Plot, Wavenumber,Absorbance) %>%
#   tidyr::spread(Wavenumber, Absorbance)

```

##Here make it with values per seed (as Burgi suggested) 

```{r}
# df_Us <- df_G %>%
#   mutate(Wavenumber=factor(Wavenumber)) %>%
#  group_by(Cultivar,Block,Plot,Wavenumber,Seed) %>%
#   summarise_all(funs(mean))  %>%
#   dplyr::select(Cultivar,Block, Plot, Wavenumber,Absorbance,Seed) %>%
#   tidyr::spread(Wavenumber, Absorbance)


##------------save as table matrix for PCA 
```




#select columns of interest Cultivar rep AbsValue Wavenumber

```{r}

str(df_G)

df_sp1<-df_G%>%
  dplyr::select(-Hardness)

str(df_sp1)

```

## Normalization with Max Peak method (Burgi feedback 18.06!!)

```{r}


df_sp2 <- df_sp1%>%
  
  group_by(Cultivar, Block)%>%
  
  mutate(AbsorbanceNorm=Absorbance/max(Absorbance))

str(df_sp2)

```

##Continue from here ##
##get the means here by cultivar , skip seed effect  ... and graph it check script ESA ...use average per Cultivar now

```{r}


df_sp3<-df_sp2%>%
  group_by(Cultivar,Block, Wavenumber)%>%
  dplyr::select(AbsorbanceNorm)%>%
  summarise_all(funs(mean))
  #mutate(Absorbance=AbsValue)%>%
  #dplyr::select(-AbsValue)
  
  str(df_sp3)

##df_sp3 will be used as dataframe for Stats (it contains the blocks)


```


## Graph it all , 

```{r, fig.height=5, fig.width=15}

##use this filter if need to select cultivars and calculate the means here to graph
df_sp4 <-df_sp3%>%
  group_by(Cultivar,Wavenumber)%>%
  dplyr::select(AbsorbanceNorm)%>%
  summarise_all(funs(mean))
  
    #filter(Cultivar!="N")
    

##write.table(df_sp3,"MaxNorm_SpectraESA2018.txt")
```


```{r, fig.height=5,fig.width=10}

df_sp4%>%
   ggplot(aes(x=Wavenumber,y=AbsorbanceNorm))+
  geom_line(aes(colour=factor(Cultivar)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  scale_x_continuous(breaks=round(seq(min(df_sp4$Wavenumber),max(df_sp4$Wavenumber),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  #expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)
  

##write.table(df_sp3,"MaxNorm_SpectraESA2018.txt")



```

## Now need to snip the spectra (remove wavenumber interval 2800-1800)




```{r}

##select only wavenumbers between 3700-2700, then 
df_spzoom1 <-df_sp4 %>%
    #filter(Cultivar!="N")%>%
  #test here subset(Wavenumber <1700 & Wavenumber >1600) 
   subset(Wavenumber <3600 & Wavenumber >2800)
  

  

df_spzoom1 %>%
   ggplot(aes(x=Wavenumber,y=AbsorbanceNorm))+
  geom_line(aes(colour=factor(Cultivar)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) 
  #geom_abline(intercept = 0.1, slope = 0)
  
#write.table(df_sp33, "BaselinedMaxNorm1.txt") #this will be used to buil the graph (portion 1 of spectra)
write.table(df_spzoom1, "S 2_BaselinedMaxNorm1.txt") #this will be used to buil the graph (portion 1 of spectra)

```

## snip spectra again section 2 

```{r}

## ##select only wavenumbers below 1900  then 
df_spzoom2 <-df_sp4 %>%
    #filter(Cultivar!="N")%>%
 
   ##subset(Wavenumber <3600 & Wavenumber >2800)
  
  subset(Wavenumber <1800 & Wavenumber >850)

  

df_spzoom2 %>%
   ggplot(aes(x=Wavenumber,y=AbsorbanceNorm))+
  geom_line(aes(colour=factor(Cultivar)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) 
  #geom_abline(intercept = 0.1, slope = 0)
  
#write.table(df_sp33, "BaselinedMaxNorm1.txt") #this will be used to buil the graph (portion 1 of spectra)


write.table(df_spzoom2, "S2_BaselinedMaxNorm2.txt") #this will be used to buil the graph (portion 1 ofspectra)



```


##combine the two sections to create a interval graph 



Now combine the two dataframes (df_spzoom1 and df_spzoom2)and bring the file to build the graph (see Excel file SpectraMaxNormalisedChopped; 
C:\Users\teixe\Documents\CarmenDocumentsPhD\A_Carmenfiles02.08.2018\PhD project\Iversen2_6CV\ANALYSYS\FTIR_S2
file is : Spectra_S2_BaseMaxNormSegmented


```{r}

getwd()

#create file
df_spSegment <- read.table("S2_Segmented_BaselinedMaxNorm1And2.txt",header=TRUE)


```


## check data  



```{r}

str(df_spSegment)

```

format 


```{r, fig.height=5, fig.width=20}


#adjust format and follow the same original script 
df_spSegment2<-df_spSegment  %>%
 # mutate(Days= as.factor(IncubationDays))%>%
  mutate (SpectraPart= factor(SpectraPart, levels=c("3600-2800", "1800-850")))%>%
  mutate (Cultivar_f= factor(Cultivar, levels=c("Antas","Denmark", "Leura", "Monti", 'Narrikup', "Woogenellup"),labels=c("Antas","Denmark", "Leura", "Monti", 'Narrikup', "Woogenellup")))%>%
  mutate (SpectraPart_f = factor(SpectraPart, levels=c('3600-2800','1800-850')))
 
 str(df_spSegment2)
                       
  
```




```{r, fig.height=10, fig.width=20}

df_spSegment2  %>%   
    #force spectra order here                              
     # df_spSegment$SpectraPart_f = factor(df_spSegment$SpectraPart, levels=c('3700-2700','1800-850'))%>% 
  ggplot(aes(x=Wavenumber,y=AbsorbanceNorm))+
    #geom_line(aes(), colour=IncubationDays))+
  geom_line(aes(colour=Cultivar),size=2)+
    #scale_color_manual(values=c("blue", "darkred"))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
    #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  #facet_grid(Cultivar_f ~SpectraPart_f,scales="free") +
  facet_grid(.~SpectraPart_f,scales="free") +
  #facet_grid(Cultivar ~.) +
  scale_x_reverse()+
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  
  theme_bw(base_size=30)+
  theme(strip.text.x =  element_blank())+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,1.2)) +
    labs(y= " Absorbance (au) ")+
    xlab(expression(Wavenumber~"(cm"^"-1"*")"))+
#theme(axis.text.y = element_text( size = 24))+
  #theme(axis.title.y = element_text(face="bold", size=14))+
#theme(axis.text.x=element_text(angle = 0, hjust=0.95,vjust=0.2,size = 28)) +
    
    #remove grid lines 
    
    #remove grid lines 
   theme(
     panel.border = element_rect(colour = "white", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),

axis.line = element_line(colour = "black"))+
     #make cultivars white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
    #increase font size panels
    #theme(strip.text.x = element_text(size = 30, colour = "orange", angle = 90))+
    
theme(text = element_text(size = 32))+
theme(axis.text.y = element_text( size = 32))+
    theme(axis.title.y = element_text(face="bold", size=32))+
     scale_y_continuous(breaks = c(seq(from = 0, to = 1.25, by = 0.5)))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 28))+
theme(axis.title.x = element_text( size=32,face="bold"))+
  theme(axis.line.x = element_line(colour = 'black', size = 3))+
  theme(axis.line.y = element_line(colour = 'black', size = 3))
  #axis line 
  #y.line = element_line(colour = 'black', size = 4)



   #Save graph 
 
 ggsave("plot_spectraMaxNorm_S2_6Cv.png", width=20, height=10, dpi=400)






```

##---------------------------------

##Create a spectra per Block to run the PCA per block!!! Need to keep the block info and save to use in PCA script 


```{r}


##use this filter if need to select cultivars and calculate the means here to graph
df_sp4B <-df_spSegment2%>%
  group_by(Wavenumber, SpectraPart_f)%>%
  dplyr::select(AbsorbanceNorm)%>%
  summarise_all(funs(mean))

write.table(df_sp4B, "meanspectraAllSubs.txt")
```



```{r}

##select only wavenumbers between 3700-2700, then 
df_spzoom1B <-df_sp4B %>%
    #filter(Cultivar!="N")%>%
  #test here subset(Wavenumber <1700 & Wavenumber >1600) 
   subset(Wavenumber <3600 & Wavenumber >2800)
  

df_spzoom1B %>%
   ggplot(aes(x=Wavenumber,y=AbsorbanceNorm))+
  geom_line(aes(colour=factor(Block)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) 
  #geom_abline(intercept = 0.1, slope = 0)
  
#write.table(df_sp33, "BaselinedMaxNorm1.txt") #this will be used to buil the graph (portion 1 of spectra)
write.table(df_spzoom1B, "S 2_BaselinedMaxNormBlock1.txt") #this will be used to buil the graph (portion 1 of spectra)

```


#then create the second segment :subset(Wavenumber <1800 & Wavenumber >850)


```{r}

##select only wavenumbers between 3700-2700, then 
df_spzoom2B <-df_sp4B %>%
    #filter(Cultivar!="N")%>%
  #test here subset(Wavenumber <1700 & Wavenumber >1600) 
   subset(Wavenumber <1800 & Wavenumber >850)
  
##graph if needed 
# df_spzoom2B %>%
#    ggplot(aes(x=Wavenumber,y=AbsorbanceNorm))+
#   geom_line(aes(colour=factor(Block)))+
#   theme_bw()+
#   #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
#   
#   #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
#   facet_grid(Cultivar ~.) +
#   #facet_grid(IncubationDays ~.) +
#   scale_x_reverse()+
#   theme_bw()+
#   theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#   expand_limits(y=c(0,0.2)) 
#   #geom_abline(intercept = 0.1, slope = 0)
  
#write.table(df_sp33, "BaselinedMaxNorm1.txt") #this will be used to buil the graph (portion 1 of spectra)
write.table(df_spzoom2B, "S 2_BaselinedMaxNormBlock2.txt") #this will be used to buil the graph (portion 1 of spectra)

```

Bind the two dataframes for analysis and bring the complete dataset 


```{r}


#total <- rbind(data frameA, data frameB)

df_spzoom_1And2 <-rbind (df_spzoom1B,df_spzoom2B)


#write.table(df_sp33, "BaselinedMaxNorm1.txt") #this will be used to buil the graph (portion 1 of spectra)
write.table(df_spzoom_1And2, "S2_BaselinedMaxNormBlock1And2.txt") #this will be used to run the PCA



```




now move o next script to run p values for each wavenumber 



End of this script
