---
title: 'Graph climate variables in growth chamber '
author: "CT"
date: "12.12.2017"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

This script calculates the Thermal time using four methods : 
1. hourly as average of the 18 seconds measurements 
2. per Tmax tmin applying the 3x8 formula 
3. simple method Tmean and  applying the segmented function 
4. super simple calculation Tb = 0 and no treshold 

```{r}
library(tidyr)
library (dplyr)
library (ggplot2)
library (lubridate)
library (scales)
library(gridExtra)
library(knitr)
```

Equation  to calculate the TT 



## Define Tt cardinal temperatures

Considered an overall average the following references:
Tb: 0.0
Top range:18-25
Tmax: 35
REFS: MonksEtAl2009	,LonatiEtAl2009	,MootEtal2003, SilsburyetAl1984. 
							
```{r}

tt_card <- data.frame(temp=c(0,15,22,35),TT=c(0,15,15,0))
tt_card %>%
  ggplot(aes(x=temp, y=TT))+
  labs(x="Temperature (degree Celsius)")+
  labs(y="Thermal Time (degree days)") +
  theme_bw()+
  geom_line()
  
```



```{r}

 

#Create and test interpolation function - Test if works 

temp_ref  <- 20 # x-axes reference
temp <- tt_card$temp # x-axes
TT <- tt_card$TT # y-axes


int_func <- function(temp,TT,temp_ref){

  # if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   out <- TT[length(TT)] 
   # FIXME: approx functions seems to do that - need param
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
   # else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  
int_func(temp,TT,temp_ref)


```




Note: this file produces the graphs for recorded variables in growht cabinet. measurements are done every 18 seconds. 

```{r, load file}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GCClimate")
getwd()
#read data , use row.names=NULL to delete Error message 

df_file <- read.table("AllData.txt",header =TRUE,row.names= NULL )

```

```{r}
summary(df_file)
```

##Method 1. TT calculate hourly from measurements every 18 seconds!!!  

```{r}

df_file_Hourly<- df_file %>%
  mutate(TimeStamp=dmy_hms(paste0(Date," ",Time))) %>%
  mutate(TimeStamp=ymd_hms(TimeStamp)) %>%
  mutate(Date=dmy(Date)) %>%
  dplyr::select(Date,TimeStamp,AI_TEMP,Hour)

summary(df_file_Hourly)
```
Average the Temp per Hour

```{r}

df_file_Hourly %>%
  group_by(Date, Hour)%>%
  dplyr::select(AI_TEMP )%>%
  summarise_all(funs(mean))

str(df_file_Hourly)


```

Connect function TT calculation 


```{r}


df_H <- df_file_Hourly %>%
  dplyr::select(Date:AI_TEMP) %>%
    rowwise() %>%
  mutate(TThour=int_func(temp,TT,AI_TEMP)) %>%
  group_by(Date) %>%
  dplyr::select(TThour)%>%
  summarise_all(funs(mean))%>%
  mutate(TTday=TThour) %>%
  mutate(SumTTday = cumsum(TTday))

summary(df_H)
str(df_H)
write.table(df_H, "SumTTHourGC.txt")

```






## Method 2 


							
```{r}

#Calculate the Tmax and Tmin f each date and link to the 3x8 formula 

df_file_TxTm<- df_file %>%
  mutate(TimeStamp=dmy_hms(paste0(Date," ",Time))) %>%
  mutate(TimeStamp=ymd_hms(TimeStamp)) %>%
  mutate(Date=dmy(Date)) %>%
  dplyr::select(Date,TimeStamp,AI_TEMP,Hour)

```

Calculate the maximum and minimum temp for each date 

```{r}
df_file_TxTm2 <-df_file_TxTm %>%
group_by(Date)%>%
summarise(Tmin=min(AI_TEMP),Tmax=max(AI_TEMP))
  

```

Apply the 3x 8 formula 


```{r}
#create REF Jones CA, Ritchie JT, Kiniry JR, Godwin DC (1986) Subroutine structure.In 'CERES-Maize: A simulation model of maize growth anddevelopment'. (Eds CA Jones, JR Kiniry) pp. 49-194. (Texas A&M University Press: Texas, USA

TTfunc <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
 } 
  
  TTav  <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2 + 0.0053 * n^3) * (Tmax-Tmin)) + Tmin # 8-h temperature
    #here already the segmented funciton is inserted
    
    TT_tn <- int_func(tt_card$temp, tt_card$T,tn) 
    
    TTsum <- TT_tn + TTsum
    
   # print(TT_tn)
    
    }
 
   TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc(10,24)



```

Link with the Tmax and Tmin table and calculate the Tmean of each date  


```{r}


df_TxTm3 <- df_file_TxTm2 
  

summary(df_TxTm3)
```



```{r}

df_TxTm4 <- df_TxTm3 %>%
  dplyr::select(Date,Tmin,Tmax) %>%
    rowwise() %>%
  mutate(TTDay=TTfunc(Tmin,Tmax)) %>%
  group_by(Date) %>%
  summarise(TTday=mean(TTDay)) %>%
  mutate(SumTTday2 = cumsum(TTday))

summary(df_TxTm4)
str(df_TxTm4)
#Compare with the summary calculated with the Hourly data 
```

## Method 3 simply Tmean - and apply to function 


```{r}

df_file_mean <-df_file_TxTm %>%
group_by(Date)%>%
summarise(Tmean=mean(AI_TEMP))%>%
  dplyr::select(Date,Tmean) %>%
    rowwise() %>%
  mutate(TTDay=int_func(temp,TT,Tmean))%>%
  group_by(Date) %>%
  summarise(TTDay=1*TTDay) %>%
  mutate(SumTTDay3 = cumsum(TTDay))



summary(df_file_mean)
str(df_file_mean)
```

## Method 4 simple TT (no function applied ) Tb = 0 only 

```{r}

df_Simple <-df_file_TxTm %>%
group_by(Date)%>%
summarise(Tmean=mean(AI_TEMP))%>%
  dplyr::select(Date,Tmean)%>%
  rowwise() %>%
  mutate(TTDay=Tmean-0)%>%
   group_by(Date) %>%
  summarise(TTDay=1*Tmean) %>%
  mutate(SumTTDay4 = cumsum(TTDay))


summary(df_Simple)
str(df_Simple)
```


##Now compare the methods 

```{r}

#merge the dataframes 

## df_H,df_TxTm4,df_file_mean,df_Simple, by = "Date"

total <- merge(df_H,df_TxTm4, by="Date")
total1 <- merge(df_file_mean,df_Simple, by="Date")

AllMethod <- merge(total,total1, by="Date")

str(AllMethod)
```


now graph the methods 

```{r fig.height=5, fig.width=15}

##Create days of Test 

stDate<-min(AllMethod$Date)

AllMethod %>%
  select(Date ,  SumTTday, SumTTday2, SumTTDay3,  SumTTDay4)%>%
  gather("VarName","Value",SumTTday:SumTTDay4)%>%
  ggplot(aes(x=Date-stDate,y=Value)) +
  geom_line(aes(colour=VarName)) +
 # ylim(0,mxT) +
  theme_bw()+
  ylab("SumTT (oCd)")+
  xlab("Days") 
  #facet_wrap(~VarName, scales='free')



```












