---
title: "Graph climate variables in growth chamber "
author: "CT"
date: "12.12.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---


```{r}
library(tidyr)
library (dplyr)
library (ggplot2)
library (lubridate)
library (scales)
library(gridExtra)
library(knitr)
```

Note: this file produces the graphs for recorded variables in growht cabinet. measurements are done every 18 seconds. 

```{r, load file}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GCClimate")
getwd()
#read data , use row.names=NULL to delete Error message 

df_file <- read.table("AllData.txt",header =TRUE,row.names= NULL )


str(df_file)



```


graph variables 


```{r}
df_gather<-df_file %>%
  #select(Date,Tx,Tm,MeanTt,Pp)%>%
gather(key= "Variable" , value = "Value", AI_TEMP,SP_TEMP,AI_HUM,AI_LIGHT)%>%
  mutate(Date=dmy(Date))


```

Graph all data (keep this chunck commented out it is too heavy to run )




```{r, fig.height=5; fig.widht=10}


# df_gather%>%
#    mutate (Variable= factor(Variable, levels=c("AI_HUM", "AI_LIGHT", "AI_TEMP", "SP_TEMP"),labels=c(" Humidity(%)", "Light(µ moles/m2/s)", "Actual Temperature (oC)", "Set Temperature (oC)")))%>%
#   ggplot(aes(x=Date, y= Value))  +
#   #geom_point(aes(colour=Variable, shape=Variable), alpha=0.8)+
#   #geom_point(colour= "darkblue", alpha=0.2) +
#   geom_line(aes(colour=Variable)) +
#   #stat_smooth(level = 0.9, size = 1, colour="white") + 
#   theme_bw() +
# facet_wrap(~Variable,ncol=2, scales = "free")+
#   xlab("Date") + 
#   #ylab(expression(Mean~soil~temperature~~"("^"o"*"C)"))+
#   theme(text = element_text(size=10))
  
                


  #ggsave("plot_ClimateGC.png", width=12, height=6, dpi=400)
```


calculate hours of light (and darkness)flux above 800; divide by o=constant 195000 to find values in hours! 


```{r,fig.height=5, fig.width=15}

#subset >800  because is the full light  
g1<- df_gather %>%
 filter(Variable== "AI_LIGHT")%>%
  subset(Value>800)

g2<-g1 %>% group_by(Date) %>%
  dplyr::select(Value)%>%
 summarise_(sum(Value/195000))
  
  

 str(g2) 

  #write.table(g2, "PpGC.txt")
 

```

then bring the Pp data and graph it 

 
 
```{r Soiltemp_mean}

df_Pp <- read.table("PpGC.txt",header =TRUE)


str(df_Pp)


df_Pp %>%

  ggplot(aes(x=as.Date(Date), y= sum.Value.195000.))  +
 #geom_point(aes(colour=Variable, shape=Variable), alpha=0.8)+
 geom_point(colour= "grey", alpha=0.2, size=3) +
 geom_line() +
#   #stat_smooth(level = 0.9, size = 1, colour="white") + 
 theme_bw() +
# facet_wrap(~Variable,ncol=2, scales = "free")+
 xlab("Month") +
ylab("Photoperiod (hours)")+

  scale_x_date(date_breaks = "1 month", 
                 date_labels = "%B")+

  theme(axis.text.y = element_text(size=16))+
  #theme(axis.title.x = element_title(size=12))+
  theme(axis.title.y = element_text(size=16))+
  theme(legend.text = element_text(size=14))+
  theme(axis.title.x = element_text(size=12))+
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=12))
                 



```

then graph Pp and the other variables 

```{r, fig.height=5, fig.width=8}

##make average per day
str(df_gather)

dfHourly <- df_file %>%
  group_by(Date,)%>% summarise_all(funs(mean))

 df_Air %>%
  mutate(Date = dmy(Date))%>% #(need to reformat date here)
  #filter(year %in% 2015:2017) %>%
  group_by(Date) %>%
  summarise_each(funs(mean))%>%
  ggplot(aes(x=Date, y= MeanTt))  +
  #geom_point(colour= "darkblue", alpha=0.2) +
  geom_line(colour= "blue")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab("Date") + 
  theme(text = element_text(size=10))+
  ylab(expression(Mean~air~temperature~~"("^"o"*"C)"))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B",
                 limits = as.Date(c('2015-06-01','2017-07-07')))




```


then create an object g2 for the grid 
```{r}
g2 <-df_Air %>%
  mutate(Date = dmy(Date))%>% #(need to reformat date here)
  #filter(year %in% 2015:2017) %>%
  group_by(Date) %>%
  summarise_each(funs(mean))%>%
  ggplot(aes(x=Date, y= MeanTt))  +
  #geom_point(colour= "darkblue", alpha=0.2) +
  geom_line(colour= "blue")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
 xlab("Date") + 
  ylab(expression(Mean~air~temperature~~"("^"o"*"C)"))+
  theme(text = element_text(size=10))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B",
                 limits = as.Date(c('2015-06-01','2017-07-07'))) 



```


Then create a grid with two graphs 

```{r}


grid.arrange(g2, g1)



```



then continue in next script AirSoilTempCorrelat....


