---
title: "Graph climate variables in growth chamber "
author: "CT"
date: "12.12.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

This script graphs the Temp and Pp during growth chamber experiment

```{r}
library(tidyr)
library (dplyr)
library (ggplot2)
library (lubridate)
library (scales)
library(gridExtra)
library(knitr)
```

Note: this file produces the graphs for recorded variables in growht cabinet. measurements are done every 18 seconds. 

```{r, load file}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GCClimate")
getwd()
#read data , use row.names=NULL to delete Error message 

df_file <- read.table("AllData.txt",header =TRUE,row.names= NULL )

```

```{r}
summary(df_file)
```





```{r}

df_file_work <- df_file %>%
  mutate(TimeStamp=dmy_hms(paste0(Date," ",Time))) %>%
  mutate(TimeStamp=ymd_hms(TimeStamp)) %>%
  mutate(Date=dmy(Date)) %>%
  dplyr::select(Date,TimeStamp,AI_TEMP,AI_LIGHT)

summary(df_file_work)
```


```{r}
str(df_file_work)
```

```{r, fig.height=5, fig.width=10}

stDate<-min(df_file_work$Date)
mxT<-max(df_file_work$AI_TEMP)
#stDate<-ymd("2016/1/1")

df_file_work %>%
  group_by(Date)  %>%
  summarise(Tn=min(AI_TEMP),Tm=mean(AI_TEMP),Tx=max(AI_TEMP),Pp=sum(AI_LIGHT>800)/187) %>%
  mutate(TTsum=cumsum(Tm)) %>%
  gather("VarName","Value",Tn:TTsum)%>%
    ggplot(aes(x=Date-stDate,y=Value)) +
  geom_line(aes(colour=VarName)) +
  #geom_smooth(aes(colour=VarName), alpha=0.03)+
 # ylim(0,mxT) +
  theme_bw()+
  ylab("Value")+
  xlab("Days of trial") +
  facet_wrap(~VarName, scales='free')


  #ggsave("plot_ClimateGC.png", width=12, height=6, dpi=400)

```


```{r, fig.height=5, fig.width=10}


stDate<-min(df_file_work$Date)
mxT<-max(df_file_work$AI_TEMP)
#stDate<-ymd("2016/1/1")

df_file_work %>%
  group_by(Date)  %>%
  summarise(Tn=min(AI_TEMP),Tm=mean(AI_TEMP),Tx=max(AI_TEMP),Pp=sum(AI_LIGHT>800)/187) %>%
  mutate(TTsum=cumsum(Tm)) %>%
  gather("VarName","Value",Tn:TTsum)%>%
  filter(VarName!="TTsum")%>%
  ggplot(aes(x=Date-stDate,y=Value)) +
  #geom_line(aes(colour=VarName)) +
  geom_smooth(aes(linetype=VarName),alpha=0.05, colour="grey")+
   geom_point(alpha=0.2)+
 # ylim(0,mxT) +
  theme_bw()+
  ylab("Value")+
  xlab("Days of trial") +
  facet_wrap(~VarName, scales='free')+
  ylim(0,25)
ggsave("plot_ClimateGC2.png", width=12, height=6, dpi=400)


```


##scripts below may not be needed now 


graph variables 


```{r}
# df_gather <- df_file %>%
# mutate(TimeStamp=dmy_hms(paste0(Date," ",Time))) %>%
# tidyr::gather(key= "Variable" , value = "Value", AI_TEMP,SP_TEMP,AI_HUM,AI_LIGHT)  %>%
#   mutate (Variable = factor(Variable, 
#                               levels=c("AI_HUM", "AI_LIGHT", "AI_TEMP", "SP_TEMP"),
#                               labels=c(" Humidity(%)", "Light(µ moles/m2/s)", "Actual Temperature (oC)", "Set Temperature (oC)"))) %>%
#   mutate(TimeStamp=ymd_hms(TimeStamp))
  

```



```{r}
# str(df_gather)
```


Graph all data (keep this chunck commented out it is too heavy to run )




```{r, fig.height=15; fig.widht=25}


# df_gather %>%
#    ggplot(aes(x=TimeStamp, y= Value))  +
#    #geom_point(aes(colour=Variable, shape=Variable), alpha=0.8)+
# #   #geom_point(colour= "darkblue", alpha=0.2) +
#    geom_line(aes(colour=Variable)) +
# #   #stat_smooth(level = 0.9, size = 1, colour="white") +
#    theme_bw() +
#    facet_wrap(~Variable,ncol=2, scales = "free")+
#    xlab("Date") +
#    #ylab(expression(Mean~soil~temperature~~"("^"o"*"C)"))+
#    theme(text = element_text(size=10))

                


  #ggsave("plot_ClimateGC.png", width=12, height=6, dpi=400)
```



```{r}

df_Day <- read.table("DailyTemp.txt",header =TRUE,row.names= NULL )

str(df_Day)

#adjust format 

df_file2 <-df_file %>%
  mutate(Date=as.Date(dmy(Date)))

str(df_file2)

df_Day2<-df_Day %>%
  mutate(Date=as.Date(dmy(Date)))

str(df_Day2)
```

merge by date 

```{r}

df_merged<-merge(df_file2, df_Day2, by="Date")

```


Now get values for temperatures set and recorded (select columns of interest)

```{r, fig.height=5, fig.width=10}

dfTemp <- df_merged %>%
  select (Date,Time,AI_TEMP,DayTemperature,NightTemperature)%>%
  tidyr::gather(key= "Variable" , value = "Value", AI_TEMP,DayTemperature,NightTemperature)  


dfTemp %>%
  mutate (Variable = factor(Variable, 
                              levels=c("AI_TEMP","DayTemperature","NightTemperature"),
                              labels=c(" Actual Temperature(oC)", " Day Temperature(oC)","Night Temperature (oC)" )))%>%
ggplot(aes(x=Date, y= Value))  +
geom_point(aes(colour=Variable, shape=Variable), alpha=0.8,size=3)+
  # geom_point(aes(colour= Variable, alpha=0.2)) +
   #geom_line(aes(colour=Variable)) + 
  scale_color_manual(values=c("grey", "black", "blue"))+ 
# #   #stat_smooth(level = 0.9, size = 1, colour="white") +
   theme_bw() +
#    facet_wrap(~Variable,ncol=2, scales = "free")+
  xlab("Month") +
  ylab(expression(Temperature~~"("^"o"*"C)"))+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 14))+
  theme(axis.text.y=element_text( size= 14))+
  theme(axis.title.y=element_text( size= 14))+
  ylim(0,25)




```



Now get values for Pp set and recorded (select columns of interest)

```{r}
#bring values of Photoperiod calculated in other script selecting > 800 flux 

df_Pp <- read.table("PpGC.txt",header =TRUE)


str(df_Pp)

#adjust formats
df_Pp2<-df_Pp %>%
 mutate(Date=as.Date(ymd(Date)))



str(df_Pp2)


```


```{r}

# then merge

df_mergePp<-merge(df_Pp2, df_Day2, by="Date")

#select rows of interest 
df_mergePp2 <- df_mergePp %>%
select(Date,PpHours, sum.Value.195000.)%>%
  mutate(A_Pp=sum.Value.195000.)%>%
  select(Date,PpHours,A_Pp)


```
gather and graph Pp

```{r, fig.height=5, fig.width=10}

df_mergePp3 <- df_mergePp2 %>%
  tidyr::gather(key= "Variable" , value = "Value", PpHours,A_Pp)  


df_mergePp3 %>%
  mutate (Variable = factor(Variable, 
                              levels=c("A_Pp", "PpHours"),
                              labels=c(" Actual Pp (hours)", " Set Pp (hours)")))%>%
ggplot(aes(x=Date, y= Value))  +
geom_point(aes(colour=Variable, shape=Variable), alpha=0.8, size=3)+
# #   #geom_point(colour= "darkblue", alpha=0.2) +
   #geom_line(aes(colour=Variable)) + 
  scale_color_manual(values=c("grey", "black"))+
# #   #stat_smooth(level = 0.9, size = 1, colour="white") +
   theme_bw() +
#    facet_wrap(~Variable,ncol=2, scales = "free")+
  xlab("Month") +
  ylab(expression(Daily~Photoperiod~"("*"hours"*")"))+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 14))+
  theme(axis.text.y=element_text( size= 14))+
  theme(axis.title.y=element_text( size= 14))+
  theme(axis.title.x=element_text( size= 14))+
  ylim(0,16)

```

Humidity 








