---
title: "Seed weightAnalysis"
author: "CT"
date: "Friday, March 18, 2016"
output: html_document
---
Purpose : 

Create a graph comparing the seed weight measured and published by Nichols

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
```

Read File 
Need to bring the whole seedweight file to have the SE !!!!Look at script Cvtrial_9

```{r, echo=FALSE}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
getwd()
file <- read.table("CVTrial2016_SeedWeightCompare.txt",header=TRUE)
head(file)
summary(file)
```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Treat=as.factor(Treat)
   
  )

str(file)
summary(file)

```



Graph the percentage of buried burrs 

```{r, fig.height= 5, fig.width=10 , warning=FALSE}

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

file %>%
  group_by(Cultivar, Treat) %>%
  summarise_each(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(PercentBurBurial_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=PercentBurBurial_mean-PercentBurBurial_sd/2, ymax=PercentBurBurial_mean+PercentBurBurial_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~Treat) +
    labs(y="% Buried burrs") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))


```

Here graph with the SE (SE = std/ sqrt n ; n=4)

```{r,fig.height= 5, fig.width=10 , warning=FALSE}

#calculate the SE in this case for 4 reps ! sqrt of 4 = 2 
df_burSE<-file %>%
  group_by(Cultivar, Treat) %>%
  summarise_each(funs(mean,sd)) %>%
  mutate(SE=PercentBurBurial_sd/2)
  
  
  df_burSE %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PercentBurBurial_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(PercentBurBurial_mean),fill=Cultivar))+
  geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=PercentBurBurial_mean-SE/2, ymax=PercentBurBurial_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~Treat) +
    labs(y="% Buried burrs") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))






```


select only the seven cultivars 

Here graph with the SE (SE = std/ sqrt n ; n=4)

```{r,fig.height= 5, fig.width=10 , warning=FALSE}

#calculate the SE in this case for 4 reps ! sqrt of 4 = 2 
df_burSE2<-file %>%
  filter(Treat=="Cut")%>%
  filter(Cultivar=="Antas"| 
         Cultivar=="Denmark"|
         Cultivar=="Coolamon"|
           Cultivar=="MountBarker"|
           Cultivar=="Narrikup"|
           Cultivar=="Rosabrook"|
           Cultivar=="Woogenellup")%>%

  group_by(Cultivar) %>%
  summarise_each(funs(mean,sd)) %>%
  mutate(SE=PercentBurBurial_sd/2)
  
  #graph it 
  df_burSE2 %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PercentBurBurial_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(PercentBurBurial_mean),fill=Cultivar))+
  geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=PercentBurBurial_mean-SE/2, ymax=PercentBurBurial_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    #facet_grid(.~Treat) +
    labs(y="% Buried burrs") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0.5,size = 12))


```


```{r}
#Statistical Analisis 
#Do ANOVA simple as per D. Saville : each sowing date separately.


 
#summary(file)

df_burANOVA <- file %>%    #use to filter%>%
  filter(Treat=="Cut")%>%
  filter(Cultivar=="Antas"| 
         Cultivar=="Denmark"|
         Cultivar=="Coolamon"|
           Cultivar=="MountBarker"|
           Cultivar=="Narrikup"|
           Cultivar=="Rosabrook"|
           Cultivar=="Woogenellup")


#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file %>%
 dplyr:: select(-PropBurrBurial)

head(file.subset)
summary(file.subset)
```









Here Analyse the percentage of buried burs overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PercentBurBurial ~ Cultivar*Treat + Block, data = file.subset)
my.anova <- aov(PercentBurBurial ~ Cultivar + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

Correlate with the burr burial ranks by Nichols 2013

```{r}


rankBur <- read.table("CVTrial2017_RankBurBurial.txt",header=TRUE)
```


merge dataframes of interest 

```{r}


# define merging by 
df_merge <- merge (  df_burSE2, rankBur, by.x="Cultivar")

df_merge <-df_merge %>%
  mutate (BurialRank=as.numeric(BurialRank))
```

Plot percent buried burrs against the ranks 

```{r, fig.height=5, fig.width=10}

df_merge %>%
   ggplot(aes(x=BurialRank, y=PercentBurBurial_mean)) + # do percentage here
   geom_point(aes(shape= Cultivar), size=5)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6))+
  geom_point()+
  geom_errorbar(aes(ymin=PercentBurBurial_mean-PercentBurBurial_sd/4,
                    ymax=PercentBurBurial_mean+PercentBurBurial_sd/4))+
    #labs(x="Hours",y="Cummulative Germination Percent(%)")+
  #facet_grid(.~Temp)
  #facet_wrap(.~Temp, ncol=6)

#facet_wrap(~Month_f,ncol=3, scales = "free")+
  theme_bw(base_size=16)+
  #scale_x_continuous(breaks = c(1,200,300))+
 #ylim(0, 2000)+
  xlim(0, 8)+
  theme(axis.text.x=element_text(angle = +0, hjust = 0.5, size= 12))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 12))+
  labs(y="Percentage of buried burrs (%) ",x="Burial Rank ")
 # geom_abline(intercept = 50, slope = 0)


ggsave("plot_BurrBurial.png", width=12, height=6, dpi=400)



```







Perform anova in cultivars 



```{r}


#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


do a cluster analysis

```{r}
df_work<-file %>% dplyr::select(Cultivar,PercentBurBurial) %>% group_by(Cultivar) %>%
  summarise_all(funs(mean,sd))

summary(df_work)


```
Cluster 

```{r}
clusNo <- 7 # selected from sensitivity cluster analysis below

myClus <- kmeans(df_work[,c("mean")], centers = clusNo)

myClus_res.within.ss <- sum(myClus$withinss)

clusterClass <- myClus$cluster

dftemp1 <- cbind(df_work, clusterNo = factor(clusterClass))

summary(dftemp1)

```



```{r, fig.width=12}
theme_set(theme_gray(base_size = 20))
dftemp1 %>%
  
  mutate(Cluster = factor(clusterNo,levels=c(1,2,3,4,5,6,7,8,9,10)))  %>%
  ggplot(aes(x=Cultivar,y=mean)) +
  theme_bw()+
  geom_errorbar(aes(ymin=mean-sd/2.45,ymax=mean+sd/2.45,colour=Cluster),alpha=0.8, width=0.5, linetype=2)+
  geom_point(aes(shape=Cluster, colour=Cluster), size =5) +
  ylab("Burr Burial  (%)") +
  xlab("Sowing date")
  
```


end of this script 