 ---
title: "BurrBurialandSeedNumberYield_Analysis"
author: "CT"
date: "Friday, March 18, 2016"
output: html_document
---
Purpose : 

Calculation for the seed number per m2, seed yield and estimated regeneration for the 16 cv trial in 2016 (season1) and 2017 (season2) 
ANOVA for the variates : seed number per m2, seed yield and estimated regeneration 

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
```




Read File 

```{r, echo=FALSE}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
getwd()
file <- read.table("CVTrial2017_Seed.txt",header=TRUE)
head(file)
summary(file)
```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Treat=as.factor(Treat)
   
  )

str(file)
summary(file)

```



Graph the SeedPerm2  average of both years!

```{r, fig.height= 5, fig.width=10 , warning=FALSE}

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

file %>%
  group_by(Cultivar, Treat) %>%
  summarise_each(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(SeedsPerM2_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsPerM2_mean-SeedsPerM2_sd/2, ymax=SeedsPerM2_mean+SeedsPerM2_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~Treat) +
    labs(y="Seeds per m2") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))


```

Here graph with the SE (SE = std/ sqrt n ; n=3)

```{r,fig.height= 5, fig.width=10 , warning=FALSE}

#calculate the SE in this case for 4 reps ! sqrt of 4 = 2 
df_burSE<-file %>%
  group_by(Cultivar, Treat) %>%
  summarise_each(funs(mean,sd)) %>%
  mutate(SE=SeedsPerM2_sd/2)
  
  
  df_burSE %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(SeedsPerM2_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(SeedsPerM2_mean),fill=Cultivar))+
  geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsPerM2_mean-SE/2, ymax=SeedsPerM2_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~Treat) +
    labs(y="Seeds per m2") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))






```


Do graph only with the 7 cultivars 



```{r, fig.height=5, fig.width=10}

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

df_burSubset<-file %>%
  filter(Year !="2017")%>%
  filter(Treat=="Cut")%>%
  filter(Cultivar=="Antas"| 
         Cultivar=="Denmark"|
         Cultivar=="Coolamon"|
           Cultivar=="MountBarker"|
           Cultivar=="Narrikup"|
           Cultivar=="Rosabrook"|
           Cultivar=="Woogenellup")%>%
  group_by(Cultivar) %>% 
  dplyr::select(SeedsPerM2)%>%
  summarise_each(funs(mean,sd)) %>%
  mutate(SE=sd/2)

  #Then graph it 
df_burSubset %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(SeedsPerM2_mean),fill=colPal)) +
  #ggplot(aes(x=Cultivar, y=(mean),fill=Cultivar))+
  ggplot(aes(x=Cultivar, y=(mean)))+
  geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=mean-SE/2, ymax=mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    #facet_grid(.~Treat) +
    labs(y="Seeds per m2") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))
 
#ggsave( "plot_SeedNumberTotal_.png", width=10, height=5, dpi=400)
```


Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}
df_seedANOVA <- file %>%
#use filters to select  data 
  filter(Year=="2016")%>%
  filter(Treat=="Cut")%>%
  filter(Cultivar=="Antas"| 
         Cultivar=="Denmark"|
         Cultivar=="Coolamon"|
           Cultivar=="MountBarker"|
           Cultivar=="Narrikup"|
           Cultivar=="Rosabrook"|
           Cultivar=="Woogenellup")%>%
  dplyr:: select(Cultivar:SeedYieldKgHa)
```

subset for anova
```{r}

 
summary(df_seedANOVA)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA 

head(file.subset)
summary(file.subset)

```

here select the variable 
seed per sqrt meter or seed per sqrtm


```{r}

#ANOVA

my.anova <- aov(SeedYieldKgHa ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsPerM2 ~ Cultivar + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

Perform Tukeys 

This is Tukeys test for mean comparison 

```{r}
#posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)
#loop with varios confidence intervals or alphas

for (i in seq(0.1, 0.95, by=0.1)) {
  
print(paste0("-------------------- CI is: ",i," -------------------"))  
posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=i) # check se CI aand alpha are correctly interpreted
print(posthoc)  
  
hsdTest <-HSD.test(my.anova, 'Cultivar', group=TRUE,alpha = 1-i)
print(hsdTest )
}


```

Then 
This is the mean separation using Tukey 


```{r}

fogo <-HSD.test(my.anova, 'Cultivar', group=TRUE)
fogo

```



Perform anova in cultivars with variable Seed number per m2

```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```

now do the mean table to write

```{r}


means<-file.subset%>%
  group_by(Treat,Cultivar)%>%
  dplyr::select( SeedsPerM2)%>%
  summarise_all(funs(mean))

```

now analyse seed yield kg/ha

Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}

str(file)
df_seedANOVA2 <- file %>%
filter(Year=="2016")%>%
   select(Cultivar:Treat, SeedYieldKgHa)
```


subset for anova
```{r}

 
summary(df_seedANOVA2)

#-------------------------------------------------
# anova 

file.subset2 <- df_seedANOVA2 

head(file.subset2)
summary(file.subset2)

```


Here Analyse the percentage of kg seeds per ha  overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedYieldKgHa ~ Cultivar*Treat + Block, data = file.subset2)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```


Perform anova in cultivars 


```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


Now analyse the regeneration of the seedlings 

Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}

df_seedANOVA3 <- file %>%
filter(Year=="2016")%>%
   select(Cultivar:Treat, EstimatedRegeneration)
```

subset for anova
```{r}

 
summary(df_seedANOVA3)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA3 

head(file.subset)
summary(file.subset)

```

see all treatmenst 

```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(EstimatedRegeneration ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)
```



```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```



```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```


get values for cultivar and treat 
```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


now perform  Year 2017 (cumulative seed numbers !! )

Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}
df_seedANOVA4 <- file %>%
filter(Year=="2017")%>%
   select(Year:SeedsPerM2)
```



subset for anova4
```{r}

 
summary(df_seedANOVA4)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA4 

head(file.subset)
summary(file.subset)

```

Here Analyse the percentage ofseeds overall :



```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedsPerM2 ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar", "Treat"), alpha= 0.05, p.adj="none")) 
```



```{r}
df_seedANOVA5 <- file %>%
filter(Year=="2017")%>%
   select(Year:SeedYieldKgHa)
```



subset for anova5
```{r}

 
summary(df_seedANOVA5)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA5 

head(file.subset)
summary(file.subset)

```


```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedYieldKgHa ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)

```

see effect of scultivar 

```{r}

#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar", "Treat"), alpha= 0.05, p.adj="none"))

```







end of this script 