 ---
title: "BurrsPerM2_Analysis_16 cv_trial"
author: "CT"
date: "28.12. 2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
Purpose : 
se
Calculation for the  number of burrs per m2 for measurements in  2016 
ANOVA for the variates : BursPerM2 of only Cut Treatmets

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
library(knitr)
```

Read File 

```{r, echo=FALSE}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
getwd()
file <- read.table("CVTrial2016_BurrsPerM2.txt",header=TRUE)
head(file)
summary(file)
```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  #dplyr:: select_(-PlotSide)%>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Treat=as.factor(Treat)
   
  )

str(file)
summary(file)

```



Graph the seedperburr
```{r, fig.height= 5, fig.width=10 , warning=FALSE}

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

file %>%
  group_by(Cultivar, Treat) %>%
  summarise_all(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(BursPerM2_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=BursPerM2_mean-BursPerM2_sd/2, ymax=BursPerM2_mean+BursPerM2_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~Treat) +
    labs(y="BursPerM2") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))


```


filter only seven cultivarsof interest 

```{r, fig.height=6, fig.width=12}

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

fileSeven<-file %>%
  filter(Cultivar=="Antas"|
          Cultivar=="Denmark"|
          Cultivar=="Coolamon"|
            Cultivar=="MountBarker"|
            Cultivar=="Narrikup"|
            Cultivar=="Rosabrook"|
            #Cultivar=="Whatawhata"|
            Cultivar=="Woogenellup")
#divide sd/2 and then /2 again to get the SE
fileSeven %>%
  group_by(Cultivar, Treat) %>%
  summarise_all(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(BursPerM2_mean)))+
   geom_bar(stat="identity", position = dodge_x, fill = "lightgrey") +
  geom_errorbar(aes(ymin=BursPerM2_mean-BursPerM2_sd/4, ymax=BursPerM2_mean+BursPerM2_sd/4),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    #facet_grid(.~Treat) +
    ylab(expression(Burrs~per~"m"^"2")) + 
  theme_bw()+
theme(axis.text.y = element_text( size = 26))+
theme(axis.title.y = element_text(face="bold", size=28))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 22,face="bold"))+
theme(axis.title.x = element_text( size=26))


#ggsave( "plot_BursPerM2_.png", width=15, height=10, dpi=400)

```

density1 <- seq(5,35,length.out=7)

Build a graph with strips across ? 


```{r, fig.height=6, fig.width=12}

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

density1 <- seq(5,35,length.out=7)


fileSeven<-file %>%
  filter(Cultivar=="Antas"|
          Cultivar=="Denmark"|
          Cultivar=="Coolamon"|
            Cultivar=="MountBarker"|
            Cultivar=="Narrikup"|
            Cultivar=="Rosabrook"|
            #Cultivar=="Whatawhata"|
            Cultivar=="Woogenellup")
#divide sd/2 and then /2 again to get the SE
fileSeven %>%
  group_by(Cultivar, Treat) %>%
  summarise_all(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(BursPerM2_mean)))+
  geom_bar(aes(fill=Cultivar)+scale_fill_brewer(palette="OrRd"))+
  
   #geom_bar(stat="identity", position = dodge_x, fill= Cultivar, scale_fill_brewer(palette="OrRd")) +
  geom_errorbar(aes(ymin=BursPerM2_mean-BursPerM2_sd/4, ymax=BursPerM2_mean+BursPerM2_sd/4),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    #facet_grid(.~Treat) +
    ylab(expression(Burrs~per~"m"^"2")) + 
  theme_bw()+
theme(axis.text.y = element_text( size = 26))+
theme(axis.title.y = element_text(face="bold", size=28))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 22,face="bold"))+
theme(axis.title.x = element_text( size=26))


#ggsave( "plot_BursPerM2_.png", width=15, height=10, dpi=400)

```

```{r}

```




Now perform anova in file seven 




Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}
df_seedANOVA <- fileSeven
#filter(Year=="2016")%>%
   #select_(Cultivar:SeedsPerBur)
```

subset for anova
```{r}

 
summary(df_seedANOVA)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA 

head(file.subset)
summary(file.subset)

```


Here Analyse the percentage ofseeds overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(BursPerM2 ~ Cultivar + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

then perfomr Tukeys test 

This is Tukeys test for mean comparison 

```{r}
posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)

posthoc

```

and 


```{r}

fogo <-HSD.test(my.anova, 'Cultivar', group=TRUE)
fogo

```
end of this script 