 ---
title: "SeedWeight_Analysis"
author: "CT"
date: "Friday, March 18, 2016"
output: html_document
---
Purpose : 

Calculation for the seed weight per individual seed (mg)

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
```




Read File 

```{r, echo=FALSE}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
getwd()
file <- read.table("CVTrial2017_Seed.txt",header=TRUE)
head(file)
summary(file)
```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Treat=as.factor(Treat)
   
  )

str(file)
summary(file)

```


Calculate seed weight as = divide seedyield per 10000 to have kg per m2. then divide /1000 to have grams then divide again in 1000 to havve in mg

```{r}
file <-file %>%
  mutate(IndivSeedweight=((SeedYieldKgHa/10000)/SeedsPerM2)*1000000)
```




Graph the IndivSeedweight  average of both years!

```{r, fig.height= 5, fig.width=10 , warning=FALSE}

# define position of bar and errorbar
# dodge_x <- position_dodge(width = 0.9)
# 
# file %>%
#   group_by(Cultivar, Treat) %>%
#   summarise_each(funs(mean,sd)) %>%
#   #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
#   #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
#   ggplot(aes(x=Cultivar, y=(SeedsPerM2_mean),fill=Cultivar))+
#    geom_bar(stat="identity", position = dodge_x) +
#   geom_errorbar(aes(ymin=SeedsPerM2_mean-SeedsPerM2_sd/2, ymax=SeedsPerM2_mean+SeedsPerM2_sd/2),
#                 width=0.25, size=0.3,position=dodge_x)   +
#   theme_grey(base_size = 16) +
#     facet_grid(.~Treat) +
#     labs(y="Seeds per m2") +
#   theme_bw()+
# theme(axis.text.y = element_text( size = 10))+
# theme(axis.title.y = element_text(face="bold", size=12))+
# theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))


```

Here graph with the SE (SE = std/ sqrt n ; n=4)

```{r,fig.height= 5, fig.width=10 , warning=FALSE}

# #calculate the SE in this case for 4 reps ! sqrt of 4 = 2 
# df_burSE<-file %>%
#   group_by(Cultivar, Treat) %>%
#   summarise_each(funs(mean,sd)) %>%
#   mutate(SE=SeedsPerM2_sd/2)
#   
#   
#   df_burSE %>%
#   #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
#   #ggplot(aes(x=Cultivar, y=(SeedsPerM2_mean),fill=colPal)) +
#   ggplot(aes(x=Cultivar, y=(SeedsPerM2_mean),fill=Cultivar))+
#   geom_bar(stat="identity", position = dodge_x) +
#   geom_errorbar(aes(ymin=SeedsPerM2_mean-SE/2, ymax=SeedsPerM2_mean+SE/2),
#                 width=0.25, size=0.3,position=dodge_x)   +
#   theme_grey(base_size = 16) +
#     facet_grid(.~Treat) +
#     labs(y="Seeds per m2") +
#   theme_bw()+
# theme(axis.text.y = element_text( size = 10))+
# theme(axis.title.y = element_text(face="bold", size=12))+
# theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))






```


Do graph only with the 7 cultivars 



```{r}
# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

df_burSubset<-file %>%
  filter(Year !="2017")%>%
  filter(Treat=="Cut")%>%
  filter(Cultivar=="Antas"| 
         Cultivar=="Denmark"|
         Cultivar=="Coolamon"|
           Cultivar=="MountBarker"|
           Cultivar=="Narrikup"|
           Cultivar=="Rosabrook"|
           Cultivar=="Woogenellup")%>%
  group_by(Cultivar) %>% 
  dplyr::select(IndivSeedweight)%>%
  summarise_each(funs(mean,sd)) %>%
  mutate(SE=sd/2)

  #Then graph it 
df_burSubset %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(SeedsPerM2_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(mean),fill=Cultivar))+
  geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=mean-SE/2, ymax=mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    #facet_grid(.~Treat) +
    labs(y="Seeds per m2") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))
 

```


Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}
df_seedANOVA <- file %>%
#use filters to select  data 
  filter(Year=="2016")%>%
  filter(Treat=="Cut")%>%
  filter(Cultivar=="Antas"| 
         Cultivar=="Denmark"|
         Cultivar=="Coolamon"|
           Cultivar=="MountBarker"|
           Cultivar=="Narrikup"|
           Cultivar=="Rosabrook"|
           Cultivar=="Woogenellup")%>%
  dplyr:: select(Cultivar:IndivSeedweight)
```

subset for anova
```{r}

 
summary(df_seedANOVA)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA 

head(file.subset)
summary(file.subset)

```


Here Analyse the percentage ofseeds overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

my.anova <- aov(IndivSeedweight ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsPerM2 ~ Cultivar + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```





end of this script 