 ---
title: "Biomass Yield_Analysis_16 cv_trial"
author: "CT"
date: "Friday, March 18, 2016"
output: html_document
---
Purpose : 
se
Calculation for the clover and weed  yield and estimated regeneration for the 16 cv trial in september 2016 
ANOVA for the variates : weed (dmWeed is kg/ha)

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
```

Read File 

```{r, echo=FALSE}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
getwd()
file <- read.table("CVTrial2017_Biomass.txt",header=TRUE)
head(file)
summary(file)
```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  filter(Cultivar!= "Nomad_Wc")%>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Treat=as.factor(Treat)
   
  )

str(file)
summary(file)

```

select sampling date!! September and October 

Graph the dmweed 

```{r, fig.height= 5, fig.width=10 , warning=FALSE}

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

file %>%
  group_by(Cultivar, Treat,Month,Date) %>%
  summarise_each(funs(mean,sd)) %>%
   #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(Dmweed_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=Dmweed_mean-Dmweed_sd/2, ymax=Dmweed_mean+Dmweed_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(Treat~Date) +
    labs(y="Weed kg/ha") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))


```

Here graph with the SE (SE = std/ sqrt n ; n=4)

```{r,fig.height= 5, fig.width=10 , warning=FALSE}

#calculate the SE in this case for 4 reps ! sqrt of 4 = 2 
df_burSE<-file %>%
  gather(key= "Variable" , value = "KgHa" , Dmclover:Dmweed)%>%
  group_by(Cultivar, Treat,Variable, Month) %>%
  dplyr::select(KgHa) %>%
  summarise_all(funs(mean,sd))
  
#colours
cols <- c(Weed="darkgrey", Clover="black")
  
##graph as a stack bar
df_burSE%>%
  ungroup(Variable)%>%
mutate(Variable = factor(Variable, levels = c("Dmweed",
                                 "Dmclover"),
                          labels = c("Weed",
                                 "Clover")
                          )) %>%
   mutate (Month= factor(Month, levels=c("September", "October" ),labels=c("September", "October")))%>%
  
  
  ggplot(aes(x=Cultivar, y=mean, fill=factor(Variable))) +
  
  geom_bar(stat="identity") +
  theme_bw()+
  facet_grid(Treat~Month) +
  scale_fill_manual(values = cols)+
  ylab("DM yield (Kg per ha)") +
  xlab("Cultivar") +
  theme(axis.text.x = element_text( angle=90,hjust=0.95,vjust=0.2)) + 
  theme(legend.title=element_blank()) +
  theme(text = element_text(size=16))







```

Make the sum of September and October

```{r}

dfSum<-df_burSE%>%
  group_by(Cultivar, Treat,Variable) %>%
  dplyr::select(mean) %>%
  summarise_all(funs(sum))

```





Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}
df_bioANOVA <- file %>%
filter(Month=="September")%>%
   select(Cultivar:Dmweed,Month)
```

subset for anova
```{r}

 
summary(df_bioANOVA)

#-------------------------------------------------
# anova 

file.subset <- df_bioANOVA

head(file.subset)
summary(file.subset)

```


Here Analyse the Dmclover:


```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(Dmclover ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```

Perform anova in cultivars 



```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


Here Analyse the DmWeed:


```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(Dmweed ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


```{r}
df_bioANOVAOct <- file %>%
filter(Month=="October")%>%
   select(Cultivar:Dmweed,Month)
```

subset for anova
```{r}

 
summary(df_bioANOVAOct)

#-------------------------------------------------
# anova 

file.subset2 <- df_bioANOVAOct

head(file.subset2)
summary(file.subset2)

```



Here Analyse the Dmclover:


```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(Dmclover ~ Cultivar*Treat + Block, data = file.subset2)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```



Here Analyse the Dmweed October :


```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(Dmweed ~ Cultivar*Treat + Block, data = file.subset2)
summary(my.anova)
```

weed kg /ha October 

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```
