 ---
title: "SeedlingRegeneration_Analysis_16 cv_trial"
author: "CT"
date: "28.12. 2017"
output: html_document
---
Purpose : 
se
Calculation for the seed number per burr for measurements in  2016 
ANOVA for the variates : SeedPerBur

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
```

Read File 

```{r, echo=FALSE}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
getwd()
file <- read.table("CVTrial2017_Regeneration.txt",header=TRUE)
head(file)
summary(file)
```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  #select(-PlotSide)%>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Treat=as.factor(Treat)
   
  )

str(file)
summary(file)

```



Graph the seedperburr
```{r, fig.height= 5, fig.width=15 , warning=FALSE}

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

file %>%
  #filter(Month=="January")%>%
  group_by(Cultivar, Treat,Month) %>%
  summarise_each(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(SeedlingPerm2_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  #geom_bar(aes(fill=Cultivar))+ 
  #scale_fill_brewer(palette="OrRd")+
  
  geom_errorbar(aes(ymin=SeedlingPerm2_mean-SeedlingPerm2_sd/2, ymax=SeedlingPerm2_mean+SeedlingPerm2_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 18) +
    facet_grid(Treat~Month) +
    labs(y="Seedling per m2") +
  theme_bw()+
theme(axis.text.y = element_text( size = 14))+
theme(axis.title.y = element_text(face="bold", size=14))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 14))


```

Here graph with the SE (SE = std/ sqrt n ; n=4)

```{r,fig.height= 5, fig.width=15 , warning=FALSE}

#calculate the SE in this case for 4 reps ! sqrt of 4 = 2 
df_burSE<-file %>%
  #filter(Month =="January")%>%
  group_by(Cultivar, Treat,Month) %>%
  summarise_each(funs(mean,sd)) %>%
  mutate(SE=SeedlingPerm2_sd/2)
  
  
  df_burSE %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(SeedlingPerm2_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(SeedlingPerm2_mean),fill=Cultivar))+
  geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=SeedlingPerm2_mean-SE/2, ymax=SeedlingPerm2_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(Treat~Month) +
    labs(y="Seedlings per m2") +
    ylim(0,1500)+
  theme_bw()+
theme(axis.text.y = element_text( size = 14))+
theme(axis.title.y = element_text(face="bold", size=14))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 14))



#ggsave("plot_Regeneration.png", width=12, height=6, dpi=400)


```




```{r, fig.height= 5, fig.width=15 , warning=FALSE}

#calculate the SE in this case for 4 reps ! sqrt of 4 = 2 
df_burSE<-file %>%
  filter(Month !="June")%>%
  group_by(Cultivar, Treat,Month) %>%
  summarise_all(funs(mean,sd)) %>%
  mutate(SE=SeedlingPerm2_sd/2)
  
df_burSE$Month_f=factor(df_burSE$Month, levels=c("January", "March", "May", "June"))
  
 df_burSE %>%
    
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(SeedlingPerm2_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(SeedlingPerm2_mean),fill=Cultivar, label=Cultivar))+
  geom_bar(stat="identity", position = dodge_x) +
   #geom_text(position="stack",angle = 90)+
  geom_errorbar(aes(ymin=SeedlingPerm2_mean-SE/2, ymax=SeedlingPerm2_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(Treat~Month_f) +
    labs(y="Seedlings per m2") +
    ylim(0,2000)+
  theme_bw()+
theme(axis.text.y = element_text( size = 14))+
theme(axis.title.y = element_text(face="bold", size=14))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 14))



ggsave("plot_Regeneration.png", width=12, height=6, dpi=400)

```



Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}
df_seedANOVA <- file %>%
filter(Month=="January")%>%
dplyr:: select(Cultivar:SeedlingPerm2)
```

subset for anova
```{r}

 
summary(df_seedANOVA)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA 

head(file.subset)
summary(file.subset)

```


Here Analyse the percentage ofseeds overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedlingPerm2 ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

Perform anova in cultivars 



```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```

now do the mean table to write

```{r}


means<-file.subset%>%
  group_by(Treat,Cultivar)%>%
  dplyr::select( SeedlingPerm2)%>%
  summarise_all(funs(mean))

```

now analyse for regeneration in March

Statistical Analisis 
Do ANOVA simple as per D. Saville :each season and variate separately
Select month and variable to analyse

```{r}

str(file)
df_seedANOVA2 <- file %>%
filter(Month=="March")%>%
   select(Cultivar,Plot,Block,Treat, SeedlingPerm2)
```


subset for anova
```{r}

 
summary(df_seedANOVA2)

#-------------------------------------------------
# anova 

file.subset2 <- df_seedANOVA2 

head(file.subset2)
summary(file.subset2)

```


Here Analyse 


```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedlingPerm2 ~ Cultivar*Treat + Block, data = file.subset2)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```


Perform anova in cultivars 


```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


tistics
   MSerror Df     Mean       CV  t.value      LSD
  57883.99 87 600.0483 40.09526 1.987608 239.1003

$parameters
        test p.ajusted   name.t ntr alpha
  Fisher-LSD      none Cultivar  15  0.05

$means
            SeedlingPerm2      std r         LCL       UCL Min  Max    Q25    Q50    Q75
Antas             982.750 337.1578 8  813.680589 1151.8194 252 1358  884.0 1042.0 1200.0
Campeda           370.600 234.3231 8  201.530589  539.6694   0  726  252.0  299.4  568.0
Coolamon          429.750 151.0179 8  260.680589  598.8194 252  568  299.4  457.4  568.0
Denmark           449.500 163.5455 8  280.430589  618.5694 252  726  370.5  410.0  568.0
Karridale         528.500 219.4194 8  359.430589  697.5694 252  884  370.5  568.0  607.5
Leura             177.250 156.1938 8    8.180589  346.3194   0  410    0.0  252.0  252.0
Monti             187.125 219.6851 8   18.055589  356.1944   0  568    0.0  133.5  291.5
MountBarker      1219.750 259.4487 8 1050.680589 1388.8194 726 1516 1160.5 1200.0 1397.5
Napier            686.500 184.0644 8  517.430589  855.5694 410  884  568.0  647.0  884.0
Narrikup          923.500 163.5455 8  754.430589 1092.5694 726 1200  844.5  884.0 1042.0
Rosabrook         350.750 187.6621 8  181.680589  519.8194 252  726  252.0  252.0  331.0
SeatonPark        587.750 320.8995 8  418.680589  756.8194 252 1042  252.0  568.0  884.0
Trikkala          370.500 163.5455 8  201.430589  539.5694 252  568  252.0  252.0  568.0
Whatawhata        516.750 332.9366 8  347.680589  685.8194   0 1042  252.0  568.0  726.0
Woogenellup      1219.750 259.4487 8 1050.680589 1388.8194 884 1516 1002.5 1279.0 1397.5

$comparison
NULL

$groups
            SeedlingPerm2 groups
MountBarker      1219.750      a
Woogenellup      1219.750      a
Antas             982.750     ab
Narrikup          923.500     bc
Napier            686.500     cd
SeatonPark        587.750     de
Karridale         528.500     de
Whatawhata        516.750     de
Denmark           449.500     de
Coolamon          429.750      e
Campeda           370.600     ef
Trikkala          370.500     ef
Rosabrook         350.750     ef
Monti             187.125      f
Leura             177.250      f

attr(,"class")
[1] "group"
Show in New WindowClear OutputExpand/Collapse Output
$statistics

Now perform for June 


```{r}
str(file)
df_seedANOVA3 <- file %>%
filter(Month=="May")
  #dplyr:: select_(Cultivar,Plot,Block,Treat, SeedlingPerm2)


summary(df_seedANOVA3)

#-------------------------------------------------
# anova 

file.subset3 <- df_seedANOVA3 

head(file.subset3)
summary(file.subset3)

```

Run ANova

```{r}
#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedlingPerm2 ~ Cultivar*Treat , data = file.subset3)
summary(my.anova)
```



```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar", "Treat"), alpha= 0.05, p.adj="none")) 
```



end of this script 