 ---
title: "SeedlingRegeneration_Analysis_16 cv_trial"
author: "CT"
date: "28.12. 2017"
output: html_document
---
Purpose : 

Calculation for the cumulative seedling numbers for the subset of 7 cultivars.








```{r}

#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)

```

Read File 

```{r, echo=FALSE}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
getwd()
file <- read.table("CVTrial2017_Regeneration.txt",header=TRUE)

seed <-  read.table("CVTrial2017_Seed.txt",header=TRUE)

df_HardRank <-  read.table("CVTrial2017_RankHard.txt",header=TRUE)

head(file)
summary(file)
```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  #select(-PlotSide)%>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Treat=as.factor(Treat),
    MeasurementDate=as.Date(dmy(MeasurementDate))
   
  )

str(file)
summary(file)

```



Filter treatments and cultivars of interest 

```{r, fig.height= 5, fig.width=15 , warning=FALSE}

#subset the data of interest 
df_fileSub <-file %>%
  #filter(Month !="JuneMid")%>%
  filter(Treat=="Cut")%>%

   filter(Cultivar=="Antas"|
          Cultivar=="Denmark"|
          Cultivar=="Coolamon"|
            Cultivar=="MountBarker"|
            Cultivar=="Narrikup"|
            Cultivar=="Rosabrook"|
             #Cultivar=="Whatawhata"|
            Cultivar=="Woogenellup")


```



Calculate the cumulative number of seedlings by each plot 

```{r}

#
str(df_fileSub)



# create an ID of each chunk
df_temp <- df_fileSub %>%
  
  mutate(codeID = as.factor(paste0(Plot,"_",Treat)))
  
# define unique factors to loop around
codesNames <- unique(df_temp$codeID)
  
  

# prepare final df to store data
df_final <- data.frame()



# loop
for(i in 1:length(codesNames)) {
  
  df_sub <- data.frame() # empty df
  
  df_sub <- df_temp %>%
    subset(codeID == codesNames[i]) %>% # segment one unique combination
    mutate(codeID = factor(codeID)) %>%
    arrange(MeasurementDate) %>%
    mutate(SeedlingNumber_cum = cumsum(SeedlingPerm2))
       
    
     df_final <- rbind(df_final,df_sub)
  
}

summary(df_final)


```



then rename dataframe 
```{r}

#rename dataframe

df_Cum <- df_final
  
  # filter(Month=="June")



```




Then merge with dataframe which contains the total number of seeds per m2 to calculate the remaining seeds in the soil bank. 

```{r}

#Select only columns of interest for seed data to merge 
df_seedSub <- seed %>%
  filter(Year !="2017")%>%
  filter(Treat=="Cut")%>%
  
  
filter(Cultivar=="Antas"|
          Cultivar=="Denmark"|
          Cultivar=="Coolamon"|
            Cultivar=="MountBarker"|
            Cultivar=="Narrikup"|
            Cultivar=="Rosabrook"|
            #Cultivar=="Whatawhata"|
            Cultivar=="Woogenellup")%>%
  dplyr::select(Plot,SeedsPerM2)


```

merge dataframes 

```{r}

df_total <- merge(df_Cum,df_seedSub,by="Plot")

```

Calculate number of remaining seed in soil bank



```{r}
str(df_total)

df_total<-df_total %>%
  mutate(NumberRemainSeeds=SeedsPerM2- SeedlingNumber_cum)%>%
  mutate(PercRemainSeeds=100*(NumberRemainSeeds/SeedsPerM2))%>%
  mutate(PercLostSeeds=100-PercRemainSeeds)
  
  str(df_total)
```


```{r,fig.height=8; fig.widht=18}

checkMean <-df_total %>%
  #filter(Month!=JuneMid)%>%
  group_by(Cultivar,Month)%>%
  dplyr::select(PercLostSeeds)%>%
  summarise_all(funs(mean))

checkMean %>%
   filter(Month== "January"|Month== "March")%>%
  ggplot(aes(x=Cultivar, y=PercLostSeeds)) + 
   geom_point(aes(shape= Cultivar,colour = Cultivar), size=6)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14))+
     #labs(x="Hours",y="Cummulative Germination Percent(%)")+
  #facet_grid(.~Temp)
  #facet_wrap(.~Temp, ncol=6)

facet_wrap(~Month, scales = "free")+
  #facet_wrap(Variable~Month2)+
  theme_bw(base_size=16)+
  #scale_x_continuous(breaks = c(1,200,300))+
  #scale_y_continuous(limits = c(min_xy, max_xy))+
  #xlim(0, 6)+
  theme(axis.text.x=element_text(angle = +90, hjust = 0, size= 7))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 14))+
  theme(axis.title.y = element_text(angle = 90, hjust = 0.5, size= 12))+
  labs(y= "       Percentage lost seeds (%)  ",
       x="Hardseed Rank ")
 # geom_abline(intercept = 50, slope = 0)

#ggsave( "plot_SeedLostwhata_.png", width=15, height=10, dpi=400)
```



Merge with the hardseed rank to graph Remaining seeds in soil versus Hardseed Rank

```{r}



df_totalRank <- merge(df_total,df_HardRank,by="Cultivar")
```

Check mean values 

```{r}
df_MM<-df_totalRank%>%
  group_by(Month,Cultivar)%>%
  filter (Month != "JuneMid")%>%
  arrange(MeasurementDate)%>%
summarise_all(funs(mean))


```





Plot mean number remaining seeds against hard Rank 

```{r}
df_totalRankMean<-df_totalRank%>%
  group_by(Month,Cultivar)%>%
  dplyr::select(SeedsPerM2, NumberRemainSeeds,HardseedRank,PercRemainSeeds,PercLostSeeds)%>%
summarise_all(funs(mean))

#gather vvalues 

df_gathered<-df_totalRankMean %>%
  gather(key= "Variable" , value = "Value" , NumberRemainSeeds,PercRemainSeeds,PercLostSeeds)
```



Plot mean percent of  remaining seeds against hard Rank in June 


```{r, fig.height=16, fig.width=20}

#min_xy <- min(min(df_gathered$HardseedRank), min(df_gathered$Value))
#max_xy <- max(max(df_gathered$HardseedRank), max(df_gathered$Value))

df_gathered %>%
    filter(Month=="January"|Month=="March"|Month=="June")%>%
  mutate (Month2= factor(Month, levels=c("January", "March", "June"),labels=c("A_January", "B_March", "C_June")))%>%
  #filter(Month=="January"|Month=="March")%>%
    
  
  #filter(Month=="March")%>%
ggplot(aes(x=HardseedRank, y=Value)) + 
  #ggplot(aes(x=Variable, y=Value)) + 
   geom_point(aes(shape= Cultivar), size=6)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
     #labs(x="Hours",y="Cummulative Germination Percent(%)")+
  #facet_grid(.~Temp)
  #facet_wrap(.~Temp, ncol=6)

facet_wrap(Variable~Month2, scales = "free")+
  #facet_wrap(Variable~Month2)+
  theme_bw(base_size=16)+
  #scale_x_continuous(breaks = c(1,200,300))+
  #scale_y_continuous(limits = c(min_xy, max_xy))+
  #xlim(0, 6)+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 16))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 14))+
  theme(axis.title.y = element_text(angle = 90, hjust = 0.5, size= 12))+
  labs(y= "       Percentage            (%)                                                                 Number of remaining seeds per m2 ",
       x="Hardseed Rank ")  
 # geom_abline(intercept = 50, slope = 0)

 ggsave( "plot_SeedRemainPerc_.png", width=15, height=10, dpi=400)

```





get the lm for January 




```{r}

df_January<-df_totalRankMean %>%
  
filter(Month=="January")

str(df_January)
  
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}

#use all datapoints 
df <- df_January%>% 
  #dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E) %>%
  #group_by(SowTreat,Cultivar) %>%
  #summarise_each(funs(mean)) %>%
  mutate(y=PercRemainSeeds,x=HardseedRank)%>%
  dplyr::select(-PercRemainSeeds, -HardseedRank)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_point(aes(colour = factor(Cultivar)), size=5) + scale_shape(solid = FALSE)+ 
  
  theme_bw()+
  scale_x_continuous(limits = c(0,6))+
  scale_y_continuous(limits = c(90,100))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE)  
  #facet_grid(Cultivar~.,scales="free")
  
p1


```


Here Analyse 


```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedlingPerm2 ~ Cultivar + Block, data = file.subset2)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```


Perform anova in cultivars 


```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


tistics
   MSerror Df     Mean       CV  t.value      LSD
  57883.99 87 600.0483 40.09526 1.987608 239.1003

$parameters
        test p.ajusted   name.t ntr alpha
  Fisher-LSD      none Cultivar  15  0.05

$means
            SeedlingPerm2      std r         LCL       UCL Min  Max    Q25    Q50    Q75
Antas             982.750 337.1578 8  813.680589 1151.8194 252 1358  884.0 1042.0 1200.0
Campeda           370.600 234.3231 8  201.530589  539.6694   0  726  252.0  299.4  568.0
Coolamon          429.750 151.0179 8  260.680589  598.8194 252  568  299.4  457.4  568.0
Denmark           449.500 163.5455 8  280.430589  618.5694 252  726  370.5  410.0  568.0
Karridale         528.500 219.4194 8  359.430589  697.5694 252  884  370.5  568.0  607.5
Leura             177.250 156.1938 8    8.180589  346.3194   0  410    0.0  252.0  252.0
Monti             187.125 219.6851 8   18.055589  356.1944   0  568    0.0  133.5  291.5
MountBarker      1219.750 259.4487 8 1050.680589 1388.8194 726 1516 1160.5 1200.0 1397.5
Napier            686.500 184.0644 8  517.430589  855.5694 410  884  568.0  647.0  884.0
Narrikup          923.500 163.5455 8  754.430589 1092.5694 726 1200  844.5  884.0 1042.0
Rosabrook         350.750 187.6621 8  181.680589  519.8194 252  726  252.0  252.0  331.0
SeatonPark        587.750 320.8995 8  418.680589  756.8194 252 1042  252.0  568.0  884.0
Trikkala          370.500 163.5455 8  201.430589  539.5694 252  568  252.0  252.0  568.0
Whatawhata        516.750 332.9366 8  347.680589  685.8194   0 1042  252.0  568.0  726.0
Woogenellup      1219.750 259.4487 8 1050.680589 1388.8194 884 1516 1002.5 1279.0 1397.5

$comparison
NULL

$groups
            SeedlingPerm2 groups
MountBarker      1219.750      a
Woogenellup      1219.750      a
Antas             982.750     ab
Narrikup          923.500     bc
Napier            686.500     cd
SeatonPark        587.750     de
Karridale         528.500     de
Whatawhata        516.750     de
Denmark           449.500     de
Coolamon          429.750      e
Campeda           370.600     ef
Trikkala          370.500     ef
Rosabrook         350.750     ef
Monti             187.125      f
Leura             177.250      f

attr(,"class")
[1] "group"
Show in New WindowClear OutputExpand/Collapse Output
$statistics

Now perform for June 


```{r}
str(file)
df_seedANOVA3 <- filesub %>%
filter(Month=="June")
  #dplyr:: select_(Cultivar,Plot,Block,Treat, SeedlingPerm2)


summary(df_seedANOVA3)

#-------------------------------------------------
# anova 

file.subset3 <- df_seedANOVA3 

head(file.subset3)
summary(file.subset3)

```

Run ANova

```{r}
#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedlingPerm2 ~ Cultivar , data = file.subset3)
summary(my.anova)
```



```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar", "Treat"), alpha= 0.05, p.adj="none")) 
```



end of this script 