 ---
title: "SeedPerBur_Analysis_16 cv_trial"
author: "CT"
date: "28.12. 2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
Purpose : 
se
Calculation for the seed number per burr for measurements in  2016 
ANOVA for the variates : SeedPerBur

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
library(knitr)
```

Read File 

```{r, echo=FALSE}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
getwd()
file <- read.table("CVTrial2016_SeedPerBurr.txt",header=TRUE)
head(file)
summary(file)
```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  #dplyr:: select_(-PlotSide)%>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Treat=as.factor(Treat)
   
  )

str(file)
summary(file)

```



Graph the seedperburr
```{r, fig.height= 5, fig.width=10 , warning=FALSE}

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

file %>%
  group_by(Cultivar, Treat) %>%
  summarise_each(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(SeedsPerBur_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsPerBur_mean-SeedsPerBur_sd/2, ymax=SeedsPerBur_mean+SeedsPerBur_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~Treat) +
    labs(y="Seeds per Bur") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))


```

Here graph with the SE (SE = std/ sqrt n ; n=4)

```{r,fig.height= 5, fig.width=10 , warning=FALSE}

#calculate the SE in this case for 4 reps ! sqrt of 4 = 2 
df_burSE<-file %>%
  group_by(Cultivar, Treat) %>%
  summarise_each(funs(mean,sd)) %>%
  mutate(SE=SeedsPerBur_sd/2)
  
  
  df_burSE %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(SeedsPerBur_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(SeedsPerBur_mean),fill=Cultivar))+
  geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsPerBur_mean-SE, ymax=SeedsPerBur_mean+SE),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~Treat) +
    labs(y="Seeds per Bur") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))






```

Select the seven cultivars and do graph 


```{r, fig.height=6, fig.width=12}



fileSeven2 <-file %>%
  filter(Cultivar=="Antas"|
          Cultivar=="Denmark"|
          Cultivar=="Coolamon"|
            Cultivar=="MountBarker"|
            Cultivar=="Narrikup"|
            Cultivar=="Rosabrook"|
            #Cultivar=="Whatawhata"|
            Cultivar=="Woogenellup")

fileSeven3 <-fileSeven2 %>%
  group_by(Cultivar) %>%
  dplyr::select(SeedsPerBur)%>%
  summarise_each(funs(mean,sd))


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)
#need to divide by 4 to get the SE !!! 
fileSeven3%>%
  ggplot(aes(x=Cultivar, y=(mean),fill=Cultivar))+
  geom_bar(stat="identity", position = dodge_x, fill = "cornsilk4") +
  geom_errorbar(aes(ymin=mean-sd/4, ymax=mean+sd/4),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    #facet_grid(.~Treat) +
    #labs(y="Seeds per Burr") +
  ylab(expression(Seeds~per~"Burr")) +
  theme_bw()+
theme(axis.text.y = element_text( size = 26))+
theme(axis.title.y = element_text(face="bold", size=28))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 22,face="bold"))+
theme(axis.title.x = element_text( size=26))


#ggsave( "plot_SeedsPerBur_.png", width=15, height=10, dpi=400)



```



Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}
#df_seedANOVA <- file 
df_seedANOVA <- fileSeven2
#filter(Year=="2016")%>%
   #select_(Cultivar:SeedsPerBur)
```

subset for anova
```{r}

 
summary(df_seedANOVA)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA 

head(file.subset)
summary(file.subset)

```


Here Analyse the percentage ofseeds overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedsPerBur ~ Cultivar + Block, data = file.subset)
summary(my.anova)
```
First LSD 

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

Perform Tukeys 


This is Tukeys test for mean comparison 

```{r}
#posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)
posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.25)

posthoc

```


Then 
This is the mean separation using Tukey 


```{r}

fogo <-HSD.test(my.anova, 'Cultivar', group=TRUE)
fogo

```

now do the mean table to write

```{r}


means<-file.subset%>%
  group_by(Treat,Cultivar)%>%
  dplyr::select( SeedsPerBur)%>%
  summarise_all(funs(mean))

```

now analyse seed yield kg/ha

Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}

str(file)
df_seedANOVA2 <- file %>%
filter(Year=="2016")%>%
   select(Cultivar:Treat, SeedYieldKgHa)
```


subset for anova
```{r}

 
summary(df_seedANOVA2)

#-------------------------------------------------
# anova 

file.subset2 <- df_seedANOVA2 

head(file.subset2)
summary(file.subset2)

```


Here Analyse the percentage of kg seeds per ha  overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedYieldKgHa ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```


Perform anova in cultivars 


```{r}


#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


Now analyse the regeneration of the seedlings 

Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}

df_seedANOVA3 <- file %>%
filter(Year=="2016")%>%
   select(Cultivar:Treat, EstimatedRegeneration)
```

subset for anova
```{r}

 
summary(df_seedANOVA3)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA3 

head(file.subset)
summary(file.subset)

```

see all treatmenst 

```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(EstimatedRegeneration ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)
```



```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```



```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```


get values for cultivar and treat 
```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


end of this script 