 ---
title: "SeedlingRegeneration_Analysis_16 cv_trial"
author: "CT"
date: "28.12. 2017"
output: html_document
---
Purpose : 

This script is similar to Script 8 cumulative regeneration but it is updagted !! 
Calculation for the cumulative seedling numbers for the subset of 7 cultivars.
Buid a graph with the SE and only remaining number of seeds and percentage of lost seeds, Include SE in graph  




```{r}

#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)

```

Read File 

```{r, echo=FALSE}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
getwd()
file <- read.table("CVTrial2017_Regeneration.txt",header=TRUE)

seed <-  read.table("CVTrial2017_Seed.txt",header=TRUE)

df_HardRank <-  read.table("CVTrial2017_RankHard.txt",header=TRUE)

head(file)
summary(file)
```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  #select(-PlotSide)%>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Treat=as.factor(Treat),
    MeasurementDate=as.Date(dmy(MeasurementDate))
   
  )

str(file)
summary(file)

```



Filter treatments and cultivars of interest 

```{r, fig.height= 5, fig.width=15 , warning=FALSE}

#subset the data of interest 
df_fileSub <-file %>%
  #filter(Month !="JuneMid")%>%
  filter(Treat=="Cut")%>%

   filter(Cultivar=="Antas"|
          Cultivar=="Denmark"|
          Cultivar=="Coolamon"|
            Cultivar=="MountBarker"|
            Cultivar=="Narrikup"|
            Cultivar=="Rosabrook"|
             #Cultivar=="Whatawhata"|
            Cultivar=="Woogenellup")


```



Calculate the cumulative number of seedlings by each plot 

```{r}

#
str(df_fileSub)



# create an ID of each chunk
df_temp <- df_fileSub %>%
  
  mutate(codeID = as.factor(paste0(Plot,"_",Treat)))
  
# define unique factors to loop around
codesNames <- unique(df_temp$codeID)
  
  

# prepare final df to store data
df_final <- data.frame()



# loop
for(i in 1:length(codesNames)) {
  
  df_sub <- data.frame() # empty df
  
  df_sub <- df_temp %>%
    subset(codeID == codesNames[i]) %>% # segment one unique combination
    mutate(codeID = factor(codeID)) %>%
    arrange(MeasurementDate) %>%
    mutate(SeedlingNumber_cum = cumsum(SeedlingPerm2))
       
    
     df_final <- rbind(df_final,df_sub)
  
}

summary(df_final)


```



then rename dataframe 
```{r}

#rename dataframe

df_Cum <- df_final
  
  # filter(Month=="June")



```




Then merge with dataframe which contains the total number of seeds per m2 to calculate the remaining seeds in the soil bank. 

```{r}

#Select only columns of interest for seed data to merge 
df_seedSub <- seed %>%
  filter(Year !="2017")%>%
  filter(Treat=="Cut")%>%
  
  
filter(Cultivar=="Antas"|
          Cultivar=="Denmark"|
          Cultivar=="Coolamon"|
            Cultivar=="MountBarker"|
            Cultivar=="Narrikup"|
            Cultivar=="Rosabrook"|
            #Cultivar=="Whatawhata"|
            Cultivar=="Woogenellup")%>%
  dplyr::select(Plot,SeedsPerM2)


```

merge dataframes 

```{r}

df_total <- merge(df_Cum,df_seedSub,by="Plot")

```

Calculate number of remaining seed in soil bank



```{r}
str(df_total)

df_total<-df_total %>%
  mutate(NumberRemainSeeds=SeedsPerM2- SeedlingNumber_cum)%>%
  mutate(PercRemainSeeds=100*(NumberRemainSeeds/SeedsPerM2))%>%
  mutate(PercLostSeeds=100-PercRemainSeeds)
  
  str(df_total)
```

then merge with the Hardseed Ranking 



Merge with the hardseed rank to graph Remaining seeds in soil versus Hardseed Rank

```{r}

df_totalRank <- merge(df_total,df_HardRank,by="Cultivar")
str(df_totalRank)
```




```{r}
df_NumberSeedsRemain <-df_totalRank %>%
  filter(Month!="JuneMid")%>%
  group_by(Cultivar,Month, HardseedRank )%>%
  dplyr::select(PercLostSeeds)%>%
  summarise_all(funs(mean,sd))%>%
  ungroup()


```


Then calculate the max sd and graph the percentage of lost seeds due to strike  

```{r,fig.height=5, fig.width=15}

#Here how to create the end error bar with max Sd 
# find size of bar per month
# find single position of x y to put the bar

#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.15 # extra position for single error bar
x_max<-max(df_NumberSeedsRemain$HardseedRank)
y_max<-max(df_NumberSeedsRemain$mean)

# find largest standard error
sd_df <- df_NumberSeedsRemain %>% 
  group_by(Month) %>%
  dplyr::select(sd)%>%
  summarise_all(max)%>%
  #summarise(max_sd = max(sd)) %>% 
  ungroup() %>%
  rowwise() %>%
  #rename variables
  mutate(HardseedRank = x_max*extraPos, mean = y_max*extraPos,max_sd=sd )

summary(sd_df)

#divide sd/4 as number of replicates were 4 and need to divide the SE by two for graph

df_NumberSeedsRemain%>%
  mutate(Month= factor(Month, levels=c("January", "March", "June"),
                           labels=c("January", "March", "June")))%>%
 # filter(Cultivar=="Antas"|Cultivar=="Denmark"|Cultivar=="Leura")%>%
ggplot(aes(x=HardseedRank, y=mean)) + 
  geom_point(aes(shape=Cultivar),size=5, stroke=2)+
 # geom_line(aes(linetype=Cultivar),alpha=0.2)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  #scale_shape_manual(values = c(0,1,2,3,4))+
  #scale_shape_manual(values = c(1,2,4,7,8,9))+
  geom_errorbar(data=sd_df, aes(ymin=mean-max_sd/4,
                    ymax=mean+max_sd/4), width=1)+
  facet_wrap(~Month,ncol=3, scales = "free")+
  theme_bw(base_size = 26)+
  #scale_y_continuous(breaks = c(5,10,20,30,40,50))+
  ylim(0, 50)+
  #xlim(0,10)+
  labs(y="Cumulative emergence (%) ",x="Hardseed Rank")+ 
  geom_abline(intercept = 30, slope = 0, linetype=2)+
#Themes
#theme(axis.text.y = element_text( size = 26))+
#theme(axis.title.y = element_text(face="bold", size=18))+
#theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 20,face="bold"))+
  theme(axis.title.x = element_text( size=24)) + scale_x_continuous(breaks = c(0:6))+
  theme(text=element_text(size=30,  family="serif"))+
  theme(title=element_text(size=22,  family="serif",face="bold"))+
  theme(title=element_text(size=22,  family="serif",face="bold"))
  
  

ggsave( "plot_CumulativeEmergence_.png", width=15, height=6, dpi=500)
#OBS ANOVA for this dataset follows ......)

```



build a graph with the number of seeds which remained in seed bank

```{r}

df_NumberSeedsBank <-df_totalRank %>%
  filter(Month!="JuneMid")%>%
  group_by(Cultivar,Month, HardseedRank )%>%
  dplyr::select( NumberRemainSeeds)%>%
  summarise_all(funs(mean,sd))%>%
  ungroup()



```
Then calculate the max sd and graph the number of seeds in seed bank   

```{r,fig.height=5, fig.width=15}


#Here how to create the end error bar with max Sd 
# find size of bar per month
# find single position of x y to put the bar

#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.05 # extra position for single error bar
x_max<-max(df_NumberSeedsBank$HardseedRank)
y_max<-max(df_NumberSeedsBank$mean)

# find largest standard error
sd_df <- df_NumberSeedsBank %>% 
  group_by(Month) %>%
  dplyr::select(sd)%>%
  summarise_all(max)%>%
  #summarise(max_sd = max(sd)) %>% 
  ungroup() %>%
  rowwise() %>%
  #rename variables
  mutate(HardseedRank = x_max*extraPos, mean = y_max*extraPos,max_sd=sd )

summary(sd_df)

#divide sd/2 as number of replicates were 4 

df_NumberSeedsBank%>%
  mutate(Month= factor(Month, levels=c("January", "March", "June"),
                           labels=c("January", "March", "June")))%>%
 # filter(Cultivar=="Antas"|Cultivar=="Denmark"|Cultivar=="Leura")%>%
ggplot(aes(x=HardseedRank, y=mean)) + 
  geom_point(aes(shape=Cultivar),size=7, stroke=2)+
 # geom_line(aes(linetype=Cultivar),alpha=0.2)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  #scale_shape_manual(values = c(0,1,2,3,4))+
  #scale_shape_manual(values = c(1,2,4,7,8,9))+
  geom_errorbar(data=sd_df, aes(ymin=mean-max_sd/4,
                    ymax=mean+max_sd/4), width=1)+
  facet_wrap(~Month,ncol=3, scales = "free")+
  #theme_bw()+
  #scale_x_continuous(breaks = c(5,10,15,20,30))+
  #ylim(0, 80)+
  ylim(3500,14000)+
  labs(y="Number of seeds in seed bank",x="Hardseed Rank")+ 
  geom_abline(intercept = 10000, slope = 0, linetype=2)+
  theme_bw(base_size = 26)+
    #geom_abline(intercept = 100, slope = 0, linetype=2)+
#  theme(axis.text.y = element_text( size = 20))+
# theme(axis.title.y = element_text(face="bold", size=22))+
# theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 22,face="bold"))+
# theme(axis.title.x = element_text( size=24))

#theme(axis.title.x = element_text( size=24)) + 
  scale_x_continuous(breaks = c(0:6))+
  theme(text=element_text(size=26,  family="serif"))+
  theme(title=element_text(size=20, family="serif",face="bold"))+
  #theme(title=element_text(size=22,  family="serif",face="bold"))

ggsave( "plot_NumberSeedsInSeedBank_.png", width=15, height=6, dpi=500)

```




Plot mean number remaining seeds against hard Rank 

```{r}
df_totalRankMean<-df_totalRank%>%
  group_by(Month,Cultivar)%>%
  dplyr::select(SeedsPerM2, NumberRemainSeeds,HardseedRank,PercRemainSeeds,PercLostSeeds)%>%
summarise_all(funs(mean))

#gather vvalues 

df_gathered<-df_totalRankMean %>%
  gather(key= "Variable" , value = "Value" , NumberRemainSeeds,PercRemainSeeds,PercLostSeeds)
```



Plot mean percent of  remaining seeds against hard Rank in June 


```{r, fig.height=16, fig.width=20}

#min_xy <- min(min(df_gathered$HardseedRank), min(df_gathered$Value))
#max_xy <- max(max(df_gathered$HardseedRank), max(df_gathered$Value))

df_gathered %>%
    filter(Month=="January"|Month=="March"|Month=="June")%>%
  mutate (Month2= factor(Month, levels=c("January", "March", "June"),labels=c("A_January", "B_March", "C_June")))%>%
  #filter(Month=="January"|Month=="March")%>%
    
  
  #filter(Month=="March")%>%
ggplot(aes(x=HardseedRank, y=Value)) + 
  #ggplot(aes(x=Variable, y=Value)) + 
   geom_point(aes(shape= Cultivar), size=8)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
     #labs(x="Hours",y="Cummulative Germination Percent(%)")+
  #facet_grid(.~Temp)
  #facet_wrap(.~Temp, ncol=6)

facet_wrap(Variable~Month2, scales = "free")+
  #facet_wrap(Variable~Month2)+
  theme_bw(base_size=16)+
  #scale_x_continuous(breaks = c(1,200,300))+
  #scale_y_continuous(limits = c(min_xy, max_xy))+
  #xlim(0, 6)+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 16))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 14))+
  theme(axis.title.y = element_text(angle = 90, hjust = 0.5, size= 12))+
  labs(y= "       Percentage            (%)                                                                 Number of remaining seeds per m2 ",
       x="Hardseed Rank ")  
 # geom_abline(intercept = 50, slope = 0)

 ggsave( "plot_SeedRemainPerc_.png", width=15, height=10, dpi=400)

```





```{r, fig.height=16, fig.width=20}

#min_xy <- min(min(df_gathered$HardseedRank), min(df_gathered$Value))
#max_xy <- max(max(df_gathered$HardseedRank), max(df_gathered$Value))

df_gathered %>%
    filter(Month=="January"|Month=="March"|Month=="June")%>%
  mutate (Month2= factor(Month, levels=c("January", "March", "June"),labels=c("A_January", "B_March", "C_June")))%>%
  #filter(Month=="January"|Month=="March")%>%
    
  
  #filter(Month=="March")%>%
ggplot(aes(x=HardseedRank, y=Value)) + 
  #ggplot(aes(x=Variable, y=Value)) + 
   geom_point(aes(shape= Cultivar), size=8)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
     #labs(x="Hours",y="Cummulative Germination Percent(%)")+
  #facet_grid(.~Temp)
  #facet_wrap(.~Temp, ncol=6)

facet_wrap(Variable~Month2, scales = "free")+
  #facet_wrap(Variable~Month2)+
  theme_bw(base_size=16)+
  #scale_x_continuous(breaks = c(1,200,300))+
  #scale_y_continuous(limits = c(min_xy, max_xy))+
  #xlim(0, 6)+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 16))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 14))+
  theme(axis.title.y = element_text(angle = 90, hjust = 0.5, size= 12))+
  labs(y= "       Percentage            (%)                                                                 Number of remaining seeds per m2 ",
       x="Hardseed Rank ")  
 # geom_abline(intercept = 50, slope = 0)

 #ggsave( "plot2_SeedRemainPerc_.png", width=15, height=10, dpi=400)

```



get the lm for January 




```{r}

df_January<-df_totalRankMean %>%
  
filter(Month=="January")

str(df_January)
  
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}

#use all datapoints 
df <- df_January%>% 
  #dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E) %>%
  #group_by(SowTreat,Cultivar) %>%
  #summarise_each(funs(mean)) %>%
  mutate(y=PercRemainSeeds,x=HardseedRank)%>%
  dplyr::select(-PercRemainSeeds, -HardseedRank)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_point(aes(colour = factor(Cultivar)), size=5) + scale_shape(solid = FALSE)+ 
  
  theme_bw()+
  scale_x_continuous(limits = c(0,6))+
  scale_y_continuous(limits = c(90,100))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE)  
  #facet_grid(Cultivar~.,scales="free")
  
p1


```


Here Analyse by Month first the cumulativepercentage of seed loss and then seeds in seedbnk 


```{r}
#Select variable to analys 

file.subset2<- df_totalRank %>%
  dplyr::select(Cultivar:Block, PercLostSeeds,NumberRemainSeeds)%>%
  filter(Month!="JuneMid")


```



## Create index to filter for loop ANOVA in file.subset2

```{r}
y <- c("January","March","June")

sdIndex <- unique(file.subset2$Month)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```


get mean separation when P <0.05


## Then loop anova for each individual Month 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset3 <- file.subset2 %>%
  filter(Month==sdIndex[i])
  
 
head(file.subset3, 50)
   summary(file.subset3)
my.anova <- aov(PercLostSeeds ~ Cultivar + Block, data = file.subset3)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


 if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
   print("***Sig Cultivar***") 
   print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```


do the same procedure for Number of seeds in seed bank 


```{r}

#ANOVA

for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset3 <- file.subset2 %>%
  filter(Month==sdIndex[i])
  
 
head(file.subset3, 50)
   summary(file.subset3)
my.anova <- aov(NumberRemainSeeds ~ Cultivar + Block, data = file.subset3)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


 if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
   print("***Sig Cultivar***") 
   print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}


```


Then loop ANOVA with post hoc test as Tukeys 


## Then loop anova for each individual Month 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset3 <- file.subset2 %>%
  filter(Month==sdIndex[i])
  
 
head(file.subset3, 50)
   summary(file.subset3)
my.anova <- aov(PercLostSeeds ~ Cultivar + Block, data = file.subset3)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  #print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) }
  print(posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)) }


 # if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
 #   print("***Sig Cultivar***") 
 #   print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant


print (fogo <-HSD.test(my.anova, 'Cultivar', group=TRUE))

  
}

```


Now do tukeys with variable: Number of seeds in seed bank

Then loop ANOVA with post hoc test as Tukeys 


## Then loop anova for each individual Month 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset3 <- file.subset2 %>%
  filter(Month==sdIndex[i])
  
 
head(file.subset3, 50)
   summary(file.subset3)
my.anova <- aov(NumberRemainSeeds ~ Cultivar + Block, data = file.subset3)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  #print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) }
  print(posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)) }


 # if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
 #   print("***Sig Cultivar***") 
 #   print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant


print (fogo <-HSD.test(my.anova, 'Cultivar', group=TRUE))

  
}

```

end of this script 