---
title: "BurrBurialAnalysis"
author: "CT"
date: "Friday, March 18, 2016"
output: html_document
---
Purpose : 

Calculation for the percentage of buried burs for the 16 cv trial in 2017 
ANOVA for the variate : precentage of buried burs 

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
```

Read File 

```{r, echo=FALSE}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
getwd()
file <- read.table("CVTrial2017.txt",header=TRUE)
head(file)
summary(file)
```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Treat=as.factor(Treat)
   
  )

str(file)
summary(file)

```



Graph the percentage of buried burrs 

```{r, fig.height= 5, fig.width=10 , warning=FALSE}

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

file %>%
  group_by(Cultivar, Treat) %>%
  summarise_each(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(PercentBurBurial_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=PercentBurBurial_mean-PercentBurBurial_sd/2, ymax=PercentBurBurial_mean+PercentBurBurial_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~Treat) +
    labs(y="% Buried burrs") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))


```

Here graph with the SE (SE = std/ sqrt n ; n=3)

```{r,fig.height= 5, fig.width=10 , warning=FALSE}

#calculate the SE in this case for 4 reps ! sqrt of 4 = 2 
df_burSE<-file %>%
  group_by(Cultivar, Treat) %>%
  summarise_each(funs(mean,sd)) %>%
  mutate(SE=PercentBurBurial_sd/2)
  
  
  df_burSE %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PercentBurBurial_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(PercentBurBurial_mean),fill=Cultivar))+
  geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=PercentBurBurial_mean-SE/2, ymax=PercentBurBurial_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~Treat) +
    labs(y="% Buried burrs") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))






```






Statistical Analisis 
Do ANOVA simple as per D. Saville : each sowing date separately.

```{r}

 
summary(file)

df_burANOVA <- file #use to filter%>%
  


#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file %>%
  select(-PropBurrBurial)

head(file.subset)
summary(file.subset)

```

Here Analyse the percentage of buried burs overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(PercentBurBurial ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

Perform anova in cultivars 



```{r}


#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


do a cluster analysis

```{r}
df_work<-file %>% dplyr::select(Cultivar,PercentBurBurial) %>% group_by(Cultivar) %>%
  summarise_all(funs(mean,sd))

summary(df_work)


```
Cluster 

```{r}
clusNo <- 7 # selected from sensitivity cluster analysis below

myClus <- kmeans(df_work[,c("mean")], centers = clusNo)

myClus_res.within.ss <- sum(myClus$withinss)

clusterClass <- myClus$cluster

dftemp1 <- cbind(df_work, clusterNo = factor(clusterClass))

summary(dftemp1)

```



```{r, fig.width=12}
theme_set(theme_gray(base_size = 20))
dftemp1 %>%
  
  mutate(Cluster = factor(clusterNo,levels=c(1,2,3,4,5,6,7,8,9,10)))  %>%
  ggplot(aes(x=Cultivar,y=mean)) +
  theme_bw()+
  geom_errorbar(aes(ymin=mean-sd/2.45,ymax=mean+sd/2.45,colour=Cluster),alpha=0.8, width=0.5, linetype=2)+
  geom_point(aes(shape=Cluster, colour=Cluster), size =5) +
  ylab("Burr Burial  (%)") +
  xlab("Sowing date")
  
```


end of this script 