 ---
title: "SeedlingRegeneration_Analysis_16 cv_trial"
author: "CT"
date: "28.12. 2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
Purpose : 
Correlate the hardseed rating with the estimated counts (January, march,may).
Here Cumulative mean populations in each measurement date are used !! no distinction between cut an uncut 

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
library(knitr)
```

Read File 

```{r, echo=FALSE}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
getwd()
file <- read.table("CVTrial2017_Regeneration.txt",header=TRUE)
head(file)
summary(file)
rank <- read.table("CVTrial2017_RankHard.txt",header=TRUE)

```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  #select(-PlotSide)%>%
  mutate(
    #Plot = as.factor(Plot),
    #Block = as.factor(Block),
    Cultivar = as.factor(Cultivar)
    #Treat=as.factor(Treat)
   
  )

str(file)
summary(file)

```




merge dataframes by cultivar 
```{r, fig.height= 5, fig.width=15 , warning=FALSE}

# define merging by 
df_merge <- merge (file, rank, by.x="Cultivar")

df_merge <-df_merge %>%
  mutate (HardseedRank=as.numeric(HardseedRank))%>%
  filter(Cultivar!="Whatawhata")
```



Here plot hard rank against seedling pop 

```{r,fig.height= 5, fig.width=15 , warning=FALSE}

#Create a graph with hard in X and seedling in y 

str(df_merge)
df_merge$Month_f=factor(df_merge$Month, levels=c("January", "March", "May"))
#graph it
 df_merge %>%
   ggplot(aes(x=HardseedRank, y=CumSeedlingPerm2, colour=Cultivar)) + # do percentage here
 
  geom_point(aes(shape= Cultivar), size=5)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14))+
  geom_point()+
    #labs(x="Hours",y="Cummulative Germination Percent(%)")+
  #facet_grid(.~Temp)
  #facet_wrap(.~Temp, ncol=6)

facet_wrap(~Month_f,ncol=3, scales = "free")+
  theme_bw(base_size=16)+
  #scale_x_continuous(breaks = c(1,200,300))+
 # ylim(0, 2000)+
  xlim(0, 6)+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 12))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 12))+
  labs(y="Mean Cumulative Seedlings per m2 ",x="Hardseed Rank ")
 # geom_abline(intercept = 50, slope = 0)


#ggsave("plot_Regeneration.png", width=12, height=6, dpi=400)


```

subset : 
Select only the seven cultivars in January 

```{r}

str(df_merge)
df_merge$Month_f=factor(df_merge$Month, levels=c("January", "March", "May"))%>%
  
  
#graph it
 df_merge %>%
   ggplot(aes(x=HardseedRank, y=CumSeedlingPerm2, colour=Cultivar)) + # do percentage here
 
  geom_point(aes(shape= Cultivar), size=5)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14))+
  geom_point()+
    #labs(x="Hours",y="Cummulative Germination Percent(%)")+
  #facet_grid(.~Temp)
  #facet_wrap(.~Temp, ncol=6)

facet_wrap(~Month_f,ncol=3, scales = "free")+
  theme_bw(base_size=16)+
  #scale_x_continuous(breaks = c(1,200,300))+
 # ylim(0, 2000)+
  xlim(0, 6)+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 12))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 12))+
  labs(y="Mean Cumulative Seedlings per m2 ",x="Hardseed Rank ")
 # geom_abline(intercept = 50, slope = 0)



```







Explore with the cumulative number of seedlings according to date


```{r, fig.height= 5, fig.width=15 , warning=FALSE}

df_merge %>%
   ggplot(aes(x=Date, y=CumSeedlingPerm2, colour=Cultivar)) + # do percentage here
 
  geom_point(aes(shape= Cultivar), size=5)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14))+
  geom_point()+
    #labs(x="Hours",y="Cummulative Germination Percent(%)")+
  #facet_grid(.~Temp)
  #facet_wrap(.~Temp, ncol=6)

#facet_wrap(~Month_f,ncol=3, scales = "free")+
  theme_bw(base_size=16)+
  #scale_x_continuous(breaks = c(1,200,300))+
 # ylim(0, 2000)+
  #xlim(0, 6)+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 12))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 12))+
  labs(y="Mean Cumulative Seedlings per m2 ",x="Date")
 # geom_abline(intercept = 50, slope = 0)




```



Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}
df_seedANOVA <- file %>%
filter(Month=="January")%>%
   select(Cultivar:SeedlingPerm2)
```

subset for anova
```{r}

 
summary(df_seedANOVA)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA 

head(file.subset)
summary(file.subset)

```


Here Analyse the percentage ofseeds overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedlingPerm2 ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

Perform anova in cultivars 



```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```

now do the mean table to write

```{r}


means<-file.subset%>%
  group_by(Treat,Cultivar)%>%
  dplyr::select( SeedlingPerm2)%>%
  summarise_all(funs(mean))

```

now analyse for regeneration in March

Statistical Analisis 
Do ANOVA simple as per D. Saville :each season and variate separately
Select month and variable to analyse

```{r}

str(file)
df_seedANOVA2 <- file %>%
filter(Month=="March")%>%
   select(Cultivar,Plot,Block,Treat, SeedlingPerm2)
```


subset for anova
```{r}

 
summary(df_seedANOVA2)

#-------------------------------------------------
# anova 

file.subset2 <- df_seedANOVA2 

head(file.subset2)
summary(file.subset2)

```


Here Analyse 


```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedlingPerm2 ~ Cultivar*Treat + Block, data = file.subset2)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```


Perform anova in cultivars 


```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


tistics
   MSerror Df     Mean       CV  t.value      LSD
  57883.99 87 600.0483 40.09526 1.987608 239.1003

$parameters
        test p.ajusted   name.t ntr alpha
  Fisher-LSD      none Cultivar  15  0.05

$means
            SeedlingPerm2      std r         LCL       UCL Min  Max    Q25    Q50    Q75
Antas             982.750 337.1578 8  813.680589 1151.8194 252 1358  884.0 1042.0 1200.0
Campeda           370.600 234.3231 8  201.530589  539.6694   0  726  252.0  299.4  568.0
Coolamon          429.750 151.0179 8  260.680589  598.8194 252  568  299.4  457.4  568.0
Denmark           449.500 163.5455 8  280.430589  618.5694 252  726  370.5  410.0  568.0
Karridale         528.500 219.4194 8  359.430589  697.5694 252  884  370.5  568.0  607.5
Leura             177.250 156.1938 8    8.180589  346.3194   0  410    0.0  252.0  252.0
Monti             187.125 219.6851 8   18.055589  356.1944   0  568    0.0  133.5  291.5
MountBarker      1219.750 259.4487 8 1050.680589 1388.8194 726 1516 1160.5 1200.0 1397.5
Napier            686.500 184.0644 8  517.430589  855.5694 410  884  568.0  647.0  884.0
Narrikup          923.500 163.5455 8  754.430589 1092.5694 726 1200  844.5  884.0 1042.0
Rosabrook         350.750 187.6621 8  181.680589  519.8194 252  726  252.0  252.0  331.0
SeatonPark        587.750 320.8995 8  418.680589  756.8194 252 1042  252.0  568.0  884.0
Trikkala          370.500 163.5455 8  201.430589  539.5694 252  568  252.0  252.0  568.0
Whatawhata        516.750 332.9366 8  347.680589  685.8194   0 1042  252.0  568.0  726.0
Woogenellup      1219.750 259.4487 8 1050.680589 1388.8194 884 1516 1002.5 1279.0 1397.5

$comparison
NULL

$groups
            SeedlingPerm2 groups
MountBarker      1219.750      a
Woogenellup      1219.750      a
Antas             982.750     ab
Narrikup          923.500     bc
Napier            686.500     cd
SeatonPark        587.750     de
Karridale         528.500     de
Whatawhata        516.750     de
Denmark           449.500     de
Coolamon          429.750      e
Campeda           370.600     ef
Trikkala          370.500     ef
Rosabrook         350.750     ef
Monti             187.125      f
Leura             177.250      f

attr(,"class")
[1] "group"
Show in New WindowClear OutputExpand/Collapse Output
$statistics

Now perform for June 


```{r}
str(file)
df_seedANOVA3 <- file %>%
filter(Month=="June")
  #dplyr:: select_(Cultivar,Plot,Block,Treat, SeedlingPerm2)


summary(df_seedANOVA3)

#-------------------------------------------------
# anova 

file.subset3 <- df_seedANOVA3 

head(file.subset3)
summary(file.subset3)

```

Run ANova

```{r}
#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedlingPerm2 ~ Cultivar*Treat + Block, data = file.subset3)
summary(my.anova)
```



```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar", "Treat"), alpha= 0.05, p.adj="none")) 
```



end of this script 