---
title: "Germination Seeds different Temperatures  4CV"
author: "CT"
date: " September  , 2015"
output: html_document
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)  
library(agricolae)
library(knitr)
library (lubridate)

```


```{r loadFile}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\Gitsubclover")
getwd()

#create file
df_seed <- read.table("SeedGerm.txt",header=TRUE)
head(df_seed)
# Jeito 1 de trocar formato (usando base R)
df_seed$Date <- dmy(df_seed$Date)

# jeito 2 de trocar formato (usando dplyr)
df_seed <- df_seed %>%
  mutate(Temp = as.factor(Temp), rep = as.factor(rep))%>%
#  mutate(PropSoft =round((Soft/SeedNumber)*100),2)
  mutate(PropGerm = round(CountedGerm/50*100,digits=2))

summary(df_seed) # explore values
str(df_seed) # check formats
head(df_seed) # see to rows
tail(df_seed)

```

```{r}
#graph it
 df_seed %>%
  group_by(Temp,Cv,rep) %>% # need to keep level in which cumulation occurs
  arrange(HoursofTest) %>% # need to tell which factor to accumulate within
  mutate(PropGerm_cum = cumsum(CountedGerm)) %>%
  #mutate(PropGermCum=PropGerm_cum/max(CountedGerm))%>%
  group_by(Temp,Cv,HoursofTest) %>%
  dplyr::select(Temp,Cv,HoursofTest,PropGerm_cum) %>%
  summarise_each(funs(mean)) %>%
ggplot(aes(x=HoursofTest, y=PropGerm_cum/50*100, colour=factor(Cv))) + # do percentage here
  geom_point()+
  geom_line()+
  labs(x="Hours",y="Cummulative Germination Percnet(%)")+
  facet_grid(.~Temp)

head(df_seed)

```


```{rCreate }
df_seed <- df_seed %>%
  group_by(Temp,Cv,rep) %>% # need to keep level in which cumulation occurs
  arrange(HoursofTest) %>% # need to tell which factor to accumulate within
  mutate(PropGerm_cum = cumsum(CountedGerm)) %>%
  #mutate(PropGermCum=PropGerm_cum/max(CountedGerm))%>%
  group_by(Temp,Cv,HoursofTest) %>%
  
  #parei aqui - fix me stdev and sE 
  head(df_seed)
  dplyr::select(PropGerm_cum)%>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x=HoursofTest, y=mean, colour=factor(Cv), shape=factor(Cv))) +
  geom_point() +
  geom_line() +
 facet_grid(.~Temp) +
  labs(x="Sowing Date",y="Maximum Percentage of Hardseeds") +
  geom_errorbar(aes(ymin=mean-sd/2,
                    ymax=mean+sd/2))


