---
title: "Hardseeds method check_rub and unrub seeds "
author: "CT"
date: "16 June, 2016"
output: html_document
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```


```{r loadFile}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\Gitsubclover")
getwd()

#create file
df_rub <- read.table("RubTest.txt",header=TRUE)
head(df_rub)


# jeito 2 de trocar formato (usando dplyr)
df_rub <- df_rub %>%
  mutate(CV = as.factor(CV), Treat = as.factor(Treat))%>%
#  mutate(PropSoft =round((Soft/Seeds)*100),2)
  mutate(PropSoft = round(Softseeds/Seeds*100,digits=2))

summary(df_rub) # explore values
str(df_rub) # check formats
head(df_rub) # see to rows
tail(df_rub)

```


```{r TransformPercentSoft}



#data transformation

df_rub$transf_sqr <- sqrt(df_rub$PropSoft)
df_rub$transf_log <- log(df_rub$PropSoft)
df_rub$transf_acos <- acos(df_rub$PropSoft/100)

head(df_rub)

file <- df_rub

x <- c("transf_sqr", "transf_log", "transf_acos")
colsSelec <- match(x,colnames(file))

file %>%
  tidyr::gather("transformation","value",colsSelec) %>%
  ggplot(aes(value)) + 
  geom_histogram() +
  facet_grid(.~transformation, scales="free")

head(file)

#normality test
shapiro.test(file$transf_acos)

#QQplot
var<-file$transf_acos
qqnorm(var)
qqline(var, col = 2)
qqplot(var, rt(300))

#-------------------------------------------------
# ANOVA (selecing by hand FIXME: do loop)
# file.subset <- file %>% subset(SowTreat == "S2" & round==1)
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_acos ~ CV*Treat + Rep, data = file.subset)

summary(my.anova)
TukeyHSD(my.anova)

#Means separation 
(LSD.test(my.anova, "SowTreat", alpha= 0.05, p.adj="none")) 

```




g1 <- df_rub %>%
  group_by(CV,Treat,Rep) %>%
  summarise_each(funs(mean)) 
head(g1)
# create graph 
g1 %>%
  ggplot(aes(x=Treat,y=PropSoft,colour=factor(CV)))+
  geom_point() 
  #geom_line() +
  #facet_grid(SowTreat~Depth)



```



Graph date Propsoft  

```{r Graph}
df_rub %>%
  group_by(CV,Treat,Rep) %>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x=CV, y=(PropSoft_mean))) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=PropSoft_mean-PropSoft_mean_sd/2,
                    ymax=PropSoft_mean+PropSoft_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
  facet_grid(CV~.) +
theme(axis.text.x=element_text(angle = +90, hjust = 0))
head(df_rub)



  
  
```


```{r}

```




Calculate the mean and error bars for each cultivar 

```{r}
  

```



