---
title: "Trifoliates Iversen "
author: "CT"
date: "04.07.2018" 
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Analysis of trifoliates expansion for Iversen using the data from first trifo event (not from sowing) 
- Calculate stat for the days to reach 5 trifoliates from emergence 
- Run ANOVA for variable "Number of days to reach 5 Trifoliates " and thermal time to 5 trifoliate leaves  
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```

Read document generated in script "3" 5Trifo_rate

```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifoCountsI2")
getwd()
#create file

##Path "C:/GitHubRepos/SubCloverPhD/SubClover/TrifoCountsI2/DaysTT5TFromEmergence.txt"

#df_trifo <- read.table("DaysTT5TFromEmergence.txt",header=TRUE)
df_trifo <- read.table("TT5Trifo_FromFirstTrifo.txt",header=TRUE)

head(df_trifo)


```
Define formats and calculate the number of trifoliates considering the sub samples (S1-S10)

```{r loadFile}


# define factors for the ones that "look like" values
df_trifo$Plot <- as.factor(df_trifo$Plot)
df_trifo$Block <- as.factor(df_trifo$Block)
df_trifo$Cultivar <- as.factor(df_trifo$Cultivar)
df_trifo$SowTreat <- as.factor(df_trifo$SowTreat)

 #df_trifo <- df_trifo %>%
 # mutate(SowingDate = ymd(SowingDate)) 

str(df_trifo)



```

## Check average values to see if TT5TrifoFrom1Trifo is lower than SummTT5Trifo

```{r}

df_mean <-df_trifo %>%
  dplyr:: select(Plot:Cultivar,DAS5T, SummTT5Trifo,DAS5TrifoFromFirstTrifo,TT5TrifoFrom1Trifo )%>%

  #group_by(Cultivar,SowTreat) %>%
  group_by(SowTreat) %>%
  # dplyr::select(SummTT5Trifo)%>%
  # summarise_all(funs(mean,sd))%>%
  #   mutate(SE=sd/1.73)
  
  #summarise_at(c( "SummTT5Trifo", "TT5TFromEmerg"), mean, na.rm = TRUE)
  summarise_at(c( "DAS5TrifoFromFirstTrifo", "TT5TrifoFrom1Trifo"), mean, na.rm = TRUE)


```



##Run stats for the TT5TrifoFrom1Trifo to reach 5 trifoliates 
##general use Sow Treat as Factor 

```{r}
 
  file <- df_trifo


file.subs <- file 

head(file.subs)
summary(file.subs)

#ANOVA

#my.anova <- aov(DAS5TFromEmerg ~ SowTreat + Block, data = file.subs)
my.anova <- aov(TT5TrifoFrom1Trifo ~ Cultivar + Block, data = file.subs)
#my.anova <- aov(DAS5TFromEmerg ~ Cultivar*SowTreat+ Block, data = file.subs)

summary(my.anova)

```


```{r}
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))

```



## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(df_trifo$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```
## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_trifo %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(TT5TrifoFrom1Trifo ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```

Then run for TT 
STOPPED HERE 

## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(df_trifo$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```
## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_trifo %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(TT5TFromEmerg ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```




