---
title: "Trifoliates Iversen "
author: "CT"
date: "04.07.2018" 
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Add Photoperiod at First trifoliat and Emergence for each plot 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```

Read document generated in script "3" 5Trifo_rate

```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifoCountsI2")
getwd()
#create file

##Path "C:/GitHubRepos/SubCloverPhD/SubClover/TrifoCountsI2/DaysTT5TFromEmergence.txt"

df_trifo <- read.table("DaysTT1TFromEmergence.txt",header=TRUE)


head(df_trifo)


```
Define formats and calculate the number of trifoliates considering the sub samples (S1-S10)

```{r loadFile}


# define factors for the ones that "look like" values
df_trifo$Plot <- as.factor(df_trifo$Plot)
df_trifo$Block <- as.factor(df_trifo$Block)
df_trifo$Cultivar <- as.factor(df_trifo$Cultivar)
df_trifo$SowTreat <- as.factor(df_trifo$SowTreat)

 #df_trifo <- df_trifo %>%
 # mutate(SowingDate = ymd(SowingDate)) 

str(df_trifo)



```

Bring the photoperiod data 

```{r}

df_Photo <- read.table("Photoperiod.txt",header=TRUE)

# rename date column for merge
df_Photo <- df_Photo %>%
mutate(SowingDate = Date)
head(df_Photo)

# convert to date format
df_Photo <- df_Photo %>%
mutate(Date=dmy(Date))

```

Then add the photoperiod at frist trifoliate


```{r}

str(df_trifo)
  
  df_insertion<-df_trifo%>%
  select(Plot,Date50FirstTrif)%>%
  mutate(Date=ymd(Date50FirstTrif))
  
  str(df_insertion)
  str(df_Photo)
  
  # force formats of dates
#df_insertion$Date <- round(df_insertion$Date50FirstTrif,0)
#df_Photo$Date <- round(df_Photo$Date,0)
  
Merged<-merge(df_insertion,df_Photo, by="Date")
##Here you have Pp at First Trifoliate for each plot
Merged1<-Merged%>%
  mutate(Pp1Trifo=Pp)%>%
  select(Plot,Pp1Trifo)

write.table(Merged1, "PpAtFirstTrifo.txt")
```


## Now include the photoperiod at emergence (repeat process ) 

```{r}

dfEmergenceDate <- read.table("DASSeedEmer.txt",header=TRUE)


str(dfEmergenceDate)

#adjust format
df_insertionEmerg<-dfEmergenceDate%>%
  select(Plot,Date50SeedEm)%>%
  mutate(Date=dmy(Date50SeedEm))%>%
  select(Plot,Date)
##merge with Photoperiod by date 

Merged2<-merge(df_insertionEmerg,df_Photo, by="Date")
##Here you have Pp at First Trifoliate for each plot
Merged2<-Merged2%>%
  mutate(PpEmerg=Pp)%>%
  select(Plot,PpEmerg)


```




Now combine the PpEmerg and PP1trifo per plot and save 


```{r}

MergedAll<-merge(Merged1,Merged2, by="Plot")

write.table(MergedAll,"PhotoperiodEmergAnd1trifo.txt")

```

Use the data to plot phyllochron in Y and photoperiod in x 