---
title: "Trifoliates Iversen "
author: "CT"
date: "31.08.2016"
output: html_document
---

Purpose:

-Analysis of trifoliates expansion for Iversen from previous script (use file Perc_Trifo)
- Calculate the 50% percent based on maximum number of leaves
- Calculate rate of leaf appearance (1/Days) 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
```



```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifoCountsI2")
getwd()
#create file
df_trif <- read.table("Perc_Trifo.txt",header=TRUE)
str(df_trif)


```

Select only columns of interest 
```{r}

df_trif <-df_trif %>%
dplyr::select (-s1:-s10)
str(df_trif)

```



Define formats 

```{r loadFile}


# define factors for the ones that "look like" values
df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Cultivar <- as.factor(df_trif$Cultivar)
df_trif$SowTreat <- as.factor(df_trif$SowTreat)

 df_trif <- df_trif %>%
  mutate(SowingDate = dmy(SowingDate), 
         ReadingDate = dmy(ReadingDate),
         DAS = as.numeric(DAS))
         

str(df_trif)


```

Calculate the 50 percent of leaves  based on maximum number of leaves attained 

```{r, fig.height=5, fig.width=10}


df_50_Perc <- df_trif %>%

  group_by(Plot, Block,Cultivar,SowTreat, PercentTrifo, ReadingDate) %>%
  summarise(av_Perc = mean(PercentTrifo), 
            #av_TT = mean(TT_to_emerg),
            av_DAS = mean(DAS)
            )

str(df_50_Perc)
summary(df_50_Perc)
head(df_50_Perc)


```

Loop, apply funciton approx and try catch to get DAS to 50% 
```{r}

#sow <- unique(df_50_Perc$SowTreat)
#sowd <- unique(df_50_Perc$SowingDate)
plots <- unique(df_50_Perc$Plot)
 

# create empty df
# df_tt_50p_emerg <- data.frame(Plot = NULL,
#                               Block = NULL,
#                              SowingD = NULL,
#                              Cultivar = NULL, 
#                              SowTreat = NULL,
#                              PercEmerg = NULL, 
#                              TT50Em = NULL)

#loop trough each combination of factor levels

for(p in 1:length(plots)) {
#  for(j in 1:length(var)){
 #   for(k in 1:length(sow)){
      
      # clean value holders
      DAS_50p_emerg <- 0
      #tt_50p_emerg <- 0
      
      #FIX ME Partially set 
    
     # print(paste0(cv[i]," ",var[j]," ", sow[k]))
      # filter for each combination

  df_sub <- df_50_Perc %>%
    # subset(Cultivar == as.character(cv[i]) &
    # Plot == as.character(var[j]) &
    #   Block == as.character(var[b]) &
    # SowTreat == as.character(sow[k])) %>%
    subset(Plot == plots[p]) %>%
    arrange(PercentTrifo)
  
  df_sub
  head(df_sub)
  # create percentage with maximum value recorded 
  # to avoid crossing the 50% line twice
  
  df_sub$av_Perc_max <- 0 # create new col
  
  for(z in 1:nrow(df_sub)) {
    
    df_sub$av_Perc_max[z] <- max(df_sub$av_Perc[z],
                                 df_sub$av_Perc_max[z-1])
    
  }
  
  df_sub
  head(df_sub)
  tail(df_sub)

  # Interpolate 
  y_ref <- 50 # y value where we want to find x by interpolation
  
  # interpolate
  #find DAS at 50 Pecent Emergence 

  tryCatch(  
  DAS_50p_emerg <- approx(df_sub$PercentTrifo, 
  df_sub$av_DAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  DAS_50p_emerg <- NA
  }
)
  #find TT at 50 Pecent Emergence
#   tryCatch(  
#   tt_50p_emerg <- approx(df_sub$av_Perc, 
#   df_sub$av_TT , xout = y_ref, rule = 1)$y,
#   error = function(e) 
#   {
#   tt_50p_emerg <- NA
#   }
# )

  df_temp <- NULL 
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             PercEmerg = df_sub$PercentTrifo[1], 
                             SowTreat = df_sub$SowTreat[1],
                             Plot = df_sub$Plot[1],
                             Block = df_sub$Block[1],
                             DAS50E = DAS_50p_emerg)
                             #TT50E = tt_50p_emerg)
  print(p)
  
  if(p == 1) {
    df_tt_50p_emerg <- df_temp
  } else {
   df_tt_50p_emerg <- rbind(df_tt_50p_emerg,df_temp) 
  }                     
  
#    } 
  } # end plot loop


head(df_tt_50p_emerg)



summary(df_tt_50p_emerg)



```

Include dates of sowing again in dataframe 
```{r}
sdLookup <- data.frame (
  SowTreat = c("S1","S2","S3","S4","S5","S6","S7","S8"),
  SowingDate = c("24/06/2015", 
                 "28/07/2015" ,
                 "15/09/2015" ,
                 "5/11/2015" ,
                 "15/12/2015" ,
                 "17/02/2016" ,
                 "15/03/2016",
                 "4/05/2016"))

sdLookup$SowingDate <- dmy(sdLookup$SowingDate)

df_tt_50p_emerg <- merge(df_tt_50p_emerg, sdLookup, by="SowTreat")
summary(df_tt_50p_emerg)


write.table(df_tt_50p_emerg,"df_tt_50p_emergTrifo.txt")
```




Calculate RAte (1/days to 50%) 


```{r}

#try 1/DAS50% = Rate

df_RateTrifo <- df_tt_50p_emerg %>%
  mutate(Rate=1/DAS50E)

  summary(df_RateTrifo)
  
  write.table(df_RateTrifo,"RateTrifo.txt")

```



Graph rate and SowTreat

```{r}
#Graph 

  df_RateTrifo %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 50% leaf emergence  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

```




End of this script Calc 3. 
Move to script 4 to include temperatures  
