---
title: "Trifoliates Iversen "
author: "CT"
date: "31.08.2016"
output: html_document
---

Purpose:

-Analysis of trifoliates expansion for Iversen
- Calculate percent based on maximum number of leaves
- Calculate percent leaves in each sowing date 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
```



```{r}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\TrifoCountsI2")
getwd()
#create file
df_trifo <- read.table("TrifoCountall.txt",header=TRUE)
head(df_trifo)


```
Define formats and calculate the number of trifoliates considering the sub samples (S1-S10)

```{r loadFile}


# define factors for the ones that "look like" values
df_trifo$Plot <- as.factor(df_trifo$Plot)
df_trifo$Block <- as.factor(df_trifo$Block)
df_trifo$Cultivar <- as.factor(df_trifo$Cultivar)
df_trifo$SowTreat <- as.factor(df_trifo$SowTreat)

 df_trifo <- df_trifo %>%
  mutate(SowingDate = dmy(SowingDate), 
         ReadingDate = dmy(ReadingDate),
         Trifo = (s1+s2+s3+s4+s5+s6+s7+s8+s9+s10)/10)

str(df_trifo)
head(df_trifo)
tail(df_trifo)


df_trifo %>% filter(Plot ==1) %>% summary()



```

Calculate the percent of leaves  based on maximum number of leaves attained 

```{r, fig.height=5, fig.width=10}


df_T <- df_trifo %>%
group_by(Plot) %>%
mutate(PercentTrifo=Trifo/round(max(Trifo)*1,digits=2))%>%
  mutate (PercentTrifo= PercentTrifo*100)

#check 
str(df_T)

```

Graph to see if makes sense
```{r}
#Graph         
  df_T %>%  group_by(Cultivar, SowTreat, DAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=PercentTrifo)) + 
  geom_point(aes(colour=Cultivar, shape=Cultivar)) +
  geom_line(aes(colour=Cultivar)) +
  #facet_grid (SowTreat~., scales = "free")+
  facet_wrap (~SowTreat,ncol=4, scales = "free")+
  labs(y="Percent  trifoliates",x="Days after sowing")+
    #geom_abline(intercept = 6, slope = 0)
   geom_abline(intercept = 50, slope = 0)



```

compare sowing dates 


```{r}
#Graph 

  df_T %>%  group_by(Cultivar, SowTreat, DAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=PercentTrifo)) + 
  geom_point(aes(shape=SowTreat,colour=SowTreat)) +
  geom_line(aes(colour=SowTreat)) +
  #facet_grid (SowTreat~., scales = "free")+
  theme_bw()+
  labs(y="Percente trifoliates",x="Days after sowing")+
    geom_abline(intercept = 50, slope = 0)

```
Prepare dataframe to calculate rate (1/Days to 50 %) in the next script.


```{r}
write.table(df_T, "Perc_Trifo.txt")


```


End of this script Calc 2. 
Move to script 3 to calculate rate of leaf appearance 
