---
title: "Trifoliates Iversen "
author: "CT"
date: "17.08.2017"
output: html_document
---

Purpose:

-Combine the rate of trifoliate appearance with Mean Air Temp during trifo appearance   
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
```

Get data from Emergence Folder, Daily Mean Air temperature and dates to combine in dataframe 


```{r}

setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\TrifoCountsI2")
getwd()
#create file

df_trif <- read.table("RateTrifo.txt",header=TRUE)
#adjust formats 
df_trif$SowingDate <- ymd(df_trif$SowingDate )
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$DAS5T <- as.numeric(df_trif$DAS5T)

```

Create df_MD to workout dates to % trifoliates 
```{r}

  df_MD <- df_trif %>%
  mutate(Date50E=SowingDate+DAS50E) %>%
  group_by(Plot, DAS50E) %>% 
  dplyr::filter(row_number() == 1)

str(df_MD)

H <-df_MD %>%
 dplyr:: select (Plot, Date50E)

#save and store table 
write.table(H, "DateTo5Trifos.txt")

```

Bring data from emergence foldeer 

```{r}
df_S <- read.table("DASSeedEmer.txt",header=TRUE)

#change formats 
df_S <- df_S %>%
  mutate(Plot=as.factor(Plot),
         DAS50SeedEm= as.numeric(DAS50SeedEm),
         Date50SeedEm= dmy(Date50SeedEm))

         
str(df_S)


```



```{r}


#create file
df_A <- read.table("AirTemp.txt",header=TRUE)

#adjust formats
df_A %>%
  mutate(Date=dmy(Date))

str(df_A)

df_B <- df_A %>%
  mutate(SumAir = cumsum(AirTt)) %>%
  mutate(Date=dmy(Date))%>%
  dplyr::select(-AirTt)


summary(df_B)
summary (df_S)


#then save table df_B with the ACcumulated Air Temperature and merge 

write.table(df_B, "AccumAir.txt")

df1 <- merge(df_S,df_B, by.x="Date50SeedEm",by.y="Date")%>%
mutate(AirTempAcc_emerg = SumAir) %>%
  dplyr::select(-SumAir)

str(df1)

write.table(df1,"AccAirEmerg.txt")
```

Re start from here : Bring the calculated Mean AirTrifo file and merge 

```{r}

#create file
df_trif <- read.table("RateTrifo.txt",header=TRUE)
df_MeanAir <- read.table("MeanAirTrifo.txt",header=TRUE)

str(df_trif)
str(df_MeanAir)


```

adjust formats and Calculate the date to 50%  
```{r}

#adjust formats 
df_trif$SowingDate <- ymd(df_trif$SowingDate )
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$DAS5T <- as.numeric(df_trif$DAS5T)

df_MeanAir$Plot <- as.factor(df_MeanAir$Plot)



```


```{r}


dfok <- merge(df_trif,df_MeanAir, by="Plot")

str(dfok)
```

Then graph results 

```{r}
dfok %>%
  group_by(MeanAirTempTrifo, SowingDate, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=MeanAirTempTrifo, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Mean Air temperature ",y="1/ Days to 5 trifoliates  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

# then merge the dataframes to find out the mean temperature 


```




```{r}


  
  write.table(dfok,"df_DAS5Trifo_MeanAirT.txt")

```



Graph rate and SowTreat

```{r}
#Graph 

  df_RateTrifo %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 50% leaf emergence  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

```




End of this script Calc 3. 
Move to script 4 to include temperatures  
