---
title: "Emergence seedlings Poukawa"
author: "CT"
date: " March,  2016"
output: html_document
---

Purpose:

-Analysis of plant population fo Poukawa 

-calculate the final plant population, the percentage of emergence and make a preliminary ANOVA

-Combine with thermal time based on Air temperature  



```{r loadLibraries, warning=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(mosaic)
library(lattice)
```
In this step re3ad file and change formats 
Calculate the seedling population (seedlings per 1m2 )

```{r loadFile, fig.height=5, fig.width= 10}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergencePoukawa")
getwd()

#create file
df_emerg <- read.table("PlantPopPok.txt",header=TRUE)
head(df_emerg)

# define factors for the ones that "look like" values
df_emerg$Plot <- as.factor(df_emerg$Plot)
df_emerg$Block <- as.factor(df_emerg$Block)

 df_emerg <- df_emerg %>%
  mutate(SowingDate = dmy(SowingDate), 
         ReadingDate = dmy(ReadingDate),
         PlantPop = (Sub1+Sub2+Sub3)/3/0.01)

str(df_emerg)
# head(df_emerg)
# tail(df_emerg)


df_emerg %>% filter(Plot ==1) %>% summary()



```

DAta visualisation: Graph the seedling population per 1m2

```{r,fig.height=5, fig.width=10}

#Graph         
 
  #mutate (SowTreat= factor(SowTreat, levels=c("S2","S3"),labels=c( "March", "May")))%>%
 
   df_emerg %>% 
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7","S8"),labels=c("February", "March", "May", "July", "August","October","November","January")))%>%
  group_by(Cultivar, SowTreat, DAS) %>%
  #filter(Cultivar =="Monti"|Cultivar== "Antas") %>%
  #filter(SowTreat=="March"|SowTreat=="May") %>%
    #dplyr::select(-SowingDate, - ReadingDate) %>%
  summarise_all(funs(mean,sd)) %>%
  ggplot(aes(x=DAS, y=PlantPop_mean)) + 
  geom_point(aes(colour=Cultivar)) +
  geom_line(aes(colour=Cultivar)) +
  # facet_grid (SowTreat~., scales = "free")+
    facet_wrap (~SowTreat,ncol=4, scales = "free")+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 0, hjust = 1))+
                  #geom_errorbar(aes(ymin=PlantPop_mean-PlantPop_sd/1.73,
                    #ymax=PlantPop_mean+PlantPop_sd/1.73))+
  labs(y="Number of seedlings per m2",x="Days after sowing") +
  ylim(0,2200)
  #+geom_abline(intercept = 50, slope = 0)

```

Now Calculate the Percentage of Emergence in relation to the final emergence. Need to calculate the final population first and then estimate the percentage. all  plots have to end up with 100% !! 
 

```{r CalculatePercentageEmergence, fig.height=5, fig.width= 10 }

df_FinalPop<- df_emerg %>%
#not using max pop due to mortality 
  #group_by(Plot) %>%
  #mutate(PercEmerg = round(PlantPop/max(PlantPop)*100,digits=2))

group_by(Plot) %>%
  filter(DAS==max(DAS))%>%
  dplyr::select(PlantPop)%>%
  summarise_all(funs(max))%>%
  mutate(FinalPop=round((PlantPop)*1,digits=2))%>%
  dplyr::select(-PlantPop)


#Now merge the two dataframes to calculate the percentage of emergence relative to the final pop 

df_merged1 <- merge(df_FinalPop,df_emerg,by="Plot")%>%
  mutate(PercFinalEmerg=PlantPop/FinalPop*100)


```

```{r}


```




Graph the percentage of emergence versus days after sowing 

```{r, fig.height=5, fig.width=10}

 #Graph         
  df_merged1 %>%  
   #mutate (SowTreat= factor(SowTreat, levels=c("S2","S3"),labels=c( "March", "May")))%>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7","S8"),labels=c("February", "March", "May", "July", "August","October","November","January")))%>%
  group_by(Cultivar, SowTreat, DAS) %>%
  #filter(Cultivar =="Monti"|Cultivar== "Antas") %>%
  #filter(SowTreat=="March"|SowTreat=="May") %>%
#  filter(Cultivar =="Monti") %>%
  dplyr::select(-SowingDate, - ReadingDate) %>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x=DAS, y=PercFinalEmerg_mean)) + 
  geom_point(aes(colour=Cultivar)) +
  geom_line(aes(colour=Cultivar)) +
  facet_wrap (~SowTreat,ncol=4, scales = "free")+
  labs(y="Percentage  of Seedling emergence (%)",x="Days after sowing") +
    theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=PercFinalEmerg_mean-PercFinalEmerg_sd/1.73,
                    ymax=PercFinalEmerg_mean+PercFinalEmerg_sd/1.73))+
  ylim(0,200)+
  geom_abline(intercept = 50, slope = 0)
```

 





Do not have soil Temperature for Poukawa yet here. 
The soil estimated data is included furhter on in script 6 (EmergSoilT).
Below used Air Temp to continue  this script as it generated the dataframe for script 3 (50% emergence) 


```{r SoilTemp}
# df_CumTT.txt is generated in folder PokWeather... basically here is the same as per TT because do not have soil Temp
#Remember to format dates as ymd 

df_SoilTT <- read.table("df_CumTTPo.txt",header=TRUE)
head(df_SoilTT)

# convert to date format

df_SoilTT <- as.data.frame(df_SoilTT) %>%
 mutate(Date=ymd(Date))


# check
head(df_SoilTT)


```

Merge the dataframes 

```{r}

# Merge Tt at measurement date
df_emerg_perc_TT <- NULL
df_emerg_perc_TT <- merge(df_merged1,df_SoilTT,by.x="ReadingDate",by.y="Date")
df_emerg_perc_TT <- merge(df_emerg_perc_TT,df_SoilTT,by.x="SowingDate",by.y="Date")

df_emerg_perc_TT$TT_to_emerg <- df_emerg_perc_TT$SumTTday.x-df_emerg_perc_TT$SumTTday.y
summary(df_emerg_perc_TT)

#Remove extra columns 
df <-df_emerg_perc_TT %>%
  dplyr::select(SowingDate:DAS, PlantPop:PercFinalEmerg,Pp.x,TT_to_emerg)

summary(df)

#save as table 
write.table(df, "df_emerg_perc_Po.txt")
head(df_emerg_perc_TT )




```

```{r}
# graph emerg x tt
df_emerg_perc_TT %>%
  group_by(Cultivar, SowTreat, TT_to_emerg) %>%
  #dplyr::select(-SowingDate, - ReadingDate) %>%
#  filter(Cultivar =="Narrikup") %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=TT_to_emerg, y=PercEmerg,colour=Cultivar)) + 
  geom_point() +
  geom_line() +
  #facet_grid (Cultivar~., scales = "free")+
  geom_abline(intercept = 50, slope = 0) +
  facet_wrap (~SowTreat,ncol=4, scales = "free")+
  xlab("Thermal-time from sowing (AirTemp") +
  ylab("Percentage emergence")
```


End of this script ...continue in Pok_Calc2