---
title: "Emergence seedlings Poukawa"
author: "CT"
date: "07.08.2017"
output:
  word_document: default
 
---

Purpose:

-Analysis of DAS50 Pokawa site dataset 
 

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(mosaic)
library(lattice)
```

Read dataframe created in previous script (EmergencePok_Calc3)
Change formats and check the data frame 
```{r loadFile}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\EmergencePoukawa")
getwd()

#create file
df_emerg <- read.table("df_tt_50p_emergPo.txt",header=TRUE)

# define factors for the ones that "look like" values
df_emerg$Plot <- as.factor(df_emerg$Plot)
df_emerg$Block <- as.factor(df_emerg$Block)


str(df_emerg)
head(df_emerg)
tail(df_emerg)


df_emerg %>% filter(Plot ==1) %>% summary()

str(df_emerg)
```


```{r, fig.height= 7, fig.width= 10}
# Graph it 

# 
# #Graph         
#   df_emerg %>%  group_by(Cultivar, SowTreat, DAS) %>%
#   #filter(SowTreat =="S2"& SowTreat =="S4")%>%
#   #dplyr::select(-SowingDate, - ReadingDate) %>%
#   summarise_each(funs(mean)) %>%
#   ggplot(aes(x=DAS, y=PlantPop)) + 
#   geom_point(aes(colour=Cultivar,shape=Cultivar)) +
#   geom_line(aes(colour=Cultivar)) +
#   #add error bar
#   geom_errorbar(aes(x=20,ymin=200,ymax=300,width=0.2))+
#   facet_wrap(~SowTreat,ncol=4, scales = "free")+
#   theme_bw()+
#   ylim(0, 2200)+
#   labs(y="Number of seedlings per m2",x="Days after sowing") +
#   geom_abline(intercept = 1000, slope = 0)

```

Here only change dataframe name and check


```{r ANOVA DAS 50% Emerg}

#compare DAS 50% emerg in eavh Sowing dates and cultivars

df_emerg_perc3 <- df_emerg


head(df_emerg_perc3)
summary (df_emerg_perc3)

write.table(df_emerg_perc3, "df_emerg_perc3.txt")
str(df_emerg_perc3)
```

then select each sowing date individually for statistics; here starting with S1  


```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S1") 
summary (df_emerg_S1)  
  
```


Run ANOVA pure numbers for DAS50Emergence
Repeat the process for all sowing dates 
Write in Chapter 4 

```{r}
#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$DAS50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#To get means select the factor : SowTreat or Cultivar
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )


```

S2
 
```{r}

df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S2") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$DAS50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )

```

S3

```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S3") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$DAS50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )


```
S4


```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S4") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$DAS50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )



```

S5


```{r}

df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S5") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$DAS50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )


```

S6

```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S6") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$DAS50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )


```


S7 

```{r}

df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S7") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$DAS50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )

```
S8

```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S8") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$DAS50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )

```
End of this script. 
Continue with ANOVA for TT50 in the next script. 

