---
title: "Emergence seedlings Poukawa"
author: "CT"
date: "07.08.2017"
output:
  word_document: default
 
---

Purpose:

-Statistical analysis of thermal time for 50% emergence for  Pokawa site  
 

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(mosaic)
library(lattice)
```

Read files and change formats
Check data 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergencePoukawa")
getwd()

#create file
df_emerg <- read.table("df_tt_50p_emergPo.txt",header=TRUE)

# define factors for the ones that "look like" values
df_emerg$Plot <- as.factor(df_emerg$Plot)
df_emerg$Block <- as.factor(df_emerg$Block)


str(df_emerg)
head(df_emerg)
tail(df_emerg)


df_emerg %>% filter(Plot ==1) %>% summary()

str(df_emerg)
```

Here only change dataframe name to match the script below

```{r ANOVA TTAS 50% Emerg}

#compare DAS 50% emerg in eavh Sowing dates and cultivars

df_emerg_perc3 <- df_emerg


head(df_emerg_perc3)
summary (df_emerg_perc3)

#write.table(df_emerg_perc3, "df_emerg_perc3.txt")
str(df_emerg_perc3)
```

Then select each sowing date individually for statistical tests; here starting with S1  

Repeat the process for each sowing date 

```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S1") 
summary (df_emerg_S1)  
  
```



Run ANOVA pure numbers for TTAS50Emergence 

```{r}
#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$TT50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#To get means select the factor : SowTreat or Cultivar
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )


```

S2
 
```{r}

df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S2") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$TT50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )

```

S3

```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S3") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$TT50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )


```
S4


```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S4") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$TT50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )



```

S5


```{r}

df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S5") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$TT50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )


```

S6

```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S6") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$TT50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )


```


S7 

```{r}

df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S7") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$TT50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )

```
S8

```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S8") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$TT50E)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )

```

End of this script. 
Further analysis in script 6. 