
---
title: "ThermalTime calculation for Antas with base temperature zero and TB emergence"
author: "CT"
date: "Friday, January 01, 2016"
output: html_document
---

This script does this:

- get the dataframe with sowing dates and date to 50% Emergence  
- get the dataframe with mean soil  temperature estimated for Poukawa
- merge the two dataframes to calculate the thermal time for Antas using the emergence Tb and assumed cardinal temps. 

```{r}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
```



```{r, load file}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergencePoukawa")
getwd()

#create file
df_emerg4 <- read.table("df_MeanSoilTemp50EmergPo.txt",header=TRUE)
#head(df_emerg4)


df_emerg4$SowingDate <- ymd(df_emerg4$SowingDate )
df_emerg4$Date50E <- as.Date(df_emerg4$Date50E)
df_emerg4$Plot <- as.factor(df_emerg4$Plot)
 str(df_emerg4)
# head(df_emerg4)

D <- df_emerg4 %>%
dplyr::select(Cultivar,SowTreat, Plot, SowingDate, DAS50E, Date50E)

summary(D)

df_emerg4 <- NULL

```

now you can jump direct to the soil TT Accum.chunk. For Pokawa need to use Min and Max as mean because it is estimated soil temperature. 




```{r, fig.height=5, fig.width=8}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergencePoukawa")
getwd()

#create file
df_emerg6 <- read.table("SoilTempPo.txt",header=TRUE)

#Then add columns for Tmax and Tmin repeat values for T mean as do not know actual values for Tmax Tmin 
df_emerg6 <-df_emerg6 %>%
  mutate(Tx=1*(TempSoil10mm), Tm=(1*(TempSoil10mm)))

  # adjust format date 
df_emerg6$Date <- dmy(df_emerg6$Date )

str(df_emerg6)
```

Add the accumulation of of thermal time use reference as  

use the TB for emergence 


'Antas'	-1.85 (±0.02)
'Denmark'	 +1.0 (±0.03)
'Leura'	-1.29 (±0.04)
'Monti'	-1.73 (±0.05)
'Narrikup'	+1.02 (±0.05) 
'Woogenellup'	 +2.2 (±0.01)


use consistent method as per re analysis tb=0, t opt range =15, 22, t max = 35 oC.


For Antas : 
```{r}
#Create Thermal time cardinal temperatures see data above- TT = Topt - Tb ... 21.7 - (-1.85)= 23.55 ! 

#For cardinal temperatures 
tt_card <- data.frame(temp=c(-1.85,15,22,35),TT=c(0,15,15,0))
#for Tb=0
#tt_card <- data.frame(temp=c(0,15,22,35),TT=c(0,15,15,0))
tt_card %>%
  ggplot(aes(x=temp, y=TT))+
  #labs(x="Temperature (degree Celsius)")+
  #labs(y="Thermal Time (oCd)") +
  geom_line()+
  theme_bw()+
  ylim(0,25)+
xlab(expression(Temperature~"("^"o"*"C)"))+
  ylab(expression(Thermal~Time~Antas~"("^"o"*"Cd)"))+
  theme(axis.text.x=element_text(angle = 0, hjust = 0, size= 14))+
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 14))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 14))+
  theme(axis.title.y=element_text(size= 14))

```


#Create and test interpolation function - Test if works 

```{r}

temp_ref  <- 25 # x-axes reference
temp <- tt_card$temp # x-axes
TT <- tt_card$TT # y-axes


int_func <- function(temp,TT,temp_ref){

  # if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   out <- TT[length(TT)] 
   # FIXME: approx functions seems to do that - need param
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
   # else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  
int_func(temp,TT,temp_ref)


```

 
 use the 3x8 hours formula to calculate daily TT 
```{r}

#create REF Jones CA, Ritchie JT, Kiniry JR, Godwin DC (1986) Subroutine structure.In 'CERES-Maize: A simulation model of maize growth anddevelopment'. (Eds CA Jones, JR Kiniry) pp. 49-194. (Texas A&M University Press: Texas, USA

TTfunc <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
 } 
  
  TTav  <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2 + 0.0053 * n^3) * (Tmax-Tmin)) + Tmin # 8-h temperature
    
    TT_tn <- int_func(tt_card$temp, tt_card$T,tn) 
    
    TTsum <- TT_tn + TTsum
    
   # print(TT_tn)
    
    }
 
   TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc(10,24)

```
 
 

- Compares with simple method to calculate Tt with base temperature of 0oC 
```{r, warning=FALSE}

df_We_tt <- df_emerg6 %>%
  #mutate(Date=dmy(Date)) %>%
  rowwise() %>%
  mutate(TTday=TTfunc(Tm,Tx), TTday_s=(Tm+Tx)/2, diff=(TTday_s-TTday))

summary(df_We_tt)

```
 
 
 
```{r}
#Check TT  two methods : TTday_s = simple method (Tmean - Tbzero)
df_We_tt  %>% 
ggplot(aes(x=TTday_s, y= TTday)) +
  geom_point(shape=21,alpha=0.2,colour='red')+
  geom_abline(intercept = 0, slope = 1)

```
 
 
 Then accumulate the TT 
 
 
```{r}

 df_AntasTT <-df_We_tt%>%
    arrange(Date)%>%
    mutate(SumTTday = cumsum(TTday))%>%
  mutate(SUMTTday_s = cumsum(TTday_s)) %>%
  dplyr::select(-TempSoil10mm) 



summary(df_AntasTT)


```


Calculate tt at sow then tt ate date of 50 emergence make one minus another to find TT emerg 

```{r}
df1 <- merge(D,df_AntasTT, by.x="SowingDate",by.y="Date") %>%
  mutate(soilTempAcc_sow = SumTTday) %>%
  dplyr::select(-SumTTday)%>%
  filter(Cultivar=="Antas")

str(df1)
```


Need to force a date for 50 % emergence (round) 

```{r}

# force formats of dates
df1$Date <- round(df1$Date50E,0)
df_AntasTT$Date <- round(df_AntasTT$Date,0)

  df_merge <- merge(df1, df_AntasTT, by="Date") %>%
    mutate(soilTempAcc_em = SumTTday) %>%
  dplyr::select(-SumTTday) %>%
  mutate(SummTTEmerg = (soilTempAcc_em-soilTempAcc_sow))

 summary(df_merge)
```

get the TT and SE for all cultivars. exclude S1 . Consider Tb=0 for all cultivars. 

```{r}
df_TT <- df_merge%>%
   filter(SowTreat!= "S1")

#then select sow treat and means and se

df_TTA <-df_TT %>%
  #group_by(Cultivar) %>%
  dplyr::select(SummTTEmerg)%>%
  summarise_all(funs(mean,sd))%>%
    mutate(SE=sd/1.73)
  
```








END ....


