---
title: "Emergence seedlings I2 graphs with Mean Soil Temp Poukawa"
author: "CT"
date: "07.08.2017"
output: html_document
---

This script does this:
-get dataframe produced in Pok_Calc5EmergSoilT (df3; df_MeanSoilTemp50EmergPo.txt)
-graph y=Days to 50% emergence ; x= mean soil Temp
-graph y= 1/days to 50% emergence ; x= mean soil Temp



```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
library (gridExtra)
```


```{r loadFile}
# Get dataframe from previous script (written table )
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergencePoukawa")
getwd()

#create file
df_G <- read.table("df_MeanSoilTemp50EmergPo.txt",header=TRUE)


df_G$Date50E <- ymd(df_G$Date50E)
df_G$SowingDate <- ymd(df_G$SowingDate )
df_G$Cultivar <- as.factor(df_G$Cultivar)
df_G$Plot <- as.factor(df_G$Plot)

summary(df_G)

# this is to "clean previous dfs : df_emerg4 <- NULL

```

Include 1/DAS50E 


```{r}

df_H <- df_G %>%
  mutate(InvDAS50E= 1/ DAS50E)

```


```{r, fig.height=5, fig.width=10, echo = FALSE}



fontSize <- 12.0

#DAS50E
#g1 <- df_H %>%
  #filter(year %in% 1960:2000) %>%
  #group_by(day) %>%
 # summarise_each(funs(mean)) %>%
  g1 <- df_H %>%
  ggplot(aes(x=meanTemp_Em, y=DAS50E, colour=SowTreat))  +
  geom_point(alpha=0.8) +
  #geom_smooth()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Estimated~Soil~temperature~~"("^"o"*"C)")) +  
  ylab("Days to 50% emergence  (days)") +
    facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=11))+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,40))

# 1/DAS50E
  g2 <- df_H %>%
  ggplot(aes(x=meanTemp_Em, y=InvDAS50E, colour=SowTreat))  +
  geom_point(alpha=0.8) +
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Estimated~Soil~temperature~~"("^"o"*"C)")) + 
  ylab(" Rate (1/ Days) to 50% emergence") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=11))+
 scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.25))
  grid.arrange(g1, g2)
# 

# 

```

use the means for each sowtreat 



calculate mean values for each cultivar and sow Treat

```{r}
df_mean<-df_H%>%
  group_by(Cultivar,SowTreat)%>%
   summarise_all(funs(mean))
```


```{r, fig.height=5, fig.width=10}

fontSize <- 14.0



#DAS50E
#
  g3 <- df_mean %>%
  #filter(Cultivar=="Monti"| Cultivar=="Antas")%>%
 # filter (SowTreat== "S3"| SowTreat== "S4"|SowTreat== "S5"|SowTreat== "S6")%>%
    #group_by(Cultivar,SowTreat)%>%
    #summarise_all(funs(mean))
  ggplot(aes(x=meanTemp_Em, y=DAS50E, colour=SowTreat))  +
    geom_point(aes(shape= SowTreat), size=4)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
 # geom_point(alpha=0.8) +
  #geom_smooth()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Estimated~Soil~temperature~~"("^"o"*"C)")) +  
  ylab("Days to 50% emergence  (days)") +
    facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=11))+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,40))

# 1/DAS50E
  g4 <- df_mean %>%
   #filter(Cultivar=="Monti"| Cultivar=="Antas")%>%
  #filter (SowTreat== "S3"| SowTreat== "S4"|SowTreat== "S5"|SowTreat== "S6")%>%
  ggplot(aes(x=meanTemp_Em, y=InvDAS50E, colour=SowTreat))  +
    geom_point(aes(shape= SowTreat), size=4)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  #geom_point(alpha=0.8) +
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Estimated~Soil~temperature~~"("^"o"*"C)")) + 
  ylab(" Rate (1/ Days) to 50% emergence") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=11))+
 scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.25))
  grid.arrange(g3, g4)

```



```{r}

```











here get the equations from all temperatures BUT FOR POUKAWA this is not a good idea! Estimated soil temps!

```{r, fig.height=7,fig.width=12}

require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}


df <- df_H %>%
  dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E) %>%
  group_by(SowTreat,Cultivar) %>%
  summarise_each(funs(mean)) %>%
  mutate(y=InvDAS50E,x=meanTemp_Em) %>%
  dplyr::select(-meanTemp_Em, -InvDAS50E)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="grey", linetype= 2,formula = y ~ x) +
  geom_point()+
  theme_bw()+
  scale_x_continuous(limits = c(0,25))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE) + 
  facet_grid(Cultivar~.,scales="free")
  
p1
```


Overall Linear equations are :
-------------------------------------------------------------------------------------
Antas : y = 0.13 - 0.0029x (R2= 0.197)
Denmark : y = 0.097 - 0.0013x (R2= 0.0429)
Leura: y = 0.14 - 0.0042x (R2=0.298)
Monti: y= 0.12 - 0.0029 x (R2=0.174)
Narrikup : y = 0.11 -0.0023x (R2=0.095)
Woogenellup: y = 0.12-0.0024x (R2=0.131)
----------------------------------------------------------------------------------------

Try to subset the temperatures and see a segmented relationship 

```{r}
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}


df <- df_H %>%
  subset(meanTemp_Em>5 & meanTemp_Em<10)%>%
  dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E) %>%
  group_by(SowTreat,Cultivar) %>%
  summarise_all(funs(mean)) %>%
  mutate(y=InvDAS50E,x=meanTemp_Em) %>%
  dplyr::select(-meanTemp_Em, -InvDAS50E)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="grey", linetype= 2,formula = y ~ x) +
  geom_point()+
  theme_bw()+
  scale_x_continuous(limits = c(0,15))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE) + 
  facet_grid(Cultivar~.,scales="free")
  
p1


#get statistical summary here 
summary(lm(y ~ x, df))

```

Equations for ascending segment (temperature range = 7 - 10)
-------------------------------------------------------------
A: y=  -0.47 + 0.067x ,  r2 0.98
D: y = -0.4 + 0.056x , r2 0.97
L: y = -0.37 + 0.054 , r2 0.97
M: y = -0.37 + 0.055 ,r2 0.94
N: y = -0.37 + 0.053 , r2 0.84
W: y = -0.27 + 0.042, r2 0.89

Mean : y = - 0.036 (0.02) + 0.05 (0.002)x, r2 0.87
-----------------------------------------------------------------

Now see the descending segment 

```{r}
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}


df <- df_H %>%
  subset(meanTemp_Em>11 & meanTemp_Em<25)%>%
  dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E) %>%
  group_by(SowTreat,Cultivar) %>%
  summarise_all(funs(mean)) %>%
  mutate(y=InvDAS50E,x=meanTemp_Em) %>%
  dplyr::select(-meanTemp_Em, -InvDAS50E)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="grey", linetype= 2,formula = y ~ x) +
  geom_point()+
  theme_bw()+
  scale_x_continuous(limits = c(10,25))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE) + 
  facet_grid(Cultivar~.,scales="free")
  
p1


#get statistical summary here 
summary(lm(y ~ x, df))



```



-----------------------------------------------------------------

Graph with geom smooth to demonstrate relationship emergence rate and estimated soil temperature (better aestethics)



```{r fig.height=5, fig.width=10, echo = FALSE, warning=FALSE}

#graph S2-S8 



fontSize <- 12.0

#DAS50E
#g1 <- df_H %>%
  #filter(year %in% 1960:2000) %>%
  #group_by(day) %>%
 # summarise_each(funs(mean)) %>%
  g1 <- df_mean %>%
    #filter(SowTreat!="S1")%>%
  ggplot(aes(x=meanTemp_Em, y=DAS50E,shape=Cultivar))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  #geom_smooth()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Estimated~Soil~temperature~~"("^"o"*"C)")) + 
  ylab("Days to 50% emergence  (days)") +
    facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=10))+
  geom_smooth(method = "lm") # +
  # scale_x_continuous(limits = c(0,25))+
  # scale_y_continuous(limits = c(0,40))

# 1/DAS50E
  g2 <- df_mean %>%
    #filter(SowTreat!="S1")%>%
  ggplot(aes(x=meanTemp_Em, y=InvDAS50E )) +
  #geom_point(alpha=0.2,size=3, shape=) +
  geom_point(aes(shape=SowTreat, colour=SowTreat), size =5)+
    scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  geom_smooth(method = "lm")+
  theme_bw() +
  xlab(expression(Estimated~Soil~temperature~"("^"o"*"C)")) + 
  ylab(" Rate (1/ Days) to 50% emergence") +
  #facet_grid(.~Cultivar, scales="free")+
  facet_grid(.~Cultivar)+
 theme(text = element_text(size=10)) +
  scale_x_continuous(limits = c(5,25))
 #scale_y_continuous(limits = c(0,0.25))+
  grid.arrange(g1, g2)
# 

  #grid.arrange(g1, g2)
  
  #show only emergence rate 
  grid.arrange( g2)

```

Then get the equations for the interval between 5 - 17 degrees 

```{r}

# 1/DAS50E (going up)
  g1 <- df_H %>%
    filter(SowTreat!="S1")%>%
  ggplot(aes(x=meanTemp_Em, y=InvDAS50E, shape=Cultivar))+
  geom_point(colour= "red", alpha=0.2)+
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  #geom_smooth(method = "lm")+
  geom_smooth(method = "lm", se=FALSE, color="blue", formula = y ~ x) +
            geom_point()


p1 = g1 + geom_text(data=eq,aes(x = 5, y = 0.25,label=V1), parse = TRUE, inherit.aes=FALSE) + #facet_grid(group~.)
p1 
  theme_bw() +
  xlab("Mean Soil Temp (oC)") + 
  ylab(" Rate (1/ Days) to 50% emergence") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=10))+
 scale_x_continuous(limits = c(0,17))+
 scale_y_continuous(limits = c(0,0.25))+
 
   

  #grid.arrange(g1, g2)
# 

  
  grid.arrange(g1, g2)




```


