---
title: "Emergence seedlings Poukawa"
author: "CT"
date: "07.08.2017"
output:
  word_document: default
 
---

Purpose:

-Analysis of DAS50 Pokawa site dataset using dataframe generated in script 3 (df_RateEmergPo)
 

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(mosaic)
library(lattice)
```

Read dataframe created in previous script (EmergencePok_Calc3)
Change formats and check the data frame 
```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergencePoukawa")
getwd()

#create file
df_emerg <- read.table("df_RateEmergPo.txt",header=TRUE)

# define factors for the ones that "look like" values
df_emerg$Plot <- as.factor(df_emerg$Plot)
df_emerg$Block <- as.factor(df_emerg$Block)


str(df_emerg)
head(df_emerg)
tail(df_emerg)


df_emerg %>% filter(Plot ==1) %>% summary()

str(df_emerg)
```


```{r, fig.height= 7, fig.width= 10}
# Graph it 

# 
# #Graph         
#   df_emerg %>%  group_by(Cultivar, SowTreat, DAS) %>%
#   #filter(SowTreat =="S2"& SowTreat =="S4")%>%
#   #dplyr::select(-SowingDate, - ReadingDate) %>%
#   summarise_each(funs(mean)) %>%
#   ggplot(aes(x=DAS, y=PlantPop)) + 
#   geom_point(aes(colour=Cultivar,shape=Cultivar)) +
#   geom_line(aes(colour=Cultivar)) +
#   #add error bar
#   geom_errorbar(aes(x=20,ymin=200,ymax=300,width=0.2))+
#   facet_wrap(~SowTreat,ncol=4, scales = "free")+
#   theme_bw()+
#   ylim(0, 2200)+
#   labs(y="Number of seedlings per m2",x="Days after sowing") +
#   geom_abline(intercept = 1000, slope = 0)

```

Here only change dataframe name and check



##Run stats for the number of days to reach 5 ttrifoliates (DAS9T) - general use Sow Treat as Factor 
##Here run as balanced design 

```{r}
 
  file <- df_emerg


file.subs <- file 

head(file.subs)
summary(file.subs)

#ANOVA

my.anova <- aov(DAS50E ~ SowTreat + Block, data = file.subs)
#my.anova <- aov(DAS50E ~ Cultivar + Block, data = file.subs)

summary(my.anova)

```


```{r}
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))

```


then create a loop anova for DAS50E 


## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(df_emerg$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```


then loop anova if significant 

## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_emerg %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(DAS50E ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


 if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
   print("***Sig Cultivar***") 
   print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```



End of this script. 
Continue with ANOVA for TT50 in the next script. 

