---
title: "Emergence seedlings I2"
author: "CT"
date: "3.03.2016"
output: html_document
---

This script does this:

- get the dataframe produced in Calc1  
- Calculate the DAS and TT for the 50% emergence by a loop interpolating points


```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
```


```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergencePoukawa")
getwd()

#create file
df_emerg1 <- read.table("df_emerg_perc_Po.txt",header=TRUE)

#Change formats 
df_emerg1$ReadingDate <- ymd(df_emerg1$ReadingDate )
df_emerg1$SowingDate <- ymd(df_emerg1$SowingDate )
df_emerg1$Block <- as.factor(df_emerg1$Block)
df_emerg1$Plot <- as.factor(df_emerg1$Plot)

#change name of column Pp.x cause Pp.x was causing  error 
# df_emerg1 %>%
#   mutate(Pp.x= as.numeric(Pp))%>%
#   dplyr::select(-Pp.x)
         
str(df_emerg1)

```

Calculate 50 PercentEmergence and finding out the DAS and TTAS for the 50% emergence 

```{r SummariseDf}

# This step is now unnecessary as we want Plot values anyway (FIXME)
df_50_Perc <- df_emerg1 %>%
  mutate(DAS = as.numeric(ReadingDate-SowingDate)) %>%
  group_by(Plot, Block,Cultivar,SowTreat, PercEmerg, ReadingDate) %>%
  summarise(av_Perc = mean(PercEmerg), 
            av_TT = mean(TT_to_emerg),
            av_DAS = mean(DAS)
            )

str(df_50_Perc)
summary(df_50_Perc)
head(df_50_Perc)

# write.table(df_50_Perc, "df_50_PercEmerg.txt") # FIXME: this file is not yet 50%

#  loop to calculate tt_50p_flow for each var x sd x cv
#cv <- unique(df_50_Perc$Cultivar)
#var <- unique(df_50_Perc$PercEmerg)
#sow <- unique(df_50_Perc$SowTreat)
#sowd <- unique(df_50_Perc$SowingDate)
plots<- unique(df_50_Perc$Plot)
 

# create empty df
# df_tt_50p_emerg <- data.frame(Plot = NULL,
#                               Block = NULL,
#                              SowingD = NULL,
#                              Cultivar = NULL, 
#                              SowTreat = NULL,
#                              PercEmerg = NULL, 
#                              TT50Em = NULL)

#loop trough each combination of factor levels

for(p in 1:length(plots)) {
#  for(j in 1:length(var)){
 #   for(k in 1:length(sow)){
      
      # clean value holders
      DAS_50p_emerg <- 0
      tt_50p_emerg <- 0
      
      #FIX ME Partially set 
    
     # print(paste0(cv[i]," ",var[j]," ", sow[k]))
      # filter for each combination

  df_sub <- df_50_Perc %>%
    # subset(Cultivar == as.character(cv[i]) &
    # Plot == as.character(var[j]) &
    # Block == as.character(var[b]) &
    # SowTreat == as.character(sow[k])) %>%
    subset(Plot == plots[p]) %>%
    arrange(PercEmerg)
  
  df_sub
  head(df_sub)
  # create percentage with maximum value recorded 
  # to avoid crossing the 50% line twice
  
  df_sub$av_Perc_max <- 0 # create new col
  
  for(z in 1:nrow(df_sub)) {
    
    df_sub$av_Perc_max[z] <- max(df_sub$av_Perc[z],
                                 df_sub$av_Perc_max[z-1])
    
  }
  
  df_sub
  head(df_sub)
  tail(df_sub)

  # Interpolate 
  y_ref <- 50 # y value where we want to find x by interpolation
  
  # interpolate
  #find DAS at 50 Pecent Emergence 

  tryCatch(  
  DAS_50p_emerg <- approx(df_sub$PercEmerg, 
  df_sub$av_DAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  DAS_50p_emerg <- NA
  }
)
  #find TT at 50 Pecent Emergence
  tryCatch(  
  tt_50p_emerg <- approx(df_sub$av_Perc, 
  df_sub$av_TT , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  tt_50p_emerg <- NA
  }
)

  df_temp <- NULL
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             PercEmerg = df_sub$PercEmerg[1], 
                             SowTreat = df_sub$SowTreat[1],
                             Plot = df_sub$Plot[1],
                             Block = df_sub$Block[1],
                             DAS50E = DAS_50p_emerg,
                             TT50E = tt_50p_emerg)
  print(p)
  
  if(p == 1) {
    df_tt_50p_emerg <- df_temp
  } else {
   df_tt_50p_emerg <- rbind(df_tt_50p_emerg,df_temp) 
  }                     
  
  
      
#    } 
  } # end plot loop



head(df_tt_50p_emerg)

write.table(df_tt_50p_emerg,"df_tt_50p_emergPo.txt")

summary(df_tt_50p_emerg)

```

Graph results to write in cahpter 4.
Include SowTreat and Sowind date in dataframe

```{r GraphResults}

sdLookup <- data.frame (
  SowTreat = c("S1","S2","S3","S4","S5","S6","S7","S8"),
  SowingDate = c("19/02/2016", 
                 "30/03/2016" ,
                 "30/05/2016" ,
                 "05/07/2016" ,
                 "24/08/2016" ,
                 "11/10/2016" ,
                 "24/11/2016",
                 "05/01/2017"))

sdLookup$SowingDate <- dmy(sdLookup$SowingDate)


df_tt_50p_emerg <- merge(df_tt_50p_emerg, sdLookup, by="SowTreat")
summary(df_tt_50p_emerg)





```

```{r, fig.height=5, fig.width=10}

#Here just to check means 
# mean <-df_tt_50p_emerg %>%
#   group_by(SowTreat, SowingDate, Cultivar,DAS50E) %>%
#   summarise_each(funs(mean,sd))
# summary (mean)


df_tt_50p_emerg %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(DAS50E) %>%
  summarise_each(funs(mean,sd)) %>%
  
  # if needed to exclude cultivars for analysis use filter 
  # filter( Cultivar != "Woogenellup" &
  #        Cultivar != "Monti" &
  #        Cultivar != "Antas" &
  #        Cultivar != "Denmark" &
  #        Cultivar != "Leura") %>%
         
 
  
ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="Days to 50% emergence ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 12))+
  theme(axis.text.y = element_text(angle = 0, hjust = 1, size = 12))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()
 


```

Calculate the rate of emergence (1/Days)

```{r}

#try 1/DAS50% = Rate

df_RateEmerg <- df_tt_50p_emerg %>%
  mutate(Rate=1/DAS50E)

  summary(df_RateEmerg)
  
  
  
```

Graph the rate 

```{r}
df_RateEmerg %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 50% emergence ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()
  
  write.table(df_RateEmerg, "df_RateEmergPo.txt")
```

graph with variable TT50E 

```{r, fig.height=5, fig.width=10}


df_tt_50p_emerg %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(TT50E) %>%
  summarise_each(funs(mean,sd)) %>%
  
  # if needed to exclude cultivars for analysis use filter 
  # filter( Cultivar != "Woogenellup" &
  #        Cultivar != "Monti" &
  #        Cultivar != "Antas" &
  #        Cultivar != "Denmark" &
  #        Cultivar != "Leura") %>%
         
 
  
ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="Thermal time to 50% emergence ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()
 

```

Graph average thermal time for emergence and percentage of emergence (similar to script 1)

```{r}

df_50_Perc %>%
  ungroup() %>%
  mutate(Cultivar=factor(Cultivar)) %>%
  mutate(SowTreat=factor(SowTreat)) %>%
  mutate(ReadingDate= ymd(ReadingDate)) %>%
  group_by(Cultivar,SowTreat, ReadingDate) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=av_TT,y=PercEmerg)) +
  geom_point(aes(colour=Cultivar)) + 
  facet_wrap(~SowTreat,ncol=4)+
  geom_line(aes(linetype=Cultivar)) +
  geom_abline(intercept=50,slope=0) +
  geom_vline(xintercept = 100, linetype=2)


```

End of this script.
