---
title: "Emergence seedlings Poukawa"
author: "CT"
date: "03.03.2016"
output:
  word_document: default
 
---

Purpose:

-Statistical Analysis of plant population 
 



```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(mosaic)
library(lattice)
```


```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergencePoukawa")
getwd()

#create file
df_emerg <- read.table("PlantPopPok.txt",header=TRUE)

# define factors for the ones that "look like" values
df_emerg$Plot <- as.factor(df_emerg$Plot)
df_emerg$Block <- as.factor(df_emerg$Block)

 df_emerg <- df_emerg %>%
  mutate(SowingDate = dmy(SowingDate), 
         ReadingDate = dmy(ReadingDate),
         PlantPop = (Sub1+Sub2+Sub3)/3/0.01)

str(df_emerg)
head(df_emerg)
tail(df_emerg)


df_emerg %>% filter(Plot ==1) %>% summary()


```

Calculates the Plant Population 

```{r ANOVAMaxPlantPop}

#compare max plant population among Sowing dates and cultivars

df_emerg_perc3 <- df_emerg %>%
group_by(SowTreat,Cultivar,Block,Plot) %>%
  filter(DAS==max(DAS))%>%
  dplyr::select(PlantPop)%>%
  summarise_all(funs(max))%>%
  mutate(FinalPop=round((PlantPop)*1,digits=2))

head(df_emerg_perc3)
summary (df_emerg_perc3)

write.table(df_emerg_perc3, "df_emerg_perc3Pok.txt")
```

Run anova general (get means to write about it in chapters )

```{r}

df_emerg_S1 <-df_emerg_perc3 
#filter(SowTreat=="S1") 
summary (df_emerg_S1)


#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$FinalPop)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#To get means select the factor : SowTreat or Cultivar
my.anova <- aov(transf_no ~ SowTreat*Cultivar + Block, 
                data = file.subset)




```



```{r}

summary(my.anova)

#Means separation 
#(LSD.test(my.anova, c("SowTreat","Cultivar"), alpha= 0.05, p.adj="none") )
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none") )
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
```



Then select each sowing date individually to perform ANOVA; here starting with S1  


```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S1") 
summary (df_emerg_S1)  
  
```



Run ANOVA pure numbers starting with Sowing date 1

```{r}
#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$FinalPop)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#To get means select the factor : SowTreat or Cultivar
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)




```

```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
```

ANOVA for S2
 
```{r}

df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S2") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$FinalPop)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)





```

```{r}
summary(my.anova)
```


```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
```

spwcial analysis ;separate Antas and Monti only here 
```{r}

df_emerg_S2AM <-df_emerg_perc3 %>%
filter(SowTreat=="S2") %>%
filter(Cultivar=="Antas"|Cultivar=="Monti")
summary (df_emerg_S2AM)  

#data transf
file <- df_emerg_S2AM
file$transf_no <- 1*(df_emerg_S1$FinalPop)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
```





ANOVA for S3

```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S3") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$FinalPop)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)




```

```{r}
summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
```

ANOVA for S4

```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S4") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$FinalPop)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)





```

```{r}
summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
```

ANOVA for S5


```{r}

df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S5") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$FinalPop)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)




```


```{r}
summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
```




ANOVA for S6

```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S6") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$FinalPop)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)




```



```{r}
summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
```


ANOVA for S7 

```{r}

df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S7") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$FinalPop)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)



```


```{r}
summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
```


ANOVA for S8

```{r}
df_emerg_S1 <-df_emerg_perc3 %>%
filter(SowTreat=="S8") 
summary (df_emerg_S1)  

#data transf
file <- df_emerg_S1
file$transf_no <- 1*(df_emerg_S1$FinalPop)
head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)



```

```{r}
summary(my.anova)

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
```



End of this script. 
More analysis in script Calc3. 