---
title: "Spectra of S2 FTIR test"
author: "CT"
date: "18.09.2017"
output: html_document
#here files have already been baselined corrected in OPUS. 
#Raw data is on folder Bionami Maatrix 25.04; worksheet Columns to R.
#In this script the analysis of wavenumber range 650 and 670 is performed. find peaks in this region   
---


```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)
library(hyperSpec)

```


```{r readData}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\FTIR_S2")
getwd()
file <- read.table ("S2.txt",  header = TRUE)

str (file)

```
Adjust formats 

```{r}

file1 <-file %>%
mutate(
    Plot = as.factor(Plot),
    #wavelength = leave as integer for greaphics 
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Hardness = as.numeric (Hardness),
    Seed = as.factor(Seed)
  )  

str (file1)


```
Subset a range of interest


```{r}

df_1500<-file1 %>%
  #subset range 
  subset (wavelength==1500)

```


Graph wavenumber 742, 769, 1209, 1211, 1971, 3716


```{r}

df_1500%>%
  dplyr::select(Cultivar,Absorbance, wavelength, Hardness)%>%
  group_by(Cultivar)%>%
  summarise_each(funs(mean))%>%
  ggplot(aes(x=Absorbance,y=Hardness, colour=Cultivar, shape=Cultivar))+
           geom_point(size=3)+
  theme_bw()+
#scale_x_continuous(breaks=seq(min(file1$wavelength),max(file1$wavelength),10))+
  #scale_x_reverse()+
  #scale_x_continuous(lim=c(650,4000))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.01)) +
 ylab(expression(Hardness~"(%)"))+
  xlab(expression(Absorbance~"(1500 cm"^"-1"*")"))#expand_limits(x=650, 4000)+
  geom_abline(intercept = 0.1, slope = 0)
  
  


```
  

```{r}

df_1250 <-file1 %>%
  #subset peak
  subset (wavelength==1250)
  

```

then check with hardness 

```{r}
df_1250 %>%
  dplyr::select(Cultivar,Absorbance, wavelength, Hardness)%>%
  group_by(Cultivar)%>%
  summarise_each(funs(mean))%>%
  ggplot(aes(x=Absorbance,y=Hardness, colour=Cultivar, shape=Cultivar))+
           geom_point(size=3)+
  theme_bw()+
#scale_x_continuous(breaks=seq(min(file1$wavelength),max(file1$wavelength),10))+
  #scale_x_reverse()+
  #scale_x_continuous(lim=c(650,4000))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.01)) +
 ylab(expression(Hardness~"(%)"))+
  xlab(expression(Absorbance~"(1250 cm"^"-1"*")"))#expand_limits(x=650, 4000)+
  geom_abline(intercept = 0.1, slope = 0)

```

then try another wavenumber 897

```{r}

df_1209 <-file1 %>%
  #subset peak
  subset (wavelength==1209)

```



```{r}

df_1209 %>%
  dplyr::select(Cultivar,Absorbance, wavelength, Hardness)%>%
  group_by(Cultivar)%>%
  summarise_each(funs(mean))%>%
 ggplot(aes(x=Absorbance,y=Hardness, colour=Cultivar, shape=Cultivar))+
           geom_point(size=3)+
  theme_bw()+
#scale_x_continuous(breaks=seq(min(file1$wavelength),max(file1$wavelength),10))+
  #scale_x_reverse()+
  #scale_x_continuous(lim=c(650,4000))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.01)) +
 ylab(expression(Hardness~"(%)"))+
  xlab(expression(Absorbance~"(1209 cm"^"-1"*")"))#expand_limits(x=650, 4000)+
  geom_abline(intercept = 0.1, slope = 0)
```

Then try for 710 WL 

```{r}
df_select <- file1 %>%
  #subset peak
  subset (wavelength==2451)


```



```{r}
df_select %>%
  dplyr::select(Cultivar,Absorbance, wavelength, Hardness)%>%
  group_by(Cultivar)%>%
  summarise_each(funs(mean))%>%
  ggplot(aes(x=Absorbance,y=Hardness))+
           geom_point(size=3,aes(colour=Cultivar, shape=Cultivar))+
  geom_smooth(method = "lm")+
  theme_bw()+
#scale_x_continuous(breaks=seq(min(file1$wavelength),max(file1$wavelength),10))+
  #scale_x_reverse()+
  #scale_x_continuous(lim=c(650,4000))+
 # theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
#  expand_limits(y=c(0,0.01)) +
 ylab(expression(Hardness~"(%)"))+
  xlab(expression(Absorbance~"(2451 cm"^"-1"*")"))#expand_limits(x=650, 4000)+
  #geom_abline(intercept = 0.1, slope = 0)

```


675

```{r}
df_675 <-file1 %>%
  #subset peak
  subset (wavelength==675)

```



```{r}
df_675 %>%
  dplyr::select(Cultivar,Absorbance, wavelength, Hardness)%>%
  group_by(Cultivar)%>%
  summarise_each(funs(mean))%>%
  ggplot(aes(x=Absorbance,y=Hardness, colour=Cultivar, shape=Cultivar))+
           geom_point(size=3)+
  theme_bw()+
#scale_x_continuous(breaks=seq(min(file1$wavelength),max(file1$wavelength),10))+
  #scale_x_reverse()+
  #scale_x_continuous(lim=c(650,4000))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.01)) +
 ylab(expression(Hardness~"(%)"))+
  xlab(expression(Absorbance~"(675 cm"^"-1"*")"))#expand_limits(x=650, 4000)+
  geom_abline(intercept = 0.1, slope = 0)

```





Try 669 (that's is confirmed P < 0.05 in the Hardseed script !!)

```{r}

df_669<-file1 %>%
  #subset peak
  subset (wavelength==669)

```



```{r}

df_669 %>%
  dplyr::select(Cultivar,Absorbance, wavelength, Hardness)%>%
  group_by(Cultivar)%>%
  summarise_each(funs(mean))%>%
  ggplot(aes(x=Absorbance,y=Hardness, colour=Cultivar, shape=Cultivar))+
           geom_point(size=3)+
  theme_bw()+
#scale_x_continuous(breaks=seq(min(file1$wavelength),max(file1$wavelength),10))+
  #scale_x_reverse()+
  #scale_x_continuous(lim=c(650,4000))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.01)) +
 ylab(expression(Hardness~"(%)"))+
  xlab(expression(Absorbance~"(669 cm"^"-1"*")"))#expand_limits(x=650, 4000)+
  geom_abline(intercept = 0.1, slope = 0)


```

