---
title: "Percent red leaves and red scoring  Experiment 2 "
author: "CT"
date: "31.10.2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(markdown)
#install.packages(markdown)

```


Use this pathC:\GitHubRepos\SubcloverPhD\SubClover\Temperatures Cold test

GEt thsi file : Expt2Data.txt

variables are : 
AverageRedLeaves (that is already in percentage)
RedIntensityScore (score 1-5)

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Temperatures Cold test")
getwd()

#create file
df_Exp2 <- read.table("DataExpt2.txt",header=TRUE)
head(df_Exp2)


# change format 
#df_seed$Date <- dmy(df_seed$Date)

# jeito 2 de trocar formato (usando dplyr)
df_Exp2 <- df_Exp2 %>%
  mutate(PotNumber = as.factor(PotNumber), 
         RepBlock = as.factor(RepBlock),
        
        AverageRedLeaves = as.numeric(AverageRedLeaves),
        RedIntensityScore = as.numeric(RedIntensityScore)) 
  

#summary(df_seed) # explore values
str(df_Exp2) # check formats
#head(df_seed) # see to rows
#tail(df_seed)



```




Work first with the AverageRedLeaves data

```{r}

str(df_Exp2)
##rename dataframe 

file <-df_Exp2
  
##data transformation
file$transf_sqr <- sqrt(file$AverageRedLeaves)
file$transf_log <- log(file$AverageRedLeaves)
file$transf_not <- 1*(file$AverageRedLeaves/1)
file$transf_acos <- acos(file$AverageRedLeaves/100)
file$transf_sqrx <- (file$AverageRedLeaves^2)
#mutate(mydata, sqr.x = x^2)


head(file)

x <- c("transf_sqr", "transf_log","transf_acos","transf_not", "transf_sqrx" )
colsSelec <- match(x,colnames(file))




``` 




```{r, fig.height=7, fig.widht=8}


file %>%
  tidyr::gather("transformation","value",colsSelec) %>%
  ggplot(aes(value)) + 
  geom_histogram() +
  facet_grid(.~transformation, scales="free")+
  theme_bw()



```




check normality shapiro test +QQplots

```{r}

#normality test
shapiro.test(file$transf_acos)
shapiro.test(file$transf_not)
shapiro.test(file$transf_sqr)
shapiro.test(file$transf_log)
shapiro.test(file$transf_sqrx)




##QQplot
#var<-file$transf_acos

#var<-file$transf_not
var<-file$transf_sqr
#var<-file$transf_log
#var<-file$transf_sqrx

qqnorm(var)
qqline(var, col = 2)
qqplot(var, rt(300, df = 5))



```




then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

str (file)

file <- file %>%
  dplyr::select(RepBlock, Cultivar,Subspecies, Origin, transf_sqr)

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)



#my.anova <- aov(transf_sqr~ Cultivar + RepBlock, data = file.subset)

my.anova <- aov(transf_sqr~ Subspecies + RepBlock, data = file.subset)
#my.anova <- aov(transf_sqr~ Origin + RepBlock, data = file.subset)


```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))

```

then perfomr Tukeys test 

This is Tukeys test for mean comparison 

```{r}
posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)

posthoc

```

and 


```{r}

fogo <-HSD.test(my.anova, 'Cultivar', group=TRUE)
fogo

```

Now repeat the procedure with the RedIntensityScore


```{r}

str(df_Exp2)
##rename dataframe 

file <-df_Exp2
  
##data transformation
file$transf_sqr <- sqrt(file$RedIntensityScore)
file$transf_log <- log(file$RedIntensityScore)
file$transf_not <- 1*(file$RedIntensityScore/1)
file$transf_acos <- acos(file$RedIntensityScore/100)
file$transf_sqrx <- (file$RedIntensityScore^2)
#mutate(mydata, sqr.x = x^2)


head(file)

x <- c("transf_sqr", "transf_log","transf_acos","transf_not", "transf_sqrx" )
colsSelec <- match(x,colnames(file))




``` 




```{r, fig.height=7, fig.widht=8}


file %>%
  tidyr::gather("transformation","value",colsSelec) %>%
  ggplot(aes(value)) + 
  geom_histogram() +
  facet_grid(.~transformation, scales="free")+
  theme_bw()



```


check normality shapiro test +QQplots

```{r}

#normality test
shapiro.test(file$transf_acos)
shapiro.test(file$transf_not)
shapiro.test(file$transf_sqr)
shapiro.test(file$transf_log)
shapiro.test(file$transf_sqrx)




##QQplot
#var<-file$transf_acos

#var<-file$transf_not
var<-file$transf_sqr
#var<-file$transf_log
#var<-file$transf_sqrx

qqnorm(var)
qqline(var, col = 2)
qqplot(var, rt(300, df = 5))



```

then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

str (file)

file <- file %>%
  dplyr::select(RepBlock, Cultivar,Subspecies, Origin, transf_sqr)

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(Abn_perc~ Cultivar*SowTreat*Depth + Block, data = file.subset)
#my.anova <- aov(Abn_perc~ Cultivar + Block, data = file.subset)
#my.anova <- aov(Abn_perc~ Depth + Block, data = file.subset)
#my.anova <- aov(Abn_perc~ SowTreat + Block, data = file.subset)
##Use sqrt transformed data 

#my.anova <- aov(transf_sqr~ Cultivar + RepBlock, data = file.subset)

#my.anova <- aov(transf_sqr~ Subspecies + RepBlock, data = file.subset)
my.anova <- aov(transf_sqr~ Origin + RepBlock, data = file.subset)




```


```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

then perfomr Tukeys test 

This is Tukeys test for mean comparison 

```{r}
posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)

posthoc

```



and 


```{r}

fogo <-HSD.test(my.anova, 'Cultivar', group=TRUE)
fogo

```


end of this script 


