---
title: "Regeneration Analysis"
author: "CT"
date: "September  18, 2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
Purpose : 
calculations of regeneration mean scores or plots in Iv2
 
ANOVA for the variate : regeneration mean scores 

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
library(knitr)
```

Read File 


```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\RegenerationIv2")
getwd()
file <- read.table("RegenerationScoreIv2.txt",header=TRUE)

head (file)
```





Define the formats  

```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    ReadingDate = dmy(ReadingDate),
    SowingDate = dmy(SowingDate),
    PopScore= as.numeric(PopScore)
  )

str(file)
summary(file)

```



Here calculates prepare dodge positions and graph with SE directly

```{r, fig.height= 5, fig.width=10 , warning=FALSE}

#barplot 
#The palette with grey:cbPalette <- c("999999"),"666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")

#cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)

  df_score <- file 
  


```

Graph the pop score . To get the SE use /1.73 x 2 

```{r, fig.height= 5, fig.width=10 , warning=FALSE}
df_score %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_each(funs(mean,sd))%>%
  filter(SowTreat=="S6")%>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=( PopScore_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin= PopScore_mean- PopScore_sd/3.46, ymax= PopScore_mean+ PopScore_sd/3.46),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
    labs(y="Regeneration Score") +
  theme_bw()+
theme(axis.text.y = element_text( size = 12))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0.2,size = 18))

head(df_score)
```


## Create index to filter for loop ANOVA

```{r}
y <- c("S2","S3","S4","S6")

sdIndex <- unique(file$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```


then loop anova if significant 

## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- file %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(PopScore ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


 if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
   print("***Sig Cultivar***") 
   print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```

Here graph with the SE (SE = std/ sqrt n ; n=3)

```{r,fig.height= 5, fig.width=10 , warning=FALSE}




```

then do simple ANOVA


```{r}

```




