---
title: "R Notebook"
output: html_notebook
---

##Aim:

- Reads raw data weather all trials
- Check the data
- Graph temperature and Pp
- Calculates TT accumulation
- Saves technically consistent data


```{r, warning=FALSE}
library(here)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)
```


```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\PasturePlan_BayPlenty_")
getwd()

#create file
#df_We <- read.table("PasturePlanGR.txt",header=TRUE)


#df_DM <- read.table("AccDM.txt",header=TRUE)
df_We<- read.table("RawWeatherBOP.txt",header=TRUE)



```



```{r}
summary(df_We)

```


##Graph it

```{r,fig.height=5, fig.width=6}
df_We %>%
  mutate(Date=dmy(df_We$Date)) %>%
  #filter(LocationYear != "Mininera2005") %>%
  tidyr::gather("Variable", "Value",Tx:Tm) %>%
 #mutate(Month=format(as.Date(dmy(as.character(Date))),"%b")) %>%
  ggplot(aes(x=Date,y=Value))+
  geom_line(aes(colour=Variable)) +
  facet_wrap(~Location,scale="free") +
  labs(x=" Date")+
  ylab(expression(Air~temperature~~"("^"o"*"C)")) +
  theme_bw()+
  scale_color_manual(values=c("#333333", "#9999CC", "#CC3300"))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  scale_x_date(labels = date_format("%b-%Y")) +



  #theme(axis.title.x = element_text( size=24)) + 
  #scale_x_continuous(breaks = c(-1:6))+
  #scale_y_continuous(breaks= c(0, 3000,6000,12000))+
  theme(axis.text.x=element_text(size=12))+
  theme(axis.title.x=element_text(size=16))+
   theme(axis.text.y = element_text( size = 12,face="bold"))+
  theme(axis.title.y = element_text( size = 16,face="bold"))+
  #theme(title=element_text(size=12, ,face="bold"))+
  # theme(text=element_text(size=30,  family="serif",face="bold"))+
  # theme(title=element_text(size=22,  family="serif",face="bold"))+
  # theme(title=element_text(size=22,  family="serif",face="bold"))+
  # #remove grid lines 
   theme(
      panel.border = element_rect(colour = "black", size = 3), 
      panel.grid.major = element_blank(),
      panel.grid.minor = element_blank(),
      axis.line = element_line(colour = "black"))+
   


  # and strip gridlines
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
   
   theme(strip.text.x = element_text(size = 16, colour = "black", angle = 0))
  
 

#ggsave(paste0(workDPath,"ch03_01_ReanTempPp.tiff"),width=10, height=10,dpi = 300)


```

##Split Graph in Australia and New Zealand 

```{r,fig.height=14, fig.width=14}




```







## Define Tt cardinal temperatures

Considered an overall average the following Mills et al reference:
Tb: 3
Top range:25
Tmax: 40
							

```{r}
s<-18
tt_card <- data.frame(temp=c(3,25,25.5,40),TT=c(0,22,22,0))
tt_card %>%
  ggplot(aes(x=temp, y=TT))+
  #labs(x="Temperature (degree Celsius)")+
  #labs(y="Thermal Time (oCd)") +
  geom_line()+
  theme_bw()+
  ylim(0,30)+
xlab(expression(Temperature~"("^"o"*"C)"))+
  ylab(expression(Thermal~Time~"("^"o"*"Cd)"))+
  theme(axis.text.x=element_text( size= s))+
  theme(axis.title.x=element_text( size= s))+
  theme(axis.text.y=element_text( size= s))+
  theme(axis.title.y=element_text(size= s))+
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.background = element_blank(),
        panel.border = element_rect(colour = "black")) 

##ggsave(paste0(workDPath,"ch03_02_TtCalcModel.tiff"),width=12, height=8,dpi = 300)

```



#Create and test interpolation function - Test if works 

```{r}

temp_ref  <- 25 # x-axes reference
temp <- tt_card$temp # x-axes
TT <- tt_card$TT # y-axes


int_func <- function(temp,TT,temp_ref){

  # if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   out <- TT[length(TT)] 
   # FIXME: approx functions seems to do that - need param
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
   # else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  
int_func(temp,TT,temp_ref)



```

#create REF Jones CA, Ritchie JT, Kiniry JR, Godwin DC (1986) Subroutine structure.In 'CERES-Maize: A simulation model of maize growth anddevelopment'. (Eds CA Jones, JR Kiniry) pp. 49-194. (Texas A&M University Press: Texas, USA

```{r}

TTfunc <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
 } 
  
  TTav  <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2 + 0.0053 * n^3) * (Tmax-Tmin)) + Tmin # 8-h temperature
    
    TT_tn <- int_func(tt_card$temp, tt_card$T,tn) 
    
    TTsum <- TT_tn + TTsum
    
   # print(TT_tn)
    
    }
 
   TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc(10,24)

```
Calculate TT 

- Compares with simple method to calculate Tt with base temperature of 0oC

```{r}
df_We_tt <- df_We %>%
  mutate(Date=dmy(Date)) %>%
  rowwise() %>%
  mutate(TTday=TTfunc(Tm,Tx), TTday_s=(Tm+Tx)/2, diff=(TTday_s-TTday))

summary(df_We_tt)


```


```{r}
#Check TT  two methods : TTday_s = simple method (Tmean - Tbzero)
df_We_tt  %>% 
ggplot(aes(x=TTday_s, y= TTday)) +
  geom_point(shape=21,alpha=0.2,colour='red')+
  geom_abline(intercept = 0, slope = 1)

```


```{r}
str(df_We_tt)
```












```{r}

ly<-unique(df_We_tt$Location)
df_CumTT<-data.frame()
for(i in 1:length(ly)) {
  
  dfsub<-df_We_tt%>%filter(Location==ly[i])%>%
    arrange(Date)%>%
    mutate(SumTTday = cumsum(TTday)) %>%  
    mutate(MinDate=min(Date))%>%
    mutate(DayCount=as.numeric(Date-MinDate))

  df_CumTT<-rbind(df_CumTT,dfsub)
  dfsub<-NULL
}

summary( df_CumTT)
```

# #Calculate accumulated Themal time 

```{r}

head(df_CumTT)
```
Stopped here
#Graph the accumulate TT 
```{r}

df_CumTT %>%
  ggplot(aes(x=DayCount,y=SumTTday))+
  geom_line(aes(colour=Location, linetype=Country)) +
  #facet_wrap(~LocationYear,scale="free") +
  xlim(0,max(df_CumTT$DayCount))+
  ylim(0,max(df_CumTT$SumTTday))+
  facet_grid(.~Country)


```



```{r}
#write.table(df_CumTT,paste0(workDPath, "df_CumTT.txt"))

write.table(df_CumTT, "df_CumTTPP.txt")


```



Then find the Growth rate DM/kg/ha per oCd


```{r}

df_We<- read.table("PasturePlanGR.txt",header=TRUE)



```

Build Graph using the new dataframe with kgperTT
file is: KgDMPerTTPasturePlan
Get Data with kgDMperTT in the next script



