---
title: "Trifoliates Poukawa "
author: "CT"
date: "17.08.2017"
output: html_document
---

Purpose:

-Analysis of trifoliates expansion for Poukawafrom previous script (use number TrifoPok)
- Calculate the ti,me to reach 5 number of leaves
- Calculate rate of leaf appearance (1/Days) 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
```



```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifoPok")
getwd()
#create file
df_trif <- read.table("Number_TrifoPok.txt",header=TRUE)
str(df_trif)


```




Define formats 

```{r loadFile}


# define factors for the ones that "look like" values

df_trif <- df_trif %>%
  mutate(SowingDate = ymd(SowingDate), 
         ReadingDate = ymd(ReadingDate),
         DAS = as.numeric(DAS))


df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Cultivar <- as.factor(df_trif$Cultivar)
df_trif$SowTreat <- as.factor(df_trif$SowTreat)

 
         

str(df_trif)


```

Calculate the 50 percent of leaves  based on maximum number of leaves attained 
Change name of column TrifoNumber for PercentTrifo to keep stable code. Multiplication by 10 to equal to 50 value. 

```{r}
#change name of column TrifoNumber for PercentTrifo

df_trif <-df_trif %>%
  mutate(PercentTrifo= 10 *(TrifoNumber))

str(df_trif)
```


```{r, fig.height=5, fig.width=10}


# df_50_Perc <- df_trif %>%
#  group_by(Plot, Block,Cultivar,SowTreat, ReadingDate) %>%
#   #group_by(Plot)%>%
#   summarise(av_Perc = mean(PercentTrifo), 
#             #av_TT = mean(TT_to_emerg),
#             av_DAS = mean(DAS)
#             )
# 
# str(df_50_Perc)
# summary(df_50_Perc)
# head(df_50_Perc)


df_50_Perc <- df_trif %>%
mutate(av_Perc=PercentTrifo)%>%
mutate(av_DAS=DAS)

#group_by(Plot, Block,Cultivar,SowTreat, ReadingDate) %>%
#   #group_by(Plot)%>%
#   summarise(av_Perc = mean(PercentTrifo), 
#             #av_TT = mean(TT_to_emerg),
#             av_DAS = mean(DAS) 
#             )
# 
# str(df_50_Perc)
# summary(df_50_Perc)
# head(df_50_Perc)


```

Loop, apply funciton approx and try catch to get DAS to 50% 
```{r}

#sow <- unique(df_50_Perc$SowTreat)
#sowd <- unique(df_50_Perc$SowingDate)
plots <- unique(df_50_Perc$Plot)
 

# create empty df
# df_tt_50p_emerg <- data.frame(Plot = NULL,
#                               Block = NULL,
#                              SowingD = NULL,
#                              Cultivar = NULL, 
#                              SowTreat = NULL,
#                              PercEmerg = NULL, 
#                              TT50Em = NULL)

#loop trough each combination of factor levels

for(p in 1:length(plots)) {
#  for(j in 1:length(var)){
 #   for(k in 1:length(sow)){
      
      # clean value holders
      DAS_50p_emerg <- 0
      #tt_50p_emerg <- 0
      
      #FIX ME Partially set 
    
     # print(paste0(cv[i]," ",var[j]," ", sow[k]))
      # filter for each combination

  df_sub <- df_50_Perc %>%
    # subset(Cultivar == as.character(cv[i]) &
    # Plot == as.character(var[j]) &
    #   Block == as.character(var[b]) &
    # SowTreat == as.character(sow[k])) %>%
    subset(Plot == plots[p]) %>%
    arrange(PercentTrifo)
  
  df_sub
  head(df_sub)
  # create percentage with maximum value recorded 
  # to avoid crossing the 50% line twice
  
  df_sub$av_Perc_max <- 0 # create new col
  
  for(z in 1:nrow(df_sub)) {
    
    df_sub$av_Perc_max[z] <- max(df_sub$av_Perc[z],
                                 df_sub$av_Perc_max[z-1])
    
  }
  
  df_sub
  head(df_sub)
  tail(df_sub)

  # Interpolate 
  y_ref <- 50 # y value where we want to find x by interpolation
  
  # interpolate
  #find DAS at 50 Pecent Emergence 

  tryCatch(  
  DAS_50p_emerg <- approx(df_sub$PercentTrifo, 
  df_sub$av_DAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  DAS_50p_emerg <- NA
  }
)
  #find TT at 50 Pecent Emergence
#   tryCatch(  
#   tt_50p_emerg <- approx(df_sub$av_Perc, 
#   df_sub$av_TT , xout = y_ref, rule = 1)$y,
#   error = function(e) 
#   {
#   tt_50p_emerg <- NA
#   }
# )

  df_temp <- NULL 
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             PercEmerg = df_sub$PercentTrifo[1], 
                             SowTreat = df_sub$SowTreat[1],
                             Plot = df_sub$Plot[1],
                             Block = df_sub$Block[1],
                             DAS50E = DAS_50p_emerg)
                             #TT50E = tt_50p_emerg)
  print(p)
  
  if(p == 1) {
    df_tt_50p_emerg <- df_temp
  } else {
   df_tt_50p_emerg <- rbind(df_tt_50p_emerg,df_temp) 
  }                     
  
#    } 
  } # end plot loop


head(df_tt_50p_emerg)



summary(df_tt_50p_emerg)



```

Include dates of sowing again in dataframe 
```{r}
sdLookup <- data.frame (
  SowTreat = c("S1","S2","S3","S4","S5","S6","S7","S8"),
  SowingDate = c("19/02/2016", 
                 "30/03/2016" ,
                 "30/05/2016" ,
                 "05/07/2016" ,
                 "24/08/2016" ,
                 "11/10/2016" ,
                 "24/11/2016",
                 "05/01/2017"))

sdLookup$SowingDate <- dmy(sdLookup$SowingDate)

df_tt_50p_emerg <- merge(df_tt_50p_emerg, sdLookup, by="SowTreat")
summary(df_tt_50p_emerg)


```
Now correct column names after loop not to mix with other generated tables

```{r}

df_5T<-df_tt_50p_emerg%>%
  mutate(DAS5T=as.numeric(DAS50E))%>%
  dplyr::select(-PercEmerg)


```



```{r}

write.table(df_5T,"df_DAS_5_TrifoPok.txt")
```




Calculate RAte (1/days to 50%) 


```{r}

#try 1/DAS50% = Rate

df_RateTrifo <- df_5T %>%
  mutate(Rate=1/DAS5T)

  summary(df_RateTrifo)
  
  write.table(df_RateTrifo,"RateTrifoPok.txt")

```



Graph rate and SowTreat : note for Sowind dates August and October not all cultivars had the 5 trifoliates (maybe 4 trifoliates ) 

```{r}
#Graph 

  df_RateTrifo %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(DAS50E) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 5 trifoliates  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

df_RateTrifo %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 5 trifoliates  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

```




End of this script Calc 3. 
Move to script 4 to include temperatures  
