---
title: "Trifoliates Poukawa "
author: "CT"
date: "17.08.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Combine the rate of trifoliate appearance with Mean Air Temp during trifo appearance - Poukawa site   
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```

Get data from Emergence Folder, Daily Mean Air temperature and dates to combine in dataframe 


```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifoPok")
getwd()
#create file

df_trif <- read.table("RateTrifoPok.txt",header=TRUE)
#adjust formats 
df_trif$SowingDate <- ymd(df_trif$SowingDate )
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$DAS5T <- as.numeric(df_trif$DAS5T)

```

Create df_MD to workout dates to % trifoliates 
```{r}

  df_MD <- df_trif %>%
  mutate(Date5T=SowingDate+DAS5T) %>%
  group_by(Plot, DAS5T) %>% 
  dplyr::filter(row_number() == 1)

str(df_MD)

H <-df_MD %>%
 dplyr:: select (Plot, Date5T)

#save and store table 
write.table(H, "DateTo5Trifos.txt")

```

Bring data from emergence folder - need to review emergence for S1 Pok (30 days)

```{r}
df_S <- read.table("DASSeedEmerg.txt",header=TRUE)

#change formats 
df_S <- df_S %>%
  mutate(Plot=as.factor(Plot),
         DAS50E= as.numeric(DAS50E),
         DateTo50E= dmy(DateTo50E))

         
str(df_S)


```



```{r}


 #create file here to calculate average air temperature from emergence to ~ 5 trifoliate stage
df_A <- read.table("Pok_Weat.txt",header=TRUE)
# 
# #adjust formats
 df_A<-df_A %>%
  mutate(Date=dmy(Date),
         AirTt=(Tx+Tm)/2)
 
 str(df_A)
 
df_B <- df_A %>%
  mutate(SumAir = cumsum(AirTt)) %>%
  mutate(Date=ymd(Date))%>%
 dplyr::select(-AirTt)
 

summary(df_B)
summary (df_S)
# 
# 
# #then save table df_B with the ACcumulated Air Temperature and merge 
# 
write.table(df_B, "AccumAirPok.txt")
# 
 df1 <- merge(df_S,df_B, by.x="DateTo50E",by.y="Date")%>%
mutate(AirTempAcc_emerg = SumAir) %>%
 dplyr::select(-SumAir)
# 
 str(df1)
# 
write.table(df1,"AccAirEmerg.txt")
```


then get the air temperatures from sowing to 50% of plants with 5 trifoliates and subtract from emergence to get the mean temperature during foliar expansion 

```{r}

##then join with data with the Accumulated air temperature till 5Trifoliates for available plots 

df_C <- read.table("AccAir5Trifo.txt",header=TRUE)

##then merge the dataframes with emergence and trifo dates and Acc Air by Plot

str(df1)
str(df_C)
## now merge similar to emergence dataframe 

df3 <- merge (df1,df_C, by="Plot")


```




Then subtract AccAir (trifo) from AirTempAcc_emerg and divide by the number of days from emergence to 5 trifoliates to get the temperature during the period 

```{r}

df4 <-df3%>%
  mutate(diff=AccAir-AirTempAcc_emerg)%>%
  mutate(MeanAirTempTrifo=(AccAir-AirTempAcc_emerg)/(DAS5T-DAS50E))


str (df4)
```

just select columns of interest and change dataframe name 

```{r}


dfokPo <- df4%>%
  select(Plot,Block,SowingDate,Cultivar,SowTreat,MeanAirTempTrifo,DAS5T)%>%
  mutate(Rate=1/DAS5T)%>%
  mutate(SowingDate=dmy(SowingDate))

str(dfokPo)
```

Then graph results  (remember that here each replicate has a different temperature set... need to average to get a simpler graph 
## complete graph 
```{r, fig.height=5, fig.width=8}
dfokPo %>%
  group_by(MeanAirTempTrifo, SowingDate, SowTreat, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  #ggplot(aes(x=MeanAirTempTrifo, y=mean, colour=(Cultivar), shape=factor(Cultivar) )) +
 ggplot(aes(x=MeanAirTempTrifo, y=mean,colour=SowTreat, shape=Cultivar)) +
  geom_point(size=5) +
  #geom_line() +
  
  labs(y="Rate to five trifoliate stage (1/days)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()+
  xlim(0,20)+
  ylim(0,0.04)+
  #facet_wrap(~Cultivar,ncol=3, scales = "free")+
  xlab(expression(Mean~Air~Temperature~"("^"o"*"C)"))+
  theme(axis.text.x=element_text(angle = 0, hjust = 0, size= 12))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 12))+
  theme(axis.title.y=element_text(angle = 90, hjust = 0, size= 14))+
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 14))+
  theme(legend.text=element_text(size=12))
  
# then merge the dataframes to find out the mean temperature 


```



```{r}


  
  write.table(dfokPo,"df_DAS5Trifo_MeanAirTPo.txt")

```



Graph rate and SowTreat

```{r}
#Graph 

  dfokPo %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 50% leaf emergence  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

```




End of this script Calc 3. 
Move to script 4 to include temperatures  
