---
title: "Flowering 6CV autmn sown treatments"
author: "CT"
date: "26.08.2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
Aim: to calculate the percent of plants in specific open flower phase for blog purpose.
It is a  subset of S7 in open flower. 

ATTENTION : this script has to run as continuous as the final dataframe generated (df_flower) is saved for further analysis and other scripts 

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```
Read file and adjust formats 

```{r loadFile}

setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\BlogFlowIv2")

getwd()

#create file
df_flower <- read.table("F_Flower.txt",header=TRUE)

colnames(df_flower)[1] <- "Cultivar" # fix bug of extra characters in name

# convert to date format
df_flower <- df_flower %>%
mutate(Date=dmy(Date),SowingD=dmy(SowingD), 
       Percent=(S1+S2+S3+S4+S5)/5*100)

str(df_flower)
head(df_flower)
tail(df_flower)
```

Check data 
```{r}
summary(df_flower)
```

Subset SowTreat S7 ( March 2016) 


```{r}

  #subset SowTreat, Variable(Open)

df_A <- df_flower %>%
subset(SowTreat=="S7")%>%
subset(Variable=="Petal" )
  
 #select columns of interest 
df_B <- df_A%>%
dplyr::select (Cultivar:Variable, Percent)

  

```
Graph for all cultivars 

```{r Graph, fig.height= 5, fig.width= 8}

 df_B%>%
  group_by(DAS,Date,Cultivar,SowTreat,Variable)%>%
  summarise_each(funs(mean)) %>%
  #select(Variable,Percent,Cultivar,Date,SowTreat)%>%
  #filter(Variable=="Bud") %>%
  ggplot(aes(x=DAS, y=Percent)) + 
  geom_line(aes(colour=Cultivar)) +
  #acet_grid(SowTreat~Cultivar, scales = "free")+
  #facet_grid(Cultivar~., scales = "free")+
  geom_abline(intercept = 50, slope = 0) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


```

Select Monti, Woog and Leura to compare and use date as x Axis


```{r}

 df_B%>%
   group_by(DAS,Date,Cultivar,SowTreat,Variable)%>%
  summarise_each(funs(mean)) %>%
  #select(Variable,Percent,Cultivar,Date,SowTreat)%>%
  filter(Cultivar=="Monti"|Cultivar=="Woogenellup" 
        |Cultivar=="Denmark" ) %>%
  #filter(Cultivar=="Woogenellup")%>%
  #filter(Cultivar=="Leura")%>%
  ggplot(aes(x=Date, y=Percent)) + 
  #geom_line(aes(colour=Cultivar)) +
  geom_smooth (aes(colour=Cultivar),alpha=0.01)+
  #acet_grid(SowTreat~Cultivar, scales = "free")+
  #facet_grid(Cultivar~., scales = "free")+
  geom_abline(intercept = 20, slope = 0) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlab("Date ") +
  ylab("Percent of plants with open flowers (%)") +
  
  scale_y_continuous(limits = c(0, 80))+
  scale_x_date(date_breaks = "1 week", 
                 #labels=date_format("ymd"),
                 limits = as.Date(c('2016-08-20','2016-12-01')))
 
```

If need to write the data as a table ... 


```{r}
# save final DF
write.table(df_B, "df_flowBlog.txt")

```






End of this script.



