---
title: "Flowering 6CV autmn sown treatments"
author: "CT"
date: "26.08.2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
Aim: to calculate the percent of plants in specific open flower phase for blog purpose.
It is a  subset of S7 in open flower. 

ATTENTION : this script has to run as continuous as the final dataframe generated (df_flower) is saved for further analysis and other scripts 

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library (scales)

```
Read file and adjust formats 

```{r loadFile}

setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\BlogFlowIv2")

getwd()

#create file
df_flower <- read.table("df_bud_flow_bur_simple.txt",header=TRUE)

#colnames(df_flower)[1] <- "Cultivar" # fix bug of extra characters in name

# convert to date format
df_flower <- df_flower %>%
mutate(Date=ymd(Date),SowingD=ymd(SowingD))
       
       #Percent=(S1+S2+S3+S4+S5)/5*100)

str(df_flower)
# head(df_flower)
# tail(df_flower)
```

Check data 
```{r}
summary(df_flower)
```

Subset SowTreat S7 ( March 2016) 


```{r}

  #subset SowTreat, Variable(Open)

df_A <- df_flower %>%
subset(SowTreat=="S7")%>%
subset(Variable=="Flowering" )
  
 #select columns of interest 
df_B <- df_A%>%
dplyr::select (Cultivar:Variable, Percent, Date)

  
# note that column flowering has three values for each DAS (3 merged categories) need to make the average of the 3. 
df_B1<-df_B%>%
  group_by(DAS,Date,Cultivar,SowTreat,Variable)%>%
  summarise_each(funs(mean))

write.table(df_B1, "df_Blog4.txt")
#used this one to create Blog graph on 08.09.2017

```





Graph for all cultivars 

```{r Graph, fig.height= 5, fig.width= 8}

 df_B%>%
  group_by(DAS,Date,Cultivar,SowTreat,Variable)%>%
  summarise_each(funs(mean)) %>%
  #select(Variable,Percent,Cultivar,Date,SowTreat)%>%
  #filter(Variable=="Bud") %>%
  ggplot(aes(x=DAS, y=Percent)) + 
  geom_line(aes(colour=Cultivar)) +
  #acet_grid(SowTreat~Cultivar, scales = "free")+
  #facet_grid(Cultivar~., scales = "free")+
  geom_abline(intercept = 50, slope = 0) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))


```

Select Monti, Woog and Leura to compare and use date as x Axis


```{r}

 df_B%>%
  mutate (Date= as.Date(Date))%>%
  group_by(DAS,Date,Cultivar,SowTreat,Variable)%>%
  summarise_each(funs(mean)) %>%
  #select(Variable,Percent,Cultivar,Date,SowTreat)%>%
  filter(Cultivar=="Monti"|Cultivar=="Woogenellup" 
        |Cultivar=="Denmark" ) %>%
  #filter(Cultivar=="Woogenellup")%>%
  #filter(Cultivar=="Leura")%>%
  ggplot(aes(x=Date, y=Percent)) + 
  #geom_line(aes(colour=Cultivar)) +
  geom_smooth (aes(colour=Cultivar),alpha=0.01)+
  #acet_grid(SowTreat~Cultivar, scales = "free")+
  #facet_grid(Cultivar~., scales = "free")+
  geom_abline(intercept = 20, slope = 0) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlab("Date ") +
  ylab("Percent of plants with open flowers (%)") +
  
  scale_y_continuous(limits = c(0, 100))+
  scale_x_date(date_breaks = "1 week", 
                 labels=date_format("%d-%m"),
                 limits = as.Date(c('2016-08-22','2016-12-01')))
  #scale_x_date(labels = date_format("%d-%m"))
```

If need to write the data as a table ... 


```{r}
#save final DF 



```


make it cumulative number of open flowers using df_B1



```{r}


# create an ID of each chunk
df_temp <- df_B1 %>%
  dplyr::select(-Block) %>%
  mutate(codeID = as.factor(paste0(Plot)))

# define unique factors to loop around
codesNames <- unique(df_temp$codeID)

# prepare final df to store data
df_final <- data.frame()

# loop
for(i in 1:length(codesNames)) {
  
  df_sub <- data.frame() # empty df
  
  df_sub <- df_temp %>%
    subset(codeID == codesNames[i]) %>% # segment one unique combination
    mutate(codeID = factor(codeID)) %>%
    arrange(DAS) %>%
    mutate(Flo_cum = cumsum(Percent))%>%
    mutate(CumulativePercent = Flo_cum/1)
  
  df_final <- rbind(df_final,df_sub)
    
  
  df_final <- rbind(df_final,df_sub)
  
}

summary(df_final)



```


then graph the cumulative until 100 % of plants with flower 

```{r}

df_C <- df_final %>%
  subset(Flo_cum > -1 & Flo_cum < 105)


#save final DF 

write.table(df_C, "df_flowBlog3.txt")

df_C%>%
  mutate (Date= as.Date(Date))%>%
  group_by(DAS,Date,Cultivar,SowTreat,Variable)%>%
  summarise_each(funs(mean)) %>%
  #select(Variable,Percent,Cultivar,Date,SowTreat)%>%
  filter(Cultivar=="Monti"|Cultivar=="Woogenellup" 
        |Cultivar=="Denmark" ) %>%
  #filter(Cultivar=="Woogenellup")%>%
  #filter(Cultivar=="Leura")%>%
  ggplot(aes(x=Date, y=Flo_cum)) + 
  #geom_line(aes(colour=Cultivar)) +
  geom_smooth (aes(colour=Cultivar),alpha=0.01)+
  #acet_grid(SowTreat~Cultivar, scales = "free")+
  #facet_grid(Cultivar~., scales = "free")+
  geom_abline(intercept = 20, slope = 0) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
  xlab("Date ") +
  ylab("Percent of plants with open flowers (%)") +
  
  scale_y_continuous(limits = c(0, 150))+

  scale_x_date(date_breaks = "1 week", 
                 labels=date_format("%d-%m"),
                 limits = as.Date(c('2016-08-22','2016-12-01')))
  #scale_x_date(labels = date_format("%d-%m"))

```


End of this script.



