---
title: "Seed Yield Analysis"
author: "CT"
date: "Friday, June 2, 2017"
output: html_document
---
This script :
reads the file with burrs and seeds quantification form Poukawa site 



```{r}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
```

Read File 

```{r, echo=FALSE}

#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldPok")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedYieldPok")

getwd()
file <- read.table("SeedBurrYieldPok2.txt",header=TRUE)
head(file)
summary(file)
```

Calculations 

```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    Date = dmy(Date),
    SowingD = dmy(SowingD)
  )

str(file)
summary(file)
head(file)

```


```{r}

df<- file %>%
  dplyr::select(Cultivar,SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seedNo) %>%
  mutate(SeedsNo_m2 = ((seedNo/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,Block,SeedsNo_m2)

  df <- as.data.frame(df)
head(df)

```
Re start

```{r, fig.height=5, fig.width=10}

#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%

  group_by(Cultivar, SowTreat,Depth) %>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x=Cultivar, y=(SeedsNo_m2_mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsNo_m2_mean-SeedsNo_m2_sd/2,
                    ymax=SeedsNo_m2_mean+SeedsNo_m2_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    labs(y= "Seed Number per 1 m2")+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))


```


do the graph with SE (std/1.73)


```{r, fig.height=5, fig.width=10}

#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df_SE <- df %>%
    #mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
  group_by(Cultivar, SowTreat,Depth) %>%
  summarise_all(funs(mean,sd)) %>%
  mutate(SE=SeedsNo_m2_sd/1.73)
    
  df_SE %>%
  ggplot(aes(x=Cultivar, y=(SeedsNo_m2_mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsNo_m2_mean-SE/2,
                    ymax=SeedsNo_m2_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    labs(y= "Seed number per m2")+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))


```

graph as sum of below and above seeds (ESA paper 2018)

```{r,fig.height=5, fig.width=10}

 DfSum <- df %>%
  group_by(Cultivar, SowTreat, Block)%>%
  dplyr::select(SeedsNo_m2)%>%
  summarise_all(funs(sum))

#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df_SE <- DfSum %>%
    #mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_all(funs(mean,sd)) %>%
  mutate(SE=SeedsNo_m2_sd/1.73)
    
  df_SE %>%
    filter(SowTreat!="S1",SowTreat!="S5")%>%
    ungroup%>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5"),labels=c("February", "March", "May", "July", "August")))%>%
     #added ....here mutate cultivar labels for poster  
   mutate (Cultivar= factor(Cultivar, levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),labels=c("A", "D", "L", "M", "N","W")))%>%
  ggplot(aes(x=Cultivar, y=(SeedsNo_m2_mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsNo_m2_mean-SE/2,
                    ymax=SeedsNo_m2_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 18) +
    theme_bw()+
    scale_fill_brewer(palette="Blues")+
  facet_grid(.~SowTreat, scales="free") +
    ylab(expression(Number~of~seeds/m^"2")) +
  theme_bw()+
theme(axis.text.y = element_text( size = 11))+
  #theme(axis.title.y = element_text(face="bold", size=14))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0.2,size = 22)) +
  theme(text = element_text(size = 22))

#ggsave("plot_SeedNumberperm2Pok.png", width=12, height=6, dpi=400)
```

## Re graph This is the one good for the Poster! 

```{r,fig.height=5, fig.width=10}

 DfSum <- df %>%
  group_by(Cultivar, SowTreat, Block)%>%
  dplyr::select(SeedsNo_m2)%>%
  summarise_all(funs(sum))

#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df_SE <- DfSum %>%
    #mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_all(funs(mean,sd)) %>%
  mutate(SE=SeedsNo_m2_sd/1.73)
    
  df_SE %>%
    filter(SowTreat!="S1",SowTreat!="S5")%>%
    ungroup%>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5"),labels=c("February", "March", "May", "July", "August")))%>%
     #added ....here mutate cultivar labels for poster  
   mutate (Cultivar= factor(Cultivar, levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),labels=c("A", "D", "L", "M", "N","W")))%>%
  ggplot(aes(x=Cultivar, y=(SeedsNo_m2_mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
    geom_bar(aes(fill=Cultivar), colour="black",stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsNo_m2_mean-SE/2,
                    ymax=SeedsNo_m2_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 24) +
   theme_bw()+
  facet_grid(.~SowTreat, scales="free") +
    scale_fill_brewer(palette="Blues")+
    labs(y= "Seed weight (mg) ")+
   theme(axis.text.y = element_text( size = 24))+
  #theme(axis.title.y = element_text(face="bold", size=14))+
   theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0.2,size = 24)) +
 # theme(text = element_text(size = 22))+
    
    #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
    #margin y axis
   theme (axis.title.y = element_text( margin = margin(t=0,r=10,b=0,l=0)))+
    
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
   theme(text = element_text(size = 24))+
    
   scale_y_continuous(expand = c(0, 0), limits = c(0, 40000))+
    ylab(expression(Number~of~seeds/m^"2")) 

ggsave("plot_SeedNumberperm2Pok.png", width=16, height=6, dpi=400)
```

 



```{r, fig.height=5, fig.width=10}

# Graph Seeds perm2 again same format as seed yield 


 DfSum <- df %>%
  group_by(Cultivar, SowTreat, Block)%>%
  dplyr::select(SeedsNo_m2)%>%
  summarise_all(funs())

#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df_SE <- DfSum %>%
    #mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_all(funs(mean,sd)) %>%
  mutate(SE=SeedsNo_m2_sd/1.73)
  
 df_SE %>%
    filter(SowTreat!="S1",SowTreat!="S5")%>%
   ungroup%>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5"),labels=c("February", "March", "May", "July", "August")))%>%
   #here mutate cultivar labels for poster  
   mutate (Cultivar= factor(Cultivar, levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),labels=c("A", "D", "L", "M", "N","W")))%>%
   
  ggplot(aes(x=Cultivar, y=(SeedsNo_m2_mean), fill=Cultivar)) +
    geom_bar(aes(fill=Cultivar), colour="black",stat="identity",position = dodge_x) +
  #geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsNo_m2_mean-SE/2,
                    ymax=SeedsNo_m2_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)    +
  theme_grey(base_size = 24) +
  theme_bw()+
#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),

axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
   
   scale_y_continuous(expand = c(0, 0), limits = c(0, 40000))+
   
   #margin y axis
   theme (axis.title.y = element_text( margin = margin(t=0,r=20,b=0,l=0)))+
   
      scale_fill_brewer(palette="Blues")+
     facet_grid(.~SowTreat, scales="free") +
    #labs(y= "Seed yield (kg/ha)")+
   ylab(expression(Number~of~seeds/m^"2")) +
theme(axis.text.x=element_text(angle = +0, hjust = 0.5,vjust=0.2 ,size=24))+
  theme(axis.text.y=element_text(angle = 0, hjust=0.5,vjust=0.2,size = 24)) +
theme(text = element_text(size = 24))

 #ggsave("plot_seedyield.png", width=16, height=6, dpi=300)
 
```




graph as per SowTreat

```{r}
#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  #mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%

  group_by(SowTreat) %>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x=SowTreat, y=(SeedsNo_m2_mean), fill=SowTreat)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsNo_m2_mean-SeedsNo_m2_sd/2,
                    ymax=SeedsNo_m2_mean+SeedsNo_m2_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  #facet_grid(Depth~SowTreat, scales="free") +
    labs(y= "Seed Number per 1 m2")+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
  theme(text = element_text(size = 14))

```



```{r, fig.height=5, fig.width=10}
#Calculate Seed yield : number g seeds per m2 and then yield kg seeds per ha
head (file)

df1<- file %>%
  dplyr::select(Cultivar, SowingD, SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seed_weight_g) %>%
  #stop here calculate kg seed / ha
  mutate(Seedskg_ha = (((seed_weight_g/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2)*10 ) 

  df1 <- as.data.frame(df1)
summary(df1)

write.table(df1, "SeedYielPok2.txt", row.names=FALSE)

```

This graph is already with SE (std/1.73)


```{r, fig.heigt=5, fig.width=10}
# Graph Seed kg ha

#barplot 
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df1 %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  group_by(Cultivar, SowTreat,Depth) %>%
  summarise_all(funs(mean,sd)) %>%
  ggplot(aes(x= Cultivar, y=(Seedskg_ha_mean),fill= Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=Seedskg_ha_mean-(Seedskg_ha_sd/1.73)/2,
                    ymax=Seedskg_ha_mean+(Seedskg_ha_sd/1.73)/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
  theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    labs(y= "Seed yield (kg per ha)")+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
theme(text = element_text(size = 20))
```

graph not considering depth - sum above and below samples 
for coour look at : http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/

```{r, fig.height=5, fig.width=10}

# Graph Seed kg ha

#barplot 
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df2 <-df1 %>%
  group_by(Cultivar, SowTreat,Block) %>%
  dplyr::select(Seedskg_ha) %>%
  summarise_all(funs(sum)) 
    
  df3 <-df2 %>%
  group_by(Cultivar, SowTreat) %>%
  dplyr::select(Seedskg_ha) %>%
    summarise_all(funs(mean,sd)) 
  
 df3 %>%
    filter(SowTreat!="S1",SowTreat!="S5")%>%
   ungroup%>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5"),labels=c("February", "March", "May", "July", "August")))%>%
   #here mutate cultivar labels for poster  
   mutate (Cultivar= factor(Cultivar, levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),labels=c("A", "D", "L", "M", "N","W")))%>%
   
  ggplot(aes(x= Cultivar, y=mean,fill= Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=mean-(sd/1.73)/2,
                    ymax=mean+(sd/1.73)/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
  theme_bw()+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
      scale_fill_brewer(palette="Blues")+
     facet_grid(.~SowTreat, scales="free") +
    labs(y= "Seed yield (kg per ha)")+
theme(axis.text.x=element_text(angle = +0, hjust = 0.5,vjust=0.2 ))+
theme(text = element_text(size = 22))

 #ggsave("plot_seedyield.png", width=12, height=6, dpi=300)
```

try with black contour bars 
geom_bar(aes(x=a, y=b, fill=c), colour="black", stat="identity")


```{r, fig.height=5, fig.width=10}

# Graph Seed kg ha

#barplot 
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df2 <-df1 %>%
  group_by(Cultivar, SowTreat,Block) %>%
  dplyr::select(Seedskg_ha) %>%
  summarise_all(funs(sum)) 
    
  df3 <-df2 %>%
  group_by(Cultivar, SowTreat) %>%
  dplyr::select(Seedskg_ha) %>%
    summarise_all(funs(mean,sd)) 
  
 df3 %>%
    filter(SowTreat!="S1",SowTreat!="S5")%>%
   ungroup%>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5"),labels=c("February", "March", "May", "July", "August")))%>%
   #here mutate cultivar labels for poster  
   mutate (Cultivar= factor(Cultivar, levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),labels=c("A", "D", "L", "M", "N","W")))%>%
   
  ggplot(aes(x= Cultivar, y=mean)) +
  geom_bar(aes(fill=Cultivar), colour="black",stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=mean-(sd/1.73)/2,
                    ymax=mean+(sd/1.73)/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 24) +
  theme_bw()+
#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),

axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
   
   scale_y_continuous(expand = c(0, 0), limits = c(0, 5000))+
   
   #margin y axis
   theme (axis.title.y = element_text( margin = margin(t=0,r=20,b=0,l=0)))+
   
      scale_fill_brewer(palette="Blues")+
     facet_grid(.~SowTreat, scales="free") +
    labs(y= "Seed yield (kg/ha)")+
theme(axis.text.x=element_text(angle = +0, hjust = 0.5,vjust=0.2 ,size=24))+
  theme(axis.text.y=element_text(angle = 0, hjust=0.5,vjust=0.2,size = 24)) +
theme(text = element_text(size = 24))

 ggsave("plot_seedyield.png", width=16, height=6, dpi=400)
 
```





```{r, gig.height=15, fig.width=15, warning=FALSE}

  df1 %>%
  group_by(Cultivar, SowingD, Depth) %>%
  dplyr::select(Seedskg_ha) %>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x=SowingD, y=(mean))) +
  geom_point(aes(colour=Cultivar), size=6) +
  geom_line(aes(colour=Cultivar)) +
  geom_errorbar(aes(ymin=mean-sd/2,
                    ymax=mean+sd/2), width=0.2)   +
  theme_grey(base_size = 20) +
  theme_bw()+
  theme(text = element_text(size = 24))+
  facet_grid(Depth~., scales="free") +
    labs(y= "Seed yield (kg/ha)")

```


