---
output:
  word_document: default
  html_document: default
---
---
title: "SeedPer1Burr  "
author: "CT"
date: "29.08.2017"
output:
  word_document: default
  pdf_document: default
  
  #This script  reads the SeedBurrYieldPok2, calculates the number of seed per 1 burr and performs ANOVA 
---

```{r loadLibraries, warning=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(rgr)
```


Aim: Statistics for variable Seed Number per 1 m2. 


```{r loadFile}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldPok")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedYieldPok")

getwd()

#REading the dataframe generated in SeedYieldProject1 script

df_seedY<- read.table("SeedBurrYieldPok2.txt",header=TRUE)
head(df_seedY)
summary(df_seedY)


```


Define formats 
```{r}

# define factors and formats
file <- df_seedY %>%
  mutate(
    #Plot = as.factor(Plot),
    #Date = dmy(Date),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    SowTreat = as.factor(SowTreat)
  )

str(file)
#summary(file)
#head(file)




```

Calculate the number of seed in one burr
Include a column in data frame and remove extra columns in data frame 
```{r}
df<- file %>%
  dplyr::select(Cultivar,SowTreat,Block,
                Depth,
                bur_no_subSample,
                seedNo) %>%
  mutate(SeedsPerBur = ((seedNo/bur_no_subSample)*1)) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,Block,SeedsPerBur)

  df <- as.data.frame(df)
```


If need a graph create a new chunk here. 


Here only need to change df name as selection of fields were previously done. 

```{r, fig.height=5, fig.width= 10}

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  group_by(Cultivar, SowTreat,Depth) %>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x= Cultivar, y=(SeedsPerBur_mean),fill= Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsPerBur_mean-SeedsPerBur_sd/2,
                    ymax=SeedsPerBur_mean+SeedsPerBur_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
  theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    labs(y= "Number of seeds per 1 Burr ")+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
theme(text = element_text(size = 20))


```


Here graph with the SE (std/1.73)

```{r, fig.height=5, fig.width=10}
dge_x <- position_dodge(width = 0.9)


  dfSE <- df %>%
    group_by(Cultivar, SowTreat,Depth) %>%
      summarise_all(funs(mean,sd)) %>%
    mutate(SE=SeedsPerBur_sd/1.73)
  
   dfSE %>% 
  ggplot(aes(x= Cultivar, y=(SeedsPerBur_mean),fill= Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsPerBur_mean-SE/2,
                    ymax=SeedsPerBur_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
  theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    labs(y= "Number of seeds per burr ")+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
theme(text = element_text(size = 18))


```


graph as per mean desconsider depth 

```{r, fig.height=5, fig.width=10}

dge_x <- position_dodge(width = 0.9)


  dfSE2 <- df %>%
    group_by(Cultivar, SowTreat) %>%
      summarise_all(funs(mean,sd)) %>%
    mutate(SE=SeedsPerBur_sd/1.73)
  
   dfSE2 %>%
     filter(SowTreat!="S1",SowTreat!="S5")%>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5"),labels=c("February", "March", "May", "July", "August")))%>%
  ggplot(aes(x= Cultivar, y=(SeedsPerBur_mean),fill= Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsPerBur_mean-SE/2,
                    ymax=SeedsPerBur_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
  theme_bw()+
      scale_fill_brewer(palette="Blues")+
  facet_grid(.~SowTreat, scales="free") +
    labs(y= "Number of seeds per inflorescence")+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12)) +
theme(text = element_text(size = 18))
   
   #save
   
   ggsave("plot_SeedPerBurr.png", width=12, height=6, dpi=400)
```





Compare sowing date experiments (overview)



```{r}

summary(df)

df_seedYS6 <- df
#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Then anova all 

```{r}
#ANOVA

#my.anova <- aov(SeedsPerBur ~ Cultivar*Depth + Block, data = file.subset)
my.anova <- aov(SeedsPerBur ~ SowTreat*Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ Depth + Block, data = file.subset)
summary(my.anova)
```
Get the means for SowTReat 

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
```




Here ANOVA according S. Saville advice : LSD test unprotected by sowing date individually.
Use filter to sub set data (sowing date)
Start wit S1 

```{r}
#Filter  S1, S2, S3, S4 , S5 
summary(df)

df_seedYS6 <- df %>%
 ## (Use this filter for ESA 2018) filter(SowTreat!="S1", SowTreat!="S5")
  filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change the variables (comment out/in) to get mean values and ANOVA info. 
Select :SowTreat or Depth or Cultivar 
S1
```{r}
#ANOVA

#my.anova <- aov(SeedsPerBur ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ SowTreat*Cultivar + Block, data = file.subset)
my.anova <- aov(SeedsPerBur ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means for desired variables
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
```

S2

```{r}
#Filter  S1, S2, S3, S4 , S5 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

S2 summary anova 

```{r}
#ANOVA

my.anova <- aov(SeedsPerBur ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ SowTreat*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ Depth + Block, data = file.subset)
summary(my.anova)
```

S2 means 
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
```
S3 filter

```{r}
#Filter  S1, S2, S3, S4 , S5 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)
```

S3 anova
```{r}
#ANOVA

#my.anova <- aov(SeedsPerBur ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(SeedsPerBur ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ Depth + Block, data = file.subset)
summary(my.anova)
```
S3 multiple comparison 

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
```

S4filter

```{r}
#Filter  S1, S2, S3, S4 , S5 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)
```

S4 anova
```{r}
#my.anova <- aov(SeedsPerBur ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(SeedsPerBur ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ Depth + Block, data = file.subset)
summary(my.anova)
```

S4 means 
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
```
S5 filter

```{r}
#Filter  S1, S2, S3, S4 , S5 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  filter(SowTreat=="S5")
  


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)
```

S5 anova

```{r}
my.anova <- aov(SeedsPerBur ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ SowTreat*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ Depth + Block, data = file.subset)
summary(my.anova)
```

S5 multiple comparisons

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
```



End of script.
