---
output:
  word_document: default
  html_document: default
---
---
title: "kg seeds per ha in  Poukawa  "
author: "CT"
date: " 29.08.2017 "
output:
  word_document: default
  pdf_document: default
  
  #This script  reads the SeedBurrYieldPok2 and performs ANOVA on variate seedyield
---

```{r loadLibraries, warning=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(rgr)
```


Aim: Statistics for variable kg Seed/ha. 


```{r loadFile}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldPok")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedYieldPok")
getwd()

#REading the dataframe generated in SeedYieldProject1 script

df_seedY<- read.table("SeedBurrYieldPok2.txt",header=TRUE)
head(df_seedY)
summary(df_seedY)


```


Define formats 
```{r}

# define factors and formats
file <- df_seedY %>%
  mutate(
    #Plot = as.factor(Plot),
    #Date = dmy(Date),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    SowTreat = as.factor(SowTreat)
  )

str(file)
summary(file)
head(file)

```

Calculate the yield 

```{r}
df1<- file %>%
  dplyr::select(Cultivar, Block,SowingD, SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seed_weight_g) %>%
  #stop here calculate kg seed / ha
  mutate(Seedskg_ha = (((seed_weight_g/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2)*10 ) 

  df1 <- as.data.frame(df1)
summary(df1)
```




Now go for Stats for variate Seed yield 
Select columns to be used 

Here only need to change df name as selection of fields were previously done. 



```{r}


df <- df1 %>%
  dplyr::select(Cultivar,SowTreat, Depth,Block,Seedskg_ha)
# 
#   df <- as.data.frame(df)
 head(df)


```

For graphics check  SeedYieldProject1 script 

Here ANOVA according S. Saville advice : LSD test unprotected by sowing date individually.
Use filter to sub set data (sowing date)

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df 
#%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change the variables (comment out/in) to get mean values and ANOVA info. 
Select :SowTreat or Depth or Cultivar 

```{r}
#ANOVA

my.anova <- aov(Seedskg_ha ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ SowTreat*Depth + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means for desired variables. Remember to sum up the values of seed yield (above + below) 
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat", "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```
Considered the sum values for total kg of seeds per hectare (kg seeds -- std) 

S1:Above	221.2449	296.23187
S1:Below	31.60278	44.05156
Sum	252.84768	340.28343
S2:Above	574.54945	644.14118
S2:Below	173.68471	288.69963
Sum	748.23416	932.84081
S3:Above	1468.81588	976.11587
S3:Below	136.57364	133.74631
Sum	1605.38952	1109.86218
S4:Above	1437.39442	1375.16921
S4:Below	76.87602	68.19927
Sum	1514.27044	1443.36848
S5:Above	311.27763	352.08012
S5:Below	58.54861	80.10387
Sum	369.82624	432.18399

-----------------------------------------------------------------

Now check each sowing date 
S1 filter 

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
  filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)

```

ANOVA S1
```{r}
#ANOVA

#my.anova <- aov(Seedskg_ha ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(Seedskg_ha ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Depth + Block, data = file.subset)
summary(my.anova)
```

means S1
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat", "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```
S2 
```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)
```

s2 anova

```{r}
#ANOVA

#my.anova <- aov(Seedskg_ha ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(Seedskg_ha ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Depth + Block, data = file.subset)
summary(my.anova)
```
means S2
```{r}

#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat", "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S3filter 
```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  filter(SowTreat=="S3")
#-------------------------------------------------
# anova 
file <- df_seedYS6
file.subset <- file 
head(file.subset)
summary(file.subset)
```

S3 anova
```{r}
#ANOVA
#my.anova <- aov(Seedskg_ha ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(Seedskg_ha ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Depth + Block, data = file.subset)
summary(my.anova)
```


S3 means 

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat", "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S4

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  filter(SowTreat=="S4")
#-------------------------------------------------
# anova 
file <- df_seedYS6
file.subset <- file 
head(file.subset)
summary(file.subset)
```

S4

```{r}
#ANOVA
#my.anova <- aov(Seedskg_ha ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(Seedskg_ha ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Depth + Block, data = file.subset)
summary(my.anova)
```

S4
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat", "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```


S5filter  

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  filter(SowTreat=="S5")
#-------------------------------------------------
# anova 
file <- df_seedYS6
file.subset <- file 
head(file.subset)
summary(file.subset)
```

S5 Anova
```{r}
#ANOVA
#my.anova <- aov(Seedskg_ha ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(Seedskg_ha ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Depth + Block, data = file.subset)
summary(my.anova)
```

S5 means 

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat", "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```





End of script.
