---
output:
  word_document: default
  html_document: default
---
---
title: "SeedPer1m2 Poukawa  "
author: "CT"
date: " 29.08.2017 "
output:
  word_document: default
  pdf_document: default
  
  #This script  reads the SeedNumberm2_Pok and performs ANOVA on variate seednumber per1m2
---

```{r loadLibraries, warning=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(rgr)
```


Aim: Statistics for variable Seed Number per 1 m2. 


```{r loadFile}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\Gitsubclover\\SeedYieldPok")
getwd()

#REading the dataframe generated in SeedYieldProject1 script

df_seedY<- read.table("SeedBurrYieldPok2.txt",header=TRUE)
head(df_seedY)
summary(df_seedY)


```


Define formats 
```{r}

# define factors and formats
file <- df_seedY %>%
  mutate(
    #Plot = as.factor(Plot),
    #Date = dmy(Date),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    SowTreat = as.factor(SowTreat)
  )

str(file)
summary(file)
head(file)




```

Calculate the number of seeds in 1 m2 

```{r}
df<- file %>%
  dplyr::select(Cultivar,SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seedNo) %>%
  mutate(SeedsNo_m2 = ((seedNo/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,Block,SeedsNo_m2)

  df <- as.data.frame(df)
head(df)
```



Now go for Stats for variate SeedsNo per 1m2

Here only need to change df name as selection of fields were previously done. 

```{r}


#   dplyr::select(Cultivar,SowTreat,
#                 Depth,Block)
# 
#   df <- as.data.frame(df)
# head(df)


```

For graphics check  SeedYieldProject1 script 

Here ANOVA according S. Saville advice : LSD test unprotected by sowing date individually.
Use filter to sub set data (sowing date)

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df 
#%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change the variables (comment out/in) to get mean values and ANOVA info. 
Select :SowTreat or Depth or Cultivar 

```{r}
#ANOVA

#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ SowTreat*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means for desired variables. Remember to sum up the values of seed number (above + below) 
```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c( "SowTreat", "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```
Considered the sum values for total number of seeds per 1 m2 

S1:Above	2575.9	2651.6
S1:Below	502.8	565.0
Sum	3078.7	3216.6
S2:Above	8292.5	7983.9
S2:Below	2038.4	2718.8
Sum	10330.9	10702.7
S3:Above	19421.6	10899.0
S3:Below	1666.4	1212.1
Sum	21088.0	12111.1
S4:Above	16760.7	8824.6
S4:Below	1063.3	848.4
Sum	17824.0	9673.0
S5:Above	5384.2	5940.6
S5:Below	800.3	1056.0
Sum	6184.6	6996.6
-----------------------------------------------------------------

Now check each sowing date 
S1 filter 

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
  filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)

```

ANOVA
```{r}
#ANOVA

#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```

means 
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat", "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)
```

s2 anova

```{r}
#ANOVA

#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```
means S2
```{r}

#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat", "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S3filter 
```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  filter(SowTreat=="S3")
#-------------------------------------------------
# anova 
file <- df_seedYS6
file.subset <- file 
head(file.subset)
summary(file.subset)
```

S3 anova
```{r}
#ANOVA
#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```


S3 means 

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat", "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S4

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  filter(SowTreat=="S4")
#-------------------------------------------------
# anova 
file <- df_seedYS6
file.subset <- file 
head(file.subset)
summary(file.subset)
```

S4

```{r}
#ANOVA
#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```

S4
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat", "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```


S5filter  

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  filter(SowTreat=="S5")
#-------------------------------------------------
# anova 
file <- df_seedYS6
file.subset <- file 
head(file.subset)
summary(file.subset)
```

S5 Anova
```{r}
#ANOVA
#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```

S5 means 

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat", "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```





End of script.
