---
output:
  word_document: default
  html_document: default
---
---
title: "TSW  "
author: "CT"
date: " renewed 05.08.2017 (original 28.12 2016)"
output:
  word_document: default
  pdf_document: default
  
  #Aim: this script  reads the SeedBurrYield data and calculates the TSW (g)for Poukawa
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(rgr)
```

Aim: calculate the Thousand seed weight for each treatment combination (Sowing date, cultivar, depth)


```{r loadFile}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldPok")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedYieldPok")

getwd()



df_seedY<- read.table("SeedBurrYieldPok2.txt",header=TRUE)
head(df_seedY)
summary(df_seedY)


```


Define formats  
```{r}

# define factors and formats
file <- df_seedY %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    Date = dmy(Date),
    SowingD = dmy(SowingD)
  )

str(file)
summary(file)
head(file)




```

Calculate the TSW and create a column with TSW. 
Select columns of interest for ANOVA.

```{r}

df<- file %>%
  dplyr::select(Cultivar,SowTreat,Block,
                Depth,seed_weight_g,seedNo) %>%
  mutate(TSW = ((seed_weight_g/seedNo)*1000)) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,Block,TSW)

  df <- as.data.frame(df)
head(df)


```

Data visualisation: effects of sowing date and cultivar on TSW.


```{r}

#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df %>%
  mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
  group_by(Cultivar, SowTreat,Depth) %>%
  summarise_all(funs(mean,sd)) %>%
  ggplot(aes(x=Cultivar, y=(TSW_mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=TSW_mean-TSW_sd/2,
                    ymax=TSW_mean+TSW_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    labs(y= "Thousand Seed weight (g) ")+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))


```
graph with the SE 

```{r, fig.height=5,fig.width=10}

cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  
se <-df %>%
  mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
  group_by(Cultivar, SowTreat,Depth) %>%
  summarise_all(funs(mean,sd)) %>%
  mutate(SE=TSW_sd/1.73)
  
  se %>%
  ggplot(aes(x=Cultivar, y=(TSW_mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=TSW_mean-SE/2,
                    ymax=TSW_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    labs(y= "Thousand Seed weight (g) ")+
theme(axis.text.x=element_text(angle = +90, size= 16, hjust = 0))+
  theme(text = element_text(size = 16))


```


Then make as mean not considering depth ad keep S1 out 


```{r, fig.height=5,fig.width=10}

cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  
se2 <-df %>%
  mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_all(funs(mean,sd)) %>%
  mutate(SE=TSW_sd/1.73)
  
  se2 %>%
    filter(SowTreat!="S1",SowTreat!="S5")%>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5"),labels=c("February", "March", "May", "July", "August")))%>%
  ggplot(aes(x=Cultivar, y=(TSW_mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=TSW_mean-SE/2,
                    ymax=TSW_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(.~SowTreat, scales="free") +
    scale_fill_brewer(palette="Blues")+
    labs(y= "Seed weight (mg) ")+
theme(axis.text.y = element_text( size = 11))+
  #theme(axis.title.y = element_text(face="bold", size=14))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12)) +
  theme(text = element_text(size = 18))
  
    #theme(legend.position="bottom")

  #save
   
   ggsave("plot_SeedWeight.png", width=12, height=6, dpi=400)

```

Analysis overview by sowing date

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df%>%
## (Use this filter for ESA 2018) 
filter(SowTreat!="S1", SowTreat!="S5")
#no filter here 

```


```{r}
# anova 
file <- df_seedYS6
file.subset <- file 

head(file.subset)
summary(file.subset)

```

```{r}
#ANOVA
#my.anova <- aov(TSW ~ SowTreat + Block, data = file.subset)
my.anova <- aov(TSW ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(TSW ~ Depth + Block, data = file.subset)
summary(my.anova)
```

No differences among SowTreatments (P= 0.387)
S1	5.89	3.4

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "SowTreat","Cultivar"), alpha= 0.05, p.adj="none"))
```
Analysis overview by Cultivar 
Cultivar highly significant (P< 0.001) no differences by Depth 

```{r}
#ANOVA
#my.anova <- aov(TSW ~ SowTreat + Block, data = file.subset)
my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(TSW ~ Depth + Block, data = file.subset)
summary(my.anova)
```


```{r}
(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
```


Here ANOVA according S. Saville advice: LSD test unprotected by sowing date individually.
Use filters to select treatments. 
S1
```{r}
df_seedYS6 <- df %>%
  filter(SowTreat=="S1")
# anova 
file <- df_seedYS6
file.subset <- file 

head(file.subset)
summary(file.subset)


```
Anova S1
continue from here 

```{r}
#my.anova <- aov(TSW ~ SowTreat + Block, data = file.subset)
my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(TSW ~ Depth + Block, data = file.subset)
summary(my.anova)

```

S1 means separation
```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))

```

Then do S2 

```{r}
#Filter  S1, S2, S3, S4 , S5 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change  the variables to get mean values. 
Use :comment out or in to select  SowTreat or Depth or Cultivar 

```{r}
#ANOVA
#my.anova <- aov(TSW ~ SowTreat + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(TSW ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means when applicable (P<0.05)
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
```

S3

```{r}
#Filter  S1, S2, S3, S4 , S5 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)

```

S3 Anova
```{r}
#ANOVA
#my.anova <- aov(TSW ~ SowTreat + Block, data = file.subset)
my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(TSW ~ Depth + Block, data = file.subset)
summary(my.anova)
```
S3 means separation

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
```

S4

```{r}
#Filter  S1, S2, S3, S4 , S5 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)
```

S4 anova
```{r}
#ANOVA
#my.anova <- aov(TSW ~ SowTreat + Block, data = file.subset)
my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(TSW ~ Depth + Block, data = file.subset)
summary(my.anova)
```

S4 means

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
```

S5 

```{r}
#Filter  S1, S2, S3, S4 , S5 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  filter(SowTreat=="S5")
  #filter(SowTreat=="S7")

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)
```

S5ANOVA 

```{r}
#ANOVA
#my.anova <- aov(TSW ~ SowTreat + Block, data = file.subset)
my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(TSW ~ Depth + Block, data = file.subset)
summary(my.anova)
```
S5 means 

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
```


End of this script. 
