---
output:
  word_document: default
  html_document: default
---
---
title: "Seed Number and yield   "
author: "CT"
date: "Thursday, FEbruary 19, 2016"
output:
  word_document: default
  pdf_document: default
  
  #This script  reads the SeedBurrYield and tests Data first anaylsed in SeedYieldProject1
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(rgr)
```


```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldPok")
getwd()



df_seedY <- read.table("SeedYielPok2.txt",header=TRUE)
head(df_seedY)
summary(df_seedY)


```


Here ANOVA according S. Saville advice : LSD test unprotected by sowing date individually

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df_seedY)
```


## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5")

sdIndex <- unique(df_seedY$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```


then loop anova if significant 

## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_seedY %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(Seedskg_ha ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


 if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
   print("***Sig Cultivar***") 
   print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```



```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df_seedY)

df_seedYS2 <- df_seedY %>%
  #filter(SowingD=="2015-06-24")
  #filter(SowingD=="2015-07-28")
  #filter(SowingD=="2015-09-15")
  #filter(SowingD=="2015-11-05")
  #filter(SowingD=="2016-02-17")
  filter(SowingD=="S2")

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS2


file.subset <- file 

head(file.subset)
summary(file.subset)


```

```{r}
#ANOVA
my.anova <- aov(Seedskg_ha ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ SowTreat + Block, data = file.subset)

summary(my.anova)
```

Then use multiple comparisons of means
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
```


