---
title: "Seed Breakdown  Test base line corrected"
author: "CT"
date: "21 March 2017" ## revised in 15.11.2017 (ESA paper 2018)
output: html_document
---
This script reads the baselined corrected spectra for 3 cultivars (Antas, Monti and Narrikup) in 3 different incubation times (0, 42, 84) consider the data with reps generated in script 2 (Correct 2 Reps ) 

```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)

```



```{r readData}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Spectra")
getwd()

#create file
df_sp <- read.table("BreakBaselined3cv.txt",header=TRUE)

#head(df_sp)

summary(df_sp)
```
##select columns of interest Cultivar Incubation days rep AbsValue Wavenumber

```{r}
df_sp1<-df_sp%>%
  dplyr::select(Cultivar:Rep, AbsValue,WaveNumber)
  
```

## Get the mean value for Absorbance 

```{r}
df_sp2<-df_sp1%>%
  group_by(Cultivar,IncubationDays,WaveNumber)%>%
  dplyr::select(AbsValue)%>%
  summarise_all(funs(mean))%>%
  mutate(Absorbance=AbsValue)%>%
  dplyr::select(-AbsValue)
  
  str(df_sp2)
  
```



## Graph it all , 

```{r, fig.height=5, fig.width=15}

##select only Antas and Monti
df_sp3 <-df_sp2 %>%
    filter(Cultivar!="N")
    


df_sp3%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
    facet_grid(Cultivar ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)
  


```

then get the single spectra before file was averaged (per seed)

```{r,fig.height=5, fig.width=10}

df_spSeed <- read.table("BreakBaseLineReps.txt",header=TRUE)

str(df_spSeed)

##select only Antas and Monti ESA 2018 subset 
dfSpSeed1<-df_spSeed %>%
  select(-RowNo,-Hardness)%>%
  filter(Cultivar!="N")

write.table(dfSpSeed1, "SeedSpectraESA2018.txt")
```





##Graph the subset wavenumbers 2900-2700 


```{r, fig.height=4, fig.width=8}

##select only Antas and Monti
df_sp4 <-df_sp3 %>%
    subset(WaveNumber>2800 & WaveNumber<3000 )
    


df_sp4%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),400))+
    facet_grid(Cultivar ~.) +
  theme_bw()+
      scale_x_reverse()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)
```


```{r, fig.height=5, fig.width=10}

df_sp %>%
  
  ggplot(aes(x=Wavelength,y=Absorbance))+
  geom_line(aes(colour=IncubationDays))+
  #geom_line(aes(colour= factor(IncubationDays)))+
  scale_colour_gradient(low="red")+
    theme_bw()+
   #scale_x_continuous(breaks=seq(min(df_sp$Wavelength),max(df_sp$Wavelength),400))+
  scale_x_reverse()+
 # scale_x_reverse(lim=c(650,4000))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)
  #geom_vline(intercept = 1000, slope = 0)
    #scale_x_date(labels = date_format("%b-%Y"))



```

MAke the difference between incubation days 0 and 84 ; find bands which change the most. filter out 42.Use difference absolute and %. 

```{r}

df1 <- df_sp  %>%         
  mutate(IncubationDays=factor(paste0("A_",IncubationDays)))%>%
  filter(IncubationDays!="A_42") %>%
  tidyr::spread(IncubationDays,Absorbance)%>%
  mutate(DiffAbsolute=A_0-A_84,DiffRelative=DiffAbsolute/A_0*100) #%>%
#Now gather values 
#tidyr::gather("Varname", "Varvalue",A_0:DiffRelative )
summary(df1)
```


Now graph the differences 

```{r}
df2 <-df1 %>%
  filter(Cultivar!="Narrikup")%>%
  subset(DiffRelative>5 & DiffRelative<100)

df2 %>%
  ggplot(aes(x=Wavelength,y=DiffRelative))+
  geom_line(aes(colour=Cultivar))+
  theme_bw()+
 # facet_grid(.~Cultivar,scales="free") +
  scale_x_reverse()+
  geom_abline(intercept = 0, slope = 0)
 
   
  
```


#