---
title: "Framework for PCA analysis "
author: "CT"
date: "15.01.2017
output: html_document
---
- This script is an attempt normalisation using the hyperspec package by the minimum absorbance method. 
- Take the baseline corrected values and normalise by the minimum absvalue


```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)
library(calibrate)
library (hyperSpec)
```


```{r}


setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Spectra")
getwd()

#create file
df_sp <- read.table("BreakBaseLined3cv.txt",header=TRUE)
#df_sp <- read.table("BreakBaseLineReps.txt",header=TRUE)

str(df_sp)
```


Perform normalisation per minimum absorbance value 


```{r}

#here normalise by the minimum absvalue

df_spNorm<- df_sp%>%
  group_by(Cultivar, IncubationDays, Rep) %>%
   mutate(AbsValue=AbsValue-min(AbsValue))%>%
  mutate(Absorbance=AbsValue)%>%
  dplyr::select(-AbsValue)
         

```



```{r}

##select only Antas and Monti
df_spNorm <-df_spNorm %>%
    filter(Cultivar!="N")
    

df_spNorm%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
    facet_grid(Cultivar ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)
```

Perform normalisation using min and max method 
AbsValue=AbsValue-min(AbsValue)/max(AbsValue)-min(AbsValue))



```{r}

#here normalise by the max and minimum absvalue

df_spNorm2<- df_sp %>%
  group_by(Cultivar, IncubationDays, Rep) %>%
   mutate(AbsValue=AbsValue-min(AbsValue)/max(AbsValue)-min(AbsValue))%>%
  mutate(Absorbance=AbsValue)%>%
  dplyr::select(-AbsValue)
  
   df_spNorm2 %>%
     ##select only Antas and Monti
    filter(Cultivar!="N")%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
    facet_grid(Cultivar ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)      

   
  
```


Use mean of Absorbance Norm2 

```{r}

#Get mean values for cultivar and incub days 
df_spNorm3 <-df_spNorm2 %>%
     ##select only Antas and Monti
  filter(Cultivar!="N")%>%
  group_by(WaveNumber, Cultivar,IncubationDays)%>%
  dplyr::select(Absorbance)%>%
  summarise_all(funs(mean))
   
  
       

str(df_spNorm3)


```

```{r fig.height=5, fig.width=15}


    

df_spNorm3%>%
  ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
   scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
    facet_grid(Cultivar ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)


```




```{r}


 summary (df_spNorm2)
```


