---
title: "Framework for PCA analysis "
author: "CT"
date: "15.01.2017
output: html_document
---
- This script is an attempt to plot the baselined and Normalised spectra of Antas and Monti 




```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)
library(calibrate)
library(factoextra)
```


```{r}


setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Spectra")
getwd()

#create file
#This is baselined corrected only 
#df_sp <- read.table("BreakBaseLined3cv.txt",header=TRUE)

#df_sp <- read.table("UntreatedESA.txt",header=TRUE)

#this tests the baseline and normalised dataset 
df_sp <- read.table("UntreatedESANormalised.txt",header=TRUE)
str(df_sp)

tail(df_sp)

```

Now need to tidy wavenumbers and absorbance in columns as per other scripts 
 $ Cultivar      : Factor w/ 3 levels "A","M","N": 1 1 1 1 1 1 1 1 1 1 ...
 $ IncubationDays: int  0 0 0 0 0 0 0 0 0 0 ...
 $ WaveNumber    : num  650 652 654 656 658 ...
 $ Absorbance    : num  0.0169 0.0176 0.0183 0.0191 0.0197 ...

```{r}
df_sp1 <- df_sp%>%
gather(key = 'Wavenumber', value = 'Absorbance', X3997.741:X649.8979)

#ok now how can I remove the X from the string here ?? 
  
str(df_sp1)
df_sp1 %>%
  mutate(Wavenumber = as.Date.numeric(Wavenumber))
```


```{r}

df_sp2<-df_sp1%>%
  group_by(Cultivar,IncubationDays, Wavenumber)%>%
  dplyr::select(Absorbance)%>%
  summarise_all(funs(mean))
  
  
  str(df_sp2)

  write.table(df_sp2,"NormSpectraESA2018.txt")
```


Then read the worked data table 
```{r}


df_worked <- read.table("UntreatedESANormalised_2.txt",header=TRUE)

str(df_worked)
```

hum i did not like this one!!! Too weak abssorbance sig  nal!! 

```{r}

df_worked%>%
   ggplot(aes(x=Wavenumber2,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  scale_x_continuous(breaks=round(seq(min(df_worked$Wavenumber2),max(df_worked$Wavenumber2),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.01)) +
  geom_abline(intercept = 0.1, slope = 0)

```



```{r readData}


#Need to convert the cultivar names to numbers as numeric




#compute PCA
#res.pca <- prcomp (df_sp.active[,apply(df_sp.active, 2, var, na.rm=TRUE) != 0])

res.pca <- prcomp(df_sp.activeU, scale = TRUE)
#res.pca <- prcomp(df_sp.active)
```

## Visualize eigenvalues (scree plot). Show the percentage of variances explained by each principal component. 

```{r, fig.height=5, fig.width=10}

 

fviz_eig(res.pca)


```


##Graph of individuals. Individuals with a similar profile are grouped together.  

FIX ME: how to change columns for the incubation days !!
```{r, fig.height=5, fig.width=10}

# fviz_pca_ind(res.pca,
#              col.ind = "cos2", # Color by the quality of representation
#              #col.ind = "Cultivar", 
#              gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
#              #gradient.cols = c("#00AFBB", "#E7B800"),
#              geom="point",
#              
#              repel = TRUE     # Avoid text overlapping
#              )


fviz_pca_ind(res.pca,
             col.ind = "cos2", # Color by the quality of representation
             #gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             geom = c("point", "text"),
             label = "all", invisible = "none", labelsize = 6,pointsize = 4,
             repel = TRUE     # Avoid text overlapping
             )+
             scale_color_gradient2(low="white", mid="blue",
      high="dark blue", midpoint=0.6)+
   theme_bw()+
  # theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 20))+
  # theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 20))+
  theme(axis.text.y = element_text( size = 26))+
theme(axis.title.y = element_text(face="bold", size=24))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 22,face="bold"))+
theme(axis.title.x = element_text( face="bold", size=24))+
#if need the axes labels 
  xlab(expression(PC1~"(72%)"))+ 
  ylab(expression(PC2~"(17%)")) +
  xlim(-12, 12)+
  ylim(-4, 4)

   
 
```
Separate by groups for Antas 

```{r, fig.height=6, fig.width=12}
fviz_pca_ind(res.pca, label="none", habillage=df_sp.activeU$IncubationDays)
df_sp.activeU

# Add ellipses
p <- fviz_pca_ind(res.pca, label="none", habillage=df_sp.activeU$IncubationDays,
             addEllipses=TRUE, ellipse.level=0.2, alpha=0.9)+
  scale_color_brewer(palette="Set1") +
     theme_minimal()
print(p)
```


PC contributions 

```{r, fig.height=5 , fig.width=30}

# Contributions of variables to PC1
fviz_contrib(res.pca, choice = "var", axes = 1, top = 20)
# Contributions of variables to PC2
fviz_contrib(res.pca, choice = "var", axes = 2, top = 20)

```




## Graph of variables. Positive correlated variables point to the same side of the plot. Negative correlated variables point to opposite sides of the graph.

```{r, fig.height=5, fig.width=10}

fviz_pca_var(res.pca,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
             )



```

Biplot of individuals and variables 

```{r}

fviz_pca_biplot(res.pca, repel = TRUE,
                col.var = "#2E9FDF", # Variables color
                col.ind = "#696969"  # Individuals color
                )
```

Access to PCA results 

```{r}
library(factoextra)
# Eigenvalues
eig.val <- get_eigenvalue(res.pca)
eig.val
  
# Results for Variables
res.var <- get_pca_var(res.pca)
res.var$coord          # Coordinates
res.var$contrib        # Contributions to the PCs
res.var$cos2           # Quality of representation 
# Results for individuals
res.ind <- get_pca_ind(res.pca)
res.ind$coord          # Coordinates
res.ind$contrib        # Contributions to the PCs
res.ind$cos2           # Quality of representation 
   
  
```


Predict using PCA
In this section, we'll show how to predict the coordinates of supplementary individuals and variables using only the information provided by the previously performed PCA.

Supplementary individuals
Data: rows 24 to 27 and columns 1 to to 10 [in decathlon2 data sets]. The new data must contain columns (variables) with the same names and in the same order as the active data used to compute PCA.

```{r}


# Data for the supplementary individuals
ind.sup <- decathlon2[24:27, 1:10]
ind.sup[, 1:6]
```

Predict the coordinates of new individuals data. Use the R base function predict():


```{r}

ind.sup.coord <- predict(res.pca, newdata = ind.sup)
ind.sup.coord[, 1:4]
```


```{r, fig.height=5, fig.width=10}
# Plot of active individuals
p <- fviz_pca_ind(res.pca, repel = TRUE)
# Add supplementary individuals
fviz_add(p, ind.sup.coord, color ="blue")
```




Supplementary variables
Qualitative / categorical variables
The data sets decathlon2 contain a supplementary qualitative variable at columns 13 corresponding to the type of competitions.

Qualitative / categorical variables can be used to color individuals by groups. The grouping variable should be of same length as the number of active individuals (here 23).

```{r}

groups <- as.factor(decathlon2$Competition[1:23])
fviz_pca_ind(res.pca,
             col.ind = groups, # color by groups
             palette = c("#00AFBB",  "#FC4E07"),
             addEllipses = TRUE, # Concentration ellipses
             ellipse.type = "confidence",
             legend.title = "Groups",
             repel = TRUE
             )


```


Theory behind PCA results
PCA results for variables
Here we'll show how to calculate the PCA results for variables: coordinates, cos2 and contributions:

var.coord = loadings * the component standard deviations
var.cos2 = var.coord^2
var.contrib. The contribution of a variable to a given principal component is (in percentage) : (var.cos2 * 100) / (total cos2 of the component)


```{r}
# Helper function 
#::::::::::::::::::::::::::::::::::::::::
var_coord_func <- function(loadings, comp.sdev){
  loadings*comp.sdev
}
# Compute Coordinates
#::::::::::::::::::::::::::::::::::::::::
loadings <- res.pca$rotation
sdev <- res.pca$sdev
var.coord <- t(apply(loadings, 1, var_coord_func, sdev)) 
head(var.coord[, 1:4])
```


```{r}
# Compute Cos2
#::::::::::::::::::::::::::::::::::::::::
var.cos2 <- var.coord^2
head(var.cos2[, 1:4])
```


```{r}
# Compute contributions
#::::::::::::::::::::::::::::::::::::::::
comp.cos2 <- apply(var.cos2, 2, sum)
contrib <- function(var.cos2, comp.cos2){var.cos2*100/comp.cos2}
var.contrib <- t(apply(var.cos2,1, contrib, comp.cos2))
head(var.contrib[, 1:4])
```


PCA results for individuals
ind.coord = res.pca$x
Cos2 of individuals. Two steps:
Calculate the square distance between each individual and the PCA center of gravity: d2 = [(var1_ind_i - mean_var1)/sd_var1]^2 + .+ [(var10_ind_i - mean_var10)/sd_var10]^2 + .+..
Calculate the cos2 as ind.coord^2/d2
Contributions of individuals to the principal components: 100 * (1 / number_of_individuals)*(ind.coord^2 / comp_sdev^2). Note that the sum of all the contributions per column is 100


```{r}
# Coordinates of individuals
#::::::::::::::::::::::::::::::::::
ind.coord <- res.pca$x
head(ind.coord[, 1:4])
```


```{r}
# Cos2 of individuals
#:::::::::::::::::::::::::::::::::
# 1. square of the distance between an individual and the
# PCA center of gravity
center <- res.pca$center
scale<- res.pca$scale
getdistance <- function(ind_row, center, scale){
  return(sum(((ind_row-center)/scale)^2))
  }
d2 <- apply(decathlon2.active,1,getdistance, center, scale)
# 2. Compute the cos2. The sum of each row is 1
cos2 <- function(ind.coord, d2){return(ind.coord^2/d2)}
ind.cos2 <- apply(ind.coord, 2, cos2, d2)
head(ind.cos2[, 1:4])
```


```{r}
# Contributions of individuals
#:::::::::::::::::::::::::::::::
contrib <- function(ind.coord, comp.sdev, n.ind){
  100*(1/n.ind)*ind.coord^2/comp.sdev^2
}
ind.contrib <- t(apply(ind.coord, 1, contrib, 
                       res.pca$sdev, nrow(ind.coord)))
head(ind.contrib[, 1:4])
```


