---
title: "Framework for multivariate lineaar analysis "
author: "CT"
date: "05.08.2017
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
- This script is the hardseedneds analysis with selected spectra of the three cultivars based on PCA laodings  



```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)
library(calibrate)
library(factoextra)
```

# Get the segmented spectra  and continue here 
```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SpectraThermalTreatment")
getwd()

df_G <- read.table("NormalSnipped_CvByIncub.txt",header=TRUE)

str(df_G)
```

Here take the mean of each replicate !!Analyse at the replicate level!  To get the following treatment combinations : 
A01
A02
A03
M01
M02
M03
A841
A842
A843
M841
M842
M843


```{r}

df_G <-df_G %>%
  dplyr::select(Cultivar, IncubationDays,Wavenumber,AbsorbanceNorm)




str(df_G)
```


##Now you have the dataframe organized vertically: spread the wavenumber horizontally 



```{r}

#-------------here is just to produce a matrix to export to Unscrambleror PCA 

dftemp <- df_G %>%
 
#filter(Wavenumber %in% 852:3599) %>% # select only wavelengths of interest
mutate(Wavenumber=factor(Wavenumber))%>%

mutate(IncubationDays=factor(IncubationDays))

str(dftemp)

Q<-dftemp%>%
  #group_by(Wavenumber,Cultivar,IncubationDays)%>%
  group_by(Wavenumber,Cultivar, IncubationDays)%>%
  dplyr::select(AbsorbanceNorm)%>%
  summarise_all(funs(mean))

summary(dftemp)

df_U <- Q %>%
   tidyr::spread(Wavenumber, AbsorbanceNorm)# %>%
 #  mutate(RN=paste0(Cultivar,"_",Block))

#row.names(df_U) <-  df_U$RN    
```

```{r}
head(df_U)[,1:4]
```



## -------------here select key bands : 2930 2855 (lipids)
##1770, 1745, 1732 (cutin/suberin)
##1610
##1441
##1250
##1025
##897

  

```{r readData}


df_U_select<-df_U%>%
  dplyr:: select(Cultivar,IncubationDays, "896.7437", "1025.952","1249.656","1440.575","1610.281","1731.776","1745.275", "1770.345", "2854.152","2931.291")


```


Then bring the dataframe with  Sdbreak:meanSDhardSDbreak.txt


```{r}



df_Break <- read.table("MeanSDBReakThermalTreat_SelectSpectra.txt",header=TRUE)


str(df_Break)

df_Break_select <-df_Break %>%
  filter(IncubatioDays=="84")  

```


```{r, fig.height=5, fig.width=10}


##general regression all cultivars
##BA1026+BA1250+BA1441+BA1610+BA1732+BA1745+BA1770+BA2854+BA2931


summary(lm(SDbreak ~ X2855+ X2932, df_Break_select))
summary(lm(SDbreak ~  X2855, df_Break_select))

#summary(lm(SDmax ~ BA1610+BA1732+BA1745+BA1770, df_HardSpectra))
#summary(lm(SDmax ~ BA2854+BA2931, df_HardSpectra))

##summary(lm(HardAccum ~ RainIrrig+RH+PET+SoilTemp, df_All))


```


Check with SDmax transformed 



```{r}


summary(lm(Sdmaxtrans ~ BA897+BA1026+BA1250+BA1441, df_HardSpectra))

summary(lm(Sdmaxtrans ~ BA1610+BA1732+BA1745+BA1770, df_HardSpectra))


summary(lm(Sdmaxtrans ~ BA2854+BA2931, df_HardSpectra))

summary(lm(Sdmaxtrans ~ BA2854, df_HardSpectra))

summary(lm(Sdmaxtrans ~   BA897 + BA1250 +BA1441, df_HardSpectra))


summary(lm(Sdmaxtrans ~ BA897+BA1250+BA1441, df_HardSpectra))



```
```{r}



summary(lm(SDbreak ~ BA897+BA1026+BA1250, Antas))
summary(lm(SDbreak ~ BA1610+BA1732+BA1745+BA1770, df_HardSpectra))
summary(lm(SDbreak ~ BA2854+BA2931, df_HardSpectra))

summary(lm(SDbreak ~ BA1250 +BA2854+BA2931, df_HardSpectra))
summary(lm(SDbreak ~ BA1250+BA897, df_HardSpectra))


DLW<-df_HardSpectra%>%
  filter(Cultivar=="Denmark"|Cultivar=="Leura"|Cultivar=="Woogenellup")
summary(lm(SDbreak ~ BA2854, DLW))


AMN<-df_HardSpectra%>%
  filter(Cultivar=="Antas"|Cultivar=="Monti"|Cultivar=="Narrikup")
summary(lm(SDbreak ~ BA2854+BA2931,AMN ))



```
############################

```{r}

df_HardSpectra%>%
  
  ggplot(aes(x=BA897,y=SDbreak)) +
  geom_point(aes(colour=Cultivar, shape=Cultivar), size=5) +
  #geom_text(aes(label=Cultivar, colour=Cultivar),hjust=0, vjust=-2, size=8) +
  theme_bw()+
  #xlim(-10,10) +
  #ylim(-4,4) +
  theme(text = element_text(size=20)) +
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  geom_abline(slope = 0)





```



####################################

##This loop checks the lm for all Periods first  for Hardcumm
## (Sdmax)
 
 
```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_HardSpectra$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_HardSpectra %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required 
  
    
    summary(lm(SDbreak ~ BA897+BA1026+BA1250+BA1441, df_HardSpectra))
   
  #print
    

print(summary(lm(SDbreak ~ BA897+BA1026+BA1250+BA1441, df_HardSpectra)))
   

  } 


```







```{r}
str(res.pca)

```

# loadings are rotation in pca object

##source: http://www.sthda.com/english/articles/31-principal-component-methods-in-r-practical-guide/118-principal-component-analysis-in-r-prcomp-vs-princomp/

```{r}
summary(res.pca$rotation)
```

Graph the loading of PC1 and PC2 

```{r, warning=FALSE}

LabelColumn<-row.names(res.pca$rotation)

load.graph <- res.pca$rotation %>%
  as.data.frame() %>%
  dplyr::select(PC1,PC2) %>%
  mutate(WaveLength=as.numeric(LabelColumn)) %>%
  na.omit() %>% # FIXME: Cultivar and block come with value ??????
  gather("PC","PC_Value",PC1:PC2) %>%
  mutate(PC=factor(PC))

summary(load.graph)



  
```





```{r, fig.width=12}
load.graph %>%
   
        mutate(Show_WL = ifelse(WaveLength <1799,"Region 2",
                          ifelse(WaveLength > 2802,"Region 1","NotShow"))) %>%
  
  filter(Show_WL != "NotShow") %>%
  ggplot(aes(x=WaveLength,y=PC_Value)) +
  geom_line() +
  geom_abline(slope=0,intercept=0, linetype=2, colout="darkgrey")+
  #xlab(expression(Wavenumber~"(cm"^"-1"*")"))+
  ylab("Loadings")+
  xlab("X-variables")+
   scale_x_reverse()+
  theme_bw() +
  facet_grid(PC~Show_WL, scale="free")+
  #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
  
  
   #remove grid lines 
    
    #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),

axis.line = element_line(colour = "black"))+
      #make panels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
  
theme(text = element_text(size = 26))+
theme(axis.text.y = element_text( size = 20))+
    theme(axis.title.y = element_text(face="bold", size=26))+
     #scale_y_continuous(breaks = c(seq(from = 0, to = 1.25, by = 0.01)))+
theme(axis.text.x=element_text(angle = 25, hjust=0.5,vjust=0,size = 22))+
theme(axis.title.x = element_text( size=26,face="bold"))+
  theme(axis.line.x = element_line(colour = 'black', size = 3))+
  theme(axis.line.y = element_line(colour = 'black', size = 3))+
  
   #margin y axis
  theme(axis.title.y = element_text(margin =margin(t = 0, r = 20, b = 0, l = 0)))+
  theme(axis.text.x = element_text(margin = margin(b=15)))+
  #tick labels 
  ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))
 

  
  
 ggsave("plot_LoadingsPC1PC2_S2_6Cv.tiff", width=20, height=10, dpi=400)
  
```


Separate the loading regions 


```{r, fig.width=10}


Region850_1800 <-load.graph %>%
   
    subset(WaveLength<2800)
  
min_x <- min(min(Region3600_2800$WaveLength))
max_x <- max(max(Region3600_2800$WaveLength))

  
  Region3600_2800  %>%
  ggplot(aes(x=WaveLength,y=PC_Value)) +
  geom_line() +
  geom_abline(slope=0,intercept=0, linetype=2, colour="darkgrey")+
  labs(x= "x variables ([PC1_59%] _ [PC2_20%])")+
   ylab(" Loadings ")+
  #scale_x_reverse()+
  #scale_x_continuous(breaks = c(seq(from = 1000, to = 1800, by = 100)))+
  
  theme_bw() +
  facet_grid(PC~., scale="free")+
   #facet_grid(PC~. )+
    scale_x_continuous(limits = c(min_x, max_x))+
    
  #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2)) +
  
  
   #remove grid lines 
    
    #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),

axis.line = element_line(colour = "black"))+
     #make panels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
  
theme(text = element_text(size = 26))+
theme(axis.text.y = element_text( size = 20))+
    theme(axis.title.y = element_text(face="bold", size=26))+
     #scale_y_continuous(breaks = c(seq(from = 0, to = 1.25, by = 0.01)))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 26))+
theme(axis.title.x = element_text( size=26,face="bold"))+
  theme(axis.line.x = element_line(colour = 'black', size = 3))+
  theme(axis.line.y = element_line(colour = 'black', size = 3))+
  
  #tick labels 
  ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))
  
  
  
  
  
 #ggsave("plot_SpectraS2_PCA2019.25.05_LoadingsPC1PC2_REgion850_1800_6Cv.tiff", width=20, height=10, dpi=400)
  
```

## get only the most important bands in each PC


```{r}

Selected <-load.graph%>%
  subset(PC_Value > 0.01)%>%
  mutate(Wavenumber=WaveLength)

```



##Graph of individuals. Individuals with a similar profile are grouped together. 

## Add PC1 = 57% and PC2= 28% in axis titles 


```{r}

fviz_pca_ind(res.pca,
             label = "all", invisible = "none", labelsize = 6,pointsize = 4,)+

  #xlim(-60, 60)+
  ylim(-30, 20)+
#if need the axes labels 
  xlab(expression(PC1~"(59%)"))+ 
  ylab(expression(PC2~"(21%)")) 



```




```{r}

summary (res.pca)




```





```{r, fig.height=5, fig.width=10}


str(res.pca$scale)

fviz_pca_ind(res.pca,
             #col.ind = "cos2", # Color by the quality of representation
             geom = c("point","text"),
             label = "all", invisible = "none", labelsize = 7,pointsize = 4,
             repel = TRUE     # Avoid text overlapping
             )+
             scale_color_gradient2(low="light green", mid="green",
      high="black", midpoint=0.6)+
   theme_bw()+
   theme(axis.text.y = element_text( size = 26))+
theme(axis.title.y = element_text(face="bold", size=26))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 26,face="bold"))+
theme(axis.title.x = element_text( face="bold", size=26))+
  
  
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
#if need the axes labels 
  xlab(expression(PC1~"(59%)"))+ 
  ylab(expression(PC2~"(21%)")) +
  xlim(-50, 50)+
  ylim(-30, 20)

   
 
```


##SAve the plot graph 

```{r}

#ggsave("S2_plot_PC1andPC2.png", width=14, height=7, dpi=500)

```





PC contributions 

```{r, fig.height=5 , fig.width=30}

# Contributions of variables to PC1
fviz_contrib(res.pca, choice = "var", axes = 1, top = 20)
# Contributions of variables to PC2
fviz_contrib(res.pca, choice = "var", axes = 2, top = 20)

```




## Graph of variables. Positive correlated variables point to the same side of the plot. Negative correlated variables point to opposite sides of the graph.

```{r, fig.height=5, fig.width=10}

fviz_pca_var(res.pca,
             col.var = "contrib", # Color by contributions to the PC
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"),
             repel = TRUE     # Avoid text overlapping
             )



```

Biplot of individuals and variables 

```{r}

fviz_pca_biplot(res.pca, repel = TRUE,
                col.var = "#2E9FDF", # Variables color
                col.ind = "#696969"  # Individuals color
                )
```

Access to PCA results 

```{r}
library(factoextra)
# Eigenvalues
eig.val <- get_eigenvalue(res.pca)
eig.val
  
# Results for Variables
res.var <- get_pca_var(res.pca)
res.var$coord          # Coordinates
res.var$contrib        # Contributions to the PCs
res.var$cos2           # Quality of representation 
# Results for individuals
res.ind <- get_pca_ind(res.pca)
res.ind$coord          # Coordinates
res.ind$contrib        # Contributions to the PCs
res.ind$cos2           # Quality of representation 
   
  
```

################ Least discriminant analysis attempt ###########



```{r}


    LDA<-LDA <- merge( Selected, df_G , by="Wavenumber")%>%
    dplyr::select(-WaveLength, -PC_Value,-PC)

LDASpread<-LDA%>%
  group_by(Cultivar, Wavenumber,Block)%>%
  dplyr::select(AbsorbanceNorm)%>%
  summarise_all(funs(mean))%>%
tidyr::spread(Wavenumber, AbsorbanceNorm)%>%
  ungroup()%>%
  dplyr::select(-Block)

head(LDASpread)



```


source : https://rstudio-pubs-static.s3.amazonaws.com/35817_2552e05f1d4e4db8ba87b334101a43da.html

```{r}

library(MASS)
Cultivar.lda <- lda(Cultivar ~ ., data=LDASpread )

Cultivar.lda

str(Cultivar.lda)

```

Proportion of trace is the is the percentage separation achieved by each discriminant function. For example, for the cultivR data we get the same values as just calculated (53% and 31.%).


```{r, fig.height=6; fig.width=12}


Cultivar.lda.values <- predict(Cultivar.lda)
str(Cultivar.lda.values)

v<-as.vector(Cultivar.lda.values$class)

plot(Cultivar.lda.values$x[,1],Cultivar.lda.values$x[,2]) # make a scatterplot
text(Cultivar.lda.values$x[,1],Cultivar.lda.values$x[,2],v,cex=0.7,pos=4,col="red") # add labels


```

```{r, fig.width=15}

v <-as.vector(Cultivar.lda.values$class) # get labels
df <-as.data.frame(Cultivar.lda.values$x) # get data

# graph labels + data
df %>%
  mutate(Cultivars=v) %>%
  ggplot(aes(x=LD1,y=LD2)) +
  geom_point(aes(colour=Cultivars, shape=Cultivars), size=5) +
  geom_text(aes(label=Cultivars, colour=Cultivars),hjust=0, vjust=-2, size=8) +
  theme_bw()+
  xlim(-10,10) +
  ylim(-4,4) +
  theme(text = element_text(size=20)) +
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  geom_abline(slope = 0)+
  
  
```




Predict using PCA
In this section, we'll show how to predict the coordinates of supplementary individuals and variables using only the information provided by the previously performed PCA.

Supplementary individuals
Data: rows 24 to 27 and columns 1 to to 10 [in decathlon2 data sets]. The new data must contain columns (variables) with the same names and in the same order as the active data used to compute PCA.

```{r}


# Data for the supplementary individuals
ind.sup <- decathlon2[24:27, 1:10]
ind.sup[, 1:6]
```

Predict the coordinates of new individuals data. Use the R base function predict():


```{r}

ind.sup.coord <- predict(res.pca, newdata = ind.sup)
ind.sup.coord[, 1:4]
```


```{r, fig.height=5, fig.width=10}
# Plot of active individuals
p <- fviz_pca_ind(res.pca, repel = TRUE)
# Add supplementary individuals
fviz_add(p, ind.sup.coord, color ="blue")
```




Supplementary variables
Qualitative / categorical variables
The data sets decathlon2 contain a supplementary qualitative variable at columns 13 corresponding to the type of competitions.

Qualitative / categorical variables can be used to color individuals by groups. The grouping variable should be of same length as the number of active individuals (here 23).

```{r}

groups <- as.factor(decathlon2$Competition[1:23])
fviz_pca_ind(res.pca,
             col.ind = groups, # color by groups
             palette = c("#00AFBB",  "#FC4E07"),
             addEllipses = TRUE, # Concentration ellipses
             ellipse.type = "confidence",
             legend.title = "Groups",
             repel = TRUE
             )


```


Theory behind PCA results
PCA results for variables
Here we'll show how to calculate the PCA results for variables: coordinates, cos2 and contributions:

var.coord = loadings * the component standard deviations
var.cos2 = var.coord^2
var.contrib. The contribution of a variable to a given principal component is (in percentage) : (var.cos2 * 100) / (total cos2 of the component)


```{r}
# Helper function 
#::::::::::::::::::::::::::::::::::::::::
var_coord_func <- function(loadings, comp.sdev){
  loadings*comp.sdev
}
# Compute Coordinates
#::::::::::::::::::::::::::::::::::::::::
loadings <- res.pca$rotation
sdev <- res.pca$sdev
var.coord <- t(apply(loadings, 1, var_coord_func, sdev)) 
head(var.coord[, 1:4])
```


```{r}
# Compute Cos2
#::::::::::::::::::::::::::::::::::::::::
var.cos2 <- var.coord^2
head(var.cos2[, 1:4])
```


```{r}
# Compute contributions
#::::::::::::::::::::::::::::::::::::::::
comp.cos2 <- apply(var.cos2, 2, sum)
contrib <- function(var.cos2, comp.cos2){var.cos2*100/comp.cos2}
var.contrib <- t(apply(var.cos2,1, contrib, comp.cos2))
head(var.contrib[, 1:4])
```


PCA results for individuals
ind.coord = res.pca$x
Cos2 of individuals. Two steps:
Calculate the square distance between each individual and the PCA center of gravity: d2 = [(var1_ind_i - mean_var1)/sd_var1]^2 + .+ [(var10_ind_i - mean_var10)/sd_var10]^2 + .+..
Calculate the cos2 as ind.coord^2/d2
Contributions of individuals to the principal components: 100 * (1 / number_of_individuals)*(ind.coord^2 / comp_sdev^2). Note that the sum of all the contributions per column is 100


```{r}
# Coordinates of individuals
#::::::::::::::::::::::::::::::::::
ind.coord <- res.pca$x
head(ind.coord[, 1:4])
```


```{r}
# Cos2 of individuals
#:::::::::::::::::::::::::::::::::
# 1. square of the distance between an individual and the
# PCA center of gravity
center <- res.pca$center
scale<- res.pca$scale
getdistance <- function(ind_row, center, scale){
  return(sum(((ind_row-center)/scale)^2))
  }
d2 <- apply(decathlon2.active,1,getdistance, center, scale)
# 2. Compute the cos2. The sum of each row is 1
cos2 <- function(ind.coord, d2){return(ind.coord^2/d2)}
ind.cos2 <- apply(ind.coord, 2, cos2, d2)
head(ind.cos2[, 1:4])
```


```{r}
# Contributions of individuals
#:::::::::::::::::::::::::::::::
contrib <- function(ind.coord, comp.sdev, n.ind){
  100*(1/n.ind)*ind.coord^2/comp.sdev^2
}
ind.contrib <- t(apply(ind.coord, 1, contrib, 
                       res.pca$sdev, nrow(ind.coord)))
head(ind.contrib[, 1:4])
```


