---
title: "Seed Breakdown  Thermal treatment- ANOVAS specific bands "
author: "CT"
date: 16.09.2018
output: html_document
---
This script reads the baselined_normalised_snip spectra for the 3 replicates 3 cultivars (Antas, Monti and Narrikup) in 3 different incubation times (0, 42, 84, 252). the aim is to run ANOVA in for specific bands detected from the PCA analysis Unscrambler

Done so far : band 2930 and band 2850  



```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)

```



```{r readData}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SpectraThermalTreatment")
getwd()

#create file
#df_sp <- read.table("BreakBaseLineReps.txt",header=TRUE)
df_sp <- read.table("NormalSnipped_RepsByCvByIncub.txt",header=TRUE)
#head(df_sp)

head(df_sp)
```

#Adjust formats 

```{r}

df_sp <- df_sp %>%
  mutate(Cultivar=factor(Cultivar), Rep=factor(Rep), WaveNumber=as.numeric(WaveNumber), AbsValue=as.numeric(AbsValue),IncubationDays=factor(IncubationDays)) %>%
    dplyr::select(Cultivar:WaveNumber, AbsValue)

str (df_sp)

```

############################################################


# Region 3000 - 2800
##select band  of interest : in this case choose at 2930 cm-1 , which represents CH2 asymmetrical (lipids region) 



```{r}

df_sp2930 <-df_sp %>%
  subset(WaveNumber <2931 & WaveNumber >2929)
  

```

check 

```{r}

str(df_sp2930)


```



##- Now run anova in this band 
 
```{r, warning=FALSE }


##use dataframe = df_sp3295

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- df_sp2930 

head(file.subset, 50)
summary(file.subset)
  my.anova <- aov(AbsValue ~ Cultivar*IncubationDays, data = file.subset)               

    #-----------------------
summary(my.anova)

```



## Means separation with LSD (not using for while )

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar","IncubationDays"), alpha= 0.05, p.adj="none")) 
```


##Using this : Tukey 

```{r}
#posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)
#posthoc <- TukeyHSD(x=my.anova, "Cultivar", conf.level=0.95)
posthoc <- TukeyHSD(x=my.anova, c("Cultivar","IncubationDays"), conf.level=0.95, TRUE)
posthoc



```


Then 
This is the mean separation using Tukey 


```{r}

#fogo <-HSD.test(my.anova, c("Cultivar","IncubationDays"), group=TRUE)

fogo <-HSD.test(my.anova, c("IncubationDays"), group=TRUE)

#fogo <-HSD.test(my.anova, c("Cultivar"), group=TRUE)
fogo



```




        test p.ajusted                  name.t ntr alpha
  Fisher-LSD      none Cultivar:IncubationDays  12  0.05

$means
       AbsValue         std r       LCL       UCL       Min       Max       Q25       Q50       Q75
A:0   0.1929835 0.012518840 6 0.1777064 0.2082606 0.1802248 0.2082188 0.1828396 0.1907167 0.2035368
A:252 0.1809813 0.007447144 6 0.1657042 0.1962584 0.1727892 0.1897461 0.1748090 0.1804092 0.1872962
A:42  0.1486003 0.016306234 6 0.1333233 0.1638774 0.1348166 0.1695594 0.1365034 0.1416728 0.1622434
A:84  0.1643535 0.007377757 6 0.1490764 0.1796306 0.1549382 0.1717996 0.1583087 0.1663417 0.1698869
M:0   0.2107571 0.021600913 6 0.1954800 0.2260342 0.1827607 0.2270566 0.1930033 0.2224604 0.2255804
M:252 0.2717166 0.010052796 6 0.2564396 0.2869937 0.2641515 0.2847963 0.2647630 0.2662852 0.2799658
M:42  0.1949350 0.008392382 6 0.1796579 0.2102121 0.1872336 0.2055361 0.1885925 0.1920236 0.2020141
M:84  0.1791406 0.010245570 6 0.1638636 0.1944177 0.1673941 0.1903472 0.1705141 0.1796558 0.1876569
N:0   0.2070253 0.047603302 6 0.1917482 0.2223023 0.1474073 0.2502799 0.1665482 0.2233777 0.2434224
N:252 0.2430691 0.012078357 6 0.2277920 0.2583461 0.2300488 0.2571843 0.2331093 0.2420445 0.2532323
N:42  0.1833874 0.018204293 6 0.1681103 0.1986644 0.1601075 0.1991258 0.1681579 0.1909939 0.1966664
N:84  0.1912486 0.013447348 6 0.1759715 0.2065257 0.1733960 0.2024014 0.1804729 0.1974726 0.2008250

$comparison
NULL

$groups
       AbsValue groups
M:252 0.2717166      a
N:252 0.2430691      b
M:0   0.2107571      c
N:0   0.2070253      c
M:42  0.1949350     cd
A:0   0.1929835     cd
N:84  0.1912486     cd
N:42  0.1833874     de
A:252 0.1809813     de
M:84  0.1791406     de
A:84  0.1643535     ef
A:42  0.1486003      f

attr(,"class")
[1] "group"
Modify Chunk OptionsRun All Chunks AboveRun Current Chunk
Show in New WindowClear OutputExpand/Collapse Output
  Tukey multiple comparisons of means
    95% family-wise confidence level
    factor levels have been ordered

Fit: aov(formula = AbsValue ~ Cultivar * IncubationDays, data = file.subset)

$Cultivar
           diff          lwr        upr     p adj
N-A 0.034452899  0.021474423 0.04743137 0.0000001
M-A 0.042407678  0.029429202 0.05538615 0.0000000
M-N 0.007954779 -0.005023696 0.02093325 0.3110270

$IncubationDays
              diff         lwr        upr     p adj
84-42  0.002606676 -0.01387186 0.01908521 0.9751907
0-42   0.027947743  0.01146921 0.04442628 0.0001948
252-42 0.056281447  0.03980291 0.07275998 0.0000000
0-84   0.025341067  0.00886253 0.04181960 0.0008030
252-84 0.053674771  0.03719623 0.07015331 0.0000000
252-0  0.028333704  0.01185517 0.04481224 0.0001571

Modify Chunk OptionsRun All Chunks AboveRun Current Chunk
Show in New WindowClear OutputExpand/Collapse Output
$statistics
       MSerror Df      Mean       CV        MSD
##

```{r}

##Empty in purpose ANOVA for 2850 cm 

```


# Region 3000 - 2800
##select band  of interest : in this case choose at 2850 cm-1 , which represents CH2 asymmetrical (lipids region) 



```{r}

df_sp2850 <-df_sp %>%
  subset(WaveNumber <2851 & WaveNumber >2849)
  

```

check 

```{r}

str(df_sp2850)


```




##- Now run anova in this band 
 
```{r, warning=FALSE }


##use dataframe = df_sp3295

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- df_sp2850 

head(file.subset, 50)
summary(file.subset)
  my.anova <- aov(AbsValue ~ Cultivar*IncubationDays, data = file.subset)               

    #-----------------------
summary(my.anova)

```



##Using this : Tukey 

```{r}
#posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)
posthoc <- TukeyHSD(x=my.anova, "Cultivar", conf.level=0.95)
#posthoc <- TukeyHSD(x=my.anova, c("Cultivar","IncubationDays"), conf.level=0.95, TRUE)
posthoc



```


Then 
This is the mean separation using Tukey 


```{r}

#fogo1 <-HSD.test(my.anova, c("Cultivar","IncubationDays"), group=TRUE)

#fogo1 <-HSD.test(my.anova, c("IncubationDays"), group=TRUE)

fogo1 <-HSD.test(my.anova, c("Cultivar"), group=TRUE)
fogo1



```




############################Not in use yet ####################################################


Loop unique wavenumber 

```{r}

idList <-unique(df_sp2$id) 

print(paste0("Found ",length(idList)," wavelength by cultivar combinations to loop"))

data.all <- data.frame()

x <- 0 # for t test

for (i in 1:length(idList)) {
  
    df <- df_sp2 %>%
    ungroup() %>%
    mutate(IncubationDays=factor(IncubationDays), Rep=factor(Rep)) %>%
    subset(id == idList[i])
  
  my.anova <- aov(AbsValue ~ IncubationDays + Rep, data = df)
   
  pVals <- summary(my.anova)[[1]][["Pr(>F)"]]
 
    # T test when P<0.05
  if(!is.nan(pVals[1]) & pVals[1] < 0.05) {
  
  x <- x + 1
  t_test <-  LSD.test(my.anova, c("IncubationDays"), alpha= 0.05, p.adj="none")
  lsd <- t_test$statistics[6] # getting  lsd
  
  this.data <- data.frame(Cultivar=df$Cultivar[1], WaveNumber = df$WaveNumber[1], PV = pVals[1], LSD = lsd, Count=x)
  
  data.all <- rbind(data.all, this.data)
  
  this.data <- NULL
  
  } else {
    
# do nothing
   
  }
  
}
```

write a table with values by cultivar 

```{r}
write.table(data.all, "P_LSD_Break_0_84.txt")
```


graph follows in script 4. 


