---
title: "Seed Breakdown  Thermal treatment"
author: "CT"
date: 16.11.2018
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
This script reads the baselined corrected spectra for the 3 replicates 3 cultivars (Antas, Monti and Narrikup) in 3 different incubation times (0, 42, 84, 252)  

```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)

```



```{r readData}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SpectraThermalTreatment")
getwd()

#create file
#df_sp <- read.table("BreakBaseLineReps.txt",header=TRUE)
df_sp <- read.table("NormalisedSnip_Dataframe.txt",header=TRUE)
#head(df_sp)

head(df_sp)
```

##select columns of interest and re arrange the dataframe 
## make wavenumber as factor 


```{r}
df_sp2 <-df_sp %>%
  dplyr::select(-TreatCode_Cv_Incub_Rep, -TreatCode_Cv_Incub_Rep_Seed) %>%
  mutate(IncubationDays=factor(IncubationDays), Rep=factor(Rep),Seed=factor(Seed)) %>%
#filter(IncubationDays!="42")%>%  
#Now gather values 
tidyr::gather("AbsFactor", "AbsValue",starts_with("X")) %>%
mutate(WaveNumber=as.numeric(gsub("X","",AbsFactor)), AbsFactor=factor(AbsFactor)) %>%
mutate(id=factor(paste0(Cultivar,"_",AbsFactor))) 



```

check 

```{r}

str(df_sp2)


```



##- Now extract the spectra means by seed or rep or treatment 
 
```{r, warning=FALSE }



#get average by cultivar incubation and rep combination 

df_AverageRep <-df_sp2 %>%
group_by(Cultivar, IncubationDays,WaveNumber) %>%
summarise_all(funs(mean))


summary(df_AverageRep)
```

Write table with all selected data  
```{r}
#write.table(df_sp2,"BreakBaselined3cv.txt")

write.table(df_AverageRep,"NormalSnipped_CvByIncub.txt")


```



Now Spread the dataframe to feed Unscrumbler 

```{r}

df_spread<-df_AverageRep %>%
  tidyr::spread("WaveNumber", "AbsValue")

#then write a tabel with spread data 

write.table(df_spread,"Spread_NormalSnipped_CvByIncub.txt")


```


Now repeat the same procedure grouping by Cv x Incub x Rep 



```{r, warning=FALSE }



#get average by cultivar incubation and rep combination 

df_Average3Reps <-df_sp2 %>%
group_by(Cultivar, IncubationDays, Rep, WaveNumber) %>%
summarise_all(funs(mean))


summary(df_Average3Reps)


```



Write table with all selected data  
```{r}
#write.table(df_sp2,"BreakBaselined3cv.txt")

write.table(df_Average3Reps,"NormalSnipped_RepsByCvByIncub.txt")


```



Now Spread the dataframe to feed Unscrumbler 

```{r}

df_spread<-df_Average3Reps %>%
  tidyr::spread("WaveNumber", "AbsValue")

#then write a tabel with spread data 

write.table(df_spread,"Spread_NormalSnipped_RepsByCvByIncub.txt")


```









############################Not in use yet ####################################################


Loop unique wavenumber 

```{r}

idList <-unique(df_sp2$id) 

print(paste0("Found ",length(idList)," wavelength by cultivar combinations to loop"))

data.all <- data.frame()

x <- 0 # for t test

for (i in 1:length(idList)) {
  
    df <- df_sp2 %>%
    ungroup() %>%
    mutate(IncubationDays=factor(IncubationDays), Rep=factor(Rep)) %>%
    subset(id == idList[i])
  
  my.anova <- aov(AbsValue ~ IncubationDays + Rep, data = df)
   
  pVals <- summary(my.anova)[[1]][["Pr(>F)"]]
 
    # T test when P<0.05
  if(!is.nan(pVals[1]) & pVals[1] < 0.05) {
  
  x <- x + 1
  t_test <-  LSD.test(my.anova, c("IncubationDays"), alpha= 0.05, p.adj="none")
  lsd <- t_test$statistics[6] # getting  lsd
  
  this.data <- data.frame(Cultivar=df$Cultivar[1], WaveNumber = df$WaveNumber[1], PV = pVals[1], LSD = lsd, Count=x)
  
  data.all <- rbind(data.all, this.data)
  
  this.data <- NULL
  
  } else {
    
# do nothing
   
  }
  
}
```

write a table with values by cultivar 

```{r}
write.table(data.all, "P_LSD_Break_0_84.txt")
```


graph follows in script 4. 


