---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "11.01.2018"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(gridExtra)

```

-This script reads the SDmax and SDbreak (hardness indexes) and the absorbance values of different wavenumbers: S2_MaxHardBreakSpectra.txt

-Combines the info about the max hardness and slope hardseed breakdown 
-Attempt to establish correlation between the different variates 

C:\GitHubRepos\SubCloverPhD\SubClover\Spectra_S2_Anovas

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Spectra_S2_Anovas")
getwd()

#create file
df_S2 <- read.table("S2_MaxHardBreakSpectra.txt",header=TRUE)
head(df_S2)
# change format 


```

now


create the hardindex (SDmax + 1-SDbreak)

```{r}
df_S2<-df_S2 %>%
mutate(Inverse=10-(100*SDBreak))%>%
 mutate(HardIndex= SDMax+Inverse)


```





##Now plot variates to find  ...any correlation? 


##Run first for SDMAx

```{r, fig.height=10, fig.width=10}

#str(df_All4)
str (df_S2)

#pairs(~HardAccum+slope+Rain+RH+Temp,data=df_All, main="Simple Scatterplot Matrix")
  #pairs(~HardAccum+slope+Rain+RH+Temp+DaysToSeedharvest,data=df_All2, main="Simple Scatterplot Matrix")
 ##this is for df All2 
#pairs(~HardPerc_Initial14 +RateDecreasePerTTunit+Rain+RH+Temp+DaysToSeedharvest,data=df_All2, main="Simple Scatterplot Matrix")

##this is for df All3

# pairs(~HardPerc_Initial14 +RateDecreasePerTTunit+Rain+RH+Temp+SoilTemp+DaysToSeedharvest+DaysBudDuration+DAS50F,data=df_All4, main="Simple Scatterplot Matrix")

pairs(~SDMax+SDBreak+HardIndex+ABS2930+ABS2855+ABS1745+ABS1732+ABS1610+ABS1441+ABS1425+ABS1377+ABS1337+ABS1250+ABS1150+ABS1100+ABS1025+ABS897,data=df_S2, main="Simple Scatterplot Matrix")

# dfD <- df_All%>%
#   filter(Cultivar=="Denmark")
# pairs(~HardAccum+slope+Rain+RH+Temp,data=dfD, main="Simple Scatterplot Matrix Denmark")

```



then select columns of interest : here stats for overall means (SDMax and specific wavenumbers)

```{r}

#find coefficients 

#cor (df_All[,-c(1,2)])
cor (df_S2[,-c(1,2)])
# cor (dfD[,-c(1,2)])

#just change variable name to keep graphs same 


```

###Plot Weather variables with Maximum Percentage of Hardseeds 


```{r, fig.height=5, fig.width=10}

g1 <-df_S2 %>%
  #ggplot(aes(x=ABS1745, y= SDMax))  +
  ggplot(aes(x=ABS1745, y= HardIndex))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=Cultivar),size=6)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Absorbance~1745~"(cm-1)"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))
  #facet_wrap(~Cultivar)

grid.arrange(g1)

```




Plot with the sum of the 2930 and 2855 or other sums 

```{r}

SumUP<-df_S2 %>%
mutate(ABSSum=ABS2930+ABS2855+ABS1745+ABS1732)

#then asses
#summary(lm(SDMax ~ ABSSum, SumUP))

#Break
summary(lm(SDBreak ~ ABSSum, SumUP))

```


```{r, fig.height=8, fig.width=10}


#MHard<-mean(df_All3$HardAccum)

#Mslope<-mean(df_All3$slope)


g10 <-df_S2 %>%
  #ggplot(aes(x=DaysBudDuration, y= HardAccum))  +
  ggplot(aes(x=ABS1745, y= SDMax))  +
 # geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(colour=Cultivar,  shape=Cultivar),size=7)+
#   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  #xlab(expression(Days~to~BudDuration~"(n)"))+ 
  xlab(expression(Absorbance~"(cm-1)"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(SDMax%)"))+
  geom_abline(slope=0, intercept=MHard) +
  geom_vline(slope=0, xintercept=Mslope) + 
  xlim(0,0.028)+
  ylim(0,108)+
  theme(text = element_text(size=20))# +
#  facet_wrap(~SowTreat)

grid.arrange(g10)

```



```{r, fig.height=7, fig.width=15}

#MaxHardseed vs ABS 2855 

 g1 <-df_S2 %>%
  ggplot(aes(x=ABS2855, y= SDMax))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=Cultivar),size=6)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  #xlab(expression(Absorbance~1745~"(cm-1)"))+
  xlab(expression(Absorbance~2855~"(cm"^"-1"*")"))+
  ylab(SD[max]~" (%)") +
  #ylab(expression(SDmax~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  annotate("text", x = 0.095, y =90, label = "r = 0.52",size=6)
  #facet_wrap(~Cultivar)



g1_2 <-df_S2 %>%
  ggplot(aes(x=ABS1745, y= SDMax))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=Cultivar),size=8)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  #xlab(expression(Absorbance~1745~"(cm-1)"))+
  xlab(expression(Absorbance~1745~"(cm"^"-1"*")"))+
  ylab(SD[max]~" (%)") +
  #ylab(expression(SDmax~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=22))+
  annotate("text", x = 0.095, y =90, label = "r = 0.53",size=6)
  #facet_wrap(~Cultivar)
#MaxHardseed vs ABS 1150 

g2 <-df_S2 %>%
  ggplot(aes(x=ABS1150, y= SDMax))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=Cultivar),size=6)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
 xlab(expression(Absorbance~1150~"(cm"^"-1"*")"))+
   ylab(SD[max]~" (%)") +
  theme(text = element_text(size=22))+
  annotate("text", x = 0.205, y =90, label = "r = 0.52",size=6)
  
#hardAccum vs ABS 1025
g3 <-df_S2 %>%
  ggplot(aes(x=ABS1025, y= SDMax))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=Cultivar),size=6)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
   ylab(SD[max]~" (%)") +
  xlab(expression(Absorbance~1025~"(cm"^"-1"*")"))+
  theme(text = element_text(size=22))+
  annotate("text", x = 0.972, y =90, label = "r = 0.76",size=6)
#


 
 
 
  
#grid.arrange(g1, g2, g3, g4)
#grid.arrange(g1,g1_2, g2, g3 )

grid.arrange(g1_2)
# Save
#ggsave("plot_MaxHard_WeatherTendays.png", width=12, height=6, dpi=400)


```

Inspect overall Lm with SDMAx

```{r}

#summary(lm(SDMax ~ ABS2930, df_S2))
#summary(lm(SDMax ~ ABS2855, df_S2))
#summary(lm(SDMax ~ ABS1745, df_S2)) 
#summary(lm(SDMax ~ ABS1732, df_S2)) 
#summary(lm(SDMax ~ ABS1610, df_S2))  
#summary(lm(SDMax ~ ABS1441, df_S2))
#summary(lm(SDMax ~ ABS1425, df_S2))
#summary(lm(SDMax ~ ABS1377, df_S2))
#summary(lm(SDMax ~ ABS1337, df_S2))
#summary(lm(SDMax ~ ABS1250, df_S2))
#summary(lm(SDMax ~ ABS1150, df_S2))
#summary(lm(SDMax ~ ABS1100, df_S2))
#summary(lm(SDMax ~ ABS1025, df_S2))
#summary(lm(SDMax ~ ABS897, df_S2))


```

Then check for SDBreak 




```{r}

#summary(lm(SDBreak ~ ABS2930, df_S2))
#summary(lm(SDBreak ~ ABS2855, df_S2))
#summary(lm(SDBreak ~ ABS1745, df_S2)) 
#summary(lm(SDBreak ~ ABS1732, df_S2)) 
#summary(lm(SDBreak ~ ABS1610, df_S2))  
#summary(lm(SDBreak ~ ABS1441, df_S2))
#summary(lm(SDBreak ~ ABS1425, df_S2))
#summary(lm(SDBreak ~ ABS1377, df_S2))
#summary(lm(SDBreak ~ ABS1337, df_S2))
#summary(lm(SDBreak ~ ABS1250, df_S2))
#summary(lm(SDBreak ~ ABS1150, df_S2))
#summary(lm(SDBreak ~ ABS1100, df_S2))
#summary(lm(SDBreak ~ ABS1025, df_S2))
#summary(lm(SDBreak ~ ABS897, df_S2))





```


graph for SDBreak vs ABS 1745, 1337, 1250


```{r, fig.height=7, fig.width=15}

#HArdseedbreak (SDbreak) vs ABS ABS 1745, 1337, 1250

 g4 <-df_S2 %>%
  ggplot(aes(x=ABS1745, y= SDBreak))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=Cultivar),size=6)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  #xlab(expression(Absorbance~1745~"(cm-1)"))+
  xlab(expression(Absorbance~1745~"(cm"^"-1"*")"))+
  ylab(SD[Break]~"(%units /"^"o"*"Cd)") +
  #ylab(expression(SDmax~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  annotate("text", x = 0.08, y =0.013, label = "r = 0.73",size=6)
  #facet_wrap(~Cultivar)

#MaxHardseed vs ABS 1337 

g5 <-df_S2 %>%
  ggplot(aes(x=ABS1337, y= SDBreak))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=Cultivar),size=8)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
 xlab(expression(Absorbance~1337~"(cm"^"-1"*")"))+
   ylab(SD[Break]~"(%units/"^"o"*"Cd)") +
  theme(text = element_text(size=22))+
  annotate("text", x = 0.155, y =0.013, label = "r = 0.52",size=6)
  
#hardAccum vs ABS 1250
g6 <-df_S2 %>%
  ggplot(aes(x=ABS1250, y= SDBreak))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=Cultivar),size=6)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
   ylab(SD[Break]~"(%units /"^"o"*"Cd)") +
  xlab(expression(Absorbance~1025~"(cm"^"-1"*")"))+
  theme(text = element_text(size=20))+
  annotate("text", x = 0.12, y =0.013, label = "r = 0.68",size=6)
#


g7<-df_S2 %>%
  ggplot(aes(x=ABS1732, y= SDBreak))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=Cultivar),size=6)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
   ylab(SD[Break]~"(%units /"^"o"*"Cd)") +
  xlab(expression(Absorbance~1732~"(cm"^"-1"*")"))+
  theme(text = element_text(size=20))+
  annotate("text", x = 0.12, y =0.013, label = "r = 0.68",size=6)

 # g7 <-df_All4 %>%
 #   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
 #  ggplot(aes(x=Temp, y= HardAccum))  +
 #  geom_point(colour= "black", alpha=0.2) +
 #  geom_point(aes(shape=SowTreat),size=5)+
 #   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
 #  theme_bw() +
 #  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
 #  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
 #  theme(text = element_text(size=20))+
 #  facet_wrap(~Cultivar) 
 
 
 
  
#grid.arrange(g1, g2, g3, g4)
grid.arrange( g5 )
#grid.arrange( g5, g6)
# Save
#ggsave("plot_MaxHard_WeatherTendays.png", width=12, height=6, dpi=400)


```


```{r}





```



This loop checks the lm 

```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_S2$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_S2 %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required 
  
    summary(lm(SDMax ~ Rain, df_subset))  
    
  #print
    
print(summary(lm(HardAccum ~ Rain, df_subset)))


  } 


```

##Plot Days to harvest  with RAte of Hardseed breakdown 



```{r, fig.height=5, fig.width=10}
g4 <-df_All2 %>%
  ggplot(aes(x=DaysToSeedharvest, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Days~to~Harvest~"(n)"))+ 
 ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)

grid.arrange(g4)

```



##Plot Weather variables with RAte of Hardseed breakdown  


```{r, fig.height=10, fig.width=15}
#Hardbreak vs Rain 


# g6 <-df_All2 %>%
#    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
#   ggplot(aes(x=DaysToSeedharvest, y= slope))  +
#   geom_point(colour= "black", alpha=0.2) +
#   geom_point(aes(shape=SowTreat),size=5)+
#    geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
#   theme_bw() +
#   xlab(expression(Days~to~Harvest~"(n)"))+
#  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
#   theme(text = element_text(size=20))+
#   facet_wrap(~Cultivar)



g6 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Rain, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Rain~"("*"mm"*")"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#hardAccum vs RH
g7 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)

 g8 <-df_All4 %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Temp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 


  
 g9 <-df_All4 %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 
  
#grid.arrange(g4, g5, g6, g7)
grid.arrange( g6, g7, g8,g9)
# Save
# ggsave(file="Fig_weather.tiff", dpi = 300)

#ggsave("plot_CumulativeGerm.png", width=12, height=6, dpi=400)


```





```{r}


#summary(lm(slope ~ Rain, df_All2)) 
#summary(lm(slope ~ RH, df_All2)) 
#summary(lm(slope ~ Temp, df_All2)) 
#summary(lm(slope ~ DaysToSeedharvest, df_All2))

summary(lm(slope ~ SoilTemp, df_All4))


##DaysBudDuration
#summary(lm(slope ~ DaysBudDuration, df_All3))
##days to flower 
# summary(lm(slope ~ DAS50F, df_All4))
```

####################Phenological Traits ################



```{r}


##Growing Days
#summary(lm(HardAccum ~ DaysToSeedharvest, df_All4))


##DaysBudDuration
 #summary(lm(HardAccum ~ DaysBudDuration, df_All4))
##days to flower 
#summary(lm(HardAccum ~ DAS50F, df_All4))



##Growing Days
#summary(lm(slope ~ DaysToSeedharvest, df_All4))


##DaysBudDuration
#summary(lm(slope ~ DaysBudDuration, df_All4))
##days to flower 
 summary(lm(slope ~ DAS50F, df_All4))


```

Do similar graphs with the phenological traits : Growing days, bud duration and time to flower 




```{r, fig.height=15, fig.width=15}
#Hardbreak vs Rain 

str(df_All4)
 
##Growing Days vs slope
g111 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=DaysToSeedharvest , y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Growing~Period~"("*"days"*")"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#Days of blooming vs slope 
g112 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=DaysBudDuration, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Blooming~Period~"("*"days"*")"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)

#Time to flower 
 g113 <-df_All4 %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=DAS50F, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Days~to~Flower~"("*"n"*")"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 


  
  
#grid.arrange(g4, g5, g6, g7)
grid.arrange( g111, g112, g113)
# Save
# ggsave(file="Fig_weather.tiff", dpi = 300)

#ggsave("plot_CumulativeGerm.png", width=12, height=6, dpi=400)


```



```{r, fig.height=15, fig.width=15}
#Hardbreak vs Rain 

str(df_All4)
 
##Growing Days vs slope
g11 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=DaysToSeedharvest , y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Growing~Period~"("*"days"*")"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#Days of blooming vs slope 
g12 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=DaysBudDuration, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Blooming~Period~"("*"days"*")"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)

#Time to flower 
 g13 <-df_All4 %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=DAS50F, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Days~to~Flower~"("*"n"*")"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 


  
  
#grid.arrange(g4, g5, g6, g7)
grid.arrange( g11, g12, g13)
# Save
# ggsave(file="Fig_weather.tiff", dpi = 300)

#ggsave("plot_CumulativeGerm.png", width=12, height=6, dpi=400)


```






```{r}

#markdown::render("<C:\\GitHubRepos\\SubCloverPhD\\SubClover\\HardseedsProject1Read.Rmd>") 
```


