---
output:
  word_document: default
  html_document: default
---
---
title: "TSW  "
author: "CT"
date: " renewed 05.08.2017 (original 28.12 2016)"
output:
  word_document: default
  pdf_document: default
  
  #Aim: this script  reads the SeedBurrYield data and calculates the TSW (g)
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(rgr)
```

Aim: calculate the Thousand seed weight for each treatment combination (Sowing date, cultivar, depth)


```{r loadFile}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\Gitsubclover\\SeedYieldIv2")
getwd()



df_seedY<- read.table("SeedBurrYield.txt",header=TRUE)
head(df_seedY)
summary(df_seedY)


```


Define formats  
```{r}

# define factors and formats
file <- df_seedY %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    Date = dmy(Date),
    SowingD = dmy(SowingD)
  )

str(file)
summary(file)
head(file)




```

Calculate the TSW and create a column with TSW. 
Select columns of interest for ANOVA.

```{r}

df<- file %>%
  dplyr::select(Cultivar,SowTreat,Block,
                Depth,seed_weight_g,seedNo) %>%
  mutate(TSW = ((seed_weight_g/seedNo)*1000)) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,Block,TSW)

  df <- as.data.frame(df)
head(df)


```

Data visualisation: effects of sowing date and cultivar on TSW.


```{r, fig.height=5, fig.width=10}

#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df %>%
  
  mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%

  group_by(Cultivar, SowTreat,Depth) %>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x=Cultivar, y=(TSW_mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=TSW_mean-TSW_sd/2,
                    ymax=TSW_mean+TSW_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    labs(y= "Thousand Seed weight (g) ")+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))


```


Here ANOVA according S. Saville advice: LSD test unprotected by sowing date individually.
Use filters to select treatments. 

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  filter(SowTreat=="S7")

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change  the variables to get mean values. 
Use :comment out or in to select  SowTreat or Depth or Cultivar 

```{r}
#ANOVA
#my.anova <- aov(TSW ~ SowTreat + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
my.anova <- aov(TSW ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(TSW ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means when applicable (P<0.05)
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
```

End of this script. 
