---
title: "Seed Yield Analysis"
author: "CT"
date: "18.03.2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
This script :
reads the file with total seed yield and combine with HSmax and HSbreak to calculate amount of seeds readly germinable (risk fals strike), germinated in the coming 120 days (or 2400 oCd) and finally potential seeds in seed bank 
2400 is the accumulated TT in 120days 



```{r}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
library(knitr)
```

Read File 

```{r, echo=FALSE}

#olde folder setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldIv2")
##old path : 
  
  setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedYieldIv2")
##setwd("C:\\github\\SubClover\\SeedYieldIv2")
getwd()
file <- read.table("Project1_Total_SeedYieldIv2.txt",header=TRUE)
head(file)
summary(file)
```

Define formats 
```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    #Depth = as.factor (Depth),
    #Date = dmy(Date),
    #SowingD = dmy(SowingD)
  )

str(file)
summary(file)
head(file)

```
Merge with HSmax and HSbreak data per plot 
use this file : HSmax_HSbreakByPlot.txt

```{r}
getwd()
HS <- read.table("HSmax_HSbreakByPlot.txt",header=TRUE)

str(HS)

HS<- HS %>%
  mutate(Plot = as.factor(Plot))
```

merge by plot 

```{r}


df_SeedAll <- merge (file, HS, by="Plot")


##then Clean dataframe 

df_SeedAll <- df_SeedAll%>%
  rename(HSmax=HardPerc_Initial14_mean,
         HSbreak=RateDecreasePerTTunit_mean)%>%
  dplyr::select(-HardPerc_Initial14_sd , - RateDecreasePerTTunit_sd)


str(df_SeedAll)

```

Now bring germination data to calculate yield of seeds which will produce a normal seedling (discount the abnormal ungerminated)
use : AllPlotsGermination.txt

```{r}
getwd()
Germ <- read.table("AllPlotsGermination.txt",header=TRUE)

str(Germ)

Germ<- Germ %>%
  mutate(Plot = as.factor(Plot))%>%
  dplyr::select(Plot, mean)%>%
  rename(Germination=mean)
str(Germ)
##then merge 

df_SeedAllWork<-merge(df_SeedAll,Germ, by="Plot")


```






Now make all calculations :
NormalSeedsKg_ha = Yield of normalSeedlings (discount the abnormals and ungerminated seeds portion ) do as Seedskg_ha x Germ/100
Percent of seeds readly germinated (HSmax-100)
Percent of seeds which will germinate in the 120days (2400 oCd)= HSbreakx2400
Percent of seeds hardseedbank (100-PercReady + Perc120days)

then multiply by the seed yield to know the quantities in kgseed/ha 


```{r}

dfSeedCalculated <-df_SeedAllWork %>%
  mutate(Seedskg_haNormal=Seedskg_ha*(Germination/100),
         PercReady= 100-HSmax,
         Perc120days=HSbreak*2400,
         PercSeedBank=100-(PercReady+Perc120days),
         QtySeedReady=Seedskg_haNormal*(PercReady/100),
         QtySeed120=Seedskg_haNormal*(Perc120days/100),
         QtySeedBank=Seedskg_haNormal*(PercSeedBank/100), 
         QtyCheck= (QtySeedReady+QtySeed120+QtySeedBank)-Seedskg_haNormal)
         


```


stack the Qty Seeds

```{r}
dfSeed_Stack <- dfSeedCalculated %>%
  dplyr::select(Plot, Block,Cultivar, SowTreat,QtySeedReady,QtySeed120,QtySeedBank)%>%
  gather(key= "status" , value = "KgSeeds" , QtySeedReady:QtySeedBank)%>%
  group_by(Cultivar, SowTreat,status)%>%
  dplyr::select(KgSeeds)%>%
  summarise_all(mean)


```
Do graph for Feb March June 


```{r,fig.height=6, fig.width=6}

dfSeed_Stack%>%
  ungroup(status)%>%
  filter(SowTreat=="S1"|SowTreat=="S6"|SowTreat=="S7") %>%
  mutate(status = factor(status, levels = c("QtySeedReady",
                                          "QtySeed120",
                                  "QtySeedBank"),


                          labels = c("Soft",
                                 "Soften_In_120days",
                                 "SeedBank")
                          )) %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  mutate (Cultivar= factor(Cultivar, levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),labels=c("A", "D", "L", "M", "N","W")))%>%
  ggplot(aes(x=Cultivar, y=KgSeeds, fill=factor(status))) +
  #geom_bar(stat="identity") +
  geom_bar(aes(fill=status), colour="black",stat="identity")+
 # geom_bar(stat="identity",fill = "#FF6666")+
   #colour
      #scale_fill_brewer(palette="Greys")+
  #scale_fill_brewer(palette="Blues")+
  #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
  scale_fill_manual("legend", values = c("Soft" = "olivedrab", "Soften_In_120days" = "ivory","SeedBank" = "darkgrey"))+
  
  facet_wrap(.~SowTreat, ncol=1) +
  theme_bw()+
  ylab("Seed quantity (kg/ha)") +
  xlab("Cultivar") +
  theme(axis.text.x = element_text(angle = 0, hjust=1)) + theme(legend.title=element_blank()) +
  theme(text = element_text(size=18))+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))

ggsave("plot_SeedYieldProject10_Combine.tiff", width=8, height=12, dpi=600)
```



make a new graph as per poster ESA



```{r, fig.width=10, fig.height=10}

# Graph Seed kg ha

#barplot 
#The palette with grey:
#cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)
fs<-28

inv<-c("Above","Below")

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  dfB <- df1 %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  group_by(Cultivar, SowTreat,Depth) %>%
  dplyr::select(Seedskg_ha, Cultivar, SowTreat,Depth)%>%
  summarise_each(funs(mean,sd)) %>%
    mutate(SE=sd/1.73)
  
  dfB_g <- dfB %>%
    ungroup() %>%
    group_by(SowTreat,Cultivar) %>%
 #  mutate(Depth=Depth, levels=c("Below","Above"))  %>%
    mutate(Depth=Depth, levels=c("Above","Below"))  %>%
    arrange(rev(Depth)) %>%
    mutate(Mean_sum=cumsum(mean)) %>%
    mutate(SD_sum_down=Mean_sum-sd/2, 
           SD_sum_up=Mean_sum+sd/2) %>%
    ungroup() %>%
    mutate(SowTreat= factor(SowTreat, 
                             levels=c("S1", "S2", "S3", "S4", "S6", "S7"),
                             labels=c("June", "July", "September", "November", "February","March"))) # %>%
   # ungroup() %>%
  #  mutate(Depth = reorder(Depth,inv)) 
  
  
 dfB_g %>%
 # mutate(Depth=factor(Depth, levels=c("Above","Below"))) %>% 
 # ggplot(aes(x= SowTreat, y=mean, fill= rev(Depth))) +
  ggplot(aes(x= SowTreat, y=mean, fill= (Depth))) +
  geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=SD_sum_down,
                    ymax=SD_sum_up),
                width=0.25, size=0.3)  +
  facet_wrap(.~Cultivar, ncol=2) +
    theme(text = element_text(size = 15)) +
   theme(axis.text.x=element_text(angle = 45, hjust=1.0)) +
 #  theme(text = element_text(size= fs))+
   scale_fill_manual("legend", values = c("Above"   = "#CCCCCC", "Below" = "#666666" )) +
theme(
     panel.background = element_rect(fill = "white", colour = "black", size = 2, linetype = "solid"), 
     panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "grey"), 
     panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "grey"),
     axis.line = element_line(colour = "black"))+
     theme(strip.background = element_rect(colour = "black", fill = "white",size=1)) +
     ylab("Seed yield (kg/ha)") +
     xlab("Sowing month")
   
    
# 

 # ggsave("plot_SeedYield_Prjct1_Iversen2.tiff", width=14, height=16, dpi=500)
  
  
```




