---
output:
  word_document: default
  html_document: default
---
---
title: "SeedPer1m2  "
author: "CT"
date: " renew 05.08.2017 (from the 28 December script 2016)"
output:
  word_document: default
  pdf_document: default
  
  #This script  reads the SeedBurYield file, calculates the number of seed per 1 burr  and performs ANOVA 
---

```{r loadLibraries, warning=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(rgr)
```


Aim: Statistics for variable Seed Number per 1 m2. 


```{r loadFile}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\Gitsubclover\\SeedYieldIv2")
getwd()

#REading the dataframe generated in SeedYieldProject1 script

df_seedY<- read.table("SeedBurrYield.txt",header=TRUE)
head(df_seedY)
summary(df_seedY)


```


Define formats 
```{r}

# define factors and formats
file <- df_seedY %>%
  mutate(
    #Plot = as.factor(Plot),
    #Date = dmy(Date),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    SowTreat = as.factor(SowTreat)
  )

str(file)
#summary(file)
#head(file)




```

Calculate the number of seed in one burr
Include a column in data frame and remove extra columns in data frame 
```{r}
df<- file %>%
  dplyr::select(Cultivar,SowTreat,Block,
                Depth,
                bur_no_subSample,
                seedNo) %>%
  mutate(SeedsPerBur = ((seedNo/bur_no_subSample)*1)) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,Block,SeedsPerBur)

  df <- as.data.frame(df)
```


If need a graph create a new chunk here. 


Here only need to change df name as selection of fields were previously done. 

```{r}

#df<- file
#   dplyr::select(Cultivar,SowTreat,
#                 Depth,Block)
# 
#   df <- as.data.frame(df)
# head(df)


```

For graphics check  SeedYieldProject1 script 

Here ANOVA according S. Saville advice : LSD test unprotected by sowing date individually.
Use filter to sub set data (sowing date)

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change the variables (comment out/in) to get mean values and ANOVA info. 
Select :SowTreat or Depth or Cultivar 

```{r}
#ANOVA

#my.anova <- aov(SeedsPerBur ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ SowTreat*Depth + Block, data = file.subset)
my.anova <- aov(SeedsPerBur ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsPerBur ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means for desired variables
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
```

End of script.
