---
title: "Seed Yield Analysis"
author: "CT"
date: "18.03.2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
This script :
reads the file with burrs and seeds numbers and yields
-merge with dataframe which contains plant population to calculate seed numbers and yield per plant instead of per area 
- This is data exploration...overview ... move to script Project 10 for better correlations



```{r}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
library(knitr)
```

Read File 

```{r, echo=FALSE}

#olde folder setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldIv2")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedYieldIv2")

getwd()
file <- read.table("SeedBurrYield.txt",header=TRUE)
head(file)
summary(file)
```

Define formats 
```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    Date = dmy(Date),
    SowingD = dmy(SowingD)
  )

str(file)
summary(file)
head(file)

```
Calculate the number of seeds per 1 m2 

```{r}

df<- file %>%
  dplyr::select(Cultivar,SowTreat,sample_area_m2,Block,Plot,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seedNo) %>%
  mutate(SeedsNo_m2 = ((seedNo/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,Block,Plot, SeedsNo_m2)

  df <- as.data.frame(df)
head(df)

# Then sum up the above and below seeds to get total value per each plot : calculate as funs (sum) 

dftotal<-df %>%
  group_by(Cultivar,SowTreat, Plot)%>%
  dplyr::select(SeedsNo_m2)%>%
  summarise_all(funs(sum))


```


```{r}
df2<- file %>%
  dplyr::select(Plot, Cultivar, SowingD, SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seed_weight_g) %>%
  #stop here calculate kg seed / ha
  mutate(Seedskg_ha = (((seed_weight_g/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2)*10 ) 


```

 

bring data plant pop 

```{r}


file1 <- read.table("df_emerg_perc3.txt",header=TRUE)
head(file1)
summary(file1)

file2<-file1 %>%
  dplyr::select(Plot, FinalPop,Block)%>%
  mutate(Block=as.factor(Block))


```

then merge the two dataframes by Plot


```{r}
str(df2)

dfmerged <- merge(df2,file2, by=c("Plot")) 
  #mutate(SeedperPlant=SeedsNo_m2/FinalPop)
  #dplyr::select(Plot:SowTreat, Hard_perc,slope)

str(dfmerged)
```

Get mean values 


```{r}

relationship<-dfmerged%>%
  dplyr::select(Plot,Cultivar,SowTreat,FinalPop,Seedskg_ha)%>%
  group_by(Plot,Cultivar,SowTreat)%>%
  dplyr::select(FinalPop,Seedskg_ha)%>%
  summarise_all(funs(mean))

MeanData<-relationship%>%
  group_by(Cultivar,SowTreat)%>%
  dplyr::select(FinalPop,Seedskg_ha)%>%
  summarise_all(funs(mean))%>%
  ##remove Monti at S4

str(MeanData)


  


```





```{r,fig.height=5, fig.width=10}


g1 <-MeanData %>%
  ungroup() %>%
  #mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4","S5", "S6","S7","S8"),labels=c("June", #"July", "September", "November","December", "February","March","May")))%>%
  mutate(SowMonth= factor(SowTreat, 
                           levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
                           labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May"))) %>%
  #left_join(df_Photo_dir, by="SowTreat") %>%
  ggplot(aes(x=FinalPop, y= Seedskg_ha))  +
  geom_point(colour= "black", alpha=0.5) +
  geom_point(aes(shape=SowMonth),size=4)+
  scale_shape_manual(values = c(1,2,3,4,5,6,7,8)) +
  geom_text(aes(label=SowMonth),hjust=0, vjust=0,size=7) +
  #geom_errorbar(aes(ymin=PhylC_mean-PhylC_sd/2,
                    #ymax=PhylC_mean+PhylC_sd/2), width=1.5)+
 
  #geom_smooth(method='lm',formula=y~x,alpha=0.1, aes(colour=Pp_dir, fill = Pp_dir)) +
  geom_smooth(method='lm',formula=y~x,alpha=0.1)+
  theme_bw() +
  #xlab(expression(Plant~Population"("plants~/~m"*"^"2"*")")) + 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  #ylab(expression(~Phyllochron~"("^"o"*"Cd/leaf)")) +
  xlab(expression(Plant~Pop))+
  ylab(expression(Seed~Yield~(kg/ha)))+
  theme(text = element_text(size=24))+
  facet_wrap(~Cultivar)+
 #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   
  #label sizes 
theme(text = element_text(size = 24))
  

#grid.arrange(g1, g2, g3,g4,g41)
grid.arrange(g1)
# Save
#ggsave("plot_Phyllochron_PpEmergence.tiff", width=12, height=6, dpi=400)

```


```{r}

NoS1<-MeanData %>%
  filter(SowTreat!="S1")

```




# Get linear coefficients of equations above
##check what are these P values 

```{r}
library(broom)
options(scipen=999)

# create the linear fits by groups o variables
dfreg <- MeanData%>%  group_by(SowTreat) %>%
  do(fitreg = lm(FinalPop ~ Seedskg_ha, data = .))


# get the linear coefficients by group in a tidy data_frame
dfCoef <- tidy(dfreg, fitreg)
dfCoef



```



```{r}


dfCoef = glance(dfreg, fitreg)
dfCoef




```




