---
title: "Seed Yield Analysis"
author: "CT"
date: "18.03.2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
This script :
reads the file with burrs and seeds numbers and yields 



```{r}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
library(knitr)
```

Read File 

```{r, echo=FALSE}

#olde folder setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldIv2")
##old path : 
  
  setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedYieldIv2")
##setwd("C:\\github\\SubClover\\SeedYieldIv2")
getwd()
file <- read.table("SeedBurrYield.txt",header=TRUE)
head(file)
summary(file)
```

Define formats 
```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    Date = dmy(Date),
    SowingD = dmy(SowingD)
  )

str(file)
summary(file)
head(file)

```
Calculate the number of seeds per 1 m2 

```{r}

df<- file %>%
  dplyr::select(Cultivar,SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seedNo) %>%
  mutate(SeedsNo_m2 = ((seedNo/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,Block,SeedsNo_m2)

  df <- as.data.frame(df)
head(df)

#write a table to run statistics in another script 
write.table(df, "SeedNumberper1m2.txt")
```
Re start

```{r}

#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%

  group_by(Cultivar, SowTreat,Depth) %>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x=Cultivar, y=(SeedsNo_m2_mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsNo_m2_mean-SeedsNo_m2_sd/2,
                    ymax=SeedsNo_m2_mean+SeedsNo_m2_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    #labs(y= "Seed Number per m2")+
    ylab(expression(Seed~number~per~1~m^"2"))+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))


```

then do the graph with standard error 
Need to calculate as SE = sd / 1.73 (1.73 is the sqrt of n = 3)


```{r, fig.height=5, fig.width=10}


#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  dfA <-df %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%

  group_by(Cultivar, SowTreat,Depth) %>%
  summarise_each(funs(mean,sd)) %>% 
  mutate(SE=SeedsNo_m2_sd/1.73)
  
  dfA %>%
  ggplot(aes(x=Cultivar, y=(SeedsNo_m2_mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsNo_m2_mean-SE/2,
                    ymax=SeedsNo_m2_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    #labs(y= "Seed Number per m2")+
    ylab(expression(Seed~number~per~m^"2"))+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))
```

make a graph with the sum of above and below for abstract select S2, S3 and S4. 

```{r}

#calculate the sum of above and below 
df_sumseed <-df %>%
 # mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
  group_by(Cultivar, SowTreat,Block) %>%
  dplyr::select(SeedsNo_m2)%>%
  summarise_all(funs(sum)) 

#the ngraph it select only 3 sowing dates 

df_sumseed2<- df_sumseed%>% 
  filter(SowTreat!="S1", SowTreat!="S6", SowTreat!="S7") %>%
  group_by(Cultivar, SowTreat) %>%
  dplyr::select(SeedsNo_m2)%>%
  summarise_all(funs(mean,sd)) %>% 
  mutate(SE=sd/1.73)

df_sumseed2%>%
  ggplot(aes(x=Cultivar, y=(mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=mean-SE/2,
                    ymax=mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(.~SowTreat, scales="free") +
    #labs(y= "Seed Number per m2")+
    ylab(expression(Seed~number~per~m^"2"))+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))
```




```{r, fig.height=5, fig.width=10}
#Calculate Seed yield : number g seeds per m2 and then yield kg seeds per ha
head (file)

df1<- file %>%
  dplyr::select(Plot,Cultivar, SowingD, SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seed_weight_g) %>%
  #stop here calculate kg seed / ha
  mutate(Seedskg_ha = (((seed_weight_g/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2)*10 ) 

  df1 <- as.data.frame(df1)
summary(df1)

write.table(df1, "SeedYieldIv2.txt", row.names=FALSE)

```

Calculate total yield (Above+Below)



```{r, fig.heigt=5, fig.width=10}
# Graph Seed kg ha

#barplot 
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  df1 %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  group_by(Cultivar, SowTreat,Depth) %>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x= Cultivar, y=(Seedskg_ha_mean),fill= Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=Seedskg_ha_mean-Seedskg_ha_sd/2,
                    ymax=Seedskg_ha_mean+Seedskg_ha_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
  theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    labs(y= "Seed yield (kg per ha)")+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
theme(text = element_text(size = 20))
```

Use SEM instead of Stdeviation.


```{r,fig.heigt=5, fig.width=10}

# Graph Seed kg ha

#barplot 
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  dfB <-df1 %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  group_by(Cultivar, SowTreat,Depth) %>%
 # group_by(Cultivar, SowTreat) %>%
    dplyr::select(Seedskg_ha)%>%
  summarise_each(funs(mean,sd)) %>%
    mutate(SE=sd/1.73)
  
  dfB %>%
  ggplot(aes(x= Cultivar, y=(mean),fill= Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=mean-SE/2,
                    ymax=mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
  theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    labs(y= "Seed yield (kg per ha)")+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
theme(text = element_text(size = 20))


```

make a new graph as per poster ESA



```{r, fig.width=10, fig.height=10}

# Graph Seed kg ha

#barplot 
#The palette with grey:
#cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)
fs<-24

inv<-c("Above","Below")

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  dfB <- df1 %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  group_by(Cultivar, SowTreat,Depth) %>%
  dplyr::select(Seedskg_ha, Cultivar, SowTreat,Depth)%>%
  summarise_each(funs(mean,sd)) %>%
    mutate(SE=sd/1.73)
  
  dfB_g <- dfB %>%
    ungroup() %>%
    group_by(SowTreat,Cultivar) %>%
 #  mutate(Depth=Depth, levels=c("Below","Above"))  %>%
    mutate(Depth=Depth, levels=c("Above","Below"))  %>%
    arrange(rev(Depth)) %>%
    mutate(Mean_sum=cumsum(mean)) %>%
    mutate(SD_sum_down=Mean_sum-sd/2, 
           SD_sum_up=Mean_sum+sd/2) %>%
    ungroup() %>%
    mutate(SowTreat= factor(SowTreat, 
                             levels=c("S1", "S2", "S3", "S4", "S6", "S7"),
                             labels=c("June", "July", "September", "November", "February","March"))) # %>%
   # ungroup() %>%
  #  mutate(Depth = reorder(Depth,inv)) 
  
  
 dfB_g %>%
 # mutate(Depth=factor(Depth, levels=c("Above","Below"))) %>% 
 # ggplot(aes(x= SowTreat, y=mean, fill= rev(Depth))) +
  ggplot(aes(x= SowTreat, y=mean, fill= (Depth))) +
  geom_bar(stat="identity")+
  geom_errorbar(aes(ymin=SD_sum_down,
                    ymax=SD_sum_up),
                width=0.25, size=0.3)  +
  facet_wrap(.~Cultivar, ncol=2) +
    theme(text = element_text(size = fs)) +
   theme(axis.text.x=element_text(angle = 45, hjust=1.0)) +
 #  theme(text = element_text(size= fs))+
   scale_fill_manual("legend", values = c("Above"   = "#CCCCCC", "Below" = "#666666" )) +
theme(
     panel.background = element_rect(fill = "white", colour = "black", size = 2, linetype = "solid"), 
     panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "grey"), 
     panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "grey"),
     axis.line = element_line(colour = "black"))+
     theme(strip.background = element_rect(colour = "black", fill = "white",size=1)) +
     ylab("Seed yield (kg/ha)") +
     xlab("Sowing month")
   
    
# 

  ggsave("plot_SeedYield_Prjct1_Iversen2.tiff", width=10, height=14, dpi=600)
  
  
```




then make the graph with total seed yield sum up above and blow seeds and graph it 



```{r}

#Calculate the sum of above and below seeds kg /ha
dfC <-df1 %>%
  group_by(Cultivar, SowTreat,Block,Plot) %>%
  dplyr::select(Seedskg_ha)%>%
  summarise_all(funs(sum)) 


write.table(dfC, "Project1_Total_SeedYieldIv2.txt", row.names=FALSE)
  
  #calculate the mean per cultivars vzs. sowing date 
dfC1<- dfC %>% 
  #filter(SowTreat!="S1", SowTreat!="S6", SowTreat!="S7") %>%
  group_by(Cultivar, SowTreat) %>%
  dplyr::select(Seedskg_ha)%>%
  summarise_all(funs(mean,sd)) %>% 
  mutate(SE=sd/1.73)

dfC1%>%
  ggplot(aes(x=Cultivar, y=(mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=mean-SE/2,
                    ymax=mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(.~SowTreat, scales="free") +
    #labs(y= "Seed kg/ha")+
    ylab(expression(Seed~kg ~per~ha))+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))


```




```{r, gig.height=15, fig.width=15, warning=FALSE}

  df1 %>%
  group_by(Cultivar, SowingD, Depth) %>%
  dplyr::select(Seedskg_ha) %>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x=SowingD, y=(mean))) +
  geom_point(aes(colour=Cultivar), size=6) +
  geom_line(aes(colour=Cultivar)) +
  geom_errorbar(aes(ymin=mean-sd/2,
                    ymax=mean+sd/2), width=0.2)   +
  theme_grey(base_size = 20) +
  theme_bw()+
  theme(text = element_text(size = 24))+
  facet_grid(Depth~., scales="free") +
    labs(y= "Seed yield (kg/ha)")

```

