---
title: "Seed Yield Analysis"
author: "CT"
date: "18.03.2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
This script :
reads the file with burrs and seeds numbers and yields
-merge with dataframe which contains plant population to calculate seed numbers and yield per plant instead of per area 
- This is data exploration...overview ... move to script Project 10 for better correlations



```{r}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
library(knitr)
```

Read File 

```{r, echo=FALSE}

#olde folder setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldIv2")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedYieldIv2")

getwd()
file <- read.table("SeedBurrYield.txt",header=TRUE)
head(file)
summary(file)
```

Define formats 
```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    Date = dmy(Date),
    SowingD = dmy(SowingD)
  )

str(file)
summary(file)
head(file)

```
Calculate the number of seeds per 1 m2 

```{r}

df<- file %>%
  dplyr::select(Cultivar,SowTreat,sample_area_m2,Block,Plot,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seedNo) %>%
  mutate(SeedsNo_m2 = ((seedNo/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,Block,Plot, SeedsNo_m2)

  df <- as.data.frame(df)
head(df)

# Then sum up the above and below seeds to get total value per each plot : calculate as funs (sum) 

dftotal<-df %>%
  group_by(Cultivar,SowTreat, Plot)%>%
  dplyr::select(SeedsNo_m2)%>%
  summarise_all(funs(sum))


```


```{r}
df2<- file %>%
  dplyr::select(Plot, Cultivar, SowingD, SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seed_weight_g) %>%
  #stop here calculate kg seed / ha
  mutate(Seedskg_ha = (((seed_weight_g/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2)*10 ) 


```

 

bring data plant pop 

```{r}


file1 <- read.table("df_emerg_perc3.txt",header=TRUE)
head(file1)
summary(file1)

file2<-file1 %>%
  dplyr::select(Plot, FinalPop,Block)%>%
  mutate(Block=as.factor(Block))


```

then merge the two dataframes by Plot


```{r}
str(df2)

dfmerged <- merge(df2,file2, by=c("Plot")) 
  #mutate(SeedperPlant=SeedsNo_m2/FinalPop)
  #dplyr::select(Plot:SowTreat, Hard_perc,slope)

str(dfmerged)
```


```{r}

relationship<-dfmerged%>%
  dplyr::select(Plot,Cultivar,SowTreat,FinalPop,Seedskg_ha)%>%
  group_by(Plot,Cultivar,SowTreat)%>%
  select(FinalPop,Seedskg_ha)%>%
  summarise_all(funs(mean))

MeanData<-relationship%>%
  group_by(Cultivar,SowTreat)%>%
  select(FinalPop,Seedskg_ha)%>%
  summarise_all(funs(mean))

str(MeanData)
```





```{r,fig.height=5, fig.width=10}


g1 <-MeanData %>%
  ungroup() %>%
  #mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4","S5", "S6","S7","S8"),labels=c("June", #"July", "September", "November","December", "February","March","May")))%>%
  mutate(SowMonth= factor(SowTreat, 
                           levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
                           labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May"))) %>%
  #left_join(df_Photo_dir, by="SowTreat") %>%
  ggplot(aes(x=FinalPop, y= Seedskg_ha))  +
  geom_point(colour= "black", alpha=0.5) +
  geom_point(aes(shape=SowMonth),size=4)+
  scale_shape_manual(values = c(1,2,3,4,5,6,7,8)) +
  geom_text(aes(label=SowMonth),hjust=0, vjust=0,size=7) +
  #geom_errorbar(aes(ymin=PhylC_mean-PhylC_sd/2,
                    #ymax=PhylC_mean+PhylC_sd/2), width=1.5)+
 
  #geom_smooth(method='lm',formula=y~x,alpha=0.1, aes(colour=Pp_dir, fill = Pp_dir)) +
  geom_smooth(method='lm',formula=y~x,alpha=0.1)+
  theme_bw() +
  #xlab(expression(Plant~Population"("plants~/~m"*"^"2"*")")) + 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  #ylab(expression(~Phyllochron~"("^"o"*"Cd/leaf)")) +
  xlab(expression(Plant~Pop))+
  ylab(expression(Seed~Yield~(kg/ha)))+
  theme(text = element_text(size=24))+
  facet_wrap(~Cultivar)+
 #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   
  #label sizes 
theme(text = element_text(size = 24))
  

#grid.arrange(g1, g2, g3,g4,g41)
grid.arrange(g1)
# Save
#ggsave("plot_Phyllochron_PpEmergence.tiff", width=12, height=6, dpi=400)

```


# Get linear coefficients of equations above
##check what are these P values 

```{r}
library(broom)
options(scipen=999)

# create the linear fits by groups o variables
dfreg <- MeanData %>% group_by(Cultivar) %>%
  do(fitreg = lm(FinalPop ~ Seedskg_ha, data = .))

# get the linear coefficients by group in a tidy data_frame
dfCoef <- tidy(dfreg, fitreg)
dfCoef



```



```{r}


dfCoef = glance(dfreg, fitreg)
dfCoef




```





```{r}

#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
#use 3.46 as 2 x 1.73 to grph with SE instead of Sd
  dfmerged %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  #mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
group_by(Cultivar, SowTreat) %>%
    #filter(SowTreat!="S6", SowTreat!="S7")%>%
    dplyr::select(SeedperPlant)%>%
    summarise_all(funs(mean,sd)) %>%
    mutate(SE=sd/1.73)%>%
  ggplot(aes(x=Cultivar, y=(mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=mean-SE/2,     
                    ymax=mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(.~SowTreat, scales="free") +
    #labs(y= "Seed Number per m2")+
    ylab(expression(Seed~number~per~1~plant))+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))


```

Calculate seedyield grams per plant and not per ha 


```{r, fig.height=5, fig.width=10}
#Calculate Seed yield : number g seeds per m2 and then yield kg seeds per ha
#head (file)

df1<- file %>%
  dplyr::select(Cultivar, Plot,SowingD, SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seed_weight_g) %>%
 
   #stop here calculate g / m2
  mutate(Seedsgperm2 = (((seed_weight_g/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2)*1 )%>%
  
  #calculate sum of ablove and below seeds  
   group_by(SowTreat,Cultivar, Plot) %>%
  dplyr::select(Seedsgperm2)%>%
   summarise_all(funs(sum))

  df1 <- as.data.frame(df1)
str(df1)

#write.table(df1, "SeedYieldIv2.txt", row.names=FALSE)

```




then merge the two dataframes by Plot

```{r}
dfmerged2 <- merge(df1,file2, by=c("Plot")) %>%
  mutate(GramSeedperPlant=Seedsgperm2/FinalPop)
  #dplyr::select(Plot:SowTreat, Hard_perc,slope)


str(dfmerged2)
```

```{r}

str(relationship)

Se <-relationship %>%
  dplyr::select(Plot,Seedskg_ha)

str(Se)


```

```{r}


dfMerge3 <- merge(dfmerged2, Se, by="Plot")%>%
  mutate(Index=GramSeedperPlant*FinalPop)

str(dfMerge3)

```



get means 

```{r}
MeanDataIndex<-dfMerge3%>%
 
  group_by(SowTreat)%>%
  select(Index ,GramSeedperPlant,FinalPop,Seedsgperm2)%>%
  summarise_all(funs(mean))



```


```{r,fig.height=5, fig.width=10}


g1 <-MeanDataIndex %>%
  ungroup() %>%
  #mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4","S5", "S6","S7","S8"),labels=c("June", #"July", "September", "November","December", "February","March","May")))%>%
  mutate(SowMonth= factor(SowTreat, 
                           levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
                           labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May"))) %>%
  #left_join(df_Photo_dir, by="SowTreat") %>%
  ggplot(aes(x=FinalPop, y= Seedskg_ha))  +
  geom_point(colour= "black", alpha=0.5) +
  geom_point(aes(shape=SowMonth),size=4)+
  scale_shape_manual(values = c(1,2,3,4,5,6,7,8)) +
  geom_text(aes(label=SowMonth),hjust=0, vjust=0,size=7) +
  #geom_errorbar(aes(ymin=PhylC_mean-PhylC_sd/2,
                    #ymax=PhylC_mean+PhylC_sd/2), width=1.5)+
 
  #geom_smooth(method='lm',formula=y~x,alpha=0.1, aes(colour=Pp_dir, fill = Pp_dir)) +
  geom_smooth(method='lm',formula=y~x,alpha=0.1)+
  theme_bw() +
  #xlab(expression(Plant~Population"("plants~/~m"*"^"2"*")")) + 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  #ylab(expression(~Phyllochron~"("^"o"*"Cd/leaf)")) +
  xlab(expression(Plant~Pop))+
  ylab(expression(Seed~Yield~(kg/ha)))+
  theme(text = element_text(size=24))+
  facet_wrap(~Cultivar)+
 #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   
  #label sizes 
theme(text = element_text(size = 24))
  

#grid.arrange(g1, g2, g3,g4,g41)
grid.arrange(g1)
# Save
#ggsave("plot_Phyllochron_PpEmergence.tiff", width=12, height=6, dpi=400)

```


Ispect means gram seed per plant

```{r}

MeanGramperPlant<-dfmerged2%>%
group_by(SowTreat)%>%
  dplyr::select(GramSeedperPlant)%>%
  summarise_all(funs(sum))



```


Graph the grams of seed per plant 



```{r}

#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
#use 3.46 as 2 x 1.73 to grph with SE instead of Sd
  dfmerged2 %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  #mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
group_by(Cultivar, SowTreat) %>%
    dplyr::select(GramSeedperPlant)%>%
    summarise_all(funs(mean,sd)) %>%
    mutate(SE=sd/1.73)%>%
  ggplot(aes(x=Cultivar, y=(mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=mean-SE/2,     
                    ymax=mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(.~SowTreat, scales="free") +
    #labs(y= "Seed Number per m2")+
    ylab(expression(Seed~grams~per~1~plant))+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))


```

Variable Number Seeds per Plant

Find mean for each sowTreat and cultivar to write abstract

```{r}
MeanSowTreat <-dfmerged %>%
# group_by( SowTreat) %>%
  group_by( Cultivar, SowTreat)%>%
    filter(SowTreat!="S6", SowTreat!="S7")%>%
    dplyr::select(SeedperPlant)%>%
    summarise_all(funs(mean,sd)) %>%
    mutate(SE=sd/1.73)


#write a table to gather all data for finding the best Sowtreat for each cultivar 

write.table(MeanSowTreat, "SeedNumberPerPlant.txt")
```



ANOVA and Means for number of seeds per plant in each sowTreat 

## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S6","S7")

sdIndex <- unique(dfmerged$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```


```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- dfmerged %>%
  filter(SowTreat==sdIndex[i])

  #Variable = SeedperPlant
  
  head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(SeedperPlant~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

 if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
   print("***Sig Cultivar***") 
 print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } # do if
# 
# # if ((summary(my.anova)[[1]][["Pr(>F)"]][2])<0.05) {print("***Sig SowTreat***")
# #    print((LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")))
# #    } 
# if ((summary(my.anova)[[1]][["Pr(>F)"]][3])<0.05) {print("***Sig Block***")
#   print((LSD.test(my.anova, c("Block"), alpha= 0.05, p.adj="none")))
#   } 
# # if ((summary(my.anova)[[1]][["Pr(>F)"]][4])<0.05) {print("***Sig CV:Depth Int***")
# #   print((LSD.test(my.anova, c("cv:depth"), alpha= 0.05, p.adj="none")))
} 
# 
# # make mean separation if significant

#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  

```