---
title: "Seed Number and yield   "
author: "CT"
date: "19.02.2016"
output:
  word_document: default
  pdf_document: default
  html_document: default
  
  #This script  reads the SeedBurrYield and tests Data first anaylsed in SeedYieldProject1
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(rgr)
```


```{r loadFile}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldIv2")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedYieldIv2")

getwd()



df_seedY <- read.table("SeedYieldIv2.txt",header=TRUE)
head(df_seedY)
summary(df_seedY)


```


Here ANOVA according S. Saville advice : LSD test unprotected by sowing date individually
Report values in chapter whcih are the sum of the Above and below seed yields.'

Here overall SowTreat and Cultivar exploration of means 

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df_seedY)

df_seedYS6 <- df_seedY 
  #filter(SowingD=="2015-06-24")
  #filter(SowingD=="2015-07-28")
  #filter(SowingD=="2015-09-15")
  #filter(SowingD=="2015-11-05")
  #filter(SowingD=="2016-02-17")
  #filter(SowingD=="2016-03-15")
  

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6%>%
  filter(SowTreat!="S1")


file.subset <- file 

head(file.subset)
summary(file.subset)


```

```{r}
#ANOVA
my.anova <- aov(Seedskg_ha ~ Cultivar*SowTreat + Depth, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ SowTreat + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Cultivar+ Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Depth + Block, data = file.subset)
summary(my.anova)
```
```{r}
#plot(my.anova)
```

This is Tukeys test for mean comparison 

```{r}
posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)

posthoc

```

This is the mean separation using Tukey 


```{r}

fogo <-HSD.test(my.anova, 'Cultivar', group=TRUE)
fogo

```



Then use multiple comparisons of means and get the standard errors (std)
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))
```

Now run the Tukeys Honest test 

```{r}

#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))


```







S1


```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df_seedY)

df_seedYS6 <- df_seedY %>%
  filter(SowingD=="2015-06-24")
  #filter(SowingD=="2015-07-28")
  #filter(SowingD=="2015-09-15")
  #filter(SowingD=="2015-11-05")
  #filter(SowingD=="2016-02-17")
  #filter(SowingD=="2016-03-15")

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

```{r}
#ANOVA
#my.anova <- aov(Seedskg_ha ~ Cultivar*Depth + Block, data = file.subset)
my.anova <- aov(Seedskg_ha ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means and get the standard errors (std)
```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))
```


S2

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df_seedY)

df_seedYS6 <- df_seedY %>%
  #filter(SowingD=="2015-06-24")
  filter(SowingD=="2015-07-28")
  #filter(SowingD=="2015-09-15")
  #filter(SowingD=="2015-11-05")
  #filter(SowingD=="2016-02-17")
  #filter(SowingD=="2016-03-15")

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

```{r}
#ANOVA
my.anova <- aov(Seedskg_ha ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means and get the standard errors (std)
```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))
```

S3


```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df_seedY)

df_seedYS6 <- df_seedY %>%
  #filter(SowingD=="2015-06-24")
  #filter(SowingD=="2015-07-28")
  filter(SowingD=="2015-09-15")
  #filter(SowingD=="2015-11-05")
  #filter(SowingD=="2016-02-17")
  #filter(SowingD=="2016-03-15")

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

```{r}
#ANOVA
my.anova <- aov(Seedskg_ha ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Depth + Block, data = file.subset)

summary(my.anova)
```

Then use multiple comparisons of means and get the standard errors (std)
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none"))
```

s4


```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df_seedY)

df_seedYS6 <- df_seedY %>%
  #filter(SowingD=="2015-06-24")
  #filter(SowingD=="2015-07-28")
  #filter(SowingD=="2015-09-15")
  filter(SowingD=="2015-11-05")
  #filter(SowingD=="2016-02-17")
  #filter(SowingD=="2016-03-15")

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

```{r}
#ANOVA
my.anova <- aov(Seedskg_ha ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ SowTreat + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ Cultivar*Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means and get the standard errors (std)
```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))
```

s6

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df_seedY)

df_seedYS6 <- df_seedY %>%
  #filter(SowingD=="2015-06-24")
  #filter(SowingD=="2015-07-28")
  #filter(SowingD=="2015-09-15")
  #filter(SowingD=="2015-11-05")
  filter(SowingD=="2016-02-17")
  #filter(SowingD=="2016-03-15")

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

```{r}
#ANOVA
#my.anova <- aov(Seedskg_ha ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ SowTreat + Block, data = file.subset)
my.anova <- aov(Seedskg_ha ~ Cultivar*Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means and get the standard errors (std)
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c( "Cultivar", "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))
```

s7

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df_seedY)

df_seedYS6 <- df_seedY %>%
  #filter(SowingD=="2015-06-24")
  #filter(SowingD=="2015-07-28")
  #filter(SowingD=="2015-09-15")
  #filter(SowingD=="2015-11-05")
  #filter(SowingD=="2016-02-17")
  filter(SowingD=="2016-03-15")

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

```{r}
#ANOVA
#my.anova <- aov(Seedskg_ha ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(Seedskg_ha ~ SowTreat + Block, data = file.subset)
my.anova <- aov(Seedskg_ha ~ Cultivar*Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means and get the standard errors (std)
```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))
```









