---
title: "Seed Yield Analysis"
author: "CT"
date: "18.03.2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
This script :
reads the file with burrs and seeds numbers and yields
-merge with dataframe which contains plant population to calculate seed numbers and yield per plant instead of per area 



```{r}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
library(knitr)
```

Read File 

```{r, echo=FALSE}

#olde folder setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldIv2")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedYieldIv2")

getwd()
file <- read.table("SeedBurrYield.txt",header=TRUE)
head(file)
summary(file)
```

Define formats 
```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    Date = dmy(Date),
    SowingD = dmy(SowingD)
  )

str(file)
summary(file)
head(file)

```
Calculate the number of seeds per 1 m2 

```{r}

df<- file %>%
  dplyr::select(Cultivar,SowTreat,sample_area_m2,Block,Plot,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seedNo) %>%
  mutate(SeedsNo_m2 = ((seedNo/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,Block,Plot, SeedsNo_m2)

  df <- as.data.frame(df)
head(df)

# Then sum up the above and below seeds to get total value per each plot : calculate as funs (sum) 

dftotal<-df %>%
  group_by(Cultivar,SowTreat, Plot)%>%
  dplyr::select(SeedsNo_m2)%>%
  summarise_all(funs(sum))


```

bring data plant pop 

```{r}


file1 <- read.table("df_emerg_perc3.txt",header=TRUE)
head(file1)
summary(file1)

file2<-file1 %>%
  dplyr::select(Plot, FinalPop,Block)%>%
  mutate(Block=as.factor(Block))


```

then merge the two dataframes by Plot

```{r}
dfmerged <- merge(dftotal,file2, by=c("Plot")) %>%
  mutate(SeedperPlant=SeedsNo_m2/FinalPop)
  #dplyr::select(Plot:SowTreat, Hard_perc,slope)


str(dfmerged)
```




```{r}

#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
#use 3.46 as 2 x 1.73 to grph with SE instead of Sd
  dfmerged %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  #mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
group_by(Cultivar, SowTreat) %>%
    filter(SowTreat!="S6", SowTreat!="S7")%>%
    dplyr::select(SeedperPlant)%>%
    summarise_all(funs(mean,sd)) %>%
    mutate(SE=sd/1.73)%>%
  ggplot(aes(x=Cultivar, y=(mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=mean-SE/2,     
                    ymax=mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(.~SowTreat, scales="free") +
    #labs(y= "Seed Number per m2")+
    ylab(expression(Seed~number~per~1~plant))+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))


```

Calculate seedyield grams per plant and not per ha 


```{r, fig.height=5, fig.width=10}
#Calculate Seed yield : number g seeds per m2 and then yield kg seeds per ha
#head (file)

df1<- file %>%
  dplyr::select(Cultivar, Plot,SowingD, SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seed_weight_g) %>%
 
   #stop here calculate g / m2
  mutate(Seedsgperm2 = (((seed_weight_g/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2)*1 )%>%
  
  #calculate sum of ablove and below seeds  
   group_by(SowTreat,Cultivar, Plot) %>%
  dplyr::select(Seedsgperm2)%>%
   summarise_all(funs(sum))

  df1 <- as.data.frame(df1)
str(df1)

#write.table(df1, "SeedYieldIv2.txt", row.names=FALSE)

```

then merge the two dataframes by Plot

```{r}
dfmerged2 <- merge(df1,file2, by=c("Plot")) %>%
  mutate(GramSeedperPlant=Seedsgperm2/FinalPop)
  #dplyr::select(Plot:SowTreat, Hard_perc,slope)


str(dfmerged2)
```

Graph the grams of seed per plant 



```{r}

#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
#use 3.46 as 2 x 1.73 to grph with SE instead of Sd
  dfmerged2 %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  #mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
group_by(Cultivar, SowTreat) %>%
    dplyr::select(GramSeedperPlant)%>%
    summarise_all(funs(mean,sd)) %>%
    mutate(SE=sd/1.73)%>%
  ggplot(aes(x=Cultivar, y=(mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=mean-SE/2,     
                    ymax=mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(.~SowTreat, scales="free") +
    #labs(y= "Seed Number per m2")+
    ylab(expression(Seed~grams~per~1~plant))+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))


```

Variable Number Seeds per Plant

Find mean for each sowTreat and cultivar to write abstract

```{r}
MeanSowTreat <-dfmerged %>%
# group_by( SowTreat) %>%
  group_by( Cultivar, SowTreat)%>%
    filter(SowTreat!="S6", SowTreat!="S7")%>%
    dplyr::select(SeedperPlant)%>%
    summarise_all(funs(mean,sd)) %>%
    mutate(SE=sd/1.73)


#write a table to gather all data for finding the best Sowtreat for each cultivar 

write.table(MeanSowTreat, "SeedNumberPerPlant.txt")
```



ANOVA and Means for number of seeds per plant in each sowTreat 

## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S6","S7")

sdIndex <- unique(dfmerged$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```


```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- dfmerged %>%
  filter(SowTreat==sdIndex[i])

  #Variable = SeedperPlant
  
  head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(SeedperPlant~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

 if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
   print("***Sig Cultivar***") 
 print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } # do if
# 
# # if ((summary(my.anova)[[1]][["Pr(>F)"]][2])<0.05) {print("***Sig SowTreat***")
# #    print((LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")))
# #    } 
# if ((summary(my.anova)[[1]][["Pr(>F)"]][3])<0.05) {print("***Sig Block***")
#   print((LSD.test(my.anova, c("Block"), alpha= 0.05, p.adj="none")))
#   } 
# # if ((summary(my.anova)[[1]][["Pr(>F)"]][4])<0.05) {print("***Sig CV:Depth Int***")
# #   print((LSD.test(my.anova, c("cv:depth"), alpha= 0.05, p.adj="none")))
} 
# 
# # make mean separation if significant

#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  

```