---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "11.01.2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(gridExtra)

```
sow
-This script reads the weather conditions for the  seed filling period (R7-R12) and average plant population and seed yield  uses the combo : 

SeedYieldAndPlantPopAndTemRainR6_R11


-Combines the info about the max hardness and slope hardseed breakdown 
-Attempt to establish correlation between the different variates 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldIv2")
getwd()

#create file
df_SowHvst <- read.table("SeedYieldAndPlantPopAndTemRainR6_R11.txt",header=TRUE)

head(df_SowHvst)
# change format 


```

```{r}


df_All<-df_SowHvst

str(df_All)



  
  
 # create an ID of each chunk
df_All <- df_All %>%
  #dplyr::select(-Date) %>%
  mutate(codeID = as.factor(paste0(SowTreat,"_",Cultivar)))
  

  
  

```





Now plot variates to find  ...any correlation? 




```{r, fig.height=5, fig.width=10}

str(df_All)

pairs(~SeedkgHa+RainIrrig+SoilTemp+PlantPop,data=df_All, main="Simple Scatterplot Matrix")
  
# dfD <- df_All%>%
#   filter(Cultivar=="Denmark")
# pairs(~HardAccum+slope+Rain+RH+Temp,data=dfD, main="Simple Scatterplot Matrix Denmark")

```

then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

#find coefficients 

cor (df_All[,-c(1,2)])
# cor (dfD[,-c(1,2)])
```

Plot plant po and Weather variables with seed yield 
remove Monti S4 (outlier)


```{r, fig.height=10, fig.width=10}
#hardAccum vs Rain 

g1 <-df_All %>%
  #filter(codeID!="S4_Monti")%>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  # mutate(Cultivar= factor(Cultivar, 
  #                          levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),
  #                          labels=c("A", "D", "L", "M", "N.", "W"))) %>%
                           
  ggplot(aes(x=RainIrrig, y= SeedkgHa))  +
  geom_point(aes(shape=SowTreat, colour=Cultivar ),size=7)+
  #geom_text(aes(label=Cultivar, colour=SowTreat),hjust=0, vjust=0,size=7) +
  #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Rain~"("*"mm"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  ylab(expression(Seed~Yield~"("*"kg/ha"*")"))+
  theme(text = element_text(size=20))+
  ylim(0,3500)+
  #facet_wrap(~Cultivar)+
  #theme(title =  element_text(size=14))
 #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
    
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
  #theme(legend.position="bottom")
  theme(legend.position = "none") 
#+
  #theme(title =  element_text(size=14))
  


 g2 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
   mutate(Cultivar= factor(Cultivar, 
                           levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),
                           labels=c("A", "D", "L", "M", "N.", "W"))) %>%
  ggplot(aes(x=SoilTemp, y= SeedkgHa))  +
 # geom_point(colour= "black", alpha=0.2) +
   geom_point(aes(shape=SowTreat, colour=Cultivar ),size=7)+
  #geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
     ylim(0,3500)+
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
 ylab(expression(Seed~Yield~"("*"kg/ha"*")"))+
  theme(text = element_text(size=20))+
  #facet_wrap(~Cultivar)
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
 #+
 theme(legend.position = "none")
  #theme(title =  element_text(size=14))
  #theme(legend.position="bottom")
 
 
 g3 <-df_All %>%
  # filter(codeID!="S4_Monti")%>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=PlantPop, y= SeedkgHa))  +
  #geom_point(colour= "black", alpha=0.2) +
  #geom_point(aes(shape=SowTreat),size=4)+
   geom_point(aes(shape=SowTreat, colour=Cultivar ),size=7)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
     ylim(0,3500)+
 xlab(expression(Plant~number~per~m^"2"))+  
 ylab(expression(Seed~Yield~"("*"kg/ha"*")"))+
  theme(text = element_text(size=20))+
  #facet_wrap(~Cultivar)
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   theme(legend.position = "none")
 #+
   # theme(legend.position="bottom")
  #theme(title =  element_text(size=14))
  
grid.arrange(g3, g2, g1)
# Save
#ggsave("plot_MaxHard_WeatherTSowHvst.png", width=12, height=6, dpi=400)


```


##Plant Pop
##remove Montti S4 data

```{r}
library(broom)
options(scipen=999)

str(df_All)

##Remove outlier montis4
MeanData <-df_All %>%
  filter(codeID!="S4_Monti")


# create the linear fits by groups o variables
#dfreg <- MeanData %>% group_by(Cultivar) %>%
dfregPop <- MeanData %>%
  do(fitreg = lm(SeedkgHa ~  PlantPop, data = .))

# get the linear coefficients by group in a tidy data_frame
dfCoef <- tidy(dfregPop, fitreg)
dfCoef

```



```{r}

dfCoef = glance(dfregPop, fitreg)
dfCoef

##R2 = 0.32 means r=0.56, Pvalue =0.0004 for plant pop

```

###############
Exactly -1. A perfect downhill (negative) linear relationship

-0.70. A strong downhill (negative) linear relationship

-0.50. A moderate downhill (negative) relationship

-0.30. A weak downhill (negative) linear relationship

0. No linear relationship
###############################

##Rain

```{r}
library(broom)
options(scipen=999)

str(df_All)

##Remove outlier montis4
MeanData <-df_All%>%
  subset(RainIrrig>50, RainIrrig<100) # filter(codeID!="S4_Monti")


# create the linear fits by groups o variables
#dfreg <- MeanData %>% group_by(Cultivar) %>%
dfregRain <- MeanData %>%
  do(fitreg = lm(SeedkgHa ~ RainIrrig, data = .))

# get the linear coefficients by group in a tidy data_frame
dfCoef <- tidy(dfregRain, fitreg)
dfCoef



```




```{r}

dfCoef = glance(dfregRain, fitreg)
dfCoef

##R2 = 0.08 means r=0.3, Pvalue =0.08 for rain 

```

##Do for Soil temp 

```{r}


library(broom)
options(scipen=999)

str(df_All)

##keep monti
MeanData <-df_All %>%
filter(SowTreat!="S4")%>%
 filter(SowTreat!="S6") 
 

str(MeanData)

# create the linear fits by groups o variables
#dfreg <- MeanData %>% group_by(Cultivar) %>%
dfregSoilT <- MeanData %>%
  do(fitreg = lm(SeedkgHa ~ SoilTemp, data = .))

# get the linear coefficients by group in a tidy data_frame
dfCoef <- tidy(dfregSoilT, fitreg)
dfCoef

```

`


```{r}


dfCoef = glance(dfregSoilT, fitreg)
dfCoef

##R2 = 0.18,  means r=0.4, Pvalue =0.009 for soilTemp 

```


overall correlation inspect for all 3 variables 


##Linear regression with weather parameters between phenophase R8-R12 and SDmax (SDmax=a+bx) are:  r Rain+Irrigation =0.34 (P=0.03);  rRH (%)  = 0.26 (P=0.10) and rAirTemp =0.22 (P=0.17), rsoilTemp =0.14 (P=0.4), rPET =0.08 (P=0.6).   

```{r}

#summary(lm(HardAccum ~ RainIrrig, df_All))
#summary(lm(HardAccum ~ RH, df_All))
#summary(lm(HardAccum ~ Temp, df_All))
#summary(lm(HardAccum ~ SoilTemp, df_All))
summary(lm(HardAccum ~ PET, df_All))
#summary(lm(HardAccum ~ DiffRainPET, df_All))




```


This loop checks the lm for all cultivars 

```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_All$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_All %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required 
  
    #summary(lm(HardAccum ~ RainIrrig, df_subset))  
    #summary(lm(HardAccum ~ RH, df_subset))
    summary(lm(HardAccum ~ Temp, df_subset))
  #print
    
print(summary(lm(HardAccum ~ RainIrrig, df_subset)))
#print(summary(lm(HardAccum ~ RH, df_subset)))
   # print(summary(lm(HardAccum ~ Temp, df_subset)))

  } 


```



Plot Weather variables with RAte of Hardseed breakdown  during R8-R12



```{r, fig.height=12, fig.width=15}
#hardAccum vs Rain 

g11 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RainIrrig, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
  #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  #geom_text(aes(label=SowTreat),hjust=0, vjust=0,size=7) +
  xlab(expression(Rain+Irrigation~"("*"mm"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
 ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  
#slope vs RH
g12 <-df_All %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  
 g13 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Temp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
  # geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) +
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 g14 <-df_All %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 g15 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=PET, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
 xlab(expression(PET~"("*"mm"*")"))+  
 ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
   
    theme(text = element_text(size=20))+
   theme(axis.text.x = element_text( 
                           size=12, angle=45 ))+
  facet_wrap(~Cultivar)+
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 
 # g42 <-df_All %>%
 #   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
 #  ggplot(aes(x=DiffRainPET , y= slope))  +
 #  geom_point(colour= "black", alpha=0.2) +
 #  geom_point(aes(shape=SowTreat),size=4)+
 #   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
 #  theme_bw() +
 # xlab(expression(Water~balance~"("*"mm"*")"))+  
 #  ylab(expression(SDmax~"("*"%"*")"))+
 #  theme(text = element_text(size=20))+
 #  facet_wrap(~Cultivar)
  
grid.arrange(g11, g12, g13,g14,g15)
# Save
#ggsave(file="whatever.pdf", g1, g2, g3,g4,g41)
#ggsave("plot_MaxHard_EnviroTSowHvst.png", width=14, height=7, dpi=400)


```



old graph




```{r, fig.height=10, fig.width=15}
#Hardbreak vs Rain 

g4 <-df_All %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RainIrrig, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RainIrrig~"("*"mm"*")"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#hardAccum vs RH
g5 <-df_All %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  
 g6 <-df_All %>%
     mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Temp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 
 
 g7 <-df_All %>%
     mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 
 
 
 g8 <-df_All %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=PET, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(PET~"("*"mm"*")"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
 
  
grid.arrange(g4, g5, g6, g7,g8)
# Save
# ggsave(file="Fig_weather.tiff", dpi = 300)

#ggsave("plot_HardBreak_WeatherTSowHvst.png", width=12, height=6, dpi=400)


```
 Inspect correlation overall 
 
 overall correlation inspect for all 3 variables ; remember here slope is the decrease in percentage units 
 
 data generated was : Linear regression with weather parameters between phenophase R8-R12 and SDmax (SDmax=a+bx) are:  r Rain+Irrigation =0.26 (P=0.1);  rRH (%)  = 0.37 (P=0.02) and rAirTemp =0.22 (P=0.18), rsoilTemp =0.39 (P=0.02), rPET =0.31(P=0.06).   

```{r}

#summary(lm(slope ~ RainIrrig, df_All))
#summary(lm(slope ~ RH, df_All))
#summary(lm(slope ~ Temp, df_All))
#summary(lm(slope ~ SoilTemp, df_All))
summary(lm(slope ~ PET, df_All))
```

This loop checks the lm for all cultivars 

```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_All$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_All %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required 
  
    #summary(lm(HardAccum ~ RainIrrig, df_subset))  
    #summary(lm(HardAccum ~ RH, df_subset))
    summary(lm(slope ~ RH, df_subset))
  #print
    
print(summary(lm(slope ~ RH, df_subset)))
#print(summary(lm(HardAccum ~ RH, df_subset)))
   # print(summary(lm(HardAccum ~ Temp, df_subset)))

  } 


```






```{r}

#markdown::render("<C:\\GitHubRepos\\SubCloverPhD\\SubClover\\HardseedsProject1Read.Rmd>") 
```


