---
output:
  word_document: default
  html_document: default
---
---
title: "SeedPer1m2  "
author: "CT"
date: " renew 05.08.2017 (from the 28 December script 2016)"
output:
  word_document: default
  pdf_document: default
  
  #This script  reads the SeedNumberm2_Iv2 and performs ANOVA on variate seednumber per1m2
---

```{r loadLibraries, warning=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(rgr)
```


Aim: Statistics for variable Seed Number per 1 m2. 


```{r loadFile}
#old folder setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldIv2")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedYieldIv2")
getwd()

#REading the dataframe generated in SeedYieldProject1 script

df_seedY<- read.table("SeedNumberper1m2.txt",header=TRUE)
head(df_seedY)
summary(df_seedY)


```


Define formats 
```{r}

# define factors and formats
file <- df_seedY %>%
  mutate(
    #Plot = as.factor(Plot),
    #Date = dmy(Date),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    SowTreat = as.factor(SowTreat)
  )

str(file)
summary(file)
head(file)

```

Here only need to change df name as selection of fields were previously done. 

```{r}

df<- file
#   dplyr::select(Cultivar,SowTreat,
#                 Depth,Block)
# 
#   df <- as.data.frame(df)
# head(df)


```

For graphics check  SeedYieldProject1 script 
This graph already shows the SE (std/1.73)

```{r, fig.height=5, fig.width=10}


#barplot for seed density  
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
  dfA <-df %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%

  group_by(Cultivar, SowTreat,Depth) %>%
  summarise_each(funs(mean,sd)) %>% 
  mutate(SE=SeedsNo_m2_sd/1.73)
  
  dfA %>%
  ggplot(aes(x=Cultivar, y=(SeedsNo_m2_mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=SeedsNo_m2_mean-SE/2,
                    ymax=SeedsNo_m2_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(Depth~SowTreat, scales="free") +
    #labs(y= "Seed Number per m2")+
    ylab(expression(Seed~number~per~m^"2"))+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))
```






Here ANOVA according S. Saville advice : LSD test unprotected by sowing date individually.
Use filter to sub set data (sowing date)

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df 
#%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change the variables (comment out/in) to get mean values and ANOVA info. 
Select :SowTreat or Depth or Cultivar 

```{r}
#ANOVA

#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ SowTreat*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means for desired variables. Remember to sum up the values of seed number (above + below) 
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

Individual sowing dates 
analysis 

S1

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
#%>%
  filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change the variables (comment out/in) to get mean values and ANOVA info. 
Select :SowTreat or Depth or Cultivar 

```{r}
#ANOVA

#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means for desired variables. Remember to sum up the values of seed number (above + below) 
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

S2


```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
#%>%
  #filter(SowTreat=="S1")
  filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change the variables (comment out/in) to get mean values and ANOVA info. 
Select :SowTreat or Depth or Cultivar 

```{r}
#ANOVA

#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means for desired variables. Remember to sum up the values of seed number (above + below) 
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```
s3

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
#%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change the variables (comment out/in) to get mean values and ANOVA info. 
Select :SowTreat or Depth or Cultivar 

```{r}
#ANOVA

#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means for desired variables. Remember to sum up the values of seed number (above + below) 
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

s4

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
#%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change the variables (comment out/in) to get mean values and ANOVA info. 
Select :SowTreat or Depth or Cultivar 

```{r}
#ANOVA

#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means for desired variables. Remember to sum up the values of seed number (above + below) 
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

s6

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
#%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change the variables (comment out/in) to get mean values and ANOVA info. 
Select :SowTreat or Depth or Cultivar 

```{r}
#ANOVA

#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means for desired variables. Remember to sum up the values of seed number (above + below) 
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

s7

```{r}
#Filter  S1, S2, S3, S6 , S7 
summary(df)

df_seedYS6 <- df %>%
#%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change the variables (comment out/in) to get mean values and ANOVA info. 
Select :SowTreat or Depth or Cultivar 

```{r}
#ANOVA

#my.anova <- aov(SeedsNo_m2 ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(SeedsNo_m2 ~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsNo_m2 ~ Depth + Block, data = file.subset)
summary(my.anova)
```

Then use multiple comparisons of means for desired variables. Remember to sum up the values of seed number (above + below) 
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Depth"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c( "Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```



End of script.
