---
title: "Seed Yield Iv2 6CV and environment "
author: "CT"
date: "19.06.2018"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(gridExtra)

```
sow
-This script reads the weather conditions for thw whole growing period (from sowing to  harvest (RH, TEMP, RainIrrig) : EnviroSowToHarvest.txt
-Combines the info about the seed yield mean for each cultivar in each sowing date  
-Attempt to establish correlation between the different variates 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedYieldIv2")
getwd()

#create file
df_SowHvst <- read.table("EnviroSowToHarvest.txt",header=TRUE)
head(df_SowHvst)
# change format 


```

now gather and create SowTreat column


```{r}

df_SowHvst <-df_SowHvst %>%
  gather(key= "SowTreat" , value = "Value" , S1:S7)
  

```


bring data frame with seed yield (rawdata similar to script 1 )


```{r}

setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedYieldIv2")

getwd()
file <- read.table("SeedBurrYield.txt",header=TRUE)
head(file)
summary(file)

```



Define formats 
```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Depth = as.factor (Depth),
    Date = dmy(Date),
    SowingD = dmy(SowingD)
  )

str(file)
summary(file)
head(file)

```


Calculate the seed yield 

```{r}

df1<- file %>%
  dplyr::select(Cultivar, SowingD, SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g,seed_weight_g) %>%
  #stop here calculate kg seed / ha
  mutate(Seedskg_ha = (((seed_weight_g/bur_weight_subSample_g)*
           bur_total_weight_g)/sample_area_m2)*10 ) 



```




```{r}


df1 %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  group_by(Cultivar, SowTreat,Depth) %>%
  summarise_each(funs(mean,sd))



```


then make the table  with total seed yield sum up above and blow seeds and graph it 



```{r,fig.heigt=5, fig.width=10}


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)


#Calculate the sum of above and below seeds kg /ha
dfC <-df1 %>%
  group_by(Cultivar, SowTreat,Block) %>%
  dplyr::select(Seedskg_ha)%>%
  summarise_all(funs(sum)) 
  
  #calculate the mean per cultivars vzs. sowing date 
dfC1<- dfC %>% 
  #filter(SowTreat!="S1", SowTreat!="S6", SowTreat!="S7") %>%
  group_by(Cultivar, SowTreat) %>%
  dplyr::select(Seedskg_ha)%>%
  summarise_all(funs(mean,sd)) %>% 
  mutate(SE=sd/1.73)

dfC1%>%
  ggplot(aes(x=Cultivar, y=(mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=mean-SE/2,
                    ymax=mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(.~SowTreat, scales="free") +
    #labs(y= "Seed kg/ha")+
    ylab(expression(Seed~kg ~per~ha))+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))


```




then merge with the weather data (df_SowHvst) ...and the see yield dataframe (dfC1) 
Need t spread variables RH, Temp and Rain first to create same number of rows  

```{r}

str(df_SowHvst)

##first spread 
df_SowHvst1 <-df_SowHvst %>%
  spread(Variable, Value)

# then merge 
df_All <- merge(dfC1, df_SowHvst1, by=c("Cultivar","SowTreat"))

# # then change the variable name mean = SeedYield  
 df_All <-df_All %>%
   mutate (SeedYield=1*(mean))

str(df_All)
```


inspect means 

```{r}

MeanAirTemp<- df_All %>%
  group_by(SowTreat)%>%
 dplyr::select(Temp , SeedYield)%>%
  summarise_all(funs(mean))

```


Now plot variates to find  ...any correlation? 




```{r, fig.height=5, fig.width=10}

str(df_All)

pairs(~SeedYield+RainIrrig+RH+Temp,data=df_All, main="Simple Scatterplot Matrix")
  
# dfD <- df_All%>%
#   filter(Cultivar=="Denmark")
# pairs(~HardAccum+slope+Rain+RH+Temp,data=dfD, main="Simple Scatterplot Matrix Denmark")

```

then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

#find coefficients 

cor (df_All[,-c(1,2)])
# cor (dfD[,-c(1,2)])
```

Plot Weather variables with Maximum Percentage of Hardseeds 


```{r, fig.height=15, fig.width=15}
#hardAccum vs Rain 

g1 <-df_All %>%
  ggplot(aes(x=RainIrrig, y= SeedYield))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Rain+Irrigation~"("*"mm"*")"))+ 
  ylab(expression(Seed~Yield~"("*"kg/ha"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#SeedYield vs RH
g2 <-df_All %>%
  ggplot(aes(x=RH, y= SeedYield))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(Seed~Yield~"(kg/ha)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  
 g3 <-df_All %>%
  ggplot(aes(x=Temp, y= SeedYield))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(Seed~Yield~"(kg/ha)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 
  
grid.arrange(g1, g2, g3)
# Save
#ggsave("plot_SeedYield_WeatherTSowHvst.png", width=12, height=6, dpi=400)


```
This loop checks the lm 

```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_All$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_All %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required 
  
    #summary(lm(SeedYield ~ RainIrrig, df_subset))  
    #summary(lm(SeedYield ~ RH, df_subset))
    summary(lm(SeedYield ~ Temp, df_subset))
  #print
    
#print(summary(lm(SeedYield ~ RainIrrig, df_subset)))
#print(summary(lm(SeedYield ~ RH, df_subset)))
    print(summary(lm(SeedYield ~ Temp, df_subset)))

  } 


```



```{r}

#markdown::render("<C:\\GitHubRepos\\SubCloverPhD\\SubClover\\HardseedsProject1Read.Rmd>") 
```


