---
title: "Emergence seedlings I2 and Pok graphs with Mean Soil Temp extended range "
author: "CT"
date: "17.08.2017"
output: html_document
---

This script does this:

-get dataframe combined with Iversen and Pok RAte  Emergence and mean soil Temp for Woogenellup only between 5 and 15.62 degrees 
- optimum mean Temp for Woogenellup is 15.62 


stopped here 
```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
library (gridExtra)
```

get file 

```{r loadFile}
# Get dataframe from previous script (written table )
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\EmergenceIverPokComb")
getwd()

#create file
df_G <- read.table("RateEmerg_SoilTemp_IverPokComb.txt",header=TRUE)



```

select columns of interest and Adjust formats 
```{r}

#change formats
df_G$Cultivar <- as.factor(df_G$Cultivar)
df_G$Block <- as.factor(df_G$Block)
df_G$Plot <- as.factor(df_G$Plot)
df_G$Location <- as.factor(df_G$Location)

#select columns 
df_G <-df_G %>%
dplyr:: select(Plot,Block,Cultivar,SowTreat,meanTemp_Em, InvDAS50E,Location)


str(df_G)

# this is to "clean previous dfs : df_emerg4 <- NULL
```

Subset cultivar Woogenellup between temperature 5 to max 15.62

```{r}

#subset Cultivar

df_W <-df_G %>%
subset(Cultivar=="Woogenellup")

#subset Temperature range 
df_W1 <-df_W %>%
  subset (meanTemp_Em>5 & meanTemp_Em<15.46)

str(df_W1)

#remove SowingDate 1and 8  from both locations 
df_W2 <- df_W1 %>%
   subset (SowTreat=="S2"| SowTreat=="S3"|SowTreat=="S3"|SowTreat=="S4"|  SowTreat=="S5"|
             SowTreat=="S6"|SowTreat=="S7") 
          

```



```{r}


df_W3 <-df_W2 %>%
  dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E, Location) %>%
  group_by(SowTreat,Cultivar, Location) %>%
  summarise_each(funs(mean)) %>%
  mutate(y=InvDAS50E,x=meanTemp_Em) %>%
  dplyr::select(-meanTemp_Em, -InvDAS50E, -Plot)

str(df_W3)

```

got the means here ... and graph it

```{r, fig.height=5, fig.width=10, echo = FALSE}
df_W3%>%
ggplot(aes(x=x, y=y, colour=SowTreat, shape=Location))  +
  geom_point(alpha=0.8, size= 3) +
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Soil~temperature~~"("^"o"*"C)")) + 
  ylab(" Mean Rate (1/ Days) to 50% emergence") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=12))+
 scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.25))


# 

```



here get the equations for the Woogenellup subset (min to optimum)  

```{r, fig.height=5,fig.width=10}
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}

#use all datapoints 
df <- df_W2 %>%
  dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E, Location) %>%
  group_by(SowTreat,Cultivar, Location) %>%
  summarise_each(funs(mean)) %>%
  mutate(y=InvDAS50E,x=meanTemp_Em) %>%
  dplyr::select(-meanTemp_Em, -InvDAS50E)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  #ggplot(data = df, aes(x=x, y=y, colour=SowTreat, shape=Location))+
  #ggplot(aes(x=x, y=y, colour=SowTreat, shape=Location))
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_point(aes(colour = factor(Location)), size=5) + scale_shape(solid = FALSE)+ 
  
  theme_bw()+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.25))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE) + 
  facet_grid(Cultivar~.,scales="free")
  
p1
```

End of this script
 