---
title: "Emergence seedlings I2 and Pok graphs with Mean Soil Temp extended range "
author: "CT"
date: "17.08.2017"
output: html_document
---

This script does this:
- This was Derrick;s idea of extending the soil Temp range (16.08.2017)
- get dataframe combined with Iversen and Pok DASto50% Emergence and mean soil Temp (this is produced in individual location folders!!)  
- Calculate the rate for this new dataframe 
-graph y=Days to 50% emergence ; x= mean soil Temp
-graph y= 1/days to 50% emergence ; x= mean soil Temp




```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
library (gridExtra)
```


```{r loadFile}
# Get dataframe from previous script (written table )
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergenceIverPokComb")
getwd()

#create file
df_G <- read.table("EmergIvPokComb.txt",header=TRUE)

str(df_G)


```

Adjust formats 
```{r}

df_G$Date50E <- ymd(df_G$Date50E)
df_G$Date50E <- ymd(df_G$Date50E)
df_G$SowingDate <- ymd(df_G$SowingDate )
df_G$Location <- as.factor(df_G$Location)
df_G$Cultivar <- as.factor(df_G$Cultivar)
df_G$Block <- as.factor(df_G$Block)
df_G$Plot <- as.factor(df_G$Plot)

str(df_G)

# this is to "clean previous dfs : df_emerg4 <- NULL
```

Include 1/DAS50E 


```{r}

df_H <- df_G %>%
  mutate(InvDAS50E= 1/ DAS50E)

#Save the dataframe with values 
write.table(df_H, "RateEmerg_SoilTemp_IverPokComb.txt")
```

Here Graph with sowTreat discrimated
```{r, fig.height=5, fig.width=10, echo = FALSE}



fontSize <- 12.0

#DAS50E
#g1 <- df_H %>%
  #filter(year %in% 1960:2000) %>%
  #group_by(day) %>%
 # summarise_each(funs(mean)) %>%
  g1 <- df_H %>%
  ggplot(aes(x=meanTemp_Em, y=DAS50E, colour=SowTreat))  +
  geom_point(alpha=0.8) +
  #geom_smooth()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Estimated~Soil~temperature~~"("^"o"*"C)")) +  
  ylab("Days to 50% emergence  (days)") +
    facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=11))+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,40))

# 1/DAS50E
  g2 <- df_H %>%
  ggplot(aes(x=meanTemp_Em, y=InvDAS50E, colour=SowTreat))  +
  geom_point(alpha=0.8) +
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Estimated~Soil~temperature~~"("^"o"*"C)")) + 
  ylab(" Rate (1/ Days) to 50% emergence") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=11))+
 scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.25))
  grid.arrange(g1, g2)
# 

# 

```
Here discriminate location 


```{r, fig.height=10, fig.width=10, echo = FALSE}

fontSize <- 12.0

#DAS50E
#g1 <- df_H %>%
  #filter(year %in% 1960:2000) %>%
  #group_by(day) %>%
 # summarise_each(funs(mean)) %>%
  g1 <- df_H %>%
  ggplot(aes(x=meanTemp_Em, y=DAS50E, colour=SowTreat))  +
  geom_point(alpha=0.8,) +
  geom_point(aes(shape=Location, size=4))+
  #geom_smooth()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Soil~temperature~~"("^"o"*"C)")) +  
  ylab("Days to 50% emergence  (days)") +
    facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=11))+
    theme(legend.position="top") +
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,40))

# 1/DAS50E
  g2 <- df_H %>%
  ggplot(aes(x=meanTemp_Em, y=InvDAS50E, colour=SowTreat))  +
  geom_point(alpha=0.8) +
  geom_point(aes(shape=Location, size=4))+
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Soil~temperature~~"("^"o"*"C)")) + 
  ylab(" Rate (1/ Days) to 50% emergence") +
  facet_grid(.~Cultivar, scales="free")+
    theme(legend.position="top") +
  theme(text = element_text(size=11))+
 scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.25))
  grid.arrange(g1, g2)
# 

# 

```

make the graph with means 






here get the equations from all temperatures 

```{r, fig.height=7,fig.width=12}
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}


df <- df_H %>%
  dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E) %>%
  group_by(SowTreat,Cultivar) %>%
  summarise_each(funs(mean)) %>%
  mutate(y=InvDAS50E,x=meanTemp_Em) %>%
  dplyr::select(-meanTemp_Em, -InvDAS50E)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_point()+
  theme_bw()+
  scale_x_continuous(limits = c(0,25))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE) + 
  facet_grid(Cultivar~.,scales="free")
  
p1
```


Try to leave S1 and S8 out of that 

```{r fig.height=6, fig.width=12, echo = FALSE, warning=FALSE}

#graph S2-S8 



fontSize <- 12.0

#DAS50E
#g1 <- df_H %>%
  #filter(year %in% 1960:2000) %>%
  #group_by(day) %>%
 # summarise_each(funs(mean)) %>%
  g1 <- df_H %>%
    filter(SowTreat!="S1")%>%
    filter(SowTreat!="S8")%>%
  ggplot(aes(x=meanTemp_Em, y=DAS50E,shape=Cultivar))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  #geom_smooth()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
 xlab("Mean Soil Temp (oC)") + 
  ylab("Days to 50% emergence  (days)") +
    facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=10))+
  geom_smooth(method = "lm") # +
  # scale_x_continuous(limits = c(0,25))+
  # scale_y_continuous(limits = c(0,40))

# 1/DAS50E
  g2 <- df_H %>%
    filter(SowTreat!="S1")%>%
    filter(SowTreat!="S8")%>%
  ggplot(aes(x=meanTemp_Em, y=InvDAS50E, shape=Cultivar))  +
  geom_point(colour= "red", alpha=0.2) +
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  geom_smooth(method = "lm")+
  theme_bw() +
  xlab("Mean Soil Temp (oC)") + 
  ylab(" Rate (1/ Days) to 50% emergence") +
  facet_grid(.~Cultivar, scales="free")+
 theme(text = element_text(size=10)) #+
 # scale_x_continuous(limits = c(0,17))+
 #  scale_y_continuous(limits = c(0,0.25))
  grid.arrange(g1, g2)
# 

  
  grid.arrange(g1, g2)

```




Here get the graph for all cultivars or filter to look at specific cultivar  



```{r, fig.height=10, fig.width=10, echo = FALSE}

fontSize <- 12.0

#DAS50E
#g1 <- df_H %>%
  #filter(year %in% 1960:2000) %>%
  #group_by(day) %>%
 # summarise_each(funs(mean)) %>%
  g10 <- df_H %>%
    #filter(Cultivar=="Woogenellup")%>%
    ggplot(aes(x=meanTemp_Em, y=DAS50E, colour=SowTreat))  +
  geom_point(alpha=0.8) +
  geom_point(aes(shape=Location, size=4))+
  #geom_smooth()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Soil~temperature~~"("^"o"*"C)")) +  
  ylab("Days to 50% emergence  (days)") +
    facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=11))+
    theme(legend.position="top") +
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,40))

# 1/DAS50E
  g20 <- df_H %>%
  #filter(Cultivar=="Woogenellup")%>%
  ggplot(aes(x=meanTemp_Em, y=InvDAS50E, colour=SowTreat))  +
  geom_point(alpha=0.8) +
  geom_point(aes(shape=Location, size=4))+
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Soil~temperature~~"("^"o"*"C)")) + 
  ylab(" Rate (1/ Days) to 50% emergence") +
  facet_grid(.~Cultivar, scales="free")+
    theme(legend.position="top") +
  theme(text = element_text(size=11))+
 scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.25))
  grid.arrange(g10, g20)
# 

# 

```


get mean and Sd for Woogenelup DAS50E 

```{r, fig.height=5; fig.width=10}




df_mean <- df_H %>%
    #filter(Cultivar=="Woogenellup")%>%
    group_by(Cultivar,Location, SowTreat,SowingDate) %>%
  dplyr::select(DAS50E,meanTemp_Em) %>%
  summarise_all(funs(mean,sd)) 

str(df_mean)

 df_mean %>%
  ggplot(aes(x=meanTemp_Em_mean, y=DAS50E_mean, colour=SowTreat, shape=Location)) +
  geom_point(size=4.5) +
  #geom_line() +
 #facet_grid(Depth~Cultivar) +
  labs(x="Soil Temperature",y="Days to 50% Emergence for Woogenellup") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=DAS50E_mean-DAS50E_sd/1.73,
                    ymax=DAS50E_mean+DAS50E_sd/1.73))+
  theme_bw()+
  ylim(0,60)+
  theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 11))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 12))




```

analyse  InvDAS50E
```{r, fig.height=5, fig.width=10}
df_mean2 <- df_H %>%
    #filter(Cultivar=="Woogenellup")%>%
    #group_by(Cultivar,Location, SowTreat,SowingDate) %>%
  group_by(Location, SowTreat,SowingDate) %>%
  dplyr::select(InvDAS50E,meanTemp_Em) %>%
  summarise_all(funs(mean,sd)) 

str(df_mean2)

 df_mean2 %>%
  ggplot(aes(x=meanTemp_Em_mean, y=InvDAS50E_mean, colour=SowTreat, shape=Location)) +
  geom_point(size=4.5) +
  #geom_line() +
 #facet_grid(Depth~Cultivar) +
  labs(x="Soil Temperature",y="Rate (1/days) 50% Emergence") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=InvDAS50E_mean-InvDAS50E_sd/1.73,
                    ymax=InvDAS50E_mean+InvDAS50E_sd/1.73))+
  theme_bw()+
  ylim(0,0.3)+
  theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 11))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 12))
```

then find linear equations for the segment 1 ascending ()


```{r fig.height=5, fig.width=10}

require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}

#use mean values for all cultivars 
df <- df_mean2 %>%
  
  #use this or segment 1 : ascend temp 0-15.7
  subset(meanTemp_Em_mean>0 & meanTemp_Em_mean<15.7) %>%
  
   #use this for segment 2 : descend temp >15.7
  #subset(meanTemp_Em_mean>15.7 & meanTemp_Em_mean<30) %>%
  
  mutate(y=InvDAS50E_mean,x=meanTemp_Em_mean) %>%
  dplyr::select(-meanTemp_Em_mean, -InvDAS50E_mean)

#eq <- ddply(df,.(Location),lm_eqn)
eq <- ddply(df,.(),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.20)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="grey", linetype= 2, formula = y ~ x) +
  geom_point(aes(shape=Location, colour=Location), size=4)+
  theme_bw()+
  scale_x_continuous(limits = c(0,35))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE)  
  #facet_grid(Location~.,scales="free")
  
p1

```

```{r}
#get statistical summary here 
summary(lm(y ~ x, df))
```


Output:both locations 

Segment 1 (ascending): y=-0.026+0.013x (R2=0.457)
Segment 2 (descending): y=0.023-0.007 x (R2=0.052)
