 ---
title: "SeedWeight_Analysis Growth Chamber "
author: "CT"
date: " , 2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default

---
Purpose : 

Calculation for the seed individual weight  (g)
use file RawData : GCSeedRawData.txt

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
library(extrafont)
library(knitr)

```




Read File 

```{r, echo=FALSE}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GCBurSeed")
getwd()
file <- read.table("GCSeedRawData.txt",header=TRUE)
head(file)


#summary(file)
```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  mutate(
    BurrStage = as.factor(BurrStage),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar)
   
  )

str(file)
summary(file)

```



Statistical Analysis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select y variable to analyse

```{r}

#select variable :  IndividualSeedWeight.mg
df_seedANOVA_1 <- file%>%
dplyr:: select(Cultivar:BurrStage, IndividualSeedWeightmg)
```

subset for anova
```{r}

 
summary(df_seedANOVA_1)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA_1 

head(file.subset)
summary(file.subset)

```


## ########ANOVA#############

```{r}

#ANOVA

my.anova <- aov(IndividualSeedWeightmg ~ Cultivar * BurrStage + Block, data = file.subset)
#my.anova <- aov(SeedsPerM2 ~ Cultivar + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("BurrStage"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar", "BurrStage"), alpha= 0.05, p.adj="none")) 
```

Performey Tukey's test 

```{r}
posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)

posthoc


```

Then 
This is the mean separation using Tukey 


```{r}

fogo <-HSD.test(my.anova, 'Cultivar', group=TRUE)
fogo

```

Correlate with the values of Nichols and Actual seed lots weights

```{r}
#Bring data Nichols 

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Bur16cv")
getwd()
df_SeedComp <- read.table("CVTrial2016_SeedWeightCompare.txt",header=TRUE)
head(df_SeedComp)
summary(df_SeedComp)



```

merge with the seed weight dataframe by Cultivar 

```{r}

#dataframes to merge : df_burSubset and df_SeedComp
str(df_burSubset)
str(df_SeedComp)

df_Merged <- merge(df_burSubset,df_SeedComp, by="Cultivar")

```

Now  create the graph with Nichols standard seed weight 9x)and the measured weithgs in Y axis. 
 


```{r,fig.height=5, fig.width=10}



str(df_Merged)

df_Merged %>%
   ggplot(aes(x=S2Nichols, y=mean)) + # mean=measured value
   geom_point(aes(shape= Cultivar), size=5)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6))+
  geom_point()+
  geom_errorbar(aes(ymin=mean-SE/2,
                    ymax=mean+SE/2),width=0.5)+
   
  #edit the size of error bars for Errol
  #geom_errorbar(aes(ymin=mean-ci, ymax=mean+ci),
                 # width=1,
                  #size=0.5
  
  
#facet_wrap(~Month_f,ncol=3, scales = "free")+
  theme_bw(base_size=16)+
  #scale_x_continuous(breaks = c(1,200,300))+
 ylim(4, 12)+
 xlim(4, 12)+
theme(axis.text.y = element_text( size = 26))+
theme(axis.title.y = element_text(face="bold", size=22))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 22,face="bold"))+
theme(axis.title.x = element_text( size=24))+
  labs(y="Measured seed weight (mg) ",x="Reported seed weight (mg) ")
 # geom_abline(intercept = 50, slope = 0)


#ggsave("plot_SeedWeightComparison.png", width=12, height=6, dpi=400)


```

then compare seed weight with Actual seeds used to sow! 



```{r,fig.height=5, fig.width=10}


loadfonts(device = "win")

str(df_Merged)

df_Merged %>%
   ggplot(aes(x=S3Actual, y=mean)) + # mean=measured value
   geom_point(aes(shape= Cultivar), size=5, stroke=2)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6))+
  geom_point()+
  geom_errorbar(aes(ymin=mean-SE/2,
                    ymax=mean+SE/2),size=0.85,width=0.4)+
#facet_wrap(~Month_f,ncol=3, scales = "free")+
  theme_bw(base_size=16)+
  #scale_x_continuous(breaks = c(1,200,300))+
 ylim(4, 12)+
  xlim(4, 12)+
  #labels
  annotate("text", x=5, y=11, label= "r = 0.80", size = 8,family="serif") +
  
  annotate("text", x=6, y=7.5, label= "C", size = 8,family="serif", face="bold") +
  annotate("text", x=7, y=6.5, label= "D", size = 8,family="serif", face="bold") +
  annotate("text", x=8, y=6.3, label= "R", size = 8,family="serif", face="bold") +
  annotate("text", x=9, y=7.0, label= "N", size = 8,family="serif", face="bold") +
  annotate("text", x=9, y=9.1, label= "M", size = 8,family="serif", face="bold") +
  annotate("text", x=10, y=10.4, label= "W", size = 8,family="serif", face="bold") +
  annotate("text", x=11, y=10.3, label= "A", size = 8,family="serif", face="bold") +
  
#geom_text(aes(label=text), family="Times", fontface="italic")+
#theme(axis.text.y = element_text( size = 26, family="Serif"))+
#theme(axis.title.y = element_text( face="bold", size=22))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 26,face="bold"))+
theme(axis.title.x = element_text( size=26))+
  
  theme(axis.text.y=element_text(angle = 0, hjust=0.5,vjust=0,size = 26,face="bold"))+
  theme(axis.title.y = element_text( size=26))+
  
  labs(y="Measured seed weight (mg) ",x="Initial seed weight (mg) ")+
  
  
  theme(text=element_text(size=26,  family="serif"))+
  theme(title=element_text(size=26,  family="serif"))+
  theme(title=element_text(size=26,  family="serif"))+


#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))

print(df_Merged)
 # geom_abline(intercept = 50, slope = 0)



ggsave("plot_SeedWeightComparison_Actual.png", width=12, height=6, dpi=400)


```


end of this script 