---
title: "PCA Test with fake data "
author: "CT"
date: "Wednesday, Mai 23, 2018"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

Purpose:

-Test a new R code for PCA analysis 
 

this method is available at : https://www.r-bloggers.com/computing-and-visualizing-pca-in-r/

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(mosaic)
library(lattice)

```


```{r loadFile}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergenceIv2")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\PCATest")
getwd()

#create file
df_raw <- read.table("Data.txt",header=TRUE)


```



```{r}

str(df_raw)



# define factors for the ones that "look like" values
df_raw$Treatments <- as.factor(df_raw$Treatments)
df_raw$V2 <- as.numeric(df_raw$V2)
df_raw$V3<- as.numeric(df_raw$V3)

str(df_raw)




```


```{r}
# apply PCA - scale. = TRUE is highly 
# advisable, but default is FALSE. 

#leave only numbers here 

df_worked<-df_raw %>%
  dplyr::select(V1:V3)
  
df_Treatments <- df_raw %>%
dplyr::select(Treatments)


str(df_worked)

Data.pca <- prcomp(df_worked,
                 center = TRUE,
                 scale. = TRUE) 





```

Print 

```{r}

# print method
print(Data.pca)


```

The plot method returns a plot of the variances (y-axis) associated with the PCs (x-axis). 

```{r}

# plot method
plot(Data.pca, type = "l")

```

The summary method describe the importance of the PCs. The first row describe again the standard deviation associated with each PC. The second row shows the proportion of the variance in the data explained by each component while the third row describe the cumulative proportion of explained variance. We can see there that the first two PCs accounts for more than {95\%} of the variance of the data.

```{r}

# summary method
summary(Data.pca)

```

biplot 

```{r}

biplot (Data.pca)

```




