---
title: "Flowering 6CV"
author: "CT"
date: "06.07.2017"
output: html_document
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
```
This script calculates the 50 % Flowering - DAS and TTAS for Poukawa based on script FlowPok1

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowPok")
getwd()

#create file ; this file was generated in the previous script FlowerProject2

df_P <- read.table("df_flowerPo3.txt",header=TRUE)

head(df_P)


```

#Prepare dataframe 
#Just change colum title name  and select only columns of interest 
#Do it to get similat columns as Iversen scripts (see script FlowerProject3)


```{r}

df_P <- df_P %>%
select(SowingD:PlotNumber,DAS, Percent,TTAS)%>%
mutate(Plot=as.numeric(PlotNumber))%>%
  dplyr::select(-PlotNumber)



str(df_P)

```

#Adjust formats 

```{r}

df_P <- df_P%>%
  mutate(Date=ymd(Date),SowingD=ymd(SowingD)) %>%
mutate(Percent=as.numeric(Percent))%>%
  mutate(DAS=as.numeric(DAS))%>%
  mutate(SimpleCat_Perc=as.numeric(1*Percent))

str(df_P)


```



Find 50 Percent of the variable bud  for cultivar and sowtreat.This considers only average values 

```{r Calc50PercFlower}

# Average by plots
#dplyr used

df_50_Perc <- df_P %>%
  group_by(Cultivar,SowTreat, Date, SowingD,DAS,Block,Plot) %>%
  summarise(av_Perc = mean(Percent), 
            av_TT = mean(TTAS),
            av_DAS=mean(DAS))

#functions use
str(df_50_Perc)
summary(df_50_Perc)
head(df_50_Perc)

write.table(df_50_Perc, "df_50_Perc.txt")

#  loop to calculate tt_50p_flow for each var x sd x cv
cv <- unique(df_50_Perc$Cultivar)
var <- unique(df_50_Perc$Variable)
sow <- unique(df_50_Perc$SowTreat)
sowd <- unique(df_50_Perc$SowingD)
#block <- unique(df_50_Perc$Block)
#plot <- unique(df_50_Perc$Plot)


# create empty df
df_tt_50p_flow <- data.frame(SowingD = NULL,
                             Cultivar = NULL, 
                             SowTreat = NULL,
                             #Variable = NULL, 
                             DAS= NULL,
                             #Plot=NULL,
                             #Block=NULL,
                             TT50F = NULL)

#loop trough each combination of factor levels

for(i in 1:length(cv)) {
  #for(j in 1:length(var)){
    for(k in 1:length(sow)){
      
      # clean value holders
      DAS_50p_flow <- 0
      tt_50p_flow <- 0
      
    
      #print(paste0(cv[i]," ",var[j]," ", sow[k]))
      print(paste0(cv[i]," ", sow[k]))
      # filter for each combination

  df_sub <- df_50_Perc %>%
    subset(Cultivar == as.character(cv[i]) &
    #Variable == as.character(var[j]) &
    SowTreat == as.character(sow[k]))
  
  df_sub
  
  # create percentage with maximum value recorded 
  # to avoid crossing the 50% line twice
  
  df_sub$av_Perc_max <- 0 # create new col
  
  for(z in 1:nrow(df_sub)) {
    
    df_sub$av_Perc_max[z] <- max(df_sub$av_Perc[z],
                                 df_sub$av_Perc_max[z-1])
    
  }
  
  df_sub
  head(df_sub)
  tail(df_sub)

  # Interpolate 
  y_ref <- 50 # y value where we want to find x by interpolation
  
  # interpolate
  #find DAS at 50 Pecent Flower 

  tryCatch(  
  DAS_50p_flow <- approx(df_sub$av_Perc_max, 
  df_sub$av_DAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  DAS_50p_flow <- NA
  }
)
  #find TT at 50 Pecent Flower
  tryCatch(  
  tt_50p_flow <- approx(df_sub$av_Perc_max, 
  df_sub$av_TT , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  tt_50p_flow <- NA
  }
)

  df_temp <- NULL
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             #Variable = df_sub$Variable[1], 
                             SowTreat = df_sub$SowTreat[1],
                             SowingD = df_sub$SowingD[1], 
                             DAS50F = DAS_50p_flow,
                             TT50F = tt_50p_flow)
                        
  
  df_tt_50p_flow <- rbind(df_tt_50p_flow,df_temp)
      
    } 
  }
 #}


summary(df_tt_50p_flow)



write.table(df_tt_50p_flow,"df_tt_50p_fl.txt")

summary(df_tt_50p_flow)


```


Create a loop with the values per plot



```{r}


plots <- unique(df_P$Plot)

#loop trough each combination of factor levels

for (p in 1:length(plots)) {
#  for(j in 1:length(var)){
 #   for(k in 1:length(sow)){
      



      
      # clean value holders
      DAS_50p_flow <- 0
      tt_50p_flow <- 0
      
     
      # filter for each combination

df_sub <- df_P %>%
    # subset(Cultivar == as.character(cv[i]) &
    # Plot == as.character(var[j]) &
    #   Block == as.character(var[b]) &
    # SowTreat == as.character(sow[k])) %>%
    subset(Plot == plots[p]) %>%
    arrange(Percent)
    #arrange(DAS)
      
      df_sub
  head(df_sub)
  # create percentage with maximum value recorded 
  # to avoid crossing the 50% line twice
  
  df_sub$av_Perc_max <- 0 # create new col
  
  for(z in 1:nrow(df_sub)) {
    
    df_sub$av_Perc_max[z] <- max(df_sub$Percent[z],
                                 df_sub$Percent[z-1])
    
  }

  
  df_sub
  head(df_sub)
  tail(df_sub)
  
  
  # Interpolate 
  y_ref <- 50 # y value where we want to find x by interpolation
  
  # interpolate
  #find DAS at 50 Pecent Emergence 

  tryCatch(  
  DAS_50p_flow <- approx(df_sub$Percent, 
  df_sub$DAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  DAS_50p_flow <- NA
  }
)
  #find TT at 50 Pecent Flowering
  tryCatch(  
  tt_50p_flow <- approx(df_sub$Percent, 
  df_sub$TTAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  tt_50p_flow <- NA
  }
)

   df_temp <- NULL
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             Percent = df_sub$Percent[1], 
                             SowTreat = df_sub$SowTreat[1],
                             Plot = df_sub$Plot[1],
                             Block = df_sub$Block[1],
                             DAS50F = DAS_50p_flow,
                             TT50F = tt_50p_flow)

 print(p)
  
  if(p == 1) {
    df_tt_50p_Flo <- df_temp
  } else {
   df_tt_50p_Flo <- rbind(df_tt_50p_Flo,df_temp) 
  }                     
  } 

# end plot loop
  
```

Check dataframe 

```{r}

summary (df_tt_50p_Flo) 
  
##Fantastic!!! continue from here! 

```

## Calculate Rate Flowering


```{r GraphResults}

dfRateFloPok <-df_tt_50p_Flo %>%
  mutate(RateFlo=1/DAS50F)
  
str(dfRateFloPok)

```

## Incorporate the mean Pp and Mean temp in the next script....

##That's Super  store this dataframe as txt table 
```{r}


#Save as table 
write.table(dfRateFloPok, "df_TTDAS_RateFlower50F_Po.txt")


```





