---
title: "Flowering 6CV Pok "
author: "CT"
date: "06.07.2017"
output: html_document
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
```
This script reads the DAS and TTAS for Poukawa based on script FlowPok2. Then calculates the date of flowering and relates to weather conditions at flowering : temp and Pp 


```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowPok")
getwd()

#create file ; this file was generated in the previous script FlowerProject2

df_P <- read.table("df_tt_50p_flow.txt",header=TRUE)

str(df_P)


```
Calculate the date of 50% flowering 

```{r}
df_P2 <-df_P %>%
  mutate(SowingD=as.Date(SowingD))%>%
  mutate(Date=(SowingD+DAS50F))
  
  str(df_P2)
```

Then bring the weather data (temp and Pp) and merge 


```{r}
df_Weather <- read.table("Pok_Weat.txt",header=TRUE)
str(df_Weather)

d1<-df_Weather %>%
  mutate(Tmean=Tx-Tm/2)%>%
  mutate(Date=dmy(Date))



```

Now find the mean temp and PP for S2, S3 and S4


Notes about weather Pok during 50% Flower :

S2 27 August - 04 Oct mean Temp 12.4oC and 12.8Pp 

S3 24 Sept -15 Oct 13.2 oC and 13.7Pp

S4 27-09 - 31 Oct 15oC and 14.1 Pp

```{r}

df_S2 <-d1%>%
  subset(Date>"2016-08-27" & Date<"2016-10-04")%>%
  summarise_all(funs(mean))
  

df_S3 <-d1%>%
  subset(Date>"2016-09-24" & Date<"2016-10-15")%>%
  summarise_all(funs(mean))

df_S4 <-d1%>%
  subset(Date>"2016-09-27" & Date<"2016-10-31")%>%
  summarise_all(funs(mean))
  
```

