---
title: "Runners Growth Chamber "
author: "CT"
date: "17.08.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Analysis of runner elongation for Growth chamber experiment from previous script (use Runner)
- Calculate the time to reach 50% plants with runner (2 plant means 100%  : as all  plants had produced runners )
- Calculate rate of runner appearance (1/Days) 
 - variable Runner is already in percentage!!! 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```



```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GCRunner")
getwd()
#create file
#use file generated in script 1: GCNumber_Runner
#df_Runner <- read.table("Number_Runner.txt",header=TRUE)

df_Runner <- read.table("GCNumber_Runner.txt",header=TRUE)
str(df_Runner)


```


Define formats 

```{r loadFile}


# define factors for the ones that "look like" values

df_run_worked <- df_Runner %>%
  mutate(SowingDate = ymd(SowingDate), 
         ReadingDate = ymd(ReadingDate),
         DAS = as.numeric(DAS),
         Plot= as.factor(Plot),
         Block=as.factor(Block),
         Cultivar=as.factor(Cultivar))
        # SowTreat=as.factor(SowTreat))%>%
  #dplyr::select(-s1,-s2,-s3,-s4,-s5,-s6,-s7,-s8,-s9,-s10)

 

```


```{r}

str(df_run_worked)

```



update the loop

```{r}

plots <- unique(df_run_worked$Plot)
 
df_all <- data.frame()

for(p in 1:length(plots)) {

      # clean value holders
      DAS_50_run <- 0

  df_sub <- df_run_worked %>%
    subset(Plot == plots[p]) %>%
    arrange(Runner)
  
  df_sub
  head(df_sub)
 
   # record maximum value recorded to avoid crossing- FIXME: Not needed here?
  max_runner <- max(df_sub$Runner) # create new col
  
  # for(z in 1:nrow(df_sub)) {
  #   
  #   df_sub$max_run[z] <- max(df_sub$NumberRun[z],
  #                                df_sub$NumberRun[z-1])
  #   
  # }
  # 
  df_sub
  
  
  ##############################################
   # Interpolate 
  y_ref <- 50 # y value where we want to find x by interpolation in this case needed 50  
  
  # interpolate
  tryCatch(  
 DAS_50_run <- approx(df_sub$Runner, 
  df_sub$DAS, xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
   DAS_50_runs <- max_trifo # FIXME: This should give max but gives NA - quick fix below temporarily
  }
)
  
 # COMPACT SYNTHAX FOR IFELSE when plots had reachedmore than 8 but less than 9 trifoliates ! 
  
 DAS_50_run <- ifelse(is.na( DAS_50_run),max_trifo, DAS_50_run) # FIXME: This should be unecessary if try catch gives max value
 
  df_temp <- NULL 
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             SowingDate = df_sub$SowingDate[1],
                             Plot = df_sub$Plot[1],
                             Block = df_sub$Block[1],
                             DAS50Run = DAS_50_run,
                             RunnerNumber = min(y_ref,max_runner))

#  print(p)
  
df_all <- rbind(df_all,df_temp)                 
  
  } # end plot loop

summary(df_all)


```



Just rename dataframe after the loop  
```{r}

df_50Run <- df_all
summary(df_50Run)


```



Now correct column names after loop not to mix with other generated tables

```{r}

df_50R<-df_50Run%>%
  mutate(DAS=as.numeric(DAS50Run))%>%
  dplyr::select(-DAS50Run)

str(df_50R)
 


```



```{r}

write.table(df_50R,"GC_df_DAS_50toRunner.txt")
```




Calculate RAte (1/days to 50%) 


```{r}

#try 1/DAS50% = Rate

df_RateRunner <- df_50R %>%
  mutate(Rate=1/ DAS)

  summary(df_RateRunner)
  
  write.table(df_RateRunner,"GC_RateRunner.txt")

```



Graph rate and SowTreat

```{r}
#Graph 

#   df_RateRunner %>%
#   group_by(Cultivar) %>%
#   dplyr::select(DAS)%>%
#   summarise_each(funs(mean,sd)) %>%
#   #Graph
#   ggplot(aes(x=, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
#   geom_point() +
#   geom_line() +
#   labs(x="Sowing Date",y="1/ Days to 9 trifoliates  ") +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))+
#   geom_errorbar(aes(ymin=mean-sd/2,
#   ymax=mean+sd/2))+
#   theme_bw()
# 
# df_RateRunner %>%
#   group_by(SowingDate, Cultivar) %>%
#   dplyr::select(Rate) %>%
#   summarise_each(funs(mean,sd)) %>%
#   #Graph
#   ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
#   geom_point() +
#   geom_line() +
#   labs(x="Sowing Date",y="1/ Days to 9 trifoliates  ") +
#   theme(axis.text.x = element_text(angle = 90, hjust = 1))+
#   geom_errorbar(aes(ymin=mean-sd/2,
#   ymax=mean+sd/2))+
#   theme_bw()

```




End of this script Calc 2. 
Move to script 3 to include temperatures  
