---
title: "Runner DA50% and rate to 50% Growth Chamber  "
author: "CT"
date: "17.08.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Combine the rate of runner appearance of 50% plants with one runner  and  Mean Air Temp during runner  appearance  GC experiment  
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```

Get data from Emergence Folder and dates to combine into a dataframe 


```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GCRunner")
getwd()
#create file

df_RunnerRate <- read.table("GC_RateRunner.txt",header=TRUE)



#adjust formats 
df_RunnerRate$SowingDate <- ymd(df_RunnerRate$SowingDate )
df_RunnerRate$Block <- as.factor(df_RunnerRate$Block)
##rename Plot as Pot to harmonise with other scripts 
df_RunnerRate$Pot <- as.factor(df_RunnerRate$Plot)
df_RunnerRate$DAS50Run <- as.numeric(df_RunnerRate$DAS)

```

Create df_MD to workout dates to % runner 
```{r}

  df_MD <- df_RunnerRate %>%
  mutate(DateRunner=SowingDate+DAS) %>%
  group_by(Plot, DAS) %>% 
  dplyr::filter(row_number() == 1)

#str(df_MD)

H <-df_MD %>%
 dplyr:: select (Plot, DateRunner)

#save and store table 
#write.table(H, "GC_DateTo50Runner.txt")

```



##Add the number of days for 50% emergence to calculate the days to runner  after emergence (DAE)

##File ready at : GC_DASToEmergence.txt (already calculated the days after emergence)

 

```{r}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GCRunner")
getwd()
#create file
df_trif2 <- read.table("GC_DASToEmergence.txt",header=TRUE)


str(df_trif2)


```

Define formats 

```{r loadFile}


# define factors for the ones that "look like" values

df_trif2 <- df_trif2 %>%
  mutate(SowingDate = ymd(SowingDate), 
         Date50Emerg = ymd(Date50Emerg),
         DAS_ToEmerg = as.numeric(DAS_ToEmerg))


df_trif2$Pot <- as.factor(df_trif2$Pot)
df_trif2$Block <- as.factor(df_trif2$Block)
df_trif2$Cultivar <- as.factor(df_trif2$Cultivar)
#df_trif$SowTreat <- as.factor(df_trif$SowTreat)

##Reminder !!! Exclude the info ot 1_T ...that comes automatically from excel but not essential here 
 
         

str(df_trif2)


```

##Remove extra columns 



```{r}

##Estimate date for runner appearance after after emergence 
##Here select only columns related to emergence  !! 

df_DatetoEmerg <-df_trif2 %>%
  select(Cultivar:Block,DAS_ToEmerg)
  
  
 ## mutate(DateTo5TFromEmerg=Date50Emerg+ DAE_1T)
  

```




# ################## Quantify Days  from emergence to runner ############

```{r}

#prep dataframe with TT at emergence 


str (df_MD )
##bring data frame above with the runner info: df_MD
#select columns needed : 

df_Runner_select <-df_MD%>%
  select(Cultivar, SowingDate, Block,DAS50Run, Pot)


##bring data frame above : df_trif2

df_trif2Select <-df_trif2%>%
  select(Date50Emerg, Pot,DAS_ToEmerg)

  
df_TempA1 <- merge(df_Runner_select,df_trif2Select,by="Pot")

##inspect  new data frame

 


```

##Now calculate the DAE to Run  


```{r}


##calculate number of days from emergence to runner 
df_TempA1 <- df_TempA1%>%
  mutate(DAEToRun_Em=DAS50Run-DAS_ToEmerg)

str(df_TempA1, warning=FALSE)

```


## continue from here to clean dataframe and perform anova 


```{r}
df_DAEToRunner_Emerg<-df_TempA1 %>%
dplyr::select(Pot, Cultivar, Block,DAEToRun_Em)


```


Check : Inspect means  before ANOVA

```{r}
#Graph 


 # a <- df_RateTrifo %>%

 f <- df_DAEToRunner_Emerg %>%
  group_by( Cultivar) %>%
  dplyr::select(  DAEToRun_Em ) %>%
  summarise_all(funs(mean,sd))



```



## ######################### RUN ANOVA ##########################



```{r ANOVAMaxPlantPop}

#compare DAE_1T  among cultivars

df_ANOVA <- df_DAEToRunner_Emerg %>%
  dplyr::select(Cultivar,Block,Pot,DAEToRun_Em)

```
Overall analysis consider sowing date and cultivar 


```{r}
##Overview   

file <- df_ANOVA 

str(file)
# -----------------------------------------------
#here if transformation is needed 
file$transf_no <- 1*(df_ANOVA$DAEToRun_Em)

head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

```



First LSD  Fisher's

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 

#(LSD.test(my.anova, c("Block"), alpha= 0.05, p.adj="none")) 

```


Perform Tukeys 


This is Tukeys test for mean comparison 




```{r}
posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)
#posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.25)

posthoc

```

Then 
This is the mean separation using Tukey 


```{r}

fogo<-HSD.test(my.anova, 'Cultivar', group=TRUE)
fogo

```

##End of this script. 



