---
title: "Thermal time to reach therunner stage in I2"
author: "CT"
date: "28.11.2017"
output: html_document
---

This script does this:

- get the dataframe with sowing dates and DAS  to 50% of plants with runners 
- get the dataframe with max and min soil temperature in Iversen (soil temperatures gave better fit !!! )  
- merge the two dataframes to calculate the thermal time from sowing to runner stage  using the  Tb= 0 and standard cardinal temps.


#---------------------------------------------------------------------------------------------------------------
use consistent method as per re analysis tb=0, t opt range =15, 22, t max = 35 oC.
# -------------------------------------------------------------------------------------------------------------



```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
```


```{r loadFile}
# Get dataframe 1 with DAS5trifo info 
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\RunnerIv2")
getwd()

#create file
df_run4 <- read.table("df_DAS_50toRunner.txt",header=TRUE)

df_run4$SowingDate <- ymd(df_run4$SowingDate )
df_run4$Block <- as.factor(df_run4$Block)
df_run4$Plot <- as.factor(df_run4$Plot)
# str(df_run4)
# head(df_run4)

D <- df_run4 %>%
dplyr::select(Cultivar,SowTreat, Plot, SowingDate,DAS,Block)

str(D)

df_run4 <- NULL

```


```{r}


#Then calculate the date to 50% Eof plants to have first runner  sum the date or sowing + DAS
#Note df_Md has duplicated rows - fix it!! 

df_MD <- D %>%
  mutate(DateRunner=SowingDate+DAS) 
  # group_by(Plot, DAS) %>% 
  # dplyr::filter(row_number() == 1)

str(df_MD)
#Here DAte9T is included no need to change format 

         
```


Read the temperature  data and adjust formats; here use soil temp 

```{r}

# Get dataframe 1 with the soil Temp 
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\RunnerIv2")
getwd()

#create file here using the soil temperature !!!! 
#this was with air #df_emerg6 <- read.table("RawWeaIv2.txt",header=TRUE)

df_emerg6 <- read.table("SoilTempTXTM.txt",header=TRUE)
head(df_emerg6)

df_emerg6$Date <- dmy(df_emerg6$Date )
# df_emerg4$SowingDate <- ymd(df_emerg4$SowingDate )
# df_emerg4$Block <- as.factor(df_emerg4$Block)
# df_emerg4$Plot <- as.factor(df_emerg4$Plot)
str(df_emerg6)
head(df_emerg6)



```

Add the accumulation of of thermal time use reference as  



#---------------------------------------------------------------------------------------------------------------
use consistent method as per re analysis tb=0, t opt range =15, 22, t max = 35 oC.
# -----------------------------------------------------------------------------------------------------------

 
```{r}
#Create Thermal time cardinal temperatures see data above- TT = Topt - Tb ... 16.7 - (1.0)= 15.7 ! 

#For cardinal temperatures  
#tt_card <- data.frame(temp=c(1,15,22,35),TT=c(0,15,15,0))

#for TT at Tb=0 
tt_card <- data.frame(temp=c(0,15,22,35),TT=c(0,15,15,0))
tt_card %>%
  ggplot(aes(x=temp, y=TT))+
  #labs(x="Temperature (degree Celsius)")+
  #labs(y="Thermal Time (oCd)") +
  geom_line()+
  theme_bw()+
  ylim(0,25)+
xlab(expression(Temperature~"("^"o"*"C)"))+
  ylab(expression(Thermal~Time~Trifoliate~"("^"o"*"Cd)"))+
  theme(axis.text.x=element_text(angle = 0, hjust = 0, size= 14))+
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 14))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 14))+
  theme(axis.title.y=element_text(size= 14))

```

 then make the loop 
 
 
```{r}

#Create and test interpolation function - Test if works 

temp_ref  <- 25 # x-axes reference
temp <- tt_card$temp # x-axes
TT <- tt_card$TT # y-axes


int_func <- function(temp,TT,temp_ref){

  # if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   out <- TT[length(TT)] 
   # FIXME: approx functions seems to do that - need param
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
   # else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  
int_func(temp,TT,temp_ref)

```
 
 use the 3x8 hours formula to calculate daily TT 
```{r}

#create REF Jones CA, Ritchie JT, Kiniry JR, Godwin DC (1986) Subroutine structure.In 'CERES-Maize: A simulation model of maize growth anddevelopment'. (Eds CA Jones, JR Kiniry) pp. 49-194. (Texas A&M University Press: Texas, USA

TTfunc <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
 } 
  
  TTav  <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2 + 0.0053 * n^3) * (Tmax-Tmin)) + Tmin # 8-h temperature
    
    TT_tn <- int_func(tt_card$temp, tt_card$T,tn) 
    
    TTsum <- TT_tn + TTsum
    
   # print(TT_tn)
    
    }
 
   TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc(10,24)

```
 
 
 
- Compares with simple method to calculate Tt with base temperature of 0oC 
```{r, warning=FALSE}

df_We_tt <- df_emerg6 %>%
  #mutate(Date=dmy(Date)) %>%
  rowwise() %>%
  mutate(TTday=TTfunc(Tm,Tx), TTday_s=(Tm+Tx)/2, diff=(TTday_s-TTday))

summary(df_We_tt)

```
 
 
 
```{r}
#Check TT  two methods : TTday_s = simple method (Tmean - Tbzero)
df_We_tt  %>% 
ggplot(aes(x=TTday_s, y= TTday)) +
  geom_point(shape=21,alpha=0.2,colour='red')+
  geom_abline(intercept = 0, slope = 1)

```
 
 
 Then accumulate the TT 
 
 
```{r}

 df_TT <-df_We_tt%>%
    arrange(Date)%>%
    mutate(SumTTday = cumsum(TTday))%>%
  mutate(SUMTTday_s = cumsum(TTday_s)) 
  #dplyr::select(-MeanTt)

#head(df_soilTemp)

summary(df_TT)

#df_emerg6 <- NULL

```


figure out how to calculate tt at sow then tt ate date of 50 % plants with runner  make one minus another to find TT

```{r}
df1 <- merge(df_MD,df_TT, by.x="SowingDate",by.y="Date") %>%
  mutate(AirTempAcc_sow = SumTTday) %>%
  dplyr::select(-SumTTday)
  #filter(Cultivar=="Narrikup")

str(df1)
```


Need to force a date for 50 % runner (round) to calculate the average temperature during runner 
Save dataframe as txt file 

```{r}

# force formats of dates
df1$Date <- round(df1$DateRunner,0)
df_TT$Date <- round(df_TT$Date,0)


  df_merge <- merge(df1, df_TT, by="Date") %>%
    mutate(AirTempAcc_em = SumTTday) %>%
  dplyr::select(-SumTTday) %>%
  mutate(SummTTRunner = (AirTempAcc_em-AirTempAcc_sow))  

summary(df_merge)

 
```

get the TT and SE for the cultivar. exclude Sow treats if needed.

```{r}
df_TT <- df_merge %>%
  select(Date:Plot,Block, DAS,SummTTRunner)
  
   #filter(SowTreat!= "S1")



```

```{r}
#then select sow treat and means and se

df_TTN <-df_TT %>%
  group_by(Cultivar,SowTreat) %>%
  dplyr::select( SummTTRunner)%>%
  summarise_all(funs(mean,sd))%>%
    mutate(SE=sd/1.73)
  
```


```{r}
#save df_TT as table to do statistics in script 7 _ stats Thermal time 

write.table(df_TT,"ThermalT_Runner.txt")
```


Perform Anova 



## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(df_TT$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```

# Then loop anova for each individual sowing date 

```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_TT %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
#my.anova <- aov( DAS5T ~ Cultivar + Block, data = file.subset)
   my.anova <- aov( SummTTRunner ~ Cultivar + Block, data = file.subset)

print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```



perfom anova general 

```{r}


file <- df_TT


file.subs <- file 

head(file.subs)
summary(file.subs)

#ANOVA

#my.anova <- aov(DAS ~ SowTreat + Block, data = file.subs)
my.anova <- aov(SummTTRunner ~ Cultivar + Block, data = file.subs)
#my.anova <- aov(SummTTRunner ~ SowTreat + Block, data = file.subs)

summary(my.anova)
```


```{r}
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))

```



END ...


