---
title: "Runners  Iversen   "
author: "CT"
date: "05.07.2018" 
output:
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:
-bring data from DAS and TT from first trifo (from another folder )
-merge with dataframe ThermalT_Runner 
-calculate DAS and TT from emergence to runner phenophases 
-Analysis of runner initiation for Iversen using the data from emergence event (not from sowing) 
- Calculate stat for the days to reach first runner initiation from emergence 
- Run ANOVA for variable "Number of days to reach runner " and thermal time to runner 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```

Read document generated in script "3" 5Trifo_rate

```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\RunnerIv2")
getwd()

##Path "C:/GitHubRepos/SubCloverPhD/SubClover/RunnerIv2/ThermalT_Runner.txt"

##file ThermalT_Runner.txt
df_R<- read.table("TTFromFirstTrifoToRunner.txt",header=TRUE)

head(df_R)


```



Define formats and calculate the number of trifoliates considering the sub samples (S1-S10)

```{r loadFile}


# define factors for the ones that "look like" values
df_R$Plot <- as.factor(df_R$Plot)
df_R$Block <- as.factor(df_R$Block)
df_R$Cultivar <- as.factor(df_R$Cultivar)
df_R$SowTreat <- as.factor(df_R$SowTreat)

 #df_R <- df_R %>%
 # mutate(SowingDate = ymd(SowingDate)) 

str(df_R)



```





```{r}

df_meanR <-df_R %>%
  dplyr:: select(Plot:SowTreat,DaysRunnerFromRunner, TTFromFirstTrifo)%>%

  #group_by(Cultivar,SowTreat) %>%
  group_by(SowTreat) %>%
  # dplyr::select(SummTT5Trifo)%>%
  # summarise_all(funs(mean,sd))%>%
  #   mutate(SE=sd/1.73)
  
  #summarise_at(c( "SummTTRunner", "TTRunFromEmerg"), mean, na.rm = TRUE)
  summarise_at(c( "DaysRunnerFromRunner", "TTFromFirstTrifo"), mean, na.rm = TRUE)


```




##Run stats for the number of days to reach Runner initiation - use DASRunFromEmerg;
##general use Sow Treat as Factor 

```{r}
 
  file <- df_R


file.subs <- file 

head(file.subs)
summary(file.subs)

#ANOVA

#my.anova <- aov(DASRunFromEmerg ~ SowTreat + Block, data = file.subs)
#my.anova <- aov(DASRunFromEmerg ~ Cultivar + Block, data = file.subs)
my.anova <- aov(TTFromFirstTrifo ~ Cultivar*SowTreat+ Block, data = file.subs)

summary(my.anova)

```


```{r}
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))


```



## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(df_R$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```
## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_R %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(TTFromFirstTrifo ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}


```

Then run for TT 




```{r}
 
  file <- df_mergedRunner


file.subs <- file 

head(file.subs)
summary(file.subs)

#ANOVA

#my.anova <- aov(TTRunFromEmerg ~ SowTreat + Block, data = file.subs)
#my.anova <- aov(TTRunFromEmerg ~ Cultivar + Block, data = file.subs)
my.anova <- aov(TTRunFromEmerg ~ Cultivar*SowTreat+ Block, data = file.subs)

summary(my.anova )

(LSD.test(my.anova, c("SowTreat", "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))

```




## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(df_mergedRunner$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```
## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_mergedRunner %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(TTRunFromEmerg ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```




