---
title: "Runners  Iversen   "
author: "CT"
date: "05.07.2018" 
output:
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:
-bring data from DAS and TT from first trifo (from another folder )
-merge with dataframe ThermalT_Runner 
-calculate DAS and TT from emergence to runner phenophases 
-calculate Pp at runner  

 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```

Read document generated in script "3" 5Trifo_rate

```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\RunnerIv2")
getwd()

##Path "C:/GitHubRepos/SubCloverPhD/SubClover/RunnerIv2/ThermalT_Runner.txt"

##file ThermalT_Runner.txt
#df_R<- read.table("TTFromFirstTrifoToRunner.txt",header=TRUE)
df_R<- read.table("DateTo50Runner.txt",header=TRUE)
head(df_R)


```



Define formats and calculate the number of trifoliates considering the sub samples (S1-S10)

```{r loadFile}


## define factors for the ones that "look like" values
df_R$Plot <- as.factor(df_R$Plot)
df_R$DAS <- as.numeric(df_R$DAS)
#df_R$Cultivar <- as.factor(df_R$Cultivar)
#df_R$SowTreat <- as.factor(df_R$SowTreat)

 df_R <- df_R %>%
  mutate(Date = ymd(DateRunner))
  

str(df_R)



```


bring Pp data and merge 
Bring the photoperiod data 

```{r}

df_Photo <- read.table("Photoperiod.txt",header=TRUE)

# rename date column for merge
df_Photo <- df_Photo %>%
mutate(SowingDate = Date)
head(df_Photo)

# convert to date format
df_Photo <- df_Photo %>%
mutate(Date=dmy(Date))

str(df_Photo)

```

```{r}

str(df_Photo)

merged<-merge(df_R, df_Photo, by="Date")%>%
  mutate(PpRunner=1*Pp)%>%
  select(-Pp)



```




Define formats and calculate the number of trifoliates considering the sub samples (S1-S10)

```{r loadFile}


write.table(merged, "PpatRunnerV12.txt")



```

End of this script 