---
title: "Seed Status_ 6CV"
author: "CT"
date: "31.10.2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(markdown)
#install.packages(markdown)

```
Here calculate the total percentage off abnormal seeds for cultivars and sow treat 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\DeadAbnSeeds")
getwd()

#create file
df_seed <- read.table("HardseedsLiveData.txt",header=TRUE)
head(df_seed)
# change format 
df_seed$Date <- dmy(df_seed$Date)

# jeito 2 de trocar formato (usando dplyr)
df_seed <- df_seed %>%
  mutate(Plot = as.factor(Plot), 
         Block = as.factor(Block),
        Depth = as.factor(Depth),
        Soft = as.numeric(Soft),
         SoftDead = as.numeric(SoftDead),
         SoftGerm = as.numeric (SoftGerm),
         SoftAbn = as.numeric (SoftAbn),
         SoftUngerm = as.numeric (SoftUngerm),
       HardUngermFinal = as.numeric (HardUngermFinal)) 
  

summary(df_seed) # explore values
str(df_seed) # check formats
head(df_seed) # see to rows
tail(df_seed)



```

Calculate the cumulative number of Abnormal seedlings (use loop to do that!)

```{r}

 

# create an ID of each chunk
df_temp <- df_seed %>%
  dplyr::select(-Date) %>%
  mutate(codeID = as.factor(paste0(Plot,"_",Depth)))

# define unique factors to loop around
codesNames <- unique(df_temp$codeID)

# prepare final df to store data
df_final <- data.frame()

# loop
for(i in 1:length(codesNames)) {
  
  df_sub <- data.frame() # empty df
  
  df_sub <- df_temp %>%
    subset(codeID == codesNames[i]) %>% # segment one unique combination
    mutate(codeID = factor(codeID)) %>%
    arrange(Round) %>%
    mutate(SoftAbn_cum = cumsum(SoftAbn)) %>%
    mutate(AbnCumProp = SoftAbn_cum/max(InitialSeedlotR1Number)*100)
  
  df_final <- rbind(df_final,df_sub)
  
}

summary(df_final)

```





```{r CreatePercentSoft}
#Rename dataframe and columns
df_Abn <- df_final%>%
  mutate(Abn_perc=AbnCumProp)




```


graph the total percentage of abnormal seedlings 

```{r, fig.height=6, fig.width=10}

df_Abn %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  filter(Round == 119) %>%
  group_by(Cultivar,SowTreat, Depth) %>%
  dplyr::select(Abn_perc) %>%
  summarise_all(funs(mean,sd)) %>%
  ggplot(aes(x=Cultivar, y=mean, colour=Cultivar, shape=Cultivar)) +
  geom_point(size=3) +
  #geom_line() +
 facet_grid(Depth~SowTreat) +
  #facet_wrap(Depth~SowTreat)+
  labs(x="Cultivar",y=" Percentage of abnormal seedlings (%)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=mean-sd/3.46,
                    ymax=mean+sd/3.46))+
  theme_bw()+
  ylim(0,30)+
  theme(axis.text.x=element_text(angle = 90, hjust = 0.5, size= 14))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 14))


```






then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

file <- df_Abn %>%
  dplyr::select(Block, Cultivar,SowTreat,Plot,Depth,Abn_perc)

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(Abn_perc~ Cultivar*SowTreat*Depth + Block, data = file.subset)
#my.anova <- aov(Abn_perc~ Cultivar + Block, data = file.subset)
#my.anova <- aov(Abn_perc~ Depth + Block, data = file.subset)
my.anova <- aov(Abn_perc~ SowTreat + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
 (LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

The lowest percentage os abnormal seeds was observed in S1,S2,S3 . In S4, S6 and S7 the percentage of abnormal seeds was double. 

Then test each sowing date individually 
S1


```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S1")

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(Abn_perc~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(Abn_perc~ Cultivar*Depth + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



S2

```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S2")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(Abn_perc~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Abn_perc~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S3


```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S3")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(Abn_perc~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Abn_perc~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



S4

```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S4")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(Abn_perc~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Abn_perc~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S6


```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S6")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(Abn_perc~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Abn_perc~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



S7

```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S7")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(Abn_perc~ Cultivar*Depth + Block, data = file.subset)
#my.anova <- aov(Abn_perc~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```




