---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "Thursday, 22 September , 2016"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(markdown)
#install.packages(markdown)

```
Here calculate the total percentage off dead seeds for cultivars and sow treat 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
df_seed <- read.table("HardseedsLiveData.txt",header=TRUE)
head(df_seed)
# change format 
df_seed$Date <- dmy(df_seed$Date)

# jeito 2 de trocar formato (usando dplyr)
df_seed <- df_seed %>%
  mutate(Plot = as.factor(Plot), 
         Block = as.factor(Block),
        Depth = as.factor(Depth),
        Soft = as.numeric(Soft),
         SoftDead = as.numeric(SoftDead),
         SoftGerm = as.numeric (SoftGerm),
         SoftAbn = as.numeric (SoftAbn),
         SoftUngerm = as.numeric (SoftUngerm),
       HardUngermFinal = as.numeric (HardUngermFinal)) 
  

summary(df_seed) # explore values
str(df_seed) # check formats
head(df_seed) # see to rows
tail(df_seed)



```



```{r CreatePercentSoft}
#Create a column that is the Accumulated Dead this is to calculate the Maximum percentage of dead seeds  



# create an ID of each chunk
df_temp <- df_seed %>%
  dplyr::select(-Date) %>%
  mutate(codeID = as.factor(paste0(Plot,"_",Depth)))

# define unique factors to loop around
codesNames <- unique(df_temp$codeID)

# prepare final df to store data
df_final <- data.frame()

# loop
for(i in 1:length(codesNames)) {
  
  df_sub <- data.frame() # empty df
  
  df_sub <- df_temp %>%
    subset(codeID == codesNames[i]) %>% # segment one unique combination
    mutate(codeID = factor(codeID)) %>%
    arrange(Round) %>%
    mutate(SoftDead_cum = cumsum(SoftDead)) %>%
    mutate(dead_perc = SoftDead_cum/max(InitialSeedlotR1Number)*100)
  
  df_final <- rbind(df_final,df_sub)
  
}

summary(df_final)



```


graph the total percentage of dead seeds 

```{r, fig.height=6, fig.width=10}


#change dataframe name to continue 


df_dead <- df_final

#plot results 

df_dead %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  filter(Round == 119) %>%
  group_by(Cultivar,SowTreat, Depth) %>%
  dplyr::select(dead_perc) %>%
  summarise_all(funs(mean,sd)) %>%
  ggplot(aes(x=Cultivar, y=mean, colour=Cultivar, shape=Cultivar)) +
  geom_point() +
  #geom_line() +
 facet_grid(Depth~SowTreat) +
  #facet_wrap(Depth~SowTreat)+
  labs(x="Sowing Date",y=" Percentage of Dead seeds (%)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=mean-sd/3.46,
                    ymax=mean+sd/3.46))+
  theme_bw()+
  ylim(0,30)+
  theme(axis.text.x=element_text(angle = 90, hjust = 0.5, size= 12))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 12))


```



Data Transformation :dead_perc


```{r}

str(df_SoftGerm)
##rename dataframe 

file <-df_SoftGerm
  #filter(SowTreat=="S1")
 #filter(SowTreat=="S2")
 #filter(SowTreat=="S3") 
 #filter(SowTreat=="S4")
 #filter(SowTreat=="S6")
 #filter(SowTreat=="S7")




##data transformation
file$transf_sqr <- sqrt(file$SoftGerm_perc)
file$transf_log <- log(file$SoftGerm_perc)
file$transf_not <- 1*(file$SoftGerm_perc/1)
file$transf_acos <- acos(file$SoftGerm_perc/100)
file$transf_sqrx <- (file$SoftGerm_perc^2)
#mutate(mydata, sqr.x = x^2)


head(file)

x <- c("transf_sqr", "transf_log","transf_acos","transf_not", "transf_sqrx" )
colsSelec <- match(x,colnames(file))




``` 




then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

file <- df_dead %>%
  dplyr::select(Block, Cultivar,SowTreat,Plot,Depth,dead_perc)

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(dead_perc ~ Cultivar*SowTreat*Depth + Block, data = file.subset)
#my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(dead_perc ~ Depth + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

The lowest percentage os dead seeds was observed in S1 and S1. In S4, S5 and S6 the percentage of dead seeds was threefold higher. 

Then test each sowing date individually 
S1


```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S1")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(dead_perc ~ Cultivar*Depth+Block, data = file.subset)
#my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



Then test each sowing date individually 

Loop Anova 

## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(file$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```




## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- file %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(dead_perc ~ Cultivar*Depth + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar","Depth"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```



S2

```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S2")

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(dead_perc ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S3


```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S3")

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(dead_perc ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



S4

```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S4")

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(dead_perc ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S6


```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S6")

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(dead_perc ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



S7

```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S7")

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(dead_perc ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```




