---
title: 'Graph climate variables in growth chamber '
author: "CT"
date: "16.12.2016"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

This script calculates the Thermal time using four methods : 
1. hourly as average of the 18 seconds measurements 


```{r}
library(tidyr)
library (dplyr)
library (ggplot2)
library (lubridate)
library (scales)
library(gridExtra)
library(knitr)
```

Equation  to calculate the TT 



## Define Tt cardinal temperatures

Considered an overall average the following references:
Tb: 0.0
Top range:18-25
Tmax: 35
REFS: MonksEtAl2009	,LonatiEtAl2009	,MootEtal2003, SilsburyetAl1984. 
							
```{r}

tt_card <- data.frame(temp=c(0,15,22,35),TT=c(0,15,15,0))
tt_card %>%
  ggplot(aes(x=temp, y=TT))+
  labs(x="Temperature (degree Celsius)")+
  labs(y="Thermal Time (degree days)") +
  theme_bw()+
  geom_line()
  
```



```{r}

 

#Create and test interpolation function - Test if works 

temp_ref  <- 20 # x-axes reference
temp <- tt_card$temp # x-axes
TT <- tt_card$TT # y-axes


int_func <- function(temp,TT,temp_ref){

  # if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   out <- TT[length(TT)] 
   # FIXME: approx functions seems to do that - need param
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
   # else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  
int_func(temp,TT,temp_ref)


```




Note: this file produces the graphs for recorded variables in growht cabinet. measurements are done every 18 seconds. 

```{r, load file}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GCFlower")
getwd()
#read data , use row.names=NULL to delete Error message 

df_file <- read.table("AllData.txt",header =TRUE,row.names= NULL )

```

```{r}
summary(df_file)
```

##Method 1. TT calculate hourly from measurements every 18 seconds!!!  

```{r}

df_file_Hourly<- df_file %>%
  mutate(TimeStamp=dmy_hms(paste0(Date," ",Time))) %>%
  mutate(TimeStamp=ymd_hms(TimeStamp)) %>%
  mutate(Date=dmy(Date)) %>%
  dplyr::select(Date,TimeStamp,AI_TEMP,Hour)

summary(df_file_Hourly)
```
Average the Temp per Hour

```{r}

df_file_Hourly %>%
  group_by(Date, Hour)%>%
  dplyr::select(AI_TEMP )%>%
  summarise_all(funs(mean))

str(df_file_Hourly)


```

Connect function TT calculation 


```{r}


df_H <- df_file_Hourly %>%
  dplyr::select(Date:AI_TEMP) %>%
    rowwise() %>%
  mutate(TThour=int_func(temp,TT,AI_TEMP)) %>%
  group_by(Date) %>%
  summarise(TTday=mean(TThour))


#split script here to fix 
#%>% 
 # mutate(SumTTday = cumsum(TTday))


df_H2<- df_H %>%
   mutate(SumTTday = cumsum(TTday))


##summarise 
summary(df_H2)
str(df_H2)
write.table(df_H2, "SumTTHourGC.txt")


```

 

