---
title: "Flowering 3CV_growth chamber experiment "
author: "CT"
date: "30.01.2016"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r loadLibraries, warning=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```
This script calculates the means of DAS and TTAS50Flo and perform the statistics 

```{r loadFile}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GCFlower")

getwd()

#create file
df_raw <- read.table("GCdf_tt_50p_flow.txt",header=TRUE)

head (df_raw)
```
check formats
```{r}

df_work<-df_raw %>%
  mutate(SowingD=ymd(SowingD)) %>%
  rename(PhenoStage=Variable)%>%
  mutate(Plot=factor(Plot), Block=factor(Block))
         
str(df_work)

```

## Add the columns refering to days from emergence




##Add the number of days for 50% emergence to calculate the days to runner  after emergence (DAE)

##File ready at : GC_DASToEmergence.txt (already calculated the days after emergence)

 

```{r}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GCFlower")
getwd()
#create file
df_trif2 <- read.table("GC_DASToEmergence.txt",header=TRUE)


str(df_trif2)


```

Define formats 

```{r loadFile}


# define factors for the ones that "look like" values

df_trif2 <- df_trif2 %>%
  mutate(SowingDate = ymd(SowingDate), 
         Date50Emerg = ymd(Date50Emerg),
         DAS_ToEmerg = as.numeric(DAS_ToEmerg))


df_trif2$Pot <- as.factor(df_trif2$Pot)
df_trif2$Block <- as.factor(df_trif2$Block)
df_trif2$Cultivar <- as.factor(df_trif2$Cultivar)
#df_trif$SowTreat <- as.factor(df_trif$SowTreat)

##Reminder !!! Exclude the info ot 1_T ...that comes automatically from excel but not essential here 
 
         

str(df_trif2)


```

##Remove extra columns 



```{r}

##Estimate date for runner appearance after after emergence 
##Here select only columns related to emergence  !! 

df_DatetoEmerg <-df_trif2 %>%
select(Cultivar:Block,DAS_ToEmerg)%>%
  mutate(Plot=Pot)
  


```

# ################## Quantify Days  from emergence to flowering phenophases  ############

```{r}

#prep dataframe with TT at emergence 


str (df_DatetoEmerg)

## merge the dataframes by Plot 
  
df_TempA1 <- merge(df_DatetoEmerg,df_work,by="Plot")

##inspect  new data frame
 str(df_TempA1 )
 
##clean dataframe _remove duplicated and extras 
 
df_TempA2 <- df_TempA1%>%
  select(-Block.y, -Cultivar.y)%>%
  mutate(Cultivar=Cultivar.x, Block=Block.x)%>%
  mutate(DAE50F=DAS50F-DAS_ToEmerg)
  
```

## Now dataframe contains DAS and DAE for specific phenophases 



## Create index to filter for loop ANOVA


```{r}
y <- c("Bud","Bur","Flowering")

sdIndex <- unique(df_TempA2$PhenoStage)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```


## Then loop anova for each individual cultivar and variable first with days to flower from sowing (DAs50F)

```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_TempA2 %>%
  filter(PhenoStage==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(DAS50F ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```



## Repeat the process - Do Stats for DAE50F then 


```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_TempA2 %>%
  filter(PhenoStage==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(DAE50F ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```


###Graphs not needed at htis stage ####################


graph DAS and TT 50Bud for all cultivars and sowing dates 

```{r, fig.height=6, fig.width=15}

# df_work_bud_mean%>%
#   
# ggplot(aes(x=SowingD,y=mean, shape=Cultivar))+
#   geom_point(aes(shape=Cultivar),size=5)+
#     scale_shape_manual(values = c(1,2,0)) +
#   facet_grid(Variable~PhenoStage, scales="free")+
#   
#     theme_grey(base_size = 16) +
#     theme_bw()+
#     geom_abline(intercept = 100, slope = 0, linetype=2)+
#    
# theme(axis.text.x=element_text(angle = 0, hjust = 0))+
# theme(text = element_text(size = 16)) +
#  # theme(axis.text.x = element_text(angle = 0, hjust = 1.5))+
#   #scale_x_date(date_breaks = "1 month",date_labels =  "%b")+
# labs(x="Sowing Month")+
#     #limits = as.Date (c("2016"))
# ylab(expression(Tt~"("^"o"*"Cd)"~~~~~~~~~~~~~~~~~~~~~~Days))
#     
# #ggsave("plot_xxx.png", width=12, height=6, dpi=400)
#  summary(df_work_bud_mean)
```

Make the mean and SE
`
```{r}

# aMean <- a %>%
#   tidyr::gather("Variable","Value",DAS50F:TT50F) %>%
#   dplyr::select(SowingD,SowTreat, Variable, Value) %>%
#   
#   
#   summarise_all(funs(max(PercGerm_cum), sd)) 
#   summarise_all(funs)
#   ggplot(aes(x=SowingD,y=Value, shape=Cultivar))+
#     #scale_x_discrete(name="Mon")
#   geom_point(aes(shape=Cultivar),size=5)+
#     scale_shape_manual(values = c(1,2,0,4,7,8)) +
#      #scale_shape_manual(values = c(1,2,0)) +
#   #geom_line(aes(colour=Variable))+
#   facet_grid(Variable3~., scales="free")+
#   
#     theme_grey(base_size = 16) +
#     theme_bw()+
#     geom_abline(intercept = 100, slope = 0, linetype=2)+
#    
# theme(axis.text.x=element_text(angle = 0, hjust = 0))+
# theme(text = element_text(size = 16))+
# labs(x="Sowing Month")+
# ylab(expression(Tt~"("^"o"*"Cd)"~~~~~~~~~~~~~~~~~~~~~~Days))
#     



```


