---
title: "Flowering 3CV_growth chamber experiment "
author: "CT"
date: "30.01.2016"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r loadLibraries, warning=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```
This script calculates the means of DAS and TTAS50Flo and Thermal time from emergence and perform the statistics 

```{r loadFile}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GCFlower")

getwd()

#create file
df_raw <- read.table("GCdf_tt_50p_flow.txt",header=TRUE)

head (df_raw)
```
check formats
```{r}

df_work<-df_raw %>%
  mutate(SowingD=ymd(SowingD)) %>%
  rename(PhenoStage=Variable)%>%
  mutate(Plot=factor(Plot), Block=factor(Block))
         
str(df_work)

```

## Add the columns refering to days from emergence
## Bring data form runner fold which contains the thermal time values at emergence: file  GC_ThermalTime_Emergence



```{r}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GCFlower")
getwd()
#create file
#df_trif2 <- read.table("GC_DASToEmergence.txt",header=TRUE)
df_Em <- read.table("GC_ThermalTime_Emergence.txt",header=TRUE)

str(df_Em)


```

 
Define formats  (df_Em)

```{r loadFile}


# define factors for the ones that "look like" values and dates 

df_Em<- df_Em %>%
  mutate(SowingDate = ymd(SowingDate), 
         Date50Emerg = ymd(Date50Emerg),
         DateRun_Em = ymd(DateRun_Em),
         Date = ymd(Date))
          


df_Em$Pot <- as.factor(df_Em$Pot)

# df_trif2$Block <- as.factor(df_trif2$Block)
# df_trif2$Cultivar <- as.factor(df_trif2$Cultivar)
#df_trif$SowTreat <- as.factor(df_trif$SowTreat)

##Reminder !!! Exclude the info ot 1_T ...that comes automatically from excel but not essential here 
 
## select only columns of interest

df_Em <- df_Em %>%
  select (Plot, SumTTEmerg)


str(df_Em)


```


##Merge the dataframes to subtract thermal time at phenophases and emergence 

```{r}

df_TempA1 <- merge(df_Em,df_work,by="Plot")

str(df_TempA1)

```

#
# ################## Quantify TT from emergence to flowering phenophases (TT50F - TT Emergence ) ############

```{r}

 
df_TempA2 <- df_TempA1%>%
  mutate(TT50FEm= TT50F-SumTTEmerg)

str (df_TempA2)


```

## Now dataframe contains TT50F  and TT50FEm for specific phenophases 


## Create index to filter for loop ANOVA


```{r}
y <- c("Bud","Bur","Flowering")

sdIndex <- unique(df_TempA2$PhenoStage)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```


## Then loop anova for each individual cultivar and variable first with days to flower from sowing (TT50F)

```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_TempA2 %>%
  filter(PhenoStage==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(TT50F ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```



## Repeat the process - Do Stats for TT50FEm (from emergence) 


```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_TempA2 %>%
  filter(PhenoStage==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(TT50FEm ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```


###Graphs not needed at htis stage ####################


