---
title: "BurrBurialAnalysis Poukawa site"
author: "CT"
date: "02.062017"
output: html_document
#This script calculates burr yields from Poukawa experimental site 
---

Purpose: to calculate the percentage of burr burial in Poukawa site and make the stats

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
```

Read File with raw data 

```{r, echo=FALSE}
#setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\Gitsubclover\\BurrYieldBurPok")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\BurrYieldBurPok")

getwd()
file <- read.table("SeedBurrYieldPok.txt",header=TRUE)
head(file)
summary(file)
```

Define formats here prior calculations 

```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Date = dmy(Date),
    SowingD = dmy(SowingD)
  )

str(file)
summary(file)

```
Calculate the weight of individual burrs and then  calculate the number of total burrs 

```{r}


df <- file %>%
  dplyr::select(Cultivar,SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g) %>%
  mutate(IndBurrW = bur_weight_subSample_g/
           bur_no_subSample,
         BurrNumber = bur_total_weight_g/IndBurrW) %>%  
  group_by(Cultivar, SowTreat,Depth,Block) %>%
  summarise_each(funs(mean)) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,BurrNumber,Block)

  df <- as.data.frame(df)
head(df)

```

Calculate the proportion of buried burrs 

```{r, fig.height= 5, fig.width=10 , warning=FALSE}


# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)

  df_bur <- df %>%
  tidyr::spread(Depth,BurrNumber) %>%
  mutate(PropBurrBuried= Below/(Below+Above)*100)

summary(df_bur)

# define position of bar and errorbar; do not remove this line !
dodge_x <- position_dodge(width = 0.9)

```

```{r, fig.height= 5, fig.width=10 , warning=FALSE}
df_bur %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_each(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=PropBurrBuried_mean-PropBurrBuried_sd/2, ymax=PropBurrBuried_mean+PropBurrBuried_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
    labs(y="Percentage of Buried burrs (%)") +
  theme_bw()+
theme(axis.text.x=element_text(angle = +89, hjust = 0.95, size = 12))

#head(df_bur)
```



make a graph with the SE 

```{r, fig.width=10, fig.height=5}

# define position of bar and errorbar; do not remove this line !
dodge_x <- position_dodge(width = 0.9)


df_burSE <- df_bur %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_all(funs(mean,sd)) %>%
  mutate(SE=PropBurrBuried_sd/1.73 )
  
  df_burSE %>%
  
  ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=PropBurrBuried_mean-SE/2, ymax=PropBurrBuried_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
    labs(y="Percentage of Buried burrs (%)") +
  theme_bw()+
theme(axis.text.x=element_text(angle = +89, hjust = 0.95, size = 12))




```



Try another graph style 


```{r,  fig.height= 5, fig.width=10 , warning=FALSE}}

df_bur  %>% 
  group_by(Cultivar, SowTreat) %>%
  summarise_each(funs(mean,sd)) %>%
  
  #mutate(Month=format(as.Date(ymd(SowingDate)),"%b")) %>%
  ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=Cultivar))+
  labs(x="Cultivar", y="   % Buried burrs ")+
  #geom_boxplot(alpha=0.2)+
  geom_point(alpha=0.2)+
  geom_boxplot(alpha=0.2)+
  geom_jitter(alpha=0.2,width = 0.3, aes(colour=Cultivar))+
  #labs(x=" Sowing Month", y="                oCd                Days ")+
  #facet_wrap(~Country)
  #geom_point(shape=21) +
# theme(legend.position="none")+
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
  theme_bw()+
  theme(axis.text.x=element_text(angle = +89, hjust = 0.95))



```

Need to fix this graph !!! colour does not match ! 

```{r, fig.height= 5, fig.width=10 , warning=FALSE}}
df_bur %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_each(funs(mean,sd)) %>%
  mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=PropBurrBuried_mean-PropBurrBuried_sd/2, ymax=PropBurrBuried_mean+PropBurrBuried_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
    labs(y="Percentage Buried burrs") +
theme(axis.text.x=element_text(angle = +89, hjust = 0.95))
head(df_bur)

```

Do ANOVA simple as per D. Saville here overview of the experiments (no filter )

```{r}

#Filter  S1, S2, S3, S4, S5
summary(df_bur)

df_burANOVA <- df_bur #use to filter%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  


#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)

```

summary of ANOVA overall SowTreat as factor 
```{r}

#ANOVA
#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)

```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

Analyse overall cultivar


```{r}
#Filter  S1, S2, S3, S4, S5
summary(df_bur)

df_burANOVA <- df_bur #use to filter%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  


#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)
```

Summary Anova cultivar

```{r}

#ANOVA
my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)

```


mean separation cultivar

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))

```



select individual sowing dates
s1

```{r}
#Filter  S1, S2, S3, S4, S5
summary(df_bur)

df_burANOVA <- df_bur %>%
  filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  
#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)
```

anovas1
```{r}
#ANOVA
my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)
```


mean separation s1
```{r}

#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S2

```{r}
#Filter  S1, S2, S3, S4, S5
summary(df_bur)

df_burANOVA <- df_bur %>%
  filter(SowTreat=="S2")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  
#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)
```

Anova s2
```{r}
#ANOVA
my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)
```

mean separation S2
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S3

```{r}
#Filter  S1, S2, S3, S4, S5
summary(df_bur)

df_burANOVA <- df_bur %>%
  filter(SowTreat=="S3")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  
#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)
```

Anova S3

```{r}
#ANOVA
my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)
```

mean separations S3
```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```


S4 

```{r}
#Filter  S1, S2, S3, S4, S5
summary(df_bur)

df_burANOVA <- df_bur %>%
  filter(SowTreat=="S4")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  
#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)

```
anovaS4
```{r}
#ANOVA
my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)

```

summary S4
```{r}

#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```
S5

```{r}
#Filter  S1, S2, S3, S4, S5
summary(df_bur)

df_burANOVA <- df_bur %>%
  filter(SowTreat=="S5")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  
#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)
```
S5 Anova

```{r}

#ANOVA
my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)

```

S5 means 

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



The chunks below were prototypes _ Transform checks (not using it now)

```{r}


#data transformation 
df_bur$transf_no <- 1*(df_bur$PropBurrBuried)
# df_bur$transf_sqr <- sqrt(df_bur$PropBurrBuried)
# df_bur$transf_log <- log(df_bur$PropBurrBuried)
# df_bur$transf_acos <- acos(df_bur$PropBurrBuried/100)

head(df_bur)

 file <- df_bur
 
#................................................................
 #No need for this  
# x <- c( "df_bur$transf_no',transf_sqr", "transf_log", "transf_acos","df_bur$transf_no")
# colsSelec <- match(x,colnames(file))
# 
# file %>%
#   tidyr::gather("transformation","value",colsSelec) %>%
#   ggplot(aes(value)) + 
#   geom_histogram() +
#   facet_grid(.~transformation, scales="free")
# 
# head(file)
# 
# #normality test
# shapiro.test(file$transf_log)

# #QQplot
# var<-file$transf_acos
# qqnorm(var)
# qqline(var, col = 2)
# qqplot(var, rt(300))

#-------------------------------------------------
# ANOVA (selecing by hand FIXME: do loop)
file.subset <- file %>%
 #here filter the swoTreat to analyse separately
  subset(SowTreat == "S1" )







```

```{r}

file.subset <- file

#head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, data = file.subset)

summary(my.anova)

```

```{r}


#Means separation 
(LSD.test(my.anova, "Cultivar", alpha= 0.05, p.adj="none")) 

#TukeyHSD(my.anova)
```










