---
title: "Total Number of Burrs per m2 "
author: "CT"
date: "25.07.2017"
output: html_document
---

This script calculates the number of burrs per area (1m2) and run ANOVA for Poukawa 

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
```

Read File 

```{r, echo=FALSE}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\BurrYieldBurPok")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\BurrYieldBurPok")
getwd()
file <- read.table("SeedBurrYieldPok.txt",header=TRUE)
head(file)
summary(file)
```

Define formats 

```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Date = dmy(Date),
    SowingD = dmy(SowingD)
  )

str(file)
summary(file)

```

Calculate the individual burr weight and burr number 

```{r}

df <- file %>%
  dplyr::select(Cultivar,SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g) %>%
  mutate(IndBurrW = bur_weight_subSample_g/
           bur_no_subSample,
         BurrNumber = bur_total_weight_g/IndBurrW) %>%  
  group_by(Cultivar, SowTreat,Depth,Block) %>%
  summarise_each(funs(mean)) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,BurrNumber,sample_area_m2,Block)

  df <- as.data.frame(df)
head(df)

```

Calculate the total number of burs per 1 m2 . Graph it 

```{r, fig.height= 5, fig.width=10 , warning=FALSE}

#barplot 
#The palette with grey:cbPalette <- c("999999"),"666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")

#cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)

  df_bura <- df %>%
  tidyr::spread(Depth,BurrNumber) %>%
  mutate(TotalBurr_m2= (Below+Above)/sample_area_m2)




```

Graph all dataset ; panels are sowing treatments 

```{r, fig.height= 5, fig.width=10 , warning=FALSE}
df_bura %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_each(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(TotalBurr_m2_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=TotalBurr_m2_mean-TotalBurr_m2_sd/2, 
                    ymax=TotalBurr_m2_mean+TotalBurr_m2_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 18) +
    facet_grid(.~SowTreat) +
    #labs(y="% Total number of  burrs per 1 m2") +
   ylab(expression(Total~number~of~burrs~per~m^"2")) +
  theme_bw()+
theme(axis.text.y = element_text( size = 11))+
  theme(axis.title.y = element_text(face="bold", size=14))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))

```


then create a graph with the SE 

```{r, fig.height=5, fig.width=10}

dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)

  df_buraSE <- df_bura %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_all(funs(mean,sd)) %>%
    mutate(SE=TotalBurr_m2_sd/1.73)

#then graph it 
  
 df_buraSE %>%
   filter(SowTreat!="S1",SowTreat!="S5" )%>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5"),labels=c("February", "March", "May", "July", "August")))%>%
   ungroup %>%
   #added ....here mutate cultivar labels for poster  
   mutate (Cultivar= factor(Cultivar, levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),labels=c("A", "D", "L", "M", "N","W")))%>%
  ggplot(aes(x=Cultivar, y=(TotalBurr_m2_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=TotalBurr_m2_mean-SE/2, 
                    ymax=TotalBurr_m2_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 18) +
    facet_grid(.~SowTreat) +
   ylab(expression(Number~of~inflorescences/m^"2")) +
  theme_bw()+
theme(axis.text.y = element_text( size = 12))+
   scale_fill_brewer(palette="Blues")+
  #theme(axis.title.y = element_text(face="bold", size=16))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0.2,size = 22)) +
  theme(text = element_text(size = 22))
  
 #Save graph 
 
 #ggsave("plot_NumberBursPerm2Pok.png", width=12, height=6, dpi=400)
  
```

Improved graph for poster 


```{r, fig.height=5, fig.width=10}

dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)

  df_buraSE <- df_bura %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_all(funs(mean,sd)) %>%
    mutate(SE=TotalBurr_m2_sd/1.73)

#then graph it 
  
 df_buraSE %>%
   filter(SowTreat!="S1",SowTreat!="S5" )%>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5"),labels=c("February", "March", "May", "July", "August")))%>%
   ungroup %>%
   #added ....here mutate cultivar labels for poster  
   mutate (Cultivar= factor(Cultivar, levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),labels=c("A", "D", "L", "M", "N","W")))%>%
  ggplot(aes(x=Cultivar, y=(TotalBurr_m2_mean)))+
  geom_bar(aes(fill=Cultivar), colour="black",stat="identity",position = dodge_x) +
  #geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=TotalBurr_m2_mean-SE/2, 
                    ymax=TotalBurr_m2_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 18) +
   theme_bw()+
    facet_grid(.~SowTreat) +
   
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
   
   scale_y_continuous(expand = c(0, 0), limits = c(0, 15000))+
   
   
   ylab(expression(Number~of~inflorescences/m^"2")) +
   theme(axis.text.y = element_text( vjust=0.5, size = 14))+
   #margin y axis
   #theme (axis.title.y = element_text( margin = margin(t=0,r=20,b=0,l=0)))+
            
   scale_fill_brewer(palette="Blues")+
  #theme(axis.title.y = element_text(face="bold", size=16))+
   theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0.2,size = 22)) +
   theme(text = element_text(size = 22))+
   theme(axis.title.y=element_text(angle = 90, hjust=0.5,vjust=0.2,size = 20))
  
 #Save graph 
 
 ggsave("plot_NumberBursPerm2Pok.png", width=16, height=6, dpi=400)
  
```



```{r}



#empty



```


Mean overall values per sowing date 


```{r,  fig.height= 5, fig.width=10 , warning=FALSE}}

#a <-df_bura %>%
  
df_bura %>%
  group_by(SowTreat) %>%
  summarise_each(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=SowTreat, y=(TotalBurr_m2_mean),fill=SowTreat))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=TotalBurr_m2_mean-TotalBurr_m2_sd/2, 
                    ymax=TotalBurr_m2_mean+TotalBurr_m2_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    #facet_grid(.~SowTreat) +
    #labs(y="% Total number of  burrsper 1 m2", size=16) +
  ylab(expression(Total~number~of~burrs~per~1~m^"2")) +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
  theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 0, hjust=0.95,vjust=0.2,size = 12))

#head(a)

```

Mean overall values per cultivar over all sowing dates  (used to write in chapter)


```{r}

df_bura %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_each(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(TotalBurr_m2_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=TotalBurr_m2_mean-TotalBurr_m2_sd/2, 
                    ymax=TotalBurr_m2_mean+TotalBurr_m2_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
    #labs(y="% Total number of  burrsper 1 m2", size=16) +
  ylab(expression(Total~number~of~burrs~per~1~m^"2")) +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))

#head(b)
```


Do ANOVA simple as per D. Saville 

here analysis of overall experiment (sow Treat as a factor ) to get means and std 
```{r}

summary(df_bura)

df_burANOVA <- df_bura
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ SowTreat + Block, data = file.subset)

summary(my.anova)

#Means separation after ANOVA
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 


```

Analyse cultivars overall  
```{r}
summary(df_bura)

df_burANOVA <- df_bura
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)

#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 


```


Analyses of individual sowing dates here S1 

```{r}

#Filter  S1, S2, S3, S4, S5  
summary(df_bura)

df_burANOVA <- df_bura%>% #use to filter
  filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)

```
S1

```{r}

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```
S1

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

S2 select

```{r}

#Filter  S1, S2, S3, S4, S5  
summary(df_bura)

df_burANOVA <- df_bura%>% #use to filter
  filter(SowTreat=="S2")
  #filter(SowTreat=="S2")
  
#-------------------------------------------------
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)

```

S2 summary anova 
```{r}
#ANOVA
my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```

mean Separation

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```


S3 

```{r}

#Filter  S1, S2, S3, S4, S5  
summary(df_bura)

df_burANOVA <- df_bura%>% #use to filter
  filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  
#-------------------------------------------------
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)
```

S3 ANOVA

```{r}

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```

S3 mean separation 

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S4 select 

```{r}
#Filter  S1, S2, S3, S4, S5  
summary(df_bura)

df_burANOVA <- df_bura%>% #use to filter
  filter(SowTreat=="S4")
  #filter(SowTreat=="S5")
  
#-------------------------------------------------
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)
```

ANOVA summary S4 


```{r}

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```


means S4 

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S5 select 

```{r}

#Filter  S1, S2, S3, S4, S5  
summary(df_bura)

df_burANOVA <- df_bura%>% #use to filter
  filter(SowTreat=="S5")
  #filter(SowTreat=="S5")
  
#-------------------------------------------------
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)
```


S5 Anova

```{r}

my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```

S5 means 

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```












The chunks below were prototypes _ Transform checks (not using it now)

```{r}


#data transformation 
df_bur$transf_no <- 1*(df_bur$PropBurrBuried)
# df_bur$transf_sqr <- sqrt(df_bur$PropBurrBuried)
# df_bur$transf_log <- log(df_bur$PropBurrBuried)
# df_bur$transf_acos <- acos(df_bur$PropBurrBuried/100)

head(df_bur)

 file <- df_bur
 
#................................................................
 #No need for this  
# x <- c( "df_bur$transf_no',transf_sqr", "transf_log", "transf_acos","df_bur$transf_no")
# colsSelec <- match(x,colnames(file))
# 
# file %>%
#   tidyr::gather("transformation","value",colsSelec) %>%
#   ggplot(aes(value)) + 
#   geom_histogram() +
#   facet_grid(.~transformation, scales="free")
# 
# head(file)
# 
# #normality test
# shapiro.test(file$transf_log)

# #QQplot
# var<-file$transf_acos
# qqnorm(var)
# qqline(var, col = 2)
# qqplot(var, rt(300))

#-------------------------------------------------
# ANOVA (selecing by hand FIXME: do loop)
file.subset <- file %>%
 #here filter the swoTreat to analyse separately
  subset(SowTreat == "S1" )







```

```{r}

file.subset <- file

#head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, data = file.subset)

summary(my.anova)

```

```{r}


#Means separation 
(LSD.test(my.anova, "Cultivar", alpha= 0.05, p.adj="none")) 

#TukeyHSD(my.anova)
```










