---
title: "BurrBurialAnalysis"
author: "CT"
date: "Friday, March 18, 2016"
output: html_document
---
Purpose : 
calculations of burr yield per 1m 2 and total burr yield
Calculation for the percentage of buried burs 
ANOVA for the variate : precentage of buried burs 

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
```

Read File 

```{r, echo=FALSE}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\Gitsubclover\\BurrYieldBurIv2")
getwd()
file <- read.table("SeedBurrYield.txt",header=TRUE)
head(file)
summary(file)
```

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Date = dmy(Date),
    SowingD = dmy(SowingD)
  )

str(file)
summary(file)

```
Calculate the Individual burr weight and the number of burrs 

```{r}

df <- file %>%
  dplyr::select(Cultivar,SowTreat,sample_area_m2,Block,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g) %>%
  mutate(IndBurrW = bur_weight_subSample_g/
           bur_no_subSample,
         BurrNumber = bur_total_weight_g/IndBurrW) %>%  
  group_by(Cultivar, SowTreat,Depth,Block) %>%
  summarise_each(funs(mean)) %>%
  dplyr::select(Cultivar,SowTreat,
                Depth,BurrNumber,Block)

  df <- as.data.frame(df)
head(df)

write.table(df, "df.txt")

```

Here calculates the percentage of buried burrs and graph with std.

```{r, fig.height= 5, fig.width=10 , warning=FALSE}

#barplot 
#The palette with grey:cbPalette <- c("999999"),"666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")

#cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)

  df_bur <- df %>%
  tidyr::spread(Depth,BurrNumber) %>%
  mutate(PropBurrBuried= Below/(Below+Above)*100)


```

Graph the percentage of buried burrs 

```{r, fig.height= 5, fig.width=10 , warning=FALSE}
df_bur %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_each(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=PropBurrBuried_mean-PropBurrBuried_sd/2, ymax=PropBurrBuried_mean+PropBurrBuried_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
    labs(y="% Buried burrs") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))

head(df_bur)
```

Here graph with the SE (SE = std/ sqrt n ; n=3)

```{r,fig.height= 5, fig.width=10 , warning=FALSE}

df_burSE<-df_bur %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_each(funs(mean,sd)) %>%
  mutate(SE=PropBurrBuried_sd/1.73)
  
  
  df_burSE %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=Cultivar))+
  geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=PropBurrBuried_mean-SE/2, ymax=PropBurrBuried_mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
    labs(y="% Buried burrs") +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))

head(df_bur)




```





Try another style 


```{r,  fig.height= 5, fig.width=10 , warning=FALSE}}

df_bur  %>% 
  group_by(Cultivar, SowTreat) %>%
  summarise_each(funs(mean,sd)) %>%
  
  #mutate(Month=format(as.Date(ymd(SowingDate)),"%b")) %>%
  ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=Cultivar))+
  labs(x="Cultivar", y="   % Buried burrs ")+
  #geom_boxplot(alpha=0.2)+
  geom_point(alpha=0.2)+
  geom_boxplot(alpha=0.2)+
  geom_jitter(alpha=0.2,width = 0.3, aes(colour=Cultivar))+
  #labs(x=" Sowing Month", y="                oCd                Days ")+
  #facet_wrap(~Country)
  #geom_point(shape=21) +
# theme(legend.position="none")+
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
  theme_bw()+
  theme(axis.text.x=element_text(angle = +89, hjust = 0.95))



```
Graph the percentage of burrs discriminating the colours of subspecies 


```{r, fig.height= 5, fig.width=10 , warning=FALSE}}
df_bur %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_each(funs(mean,sd)) %>%
  mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=PropBurrBuried_mean-PropBurrBuried_sd/2, ymax=PropBurrBuried_mean+PropBurrBuried_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
    labs(y="Percentage Buried burrs") +
theme(axis.text.x=element_text(angle = +89, hjust = 0.95))
head(df_bur)

```

Statistical Analisis 
Do ANOVA simple as per D. Saville : each sowing date separately.

```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bur)

df_burANOVA <- df_bur #use to filter%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)

```

Here Analyse the percentage of buried burs overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

Perform anova in single sowing dates : S1 



```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bur)

df_burANOVA <- df_bur %>%    #use to filter%>%
  filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)

```

Here Analyse the percentage of buried burs overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

S2 


```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bur)

df_burANOVA <- df_bur %>% #use to filter%>%
  #filter(SowTreat=="S1")
  filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)

```

Here Analyse the percentage of buried burs overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```



S3


```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bur)

df_burANOVA <- df_bur %>% #use to filter%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)

```

Here Analyse the percentage of buried burs overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

Then S4 


```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bur)

df_burANOVA <- df_bur%>%  #use to filter%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)

```

Here Analyse the percentage of buried burs overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

S6


```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bur)

df_burANOVA <- df_bur%>% #use to filter%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)

```

Here Analyse the percentage of buried burs overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

And finally S7


```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bur)

df_burANOVA <- df_bur %>% #use to filter%>%
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA


file.subset <- file 

head(file.subset)
summary(file.subset)

```

Here Analyse the percentage of buried burs overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(PropBurrBuried ~ SowTreat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```




The chunks below filter each sowing date _ Transform checks (not using it now)


```{r}


#data transformation 
df_bur$transf_no <- 1*(df_bur$PropBurrBuried)
# df_bur$transf_sqr <- sqrt(df_bur$PropBurrBuried)
# df_bur$transf_log <- log(df_bur$PropBurrBuried)
# df_bur$transf_acos <- acos(df_bur$PropBurrBuried/100)

head(df_bur)

 file <- df_bur
 
#................................................................
 #No need for this  
# x <- c( "df_bur$transf_no',transf_sqr", "transf_log", "transf_acos","df_bur$transf_no")
# colsSelec <- match(x,colnames(file))
# 
# file %>%
#   tidyr::gather("transformation","value",colsSelec) %>%
#   ggplot(aes(value)) + 
#   geom_histogram() +
#   facet_grid(.~transformation, scales="free")
# 
# head(file)
# 
# #normality test
# shapiro.test(file$transf_log)

# #QQplot
# var<-file$transf_acos
# qqnorm(var)
# qqline(var, col = 2)
# qqplot(var, rt(300))

#-------------------------------------------------
# ANOVA (selecing by hand FIXME: do loop)
file.subset <- file %>%
 #here filter the swoTreat to analyse separately
  subset(SowTreat == "S1" )







```

```{r}

file.subset <- file

#head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, data = file.subset)

summary(my.anova)

```

```{r}


#Means separation 
(LSD.test(my.anova, "Cultivar", alpha= 0.05, p.adj="none")) 

#TukeyHSD(my.anova)
```










