---
title: "Total Number of Burrs per m2 "
author: "CT"
date: "Friday, March 18, 2016"
output: html_document
---

This script calculates the number of burrs per each plant (Burrs or inflorescence per plant ) and run ANOVA 

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
```

Read File 

```{r, echo=FALSE}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\BurrYieldBurIv2")
getwd()
file <- read.table("SeedBurrYield.txt",header=TRUE)
head(file)
summary(file)
```

Define formats 

```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.numeric(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    Date = dmy(Date),
    SowingD = dmy(SowingD)
  )

str(file)
summary(file)

```

Calculate the individual burr weight and burr number 

```{r}

df <- file %>%
  dplyr::select(Cultivar,SowTreat,sample_area_m2,Block,Plot,
                Depth,bur_total_weight_g,
                bur_no_subSample,
                bur_weight_subSample_g) %>%
  mutate(IndBurrW = bur_weight_subSample_g/
           bur_no_subSample,
         BurrNumber = bur_total_weight_g/IndBurrW) %>%  
  group_by(Cultivar, SowTreat,Depth,Block,Plot) %>%
  summarise_each(funs(mean)) %>%
  dplyr::select(Cultivar,SowTreat,Plot, 
                Depth,BurrNumber,Block)
  df <- as.data.frame(df)
head(df)

```

Calculate the total burr number per plot (sum of above and below)


```{r}
dfBurrTotal <-df%>%
  group_by(Cultivar,SowTreat,Plot)%>%
  dplyr::select(BurrNumber)%>%
  summarise_all(funs(sum))


```

Add the plant population data

```{r}
file1 <- read.table("df_emerg_perc3.txt",header=TRUE)
head(file1)
summary(file1)

file2<-file1 %>%
  dplyr::select(Plot, FinalPop)
```


```{r}
dfmerged <- merge(dfBurrTotal,file2, by=c("Plot")) %>%
  mutate(BurrsperPlant=BurrNumber/FinalPop)
  #dplyr::select(Plot:SowTreat, Hard_perc,slope)


str(dfmerged)
```




Calculate the total number of burs per 1 plant . Graph it 

```{r, fig.height= 5, fig.width=10 , warning=FALSE}

#
#barplot for urrs per plant 
#The palette with grey:
cbPalette <- c("#999999", "#666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)
#use 3.46 as 2 x 1.73 to grph with SE instead of Sd
  dfmerged %>%
  #tidyr::spread(Depth,SeedsNo_m2) %>%
  #mutate(SeedsNo_m2= Down/(Down+Up)*100) %>%
  #mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
group_by(Cultivar, SowTreat) %>%
    filter(SowTreat!="S6", SowTreat!="S7")%>%
    dplyr::select(BurrsperPlant)%>%
    summarise_all(funs(mean,sd)) %>%
    mutate(SE=sd/1.73)%>%
  ggplot(aes(x=Cultivar, y=(mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=mean-SE/2,     
                    ymax=mean+SE/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
  facet_grid(.~SowTreat, scales="free") +
    #labs(y= "Seed Number per m2")+
    ylab(expression(Burrs~number~per~1~plant))+
theme(axis.text.x=element_text(angle = +90, hjust = 0))+
  theme(text = element_text(size = 14))


```

Graph all dataset ; panels are sowing treatments 

```{r, fig.height= 5, fig.width=10 , warning=FALSE}


```

stopped here .... not ready yet 




Mean overall values per sowing date 


```{r,  fig.height= 5, fig.width=10 , warning=FALSE}}

#a <-df_bura %>%
  
df_bura %>%
  group_by(SowTreat) %>%
  summarise_each(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=SowTreat, y=(TotalBurr_m2_mean),fill=SowTreat))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=TotalBurr_m2_mean-TotalBurr_m2_sd/2, 
                    ymax=TotalBurr_m2_mean+TotalBurr_m2_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    #facet_grid(.~SowTreat) +
    #labs(y="% Total number of  burrsper 1 m2", size=16) +
  ylab(expression(Total~number~of~burrs~per~1~m^"2")) +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
  theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 0, hjust=0.95,vjust=0.2,size = 12))

#head(a)

```

Mean overall values per cultivar over all sowing dates  (used to write in chapter)


```{r}

df_bura %>%
  group_by(Cultivar) %>%
  summarise_each(funs(mean,sd)) %>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=(TotalBurr_m2_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=TotalBurr_m2_mean-TotalBurr_m2_sd/2, 
                    ymax=TotalBurr_m2_mean+TotalBurr_m2_sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    #facet_grid(.~SowTreat) +
    #labs(y="% Total number of  burrsper 1 m2", size=16) +
  ylab(expression(Total~number~of~burrs~per~1~m^"2")) +
  theme_bw()+
theme(axis.text.y = element_text( size = 10))+
theme(axis.title.y = element_text(face="bold", size=12))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))

#head(b)
```


Do ANOVA simple as per D. Saville 

here analysis of overall experiment (sow Treat as a factor ) 
```{r}

summary(df_bura)

df_burANOVA <- df_bura
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ SowTreat + Block, data = file.subset)

summary(my.anova)

#Means separation after ANOVA
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 


```

Analyse cultivars overall  
```{r}
summary(df_bura)

df_burANOVA <- df_bura
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)

#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 


```


Analyses of individual sowing dates -here S1

```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bura)

df_burANOVA <- df_bura%>% #use to filter
  filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)

```


```{r}

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

ANOVA S2 


```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bura)

df_burANOVA <- df_bura%>% #use to filter
  #filter(SowTreat=="S1")
  filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)

```


```{r}

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

ANOVA S3 


```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bura)

df_burANOVA <- df_bura%>% #use to filter
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)

```


```{r}

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

Anova S4 


```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bura)

df_burANOVA <- df_bura%>% #use to filter
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)

```


```{r}

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```


ANOVA S6 


```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bura)

df_burANOVA <- df_bura%>% #use to filter
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  filter(SowTreat=="S6")
  #filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)

```


```{r}

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

Anova S7 


```{r}

#Filter  S1, S2, S3, S4, S6 , S7 
summary(df_bura)

df_burANOVA <- df_bura%>% #use to filter
  #filter(SowTreat=="S1")
  #filter(SowTreat=="S2")
  #filter(SowTreat=="S3")
  #filter(SowTreat=="S4")
  #filter(SowTreat=="S6")
  filter(SowTreat=="S7")


#-------------------------------------------------
# anova 
file <- df_burANOVA

file.subset <- file 

head(file.subset)
summary(file.subset)

```


```{r}

#ANOVA
my.anova <- aov(TotalBurr_m2 ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

End of this script. Outputs summary also saved in Excel Analysis folder.







The chunks below were prototypes _ Transform checks (not using it now)

```{r}


#data transformation 
df_bur$transf_no <- 1*(df_bur$PropBurrBuried)
# df_bur$transf_sqr <- sqrt(df_bur$PropBurrBuried)
# df_bur$transf_log <- log(df_bur$PropBurrBuried)
# df_bur$transf_acos <- acos(df_bur$PropBurrBuried/100)

head(df_bur)

 file <- df_bur
 
#................................................................
 #No need for this  
# x <- c( "df_bur$transf_no',transf_sqr", "transf_log", "transf_acos","df_bur$transf_no")
# colsSelec <- match(x,colnames(file))
# 
# file %>%
#   tidyr::gather("transformation","value",colsSelec) %>%
#   ggplot(aes(value)) + 
#   geom_histogram() +
#   facet_grid(.~transformation, scales="free")
# 
# head(file)
# 
# #normality test
# shapiro.test(file$transf_log)

# #QQplot
# var<-file$transf_acos
# qqnorm(var)
# qqline(var, col = 2)
# qqplot(var, rt(300))

#-------------------------------------------------
# ANOVA (selecing by hand FIXME: do loop)
file.subset <- file %>%
 #here filter the swoTreat to analyse separately
  subset(SowTreat == "S1" )







```

```{r}

file.subset <- file

#head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, data = file.subset)

summary(my.anova)

```

```{r}


#Means separation 
(LSD.test(my.anova, "Cultivar", alpha= 0.05, p.adj="none")) 

#TukeyHSD(my.anova)
```










