---
title: "Seed Breakdown  Test base line corrected"
author: "CT"
date: "21 March 2017" ## revised in 15.11.2017 (ESA paper 2018)
output: html_document
---
This script reads the baselined corrected spectra for 3 cultivars (Antas, Monti and Narrikup) in 3 different incubation times (0, 42, 84) consider the data with reps generated in script 2 (Correct 2 Reps ). It normalises the spectra using the max peak method 

```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2) 
library(agricolae)
library(knitr)
library (lubridate)
library(scales)

```



```{r readData}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\ESA2018_Biochem")
getwd()

#create file
df_sp <- read.table("BreakBaselined3cv_2.txt",header=TRUE)



#head(df_sp)

summary(df_sp)
```
##select columns of interest Cultivar Incubation days rep AbsValue Wavenumber

```{r}
df_sp1<-df_sp%>%
  dplyr::select(Cultivar:Rep, AbsValue,WaveNumber)
  

str(df_sp1)

```

## Normalization with Max Peak method (Burgi feedback 18.06!!)

```{r}


df_sp2 <- df_sp1%>%
  group_by(Cultivar, IncubationDays, Rep)%>%
  mutate(Absorbance=AbsValue/max(AbsValue))




```


 

## Get the mean value for Absorbance for the Normalized spectra now 

```{r}
df_sp3<-df_sp2%>%
  group_by(Cultivar,IncubationDays,WaveNumber)%>%
  dplyr::select(Absorbance)%>%
  summarise_all(funs(mean))
  #mutate(Absorbance=AbsValue)%>%
  #dplyr::select(-AbsValue)
  
  str(df_sp3)
  
```



## Graph it all , 

```{r, fig.height=5, fig.width=15}

##select only Antas and Monti
df_sp4 <-df_sp3 %>%
    filter(Cultivar!="N")
    

df_sp4%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  #expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)
  

write.table(df_sp3,"MaxNorm_SpectraESA2018.txt")
```

zoom spectra 




```{r}

##select only wavenumbers between 3700-2700, then 
df_spzoom <-df_sp4 %>%
    filter(Cultivar!="N")%>%
  subset(WaveNumber <1700 & WaveNumber >1600) 
  
  

  

df_spzoom %>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) 
  #geom_abline(intercept = 0.1, slope = 0)
  
#write.table(df_sp33, "BaselinedMaxNorm1.txt") #this will be used to buil the graph (portion 1 of spectra)

```





Create a graph with baselined corrected spectra with snaps on x axes 



```{r}

##select only wavenumbers between 3700-2700, then 
df_sp33 <-df_sp4 %>%
    filter(Cultivar!="N")%>%
  subset(WaveNumber <3600 & WaveNumber >2800) 
  
  

  

df_sp33%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  #geom_abline(intercept = 0.1, slope = 0)
  
write.table(df_sp33, "BaselinedMaxNorm1.txt") #this will be used to buil the graph (portion 1 of spectra)

```

subset again 
```{r}

##select only wavenumbers between 3700-2700, then 
df_sp43 <-df_sp4 %>%
    filter(Cultivar!="N")%>%
  #subset(WaveNumber <3700 & WaveNumber >2700  )
subset(WaveNumber <1800 & WaveNumber >800 )

  
  write.table(df_sp43, "BaselinedMaxNorm2.txt") #this will be used to buil the graph (portion 2 of spectra)

df_sp43%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)



```

Ok now check here why antas is doing funny in the graph!!! 


Now combine the two dataframes (df_sp33 and df_43)and bring the file to build the graph (see Excel file SpectraMaxNormalisedChopped; 
C:\Users\teixe\Documents\CarmenDocumentsPhD\A_Carmenfiles02.06.2018\ESAPaper2018\Biochem)


```{r}

getwd()

#create file
df_spSegment <- read.table("Spectra_ESA2018_BaseMaxNormSegmented.txt",header=TRUE)


```

Here graph with facet grid to get the snaped wavenumber (for the poster )


```{r}

str(df_spSegment)

```




```{r, fig.height=5, fig.width=20}



df_spSegment2<-df_spSegment  %>%
  mutate(Days= as.factor(IncubationDays))%>%
  mutate (SpectraPart= factor(SpectraPart, levels=c("3600-2800", "1800-800")))%>%
  mutate (Cultivar_f= factor(Cultivar, levels=c("A", "M"),labels=c("Antas", "Monti")))%>%
  mutate (SpectraPart_f = factor(SpectraPart, levels=c('3600-2800','1800-800')))
 
                       
  df_spSegment2  %>%   
    #force spectra order here                              
     # df_spSegment$SpectraPart_f = factor(df_spSegment$SpectraPart, levels=c('3700-2700','1800-850'))%>% 
  ggplot(aes(x=WaveNumber,y=Absorbance))+
    #geom_line(aes(), colour=IncubationDays))+
  geom_line(aes(colour=Days),size=2)+
    scale_color_manual(values=c("blue", "darkred"))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
    #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar_f ~SpectraPart_f,scales="free") +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  
  theme_bw()+
  theme(strip.text.x =  element_blank())+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,1.2)) +
    labs(y= " Absorbance ")+
    xlab(expression(Wavenumber~"(cm"^"-1"*")"))+
#theme(axis.text.y = element_text( size = 24))+
  #theme(axis.title.y = element_text(face="bold", size=14))+
#theme(axis.text.x=element_text(angle = 0, hjust=0.95,vjust=0.2,size = 28)) +
    
    #remove grid lines 
    
    #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),

axis.line = element_line(colour = "black"))+
     #make cultivars white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
    
theme(text = element_text(size = 24))+
theme(axis.text.y = element_text( size = 16))+ theme(axis.title.y = element_text(face="bold", size=24))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 24))+
theme(axis.title.x = element_text( size=24,face="bold"))
#   labs(y="Measured seed weight (mg) ",x="Reported seed weight (mg) ")
#  # geom_abline(intercept = 50, slope = 0)
 # geom_abline(intercept = 0.1, slope = 0)

   #Save graph 
 
 ggsave("plot_spectraMaxNorm_ESA2018_Poster.png", width=16, height=10, dpi=400)


```



Graph completed. Snaped spectra baseNormalised contains wavenumbers from 3600-2800 and then load the dataframe on another script to compare the P values of the vibrations. 

#