---
title: "Seed Breakdown  Test base line corrected"
author: "CT"
date: "21 March 2017" ## revised in 15.11.2017 (ESA papaer 2018)
output: html_document
---
This script reads the baselined corrected and normalised spectra (Unscrambler area method ) for 2 cultivars (Antas, Monti -2  different incubation times (0, 84) consider the data with reps generated in script 2 (Correct 2 Reps ) 

```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)

```



```{r readData}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\ESA2018_Biochem")
getwd()

#create file
#df_sp <- read.table("BreakBaselined3cv_2.txt",header=TRUE)
df_sp <- read.table("UntreatedESANormalised2018.txt",header=TRUE)
#UntreatedESANormalised2018


head(df_sp)

#summary(df_sp)
```


use gather to transform clumns in AbsValue and WaveNumber 


```{r}

df_sp_gather <- df_sp  %>%
  tidyr::gather("AbsFactor", "AbsValue",starts_with("X")) %>%
  mutate(WaveNumber=as.numeric(gsub("X","",AbsFactor)), AbsFactor=factor(AbsFactor)) %>%
  mutate(id=factor(paste0(Cultivar,"_",AbsFactor))) %>%
  group_by(id, AbsFactor, Cultivar, IncubationDays, Rep) %>%
  summarise_all(funs(mean)) %>%
  dplyr::select(-Seed, -RowNo, -id, -AbsFactor)

head(df_sp_gather)


```





```{r}
#empty
```




-----------------------------------------------------------------------------------------
then continue normal script from here .....similar to baselined spectra but use the normalised Unscrambler area method ....

##select columns of interest Cultivar Incubation days rep AbsValue Wavenumber

```{r}
df_sp1<-df_sp_gather%>%
  dplyr::select(Cultivar, IncubationDays, Rep, AbsValue,WaveNumber)
 
# df_sp1A <- df_sp1%>%
  #ungroup()

```

## Get the mean value for Absorbance 

```{r}
df_sp2<-df_sp1%>%
  group_by(Cultivar,IncubationDays,WaveNumber)%>%
  dplyr::select(AbsValue)%>%
  summarise_all(funs(mean))%>%
  mutate(Absorbance=AbsValue)%>%
  dplyr::select(-AbsValue)
  
  str(df_sp2)
  
```

#Parei aqui...horrible graph with Normalised data !! 

## Graph it all , 

```{r, fig.height=5, fig.width=15}

##select only Antas and Monti
df_sp3 <-df_sp2 
   # filter(Cultivar!="N")
    

df_sp3%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)
  

#write.table(df_sp3,"MeanSpectraESA2018.txt")
```

Create a graph with baselined corrected spectra with snaps on x axes 



```{r}

##select only wavenumbers between 3700-2700, then 
df_sp33 <-df_sp2 %>%
    filter(Cultivar!="N")%>%
  subset(WaveNumber <3700 & WaveNumber >2700) 
  
  

  

df_sp33%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)
  
write.table(df_sp33, "Baselined1.txt") #this will be used to buil the graph (portion 1 of spectra)

```

subset again 
```{r}

##select only wavenumbers between 3700-2700, then 
df_sp43 <-df_sp2 %>%
    filter(Cultivar!="N")%>%
  #subset(WaveNumber <3700 & WaveNumber >2700  )
subset(WaveNumber <1800 & WaveNumber >850 )

  
  write.table(df_sp43, "Baselined2.txt") #this will be used to buil the graph (portion 2 of spectra)

df_sp43%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar ~.) +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)



```

Now combine the two dataframes (df_sp33 and df_43)and ring the file to build the graph


```{r}

getwd()

#create file
df_spSegment <- read.table("Spectra_ESA2018_BaselinedSegmented.txt",header=TRUE)


```

Here graph with facet grid to get the snaped wavenumber 


```{r, fig.height=5, fig.width=20}

str(df_spSegment)

df_spSegment2<-df_spSegment  %>%
  mutate(Days= as.factor(IncubationDays))%>%
  mutate (SpectraPart= factor(SpectraPart, levels=c("3700-2700", "1800-850")))%>%
  mutate (Cultivar_f= factor(Cultivar, levels=c("A", "M"),labels=c("Antas", "Monti")))%>%
  mutate (SpectraPart_f = factor(SpectraPart, levels=c('3700-2700','1800-850')))
 
                       
  df_spSegment2  %>%   
    #force spectra order here                              
     # df_spSegment$SpectraPart_f = factor(df_spSegment$SpectraPart, levels=c('3700-2700','1800-850'))%>% 
  ggplot(aes(x=WaveNumber,y=Absorbance))+
    #geom_line(aes(), colour=IncubationDays))+
  geom_line(aes(colour=Days))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
    #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar_f ~SpectraPart_f,scales="free") +
  #facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  
  theme_bw()+
  theme(strip.text.x =  element_blank())+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
    labs(y= " Absorbance ")+
    xlab(expression(Wavenumber~"(cm"^"-1"*")"))+
#theme(axis.text.y = element_text( size = 24))+
  #theme(axis.title.y = element_text(face="bold", size=14))+
#theme(axis.text.x=element_text(angle = 0, hjust=0.95,vjust=0.2,size = 28)) +
theme(text = element_text(size = 24))+
theme(axis.text.y = element_text( size = 22))+ theme(axis.title.y = element_text(face="bold", size=24))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0,size = 24))+
theme(axis.title.x = element_text( size=24,face="bold"))
#   labs(y="Measured seed weight (mg) ",x="Reported seed weight (mg) ")
#  # geom_abline(intercept = 50, slope = 0)
 # geom_abline(intercept = 0.1, slope = 0)

   #Save graph 
 
 ggsave("plot_spectraESA2018_Poster.png", width=24, height=8, dpi=400)


```




Create a graph with baselined corrected spectra with time as panels 


```{r, fig.width=15, fig.height=5}

df_sp3%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(Cultivar)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  #facet_grid(Cultivar ~.) +
  facet_grid(IncubationDays ~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)


```





```{r,fig.height=5, fig.width=10}

##select only Antas and Monti
df_sp3 <-df_sp2 %>%
    filter(Cultivar!="N")
    
str(df_sp3)

df_sp3%>%
  ungroup(Cultivar)%>%
  mutate (Cultivar= factor(Cultivar, levels=c("A", "M"),labels=c("Antas", "Monti")))%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
   #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  facet_grid(Cultivar ~.) +
  scale_x_reverse(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =100))) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)



```





##Graph the subset wavenumbers 2900-2700 


```{r, fig.height=4, fig.width=8}

##select only Antas and Monti
df_sp4 <-df_sp3 %>%
    subset(WaveNumber>2800 & WaveNumber<3000 )
    


df_sp4%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),400))+
    facet_grid(Cultivar ~.) +
  theme_bw()+
      scale_x_reverse()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)
```


```{r, fig.height=5, fig.width=10}

df_sp %>%
  
  ggplot(aes(x=Wavelength,y=Absorbance))+
  geom_line(aes(colour=IncubationDays))+
  #geom_line(aes(colour= factor(IncubationDays)))+
  scale_colour_gradient(low="red")+
    theme_bw()+
   #scale_x_continuous(breaks=seq(min(df_sp$Wavelength),max(df_sp$Wavelength),400))+
  scale_x_reverse()+
 # scale_x_reverse(lim=c(650,4000))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)
  #geom_vline(intercept = 1000, slope = 0)
    #scale_x_date(labels = date_format("%b-%Y"))



```

MAke the difference between incubation days 0 and 84 ; find bands which change the most. filter out 42.Use difference absolute and %. 

```{r}

df1 <- df_sp  %>%         
  mutate(IncubationDays=factor(paste0("A_",IncubationDays)))%>%
  filter(IncubationDays!="A_42") %>%
  tidyr::spread(IncubationDays,Absorbance)%>%
  mutate(DiffAbsolute=A_0-A_84,DiffRelative=DiffAbsolute/A_0*100) #%>%
#Now gather values 
#tidyr::gather("Varname", "Varvalue",A_0:DiffRelative )
summary(df1)
```


Now graph the differences 

```{r}
df2 <-df1 %>%
  filter(Cultivar!="Narrikup")%>%
  subset(DiffRelative>5 & DiffRelative<100)

df2 %>%
  ggplot(aes(x=Wavelength,y=DiffRelative))+
  geom_line(aes(colour=Cultivar))+
  theme_bw()+
 # facet_grid(.~Cultivar,scales="free") +
  scale_x_reverse()+
  geom_abline(intercept = 0, slope = 0)
 
   
  
```


#