---
title: "Thermal treatment experiment - dataset for the ESA Poster 2018"
author: "CT"
date: 21.06.2018 (ESA paper 2018)
output: html_document
---
This script reads the baselined and mas. normalised spectra  for the 3 replicates 2 cultivars (Antas, Monti ) in 2 different incubation times (0,  84)  
And calculates the P vlaues to identify sign. bands (compare wiht PCA - Burgi analysis )

```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(scales)

```

Here bring the original file Break Baselin REps 

```{r readData}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\ESA2018_Biochem")
getwd()

#create file
df_sp <- read.table("BreakBaseLineReps.txt",header=TRUE)

#head(df_sp)

head(df_sp)
```

##select columns of interest 

- make wavelength a factor 

```{r}
df_sp2 <-df_sp %>%
mutate(IncubationDays=factor(IncubationDays), Rep=factor(Rep)) %>%
filter(IncubationDays!="42")%>%  
#Now gather values 
tidyr::gather("AbsFactor", "AbsValue",starts_with("X")) %>%
mutate(WaveNumber=as.numeric(gsub("X","",AbsFactor)), AbsFactor=factor(AbsFactor)) %>%
mutate(id=factor(paste0(Cultivar,"_",AbsFactor))) %>% # done to loop across cultivars
group_by(id, AbsFactor, Cultivar, IncubationDays, Rep) %>%
summarise_all(funs(mean)) %>%
dplyr::select(-Seed, -RowNo)

summary(df_sp2)
```

normalise the AbsValue using Max method (feedback 19.06)

```{r}

df_sp2 <- df_sp2%>%
  group_by(Cultivar, IncubationDays, Rep)%>%
  mutate(Absorbance=AbsValue/max(AbsValue))

summary(df_sp2)
```


graph the max normalised average spectra 



```{r}

df_sp3 <-df_sp2 %>%
    filter(Cultivar!="N")%>%

  group_by(Cultivar,IncubationDays,WaveNumber)%>%
  dplyr::select(Absorbance)%>%
  summarise_all(funs(mean))


```


```{r, fig.height=5, fig.width=15}


  #Graph check 
    

df_sp3%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(Cultivar)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  
    facet_grid(IncubationDays~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 0, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)
  

```

zoom

```{r}

a<-df_sp3  %>%
    subset (WaveNumber>1500 & WaveNumber<1850) %>%

  group_by(Cultivar,IncubationDays,WaveNumber)%>%
  dplyr::select(Absorbance)%>%
  summarise_all(funs(mean))
  
    

a%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(Cultivar)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
  
    facet_grid(IncubationDays~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)


```



Now graph comparing time 

```{r, fig.height=5, fig.width=15}

df_sp3%>%
   ggplot(aes(x=WaveNumber,y=Absorbance))+
  geom_line(aes(colour=factor(IncubationDays)))+
  theme_bw()+
  #scale_x_continuous(breaks=seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50))+
  
  #scale_x_continuous(breaks=round(seq(min(df_sp$WaveNumber),max(df_sp$WaveNumber),by =50)))+
    facet_grid(Cultivar~.) +
  scale_x_reverse()+
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  expand_limits(y=c(0,0.2)) +
  geom_abline(intercept = 0.1, slope = 0)



```


Select only the cultivars Antas and Monti for ESA 2018. Prepare dataframe for Stats: select the cultivars and snap the spectra.  


```{r}

#select out narrikup 
df_sp2a <- df_sp2 %>%
  filter(Cultivar!="N")



```


##Snap the Spectra : select regions 3600-2800 and 1800-800 but use the dataframe with the Reps (df_sp2)



```{r}

##select only wavenumbers between 3700-2800 
df_sp21 <-df_sp2 %>%
    filter(Cultivar!="N")%>%
  subset(WaveNumber <3600 & WaveNumber >2800) 



##then snap again ;  

##select only wavenumbers between 1800-800 
df_sp22 <-df_sp2 %>%
    filter(Cultivar!="N")%>%
  subset(WaveNumber <1800 & WaveNumber >800) 


#df_snap2b <- df_sp2a [!anywhere(df_sp2a, mIntervals[, 2801], mIntervals[, 1801], incbounds = FALSE)]



```

Bind the dataframe 


```{r}

df_spBind <- rbind(df_sp21, df_sp22)
  #filter(Cultivar!="N")%>%
  #dplyr::select(-AbsValue)

#str(df_sp4Bind)


```


Loop unique wavenumber but using the absorbance values (normalised column)

```{r}

idList <-unique(df_spBind$id) 

print(paste0("Found ",length(idList)," wavelength by cultivar combinations to loop"))

data.all <- data.frame()

x <- 0 # for t test

for (i in 1:length(idList)) {
  
    df <- df_spBind %>%
    ungroup() %>%
    mutate(IncubationDays=factor(IncubationDays), Rep=factor(Rep)) %>%
    subset(id == idList[i])
  
  my.anova <- aov(Absorbance ~ IncubationDays + Rep, data = df)
   
  pVals <- summary(my.anova)[[1]][["Pr(>F)"]]
 
    # T test when P<0.05
  if(!is.nan(pVals[1]) & pVals[1] < 0.05) {
  
  x <- x + 1
  t_test <-  LSD.test(my.anova, c("IncubationDays"), alpha= 0.05, p.adj="none")
  lsd <- t_test$statistics[6] # getting  lsd
  
  this.data <- data.frame(Cultivar=df$Cultivar[1], WaveNumber = df$WaveNumber[1], PV = pVals[1], LSD = lsd, Count=x)
  
  data.all <- rbind(data.all, this.data)
  
  this.data <- NULL
  
  } else {
    
# do nothing
   
  }
  
}
```

write a table with values by cultivar 

```{r}


write.table(data.all, "MaxNormalised_P_LSD_ESA2018_0_84.txt")
```


graph follows in next script (Normalised) . 
```{r, fig.height=5, fig.width=15}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\ESA2018_Biochem")
getwd()

# Here comparing  incubation Days 


data1 <- read.table("MaxNormalised_P_LSD_ESA2018_0_84.txt",header=TRUE)
data1 %>%
  mutate(FlagSig=ifelse(PV>0,0,NA)) %>%
  filter(Cultivar!="N")%>%
  ggplot(aes(x=WaveNumber,y=PV))+
  geom_point(aes(colour="darkgrey"))+
    geom_point(aes(x=WaveNumber,y=FlagSig, size=1/PV,colour=Cultivar), alpha=0.1 ) +
  theme_bw()+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  facet_grid(Cultivar~.,scales="free") +
# scale_x_reverse(breaks=round(seq(min(data.all$WaveNumber),max(data.all$WaveNumber),by =50)))+
  geom_abline(intercept = 0.01, slope = 0, linetype=2) 


```

Few changes in Antas : only two bands!!! 

For Monti: around 10 regions changed!  

--------------------------------------------------------


## Now how to run with two factors : Incubation and cultivar ?

##need to creat a new id without the cultivar or loop the wavenumber .


```{r}

idList <-unique(df_spBind$id) 

print(paste0("Found ",length(idList)," wavelength by cultivar combinations to loop"))

data.all <- data.frame()

x <- 0 # for t test

for (i in 1:length(idList)) {
  
    df <- df_spBind %>%
    ungroup() %>%
    mutate(IncubationDays=factor(IncubationDays), Rep=factor(Rep)) %>%
    subset(id == idList[i])
  
  my.anova <- aov(Absorbance ~ IncubationDays + Rep, data = df)
#error here?  my.anova <- aov(Absorbance ~ IncubationDays * Cultivar + Rep, data = df)
  pVals <- summary(my.anova)[[1]][["Pr(>F)"]]
 
    # T test when P<0.05
  if(!is.nan(pVals[1]) & pVals[1] < 0.05) {
  
  x <- x + 1
  t_test <-  LSD.test(my.anova, c("IncubationDays"), alpha= 0.05, p.adj="none")
  lsd <- t_test$statistics[6] # getting  lsd
  
  this.data <- data.frame(Cultivar=df$Cultivar[1], WaveNumber = df$WaveNumber[1], PV = pVals[1], LSD = lsd, Count=x)
  
  data.all <- rbind(data.all, this.data)
  
  this.data <- NULL
  
  } else {
    
# do nothing
   
  }
  
}
```







#End of this script 