 ---
title: "ImageJ DataSet Data Exploration "
author: "CT"
date: "Monday, 28 November, 2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
Purpose : 

-Read ImageJ data collected at Bionami_Thermal treatment experiment

-Initial data visualisation : quantify potential colour changes due to degradation of cell wall components (most sensitive = hemicellulose ; relate to suberin and cutin components (?) )

 -Notes: 
 -Values for each of the R, G and B components.
 -That value can be anything between 0 and 255.This is a light level. The higher the RGB values, the lighter the color, the lower the RGB's, the darker the color. Set RGB to 0,0,0 and the result is  black.

- ANOVA -  for the variates : 
Red		Green		Blue		RGBdiv3		0.3R_0.6G_0.1B

## Load Libraries 

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
library(knitr)
```



## Read File 

```{r, echo=FALSE}

##Include the file path 
##path in LeNovo_Yoga: C:\GitHubRepos\SubCloverPhD\SubClover\ThermalTreatmentImageJ

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\ThermalTreatmentImageJ")

getwd()

##Include file name "XX.txt" and create a data frame 
##file name : XX

##FIX ME :need to correct the  number of reps in the original file ! 


file <- read.table("RawData_ThermalT_Colour2.txt",header=TRUE)

head(file)
summary(file)


```


##Define the formats  

```{r}

# Define factors and formats
file <- file %>%
  mutate(
    Rep = as.factor(Rep),
    Cultivar = as.factor(Cultivar),
    Incubation=as.factor(Incubation),
    Seed =as.factor(Seed),
    Variable=as.character(Variable),
    Area = as.numeric(Area),
    Mean = as.numeric(Mean),
    Min = as.numeric(Min),
    Max = as.numeric(Max)
   
  )

```

#Data check 


```{r}


##Inspect data structure 

str(file)

```

  

```{r}

##Inspect data summary 

summary(file)

```

##Data visualisation 

```{r}

##Select variable and columns of interest : reduce the ammount of data to analyse 

file_select <- file %>%
    filter(Variable == "Red")%>%
  select(Cultivar, Incubation, Rep, Variable, Mean)
  
#Check headings 
head(file_select)


```

#check summary  
```{r}


summary(file_select)
```

## This step:  calculate the mean and sd for each cultivar and incubation 
## good source for data transformation : https://ugoproto.github.io/ugo_r_doc/dplyr.pdf


```{r}


Mean_sd <-file_select %>%
  group_by(Cultivar, Incubation) %>%
  #select within Variable "Red" the column you want to get the mean and standard deviation 
 select (Mean)%>%
  summarise_all(funs(mean,sd))

#check
head(Mean_sd)
```

##Graph 
##simple version

```{r}
## define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

#use selected dataframe 

Mean_sd %>%
  filter(Incubation=="0")%>%
  ggplot(aes(x=Cultivar, y=(mean)))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=mean-sd/2, ymax=mean+sd/2),
                width=0.25, size=0.3,position=dodge_x) +  
        theme_bw() +


```




## good source for graphics in ggplot2 : https://www.rstudio.com/wp-content/uploads/2015/03/ggplot2-cheatsheet.pdf

```{r, fig.height= 5, fig.width=10 , warning=FALSE}

## define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

#use select dataframe 
Mean_sd %>%
  ggplot(aes(x=Cultivar, y=(mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin=mean-sd/2, ymax=mean+sd/2),
                width=0.25, size=0.3,position=dodge_x)   +
  
  theme_grey(base_size = 5) +
  #facet grid or facet wrap generate panels 
    facet_grid(.~Incubation) +
    labs(y="Red level from RGB ", x="Cultivar") +
  
  theme_bw()+
theme(axis.text.y = element_text( size = 24))+
theme(axis.title.y = element_text(face="bold", size=24))+
theme(axis.text.x=element_text(angle = 0, hjust=0.95,vjust=0.2,size = 24))


```

#######STOP HERE !  Need to adjust scripts from here on ##### 


## Here graph with the SE (SE = sd/ sqrt n ; in this case n=4 ; SE= sd/2)

```{r,fig.height= 5, fig.width=10 , warning=FALSE}

#try create similar graph with SE 

  
  



```


## 

```{r, fig.height=5, fig.width=10}

# define position of bar and errorbar
# dodge_x <- position_dodge(width = 0.9)
# 
# df_burSubset<-file %>%
#   filter(Year !="2017")%>%
#   filter(Treat=="Cut")%>%
#   filter(Cultivar=="Antas"| 
#          Cultivar=="Denmark"|
#          Cultivar=="Coolamon"|
#            Cultivar=="MountBarker"|
#            Cultivar=="Narrikup"|
#            Cultivar=="Rosabrook"|
#            Cultivar=="Woogenellup")%>%
#   group_by(Cultivar) %>% 
#   dplyr::select(SeedsPerM2)%>%
#   summarise_each(funs(mean,sd)) %>%
#   mutate(SE=sd/2)
# 
#   #Then graph it 
# df_burSubset %>%
#   #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
#   #ggplot(aes(x=Cultivar, y=(SeedsPerM2_mean),fill=colPal)) +
#   #ggplot(aes(x=Cultivar, y=(mean),fill=Cultivar))+
#   ggplot(aes(x=Cultivar, y=(mean)))+
#   geom_bar(stat="identity", position = dodge_x) +
#   geom_errorbar(aes(ymin=mean-SE/2, ymax=mean+SE/2),
#                 width=0.25, size=0.3,position=dodge_x)   +
#   theme_grey(base_size = 16) +
#     #facet_grid(.~Treat) +
#     labs(y="Seeds per m2") +
#   theme_bw()+
# theme(axis.text.y = element_text( size = 10))+
# theme(axis.title.y = element_text(face="bold", size=12))+
# theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 12))
 
##To save graph as image  
#ggsave( "plot_NameGraph_.png", width=10, height=5, dpi=500)
```


###########  Basic Stats ########## 
##Perform  ANOVA simple as per D. Saville (LSD)
Select year and variable to analyse

```{r}
df_seedANOVA <- file %>%
#use filters to select  data 
  # filter(Year=="2016")%>%
  # filter(Treat=="Cut")%>%
  # filter(Cultivar=="Antas"| 
  #        Cultivar=="Denmark"|
  #        Cultivar=="Coolamon"|
  #          Cultivar=="MountBarker"|
  #          Cultivar=="Narrikup"|
  #          Cultivar=="Rosabrook"|
  #          Cultivar=="Woogenellup")%>%
  # dplyr:: select(Cultivar:SeedYieldKgHa)

```

subset for anova
```{r}

 
summary(df_seedANOVA)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA 

head(file.subset)
summary(file.subset)

```

here select the variable 
seed per sqrt meter or seed per sqrtm


```{r}

#ANOVA

#my.anova <- aov(SeedYieldKgHa ~ Cultivar + Block, data = file.subset)
#my.anova <- aov(SeedsPerM2 ~ Cultivar + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```

Perform Tukeys 

This is Tukeys test for mean comparison 

```{r}
#posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)
#loop with varios confidence intervals or alphas

for (i in seq(0.1, 0.95, by=0.1)) {
  
print(paste0("-------------------- CI is: ",i," -------------------"))  
posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=i) # check se CI aand alpha are correctly interpreted
print(posthoc)  
  
hsdTest <-HSD.test(my.anova, 'Cultivar', group=TRUE,alpha = 1-i)
print(hsdTest )
}


```

Then 
This is the mean separation using Tukey 


```{r}

fogo <-HSD.test(my.anova, 'Cultivar', group=TRUE)
fogo

```



Perform anova in cultivars with variable Seed number per m2

```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```

now do the mean table to write

```{r}


means<-file.subset%>%
  group_by(Treat,Cultivar)%>%
  dplyr::select( SeedsPerM2)%>%
  summarise_all(funs(mean))

```

now analyse seed yield kg/ha

Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}

str(file)
df_seedANOVA2 <- file %>%
filter(Year=="2016")%>%
   select(Cultivar:Treat, SeedYieldKgHa)
```


subset for anova
```{r}

 
summary(df_seedANOVA2)

#-------------------------------------------------
# anova 

file.subset2 <- df_seedANOVA2 

head(file.subset2)
summary(file.subset2)

```


Here Analyse the percentage of kg seeds per ha  overall :
consider sow Treat as a factor  (overview)
and then consider cultivar within each sowing date 

```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedYieldKgHa ~ Cultivar*Treat + Block, data = file.subset2)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```


Perform anova in cultivars 


```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


Now analyse the regeneration of the seedlings 

Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}

df_seedANOVA3 <- file %>%
filter(Year=="2016")%>%
   select(Cultivar:Treat, EstimatedRegeneration)
```

subset for anova
```{r}

 
summary(df_seedANOVA3)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA3 

head(file.subset)
summary(file.subset)

```

see all treatmenst 

```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(EstimatedRegeneration ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)
```



```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```



```{r}
#Means separation after ANOVA
(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```


get values for cultivar and treat 
```{r}


#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Treat", "Cultivar"), alpha= 0.05, p.adj="none")) 
```


now perform  Year 2017 (cumulative seed numbers !! )

Statistical Analisis 
Do ANOVA simple as per D. Saville :each seson and variate separately
Select year and variable to analyse

```{r}
df_seedANOVA4 <- file %>%
filter(Year=="2017")%>%
   select(Year:SeedsPerM2)
```



subset for anova4
```{r}

 
summary(df_seedANOVA4)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA4 

head(file.subset)
summary(file.subset)

```

Here Analyse the percentage ofseeds overall :



```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedsPerM2 ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)
```

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar", "Treat"), alpha= 0.05, p.adj="none")) 
```



```{r}
df_seedANOVA5 <- file %>%
filter(Year=="2017")%>%
   select(Year:SeedYieldKgHa)
```



subset for anova5
```{r}

 
summary(df_seedANOVA5)

#-------------------------------------------------
# anova 

file.subset <- df_seedANOVA5 

head(file.subset)
summary(file.subset)

```


```{r}

#ANOVA

#my.anova <- aov(PropBurrBuried ~ Cultivar + Block, data = file.subset)
my.anova <- aov(SeedYieldKgHa ~ Cultivar*Treat + Block, data = file.subset)
summary(my.anova)

```

see effect of scultivar 

```{r}

#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar", "Treat"), alpha= 0.05, p.adj="none"))

```







end of this script 