---
title: "Relationship between redsocre and biomass  "
author: "CT"
date: "17.08.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

This script does this:

-get dataframe for red score and spring biomass for the 16 cv dataset 
-need to exclude white clover and whatatwhata for teh cold paper 

##path is : C:\GitHubRepos\SubCloverPhD\SubClover\RedScoreBiomass16Cv
##file : RedBiomass

```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
library (gridExtra)
```

get file 

```{r loadFile}
# Get dataframe from previous script (written table )
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\RedScoreBiomass16Cv")
getwd()

#create file

#df_G <- read.table("RateEmerg_SoilTemp_IverPokComb.txt",header=TRUE)

df_G <- read.table("RedBiomass.txt",header=TRUE)

```

select columns of interest and Adjust formats 
```{r}

#change formats
df_G$Cultivar <- as.factor(df_G$Cultivar)
df_G$Block <- as.factor(df_G$Block)
df_G$Plot <- as.factor(df_G$Plot)
#df_G$Location <- as.factor(df_G$Location)


str(df_G)

#select columns and select out whata and Nomad Wc
df_G1 <-df_G %>%
dplyr:: select(Block,Cultivar,Cloverkg.ha ,RedScore)%>%
  filter(Cultivar != "Whatawhata" & Cultivar != "Nomad_Wc")
  


str(df_G1)


```




```{r}


df_A3 <-df_G1 %>%
  dplyr::select(Cultivar, Cloverkg.ha, RedScore , Block) %>%
  group_by(Cultivar) %>%
  summarise_all(funs(mean)) %>%
  mutate(y=Cloverkg.ha,x=RedScore) 
  #dplyr::select(-meanTemp_Em, -InvDAS50E, -Plot)

str(df_A3)

```

got the means here ... and graph it

```{r, fig.height=5, fig.width=10, echo = FALSE}
df_A3%>%
ggplot(aes(x=x, y=y, colour=Cultivar))  +
  geom_point(alpha=0.8, size= 3) +
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  #xlab(expression(Red~Score~~"("^"o"*"C)")) + 
  xlab(expression(Red~Score~~"(%)")) +
  ylab(" Mean clover yield (kg/ ha) ") +
  #facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=12))+
 scale_x_continuous(limits = c(0,100))+
  scale_y_continuous(limits = c(0,7000))


# 

```



here get the equations   

```{r, fig.height=5,fig.width=10}
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}

#use all datapoints 
df <- df_G1 %>%
  #dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E, Location) %>%
  dplyr::select(Cultivar, Cloverkg.ha, RedScore , Block)%>%
  group_by(Cultivar) %>%
  summarise_each(funs(mean)) %>%
  mutate(y=Cloverkg.ha,x=RedScore) %>%
  dplyr::select(-Cloverkg.ha, -RedScore)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_point(aes(colour = factor(Cultivar)), size=5) + scale_shape(solid = FALSE)+ 
  
  theme_bw()+
  scale_x_continuous(limits = c(0,100))+
  scale_y_continuous(limits = c(0,5000))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE)
#+ 
 # facet_grid(Cultivar~.,scales="free")
  
p1
```


```{r}
#get statistical summary here 
summary(lm(y ~ x, df))
```



End of this script
