---
title: "Senescence - Harvest time of the  6CV Iversen 2"
author: "CT"
date: " 07.06.2016"
output: html_document
---
Purpose of this script : 
calculate the days to 100 senescence from Iversen 2 dataset 

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```

Read the file and check formats 

```{r loadFile}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\HarvestDASIv2")
getwd()

#create file
df_Hvst <- read.table("DAStoSenescence.txt",header=TRUE)
head(df_Hvst)


# define formats 
df_Hvst$ReadDate <- dmy(df_Hvst$ReadDate )
df_Hvst$SowingD <- dmy(df_Hvst$SowingD)
df_Hvst$SowTreat <- as.factor(df_Hvst$SowTreat)
df_Hvst$Block <- as.factor(df_Hvst$Block)
df_Hvst$Plot <- as.factor(df_Hvst$Plot)
    

str(df_Hvst)
# head(df_Hvst)
# summary(df_Hvst)
# tail(df_Hvst)



```


Run ANOVA pure numbers for DAS50Emergence
Repeat the process for all sowing dates 
Write in Chapter 4

S1 

```{r}

file <- df_Hvst %>% 
filter(SowTreat =="S1") 
summary (file)  


#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#To get means select the factor : SowTreat or Cultivar
my.anova <- aov(DAS ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)


```
Get mean separation and  SE values 

```{r}

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
```

S2 ANOVA

```{r}

file <- df_Hvst %>% 
filter(SowTreat =="S2") 
summary (file)  


#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#To get means select the factor : SowTreat or Cultivar
my.anova <- aov(DAS ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

```

S2 mean separation 
```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )

```

S3 Anova 

```{r}
file <- df_Hvst %>% 
filter(SowTreat =="S3") 
summary (file)  


#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#To get means select the factor : SowTreat or Cultivar
my.anova <- aov(DAS ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)
```


S3 mean separation

```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )

```

S4 Anova 

```{r}

file <- df_Hvst %>% 
filter(SowTreat =="S4") 
summary (file)  


#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#To get means select the factor : SowTreat or Cultivar
my.anova <- aov(DAS ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

```


S4 means separation 

```{r}

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
```

S6 ANOVA

```{r}

file <- df_Hvst %>% 
filter(SowTreat =="S6") 
summary (file)  


#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#To get means select the factor : SowTreat or Cultivar
my.anova <- aov(DAS ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)


```

S6 means separation 

```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )


```

S7 Anova

```{r}

file <- df_Hvst %>% 
filter(SowTreat =="S7") 
summary (file)  


#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#To get means select the factor : SowTreat or Cultivar
my.anova <- aov(DAS ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)


```

S7 mean separation 

```{r}

#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )

```




