---
title: "MetFileAnalysis Lincoln"
author: "edmar.teixeira@me.com"
date: "18 August 2018"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

## Reads met files from apsim (based on MapOutApsimFiles.R)
## Creates a dataframe with column row

```{r Libs, echo = FALSE, include=FALSE}
library(data.table)
library(dplyr)
library(ggplot2)
library(gridExtra)
library(knitr)

```

## The weather file

> That's how the data looks like

C:\GitHubRepos\SubcloverPhD\SubClover\LincolnWeather Lincoln1934

```{r DirSet, echo=FALSE}

#Set paths
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\LincolnWeather")

# Get file
#metFile <- read.table(paste0("LawnRoad.met"), skip = 5, header = TRUE, comment.char = "(", blank.lines.skip = TRUE)
#metFile <- read.table(paste0("Lincoln1934"), skip = 5, header = TRUE, comment.char = "(", blank.lines.skip = TRUE)
metFile <- read.table(paste0("HB1934"), skip = 5, header = TRUE, comment.char = "(", blank.lines.skip = TRUE)

head(metFile)
tail(metFile)
summary(metFile)
```


```{r}
str(metFile)


#write.table(metFile, "HBayWeather.txt")

```



# Graph historical averages

> Daily temperaure and radiation

> Monthly rainfall

> Pooled for 30 years

```{r GraphMet, echo = FALSE}


metFile <- data.table(metFile)
#metFile <- data.frame(metFile)

fontSize <- 9.0

#mint
g1 <- metFile %>%
  filter(year %in% 1960:2000) %>%
  group_by(day) %>%
 #summarise_each(funs(mean)) %>%
  ggplot(aes(x=day, y=mint))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
 xlab("Day of the year (1-365)") + 
  ylab("Daily minimum temperature (oC)") +
  theme(text = element_text(size=fontSize))

# maxt
g2 <- metFile %>%
  filter(year %in% 1960:2000) %>%
  group_by(day) %>%
 #summarise_each(funs(mean)) %>%
  ggplot(aes(x=day, y=maxt))  +
  geom_point(colour= "red", alpha=0.2) +
  stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
 xlab("Day of the year (1-365)") + 
  ylab("Daily maximum temperature (oC)") +
  theme(text = element_text(size=fontSize))


#radn
g3 <- metFile %>%
  filter(year %in% 1960:2000) %>%
  group_by(day) %>%
 # summarise_each(funs(mean)) %>%
  ggplot(aes(x=day, y=radn))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  stat_smooth(level = 0.9, size = 1, colour="white") + 
 theme_bw() +
  xlab("Day of the year (1-365)") + 
 # ylab("Daily solar radiation (MJ/m2)" ) +
   ylab(expression(Daily~solar~radiation~~"(MJ "*m^"-2"*")")) +
  theme(text = element_text(size=fontSize))

# rain
#http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/

metFile$month <- with(metFile, strptime(paste(year, day), format="%Y %j")$mon+1)

g4 <- metFile %>%
  filter(year %in% 1960:2000) %>%
  group_by(year, month) %>%
  summarise_each(funs(sum)) %>%
  group_by(month) %>%
  select(month, rain) %>%
  summarise(rainMean = mean(rain), rainSd = sd(rain)/2) %>%
  ggplot(aes(x=month, y=rainMean)) + 
  #geom_bar(stat ='identity') +
  geom_bar(stat="identity", fill="#0072B2", colour="black")+
  theme_bw() +
 xlab("Month") + 
  ylab("Monthly rainfall (mm)") +
  scale_x_continuous(breaks=1:12) +
  geom_errorbar(aes(ymax = rainMean + rainSd, ymin=rainMean - rainSd), 
                position=position_dodge(width=0.9), width=0.25)+
  theme(text = element_text(size=fontSize))


grid.arrange(g1, g2, g3, g4)
# Save
# ggsave(file="Fig_weather.tiff", dpi = 300)


```

make graph as means and exclude daily radiation 



```{r GraphMet, echo = FALSE}

metFile <- data.table(metFile)

fontSize <- 9.0

#mint
g1 <- metFile %>%
  filter(year %in% 1960:2000) %>%
  group_by(day) %>%
 summarise_all(funs(mean)) %>%
  ggplot(aes(x=day, y=mint))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
 xlab("Day of the year (1-365)") + 
  ylab("Daily minimum temperature (oC)") +
  theme(text = element_text(size=fontSize))
ggsave("plot_MinHistoricWeather.png", width=10, height=5, dpi=400)
# maxt
g2 <- metFile %>%
  filter(year %in% 1960:2000) %>%
  group_by(day) %>%
 summarise_all(funs(mean)) %>%
  ggplot(aes(x=day, y=maxt))  +
  geom_point(colour= "red", alpha=0.2) +
  stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
 xlab("Day of the year (1-365)") + 
  ylab("Daily maximum temperature (oC)") +
  theme(text = element_text(size=fontSize))

ggsave("plot_mAXHistoricWeather.png", width=10, height=5, dpi=400)

#radn
g3 <- metFile %>%
  filter(year %in% 1960:2000) %>%
  group_by(day) %>%
 # summarise_each(funs(mean)) %>%
  ggplot(aes(x=day, y=radn))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  stat_smooth(level = 0.9, size = 1, colour="white") +
 theme_bw() +
  xlab("Day of the year (1-365)") +
 # ylab("Daily solar radiation (MJ/m2)" ) +
   ylab(expression(Daily~solar~radiation~~"(MJ "*m^"-2"*")")) +
  theme(text = element_text(size=fontSize))

# rain
#http://www.cookbook-r.com/Graphs/Colors_(ggplot2)/

metFile$month <- with(metFile, strptime(paste(year, day), format="%Y %j")$mon+1)

g4 <- metFile %>%
  filter(year %in% 1960:2000) %>%
  mutate (month= factor(month, levels=c("1", "2", "3", "4", "5","6","7","8","9","10","11","12"),labels=c("Jan","Feb", "Mar",  "Ap", "May","Jun", "Jul", "Aug", "Sept","Oct", "Nov", "Dec")))%>%
  group_by(year, month) %>%
  summarise_all(funs(sum)) %>%
  group_by(month) %>%
  select(month, rain) %>%
  summarise(rainMean = mean(rain), rainSd = sd(rain)/2) %>%
  ggplot(aes(x=month , y=rainMean)) + 
  #geom_bar(stat ='identity') +
  geom_bar(stat="identity", fill="#0072B2", colour="black")+
  theme_bw() +
  #scale_x_discrete(labels=month.abb) +
 xlab("Month") + 
  ylab("Monthly rainfall (mm)") +
  #scale_x_continuous(breaks=1:12) +
    geom_errorbar(aes(ymax = rainMean + rainSd, ymin=rainMean - rainSd), 
                position=position_dodge(width=0.9), width=0.25)+
  theme(text = element_text(size=14))+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 12))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 12))


grid.arrange(g1, g2, g3, g4)
#grid.arrange(g1, g2, g4)
# Save
#ggsave(file="Fig_HistoricWeather.tiff", dpi = 400)
ggsave("plot_RainHistoricWeather.png", width=10, height=5, dpi=400)

```

```{r, fig.height=5, fig.width=10}

#combine Min and Max temps 

metfilegather<-metFile%>%
  group_by(day) %>%
 summarise_all(funs(mean)) %>%
 gather(key= "Temperature" , value = "Degrees", maxt,mint)

metfilegather%>%
  #filter(year %in% 1960:2000) %>%
  #group_by(day) %>%
 #summarise_all(funs(mean)) %>%
  ggplot(aes(x=day, y=Degrees))  +
  #geom_point(aes(colour= Temperature,shape=Temperature), alpha=0.2, size =5 ) +
  geom_point(aes(colour= Temperature,shape=Temperature), alpha=0.2, size =5 ) +
  scale_fill_manual(name="Temperature",
        values=c(maxt="#008B00", mint="salmon4"))+
  #geom_smooth(aes(colour=Temperature))+ 
  #geom_smooth()+ 
  
  theme_bw() +
 xlab("Day of the year (1-365)") + 
    ylab(expression(Mean~Daily~Temperature~"("^"o"*"C)"))+
  theme(text = element_text(size=18))+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 14))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 14))
 
 

#ggsave("plot_MinMaxTemp_Historic.png", width=10, height=5, dpi=400)

```

Graph simple black and white 



```{r, fig.height=5, fig.width=10}

#combine Min and Max temps 

metfilegather<-metFile%>%
  group_by(day) %>%
 summarise_all(funs(mean)) %>%
 gather(key= "Temperature" , value = "Degrees", maxt,mint)

metfilegather%>%
  #filter(year %in% 1960:2000) %>%
  #group_by(day) %>%
 #summarise_all(funs(mean)) %>%
  ggplot(aes(x=day, y=Degrees))  +
  #geom_point(aes(colour= Temperature,shape=Temperature), alpha=0.2, size =5 ) +
  geom_point(aes(shape=Temperature), alpha=0.2, size =5 ) +
 # geom_point(aes(colour= Temperature,shape=Temperature), alpha=0.2, size =5 ) +
  #scale_fill_manual(name="Temperature",
        #values=c(maxt="lightgray", mint="black"))+
        #values=c(maxt="#008B00", mint="salmon4"))+
  #geom_smooth(aes(colour=Temperature))+ 
  #geom_smooth()+ 
  
  theme_bw() +
 xlab("Day of the year (1-365)") + 
    ylab(expression(Mean~Daily~Temperature~"("^"o"*"C)"))+
  theme(text = element_text(size=18))+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 14))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 14))+
  
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   
  #label sizes 
theme(text = element_text(size = 22))
 
 

ggsave("plot_MinMaxTemp_Historic_BlackWhite.png", width=10, height=5, dpi=400)

```



```{r,fig.height=5, fig.width=10}


metFile %>%
  filter(year %in% 1960:2000) %>%
  group_by(year, month) %>%
  summarise_each(funs(sum)) %>%
  group_by(month) %>%
  select(month, rain) %>%
  summarise(rainMean = mean(rain), rainSd = sd(rain)/2) %>%
  ggplot(aes(x=month, y=rainMean)) + 
  #geom_bar(stat ='identity') +
  geom_bar(stat="identity", fill="lightgrey", colour="black")+
  theme_bw() +
 xlab("Month") + 
  ylab("Monthly rainfall (mm)") +
  scale_x_continuous(breaks=1:12) +
  geom_errorbar(aes(ymax = rainMean + rainSd, ymin=rainMean - rainSd), 
                position=position_dodge(width=0.9), width=0.25)+
  theme(text = element_text(size=fontSize))+

#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   
  #label sizes 
theme(text = element_text(size = 22))


ggsave("plot_Rainfall_Historic_BlackWhite.png", width=10, height=5, dpi=400)


```


bring PET data monthly 


```{r}

# Get file
Petfile <- read.table(paste0("MeanHistoricPet.txt"),  header = TRUE)

Petfile<-Petfile%>%
  mutate(month=as.numeric(month),
         HistoricPET=as.numeric(HistoricPET))


```

build mean rain per month

```{r}

Rain <-metFile %>%
  filter(year %in% 1960:2000) %>%
  group_by(year, month) %>%
  summarise_all(funs(sum)) %>%
  group_by(month) %>%
  select(month, rain) %>%
  summarise(rainMean = mean(rain), rainSd = sd(rain)/2) 


str(Rain)
str(Petfile)
## merge

RainPet <- merge(Rain, Petfile,  by="month")

```

build multiple graph



```{r,fig.height=5, fig.width=10}

str(RainPet)

 RainPet%>%
   #mutate(month=as.factor(month))%>%
  #mutate (month= factor(month, levels=c("1", "2", "3", "4", "5","6","7","8","9","10","11","12"),labels=c("Jan","Feb", "Mar",  "Ap", "May","Jun", "Jul", "Aug", "Sept","Oct", "Nov", "Dec")))%>%
  ggplot(aes(x=month, y=rainMean))+ 
  #geom_bar(stat ='identity') +
  geom_bar(stat="identity", fill="lightgrey", colour="black")+
 # geom_bar(aes(x=month, y=rainMean),stat="identity", fill="tan1", colour="sienna3")+
  geom_line(aes(x=month, y=HistoricPET,stat="identity"),linetype=2)+
   geom_point(aes(x=month, y=HistoricPET,stat="identity"),size=6)+
  
 theme_bw() +
 xlab("Month") + 
  ylab("Monthly rainfall and PET (mm)") +
  scale_x_continuous(breaks=1:12) +
   #scale_y_continuous()+
  geom_errorbar(aes(ymax = rainMean + rainSd, ymin=rainMean - rainSd), 
                position=position_dodge(width=0.9), width=0.25)+
  theme(text = element_text(size=fontSize))+

#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   
  #label sizes 
theme(text = element_text(size = 22))


ggsave("plot_PETRain_Historic_BlackWhite.png", width=10, height=5, dpi=400)


```





```{r PotEvap_graph}

# # Get file (simulated eo by APSIM - Pot ET for modsim paper)
# theFile <- "C:\\Apsim_dev\\Projects\\Forage_MBIE(FRNL)\\ModelStudies\\05_CoverCropPaperSoils\\LightSoil EarlyCover ETPdaily.out"
# 
# etpFile <- read.table(theFile, skip = 3, header = TRUE, comment.char = "(", blank.lines.skip = TRUE)
# head(etpFile)
# tail(etpFile)
# summary(etpFile)
# 
# 
# #etpFile$Date <- as.Date(etpFile$Dat, format="%dd-%mm-%YYYY")
# 
# #etpFile$day <- yday(etpFile$Date)
# 
# #write.csv(etpFile, file = "test.csv")
# 
# summary(etpFile)
# 
# g5 <- etpFile %>%
#   filter(year %in% 1960:2000) %>%
#    group_by(day_of_year) %>%
#  # summarise_each(funs(mean)) %>%
#   ggplot(aes(x=day_of_year, y=eo))  +
#   geom_point(colour= "darkblue", alpha=0.2) +
#   stat_smooth(level = 0.9, size = 1, colour="white") + 
#   xlab("Day of the year (1-365)") + 
#   ylab("Potential evapo-transpiration (mm)") +
#   theme(text = element_text(size=fontSize))
# 
# 
# g5 <- etpFile %>%
#   filter(year %in% 1960:2000) %>%
#   group_by(year, month) %>%
#   summarise_each(funs(sum)) %>%
#   group_by(month) %>%
#   select(month, eo) %>%
#   summarise(rainMean = mean(eo), rainSd = sd(eo)/2) %>%
#   ggplot(aes(x=month, y=rainMean)) + 
#   geom_bar(stat ='identity') +
#   xlab("Month") + 
#   ylab("Potential evapo-transpiration (mm)") +
#   scale_x_continuous(breaks=1:12) +
#   geom_errorbar(aes(ymax = rainMean + rainSd, ymin=rainMean - rainSd), 
#                 position=position_dodge(width=0.9), width=0.25)+
#   theme(text = element_text(size=fontSize))
# 
# grid.arrange(g1, g3, g4, g5)

```


