---
title: "Trifoliates Iversen "
author: "CT"
date: "17.08.2017"
output: html_document
---

Purpose:

-Analysis of trifoliates expansion for Iversen from previous script (use number Trifo)
- Calculate the time to reach 1 number of leaves
- Calculate rate of leaf appearance (1/Days) 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
```



```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FirstTrifo")
getwd()
#create file
df_trif <- read.table("Number_Trifo.txt",header=TRUE)
str(df_trif)


```


Define formats 

```{r loadFile}


# define factors for the ones that "look like" values

df_trif <- df_trif %>%
  mutate(SowingDate = ymd(SowingDate), 
         ReadingDate = ymd(ReadingDate),
         DAS = as.numeric(DAS))


df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Cultivar <- as.factor(df_trif$Cultivar)
df_trif$SowTreat <- as.factor(df_trif$SowTreat)

 
         

str(df_trif)


```

Calculate the 50 percent of leaves  based on maximum number of leaves attained 
Change name of column TrifoNumber for PercentTrifo to keep stable code. Multiplication by 10 to equal to 50 value. 

```{r}
#change name of column TrifoNumber for PercentTrifo

df_trif <-df_trif %>%
  mutate(PercentTrifo= 1 *(TrifoNumber))

str(df_trif)
```


```{r, fig.height=5, fig.width=10}



# head(df_50_Perc)


df_50_Perc <- df_trif %>%
mutate(av_Perc=PercentTrifo)%>%
mutate(av_DAS=DAS)


str(df_50_Perc)
# summary(df_50_Perc)
# head(df_50_Perc)


```

Loop, apply function approx and try catch to get DAS to 50% 
```{r}


plots <- unique(df_50_Perc$Plot)
 

# create empty df
# df_tt_50p_emerg <- data.frame(Plot = NULL,
#                               Block = NULL,
#                              SowingD = NULL,
#                              Cultivar = NULL, 
#                              SowTreat = NULL,
#                              PercEmerg = NULL, 
#                              TT50Em = NULL)

#loop trough each combination of factor levels

for(p in 1:length(plots)) {
#  for(j in 1:length(var)){
 #   for(k in 1:length(sow)){
      
      # clean value holders
      DAS_50p_emerg <- 0
      #tt_50p_emerg <- 0
      
      #FIX ME Partially set 
    
     # print(paste0(cv[i]," ",var[j]," ", sow[k]))
      # filter for each combination

  df_sub <- df_50_Perc %>%
    # subset(Cultivar == as.character(cv[i]) &
    # Plot == as.character(var[j]) &
    #   Block == as.character(var[b]) &
    # SowTreat == as.character(sow[k])) %>%
    subset(Plot == plots[p]) %>%
    arrange(PercentTrifo)
  
  df_sub
  head(df_sub)
  # create percentage with maximum value recorded 
  # to avoid crossing the 50% line twice
  
  #No need to do maximum values here as the entire numbers are needed trifoliate 1.
  # df_sub$av_Perc_max <- 0 # create new col
  # 
  # for(z in 1:nrow(df_sub)) {
  #   
  #   df_sub$av_Perc_max[z] <- max(df_sub$av_Perc[z],
  #                                df_sub$av_Perc_max[z-1])
  #   
  # }
  
  df_sub
  head(df_sub)
  tail(df_sub)

  # Interpolate 
  y_ref <- 1 # y value where we want to find x by interpolation > First trifoliate 
  
  # interpolate
  #find DAS at 50 Pecent Emergence 

  tryCatch(  
  DAS_50p_emerg <- approx(df_sub$PercentTrifo, 
  df_sub$av_DAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  DAS_50p_emerg <- NA
  }
)
  #find TT at 50 Pecent Emergence
#   tryCatch(  
#   tt_50p_emerg <- approx(df_sub$av_Perc, 
#   df_sub$av_TT , xout = y_ref, rule = 1)$y,
#   error = function(e) 
#   {
#   tt_50p_emerg <- NA
#   }
# )

  df_temp <- NULL 
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             PercEmerg = df_sub$PercentTrifo[1], 
                             SowTreat = df_sub$SowTreat[1],
                             Plot = df_sub$Plot[1],
                             Block = df_sub$Block[1],
                             DAS50E = DAS_50p_emerg)
                             #TT50E = tt_50p_emerg)
  print(p)
  
  if(p == 1) {
    df_tt_50p_emerg <- df_temp
  } else {
   df_tt_50p_emerg <- rbind(df_tt_50p_emerg,df_temp) 
  }                     
  
#    } 
  } # end plot loop


head(df_tt_50p_emerg)



summary(df_tt_50p_emerg)



```

Include dates of sowing again in dataframe 
```{r}
sdLookup <- data.frame (
  SowTreat = c("S1","S2","S3","S4","S5","S6","S7","S8"),
  SowingDate = c("24/06/2015", 
                 "28/07/2015" ,
                 "15/09/2015" ,
                 "5/11/2015" ,
                 "15/12/2015" ,
                 "17/02/2016" ,
                 "15/03/2016",
                 "4/05/2016"))

sdLookup$SowingDate <- dmy(sdLookup$SowingDate)

df_tt_50p_emerg <- merge(df_tt_50p_emerg, sdLookup, by="SowTreat")
summary(df_tt_50p_emerg)


```
Now correct column names after loop not to mix with other generated tables

```{r}

df_1T<-df_tt_50p_emerg%>%
  mutate(DAS1T=as.numeric(DAS50E))%>%
  dplyr::select(-PercEmerg)

str(df_1T)
 


```



Now need to discount the DAS to 50 % emergence to get values of first trifoliate after emergence! 

Bring dataframe from emergence folder which contains the number of days to emergence 

```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FirstTrifo")
getwd()
#create file

df_Emergence <- read.table("df_RateEmerg.txt",header=TRUE)
str(df_Emergence)

###create a column which is date to 50%Emergence \
df_Emergence1 <-df_Emergence %>%
  dplyr::select(Plot,SowingDate,DAS50E)%>%
   mutate(SowingDate = ymd(SowingDate))%>%
   mutate(Date50Emergence= as.Date(SowingDate+ DAS50E))
 
```

Merge the dataframes to have dates and days to first trifoliate after sowing and emergence 
Calculate the days to first trifoliate after emergence 

```{r}

str(df_Emergence1)
str(df_1T)

df_1Ta<-df_1T%>%
  dplyr::select(SowTreat:Block,DAS1T)


df_Trifomerged <- merge(df_Emergence1, df_1Ta, by="Plot")
summary(df_Trifomerged)

##Calculate time to first trifoliate after emergence: subtract DAS1T - DAS50E  
TfromEmerg_Trifo1 <-df_Trifomerged%>%
  mutate(DASfromEmerg= (DAS1T -DAS50E))
  
  
  
#write.table(df_1T,"df_DAS_1_Trifo.txt")

```

Check the mean values for each sowing date !! 


```{r}

str(TfromEmerg_Trifo1)

Mean_TfromEmerg<-TfromEmerg_Trifo1 %>%
 
 # group_by(Cultivar, SowTreat)%>%
   group_by(SowTreat)%>%
  dplyr::select(DASfromEmerg)%>%
  summarise_all(funs(mean,sd))%>%
  mutate(SE=sd/1.73)

```








Calculate RAte (1/days to 50%) 


```{r}

#try 1/DAS50% = Rate

df_RateFirstTrifo <- df_1T %>%
  mutate(Rate=1/DAS1T)

  summary(df_RateFirstTrifo)
  
  write.table(df_RateFirstTrifo,"RateFirstTrifo.txt")

```



Graph rate and SowTreat

```{r}
#Graph 

  df_RateFirstTrifo %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(DAS50E) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 5 trifoliates  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

df_RateFirstTrifo %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to first  trifoliate ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

```




End of this script Calc 3. 

Move to script 4 to include temperatures  
