---
title: "Trifoliates Iversen "
author: "CT"
date: "17.08.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

This script does this:

- get the dataframe with sowing dates and date to 50% first trifo   
- get the dataframe with soil temperature 
- merge the two dataframes to calculate the mean temperature during first trifo appearance 
-graph y=Days to 50% first trifo ; x= mean Soil Temp
-graph y= 1/days to 50% emergence ; x= mean Soil Temp   
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```

Get data from Emergence Folder, Daily Mean Air temperature and dates to combine in dataframe 


```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FirstTrifo")
getwd()
#create file

#use this for Days after sowing: 

df_trif <- read.table("RateFirstTrifo.txt",header=TRUE)
#use this for Days after emergence if need :

#df_trif <- read.table("RateFirstTrifoFromEmer.txt",header=TRUE)


#adjust formats 
df_trif$SowingDate <- ymd(df_trif$SowingDate )
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$DAS1T <- as.numeric(df_trif$DAS1T)

```

Create df_MD to workout dates to % trifoliates 
```{r}

str(df_trif)

  df_MD <- df_trif %>%
  select(-DAS50E)%>%
  mutate(Date50FirstTrif=SowingDate+DAS1T) %>%
  group_by(Plot, DAS1T) %>% 
  dplyr::filter(row_number() == 1)

head(df_MD)

H <-df_MD %>%
 dplyr:: select (Plot, Date50FirstTrif)

#save and store table 
write.table(H, "DateToFirstTrifo.txt")

```

Read the soil Temp data and Air temp data and  adjust formats 

```{r}

#create file
df_A <- read.table("AirTemp.txt",header=TRUE)
df_Soil <-read.table("SoilTemp.txt",header=TRUE)

#adjust formats
df_A %>%
  mutate(Date=dmy(Date))

str(df_A)

#adjust formats
df_Soil <- df_Soil%>%
mutate(Date=dmy(Date))


```

Add the accumulation of of soil temperatures to calculate the average temperature during emergence. 

```{r}
#cumulate air
df_B <- df_A %>%
  mutate(SumAir = cumsum(AirTt)) %>%
  mutate(Date=dmy(Date))%>%
  dplyr::select(-AirTt)

#cumulate soil

df_Soil1 <- df_Soil %>%
  mutate(SumTempSo = cumsum(TempSoil10mm)) %>%
  #mutate(Date=dmy(Date))%>%
  dplyr::select(-TempSoil10mm)


```

check data with graph

```{r}
df_Soil1 %>%
  ggplot(aes(x=Date,y=SumTempSo)) +
  geom_point()

df_B%>%
  ggplot(aes(x=Date,y=SumAir)) +
  geom_point()

```


Merge dataframes by date

```{r}

# first merge the soil and air temperature dataframes 

df_Temp <- merge(df_Soil1,df_B,by="Date") 


#Merge the two dataframes by Date
df1 <- merge(df_MD,df_Temp, by.x="SowingDate",by.y="Date") %>%
  mutate(soilTempAcc_sow = SumTempSo) %>%
  mutate(airTempAcc_sow=SumAir)%>%
  dplyr::select(-SumTempSo,-SumAir)

str(df1)



```

Need to force a date for 50 % of plants with first trifo  (round) to calculate the average temperature during first trifo emergence

Save dataframe as txt file


```{r}


# force formats of dates
df1$Date <- round(df1$Date50FirstTrif,0)
df_Temp$Date <- round(df_Temp$Date,0)

#then repeat same procedure done for the soing date but use the dat for 1 Trifoliate
  df_merge <- merge(df1, df_Temp, by="Date") %>%
  mutate(soilTempAcc_1T = SumTempSo) %>%
  mutate(airTempAcc_1T=SumAir)%>%
  dplyr::select(-SumTempSo, -SumAir) %>%
 
     #subtract accumulate temperature das1T from sowing 
  mutate(meanTempSoil_1T = (soilTempAcc_1T-soilTempAcc_sow)/DAS1T ) %>% 
  mutate(meanTempAir_1T = (airTempAcc_1T-airTempAcc_sow)/DAS1T )
  summary(df_merge)

write.table(df_merge, "df_MeanTempFirstTrifo.txt") 

```


get the TT and SE for all cultivars. exclude S1 . Consider Tb=0 for all cultivars. 

```{r}

df_TT1T <- df_merge%>%
  mutate(TTto1TSoil=soilTempAcc_1T -soilTempAcc_sow)%>%
  mutate(TTto1TAir=airTempAcc_1T -airTempAcc_sow)

#then select sow treat and means and se

df_TTAllcv <-df_TT1T%>%
  filter(SowTreat!= "S1")%>% 
  #group_by(Cultivar) %>%
  group_by(SowTreat)%>%
  dplyr::select(TTto1TSoil)%>%
#dplyr::select(TTto1TAir)
  summarise_all(funs(mean,sd))%>%
    mutate(SE=sd/1.73)

```


Graph results 




Then graph results  (remember that here each replicate has a different temperature set... need to average to get a simpler graph 
## complete graph 
```{r, fig.height=5, fig.width=8}
dGraph <-df_merge %>%
  group_by(SowTreat, Cultivar) %>%
  dplyr::select(Rate,meanTempSoil_1T) %>%
  summarise_all(funs(mean,sd)) 




```



```{r}

dGraph%>%
  #Graph
  #ggplot(aes(x=MeanAirTempTrifo, y=mean, colour=(Cultivar), shape=factor(Cultivar) )) +
 ggplot(aes(x=meanTempSoil_1T_mean, y=Rate_mean,colour=SowTreat, shape=Cultivar)) +
  geom_point(size=5) +
  #geom_line() +
  
  labs(y="Rate to first trifoliate stage (1/days)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=Rate_mean-Rate_sd/2,
  ymax=Rate_mean+Rate_sd/2))+
  theme_bw()+
  xlim(0,25)+
  ylim(0,0.08)+
  #facet_wrap(~Cultivar,ncol=3, scales = "free")+
  xlab(expression(Mean~Soil~Temperature~"("^"o"*"C)"))+
  theme(axis.text.x=element_text(angle = 0, hjust = 0, size= 12))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 12))+
  theme(axis.title.y=element_text(angle = 90, hjust = 0, size= 14))+
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 14))+
  theme(legend.text=element_text(size=12))
  


```



Graph rate and SowTreat

```{r}
#Graph 

  df_merge %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(DAS1T) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y=" Days to 50% first Trifo emergence  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

```



End of this script . 
Move to script 5.  and graph soil and air temperature 
