---
title: 'First Trifoliates Iversen '
author: "CT"
date: "17.02.2018"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

Purpose:

This script does this:

- get the dataframe with DAS and TT from sowing and from emergence from script 6 (merged data frame)   
 
- runs the ANOVA for  DAS and TTFirstTrifo from emergence 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
#library(mosaic)
library(lattice)
library(knitr)
```

Get data from Frist Trifo folder  


```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FirstTrifo")
getwd()
#create file

df_trif <- read.table("DaysTT1TFromEmergence.txt",header=TRUE)

str(df_trif)
```

Create df_MD to workout dates to % trifoliates 
```{r}
#adjust formats 
#df_trif$SowingDate <- ymd(df_trif$SowingDate )
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$DAS1T <- as.numeric(df_trif$DAS1T)
  

```


Then next step is to "clean" the dataframe to run ANOVA 

```{r}

df <- df_trif %>%
  dplyr::select(Plot:Block, DAS1TFromEmerg,TT1TFromEmerg)


```


  
Then ready for ANOVA ! 

## Here run ANOVA overview 


```{r}

file.subset <- df 
  #filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
#my.anova <- aov( DAS1TFromEmerg ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(  TT1TFromEmerg ~ Cultivar*SowTreat , data = file.subset)


summary(my.anova)
  
  
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
 
```



## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(df$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```

# Then loop anova for each individual sowing date using :DAS1TFromEmerg

```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov( DAS1TFromEmerg ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```

## Here run ANOVA overview 


```{r}

file.subset <- df 
  #filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
#my.anova <- aov( DAS1TFromEmerg ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(  TT1TFromEmerg ~ Cultivar*SowTreat , data = file.subset)


summary(my.anova)
  
  
  
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none")) 
```


##Now Lopp again with the other variable  : Thermal time TT1TFromEmerg 



```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov( TT1TFromEmerg ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```


## Here run ANOVA overview 


```{r}

file.subset <- df 
  #filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov( TT1TFromEmerg ~ Cultivar*SowTreat + Block, data = file.subset)

summary(my.anova)
  
  
  
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none")) 
```

End of this script . 
