---
title: "Trifoliates GC"
author: "CT"
date: "31.08.2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Analysis of trifoliates expansion for rowth Cabinet  with focus on first Trifoliate 
- Graph the main dataset 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
```



```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GC_TrifoCounts")
getwd()
#create file
df_trifo <- read.table("GCTrifoCountall.txt",header=TRUE)
head(df_trifo)


```
Define formats and calculate the mean number of trifoliates considering the sub samples (S1-S10)

```{r loadFile}


# define factors for the ones that "look like" values
df_trifo$Plot <- as.factor(df_trifo$Plot)
df_trifo$Block <- as.factor(df_trifo$Block)
df_trifo$Cultivar <- as.factor(df_trifo$Cultivar)
#df_trifo$SowTreat <- as.factor(df_trifo$SowTreat)

 df_trifo <- df_trifo %>%
  mutate(SowingDate = dmy(SowingDate), 
         ReadingDate = dmy(ReadingDate),
         Trifo = (S1+S2)/2)

str(df_trifo)
head(df_trifo)
tail(df_trifo)


df_trifo %>% filter(Plot ==1) %>% summary()



```

Graph the results : DAS and number of trifoliates 

```{r, fig.height=8, fig.width=15}
#Graph         
  df_trifo %>%
  #mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),labels=c("June", "July", "September", "November", "December", "February","March", "May")))%>%
  group_by(Cultivar, DAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=Trifo)) + 
  geom_point(aes(colour=Cultivar, shape=Cultivar), size=4) +
  geom_line(aes(colour=Cultivar)) +
  #facet_wrap(~SowTreat,ncol=4, scales = "free") +
  #facet_wrap (~SowTreat,ncol=4)+
  ylim(0,16)+
  labs(y="Number of trifoliates",x="Days after sowing")+
 # theme_grey(base_size = 16) +
  theme_bw()+
  geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 5,  slope = 0, linetype=2)+
   geom_abline(intercept = 10,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
theme(text = element_text(size = 20))


```

Other graphics with same data 
```{r, fig.height=5, fig.width=8}
#Graph         
  df_trifo %>%  
  #mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),labels=c("June", "July", "September", #"November", "December", "February","March", "May")))%>%
  group_by(Cultivar,DAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=Trifo)) + 
  geom_point(aes(colour=Cultivar, shape=Cultivar)) +
  geom_line(aes(colour=Cultivar)) +
  #facet_grid (SowTreat~., scales = "free")+
  labs(y="Number of trifoliates",x="Days after sowing")+
    #geom_abline(intercept = 6, slope = 0)
   geom_abline(intercept = 4:6, slope = 0)



```

Graph the results : DAS and number of trifoliates 

```{r, fig.height=8, fig.width=15}
#Graph 1        
  df_trifo %>%
  #mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),labels=c("June", "July", "September", "November", "December", "February","March", "May")))%>%
  #filter(Cultivar=="Antas"|Cultivar=="Denmark"|Cultivar=="Leura")%>%
  group_by(Cultivar,  DAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=Trifo)) + 
  #geom_point(aes(colour=Cultivar, shape=Cultivar), size=4) +
  geom_point(aes(shape=Cultivar), size=5) +
  #scale_shape_manual(values = c(0,1,2, 3,4,5,6,7,8,9,10,11))+
  scale_shape_manual(values = c(1,2,7)) +
  #geom_line(aes(colour=Cultivar)) +
  #geom_line()+
  #facet_wrap(~SowTreat,ncol=4, scales = "free") +
  #facet_wrap (~SowTreat,ncol=4)+
  ylim(0,16)+
  labs(y="Number of trifoliate leaves (n)",x="Days after sowing")+
  #theme_grey(base_size = 16) +
  theme_bw(base_size = 24)+
  
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
    geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 5,  slope = 0, linetype=2)+
   geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
theme(text = element_text(size = 24))


#save
   
   #ggsave("plot_NumberOfTrifoliateLeavesA.png", width=16, height=8, dpi=400)




```


get the standard  error values for the final trifoliate numbers 


```{r}

#Data check 

str(df_trifo)

#select the variable and find mean and sd
##for this experiment there were 4 replicates therefore SE=sd/2
dfMeanTrifo <- df_trifo %>% 
  #filter(DAS== "27")%>% # select the last DAS when all cultivars had available data !! 
  subset (DAS>0 & DAS<28)%>%
group_by(Cultivar,DAS) %>%
  dplyr::select(Trifo)%>%
  summarise_all(funs(mean,sd)) %>%
  mutate(SE=sd/2)
 

```

Improve graphics 


```{r , fig.height=5, fig.width=10}

 
#to graph with SE max

#then create the error bar position
#Here how to create the end error bar with max Sd 
# find size of bar per cultivar and temp
# find single position of x y to put the bar

#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.2 # extra position for single error bar
x_max<-max(dfMeanTrifo$DAS)
y_max<-max(dfMeanTrifo$mean)

## find largest standard error
sd_df1 <- dfMeanTrifo %>% 
  group_by(Cultivar) %>%
  dplyr:: select(sd)%>%
  summarise_all(funs(max))%>%
  ungroup() %>%
  rowwise() %>%
  mutate(DAS= x_max*extraPos, mean = y_max*extraPos, max_sd=sd)

summary(sd_df1)

#make a graph 
#then graph and remember to divide the sd /2 because of the 4 replicates 


dfMeanTrifo %>% 
  #select( Variable, Cultivar, Temp, mean,sd) %>%
  ggplot(aes(x=DAS, y=mean)) + 
#  geom_point(data=sd_df,aes(x=DAS,y=NumberRun_mean)) +
  geom_point(aes(shape=Cultivar), size=6) +
  scale_shape_manual(values = c(1,2,7)) +
  geom_errorbar(data=sd_df1, aes(ymin=mean-max_sd/2,
                    ymax=mean+max_sd/2), width=4,size=1.5)+
  facet_wrap (~Cultivar,ncol=3)+
  ylim(0,20) +
  xlim(0,40)+
  ylab(expression(Number~of~trifoliate~leaves~"(n)"))+
  #xlab(expression(Temperature~"("^"o"*"C)"))+
  #xlab(expression(Days~after~sowing"()"))+
  labs(x="Days after sowing")+
  theme_grey(base_size = 22) +
  theme_bw()+
  geom_abline(intercept = 1, slope = 0, linetype=2)+
  geom_abline(intercept = 5,  slope = 0, linetype=2)+
  geom_abline(intercept = 9,  slope = 0, linetype=2)+
   theme(axis.text.x=element_text(angle = 0, hjust = 0.5))+
  #remove grid lines 
    theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
  
theme(text = element_text(size = 24))


ggsave("plot_GC_NumberTrifoliateLeaves.png", width=12, height=6, dpi=400)


```





End of this script Calc 1. 
Move to script 2 to calculate percent and rate of leaf appearance 
