---
title: "Trifoliates GC "
author: "CT"
date: "17.10.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default



---

Purpose:

-Analysis of trifoliates expansion for plants in growth chamber from previous script (use data_file : GC_Number_Trifo.txt)
- Calculate the time to reach selected  number of leaves : here nine Trifoliates 
- Calculate rate of leaf appearance (1/Days) 
-Run ANOVAS perform LSD and Tukeys
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)

```



```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GC_TrifoCounts")
getwd()
#create file
df_trif <- read.table("GC_Number_Trifo.txt",header=TRUE)


str(df_trif)


```


Define formats 

```{r loadFile}


# define factors for the ones that "look like" values

df_trif <- df_trif %>%
  mutate(SowingDate = ymd(SowingDate), 
         ReadingDate = ymd(ReadingDate),
         DAS = as.numeric(DAS))


df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Cultivar <- as.factor(df_trif$Cultivar)
#df_trif$SowTreat <- as.factor(df_trif$SowTreat)

 
         

str(df_trif)


```

Calculate the 50 percent of leaves  based on maximum number of leaves attained 
Change name of column TrifoNumber for PercentTrifo to keep a stable code. Multiplication by 1 to equal to trifo value. 

```{r}
#change name of column TrifoNumber for PercentTrifo

df_trif <-df_trif %>%
  mutate(PercentTrifo= 1 *(TrifoNumber))

str(df_trif)
```


```{r, fig.height=5, fig.width=10}



df_50_Perc <- df_trif %>%
mutate(av_Perc=PercentTrifo)%>%
mutate(av_DAS=DAS)


# 
str(df_50_Perc)
# summary(df_50_Perc)
# head(df_50_Perc)


```

Loop, apply function approx and try catch to get DAS to 50% 

```{r}

#sow <- unique(df_50_Perc$SowTreat)
#sowd <- unique(df_50_Perc$SowingDate)
plots <- unique(df_50_Perc$Plot)
 

# create empty df
# df_tt_50p_emerg <- data.frame(Plot = NULL,
#                               Block = NULL,
#                              SowingD = NULL,
#                              Cultivar = NULL, 
#                              SowTreat = NULL,
#                              PercEmerg = NULL, 
#                              TT50Em = NULL)

#loop trough each combination of factor levels

for(p in 1:length(plots)) {
#  for(j in 1:length(var)){
 #   for(k in 1:length(sow)){
      
      # clean value holders
      DAS_50p_emerg <- 0
      #tt_50p_emerg <- 0
      
      #FIX ME Partially set 
    
     # print(paste0(cv[i]," ",var[j]," ", sow[k]))
      # filter for each combination

  df_sub <- df_50_Perc %>%
    # subset(Cultivar == as.character(cv[i]) &
    # Plot == as.character(var[j]) &
    #   Block == as.character(var[b]) &
    # SowTreat == as.character(sow[k])) %>%
    subset(Plot == plots[p]) %>%
    arrange(PercentTrifo)
  
  df_sub
  head(df_sub)
  # create percentage with maximum value recorded 
  # to avoid crossing the 50% line twice
  
  df_sub$av_Perc_max <- 0 # create new col
  
  for(z in 1:nrow(df_sub)) {
    
    df_sub$av_Perc_max[z] <- max(df_sub$av_Perc[z],
                                 df_sub$av_Perc_max[z-1])
    
  }
  
  df_sub
  head(df_sub)
  tail(df_sub)

  # Interpolate in desired number of leaves: in this case 9
  
 # y_ref <- 1 # y value where we want to find x by interpolation in this case needed 1 trifoliate
  #y_ref <- 5 # y value where we want to find x by interpolation in this case needed 5 trifoliates 
  y_ref <- 9 # y value where we want to find x by interpolation in this case needed 5 trifoliates 
  
  # interpolate
  #find DAS at 50 Pecent Emergence 

  tryCatch(  
  DAS_50p_emerg <- approx(df_sub$PercentTrifo, 
  df_sub$av_DAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  DAS_50p_emerg <- NA
  }
)
  #find TT at 50 Pecent Emergence
#   tryCatch(  
#   tt_50p_emerg <- approx(df_sub$av_Perc, 
#   df_sub$av_TT , xout = y_ref, rule = 1)$y,
#   error = function(e) 
#   {
#   tt_50p_emerg <- NA
#   }
# )

  df_temp <- NULL 
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             PercEmerg = df_sub$PercentTrifo[1], 
                            # SowTreat = df_sub$SowTreat[1],
                             Plot = df_sub$Plot[1],
                             Block = df_sub$Block[1],
                             DAS50E = DAS_50p_emerg)
                             #TT50E = tt_50p_emerg)
  print(p)
  
  if(p == 1) {
    df_tt_50p_emerg <- df_temp
  } else {
   df_tt_50p_emerg <- rbind(df_tt_50p_emerg,df_temp) 
  }                     
  
#    } 
  } # end plot loop


head(df_tt_50p_emerg)



summary(df_tt_50p_emerg)



```



Now correct column names after loop not to mix with other generated tables : First Trifoliate code = 1T

```{r}

#df_5T<-df_tt_50p_emerg%>%
df_9T<-df_tt_50p_emerg%>%
  mutate(DAS9T=as.numeric(DAS50E))%>%
  dplyr::select(-PercEmerg)

str(df_9T)
 


```



```{r}
#if needed 
#write.table(df_1T,"GC_df_DAS_9_Trifo.txt")
```



Calculate RAte (1/days to 50%) 


```{r}

#try 1/DAS50% = Rate

df_RateTrifo <- df_9T %>%
  mutate(Rate=1/DAS9T)

  summary(df_RateTrifo)
  
  #write.table(df_RateTrifo,"GC_9T_RateTrifo.txt")

```


##Add the number of days for 50% emergence to calculate the days to nine trifoliates after emergence (DAE)

##File ready at : GC_DASToEmergence.txt (already calculated the days after emergence for first trifoliate : DAE_1T) but need to calculate for 9 T !!! 



```{r}


setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GC_TrifoCounts")
getwd()
#create file
df_DAE <- read.table("GC_DASToEmergence.txt",header=TRUE)

str(df_DAE)


```

# Prepare and Merge dataframes by plot


```{r}
##first select only columns of interest 

df_DAESelec <-df_DAE %>%
  select(  Pot,  DAS_ToEmerg)%>%
  #change column name as per field experiments
  mutate(Plot=Pot)%>%
  select(-Pot)

str(df_DAESelec)
str(df_9T)

##Merge 

 df_merge <- merge(df_9T, df_DAESelec, by="Plot") %>%
   select(-DAS50E)
 
 str( df_merge )

 #Then calculate the DAE to 5trifoliates 
 
 DAETo9T<-df_merge %>%
   mutate(DAE_9T=as.numeric(DAS9T-DAS_ToEmerg))
 
 str( DAETo9T )  
 

```




Check : Inspect means  before ANOVA

```{r}
#Graph 


 # a <- df_RateTrifo %>%

 b <- DAETo9T  %>%
  group_by( Cultivar) %>%
  dplyr::select(  DAE_9T) %>%
  summarise_all(funs(mean,sd))



```


RUN ANOVA



```{r ANOVAMaxPlantPop}

#compare DAE_1T  among cultivars

df_emerg_perc3 <- DAETo9T %>%
  dplyr::select(Cultivar,Block,Plot,DAE_9T)

```
Overall analysis consider sowing date and cultivar 


```{r}
##Overview  
##need to specify variate :DAE_9T

file <- df_emerg_perc3
file$transf_no <- 1*(df_emerg_perc3$DAE_9T)
head(file)

#-------------------------------------------------
# ANOVA for cultivar 
file.subset <- file 

head(file.subset)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

```


First LSD 

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
```


Perform Tukeys 


This is Tukeys test for mean comparison 

```{r}
posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)
#posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.25)

posthoc

```



Then 
This is the mean separation using Tukey 


```{r}

fogo<-HSD.test(my.anova, 'Cultivar', group=TRUE)
fogo

```




##End of this script. 
##(Use similar code to calculate 5T and 9T)
