---
title: "Trifoliates GC "
author: "CT"
date: "17.10.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Analysis of trifoliates expansion for plants in growth chamber from previous script (use file : GC_Number_Trifo.txt)
- Calculate the thermal  time to reach selected  number of leaves : here first  Trifoliate 
- Calculate rate of leaf appearance (1/Days) 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```



```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GC_TrifoCounts")
getwd()
#create file
df_trif <- read.table("GC_Number_Trifo.txt",header=TRUE)


str(df_trif)


```


Define formats 

```{r loadFile}


# define factors for the ones that "look like" values

df_trif <- df_trif %>%
  mutate(SowingDate = ymd(SowingDate), 
         ReadingDate = ymd(ReadingDate),
         DAS = as.numeric(DAS))


df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Cultivar <- as.factor(df_trif$Cultivar)
#df_trif$SowTreat <- as.factor(df_trif$SowTreat)

 
         

str(df_trif)


```

Calculate the 50 percent of leaves  based on maximum number of leaves attained 
Change name of column TrifoNumber for PercentTrifo to keep a stable code. Multiplication by 1 to equal to trifo value. 

```{r}
#change name of column TrifoNumber for PercentTrifo

df_trif <-df_trif %>%
  mutate(PercentTrifo= 1 *(TrifoNumber))

str(df_trif)
```


```{r, fig.height=5, fig.width=10}


# df_50_Perc <- df_trif %>%
#  group_by(Plot, Block,Cultivar,SowTreat, ReadingDate) %>%
#   #group_by(Plot)%>%
#   summarise(av_Perc = mean(PercentTrifo), 
#             #av_TT = mean(TT_to_emerg),
#             av_DAS = mean(DAS)
#             )
# 
# str(df_50_Perc)
# summary(df_50_Perc)
# head(df_50_Perc)


df_50_Perc <- df_trif %>%
mutate(av_Perc=PercentTrifo)%>%
mutate(av_DAS=DAS)

#group_by(Plot, Block,Cultivar,SowTreat, ReadingDate) %>%
#   #group_by(Plot)%>%
#   summarise(av_Perc = mean(PercentTrifo), 
#             #av_TT = mean(TT_to_emerg),
#             av_DAS = mean(DAS) 
#             )
# 
str(df_50_Perc)
# summary(df_50_Perc)
# head(df_50_Perc)


```

Loop, apply function approx and try catch to get DAS to 50% 

```{r}

#sow <- unique(df_50_Perc$SowTreat)
#sowd <- unique(df_50_Perc$SowingDate)
plots <- unique(df_50_Perc$Plot)
 

# create empty df
# df_tt_50p_emerg <- data.frame(Plot = NULL,
#                               Block = NULL,
#                              SowingD = NULL,
#                              Cultivar = NULL, 
#                              SowTreat = NULL,
#                              PercEmerg = NULL, 
#                              TT50Em = NULL)

#loop trough each combination of factor levels

for(p in 1:length(plots)) {
#  for(j in 1:length(var)){
 #   for(k in 1:length(sow)){
      
      # clean value holders
      DAS_50p_emerg <- 0
      #tt_50p_emerg <- 0
      
      #FIX ME Partially set 
    
     # print(paste0(cv[i]," ",var[j]," ", sow[k]))
      # filter for each combination

  df_sub <- df_50_Perc %>%
    # subset(Cultivar == as.character(cv[i]) &
    # Plot == as.character(var[j]) &
    #   Block == as.character(var[b]) &
    # SowTreat == as.character(sow[k])) %>%
    subset(Plot == plots[p]) %>%
    arrange(PercentTrifo)
  
  df_sub
  head(df_sub)
  # create percentage with maximum value recorded 
  # to avoid crossing the 50% line twice
  
  df_sub$av_Perc_max <- 0 # create new col
  
  for(z in 1:nrow(df_sub)) {
    
    df_sub$av_Perc_max[z] <- max(df_sub$av_Perc[z],
                                 df_sub$av_Perc_max[z-1])
    
  }
  
  df_sub
  head(df_sub)
  tail(df_sub)

  # Interpolate 
  
  y_ref <- 1 # y value where we want to find x by interpolation in this case needed 1 trifoliate
  #y_ref <- 5 # y value where we want to find x by interpolation in this case needed 5 trifoliates 
  #y_ref <- 9 # y value where we want to find x by interpolation in this case needed 5 trifoliates 
  
  # interpolate
  #find DAS at 50 Pecent Emergence 

  tryCatch(  
  DAS_50p_emerg <- approx(df_sub$PercentTrifo, 
  df_sub$av_DAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  DAS_50p_emerg <- NA
  }
)
  #find TT at 50 Pecent Emergence
#   tryCatch(  
#   tt_50p_emerg <- approx(df_sub$av_Perc, 
#   df_sub$av_TT , xout = y_ref, rule = 1)$y,
#   error = function(e) 
#   {
#   tt_50p_emerg <- NA
#   }
# )

  df_temp <- NULL 
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             PercEmerg = df_sub$PercentTrifo[1], 
                             SowingDate = df_sub$SowingDate[1],
                             Plot = df_sub$Plot[1],
                             Block = df_sub$Block[1],
                             DAS50E = DAS_50p_emerg)
                             #TT50E = tt_50p_emerg)
  print(p)
  
  if(p == 1) {
    df_tt_50p_emerg <- df_temp
  } else {
   df_tt_50p_emerg <- rbind(df_tt_50p_emerg,df_temp) 
  }                     
  
#    } 
  } # end plot loop


head(df_tt_50p_emerg)



summary(df_tt_50p_emerg)



```



Now correct column names after loop  to avoid  mix with other generated tables : First Trifoliate code = 1T

```{r}

#df_5T<-df_tt_50p_emerg%>%
df_1T<-df_tt_50p_emerg%>%
  mutate(DAS1T=as.numeric(DAS50E))%>%
  dplyr::select(-PercEmerg)

str(df_1T)
 


```



```{r}
#if needed 
#write.table(df_1T,"GC_df_DAS_1_Trifo.txt")
```



Calculate RAte (1/days to 50%) 


```{r}

#try 1/DAS50% = Rate

df_RateTrifo <- df_1T %>%
  mutate(Rate=1/DAS1T)

  summary(df_RateTrifo)
  
  #write.table(df_RateTrifo,"GC_1T_RateTrifo.txt")

```


##Add the number of days for 50% emergence to calculate the days to first trifoliate after emergence (DAE)

##File ready at : GC_DASToEmergence.txt (already calculated the days after emergence for first trifoliate : DAE_1T)





```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GC_TrifoCounts")
getwd()
#create file
df_trif2 <- read.table("GC_DASToEmergence.txt",header=TRUE)


str(df_trif2)


```


Define formats 

```{r loadFile}


# define factors for the ones that "look like" values

df_trif2 <- df_trif2 %>%
  mutate(SowingDate = ymd(SowingDate), 
         Date50Emerg = ymd(Date50Emerg),
         DAS_ToEmerg = as.numeric(DAS_ToEmerg))


df_trif2$Pot <- as.factor(df_trif2$Pot)
df_trif2$Block <- as.factor(df_trif2$Block)
df_trif2$Cultivar <- as.factor(df_trif2$Cultivar)
#df_trif$SowTreat <- as.factor(df_trif$SowTreat)

 
         

str(df_trif2)


```


```{r}

##Estimate date for trifoliate 1 after emergence 

df_Date1T <-df_trif2 %>%
  mutate(DateTo1TFromEmerg=Date50Emerg+ DAE_1T)
  

```

## Bring  the accumulated Thermal time data > calculated in folder GC climate > GCSumTTHourGC.txt

```{r}

#create file
df_A <- read.table("GCSumTTHourGC.txt",header=TRUE) 

#define formats
df_A <- df_A %>%
  mutate(Date = ymd(Date))
str(df_A)

```


##Quantify TT from emergence to first Trifo


```{r}

#prep dataframe with TT at emergence 
str (df_Date1T )

dfTTEm<-df_Date1T %>%
  select (Pot,Date50Emerg)%>%
  mutate(Date=Date50Emerg)%>%
  select(-Date50Emerg)
  
  
#prep Sum TT dataframe


Te<-df_A %>%
  select (Date,SumTTday)
  
#merge1
merge1 

# first merge the emergence date  and air temperature dataframes 

df_Temp1 <- merge(dfTTEm,Te,by="Date")

#Hold valeus to merge later 
```


Do smae procedure for the date to 1 trifo from emergence 

```{r}

#prep dataframe with TT at emergence 
str (df_Date1T )

dfTT_1T<-df_Date1T %>%
  select (Pot,DateTo1TFromEmerg)%>%
  mutate(Date=DateTo1TFromEmerg)%>%
  select(-DateTo1TFromEmerg)

##Merge usitn dataframe Te 
df_Temp2 <- merge(dfTT_1T,Te,by="Date")




```

#merge temporary dataframes 


```{r}
#Now merge Temp1 and Temp 2 to claculate the TT to first Trifo 


df_Temp3 <- merge(df_Temp1,df_Temp2,by="Pot")

str(df_Temp3)

##subtract sumTTdays to find the TT to first trifo 

df_Temp3 <- df_Temp3 %>%
  mutate(TT_1Trifo_Emerg=SumTTday.y-SumTTday.x)

##clean dataframe and prepare to re  emerge. 

df_Temp4 <-df_Temp3 %>%
  select(Pot, TT_1Trifo_Emerg)

```


##continue from here .... re emerge dataframes with new column bring original labels and columns 

```{r}

# 
df_Temp5 <- merge(df_Temp4,df_trif2,by="Pot")
##Rename to keep track of dataframe content!!! 

str(df_Temp5)

df_TT_ToTrifo1_Emerg <-df_Temp5 %>%
  select(Pot, TT_1Trifo_Emerg, Cultivar , Block )



```



Check : Inspect means  before ANOVA

```{r}
#Graph 


 # a <- df_RateTrifo %>%

 f <- df_TT_ToTrifo1_Emerg %>%
  group_by( Cultivar) %>%
  dplyr::select(  TT_1Trifo_Emerg) %>%
  summarise_all(funs(mean,sd))



```


RUN ANOVA



```{r ANOVAMaxPlantPop}

#compare DAE_1T  among cultivars

df_emerg_perc3 <- df_TT_ToTrifo1_Emerg %>%
  dplyr::select(Cultivar,Block,Pot,TT_1Trifo_Emerg)

```
Overall analysis consider sowing date and cultivar 


```{r}
##Overview   

file <- df_emerg_perc3
file$transf_no <- 1*(df_emerg_perc3$TT_1Trifo_Emerg)
head(file)

#-------------------------------------------------
# ANOVA for sowing date 
file.subset <- file 

head(file.subset)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar + Block, 
                data = file.subset)

summary(my.anova)

```


First LSD 

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Treat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 

#(LSD.test(my.anova, c("Block"), alpha= 0.05, p.adj="none")) 

```


Perform Tukeys 


This is Tukeys test for mean comparison 

```{r}
posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)
#posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.25)

posthoc

```



Then 
This is the mean separation using Tukey 


```{r}

fogo<-HSD.test(my.anova, 'Cultivar', group=TRUE)
fogo

```




##End of this script. 
##(Use similar code to calculate 5T and 9T)
