---
title: "Trifoliates GC "
author: "CT"
date: "31.08.2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Analysis of trifoliates expansion for GC with focus on first Trifoliate 
- Graph the main dataset 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```



```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\GC_TrifoCounts")
getwd()
#create file
df_trifo <- read.table("GCTrifoCountall.txt",header=TRUE)
head(df_trifo)


```
Define formats and calculate the mean number of trifoliates considering the sub samples (S1-S10)

```{r loadFile}


# define factors for the ones that "look like" values
df_trifo$Plot <- as.factor(df_trifo$Plot)
df_trifo$Block <- as.factor(df_trifo$Block)
df_trifo$Cultivar <- as.factor(df_trifo$Cultivar)
#df_trifo$SowTreat <- as.factor(df_trifo$SowTreat)

 df_trifo <- df_trifo %>%
  mutate(SowingDate = dmy(SowingDate), 
         ReadingDate = dmy(ReadingDate),
         Trifo = (S1+S2)/2)

str(df_trifo)
head(df_trifo)
tail(df_trifo)


df_trifo %>% filter(Plot ==1) %>% summary()



```

Graph the results : DAS and number of trifoliates 

```{r, fig.height=8, fig.width=15}
#Graph 1        
  df_trifo %>%
  #mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),labels=c("June", "July", "September", "November", "December", "February","March", "May")))%>%
  #filter(Cultivar=="Antas"|Cultivar=="Denmark"|Cultivar=="Leura")%>%
  group_by(Cultivar,  DAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=Trifo)) + 
  #geom_point(aes(colour=Cultivar, shape=Cultivar), size=4) +
  geom_point(aes(shape=Cultivar), size=5) +
  #scale_shape_manual(values = c(0,1,2, 3,4,5,6,7,8,9,10,11))+
  scale_shape_manual(values = c(1,2,0)) +
  #geom_line(aes(colour=Cultivar)) +
  #geom_line()+
  #facet_wrap(~SowTreat,ncol=4, scales = "free") +
  #facet_wrap (~SowTreat,ncol=4)+
  ylim(0,16)+
  labs(y="Number of trifoliate leaves (n)",x="Days after sowing")+
  #theme_grey(base_size = 16) +
  theme_bw(base_size = 24)+
  
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
    geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 5,  slope = 0, linetype=2)+
   geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
theme(text = element_text(size = 24))


#save
   
   #ggsave("plot_NumberOfTrifoliateLeavesA.png", width=16, height=8, dpi=400)




```




"

```{r ReadThermalSumData}
# read raw data

#Temperatures from GC climate folder  
 
#df_TTSum <- read.table("df_CumTTiv2.txt",header=TRUE)
df_TTSum <- read.table("SumTTHour_Pp_GC.txt",header=TRUE)
str(df_TTSum)

# remove extra columns
df_TTSum <- df_TTSum %>%
#dplyr::select(Date,SumTTday)%>%
  mutate(Date = dmy(Date))
 
#check
head(df_TTSum)

```

Check data 
```{r}
summary(df_TTSum)
```



Merge dfs TTSum at Measurement and Sowing Date into Flowering df
```{r}

str(df_trifo)
df_trifo<-df_trifo%>%
  mutate(Date=ymd(ReadingDate))
str(df_trifo)

# Add Tt at measurement date
df_trifo2 <- merge(df_trifo,df_TTSum, by="Date")

summary(df_trifo2)

```


Change column names and select only columns of interest (tidy up)

```{r}


# change name SumTTday to TT at measurement used mutate 1 x cause rename did not work 
df_trifo2 <- df_trifo2 %>%
mutate(TT_meas = 1*(SumTTday))
#check the data 
str(df_trifo2)

#select only columns of interest 
df_trifo3<- df_trifo2 %>%
dplyr::select (-S1, -S2) 

#check data 
str(df_trifo3)
```

Need to modify the column name to be able to merge 
```{r}
# Add Tt at sowing date
df_TTSum_mod <- df_TTSum %>%
  mutate (SowingDate = Date) %>%
  dplyr::select (-Date)

 str(df_TTSum_mod)
 str(df_trifo3)

```


Merge data frames 
```{r}



df_trifo4 <- merge(df_trifo3,df_TTSum_mod, by = "SowingDate")

str(df_trifo4)

# change name TT to TT at measurement
df_trifo4 <- df_trifo4 %>%
mutate(TT_sow = 1*(SumTTday.y))
#check
str(df_trifo4)

```


Graphic

```{r MergeTTSumDate}

#aqi
# TT from Bud to Bur 3 

df_trifo3 %>%
  #filter(SowTreat != "S6" & SowTreat != "S7")%>%
  group_by(DAS,Cultivar,TT_meas) %>%
  summarise_each(funs(mean)) %>%
  #select(Variable,Percent, Cultivar,SowTreat) %>%
  #filter(Cultivar == "Narrikup" | Cultivar =="Denmark") %>%
  ggplot(aes(x=TT_meas, y=Trifo)) + 
  #geom_bar(shape=1, stat="identity")
  geom_line(aes(colour=Cultivar)) +
  #facet_grid(SowTreat~., scales = "free") +
  geom_abline(intercept = 50, slope = 0)+
  
theme(axis.text.x = element_text(angle = 90, hjust = 1))


```

calculate TT after emergence 

```{r Calc_TT_afterSow}

##bring data emergence 

df_emerg <- read.table("GC_DASToEmergence.txt",header=TRUE)
head(df_emerg)

df_emerg<-df_emerg%>%
  dplyr::select(Plot,Date50Emerg )%>%
  mutate(Date=ymd(Date50Emerg))%>%
  dplyr::select(-Date50Emerg)

str(df_emerg) 

## then get the TT
df_Emergence <- merge(df_emerg,df_TTSum, by="Date")%>%
  mutate(SumTTdayToEmerg=SumTTday)%>%
  dplyr::select(Plot,SumTTdayToEmerg)



```

merge data frames by plot to get the TT after emergence for trifo leaves 

```{r ,merge}

str(df_trifo3)

mergedAgain<-merge(df_trifo3,df_Emergence, by="Plot")%>%
 # mutate(TTTrifoFromEmerg=TT_meas-SumTTdayToEmerg)
   mutate(TTTrifoFromEmerg=TT_meas-50)

str(mergedAgain)
  

              

# save final DF"
write.table(mergedAgain, "df_ThermalTrifoLeaves.txt")

```


get the standard  error values for the final trifoliate numbers 


```{r}
str(mergedAgain)

dfMaxTrifo <- mergedAgain %>% 

  group_by(Cultivar) %>%
  filter(DAS=="27")%>%
  dplyr::select(  Trifo )%>%
  summarise_all(funs(max,sd))%>%
  mutate(SE=sd/2)
 

  ##Max SE 1.6



```

Graphics 


Graph the results : DAS and number of trifoliates 

```{r, fig.height=8, fig.width=15}
#Graph 1        
A<- mergedAgain %>%
  #mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),labels=c("June", "July", "September", "November", "December", "February","March", "May")))%>%
  #filter(Cultivar=="Monti"|Cultivar=="Narrikup"|Cultivar=="Woogenellup")%>%
  group_by(Cultivar,DAS,TTTrifoFromEmerg) %>%
  summarise_all(funs(mean,sd)) 


A %>%
  ggplot(aes(x=TTTrifoFromEmerg, y=Trifo_mean)) + 
  #geom_point(aes(colour=Cultivar, shape=Cultivar), size=4) +
  geom_point(aes(shape=Cultivar), size=8) +
  #scale_shape_manual(values = c(0,1,2, 3,4,5,6,7,8,9,10,11))+
  scale_shape_manual(values = c(1,2,7)) +
  #geom_line(aes(colour=Cultivar)) +
  #geom_line()+
  #facet_wrap(~SowTreat,ncol=4, scales = "free") +
  #facet_wrap (~SowTreat,ncol=4)+
  ylim(0,16)+
  labs(y="Number of trifoliate leaves (n)")+
  xlab(expression(Thermal~time~Sowing~"("^"o"*"Cd)"))+
  theme_bw(base_size = 24)+
  
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
    geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 5,  slope = 0, linetype=2)+
   geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
theme(text = element_text(size = 24))

#save
   
   ggsave("plot_NumberOfTrifosvsTT.png", width=12, height=6, dpi=400)
 
##Max SE = 1.6 
```

