---
title: "Trifoliates Iversen "
author: "CT"
date: "17.08.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Analysis of trifoliates expansion for Iversen from previous script (use file RateTrifo.txt)
- Calculate the date to 50% percent leaf emergence
- Calculate the mean air temperature during period
- merge the dataframes and plot 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```



```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifoCountsI2")
getwd()
#create file
df_trif <- read.table("RateTrifo.txt",header=TRUE)
str(df_trif)


```

adjust formats and Calculate the date to 50%  
```{r}


df_trif$SowingDate <- ymd(df_trif$SowingDate )
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$PercEmerg <- as.numeric(df_trif$PercEmerg)

#Then calculate the date to 50% Emergence sum the date or sowing + DAS50E
#Note df_Md has duplicated rows - fix it!! 

df_MD <- df_trif %>%
  mutate(Date50E=SowingDate+DAS50E) %>%
  group_by(Plot, DAS50E) %>% 
  dplyr::filter(row_number() == 1)

str(df_MD)
#Here DAte50E is included no nee to change format 

```


Then merge with dates for seedling emergence to find out how many days from 50 % seedling emergence to 50% leaf appearance  

```{r loadFile}


setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifoCountsI2")
getwd()
#create file
df_S <- read.table("DASSeedEmer.txt",header=TRUE)

#change formats 
df_S <- df_S %>%
  mutate(Plot=as.factor(Plot),
         DAS50SeedEm= as.numeric(DAS50SeedEm),
         Date50SeedEm= dmy(Date50SeedEm))

         
str(df_S)


```


Now bring the Air temperature data 
```{r}


setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifoCountsI2")
getwd()
#create file
df_A <- read.table("AirTemp.txt",header=TRUE)

#adjust formats
df_A %>%
  mutate(Date=dmy(Date))

str(df_A)

df_B <- df_A %>%
  mutate(SumAir = cumsum(AirTt)) %>%
  mutate(Date=dmy(Date))%>%
  dplyr::select(-AirTt)

#head(df_soilTemp)

summary(df_B)
summary (df_S)

```

Problem merging here 



```{r}


df1 <- merge(df_S,df_B, by.x="Date50SeedEm",by.y="Date")%>%
mutate(AirTempAcc_emerg = SumAir) %>%
  dplyr::select(-SumAir)

str(df1)
```

then merge with the data frame which contains the trifoliate info 
```{r}


df_M <- df_MD%>%
  group_by(SowingDate,SowTreat,Plot,Block,Cultivar)

df2 <- merge(df_B,df_M, by.x="Date",by.y="Date50E")%>%
mutate(AirTempAcc_tri = SumAir) %>%
  dplyr::select(-SumAir)

str(df2)



# then merge the dataframes to find out the mean temperature 


```



Include dates of sowing again in dataframe 
```{r}
sdLookup <- data.frame (
  SowTreat = c("S1","S2","S3","S4","S5","S6","S7","S8"),
  SowingDate = c("24/06/2015", 
                 "28/07/2015" ,
                 "15/09/2015" ,
                 "5/11/2015" ,
                 "15/12/2015" ,
                 "17/02/2016" ,
                 "15/03/2016",
                 "4/05/2016"))

sdLookup$SowingDate <- dmy(sdLookup$SowingDate)

df_tt_50p_emerg <- merge(df_tt_50p_emerg, sdLookup, by="SowTreat")
summary(df_tt_50p_emerg)


write.table(df_tt_50p_emerg,"df_tt_50p_emergTrifo.txt")
```




Calculate RAte (1/days to 50%) 


```{r}

#try 1/DAS50% = Rate

df_RateTrifo <- df_tt_50p_emerg %>%
  mutate(Rate=1/DAS50E)

  summary(df_RateTrifo)
  
  write.table(df_RateTrifo,"RateTrifo.txt")

```



Graph rate and SowTreat

```{r}
#Graph 

  df_RateTrifo %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 50% leaf emergence  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

```




End of this script Calc 3. 
Move to script 4 to include temperatures  
