---
title: "Trifoliates Iversen "
author: "CT"
date: "31.10.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Analysis of trifoliates expansion for Iversen
- Calculate stat for the days to reach 5 trifoliates 
- Run ANOVA for variable "Number of days to reach 5 Trifoliates " 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```

Read document generated in script "3" 5Trifo_rate

```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifoCountsI2")
getwd()
#create file
df_trifo <- read.table("df_DAS_5_Trifo.txt",header=TRUE)
head(df_trifo)


```
Define formats and calculate the number of trifoliates considering the sub samples (S1-S10)

```{r loadFile}


# define factors for the ones that "look like" values
df_trifo$Plot <- as.factor(df_trifo$Plot)
df_trifo$Block <- as.factor(df_trifo$Block)
df_trifo$Cultivar <- as.factor(df_trifo$Cultivar)
df_trifo$SowTreat <- as.factor(df_trifo$SowTreat)

 df_trifo <- df_trifo %>%
  mutate(SowingDate = dmy(SowingDate), 
         ReadingDate = dmy(ReadingDate),
         Trifo = (s1+s2+s3+s4+s5+s6+s7+s8+s9+s10)/10)

str(df_trifo)
head(df_trifo)
tail(df_trifo)


df_trifo %>% filter(Plot ==1) %>% summary()

#select columns of interest and rename columns 

df_Tr <- df_trifo %>%
mutate(TrifoNumber=as.numeric(Trifo))%>%
dplyr::select(-s1:-s10, -Trifo)
```



Prepare dataframe to calculate rate (1/Days to 5 trifos) in the next script.


```{r}
write.table(df_Tr, "Number_Trifo.txt")


```


End of this script Calc 2. 
Move to script 3 to calculate rate of leaf appearance 
