---
title: "Relative Humidity  Calculation Iversen 2 - Broadfields Weather data"
author: "CT"
date: "01 Jan 2018"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```

- Aim : calculate the mean RH during the growth period for each cultivar x sowing time period .


```{r readData}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Iver_weather")
getwd()

#create file
df_RH <- read.table("RelativeHumidity.txt", header=TRUE)

head(df_RH)

#summary(df_RH)
```



```{r changeformat, echo=FALSE}
str(df_RH)

#adjust format 

df_RH<-df_RH%>%
  subset (date=)
   mutate(date=as.Date(date))%>%
   mutate(RHmean=as.numeric(RHmean))
# 
# 
# 
head(df_RH)

```

## Calculation 

```{r, fig.height=6, fig.width=15}

#Calculate the mean per date   
df_RH1<-df_RH%>%
  group_by(date)%>%
  summarise_all(funs(mean))



```

## Subset for each cultivar vs. sowing date 1 combination 

Considered Antas S1 period : 2015-06-24 till 2016-01-15
          Denmark S1 period : till 2016-01-25
          Leura S1 : till 2016-01-26
          MontiS1: till 2016-01-05
          Narrikup S1 : till  2016-01-12
          woogenellup til; 2016-01-17
          
for S2 ; 2015-07-28 
          Antas till 2016-02-09
          Denmark : 2016-02-18
          Leura; 2016-02-18
          Monti: 2016-02-05
          Narrikup:2016-02-05
          Woogenellup : 2016-02-11
          
for  S3 : 2015-09-15 
          Antas till 2016-03-15
          Denmark : 2016-03-21
          Leura; 2016-03-23
          Monti: 2016-02-29
          Narrikup:2016-02-29
          Woogenellup : 2016-03-10

for S4 : 
subset(date>"2015-07-28" & date<"2016-02-09")%>%

							
```{r}
A <- df_RH1 %>%
  subset(date>"2015-06-24" & date<"2016-01-15")%>%
   #subset(date>"2015-07-28" & date<"2016-02-09")%>%
  #subset(date>"2015-09-15" & date<"2016-03-15")%>%
  dplyr::select(RHmean)%>%
  summarise_all(funs(mean))


```


```{r}
D <- df_RH1 %>%
  #subset(date>"2015-06-24" & date<"2016-01-25")%>%
  #subset(date>"2015-07-28" & date<"2016-02-18")%>%
  subset(date>"2015-09-15" & date<"2016-03-21")%>%
  dplyr::select(RHmean)%>%
  summarise_all(funs(mean))
```


```{r}
L <- df_RH1 %>%
  #subset(date>"2015-06-24" & date<"2016-01-26")%>%
  #subset(date>"2015-07-28" & date<"2016-02-18")%>%
  subset(date>"2015-09-15" & date<"2016-03-23")%>%
  dplyr::select(RHmean)%>%
  summarise_all(funs(mean))
```


```{r}
M <- df_RH1 %>%
  #subset(date>"2015-06-24" & date<"2016-01-05")%>%
  #subset(date>"2015-07-28" & date<"2016-02-05")%>%
  subset(date>"2015-09-15" & date<"2016-02-29")%>%
  dplyr::select(RHmean)%>%
  summarise_all(funs(mean))

```


```{r}

N <- df_RH1 %>%
  #subset(date>"2015-06-24" & date<"2016-01-12")%>%
  #subset(date>"2015-07-28" & date<"2016-02-05")%>%
  subset(date>"2015-09-15" & date<"2016-02-29")%>%
  dplyr::select(RHmean)%>%
  summarise_all(funs(mean))

```


```{r}
W <- df_RH1 %>%
  subset(date>"2015-06-24" & date<"2016-01-17")%>%
  subset(date>"2015-07-28" & date<"2016-02-11")%>%
  
  dplyr::select(RHmean)%>%
  summarise_all(funs(mean)) 

```





```{r}

#Create and test interpolation function - Test if works 

temp_ref  <- 25 # x-axes reference
temp <- tt_card$temp # x-axes
TT <- tt_card$TT # y-axes


int_func <- function(temp,TT,temp_ref){

  # if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   
   
   out <- TT[length(TT)] 
   # FIXME: approx functions seems to do that - need param
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
   # else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  
int_func(temp,TT,temp_ref)


```

```{r}

#create REF Jones CA, Ritchie JT, Kiniry JR, Godwin DC (1986) Subroutine structure.In 'CERES-Maize: A simulation model of maize growth anddevelopment'. (Eds CA Jones, JR Kiniry) pp. 49-194. (Texas A&M University Press: Texas, USA

TTfunc <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
 } 
  
  TTav  <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2
            + 0.0053 * n^3) * (Tmax-Tmin)) + 
      Tmin # 8-h temperature
    
    TT_tn <- int_func(tt_card$temp, tt_card$T,tn) 
    
    TTsum <- TT_tn + TTsum
    
    print(TT_tn)
    
    }
  TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc(10,30)

```

```{r ReadCalcTt}
#Here a comparison between the simple TT calculation (Tx-Tm/2) and Jones 8 hours calculation
df_We_tt <- df_Weiv %>%
  mutate(TTday=TTfunc(Tm,Tx), TTday_s=(Tm+Tx)/2, diff=(TTday_s/TTday)*100)

```


```{r}
#Check TT 
df_We_tt  %>% 
ggplot(aes(x=TTday_s, y= TTday)) +
    geom_point(shape=21,alpha=0.2)+
  geom_abline(intercept = 0, slope = 1)

```





```{r}

#Calculate accumulated Themal time 

df_CumTTiv <- df_We_tt %>%
mutate(SumTTday = cumsum(TTday)) 


head(df_CumTTiv)


```

```{r, fig.height=5, fig.width=10}
#Graph Accumulated TT 

df_CumTTiv %>% 
ggplot(aes(x=Date, y= SumTTday)) +
  theme_bw()+
  geom_line()+
  xlab(expression(Date~~"(Year-Month)")) + 
  ylab(expression(Thermal~time~~"(d"^"o"*"C)"))
    


```




```{r}

write.table(df_CumTTiv, "df_CumTTiv.txt")

```

