---
title: "Thermal Time Calculation Iversen 2 Weather data using hourly data"
author: "CT"
date: "07.12.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```



## Define Tt cardinal temperatures

Considered an overall average the following references:
Tb: 0.0
Top range:18-25
Tmax: 40
REFS: MonksEtAl2009	,LonatiEtAl2009	,MootEtal2003, SilsburyetAl1984. 
							
```{r}

#Create Thermal time cardinal temperatures need REF! 

tt_card <- data.frame(temp=c(0,15,22,35),TT=c(0,15,15,0))

tt_card %>%
  ggplot(aes(x=temp, y=TT))+
  labs(x="Temperature (degree Celsius)")+
  labs(y="Thermal Time (degree days)") +
  theme_bw()+
  geom_line()
  
```

```{r}

#Create and test interpolation function - Test if works 

temp_ref  <- 25 # x-axes reference
x_temp <- tt_card$temp # x-axes
y_TT <- tt_card$TT # y-axes


int_func <- function(temp,TT,temp_ref){

  # if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   out <- TT[length(TT)] 
   # FIXME: approx functions seems to do that - need param
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
   # else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  
int_func(x_temp,y_TT,temp_ref)


```

```{r readData}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Iver_weather")
getwd()

#create file
df_W_raw <- read.table("HourTemp_Iv2.txt",header=TRUE)

#head(df_We)

summary(df_W_raw)
```

Calculate the TThour, then transform to TT day and accumulate the Thermal time to make the TTSUM Air. 

```{r changeformat, echo=FALSE, warning=FALSE}

df_W <- df_W_raw %>%
  dplyr::select(Date:TempAir) %>%
  mutate(Date=dmy(Date)) %>%
  rowwise() %>%
  mutate(TThour=int_func(x_temp, y_TT,TempAir))


#then average the TT per Date
  df_W <-df_W %>%
  group_by(Date) %>%
    dplyr::select(TThour)%>%
   summarise_all(funs(mean))%>% 
    mutate(TTday=TThour)%>%
    mutate(SumTTday = cumsum(TTday))
  

summary(df_W)

```

```{r}
df_W %>%
  ggplot(aes(x=TempAir,y=TT))+
  geom_point() 
```


now calculate the TTSUm in each date to compare with the methods TT simple and TT 3x8 formula

```{r}
dfdailyTT <- df_W_raw %>%
  dplyr::select(Date:TempAir) %>%
  mutate(Date=dmy(Date)) %>%
  mutate(HourTT=TempAir/24)%>%
 rowwise() %>%
  group_by( Date) %>%
  mutate(TTdayH = as.numeric(sum(HourTT)))%>%
  subset(Hour<1)%>%
  select(-HourTT, -Hour)
  

```



## Graph it 

```{r, fig.height=6, fig.width=15}

df_W %>%
  #tidyr::gather("Variable", "Value",Tx:Pp) %>%
  ggplot(aes(x=Date,y=TempAir))+
  geom_line() +
  #facet_wrap(~LocationYear,scale="free") +
  #scale_color_manual(values=c("green","#333333", "#3355CC","#CC3300"))+
  theme_bw()+
  labs(x=" Date (Year/Month)")+
  ylab(expression(Air~Temperature~time~~"("^"o"*"C)/hours"))+
  theme(axis.text.y = element_text(size=18))+
  theme(axis.title.y = element_text(size=22))+
  theme(legend.text = element_text(size=22))+
  theme(axis.title.x = element_text(size=22))+
  theme(axis.text.x = element_text(angle = 0, hjust = 0.5, size=22)) 


```


find max and min temperature in each date 

```{r}
dfMax<-df_W %>%
  group_by(Date)%>%
  dplyr::select ( TempAir)%>%
  summarise_all(funs(max))
 

dfMin<-df_W %>%
  group_by(Date)%>%
  dplyr::select ( TempAir)%>%
  summarise_all(funs(min))

dfMax_MinAir <- merge(dfMax,dfMin, by="Date")%>%
  mutate(Tx=TempAir.x, Tm=TempAir.y)%>%
  select(-TempAir.x, -TempAir.y )
write.table(dfMax_MinAir, "MinMaxAirIv.txt")

```

Here consider daily temps adjusted by the 3x8 formula


```{r}

#create REF Jones CA, Ritchie JT, Kiniry JR, Godwin DC (1986) Subroutine structure.In 'CERES-Maize: A simulation model of maize growth anddevelopment'. (Eds CA Jones, JR Kiniry) pp. 49-194. (Texas A&M University Press: Texas, USA

TTfunc <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
 } 
  
  TTav  <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2
            + 0.0053 * n^3) * (Tmax-Tmin)) + 
      Tmin # 8-h temperature
    
    TT_tn <- int_func(tt_card$temp, tt_card$T,tn) 
    
    TTsum <- TT_tn + TTsum
    
    print(TT_tn)
    
    }
  TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc(10,30)

```




```{r ReadCalcTt}


#create file
df_Weiv <- read.table("MinMaxAirIv.txt", header=TRUE)

#Here a comparison between the simple TT calculation (Tx-Tm/2) and Jones 8 hours calculation
df_We_tt <- df_Weiv %>%
  mutate(TTday=TTfunc(Tm,Tx), TTday_s=(Tm+Tx)/2, diff=(TTday_s/TTday)*100)

```


```{r}
#Check TT : here plot TT day caluclated with 3x8 formula against the TT simple calculation (Tmean) 
df_We_tt  %>% 
ggplot(aes(x=TTday_s, y= TTday)) +
    geom_point(shape=21,alpha=0.2)+
  geom_abline(intercept = 0, slope = 1)

```


merge with dfdailyTT (which is originated from hourly calculations )

```{r}

#adjust date formats to match
df_We_tt2 <- df_We_tt %>%
mutate(Date=ymd(Date))
 
str(df_We_tt2)
str(df_W)

df_AllTT <- merge(df_We_tt2, df_W ,by="Date")

```

check differences between calculated TT hourly or formula 

```{r, fig.height=5, fig.width=10}
#Graph Accumulated TT 
#Check TT : here plot TT day caluclated with 3x8 formula against the TT based on hourly recorded data 
df_AllTT %>% 
ggplot(aes(x=TT, y= TTday.x)) +
  theme_bw()+
  geom_point()+
  geom_smooth()+
  xlab(expression(Thermal~time~Hourly~"(d"^"o"*"C)"))+
  ylab(expression(Thermal~time~formula~"(d"^"o"*"C)"))+
  geom_abline(intercept = 0, slope = 1)+
  ylim(0,18)
    


```

compare the methods (TT against date or Air temperature  )
# TT  =calculated with hourly recorded data;
# TTday.x is calculated using the 3x 8 formula (max and min )
#and TTday_s is calculated with the simple Tx+Tm/2

```{r, fig.height=5, fig.width=10}
dfAlTT_1 <-df_AllTT %>%
  select(Date,TempAir, TTday.x,TTday_s,TT)%>%
 gather(key= "TTdailyMethod" , value = "DegreeDays", TTday.x,TTday_s,TT)

dfAlTT_1%>%
  filter(TTdailyMethod!="TTday_s")%>%
ggplot(aes(x=TempAir, y= DegreeDays)) +
  theme_bw()+
  geom_point(aes(colour=TTdailyMethod), alpha=0.1)+
  geom_smooth(aes(colour=TTdailyMethod))+
  ylab(expression(Thermal~time~~"(d"^"o"*"C)"))+
  xlab(expression(AirTemp~"("^"o"*"C)"))+
  ylim(0,25)

 


```



the formula and the hourly records correlate well ~12.5.. 


```{r}

write.table(df_W, "df_CumTTiv2.txt")

```

