
---
title: "ThermalTime"
author: "CT"
date: "Friday, January 01, 2016"
output: html_document
---


```{r}
library(tidyr)
library (dplyr)
library (ggplot2)
library (lubridate)
```

Note: the file is called HistoricMeanTemp but actually contains the hobologger data Iversen 2

```{r, load file}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Iver_weather")
getwd()

df_file <- read.table("SoilTempMean.txt", header=TRUE)

head(df_file)

#keep this scirpt for the real weather data




```


Then simply graph...but the second is better! 
```{r Soiltemp_mean}
#Calculculate Mean Soil temp 

df_file$Date <- dmy(df_file$Date)

df_file <- df_file%>%
group_by(Date)%>%
summarise_each(funs(mean))
head(df_file)

#graph meanAir Temp

df_file %>% 
ggplot(aes(x=Date, y= TempSoil10mm)) +
  labs(y="Soil Temperature (Degree Celsius)10mm",x="Date")+
    geom_line()

```



```{r, fig.height=5, fig.width=8}


 df_file %>%
  #filter(year %in% 2015:2017) %>%
  group_by(Date) %>%
 summarise_each(funs(mean)) %>%
  ggplot(aes(x=Date, y= TempSoil10mm))  +
  #geom_point(colour= "darkblue", alpha=0.2) +
  geom_line()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
 xlab("Date") + 
  ylab(expression(Daily~mean~soil~temperature~~"( "*C^"o"*")"))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B",
                 limits = as.Date(c('2015-06-01','2017-07-07')))




```


Calculate accumulated TT simple

```{r}

df_file <- df_file%>%
group_by(Date) %>%
summarise_each(funs(mean))%>%
  mutate(TT = cumsum(TempSoil10mm))%>%
 # dplyr::select(-hour,-Air)
  dplyr::select(-TempSoil10mm) # 

write.table(df_file, "ThermalSumSoil.txt")

```

Calculate TT 3x8 hour equation

```{r}

df_fileSoil <- read.table("RawSoilTempIv2.txt", header=TRUE)

head(df_fileSoil)

df_fileSoilwork<-df_fileSoil%>%
  mutate(Tmax=Tx, 
         Tmin=Tm)

```

## Define Tt cardinal temperatures

Considered an overall average the following references:
Tb: 0.0
Top range:18-25
Tmax: 40
REFS: MonksEtAl2009	,LonatiEtAl2009	,MootEtal2003, SilsburyetAl1984. 



```{r}

#Create Thermal time cardinal temperatures need REF! 

tt_card <- data.frame(temp=c(0,18,22,37),TT=c(0,18,18,0))
tt_card %>%
  ggplot(aes(x=temp, y=TT))+
  labs(x="Temperature (degree Celsius)")+
  labs(y="Thermal Time (degree days)") +
  theme_bw()+
  geom_line()
  
```



```{r}

#Create and test interpolation function - Test if works 

temp_ref  <- 25 # x-axes reference
temp <- tt_card$temp # x-axes
TT <- tt_card$TT # y-axes


int_func <- function(temp,TT,temp_ref){

  # if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   out <- TT[length(TT)] 
   # FIXME: approx functions seems to do that - need param
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
   # else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  
int_func(temp,TT,temp_ref)


```



```{r}

#create REF Jones CA, Ritchie JT, Kiniry JR, Godwin DC (1986) Subroutine structure.In 'CERES-Maize: A simulation model of maize growth anddevelopment'. (Eds CA Jones, JR Kiniry) pp. 49-194. (Texas A&M University Press: Texas, USA

TTfunc <- function(Tmin ,Tmax){         
 
  if (Tmin>Tmax){
   print("Tmin>Tmax")
   break
 } 
  
  TTav  <- 0
  TTsum <- 0
  
  for(n in 1:8){ 
    
    tn <- 0
    
    TT_tn <- 0
    
    tn <- ((0.931 +  0.114*n - 0.0703 * n^2
            + 0.0053 * n^3) * (Tmax-Tmin)) + 
      Tmin # 8-h temperature
    
    TT_tn <- int_func(tt_card$temp, tt_card$T,tn) 
    
    TTsum <- TT_tn + TTsum
    
    print(TT_tn)
    
    }
  TTav <- TTsum/8
  
  return(TTav)
  }

TTfunc(10,30)

```



```{r ReadCalcTt}
#Here a comparison between the simple TT calculation (Tx-Tm/2) and Jones 8 hours calculation
df_Soil_tt <- df_fileSoilwork %>%
  mutate(TTday=TTfunc(Tm,Tx), TTday_s=(Tm+Tx)/2, diff=(TTday_s/TTday)*100)

```


Accumulate TT soil 

```{r}

#Calculate accumulated Themal time 

df_CumSoilTTiv <- df_Soil_tt %>%
mutate(SumTTday = cumsum(TTday)) 


head(df_CumSoilTTiv)


```



```{r}

write.table(df_CumSoilTTiv, "df_CumSoil_TTiv.txt")

```


Graph it 


```{r graph}

df_file %>% 
ggplot(aes(x=Date, y= TT)) +
   labs(y="Accumulated Thermal time (DCd)",x="Date")+ geom_line()

```

Make a graph Soil and Air temperature next script 


```{r}



```

