---
output:
  word_document: default
  html_document: default
---
---
title: "Percentage of germinated seeds  "
author: "CT"
date: " 24.08.2017 "
output:
  word_document: default
  pdf_document: default
  
  #This script  reads the Fieldbreakdaown data and performs ANOVA for different cultivars 
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(rgr)
```

Aim: compare the percentage of germinated seeds among different cultivars over time : preferentially autumn


```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FieldBreakdown")
getwd()



df_seedY<- read.table("FieldBreakData.txt",header=TRUE)
head(df_seedY)
summary(df_seedY)


```


Define formats  
```{r}

# define factors and formats
file <- df_seedY %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    DAB= as.numeric (DAB),
    ReadingDate = dmy(ReadingDate)
  )

str(file)
summary(file)
head(file)




```


Select columns of interest for ANOVA.

```{r}

df<- file %>%
  dplyr::select(Cultivar,Plot,Block,DAB, PercCumGerm)
            

  df <- as.data.frame(df)
head(df)


```

For graphics see script1 



Here ANOVA according S. Saville advice: LSD test unprotected by sowing date individually.
Use filters to select DAB (days after burial ). Here 111 DAB represents the first autumn in 2016. 

```{r}
#Filter  period of the year to compare cultivars  
summary(df)

df_seedYS6 <- df %>%
  #filter(DAB=="111")
  #filter(DAB=="111")
  #filter(DAB=="111")
  

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS6


file.subset <- file 

head(file.subset)
summary(file.subset)


```

Here need to change  the variables to get mean values. 
Use :comment out or in to select  Variable of interest  

```{r}
#ANOVA

my.anova <- aov(PercCumGerm ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```

Then use multiple comparisons of means when applicable (P<0.05)
```{r}
#Means separation after ANOVA

(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "SowTreat"), alpha= 0.05, p.adj="none"))
```

Filter reading in autumn 2017 . Select DAB = 442 (17.05.2017)

```{r}

#Filter  period of the year to compare cultivars  
summary(df)

df_seedYS7 <- df %>%
  #filter(DAB=="111")
  filter(DAB=="442")
  #filter(DAB=="111")
  

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS7


file.subset <- file 

head(file.subset)
summary(file.subset)

```


```{r}
#ANOVA

my.anova <- aov(PercCumGerm ~ Cultivar + Block, data = file.subset)

summary(my.anova)

```


```{r}
#Means separation after ANOVA

(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))

```

run for final count on 538 DAB 

```{r}
#Filter  period of the year to compare cultivars  
summary(df)

df_seedYS8 <- df %>%
  #filter(DAB=="111")
  #filter(DAB=="442")
  filter(DAB=="538")
  

#data transformation many possibilities but logit worked well, however little difference between real and transformed numbers 

#-------------------------------------------------
# anova 
file <- df_seedYS8


file.subset <- file 

head(file.subset)
summary(file.subset)

```

ANOVA 538 DAB 
```{r}

#ANOVA

my.anova <- aov(PercCumGerm ~ Cultivar + Block, data = file.subset)

summary(my.anova)
```

Means separation and Standard errors 


```{r}
#Means separation after ANOVA

(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
```





End of this script. 
