---
title: "Hardseeds breakdown field"
author: "CT"
date: 07.09.2016"
output:
  word_document: default
  
---
Purpose : 
This script reads the raw data from the field seed hardness breakdown (buried mesh bags)
  

```{r loadLibraries}
library (lubridate)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library(rgr)
```

Read file and 
```{r, loadFile}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\Gitsubclover\\FieldBreakdown")
getwd()

#create file
df_seed <- read.table("FieldBreakData.txt",header=TRUE)
head(df_seed)
summary(df_seed)

df_seed %>%
  filter(Plot==1)



```

Adjust formats and calculate the percentage of germinated seeds 
```{r}
# change format with basic R 
#df_seed$Date <- dmy(df_seed$Date)

# change formats with dplyr 

df_seed <- df_seed %>%
  mutate(Plot = as.factor(Plot), Block = as.factor(Block)) %>%
  mutate(Germinated = as.numeric(Germinated)) %>%
  mutate(DAB = as.numeric(DAB))%>%
  mutate(PercCumGerm = as.numeric(PercCumGerm))
  

#summary(df_seed) # explore values
str(df_seed) # check formats
# head(df_seed) # see to rows
# tail(df_seed)

# df_seed %>%
#   filter(Plot==1)
```

Calculate and Graph the potential Hardseeds (hardseed = 100 - Propsoftseeds) 
111 Days here was selected to be the first autumn measurement as the hardseeds percentage (compare with the laboratory results! )

```{r, fig.height=5, fig.width=10}
df_seed %>%
  mutate(hardSeed = 100-PercCumGerm) %>%
  #mutate(SowingD = dmy(SowingD)) %>%
  filter(DAB == 111) %>%  #need to keep filter to get first and max hardseed percent
  #mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
  group_by(Cultivar) %>%
  dplyr::select(hardSeed) %>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x=Cultivar, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
 #facet_grid(.~Depth) +
  labs(x="DAB",y="Maximum Percentage of Hardseeds") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
                    ymax=mean+sd/2))+
  theme_bw()+
  ylim(0,100)

head(df_seed)

summary(df_seed)

```

Select columns of interest 

Calculate the cumulative number of germinated seeds 
stopped here fix nujmber 

```{r, warning=FALSE}

 
g1 <-df_seed %>%
  dplyr::select(-SowTreat, -SowingDate:-ReadingDate, - MeshBagburrs, -NumberSeedsPerBurr) 

write.table(g1, "FieldBreakdown.txt")
```

graph the Cummulative percentage of seedlings 


```{r ,fig.height=5, fig.width= 10}




g <- g1 %>%
  #ungroup() %>%
#mutate(Depth = factor(Depth,levels=c( "Above","Below"))) %>%
  group_by(Cultivar, DAB) %>%
  dplyr::select(PercCumGerm , DAB) %>%
  summarise_each(funs(mean,sd))
# then graph the means 
g %>%
ggplot(aes(x=DAB, y=mean, colour=Cultivar, shape=Cultivar)) +
  geom_point() +
  geom_line() +
  # geom_errorbar(aes(x=50,ymin=40,ymax=43,width=0.3, colour = "blue"))+ #LSD value
  #facet_grid(Depth~SowTreat) +
  theme_bw()+
  theme(text = element_text(size=12))+
  geom_errorbar(aes(ymin=mean-sd/2,
                   ymax=mean+sd/2))+
  ylim(0,60)+
  #geom_vline(xintercept = 5, linetype=2)+
   labs(x="Burial period (days) ",y="Cumulative Percentage of Germination (%) ")
  



```


Graph the opposite , percentage of hardseeds 

```{r, fig.height=5, fig.width= 10}



g2 <- g1 %>%
 mutate(CumhardSeed = 1*(100-PercCumGerm)) %>%
group_by(Cultivar, DAB) %>%
  dplyr::select(CumhardSeed , DAB) %>%
  summarise_each(funs(mean,sd)) 

summary (g2) 

g2 %>%
  ggplot(aes(x=DAB, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
 #facet_grid(.~Depth) +
  labs(x="DAB",y="Percentage of Hardseeds") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  # geom_errorbar(aes(ymin=mean_sd/2,
  #                   ymax=mean_sd/2))+
  theme_bw()+
  ylim(0,100)


```

```{r}


g1 %>%
  dplyr::select(Plot,PercCumGerm,Cultivar,DAB) %>%
  #tidyr::spread(Depth, PercSoftCum) %>%
  ggplot(aes(x=DAB,y=PercCumGerm))+
  geom_point(aes(colour=factor(Cultivar))) +
  stat_smooth(method = "lm") +
  facet_grid(Cultivar~.)



```

This script ends here. 
Analysis in script 2 


