
---
title: "ThermalTime accumulation in Iversen mesh bags test "
author: "CT"
date: "19.09.2017"
output: html_document
---


```{r}
library(tidyr)
library (dplyr)
library (ggplot2)
library (lubridate)
```

Note: the file is called HistoricMeanTemp but actually contains the hobologger data Iversen 2

```{r, load file}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FieldBreakdown")
getwd()

df_file <- read.table("SoilTempIv.txt", header=TRUE)

head(df_file)

#keep this scirpt for the real weather data


str(df_file)
df_file<- df_file%>%
  mutate(Date=dmy(Date))
str(df_file)

```


Then simply graph it! 





```{r, fig.height=5, fig.width=8}


 df_file %>%
  #filter(year %in% 2015:2017) %>%
  group_by(Date) %>%
 summarise_each(funs(mean)) %>%
  ggplot(aes(x=Date, y= TempSoil10mm))  +
  #geom_point(colour= "darkblue", alpha=0.2) +
  geom_line()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  geom_abline(intercept = 15, slope = 0)+
 xlab("Date") + 
  theme(axis.text.x=element_text(angle = 0, hjust = 0, size= 14))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 14))+
  ylab(expression(Daily~mean~soil~temperature~~"( "*C^"o"*")"))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B",
                 limits = as.Date(c('2016-02-01','2017-08-27')))




```

Calculate TT with Tb= 15 .There will be lots of negative values as TB 15 is quite high... select only values above zero to accumulate thermal time.
Select experimental dates : 29 / 02/2016 - 20/08/2017

```{r}


df_fileTT <- df_file %>%
  subset(Date>"2016-02-28" & Date < "2017-08-20") %>%
  mutate(TTSoilSum= TempSoil10mm-15)%>%
  subset(TTSoilSum>0)

```



Calculate accumulated TT

```{r}

df_fileTT2 <- df_fileTT %>%
group_by(Date) %>%
summarise_all(funs(mean))%>%
  mutate(TT = cumsum(TTSoilSum))%>%
 # dplyr::select(-hour,-Air)
  dplyr::select(-TempSoil10mm)  

write.table(df_fileTT2, "ThermalSumSoilFieldBreak.txt")

```


Graph it 


```{r graph}

df_fileTT2 %>% 
ggplot(aes(x=Date, y= TT)) +
   #geom_point(colour= "darkblue", alpha=0.2) +
  geom_line()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  #geom_abline(intercept = 0, slope = 0)+
 xlab("Date") + 
  theme(axis.text.x=element_text(angle = 0, hjust = 0, size= 14))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 14))+
  ylab(expression(Daily~mean~soil~temperature~~"( "*C^"o"*")"))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B",
                 limits = as.Date(c('2016-02-01','2017-08-27')))

```


Here find mean temperature in period 1 _ (February to July 2016)


```{r}

df_fileP1 <- df_file %>%
  subset(Date>"2016-02-28" & Date < "2016-07-19") %>%
  
summarise_all(funs(mean))


df_fileP1 <- df_file %>%
  subset(Date>"2016-02-28" & Date < "2016-07-19") %>%
summarise_all(funs(max))


df_fileP1 <- df_file %>%
  subset(Date>"2016-02-28" & Date < "2016-07-19") %>%
summarise_all(funs(min))
```

July to November 
```{r}

df_fileP2 <- df_file %>%
  subset(Date>"2016-07-19" & Date < "2017-11-19") %>%
  
summarise_all(funs(mean))



df_fileP2 <- df_file %>%
  subset(Date>"2016-07-19" & Date < "2017-11-19") %>%
  
summarise_all(funs(max))



df_fileP2 <- df_file %>%
  subset(Date>"2016-07-19" & Date < "2017-03-08") %>%
  
summarise_all(funs(min))
```



```{r}

df_fileP3 <- df_file %>%
  subset(Date>"2017-03-08" & Date < "2017-08-20") %>%
  
summarise_all(funs(mean))


df_fileP3 <- df_file %>%
  subset(Date>"2017-03-08" & Date < "2017-08-20") %>%
  
summarise_all(funs(max))


df_fileP3 <- df_file %>%
  subset(Date>"2017-03-08" & Date < "2017-08-20") %>%
  
summarise_all(funs(min))

```


