---
title: "Graph Air and Soil Temperature"
author: "CT"
date: "21.12.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
Purpose: Correlate method to calculate soil temperature based on methdos by Langholz and Iversen2 measured data 

```{r}
library(tidyr)
library (dplyr)
library (ggplot2)
library (lubridate)
library (scales)
library(knitr)
```

Note: this file produces the graphs for estimated soil and Air temperatures using the Poukawa dataset 

```{r, load file}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Iv2_SoilAirTemp")
getwd()
#read soil and Air data 
df_file <- read.table("CompareSoilTempsMethods.txt", header=TRUE)


head(df_file)


str(df_file)


```



Then change date format and combine the two dataframes 

```{r}

df_S <- df_file %>%
  mutate(Date = dmy(Date)) %>%
  select(Date,Month,TAirMean,SoilTLangholz,SoilTIv2)%>%
  gather("VarName","Value",SoilTLangholz:SoilTIv2)




```

parei aqui 

Then graph methods by month  
 
```{r ,}

df_AS %>%
 #  select(Date, TempSoil10mm, MeanTt)%>%
 # summarise_each(funs(mean)) %>%
  ggplot(aes(x=MeanTt, y= TempSoil10mm))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  #geom_line(colour= "brown")+
  stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Mean~air~temperature~~"( "^"o"*"C)"))+ 
  ylab(expression(Mean~soil~temperature~~"( "^"o"*"C)"))+
  theme(text = element_text(size=10))

  # #scale_x_date(date_breaks = "3 month", 
  #                date_labels = "%B",
  #                limits = as.Date(c('2015-06-01','2017-07-07')))



```

then subset to fit an equation to estimate soil temperature from air temperature  paper 

```{r}

dfW <- df_AS%>%
  mutate(Tair=MeanTt)
  #subset(Date>"2015-07-27"  & Date<"2016-03-20")

dfW%>%
 #  select(Date, TempSoil10mm, MeanTt)%>%
 # summarise_each(funs(mean)) %>%
  ggplot(aes(x=MeanTt, y= TempSoil10mm))  +
  geom_point(colour= "black", alpha=0.2) +
  #geom_line(colour= "bl")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
   geom_smooth(method='lm',formula=y~x)+
  theme_bw() +
  xlab(expression(Mean~air~temperature~~"( "^"o"*"C)"))+ 
  ylab(expression(Mean~soil~temperature~~"( "^"o"*"C)"))+
  theme(text = element_text(size=20))
  #theme(title =  element_text(size=14))
  

  # #scale_x_date(date_breaks = "3 month", 
  #                date_labels = "%B",
  #                limits = as.Date(c('2015-06-01','2017-07-07')))



```


get a summary of the lm of the geom method

equation is y = a(intercept) +b (slope) x
```{r}
summary(lm(TempSoil10mm ~ MeanTt, dfW))
```

Overall Developed relationship between Air (x axis) and soil temperature (y axis) for Iversen: SoilT = 1.23 + 0.94AirTemp , R2=0.80.
 
Now do it every month (subset monthly) 



```{r}

#January 

dfJanuary<-dfW%>%
 subset(Date>"2015-12-31" & Date<"2016-01-31" )
  str(dfJanuary)

  ##apply the equation:  SoilT = 1.23 + 0.94AirTemp
 dfJanuary<-dfJanuary %>%
  select(Date,TempSoil10mm, Tair)%>%
   mutate(CoeffJan=(TempSoil10mm-1.23)/Tair)
 
 dfJanuary2<-dfJanuary %>%
 dplyr::select(CoeffJan)%>%
   summarise_all(funs(mean,sd))


```

## February

```{r}

dfFebruary<-dfW%>%
 subset(Date>"2016-01-31" & Date<"2016-03-01" )
  str(dfFebruary)

  ##apply the equation:  SoilT = 1.23 + 0.94AirTemp
 dfFebruary<-dfFebruary %>%
  select(Date,TempSoil10mm, Tair)%>%
   mutate(CoeffFeb=(TempSoil10mm-1.23)/Tair)
 
 dfFebruary2<-dfFebruary %>%
 dplyr::select(CoeffFeb)%>%
   summarise_all(funs(mean,sd))


```

##March 

```{r}

dfMarch<-dfW%>%
 subset(Date>"2016-02-29" & Date<"2016-04-01" )
  str(dfMarch)

  ##apply the equation:  SoilT = 1.23 + 0.94AirTemp
dfMarch<-dfMarch %>%
  select(Date,TempSoil10mm, Tair)%>%
   mutate(CoeffMar=(TempSoil10mm-1.23)/Tair)
 
 dfMarch2<-dfMarch %>%
 dplyr::select(CoeffMar)%>%
   summarise_all(funs(mean,sd))
  




```

##April 

```{r}

dfApril<-dfW%>%
 subset(Date>"2016-03-31" & Date<"2016-05-01" )
  str(dfApril)

  ##apply the equation:  SoilT = 1.23 + 0.94AirTemp
dfApril<-dfApril %>%
  select(Date,TempSoil10mm, Tair)%>%
   mutate(CoeffApr=(TempSoil10mm-1.23)/Tair)
 
 dfApril2<-dfApril %>%
 dplyr::select(CoeffApr)%>%
   summarise_all(funs(mean,sd))

```

##May

```{r}


dfMay <-dfW%>%
 subset(Date>"2016-04-30" & Date<"2016-06-01" )
  str(dfMay)

  ##apply the equation:  SoilT = 1.23 + 0.94AirTemp
dfMay<-dfMay %>%
  select(Date,TempSoil10mm, Tair)%>%
   mutate(CoeffMay=(TempSoil10mm-1.23)/Tair)
 
 dfMay2<-dfMay %>%
 dplyr::select(CoeffMay)%>%
   summarise_all(funs(mean,sd))

```


##June

```{r}

dfJune <-dfW%>%
 subset(Date>"2016-05-31" & Date<"2016-07-01" )
  str(dfJune)

  ##apply the equation:  SoilT = 1.23 + 0.94AirTemp
dfJune<-dfJune%>%
  select(Date,TempSoil10mm, Tair)%>%
   mutate(CoeffJune=(TempSoil10mm-1.23)/Tair)
 
 dfJune2<-dfJune %>%
 dplyr::select(CoeffJune)%>%
   summarise_all(funs(mean,sd))



```



##July

```{r}

dfJuly <-dfW%>%
 subset(Date>"2016-06-30" & Date<"2016-08-01" )
  str(dfJuly)

  ##apply the equation:  SoilT = 1.23 + 0.94AirTemp
dfJuly<-dfJuly%>%
  select(Date,TempSoil10mm, Tair)%>%
   mutate(CoeffJuly=(TempSoil10mm-1.23)/Tair)
 
 dfJuly2<-dfJuly %>%
 dplyr::select(CoeffJuly)%>%
   summarise_all(funs(mean,sd))



```

##August

```{r}
dfAugust <-dfW%>%
 subset(Date>"2016-07-30" & Date<"2016-09-01" )
  str(dfAugust)

  ##apply the equation:  SoilT = 1.23 + 0.94AirTemp
dfAugust<-dfAugust%>%
  select(Date,TempSoil10mm, Tair)%>%
   mutate(CoeffAug=(TempSoil10mm-1.23)/Tair)
 
 dfAugust2<-dfAugust %>%
 dplyr::select(CoeffAug)%>%
   summarise_all(funs(mean,sd))
```

##September 

```{r}

dfSeptember <-dfW%>%
 subset(Date>"2016-08-31" & Date<"2016-10-01" )
  str(dfSeptember)

  ##apply the equation:  SoilT = 1.23 + 0.94AirTemp
dfSeptember<-dfSeptember%>%
  select(Date,TempSoil10mm, Tair)%>%
   mutate(CoeffSept=(TempSoil10mm-1.23)/Tair)
 
 dfSeptember2<-dfSeptember %>%
 dplyr::select(CoeffSept)%>%
   summarise_all(funs(mean,sd))

```

##October 

```{r}

dfOctober <-dfW%>%
 subset(Date>"2016-09-30" & Date<"2016-11-01" )
  str(dfOctober)

  ##apply the equation:  SoilT = 1.23 + 0.94AirTemp
dfOctober<-dfOctober%>%
  select(Date,TempSoil10mm, Tair)%>%
   mutate(CoeffOct=(TempSoil10mm-1.23)/Tair)
 
 dfOctober2<-dfOctober %>%
 dplyr::select(CoeffOct)%>%
   summarise_all(funs(mean,sd))


```

##November 

```{r}

dfNovember <-dfW%>%
 subset(Date>"2016-10-31" & Date<"2016-12-01" )
  str(dfNovember)

  ##apply the equation:  SoilT = 1.23 + 0.94AirTemp
dfNovember<-dfNovember%>%
  select(Date,TempSoil10mm, Tair)%>%
   mutate(CoeffNov=(TempSoil10mm-1.23)/Tair)
 
 dfNovember2<-dfNovember %>%
 dplyr::select(CoeffNov)%>%
   summarise_all(funs(mean,sd))


```


##December 

```{r}
dfDecember <-dfW%>%
 subset(Date>"2016-10-31" & Date<"2016-12-01" )
  str(dfDecember)

  ##apply the equation:  SoilT = 1.23 + 0.94AirTemp
dfDecember<-dfDecember%>%
  select(Date,TempSoil10mm, Tair)%>%
   mutate(CoeffDec=(TempSoil10mm-1.23)/Tair)
 
 dfDecember2<-dfDecember %>%
 dplyr::select(CoeffDec)%>%
   summarise_all(funs(mean,sd))


```


End of this script _ Graphs in AirSoilTempCorrelate_Gaphs


get a summary of the lm of the geom method

equation is y = a(intercept) +b (slope) x
```{r}
# summary(lm(TempSoil10mm ~ MeanTt, dfJanuary))
```

