---
title: "Graph Air and Soil Temperature"
author: "CT"
date: "Friday, January 01, 2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---


```{r}
library(tidyr)
library (dplyr)
library (ggplot2)
library (lubridate)
library (scales)
library(gridExtra)
library(knitr)
```

Note: this file produces the graphs for soil and Air temperatures from hobologger data Iversen 2

```{r, load file}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Iv2_SoilAirTemp")
getwd()
#read soil and Air data 
df_file <- read.table("SoilTemp.txt", header=TRUE)
df_Air <- read.table("RawWeaIv2.txt", header=TRUE)

head(df_file)
tail (df_Air)
#keep this scirpt for the real weather data

str(df_Air)


```


graph air temperature (max, min mean and photoperiod)

```{r,fig.height=5, fig.width=15}

df_gather<-df_Air %>%
  select(Date,Tx,Tm,MeanTt,Pp)%>%
gather(key= "Variable" , value = "TempHour", Tx,Tm,MeanTt,Pp)%>%
  mutate(Date=dmy(Date))
  

df_gather%>%
  mutate(Variable=factor(Variable,levels=c("Tm","MeanTt","Tx","Pp"),labels = c("Tmin","Tmean","Tmax","Photoperiod")))%>%
 ggplot(aes(x=Date, y= TempHour)) +
  theme_bw()+
  geom_point(aes(colour=Variable,shape=Variable), alpha=0.8, size=3)+
  #geom_point()+
  scale_color_manual(values = c("steelblue3","orange","red", "gray20" ))+
  scale_shape_manual(values = c(15,16,17,18))+
  #geom_line(aes(colour=Variable))+
  #geom_smooth(aes(colour=Variable))+
  xlab(expression(Date~"(Month/Year)"))+
  
  ylab(expression(Air~Temperature~Photoperiod~"("^"o"*"C/hours)"))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B%Y",
                 limits = as.Date(c('2015-06-01','2017-07-07')))+
  theme(axis.text.y = element_text(size=14))+
  theme(axis.title.y = element_text(size=14))+
  theme(legend.text = element_text(size=14))+
  theme(axis.title.x = element_text(size=14))+
  ylim(0,35)
    
 #ggsave("plot_TempPpIversen.png", width=12, height=6, dpi=400)

```


do for soil temp 

```{r,  height=5, fig.width=15}

  str(df_file)

df_file%>%
  mutate(Date=dmy(Date))%>%
  #mutate(Variable=factor(Variable,levels=c("Tm","MeanTt","Tx","Pp"),labels = c("Tmin","Tmean","Tmax","Photoperiod")))%>%
 ggplot(aes(x=Date, y= TempSoil10mm)) +
  theme_bw()+
  #geom_point(aes(colour=Variable,shape=Variable), alpha=0.8, size=3)+
  geom_point(aes(),size=4)+
  scale_color_manual(values = c("gray20" ))+
  scale_shape_manual(values = c(15))+
  #geom_line(aes(colour=Variable))+
  #geom_smooth(aes(colour=Variable))+
  xlab(expression(Date~"(Month/Year)"))+
  
  ylab(expression(Soil~Temperature~"("^"o"*"C)"))+
  scale_x_date(date_breaks = "6 month", 
                 date_labels = "%B%Y",
                 limits = as.Date(c('2015-06-01','2017-07-07')))+
  theme(axis.text.y = element_text(size=18))+
  theme(axis.title.y = element_text(size=18))+
  theme(legend.text = element_text(size=18))+
  theme(axis.title.x = element_text(size=))+
  theme(axis.text.x = element_text(size=18))+
  ylim(0,25)
    
 ggsave("plot_SoilTempPpIversen.png", width=12, height=6, dpi=400)

```


```





```{r,fig.height=5, fig.width=15}

df_gather<-df_Air %>%
  select(Date,Tx,Tm,MeanTt,Pp)%>%
gather(key= "Variable" , value = "TempHour", Tx,Tm,MeanTt,Pp)%>%
  mutate(Date=dmy(Date))
  

df_gather%>%
  mutate(Variable=factor(Variable,levels=c("Tm","MeanTt","Tx","Pp"),labels = c("Tmin","Tmean","Tmax","Photoperiod")))%>%
 ggplot(aes(x=Date, y= TempHour)) +
  theme_bw()+
  geom_point(aes(colour=Variable,shape=Variable), alpha=0.8, size=3)+
  #geom_point()+
  scale_color_manual(values = c("steelblue3","orange","red", "gray20" ))+
  scale_shape_manual(values = c(15,16,17,18))+
  #geom_line(aes(colour=Variable))+
  #geom_smooth(aes(colour=Variable))+
  xlab(expression(Date~"(Month/Year)"))+
  
  ylab(expression(Air~Temperature~Photoperiod~"("^"o"*"C/hours)"))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B%Y",
                 limits = as.Date(c('2015-06-01','2017-07-07')))+
  theme(axis.text.y = element_text(size=14))+
  theme(axis.title.y = element_text(size=14))+
  theme(legend.text = element_text(size=14))+
  theme(axis.title.x = element_text(size=14))+
  ylim(0,35)
    
 #ggsave("plot_TempPpIversen.png", width=12, height=6, dpi=400)

```


subset S5 data (check with G Chamber data)




```{r,fig.height=5, fig.width=15}

df_gather<-df_Air %>%
  select(Date,Tx,Tm,MeanTt,Pp)%>%
gather(key= "Variable" , value = "TempHour", Tx,Tm,MeanTt,Pp)%>%
  mutate(Date=dmy(Date))
  

df_gather%>%
  mutate(Variable=factor(Variable,levels=c("Tm","MeanTt","Tx","Pp"),labels = c("Tmin","Tmean","Tmax","Photoperiod")))%>%
  filter(Variable=="Tmean")%>%
 ggplot(aes(x=Date, y= TempHour)) +
  theme_bw()+
  geom_point(aes(colour=Variable,shape=Variable), alpha=0.8, size=3)+
  #geom_point()+
  scale_color_manual(values = c("steelblue3","orange","red", "gray20" ))+
  scale_shape_manual(values = c(15,16,17,18))+
  geom_line(aes(colour=Variable))+
  #geom_smooth(aes(colour=Variable))+
  xlab(expression(Date~"(Month/Year)"))+
  
  ylab(expression(Air~Temperature~Photoperiod~"("^"o"*"C/hours)"))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B%Y",
                 limits = as.Date(c('2015-12-01','2016-05-07')))+
  theme(axis.text.y = element_text(size=14))+
  theme(axis.title.y = element_text(size=14))+
  theme(legend.text = element_text(size=14))+
  theme(axis.title.x = element_text(size=14))+
  ylim(0,35)
    
 #ggsave("plot_TempPpIversen.png", width=12, height=6, dpi=400)

```

```{r}
dfTT <- df_Air %>%
  select(Date, MeanTt)%>%
  mutate(Date=dmy(Date))%>%
  subset(Date>"2015-12-15"& Date<"2016-05-17")%>%
  mutate(TTsum=cumsum(MeanTt))
  


 dfTT %>% ggplot(aes(x=Date, y= TTsum))  +
   geom_line()+
  theme_bw()

```



Then graph soil 
 
```{r Soiltemp_mean}


g1<- df_file %>%
  mutate(Date = dmy(Date))%>% #(need to reformat date here)
  mutate(TempSoil10mm= as.numeric(TempSoil10mm))%>%
  #filter(year %in% 2015:2017) %>%
  group_by(Date) %>%
 summarise_all(funs(mean)) %>%
  ggplot(aes(x=Date, y= TempSoil10mm))  +
  #geom_point(colour= "darkblue", alpha=0.2) +
  geom_line(colour= "brown")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab("Date") + 
  ylab(expression(Mean~soil~temperature~~"("^"o"*"C)"))+
  theme(text = element_text(size=10))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B",
                 limits = as.Date(c('2015-06-01','2017-07-07')))



```

then graph Air 

```{r, fig.height=5, fig.width=8}


 df_Air %>%
  mutate(Date = dmy(Date))%>% #(need to reformat date here)
  #filter(year %in% 2015:2017) %>%
  group_by(Date) %>%
  summarise_each(funs(mean))%>%
  ggplot(aes(x=Date, y= MeanTt))  +
  #geom_point(colour= "darkblue", alpha=0.2) +
  geom_line(colour= "blue")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab("Date") + 
  theme(text = element_text(size=10))+
  ylab(expression(Mean~air~temperature~~"("^"o"*"C)"))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B",
                 limits = as.Date(c('2015-06-01','2017-07-07')))




```


then create an object g2 for the grid 
```{r}
g2 <-df_Air %>%
  mutate(Date = dmy(Date))%>% #(need to reformat date here)
  #filter(year %in% 2015:2017) %>%
  group_by(Date) %>%
  summarise_each(funs(mean))%>%
  ggplot(aes(x=Date, y= MeanTt))  +
  #geom_point(colour= "darkblue", alpha=0.2) +
  geom_line(colour= "blue")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
 xlab("Date") + 
  ylab(expression(Mean~air~temperature~~"("^"o"*"C)"))+
  theme(text = element_text(size=10))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B",
                 limits = as.Date(c('2015-06-01','2017-07-07'))) 



```


Then create a grid with two graphs 

```{r}


grid.arrange(g2, g1)



```



then continue in next script AirSoilTempCorrelat....


