
---
title: "Graph Air and Soil Temperature"
author: "CT"
date: "05.07.2017"
output: html_document
---
Purpose: Correlate soil and air temperature from Iversen 2 collected data 

```{r}
library(tidyr)
library (dplyr)
library (ggplot2)
library (lubridate)
library (scales)
```

Note: this file produces the graphs for soil and Air temperatures from hobologger data Iversen 2

```{r, load file}

setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\Iv2_SoilAirTemp")
getwd()
#read soil and Air data 
df_file <- read.table("SoilTemp.txt", header=TRUE)
df_Air <- read.table("RawWeaIv2.txt", header=TRUE)

head(df_file)
head (df_Air)
#keep this scirpt for the real weather data

str(df_Air)


```

Then change date format and combine the two dataframes 

```{r}

df_S <- df_file %>%
  mutate(Date = dmy(Date)) #(need to reformat date here)

df_A <-df_Air %>%
  mutate(Date = dmy(Date)) #(need to reformat date here)
  
  str(df_S)
  str(df_A)
  
df_AS <- merge(df_S,df_A, by="Date")
head(df_AS)

```



Then select only columns of interest 
 
```{r Soiltemp_andAirmean}

df_AS %>%
 #  select(Date, TempSoil10mm, MeanTt)%>%
 # summarise_each(funs(mean)) %>%
  ggplot(aes(x=MeanTt, y= TempSoil10mm))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  #geom_line(colour= "brown")+
  stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Mean~air~temperature~~"( "^"o"*"C)"))+ 
  ylab(expression(Mean~soil~temperature~~"( "^"o"*"C)"))+
  theme(text = element_text(size=10))

  # #scale_x_date(date_breaks = "3 month", 
  #                date_labels = "%B",
  #                limits = as.Date(c('2015-06-01','2017-07-07')))



```

the use geom ab line to see a stright line 


```{r, fig.height=5, fig.width=8}

df_AS %>%
 #select(Date, TempSoil10mm, MeanTt)%>%
 # summarise_each(funs(mean)) %>%
  ggplot(aes(x=MeanTt, y= TempSoil10mm))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  #geom_abline()+
  #stat_smooth (method = "lm",col = "darkblue") +
  stat_smooth (method = "lm",col = "darkblue", formula=y~x)+
  theme_bw() +
  xlab(expression(Mean~air~temperature~~"( "^"o"*"C)"))+
  ylab(expression(Mean~soil~temperature~~"( "^"o"*"C)"))+
  theme(text = element_text(size=10))

write.table(df_AS,"SoilAir.txt")


```

linear regression  
```{r}


#then try lm 

fit1 <- lm(TempSoil10mm ~ MeanTt, df_AS)
summary (fit1)

cf <- round(coef(fit), 2)




```


Then create a grid with two graphs 

```{r}


grid.arrange(g2, g1)



```



End of the script 


