---
title: "Correlate Air and Estimated Soil Temperature for Poukawa"
author: "CT"
date: "05.08.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---


```{r, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(lubridate)
library(scales)
library(knitr)
```

This file produces the estimated soil temperature based on  Air temperatures for Poukawa site. Air temperature was downloaded via ClifolNIWA and soil temperature estimated. 

```{r, load file}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Pok_SoilAirTemp")
getwd()



```

Read soil and Air data : Air temperature from NIWA Maraekakaho Cws (agent no. 40256)
Soil Temperature was calculated based on Langholz 1989 and Zheng et al 1993 for sand loam soils -Cfa climate : equation to estimate soil temperature was : Mean Soil Temp = 1.32 + b*Mean T air ; b are coefficients for each month of the year (values of b in publication Langholz 1989)

```{r}

df_file <- read.table("SoilTempPo.txt", header=TRUE)
df_Air <- read.table("RawWeaPok.txt", header=TRUE)

head(df_file)
head (df_Air)
#keep this scirpt for the real weather data

str(df_Air)
```


This step changes the  date format and combine the two dataframes 

```{r}

df_S <- df_file %>%
  mutate(Date = dmy(Date)) #(need to reformat date here)

df_A <-df_Air %>%
  mutate(Date = dmy(Date)) #(need to reformat date here)
  
  str(df_S)
  str(df_A)
  
df_AS <- merge(df_S,df_A, by="Date")
head(df_AS)

```


Then select only columns of interest for graphics 
 
```{r Soiltemp_andAirmean}

df_AS %>%
 #  select(Date, TempSoil10mm, MeanTt)%>%
 # summarise_each(funs(mean)) %>%
  ggplot(aes(x=MeanTt, y= TempSoil10mm))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  #geom_line(colour= "brown")+
  stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Mean~air~temperature~~"( "^"o"*"C)"))+ 
  ylab(expression(Mean~soil~temperature~~"( "^"o"*"C)"))+
  theme(text = element_text(size=10))

  # #scale_x_date(date_breaks = "3 month", 
  #                date_labels = "%B",
  #                limits = as.Date(c('2015-06-01','2017-07-07')))



```

Here used stat_smooth method Lm to see a more straight line 


```{r, fig.height=5, fig.width=8}

df_AS %>%
 #select(Date, TempSoil10mm, MeanTt)%>%
 # summarise_each(funs(mean)) %>%
  ggplot(aes(x=MeanTt, y= TempSoil10mm))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  #geom_abline()+
  #stat_smooth (method = "lm",col = "darkblue") +
  stat_smooth (method = "lm",col = "darkblue", formula=y~x)+
  theme_bw() +
  xlab(expression(Mean~air~temperature~~"( "^"o"*"C)"))+
  ylab(expression(Mean~estimate~soil~temperature~~"( "^"o"*"C)"))+
  theme(text = element_text(size=10))

write.table(df_AS,"SoilAirPo.txt")


```

Summary of  the linear regression  and R square values: multiple and adjusted 
```{r}


#then try lm 

fit1 <- lm(TempSoil10mm ~ MeanTt, df_AS)
summary (fit1)

#cf <- round(coef(fit), 2)




```





End of this script.
then continue in next script AirSoilGraph


