
---
title: "Graph Air and Estimated Soil Temperature Poukawa "
author: "CT"
date: "03.08.2017"
output: html_document
---
Aim: graph the air and estimated soil temperature in Poukawa. Check data.

```{r}
library(tidyr)
library (dplyr)
library (ggplot2)
library (lubridate)
library (scales)
library(gridExtra)
```

SoilTempPo was created based on Mean Air Temperature (excel file; Zheng et al 1993 and Langholz 1989 equations for sand loam soil; 50 mm depth: Cfa climate)

```{r, load file}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Pok_SoilAirTemp")
getwd()
#read soil and Air data 
df_file <- read.table("SoilTempPo.txt", header=TRUE)
df_Air <- read.table("RawWeaPok.txt", header=TRUE)

head(df_file)
head (df_Air)
#keep this scirpt for the real weather data

str(df_Air)


```

Graph of the estimated  soil temperature 
 
```{r Soiltemp_mean}


df_file %>%
  mutate(Date = dmy(Date))%>% #(need to reformat date here)
  #filter(year %in% 2015:2017) %>%
  group_by(Date) %>%
 summarise_each(funs(mean)) %>%
  ggplot(aes(x=Date, y= TempSoil10mm))  +
  #geom_point(colour= "darkblue", alpha=0.2) +
  geom_line(colour= "brown")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab("Date") + 
  ylab(expression(Mean~soil~temperature~~"("^"o"*"C)"))+
  theme(text = element_text(size=10))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B",
                 limits = as.Date(c('2016-02-01','2017-05-07')))



```

Graph of the daily mean  Air  temperature 

```{r, fig.height=5, fig.width=8}


 df_Air %>%
  mutate(Date = dmy(Date))%>% #(need to reformat date here)
  #filter(year %in% 2015:2017) %>%
  group_by(Date) %>%
  summarise_each(funs(mean))%>%
  ggplot(aes(x=Date, y= MeanTt))  +
  #geom_point(colour= "darkblue", alpha=0.2) +
  geom_line(colour= "blue")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab("Date") + 
  theme(text = element_text(size=10))+
  ylab(expression(Mean~air~temperature~~"("^"o"*"C)"))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B",
                 limits = as.Date(c('2016-06-01','2017-07-07')))




```




Create a grid with two graphs 

```{r}



g1 <-df_file %>%
  mutate(Date = dmy(Date))%>% #(need to reformat date here)
  group_by(Date) %>%
 summarise_each(funs(mean)) %>%
  ggplot(aes(x=Date, y= TempSoil10mm))  +
  #geom_point(colour= "darkblue", alpha=0.2) +
  geom_line(colour= "brown")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab("Month") + 
  ylab(expression(Mean~estimate~soil~temperature~~"("^"o"*"C)"))+
  theme(text = element_text(size=10))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B",
                 limits = as.Date(c('2016-02-01','2017-05-07')))


g2 <-df_Air %>%
  mutate(Date = dmy(Date))%>% #(need to reformat date here)
  #filter(year %in% 2015:2017) %>%
  group_by(Date) %>%
  summarise_each(funs(mean))%>%
  ggplot(aes(x=Date, y= MeanTt))  +
  #geom_point(colour= "darkblue", alpha=0.2) +
  geom_line(colour= "blue")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab("Month") + 
  theme(text = element_text(size=10))+
  ylab(expression(Mean~air~temperature~~"("^"o"*"C)"))+
  scale_x_date(date_breaks = "3 month", 
                 date_labels = "%B",
                 limits = as.Date(c('2016-02-01','2017-05-07')))


grid.arrange(g2, g1)



```


End of this script.
The next script AirSoilTempCorrelate graphs the two temperatures.


