---
title: "Hardseeds breakdown field"
author: "CT"
date: 07.09.2016"
output:
  word_document: default
  
---
Purpose : 
This script reads the raw data from the field seed hardness breakdown (buried mesh bags)

It finds the linear regressions for the cultivars according to selected time periods 

```{r loadLibraries}
library (lubridate)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library(rgr)
```

Read file and 
```{r, loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FieldBreakdown")
getwd()

#create file
df_seed <- read.table("FieldBreakdown.txt",header=TRUE)
str(df_seed)
summary(df_seed)





```

Adjust formats and calculate the percentage of germinated seeds 
```{r}
# change format with basic R 
#df_seed$Date <- dmy(df_seed$Date)


df_seed <- df_seed %>%
  mutate(Plot = as.factor(Plot), 
         Block = as.factor(Block),
         DAB = as.numeric(DAB),
      hardSeed = as.numeric(CumhardSeed))
  
str(df_seed)
#summary(df_seed) # explore values
  # check formats
  


```

Select the first period of decline in hardseeds : 0 - 145.

Then try to fit general  lm  for each cultivar )

Just change name of dataframe
```{r}
#Select depth of interest start with above seeds 

dfSubSet<- df_seed%>%
  subset (DAB<145) %>%
 dplyr::select(Plot, Cultivar, Block, DAB, hardSeed, TTSoilSum)
  
```

This loop finds the overall slope for TTSoilSum  

```{r}
all.data<-data.frame()
counter<-0
plots<-unique(dfSubSet$Plot)
#depth<-unique(dfSubSet$Depth)

length(plots)#*length(depth)
#p=d=1
for(p in 1:length(plots)) {
  #for(d in 1:length(depth)) {
  df_sub <- data.frame()  
   # print(paste0(plots[p],"_",depth[d]))
  #  counter<-counter+1
    
  df_sub <- dfSubSet %>% filter(Plot==plots[p]) # & Depth == depth[d])
  
  
  # Linear fit
  x <- df_sub$DAB
  y <- df_sub$hardSeed
  
  #print(data.frame(x=x,y=y))
  
  fit <- NULL
  fit <- lm(y ~ x)
  
  intercept <- round(fit$coefficients[[1]],2)
  slope <- round(fit$coefficients[[2]],3)
  r2 <- round(summary(fit)$r.squared * 100,2)
  # summary(fit)$adj.r.squared
  cv <- as.character(df_sub$Cultivar[1])
  block <- as.character(df_sub$Block[1])
  #sow <- as.character(df_sub$SowTreat[1])
  #sd <- dmy(df_sub$SowingD[1])
  
  
  buf <- data.frame(cv=cv, block=block, plot=plots[p], int=intercept, slope=slope, r2=r2, n=nrow(df_sub))
  
  all.data <- rbind(buf, all.data)
  
 # print(buf)
  
  #print(nrow(df_sub))
    
  #subset(dfSubSet, (dfSubSet$Plot==plots[p] & Depth == depth[d]))
    
  }
  


summary(all.data)

```

rename dataframe 
```{r}
  dfDABSlope1 <- all.data


```

Now run ANOVA to compare the rate (%hard/DAB) for each cultivar


```{r}


df_s<- dfDABSlope1

#-------------------------------------------------
# anova 
file <- df_s

file.subset <- file 

head(file.subset)
summary(file.subset)

```

```{r}

#ANOVA
my.anova <- aov(slope~ cv + block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
summary(my.anova)
```

```{r}

#(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))

(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
#Note LSD interaction from Genstat was calculated as 0.7029 



#(LSD.test(my.anova, c( "Temp"), alpha= 0.05, p.adj="none"))

```

get the R2 


```{r}

my.anova <- aov(r2~ cv + block, data = file.subset)
(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))

```

Now for th winter period - 145-380

Just change name of dataframe
```{r}
#Select depth of interest start with above seeds 

dfSubSet2<- df_seed%>%
  subset (DAB>140 & DAB<400) %>%
 dplyr::select(Plot, Cultivar, Block, DAB, hardSeed, TTSoilSum)
  
```

This loop finds the overall slope for TTSoilSum  

```{r}
all.data<-data.frame()
counter<-0
plots<-unique(dfSubSet2$Plot)
#depth<-unique(dfSubSet$Depth)

length(plots)#*length(depth)
#p=d=1
for(p in 1:length(plots)) {
  #for(d in 1:length(depth)) {
  df_sub <- data.frame()  
   # print(paste0(plots[p],"_",depth[d]))
  #  counter<-counter+1
    
  df_sub <- dfSubSet2 %>% filter(Plot==plots[p]) # & Depth == depth[d])
  
  
  # Linear fit
  x <- df_sub$DAB
  y <- df_sub$hardSeed
  
  #print(data.frame(x=x,y=y))
  
  fit <- NULL
  fit <- lm(y ~ x)
  
  intercept <- round(fit$coefficients[[1]],2)
  slope <- round(fit$coefficients[[2]],3)
  r2 <- round(summary(fit)$r.squared * 100,2)
  # summary(fit)$adj.r.squared
  cv <- as.character(df_sub$Cultivar[1])
  block <- as.character(df_sub$Block[1])
  #sow <- as.character(df_sub$SowTreat[1])
  #sd <- dmy(df_sub$SowingD[1])
  
  
  buf <- data.frame(cv=cv, block=block, plot=plots[p], int=intercept, slope=slope, r2=r2, n=nrow(df_sub))
  
  all.data <- rbind(buf, all.data)
  
 # print(buf)
  
  #print(nrow(df_sub))
    
  #subset(dfSubSet, (dfSubSet$Plot==plots[p] & Depth == depth[d]))
    
  }
  


summary(all.data)

```


rename dataframe 
```{r}
  dfDABSlope2 <- all.data


```

Now run ANOVA to compare the rate (%hard/DAB) for each cultivar


```{r}


df_s<- dfDABSlope2

#-------------------------------------------------
# anova 
file <- df_s

file.subset <- file 

head(file.subset)
summary(file.subset)

```

```{r}

#ANOVA
my.anova <- aov(slope~ cv + block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
summary(my.anova)
```

```{r}

#(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))

(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
#Note LSD interaction from Genstat was calculated as 0.7029 



#(LSD.test(my.anova, c( "Temp"), alpha= 0.05, p.adj="none"))

```

get the R2 


```{r}

my.anova <- aov(r2~ cv + block, data = file.subset)
(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))

```

And do the same for the period 380 - 540 (third part )

Just change name of dataframe
```{r}
#Select depth of interest start with above seeds 

dfSubSet3<- df_seed%>%
  subset (DAB>371 ) %>%
 dplyr::select(Plot, Cultivar, Block, DAB, hardSeed, TTSoilSum)
  
```

This loop finds the overall slope for TTSoilSum  

```{r}
all.data<-data.frame()
counter<-0
plots<-unique(dfSubSet3$Plot)
#depth<-unique(dfSubSet$Depth)

length(plots)#*length(depth)
#p=d=1
for(p in 1:length(plots)) {
  #for(d in 1:length(depth)) {
  df_sub <- data.frame()  
   # print(paste0(plots[p],"_",depth[d]))
  #  counter<-counter+1
    
  df_sub <- dfSubSet3 %>% filter(Plot==plots[p]) # & Depth == depth[d])
  
  
  # Linear fit
  x <- df_sub$DAB
  y <- df_sub$hardSeed
  
  #print(data.frame(x=x,y=y))
  
  fit <- NULL
  fit <- lm(y ~ x)
  
  intercept <- round(fit$coefficients[[1]],2)
  slope <- round(fit$coefficients[[2]],3)
  r2 <- round(summary(fit)$r.squared * 100,2)
  # summary(fit)$adj.r.squared
  cv <- as.character(df_sub$Cultivar[1])
  block <- as.character(df_sub$Block[1])
  #sow <- as.character(df_sub$SowTreat[1])
  #sd <- dmy(df_sub$SowingD[1])
  
  
  buf <- data.frame(cv=cv, block=block, plot=plots[p], int=intercept, slope=slope, r2=r2, n=nrow(df_sub))
  
  all.data <- rbind(buf, all.data)
  
 # print(buf)
  
  #print(nrow(df_sub))
    
  #subset(dfSubSet, (dfSubSet$Plot==plots[p] & Depth == depth[d]))
    
  }
  


summary(all.data)

```


rename dataframe 
```{r}
  dfDABSlope3 <- all.data


```

Now run ANOVA to compare the rate (%hard/DAB) for each cultivar


```{r}


df_s<- dfDABSlope3

#-------------------------------------------------
# anova 
file <- df_s

file.subset <- file 

head(file.subset)
summary(file.subset)

```

```{r}

#ANOVA
my.anova <- aov(slope~ cv + block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
summary(my.anova)
```

```{r}

#(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))

(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
#Note LSD interaction from Genstat was calculated as 0.7029 



#(LSD.test(my.anova, c( "Temp"), alpha= 0.05, p.adj="none"))

```

get the R2 


```{r}

my.anova <- aov(r2~ cv + block, data = file.subset)
(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))

```


