---
title: "Hardseeds Slopes 6CV"
author: "CT"
date: "Tuesday, July 19, 2016"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(markdown)
library (gridExtra)

```
this script combines the maximum hardseeds (14 days test) and the slopes of breakdown (% per day) and graph the two variables  

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
df_maxhard <- read.table("Maxhardness.txt",header=TRUE)
dftemp <-  read.table ("df_slopesBreak.txt",header = TRUE)
df_slopesbreak<-dftemp %>% dplyr::rename(Plot=plot, Depth=depth)
```

merge the two dataframes
```{r}
#Select depth of interest start with above seeds 
df_merged <- merge(df_maxhard,df_slopesbreak, by=c("Plot", "Depth")) %>% dplyr::select(Plot:SowTreat, Hard_perc,slope)

summary(df_merged)
  
```
now get the mean values 
```{r}
df_merged_av <- df_merged %>%
  group_by(Cultivar,SowTreat) %>%
  dplyr::select(Cultivar,SowTreat,slope,Hard_perc) %>%
  summarise_all(funs(mean,sd)) 

summary(df_merged_av)
```

```{r, fig.height=5,fig.width=10}
df_merged_av %>%
  mutate(slope_mean=(slope_mean*-1))%>%
  ggplot(aes(x=slope_mean,y=Hard_perc_mean))+
  geom_point(aes(colour=Cultivar,shape=SowTreat),size=4) +
  geom_smooth(fill="blue",alpha=0.1,method='lm') +
  theme_bw()+
  xlab("Hard seedness decay (%/Tt)")+ylab("Hard seed maximum (%)") +
   geom_errorbar(aes(ymin=Hard_perc_mean-Hard_perc_sd/2.45,
                    ymax=Hard_perc_mean+Hard_perc_sd/2.45),colour="grey")+

geom_errorbarh(aes(xmin=slope_mean-slope_sd/2.45,
                    xmax=slope_mean+slope_sd/2.45),colour="grey") + coord_flip()
```

now get the slopes and modify for TT based on each day represent a 17.1 oCd (1680/98days)
FIX ME : re calculate slope TT per day and adjust Sd. 

```{r}

df_merged_av_Modified <- df_merged %>%
mutate(slope=((slope/17.1)*-1))%>%
group_by(Cultivar,SowTreat) %>%
  dplyr::select(Cultivar,SowTreat,slope,Hard_perc) %>%
  summarise_all(funs(mean,sd)) 

df_merged_av_Modified %>%
  ggplot(aes(x=slope_mean,y=Hard_perc_mean))+
  geom_point(aes(colour=Cultivar),size=4) +
  geom_smooth(fill="blue",alpha=0.1,method='lm') +
  theme_bw()+
  xlab("Hard seedness decay (%/oCd)")+ylab("Hard seed maximum (%)") +
   geom_errorbar(aes(ymin=Hard_perc_mean-Hard_perc_sd/2.45,
                    ymax=Hard_perc_mean+Hard_perc_sd/2.45),colour="grey")+

geom_errorbarh(aes(xmin=slope_mean-slope_sd/2.45,
                    xmax=slope_mean+slope_sd/2.45),colour="grey") + coord_flip()

```


now analyse with slopes of thermal time

```{r}

dfTTbreak <-  read.table ("df_slopesBreakTT.txt",header = TRUE)

df_slopesbreak<-dfTTbreak %>% dplyr::rename(Plot=plot, Depth=depth)

```


merge the two dataframes
```{r}
#Select depth of interest start with above seeds 
df_mergedTT <- merge(df_maxhard,df_slopesbreak, by=c("Plot", "Depth")) %>% dplyr::select(Plot:SowTreat, Hard_perc,slope)

summary(df_mergedTT)
  
```

now get the mean values 
```{r}
df_merged_avTT <- df_mergedTT %>%
  group_by(Cultivar,SowTreat) %>%
  dplyr::select(Cultivar,SowTreat,slope,Hard_perc) %>%
  summarise_all(funs(mean,sd)) 

summary(df_merged_avTT)
```

now graph 
```{r, fig.height=5,fig.width=10}
df_merged_avTT %>%
  mutate(slope_mean=(slope_mean*-1))%>%
  ggplot(aes(x=slope_mean,y=Hard_perc_mean))+
  geom_point(aes(colour=Cultivar),size=4) +
  geom_smooth(fill="blue",alpha=0.1,method='lm') +
  theme_bw()+
  xlab("Hard seedness decay (%/TT)")+ylab("Hard seed maximum (%)") +
   geom_errorbar(aes(ymin=Hard_perc_mean-Hard_perc_sd/2.45,
                    ymax=Hard_perc_mean+Hard_perc_sd/2.45),colour="grey")+

geom_errorbarh(aes(xmin=slope_mean-slope_sd/2.45,
                    xmax=slope_mean+slope_sd/2.45),colour="grey") + coord_flip()
```
join the two graphs in one panel 

```{r, fig.height=5, fig.width=10}

fontSize <- 12.0

#g1 is for the slopes per day 
  g1 <- df_merged_av %>%
  mutate(slope_mean=(slope_mean*-1))%>%
  ggplot(aes(x=slope_mean,y=Hard_perc_mean))+
  geom_point(aes(colour=Cultivar),size=4) +
  geom_smooth(fill="blue",alpha=0.1,method='lm') +
  theme_bw()+
  xlab("Hard seedness decay (%/day)")+ylab("Hard seed maximum (%)") +
   geom_errorbar(aes(ymin=Hard_perc_mean-Hard_perc_sd/2.45,
                    ymax=Hard_perc_mean+Hard_perc_sd/2.45),colour="grey")+

geom_errorbarh(aes(xmin=slope_mean-slope_sd/2.45,
                    xmax=slope_mean+slope_sd/2.45),colour="grey") + coord_flip()

# g2 is for slopes per TT 
  g2 <- df_merged_avTT %>%
  mutate(slope_mean=(slope_mean*-1))%>%
  ggplot(aes(x=slope_mean,y=Hard_perc_mean))+
  geom_point(aes(colour=Cultivar),size=4) +
  geom_smooth(fill="blue",alpha=0.1,method='lm') +
  theme_bw()+
  xlab("Hard seedness decay (%/TT)")+ylab("Hard seed maximum (%)") +
   geom_errorbar(aes(ymin=Hard_perc_mean-Hard_perc_sd/2.45,
                    ymax=Hard_perc_mean+Hard_perc_sd/2.45),colour="grey")+

geom_errorbarh(aes(xmin=slope_mean-slope_sd/2.45,
                    xmax=slope_mean+slope_sd/2.45),colour="grey") + coord_flip()
    
    
    
  grid.arrange(g1, g2)
# 

# 


```



