---
title: "Hardseeds Slopes 6CV"
author: "CT"
date: " 27 November, 2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
Purpose: this script calculates the differential in hardseed  based on percent of hardseeds initially (Max hardseeds at day 14 or TTsum = 0) and at the final incubation day (98 days, TTsum = 1680) 

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(markdown)

```

Get the dataframe 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")

#create file
df_seed <- read.table("dfHard_break.txt",header=TRUE)
head(df_seed)



```

Thermal sum 

```{r}
# get TT at each  day
#create file
df_Tt <- read.table("dfHard_breakTT.txt",header=TRUE) %>% dplyr::select(Days,TtSum) %>% unique()
head(df_Tt)


```

```{r}
plot(df_Tt)
```



Just change name of dataframe and select columns to work 
```{r}
#Select depth of interest start with above seeds 

df_temp <- df_seed %>%
 mutate(Days=Round) %>%
 dplyr::select(Plot, Cultivar, Block, SowingD, SowTreat, Days, Depth, HardAccum, Round) 

dfSubSet <- merge(df_temp, df_Tt, by="Days")

dfSubSet$LoopIndex <- as.factor(paste0(dfSubSet$Plot,"_",dfSubSet$Depth)) # prepare for loop below

summary(dfSubSet)
  
```



```{r, fig.height= 12, fig.width=12}
#change data frame name and Graph Breakdown live hard seeds 

#df_cum_soft<- df_Dif2


dfSubSet%>%
  mutate(SowingD = dmy(SowingD)) %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  mutate(Cultivar= factor(Cultivar, 
                           levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),
                           labels=c("A", "D", "L", "M", "N.", "W"))) %>%
  #filter(Round == 14) %>%
  
  group_by(Cultivar, SowTreat,TtSum) %>%
  
  dplyr::select(HardAccum) %>%

  summarise_all(funs(mean,sd)) %>%
 
  
  ggplot(aes(x=TtSum, y=mean, colour=Cultivar, shape=Cultivar)) +
  geom_point(size=1,alpha=0.1) +
  geom_text(aes(label=Cultivar),hjust=0, vjust=0,size=7) +
  geom_line() +
 facet_grid(.~SowTreat) +
  labs(y=" Percentage of Hardseeds (%)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                 # geom_errorbar(aes(ymin=mean-sd/3.46,
                   # ymax=mean+sd/3.46))+
  theme_bw()+
  ylim(0,100)+
  xlim(0,2200)+
  #ylab(expression(Percentage~of~Hardseeds~"(%)"))+
  xlab(expression(Accumulated~Thermal~time~"("^"o"*"Cd)"))+
  #theme(text = element_text(size=12))+
  #xlab(expression(Days))+
  theme(axis.text.x=element_text(angle = 45, hjust = 0.5, size= 14))+
#  theme(axis.text.x = element_text(margin = margin(t = 0, r = 1, b = 0.8, l = 0)))+
  
    #margin y axis
   theme (axis.text.x = element_text( margin = margin(t=10,r=0,b=0,l=0)))+
  
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 16))+
  
  theme(axis.text.y=element_text(angle = 0, hjust = 0.5, size= 12))+
  theme(axis.title.y=element_text(angle = 90, hjust = 0.5, size= 16))+
#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  theme(text = element_text(size=20))+
   
   
   #make TT target labels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))
  
ggsave("plots_OverTtSum_PercentHardseeds.tiff", width=14, height=6, dpi=500)




```


new graph

```{r, fig.height= 14, fig.width=14}
#change data frame name and Graph Breakdown live hard seeds 

#df_cum_soft<- df_Dif2


Graphic<- dfSubSet%>%
  mutate(SowingD = dmy(SowingD)) %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  #mutate(Cultivar= factor(Cultivar, 
                           #levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),
                           #labels=c("A", "D", "L", "M", "N.", "W"))) %>%
  #filter(Round == 14) %>%
  
  group_by(Cultivar, SowTreat,TtSum) %>%
  
  dplyr::select(HardAccum) %>%

  summarise_all(funs(mean,sd))




dfError<- Graphic%>%
  group_by(SowTreat)%>%
  summarise(SE=max(sd)/3.46)%>%
  mutate(TtSum=2000,mean=100) %>%
  ungroup()

##x=2000
##y=100
  
 
  Graphic %>%
  ggplot(aes(x=TtSum, y=mean)) +
  #ggplot(aes(x=TtSum, y=mean, shape=Cultivar)) +
  geom_point(size=6, aes(colour=Cultivar, shape=Cultivar)) +
  #geom_text(aes(label=Cultivar),hjust=0, vjust=0,size=7) +
  geom_line(aes(colour=Cultivar)) +
   # geom_point(data = dfError,aes(x=2000,y=100))+
  geom_errorbar(data=dfError, aes(ymin=mean-SE,ymax=mean+SE),width=150)+
   
 #facet_grid(.~SowTreat) +
  facet_wrap(~SowTreat, ncol=2) +
  

  labs(y=" Percentage of Hardseeds (%)") +
  
  theme_bw()+
  ylim(0,130)+
   xlim(0,2400)+
  
  xlab(expression(Accumulated~Thermal~time~"("^"o"*"Cd)"))+
    geom_abline(intercept = 50,  slope = 0, linetype=2)+

# #remove grid lines 
    theme(
      panel.border = element_rect(colour = "black", size = 2), 
      panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
      axis.line = element_line(colour = "black"))+
   theme(text = element_text(size=26))+
    theme(axis.text.x = element_text(angle = 60, hjust = 1, size=22))+
    
#    
#    
#    #make TT target labels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))
  
#ggsave("plots_14HardPrjt_New_OverTtSum_PercentHard.tiff", width=12, height=8, dpi=500)

ggsave("plots_14HardPrjt_ReNew_OverTtSum_PercentHard.tiff", width=16, height=16, dpi=500)


```


try create a graph with maX SE (later if time allows )



```{r}


#produce means first 




#then create the error bar position
#Here how to create the end error bar with max Sd 
# find size of bar per cultivar and temp
# find single position of x y to put the bar
str(dfSubSet)
#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.1 # extra position for single error bar
x_max<-max(dfSubSet$TtSum)
y_max<-max(dfSubSet$mean)


sd_df <- dfSubSet %>% 
  group_by(Cultivar) %>%
  dplyr::select(sd)%>%
  summarise_all(funs(max))%>%
  #summarise(max_sd = max(sd)) %>% 
  ungroup() %>%
  rowwise() %>%
  mutate(TtSum = x_max*extraPos, mean = y_max*extraPos, max_sd=sd)

summary(sd_df)


##then replicat graph

dfSubSet%>%
  mutate(SowingD = dmy(SowingD)) %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  #filter(Round == 14) %>%
  group_by(Cultivar, SowTreat,TtSum) %>%
  dplyr::select(HardAccum) %>%
  summarise_all(funs(mean,sd)) %>%
  ggplot(aes(x=TtSum, y=mean, colour=Cultivar, shape=Cultivar)) +
  geom_point(size=3) +
  geom_line() +
 facet_grid(.~SowTreat) +
  labs(y=" Percentage of Hardseeds(%)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=mean-sd/3.46,
                    ymax=mean+sd/3.46))+
  theme_bw()+
  ylim(0,100)+
  xlim(0,2200)+
  #ylab(expression(Percentage~of~Hardseeds~"(%)"))+
  xlab(expression(Accumulated~Thermal~time~"("^"o"*"Cd)"))+
  #theme(text = element_text(size=12))+
  #xlab(expression(Days))+
  theme(axis.text.x=element_text(angle = 45, hjust = 0.5, size= 14))+
#  theme(axis.text.x = element_text(margin = margin(t = 0, r = 1, b = 0.8, l = 0)))+
  
    #margin y axis
   theme (axis.text.x = element_text( margin = margin(t=10,r=0,b=0,l=0)))+
  
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 16))+
  
  theme(axis.text.y=element_text(angle = 0, hjust = 0.5, size= 12))+
  theme(axis.title.y=element_text(angle = 90, hjust = 0.5, size= 16))+
#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  theme(text = element_text(size=20))+
   
   
   #make TT target labels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))
  
#ggsave("plots_OverTtSum_PercentHardseeds.tiff", width=14, height=6, dpi=500)



```





graph hardseed decay with thermal time - data exploration

```{r}
 
df_graf <-dfSubSet %>%
  group_by(Cultivar,SowingD, SowTreat, TtSum) %>%
  dplyr::select(HardAccum) %>%
  summarise_all(funs(mean,sd)) 


df_graf %>%
  filter(SowTreat=="S2")%>%
  filter(Cultivar=="Antas"| Cultivar=="Monti" )%>%
ggplot(aes(x=TtSum , y=mean, colour=Cultivar, shape=Cultivar)) +
  geom_point(size=3) +
  geom_line() +
 #facet_grid(Depth~SowTreat) +
  labs(x="TT",y=" Percentage of LiveHardseeds") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=mean-sd/3.46,
                    ymax=mean+sd/3.46),width=1,
                      size=0.4)+
  theme_bw()+
  ylim(0,100)+
  xlim(0,1900)+
  ylab(expression(Percentage~of~Hardseeds~"(%)"))+
  #theme(text = element_text(size=12))+
  xlab(expression(Thermal~time ~"("^"o"*"Cd)"))+
  theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 11))+
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 16))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 12))+
  theme(axis.title.y=element_text(angle = 90, hjust = 0.5, size= 16))

#ggsave("plot_Antas_Narrikup.png", width=12, height=6, dpi=400)
```

Select only intial and final days to calculate differential 


```{r}

str(dfSubSet)

df_Dif <-dfSubSet %>%
  filter(Round=="14"|Round=="98")%>%
  mutate (Round = as.character(Round))

#Spread Round to calculate the differencet the beggining and at the end of the incubation 

## Dif = HardAccum14 - HardAccum98 / days or TT  

df_Dif1<- df_Dif %>%
  dplyr:: select(LoopIndex,Round,HardAccum) %>%
  spread(Round, HardAccum)

#Change column names 
colnames(df_Dif1)<- c("LoopIndex", "HardPerc_Initial14", "HardPerc_End98") 

#Calculate the difference 
  df_Dif2<-df_Dif1 %>%
    mutate(Difference=HardPerc_Initial14-HardPerc_End98)

  str(df_Dif2)
  


```



Now bring the differential values to the main dataframe dfSubSet


```{r}

#Prepare data frame 1 with all column names-factors  :

#Days   Plot   Cultivar Block   SowingD    SowTreat   Depth  HardAccum 
df_A <-dfSubSet %>%
  filter(Round=="14")%>%
 dplyr:: select(Plot,Block,Cultivar:Depth, LoopIndex)
  
#bring dataframe with Differential values 
str(df_Dif2)

#merge dataframes by Loopindex 

df_Dif3 <- merge(df_A, df_Dif2, by= "LoopIndex")




```

Calculate diferential divided by TT sum 

```{r}

df_Dif3 <-df_Dif3 %>%
  mutate(RateDecreasePerDay= Difference/98)%>%
  mutate(RateDecreasePerTTunit= Difference/1680)



```

```{r}


##write table with data to work with correlations in next scripts 

write.table(df_Dif3, "MaxHardAndRate_Diff.txt")

```


Select only S2 to combine with the spectra dataset for chapter 6 


```{r}

df_Dif3_S2 <-df_Dif3 %>%
  mutate(RateDecreasePerDay= Difference/98)%>%
  mutate(RateDecreasePerTTunit= Difference/1680)%>%
filter (SowTreat =="S2")
  

write.table(df_Dif3_S2, "S2Only_MaxHardAndRate_Diff.txt")

summary (df_Dif3)

df_Dif3ByPlot <-df_Dif3 %>%
group_by(Plot)%>%
  dplyr::select(HardPerc_Initial14, RateDecreasePerTTunit)%>%
  summarise_all(funs(mean,sd))
  
write.table(df_Dif3ByPlot, "HSmax_HSbreakByPlot.txt")



```

Check if means are making sense 


```{r}

str(df_Dif3)

MeanHardEnd <-df_Dif3 %>%
  group_by(Cultivar, SowTreat)%>%
  filter(SowTreat=="S2") %>%
  #select(End98)%>%
  dplyr::select(HardPerc_Initial14, RateDecreasePerDay ) %>%
  summarise_all(funs(mean,sd))
  

```

###### Graphics ######


```{r, fig.height=5, fig.width=15}
##This is a bar graph not in use at the moment 

# df_graf2 <-df_Dif3
#   
# 
# # define position of bar and errorbar
# dodge_x <- position_dodge(width = 0.9)
# 
# df_graf2 %>%
#   group_by(Cultivar, SowTreat, Depth)%>%
#   dplyr::select(Difference) %>%
#   #dplyr::select(  RateDecreasePerDay) %>%
#   summarise_all(funs(mean,sd))%>%
#   ungroup %>%
#   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6", "S7"),labels=c("June", "July", "September", "November", "February", "March")))%>%
#      #added ....here mutate cultivar labels for poster  
#    mutate (Cultivar= factor(Cultivar, levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),labels=c("A", "D", "L", "M", "N","W")))%>%
#   #filter(SowTreat=="S2")%>%
#   #filter(Cultivar=="Antas"| Cultivar=="Monti" )%>%
#   #filter(TtSum=="0"| TtSum=="1680" )%>%
# #mutate (TtSum= factor(TtSum, levels=c("0", "1680"),labels=c("DAY 0 ", "DAY 84")))%>%
#  ggplot(aes(x=Cultivar, y=mean, fill=Cultivar)) +
#   #geom_bar(stat="identity",position = dodge_x) +
#   geom_bar(aes(fill=Cultivar), colour="black",stat="identity",position = dodge_x)+
#   geom_errorbar(aes(ymin=mean-sd/3.46,
#                     ymax=mean+sd/3.46),
#                 width=0.25, size=0.3,position=dodge_x)   +
#   theme_bw(base_size = 16) +
#     theme_bw()+
#   facet_grid(Depth~SowTreat, scales="free") +
#     scale_fill_brewer(palette="Blues")+
#     labs(y= " Decrease in Hardseed  (%) ")+
# theme(axis.text.y = element_text( size = 11))+
#   #theme(axis.title.y = element_text(face="bold", size=14))+
# theme(axis.text.x=element_text(angle = 0, hjust=0.95,vjust=0.2,size = 24)) +
#   theme(text = element_text(size = 20))+
# 
# 
# #remove grid lines 
#      theme(
#      panel.border = element_rect(colour = "black", size = 2), 
#      panel.grid.major = element_blank(),
#      panel.grid.minor = element_blank(),
#      axis.line = element_line(colour = "black"))+
#   
#   #make sowing dates white  
#    theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
#    theme(text = element_text(size = 24))+
#     
#    scale_y_continuous(expand = c(0, 0), limits = c(0, 50))
# 
# 
#         #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
#    
#     #margin y axis
#    theme (axis.title.y = element_text( margin = margin(t=0,r=10,b=0,l=0)))
#     
#    
#      
#     #ylab(expression(Number~of~seeds/m^"2")) 

```



```{r, fig.height=7, fig.width=15}

##Graph the Rate of Hardseedbreakdown /day 

str(df_Dif3)

df_graf2 <-df_Dif3
  

# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

df_graf2 %>%
  group_by(Cultivar, SowTreat, Depth)%>%
  dplyr::select(RateDecreasePerDay) %>%
  #dplyr::select(  RateDecreasePerDay) %>%
  summarise_all(funs(mean,sd))%>%
  ungroup %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6", "S7"),labels=c("June", "July", "September", "November", "February", "March")))%>%
     #added ....here mutate cultivar labels for poster  
  # mutate (Cultivar= factor(Cultivar, levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),labels=c("A", "D", "L", "M", "N","W")))%>%
  #filter(SowTreat=="S2")%>%
  #filter(Cultivar=="Antas"| Cultivar=="Monti" )%>%
  #filter(TtSum=="0"| TtSum=="1680" )%>%
#mutate (TtSum= factor(TtSum, levels=c("0", "1680"),labels=c("DAY 0 ", "DAY 84")))%>%
 ggplot(aes(x=SowTreat, y=mean)) +
  #geom_bar(stat="identity",position = dodge_x) +
  #geom_bar(aes(fill=Cultivar), colour="black",stat="identity",position = dodge_x)+
  geom_point(aes(shape=Depth), size=5)+
  geom_line()+
  scale_shape(solid = FALSE)+
  geom_errorbar(aes(ymin=mean-sd/3.46,
                    ymax=mean+sd/3.46),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_bw(base_size = 16) +
    theme_bw()+
  facet_grid(Depth~., scales="free") +
    #scale_fill_brewer(palette="Blues")+
    labs(y= "  Hardseed Breakdown rate (%/day) ")+
theme(axis.text.y = element_text( size = 12))+
 # theme(axis.title.y = element_text(face="bold", size=14))+
theme(axis.text.x=element_text(angle = 0, hjust=0.5,vjust=0.2,size = 22)) +
  theme(text = element_text(size = 20))+


#remove grid lines 
     theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
  #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
   theme(text = element_text(size = 24))+
  
    
   scale_y_continuous(expand = c(0, 0), limits = c(-0.1, 0.58))


        #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
    #margin y axis
   theme (axis.title.y = element_text( margin = margin(t=0,r=10,b=0,l=0)))
    
   
     
    #ylab(expression(Number~of~seeds/m^"2")) 
   
   # Save
#ggsave("plot_Rate_HardseedBreakPerDay.tiff", width=14, height=7, dpi=500)
   

```




```{r, fig.height=8, fig.width=12}

#Graph the maximum percentage of Live hardseeds!!! Here graph already show SE sd/3,.46 n = 3.

str( df_graf2)

  df_graf2 %>%
  mutate(SowingD = dmy(SowingD)) %>%
  group_by(Cultivar, SowTreat, Depth, SowingD)%>%
  dplyr::select(RateDecreasePerTTunit) %>%
  #dplyr::select(  RateDecreasePerDay) %>%
  summarise_all(funs(mean,sd))%>%
  ungroup %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6", "S7"),labels=c("Jun", "Jul", "Sept", "Nov", "Feb", "Mar")))%>%
  ggplot(aes(x=SowingD, y=mean, colour=Depth,linetype=Depth, shape=Depth)) +
  scale_color_manual(values = c("Above" = "black", "Below" = "grey"))+
  #scale_shape(solid = FALSE)+
  geom_point(size=6) +
  geom_line() +
 facet_wrap(~Cultivar,ncol=2) +
  labs(x="Sowing date") +
  ylab(expression(Average~breakdown~rate~"( % units per "^"o"*"Cd)"))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=mean-sd/3.46,
                    ymax=mean+sd/3.46))+
  theme_bw()+
  ylim(0,0.038)+
  #scale_x_date(breaks = "3 month")+
  theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 22))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 22))+
  
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  theme(text = element_text(size=24))+
   
   
   #make TT target labels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))
  
#ggsave("plots_HardSeedBreakdown_Tt.tiff", width=15, height=8, dpi=500)
ggsave("plots_Prjct14_HardSeedBreakdown_Tt.tiff", width=16, height=16, dpi=500)

```

##Graph the quadrant scheme with HardMax and Breakdown 




```{r, fig.height=8, fig.width=12}

#Graph the maximum percentage of Live hardseeds!!! Here graph already show SE sd/3,.46 n = 3.

str( df_graf2)

  Average <- df_graf2 %>%
  mutate(SowingD = dmy(SowingD)) %>%
  group_by(Cultivar, SowTreat, SowingD)%>%
  dplyr::select(RateDecreasePerTTunit,  HardPerc_Initial14 ) %>%
  #dplyr::select(  RateDecreasePerDay) %>%
  summarise_all(funs(mean,sd))
  
Median  <-df_graf2 %>%
    #group_by(Cultivar, SowTreat, SowingD)%>%
  dplyr::select(RateDecreasePerTTunit,  HardPerc_Initial14 ) %>%
  #dplyr::select(  RateDecreasePerDay) %>%
  summarise_all(funs(median))


```


```{r, fig.width=12, fig.height= 20, warning=FALSE}

fs<-30

ss<-2

av_shx<-median(Average$HardPerc_Initial14_mean) #= 76 #; mediam = 82

av_break<-median(Average$RateDecreasePerTTunit_mean) #= 0.013 # median = 0.12
  
  Average %>%
  ungroup %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6", "S7"),
                           labels=c("Jun", "Jul", "Sept", "Nov", "Feb", "Mar")))%>%
    mutate(Cultivar_letter= factor(Cultivar, 
                           levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),
                           labels=c("A", "D", "L", "M", "N.", "W"))) %>%
                           
  
  ggplot(aes(x=RateDecreasePerTTunit_mean, y=HardPerc_Initial14_mean, colour=Cultivar, shape=Cultivar)) +
  geom_point(fill = "white", size = 0.1, alpha=0.1) +
  geom_text(aes(label=Cultivar_letter),hjust=0, vjust=0,size=fs*0.3) +
  geom_line() +
  ylab(HS[max]~" (%)") +
  xlab(expression(HS["break"]~"(% units per "^"o"*"Cd)"))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=HardPerc_Initial14_mean-HardPerc_Initial14_sd/3.46,
                    ymax=HardPerc_Initial14_mean+HardPerc_Initial14_sd/3.46))+
    
    geom_errorbarh(aes(xmin=RateDecreasePerTTunit_mean-RateDecreasePerTTunit_sd/3.46,
                    xmax=RateDecreasePerTTunit_mean+RateDecreasePerTTunit_sd/3.46))+
  theme_bw()+

  #remove grid lines 
    theme(
      panel.border = element_rect(colour = "black", size = 1), 
      axis.line = element_line(colour = "black"))+
    
  geom_abline(slope=0, intercept=av_shx, linetype=2) +
  geom_vline(slope=0, xintercept=av_break,linetype=2) + 
  xlim(0,0.028)+
  ylim(0,115)+
  scale_x_continuous(breaks = c(0.01,0.02,0.03))+
   
  annotate("text", x = 0.004, y = 110, label = "High max \nLow break",size=fs*0.3, colour='black')+
  annotate("text", x = 0.026, y = 15, label = "Low max \nHigh break",size=fs*0.3, colour='black')+
  annotate("text", x = 0.004, y = 15, label = "Low max \nLow break",size=fs*0.3, colour='black')+
  annotate("text", x = 0.026, y = 110, label = "High max \nHigh break",size=fs*0.3, colour='black')+
    
   #make TT target labels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1)) +
  facet_wrap(~SowTreat,ncol=2) +theme(text=element_text(size=fs))
  
#ggsave("plots_SDmaxPlottedSDbreak_Quadrant.tiff", width=12, height=8, dpi=500)
ggsave("plots_Prjt14_HSmaxPlottedHSbreak_Quadrant.tiff", width=18, height=22, dpi=500)

```







##### Perform Stats Hardseed Breakdown rate  #######


```{r ANOVAMaxPlantPop}

str(df_Dif3)

#compare DAE_1T  among cultivars

df_ANOVA <- df_Dif3  %>%
  dplyr::select(Cultivar,Block,Plot, SowTreat, Depth,Difference,RateDecreasePerDay,RateDecreasePerTTunit )

```


```{r}


##Data Transformation :Hard_perc


##rename dataframe 

file <-df_ANOVA
  #filter(SowTreat=="S1")
 #filter(SowTreat=="S2")
 #filter(SowTreat=="S3") 
 #filter(SowTreat=="S4")
 #filter(SowTreat=="S6")
 #filter(SowTreat=="S7")




#data transformation
file$transf_sqr <- sqrt(file$RateDecreasePerTTunit)
file$transf_log <- log(file$RateDecreasePerTTunit)
file$transf_not <- 1*(file$RateDecreasePerTTunit/1)
file$transf_acos <- acos(file$RateDecreasePerTTunit/100)
file$transf_sqrx <- (file$RateDecreasePerTTunit^2)
#mutate(mydata, sqr.x = x^2)


head(file)

x <- c("transf_sqr", "transf_log","transf_acos","transf_not", "transf_sqrx" )
colsSelec <- match(x,colnames(file))




```



```{r, fig.height=7, fig.widht=8}


file %>%
  tidyr::gather("transformation","value",colsSelec) %>%
  ggplot(aes(value)) + 
  geom_histogram() +
  facet_grid(.~transformation, scales="free")+
  theme_bw()



```



check normality shapiro test +QQplots

```{r}

#normality test
shapiro.test(file$transf_acos)
shapiro.test(file$transf_not)
shapiro.test(file$transf_sqr)
shapiro.test(file$transf_log)
shapiro.test(file$transf_sqrx)




##QQplot
#var<-file$transf_acos

#var<-file$transf_not
var<-file$transf_sqr
#var<-file$transf_log
#var<-file$transf_sqrx

qqnorm(var)
qqline(var, col = 2)
qqplot(var, rt(300, df = 5))



```





##Overall analysis consider sowing date and cultivar 

```{r}
##Overview   variable = Difference

#file <- df_ANOVA
#file$transf_no <- 1*(df_ANOVA$Difference)
##use the : RateDecreasePerDay 
#file$transf_no <- 1*(df_ANOVA$RateDecreasePerDay)
##use the : RateDecreasePerTTunit
#file$transf_no <- 1*(df_ANOVA$RateDecreasePerTTunit)


head(file)

#-------------------------------------------------
# ANOVA 
file.subset <- file 

head(file.subset)
summary(file.subset)
#my.anova <- aov(transf_not ~ Cultivar*Depth* SowTreat, 
               # data = file.subset)
#my.anova <- aov(transf_no ~ Cultivar* SowTreat*Depth, 
                ##data = file.subset)
##Use transformed data 
my.anova <- aov(transf_sqr ~ Cultivar* SowTreat*Depth, 
                data = file.subset)

summary(my.anova)

```





#####  Inspect First LSD 

```{r}
#Means separation after ANOVA
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")) 
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))

(LSD.test(my.anova, c("Cultivar", "SowTreat"), alpha= 0.05, p.adj="none")) 


```


```{r}
posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.95)
#posthoc <- TukeyHSD(x=my.anova, 'Cultivar', conf.level=0.25)

posthoc

```

Then 
This is the mean separation using Tukey 

```{r}

fogo<-HSD.test(my.anova, 'Cultivar', group=TRUE)
fogo

```

##Make the ANOVA loop




## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(df_ANOVA$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```



## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <-df_ANOVA %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(RateDecreasePerTTunit ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```

Analyse the minimum value of Hardseeds or the Percentage of hardseed at the end of the thermal treatment (script 15 )








