---
title: "Hardseeds Live_compare hardseed and normal germ"
author: "CT"
date: "09.01.2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
##this script reads

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)


```

This script reads the 'MaxHardAndRate_Diff.txt " and the normal germ txt 
Combine the two dataframes with the objective to compare hardseedbreakdown rate and normal germination (is there a relationship?)


```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
##previous analysis : df_seed <- read.table("MeanSlope.txt",header=TRUE) 

df_seed <- read.table("MaxHardAndRate_Diff.txt",header=TRUE) 


str(df_seed)
```


then enter in the other folder 

C:\GitHubRepos\SubCloverPhD\SubClover\DeadAbnSeeds
```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\DeadAbnSeeds")
getwd()

#create file
df_norm<- read.table("MeanGermination.txt",header=TRUE) 

str(df_norm)

df_norm<-df_norm %>%
mutate(Germination=mean)

```


adjust data frames 

combine the two dataframes 


```{r}
str(df_seed)

# df_seed <- df_seed%>%
#   mutate(Cultivar=cv, SowTreat=sow, rate= -1*RateDecreasePerTTunit) %>%
#   select(-cv,-sow)


```


```{r}



dfMerge <-merge(df_seed, df_norm, by=c("Cultivar","SowTreat"))

#then rename column mean and slope

# dfMerge<-dfMerge %>%
#   mutate(Germination=mean)


```

then plot one against the other (x= RateDecreasePerTTunit, y = germination)

```{r}

str(dfMerge)

Average <-dfMerge %>%
  dplyr::select(Cultivar :Depth ,RateDecreasePerTTunit,   Germination)

##Calculate the overall mean (group by Cultivar)

OverallAverage<-Average %>%
  group_by(Cultivar, SowTreat)%>%
  dplyr::select(RateDecreasePerTTunit,   Germination)%>%
  summarise_all(funs(mean))
  
  
  
```


```{r, fig.height=7, fig.width=15}



##Calculate the overall mean (group by Cultivar)

OverallAverage %>%
  ggplot(aes(x=RateDecreasePerTTunit, y= Germination))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=8)+
  #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1, linetype=2)+
  theme_bw() +
  
  scale_x_continuous(limits = c(0,0.029),breaks=c(0,0.005, 0.01,0.015, 0.02,0.025))+
  scale_y_continuous(limits = c(0,100),breaks=c(0,20,40,60,80,100))+
  
  xlab(expression(Mean~hardseed~breakdown~"(%/"^"o"*"Cd)"))+ 
  
  #xlim(0,0.09)+
 # #scale_x_continuous(breaks=c(0,0.01, 0.02, 0.03))+
  
 # scale_x_continuous( limits=c(0,0.03)) +
 # scale_y_continuous( limits=c(0, 100)) +
  
  #scale_x_continuous(breaks=c(0.005,0.01,0.015, 0.020, 0.025, 0.03,0.035, 0.040))+
  #scale_y_continuous(breaks=c(0,20,40, 60, 80, 90,100))+
  
  #scale_y_continuous(breaks=seq(0,100,20))+
  
ylab(expression(Germination~"(%)"))+
    
  #ylim(0,1000)+
  #scale_y_continuous(breaks=c(0,25,50, 75, 100))+
  
  theme(text = element_text(size=22))+
  facet_wrap(~Cultivar, ncol=2)+

#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  theme(text = element_text(size=26))+
   
   
   #make TT target labels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
theme(axis.text.x = element_text(26))
  
  
  #theme(title =  element_text(size=14))
  
  #ggsave("plot_CorrelationHardBreakdown_GErmination.tiff", width=12, height=6, dpi=400)
  
  ggsave("plot_16Hard_CorrelationHardBreakdown_GErmination.tiff", width=16, height=16, dpi=400)
```




get a summary of the lm of the geom method (general)

equation is y = a(intercept) +b (rate) x
```{r}
summary(lm(Germination ~ RateDecreasePerTTunit, OverallAverage))
```

Plug a loop to generate summary by cultivar 

```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(OverallAverage$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- OverallAverage %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required 
  
    summary(lm(Germination ~ RateDecreasePerTTunit, df_subset))  
    
  #print
    
print(summary(lm(Germination ~ RateDecreasePerTTunit, df_subset)))


  } 



```


##Do the same with Max Hardseeds 


then plot one against the other (x= RateDecreasePerTTunit, y = germination)

```{r}

str(dfMerge)

HardAverage <-dfMerge %>%
  dplyr::select(Cultivar :Depth ,HardPerc_Initial14,  Germination,RateDecreasePerTTunit,HardPerc_End98)

##Calculate the overall mean (group by Cultivar)

OverallHardAverage<-HardAverage %>%
  group_by(Cultivar, SowTreat)%>%
  dplyr::select(HardPerc_Initial14, Germination,RateDecreasePerTTunit,HardPerc_End98)%>%
  summarise_all(funs(mean))
  
  
  
```

inspect S2

```{r}

S2<-OverallHardAverage%>%
  filter(SowTreat=="S2")

```


```{r, fig.height=7, fig.width=15}



##Calculate the overall mean (group by Cultivar)

OverallHardAverage %>%
  ggplot(aes(x=HardPerc_Initial14, y= Germination))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
  geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.2)+
  theme_bw() +
  xlab(expression(Max~hardseeds~"(%"^"*"*")"))+ 
  ylab(expression(Germination~"(%)"))+
  ylim(0,130)+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+

#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  theme(text = element_text(size=26))+
   
   
   #make TT target labels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))

  
  
  #theme(title =  element_text(size=14))
  
  #ggsave("plot_CumulativeGerm.png", width=12, height=6, dpi=400)
```




get a summary of the lm of the geom method (general)

equation is y = a(intercept) +b (rate) x
```{r}
summary(lm(Germination ~ HardPerc_Initial14,OverallHardAverage ))
```



## Is there any correlation with max seed hards and breakdown?


```{r, fig.height=7, fig.width=15}



##Calculate the overall mean (group by Cultivar)

OverallHardAverage %>%
  ggplot(aes(x=RateDecreasePerTTunit, y= HardPerc_Initial14))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
  geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.2)+
  theme_bw() +
  xlab(expression(Breakdown~"(%"^"*"*")"))+ 
  ylab(expression(Maximum~Hardseededness~"(%)"))+
  scale_x_continuous(breaks = seq(0, 0.05, by = 0.01))+
  
  scale_y_continuous(breaks=c(0,25,50, 75, 100))+
  
 # ylim(0,130)+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+

#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  theme(text = element_text(size=26))+
   
   
   #make TT target labels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))

  
  
  #theme(title =  element_text(size=14))
  
  #ggsave("plot_CumulativeGerm.png", width=12, height=6, dpi=400)
```




##compare the hardseed breakdown with the hardseed ranking from Australia (similar to Paper NZGA)



```{r}

df_Rank <- read.table("HardseedRanking.txt",header=TRUE) 


##merge with dataframe with hardseedbreakdown 
CorrelateRank <-merge(OverallAverage, df_Rank, by =c("Cultivar"))

#merge(df_seed, df_norm, by=c("Cultivar","SowTreat"))


```




Tip to use letters in grahs : 
mutate(Cultivar= factor(Cultivar, 
                           levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),
                           labels=c("A", "D", "L", "M", "N.", "W"))) %>%
                           geom_text(aes(label=Cultivar),hjust=0, vjust=0,size=7) +


```{r, fig.height=15, fig.width=15}

str(CorrelateRank)

##Calculate the overall mean (group by Cultivar)

CorrelateRank %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  mutate(Cultivar= factor(Cultivar, 
                           levels=c("Antas", "Denmark", "Leura", "Monti", "Narrikup", "Woogenellup"),
                           labels=c("A", "D", "L", "M", "N.", "W"))) %>%
  ggplot(aes(x=RateDecreasePerTTunit, y= HardSeedRanking))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=Cultivar),size=5)+
  geom_text(aes(label=Cultivar),hjust=0, vjust=0,size=10) +
  #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.2, linetype=2)+
  theme_bw() +
 xlab(expression(Mean~HSbreak~"(%/"^"o"*"Cd)"))+ 
  ylab(expression(Hard~seed~Rank))+
  ylim(0,4)+
  theme(text = element_text(size=24))+
  facet_wrap(~SowTreat, ncol=2)+
  scale_x_continuous(limits = c(0,0.029),breaks=c(0,0.005, 0.01,0.015,0.02,0.025))+


#remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  theme(text = element_text(size=28))+
   
   
   #make TT target labels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))

  
  
  #theme(title =  element_text(size=14))
  
  ggsave("plot_16_HardSeeds_CorrelationRankAndBreakdown.tiff", width=16, height=16, dpi=500)
```



## Inspect the correlation coefficient overall 

```{r}

summary(lm(HardSeedRanking  ~ RateDecreasePerTTunit, CorrelateRank)) 

```



Plug a loop to generate summary by SowTreat

```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(CorrelateRank$SowTreat)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- CorrelateRank %>%
    subset(SowTreat==cv.unique[i])
  
  #add the function or calculation required 
  
    summary(lm(HardSeedRanking  ~ RateDecreasePerTTunit, df_subset))  
    
  #print
    
print(summary(lm(HardSeedRanking ~ RateDecreasePerTTunit, df_subset)))


  } 



```


