---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "11.01.2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(gridExtra)
library(rpart)

```
sow
-This script reads the weather conditions for the  seed filling period (R7-R12)   EnviroSeedFillingR7_R12.txt
-Combines the info about the max hardness and slope hardseed breakdown 
-Attempt to establish correlation between the different variates 
- build a decision tree using rpart package 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
#df_SowHvst <- read.table("EnviroSeedFillingR7_R12.txt",header=TRUE)
df_All <- read.table("AllDataAllPeriodsSDandGerm.txt",header=TRUE)
head(df_All)
# change format 


```






```{r, fig.height=5, fig.width=10}

#str(df_All)

str(df_All)

#pairs(~HardAccum+slope+RainIrrig+RH+Temp+SoilTemp+PET+DiffRainPET,data=df_AllPlotsR7_R12, main="Simple Scatterplot Matrix")
pairs(~HardAccum+RainIrrig+RH+Temp+PET,data=df_All, main="Simple Scatterplot Matrix")
  
# dfD <- df_All%>%
#   filter(Cultivar=="Denmark")
# pairs(~HardAccum+slope+Rain+RH+Temp,data=dfD, main="Simple Scatterplot Matrix Denmark")

```

then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

#find coefficients 

cor (df_All[,-c(1,2)])
# cor (dfD[,-c(1,2)])
```
 
##Test regressions with  df_AllPlotsR7_R12


```{r}

str(df_All)
summary(lm(HardAccum ~ RainIrrig+RH+PET+SoilTemp, df_All))
summary(lm(Germination ~ RainIrrig+RH+PET+SoilTemp, df_All))
#summary(lm(HardAccum ~ RH, df_AllPlotsR7_R12))
#summary(lm(HardAccum ~ Temp, df_AllPlotsR7_R12))
#summary(lm(HardAccum ~ SoilTemp, df_AllPlotsR7_R12))
#summary(lm(HardAccum ~ PET, df_AllPlotsR7_R12))
#summary(lm(HardAccum ~ DiffRainPET, df_AllPlotsR7_R12))



```


##This loop checks the lm for all Periods first  for Hardcumm
## (Sdmax)
 
 
```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_All$Period)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_All %>%
    subset(Period==cv.unique[i])
  
  #add the function or calculation required 
  
    #summary(lm(HardAccum ~ RainIrrig+RH+PET+SoilTemp, df_subset)) 
     #summary(lm(Germination ~ RainIrrig+RH+PET+SoilTemp, df_subset))
     summary(lm(Sqrtslope ~ RainIrrig+RH+PET+SoilTemp, df_subset))
    #summary(lm(HardAccum ~ Temp, df_subset))
  #print
    
#print(summary(lm(HardAccum ~ RainIrrig+RH+PET+SoilTemp, df_subset)))
#print(summary(lm(Germination ~ RainIrrig+RH+PET+SoilTemp, df_subset)))
print(summary(lm(Sqrtslope ~ RainIrrig+RH+PET+SoilTemp, df_subset)))
   # print(summary(lm(HardAccum ~ Temp, df_subset)))

  } 


```




```{r}

AllGrw<-df_All %>%
  filter(Period=="AllGrowth")

  summary(lm(Sqrtslope ~ RainIrrig+PET, AllGrw))
  
  
  
  SeedFill<-df_All %>%
  filter(Period=="SeedFill")

  #summary(lm(Germination ~ PET+SoilTemp, SeedFill))
  summary(lm(Sqrtslope ~ PET+SoilTemp, SeedFill))
  
  
   BefHvst<-df_All %>%
  filter(Period=="BeforeHvst")

  #summary(lm(Germination ~ RH+RainIrrig+SoilTemp, BefHvst))
  summary(lm(Sqrtslope ~ SoilTemp+RH, BefHvst))

```



```{r}

BfHvst<-df_All %>%
  filter(Period=="BeforeHvst")

  summary(lm(Germination ~ RainIrrig+RH+PET+Temp+SoilTemp, BfHvst))

```



Decision tree analysis for SDbreak  with mean data  Seed Fill

```{r}

#str (df_AllPlotsR7_R12)
#str (df_All)

str (SeedFill)




# grow tree 
#fit <- rpart(Mileage~Price + Country + Reliability + Type, 
   #method="anova", data=cu.summary)


fit <- rpart(Sqrtslope~SoilTemp+PET,method="anova", SeedFill)
#fit <- rpart(HardAccum~RainIrrig+RH+Temp+SoilTemp+PET,method="anova", data=df_AllPlotsR7_R12)
#fit <- rpart(HardAccum~RainIrrig+Temp,method="anova", data=df_AllPlotsR7_R12)

printcp(fit) # display the results


plotcp(fit) # visualize cross-validation results 
summary(fit) # detailed summary of splits

# create additional plots 
par(mfrow=c(1,2)) # two plots on one page 
rsq.rpart(fit) # visualize cross-validation results   





```

```{r}
# plot tree 
 plot(fit, uniform=TRUE, 
    main="Regression Tree for SDbreak ")
 text(fit, use.n=TRUE, all=TRUE, cex=.8)



##wrong code
# plot tree 
#plot( fit,main="Regression Tree for Hardseededness (SDbreak) ")
#text( use.n=TRUE,all=TRUE, cex=.8)



```


Decision tree analysis for SDbreak  with mean data  Before Harvest 

```{r}

#str (df_AllPlotsR7_R12)
#str (df_All)

str (BefHvst)




# grow tree 
#fit <- rpart(Mileage~Price + Country + Reliability + Type, 
   #method="anova", data=cu.summary)


fit <- rpart(Sqrtslope~SoilTemp+RH,method="anova", BefHvst)
#fit <- rpart(HardAccum~RainIrrig+RH+Temp+SoilTemp+PET,method="anova", data=df_AllPlotsR7_R12)
#fit <- rpart(HardAccum~RainIrrig+Temp,method="anova", data=df_AllPlotsR7_R12)

printcp(fit) # display the results


plotcp(fit) # visualize cross-validation results 
summary(fit) # detailed summary of splits

# create additional plots 
par(mfrow=c(1,2)) # two plots on one page 
rsq.rpart(fit) # visualize cross-validation results   

# plot tree 
 plot(fit, uniform=TRUE, 
    main="Regression Tree for SDbreak ")
 text(fit, use.n=TRUE, all=TRUE, cex=.45)



```












Make one with germination data 


```{r}


str (SeedFill)


fit <- rpart(Germination ~SoilTemp+RH+PET,method="anova", SeedFill)
#fit <- rpart(HardAccum~RainIrrig+RH+Temp+SoilTemp+PET,method="anova", data=df_AllPlotsR7_R12)
#fit <- rpart(HardAccum~RainIrrig+Temp,method="anova", data=df_AllPlotsR7_R12)

printcp(fit) # display the results


plotcp(fit) # visualize cross-validation results 
summary(fit) # detailed summary of splits

# create additional plots 
par(mfrow=c(1,2)) # two plots on one page 
rsq.rpart(fit) # visualize cross-validation results   

# plot tree 
 plot(fit, uniform=TRUE, 
    main="Regression Tree for Germination ")
 text(fit, use.n=TRUE, all=TRUE, cex=.5)




 
 
```

make a tree only for antas at seed fill sdbreak






```{r}





```



prune tree 


```{r}
# prune the tree 
pfit<- prune(fit, cp=0.0518531) # from cptable   

# plot the pruned tree 
plot(pfit, uniform=TRUE, 
   main="Pruned Regression Tree for SDMax")
text(pfit, use.n=TRUE, all=TRUE, cex=.8)



```



Decision tree analysis for SDbreak with all data 

```{r}

#str (df_All)

# grow tree 
#fit <- rpart(Mileage~Price + Country + Reliability + Type, 
   #method="anova", data=cu.summary)


#fit <- rpart(HardAccum~slope+RainIrrig+RH+Temp+SoilTemp+PET+DiffRainPET,method="anova", data=df_All)
fit <- rpart(slope~RainIrrig+RH+Temp+SoilTemp+PET,method="anova", control = rpart.control(minsplit = 20, minbucket = 1), data=df_AllPlotsR7_R12)

printcp(fit) # display the results


plotcp(fit) # visualize cross-validation results 
summary(fit) # detailed summary of splits

# create additional plots 
par(mfrow=c(1,2)) # two plots on one page 
rsq.rpart(fit) # visualize cross-validation results   





```

```{r}

# plot tree 
plot(fit, uniform=TRUE, 
   main="Regression Tree for slope ")
text(fit, use.n=TRUE, all=TRUE, cex=.8)

# create attractive postcript plot of tree 
#post(fit, file = "c:/tree2.ps",
#post(fit, file = "c:/GitHubRepos/SubCloverPhD/SubClover/Hardseeds/treeSDbreak.tiff", 
  # title = "Regression Tree for SDbreak ")

##Path #C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds

```


```{r}

# prune the tree 
pfit<- prune(fit, cp=0.0560389) # from cptable   

# plot the pruned tree 
plot(pfit, uniform=TRUE, 
   main="Pruned Regression Tree for SDbreak")
text(pfit, use.n=TRUE, all=TRUE, cex=.8)





```




