---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "11.01.2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(gridExtra)
library(rpart)

```
sow
-This script reads the weather conditions for the  seed filling period (R7-R12)   EnviroSeedFillingR7_R12.txt
-Combines the info about the max hardness and slope hardseed breakdown 
-Attempt to establish correlation between the different variates 
- build a decision tree using rpart package 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
#df_SowHvst <- read.table("EnviroSeedFillingR7_R12.txt",header=TRUE)
df_All <- read.table("AllDataAllPeriodsSDandGerm.txt",header=TRUE)
head(df_All)
# change format 


```






```{r, fig.height=5, fig.width=10}

#str(df_All)

str(df_All)

#pairs(~HardAccum+slope+RainIrrig+RH+Temp+SoilTemp+PET+DiffRainPET,data=df_AllPlotsR7_R12, main="Simple Scatterplot Matrix")
pairs(~HardAccum+RainIrrig+RH+Temp+PET,data=df_All, main="Simple Scatterplot Matrix")
  
# dfD <- df_All%>%
#   filter(Cultivar=="Denmark")
# pairs(~HardAccum+slope+Rain+RH+Temp,data=dfD, main="Simple Scatterplot Matrix Denmark")

```

then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

#find coefficients 

#cor (df_All[,-c(1,2)])
# cor (dfD[,-c(1,2)])
```
 
##Test regressions with  df_AllPlotsR7_R12


```{r}

str(df_All)
summary(lm(HardAccum ~ RainIrrig+RH+PET+SoilTemp, df_All))
summary(lm(Germination ~ RainIrrig+RH+PET+SoilTemp, df_All))
#summary(lm(HardAccum ~ RH, df_AllPlotsR7_R12))
#summary(lm(HardAccum ~ Temp, df_AllPlotsR7_R12))
#summary(lm(HardAccum ~ SoilTemp, df_AllPlotsR7_R12))
#summary(lm(HardAccum ~ PET, df_AllPlotsR7_R12))
#summary(lm(HardAccum ~ DiffRainPET, df_AllPlotsR7_R12))



```


##This loop checks the lm for all Periods first  for Hardcumm
## (Sdmax)
 
 
```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_All$Period)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_All %>%
    subset(Period==cv.unique[i])
  
  #add the function or calculation required 
  
    #summary(lm(HardAccum ~ RainIrrig+RH+PET+SoilTemp, df_subset)) 
     #summary(lm(Germination ~ RainIrrig+RH+PET+SoilTemp, df_subset))
     summary(lm(Sqrtslope ~ RainIrrig+RH+PET+SoilTemp, df_subset))
    #summary(lm(HardAccum ~ Temp, df_subset))
  #print
    
#print(summary(lm(HardAccum ~ RainIrrig+RH+PET+SoilTemp, df_subset)))
#print(summary(lm(Germination ~ RainIrrig+RH+PET+SoilTemp, df_subset)))
print(summary(lm(Sqrtslope ~ RainIrrig+RH+PET+SoilTemp, df_subset)))
   # print(summary(lm(HardAccum ~ Temp, df_subset)))

  } 


```




```{r}

AllGrw<-df_All %>%
  filter(Period=="AllGrowth")

  #summary(lm(Sqrtslope ~ RainIrrig+PET, AllGrw))
  summary(lm(Germination ~ SoilTemp+PET+RainIrrig, AllGrw))
  
  
  SeedFill<-df_All %>%
  filter(Period=="SeedFill")

  #summary(lm(Germination ~ PET+SoilTemp, SeedFill))
  summary(lm(Sqrtslope ~ PET+SoilTemp, SeedFill))
  
  
   BefHvst<-df_All %>%
  filter(Period=="BeforeHvst")

  summary(lm(Germination ~ RH+RainIrrig+SoilTemp, BefHvst))
 # summary(lm(Sqrtslope ~ SoilTemp+RH, BefHvst))

```

Plot Weather variables with GErmination  in whole period  RH and Soil temp


```{r}

  str(AllGrw )


AllGrw %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp , y= Germination))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
  #geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  #ylab(expression(SDmax~"("*"%"*")"))+
  ylab(expression(Germination~"("*"%"*")"))+
  theme(text = element_text(size=22))+
  scale_x_continuous(limits = c(10,18),breaks=c(10,12,14,16, 18))+
  scale_y_continuous(limits = c(0,100),breaks=c(0,20,40,60,80, 100))+
  #facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  #theme(title =  element_text(size=14))

  ggsave("plot_Prjt18_Regression_Germination_SoilTemp_AllGrowPeriod.tiff", width=12, height=6, dpi=400)

```




```{r}

  str(SeedFill )


SeedFill %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp , y= Germination))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
  #geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  #ylab(expression(SDmax~"("*"%"*")"))+
  ylab(expression(Germination~percentage~"("*"%"*")"))+
  theme(text = element_text(size=22))+
  scale_x_continuous(limits = c(14,20),breaks=c(14,15,16,17,18))+
  scale_y_continuous(limits = c(0,100),breaks=c(0,20,40,60,80, 100))+
  #facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  #theme(title =  element_text(size=14))

  ggsave("plot_Prjt18_Regression_Germination_SoilTemp_SeedFillPeriod.tiff", width=12, height=6, dpi=400)

```

Do a quadratic


```{r}

  str(SeedFill )


SeedFill %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp , y= Germination))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
  #geom_point(aes(shape=SowTreat),size=4)+
  # geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  stat_smooth(aes(y = Germination),method = "lm", formula = y ~ x + I(x^2), size = 1, color = "darkgrey")+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  #ylab(expression(SDmax~"("*"%"*")"))+
  ylab(expression(Germination~percentage~"("*"%"*")"))+
  theme(text = element_text(size=22))+
  scale_x_continuous(limits = c(14,20),breaks=c(14,15,16,17,18))+
  scale_y_continuous(limits = c(0,100),breaks=c(0,20,40,60,80, 100))+
  #facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  #theme(title =  element_text(size=14))

  ggsave("plot_Prjt18_QuadratRegression_Germination_SoilTemp_SeedFillPeriod.tiff", width=12, height=6, dpi=400)

```



graph Germination and RH 


```{r}


str( SeedFill)

  SeedFill %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= Germination))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
  #geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  ylab(expression(Germination~"("*"%"*")"))+
  theme(text = element_text(size=22))+
   scale_x_continuous(limits = c(73,82),breaks=c(70,72,74,76, 78, 80,82))+
  scale_y_continuous(limits = c(0,100),breaks=c(0,20,40,60,80,100))+
  #facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  #theme(title =  element_text(size=14))

  ggsave("plot_18_Hardseed_GerminationVsRH_R7_R11.tiff", width=12, height=6, dpi=400)


```

Create a breaking point and split in two regressions 


# select
p1 <- df_phyllo_mean %>% filter(phylloStage=="P1") 
p2 <- df_phyllo_mean %>% filter(phylloStage=="P2")


```{r, figh.width=12,fig.height=10}

##Need to subset the data according to RH 

p1 <- SeedFill %>% subset(RH<=77.2) 
p2 <- SeedFill  %>% subset(RH>=77.2)

str( SeedFill)

  SeedFill %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= Germination))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
  #geom_point(aes(shape=SowTreat),size=4)+
  # geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
    geom_smooth(data=p1, method='lm', linetype=1,
              size=2, fill="grey", colour="black", alpha=0.2) +
   geom_smooth(data=p2, method='lm', size=2, fill="darkgrey",colour="grey", alpha=0.2) +
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  ylab(expression(Germination~"("*"%"*")"))+
  theme(text = element_text(size=22))+
   scale_x_continuous(limits = c(73,82),breaks=c(70,72,74,76, 78, 80,82))+
  scale_y_continuous(limits = c(0,100),breaks=c(0,20,40,60,80,100))+
  #facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  #theme(title =  element_text(size=14))

  ##ggsave("plot_18_BrokenStick_Hardseed_GerminationVsRH_R7_R11.tiff", width=12, height=6, dpi=400)


```


```{r}
GermRH <-SeedFill %>%
  dplyr::select(RH,Germination)

plot(GermRH)
```


```{r}
library(segmented)

  
out.lm <- lm(Germination ~ RH, data = GermRH)

o <- segmented(out.lm, seg.Z = ~RH, psi = list(RH = 76),
  control = seg.control(display = FALSE)
)

dat2 = data.frame(x=GermRH$RH, y = broken.line(o)$fit)

```


```{r}
GermRH %>% ggplot(aes(x = RH, y = Germination)) +
  geom_point() +
  geom_line(data = dat2, color = 'blue', aes(x = x, y = y))
```


```{r}
out.lm <-lm(Germination~RH,data=GermRH)

o <- segmented(out.lm, seg.Z=~RH, psi=list(RH=c(75)), control=seg.control(display=FALSE))

# show stats
print(summary(o))

     
# find slopes
s = slope(o)
print(s)

# find breaks
b = o$psi[,2]
print(b)

# get fitted broken stick
my.fitted <- fitted(o)
my.model <- data.frame(RH = GermRH$RH, Germination = my.fitted)
```


```{r}
# plot
GermRH %>%
  ggplot(aes(x=RH,y=Germination)) +
  geom_point() +
  geom_line(data=my.model, aes(x=RH,y=Germination))
```


```{r}
```


```{r}
GermRH %>% ggplot(aes(x = RH, y = Germination)) +
geom_point() +
geom_line(data = Data, color = 'blue', aes(x = x, y = y))
```


```{r}
```


#Calculate lm
```{r}
library(broom)

#p1<-p1 <- SeedFill %>% subset(RH<=76.3)   %>% na.omit() %>% ungroup() %>% dplyr::select(-phylloStage)

GermReg <- p1 %>%
 #group_by(phylloStage, SowTreat, Cultivar, Block) %>%
  group_by(SowTreat,Cultivar) %>%
 do(fit = lm(Germination ~ SoilTemp, data = .))

head(GermReg)
```


```{r}

#summary(lm(Germination ~ RH,p1))
summary(lm(Germination ~ RH,p2 ))


```

