---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "11.01.2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(gridExtra)
library(rpart)

```
sow
-This script reads the weather conditions for the  seed filling period (R7-R12)   EnviroSeedFillingR7_R12.txt
-Combines the info about the max hardness and slope hardseed breakdown 
-Attempt to establish correlation between the different variates 
- build a decision tree using rpart package 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
#df_SowHvst <- read.table("EnviroSeedFillingR7_R12.txt",header=TRUE)
df_All <- read.table("AllDataAllPeriodsSDandGerm.txt",header=TRUE)
head(df_All)
# change format 


```






```{r, fig.height=5, fig.width=10}

#str(df_All)

str(df_All)

#pairs(~HardAccum+slope+RainIrrig+RH+Temp+SoilTemp+PET+DiffRainPET,data=df_AllPlotsR7_R12, main="Simple Scatterplot Matrix")
pairs(~HardAccum+RainIrrig+RH+Temp+PET,data=df_All, main="Simple Scatterplot Matrix")
  
# dfD <- df_All%>%
#   filter(Cultivar=="Denmark")
# pairs(~HardAccum+slope+Rain+RH+Temp,data=dfD, main="Simple Scatterplot Matrix Denmark")

```

then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

#find coefficients 

cor (df_All[,-c(1,2)])
# cor (dfD[,-c(1,2)])
```
 
##Test regressions with  df_AllPlotsR7_R12


```{r}

str(df_All)
summary(lm(HardAccum ~ RainIrrig+RH+PET+SoilTemp, df_All))
summary(lm(Germination ~ RainIrrig+RH+PET+SoilTemp, df_All))
#summary(lm(HardAccum ~ RH, df_AllPlotsR7_R12))
#summary(lm(HardAccum ~ Temp, df_AllPlotsR7_R12))
#summary(lm(HardAccum ~ SoilTemp, df_AllPlotsR7_R12))
#summary(lm(HardAccum ~ PET, df_AllPlotsR7_R12))
#summary(lm(HardAccum ~ DiffRainPET, df_AllPlotsR7_R12))



```


##This loop checks the lm for all Periods first  for Hardcumm
## (Sdmax)
 
 
```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_All$Period)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_All %>%
    subset(Period==cv.unique[i])
  
  #add the function or calculation required 
  
    #summary(lm(HardAccum ~ RainIrrig+RH+PET+SoilTemp, df_subset)) 
     #summary(lm(Germination ~ RainIrrig+RH+PET+SoilTemp, df_subset))
     summary(lm(Sqrtslope ~ RainIrrig+RH+PET+SoilTemp, df_subset))
    #summary(lm(HardAccum ~ Temp, df_subset))
  #print
    
#print(summary(lm(HardAccum ~ RainIrrig+RH+PET+SoilTemp, df_subset)))
#print(summary(lm(Germination ~ RainIrrig+RH+PET+SoilTemp, df_subset)))
print(summary(lm(Sqrtslope ~ RainIrrig+RH+PET+SoilTemp, df_subset)))
   # print(summary(lm(HardAccum ~ Temp, df_subset)))

  } 


```




```{r}

AllGrw<-df_All %>%
  filter(Period=="AllGrowth")

  #summary(lm(Sqrtslope ~ RainIrrig+PET, AllGrw))
  summary(lm(Germination ~ SoilTemp+PET+RainIrrig, AllGrw))
  
  
  SeedFill<-df_All %>%
  filter(Period=="SeedFill")

  #summary(lm(Germination ~ PET+SoilTemp, SeedFill))
  summary(lm(Sqrtslope ~ PET+SoilTemp, SeedFill))
  
  
   BefHvst<-df_All %>%
  filter(Period=="BeforeHvst")

  #summary(lm(Germination ~ RH+RainIrrig+SoilTemp, BefHvst))
  summary(lm(Sqrtslope ~ SoilTemp+RH, BefHvst))

```

Plot Weather variables with GErmination  in whole period  RH and Soil temp


```{r}

  str(AllGrw )


AllGrw %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp , y= Germination))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
  #geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  #ylab(expression(SDmax~"("*"%"*")"))+
  ylab(expression(Germinatio~percentage~"("*"%"*")"))+
  theme(text = element_text(size=22))+
  scale_x_continuous(limits = c(10,18),breaks=c(10,12,14,16, 18))+
  scale_y_continuous(limits = c(0,100),breaks=c(0,20,40,60,80, 100))+
  #facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  #theme(title =  element_text(size=14))

  ggsave("plot_Prjt18_Regression_Germination_SoilTemp_AllGrowPeriod.tiff", width=12, height=6, dpi=400)

```




```{r}

  str(SeedFill )


SeedFill %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp , y= Germination))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
  #geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  #ylab(expression(SDmax~"("*"%"*")"))+
  ylab(expression(Germinatio~percentage~"("*"%"*")"))+
  theme(text = element_text(size=22))+
  scale_x_continuous(limits = c(14,20),breaks=c(14,15,16,17,18))+
  scale_y_continuous(limits = c(0,100),breaks=c(0,20,40,60,80, 100))+
  #facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  #theme(title =  element_text(size=14))

  ggsave("plot_Prjt18_Regression_Germination_SoilTemp_SeedFillPeriod.tiff", width=12, height=6, dpi=400)

```
