---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "22.09.2016"
output:
  word_document: default
  pdf_document: default
  html_document: default
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```


```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()
```



This script reads the HardseedsLiveData (from raw data excel) with all catergories of seeds (germ, abnormal, dead).calculation of max hardseeds and cumulative hardseeds.

```{r loadFile}
#create file
df_seed_raw <- read.table("HardseedsLiveData.txt",header=TRUE)
head(df_seed_raw)
```

```{r}
# jeito 2 de trocar formato (usando dplyr)
df_seed <- df_seed_raw %>%
  mutate(Plot = as.factor(Plot), 
         Block = as.factor(Block),
         Date = dmy(Date),
         Depth = factor(Depth,levels=c("Above","Below")),
         Soft = as.numeric(Soft),
         SoftDead = as.numeric(SoftDead),
         SoftGerm = as.numeric (SoftGerm),
         SoftAbn = as.numeric (SoftAbn),
         SoftUngerm = as.numeric (SoftUngerm),
       HardUngermFinal = as.numeric (HardUngermFinal)) 
  

summary(df_seed) # explore values

```

```{r}
str(df_seed) # check formats
```

here get the minimum round for the maximum percentage of hardseeds 

```{r}



# create an ID of each chunk
df_temp <- df_seed %>%
  dplyr::select(-Date) %>%
  mutate(codeID = as.factor(paste0(Plot,"_",Depth)))

# define unique factors to loop around
codesNames <- unique(df_temp$codeID)

# prepare final df to store data
df_final <- data.frame()

# loop
for(i in 1:length(codesNames)) {
  
  df_sub <- data.frame() # empty df
  
  df_sub <- df_temp %>%
    subset(codeID == codesNames[i]) %>% # segment one unique combination
    mutate(codeID = factor(codeID)) %>%
    arrange(Round) %>%
    mutate(CumSoftDead = cumsum(SoftDead)) %>%
    mutate(Total_live = InitialSeedlotR1Number-max(CumSoftDead)) %>%
    mutate(Soft_live = SoftGerm + SoftUngerm + SoftAbn) %>%
    filter(Round==min(Round)) %>% 
    mutate(Hard_perc = round(100-(Soft_live/Total_live*100),2))
  
  df_final <- rbind(df_final,df_sub)
  
}

summary(df_final)
```






```{r CreatePercentSoft}

#Change name of dataframes - u should not do that, makes things confuse

df_hard_live_max <- df_final %>% mutate(Round=factor(Round))

summary (df_hard_live_max)

```
check

```{r, fig.height=5, fig.width=10}

#Graph the maximum percentage of Live hardseeds!!! Here graph already show SE sd/3,.46 n = 3.

  df_hard_live_max %>%
  mutate(SowingD = dmy(SowingD)) %>%
  filter(Round == 14) %>%
  group_by(Cultivar,SowingD, Depth) %>%
  dplyr::select(Hard_perc) %>%
  summarise_all(funs(mean,sd)) %>%
  ggplot(aes(x=SowingD, y=mean, colour=Cultivar, shape=Cultivar)) +
  geom_point() +
  geom_line() +
 facet_grid(Depth~Cultivar) +
  labs(x="Sowing Date",y="Maximum Percentage of Live Hardseeds (%)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=mean-sd/3.46,
                    ymax=mean+sd/3.46))+
  theme_bw()+
  ylim(0,100)+
  theme(axis.text.x=element_text(angle = 0, hjust = 0.5, size= 11))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 12))

```


here loop to get the cumulative hardseeds in all rounds 

```{r}
# df_cum_soft<-df_seed %>%
#   mutate(LiveSeed=InitialSeedlotR1Number-SoftDead) %>%
#   mutate(SoftLive=SoftGerm+SoftAbn)  %>%
#   mutate(PercSoft=SoftLive/LiveSeed*100) %>%
#   mutate(PercHard=100-PercSoft) %>%
#   group_by(Plot,Depth) %>%
#   arrange(Round) %>%
#   mutate(HardAccum = 100-cumsum(PercSoft))
#   
# summary(df_cum_soft)




# create an ID of each chunk
df_temp <- df_seed %>%
  dplyr::select(-Date) %>%
  mutate(codeID = as.factor(paste0(Plot,"_",Depth)))

# define unique factors to loop around
codesNames <- unique(df_temp$codeID)

# prepare final df to store data
df_final2 <- data.frame()

# loop
for(i in 1:length(codesNames)) {
  
  df_sub <- data.frame() # empty df
  
  df_sub <- df_temp %>%
    subset(codeID == codesNames[i]) %>% # segment one unique combination
    mutate(codeID = factor(codeID)) %>%
    arrange(Round) %>%
    mutate(LiveSeed=InitialSeedlotR1Number-SoftDead) %>%
    mutate(SoftLive=SoftGerm+SoftAbn)  %>%
    mutate(PercSoft=SoftLive/LiveSeed*100) %>%
    mutate(PercHard=100-PercSoft)%>%
   
    
   # filter(Round==min(Round)) %>% 
     mutate(HardAccum = 100-cumsum(PercSoft))
  
  df_final2 <- rbind(df_final2,df_sub)
  
}

summary(df_final2)
  
```

Here graph the percentage of hardseeds based on living seeds (exclude dead seeds! )

```{r, fig.height= 8, fig.width=12}
#change data frame name and Graph Breakdown live hard seeds 

df_cum_soft<- df_final2

df_cum_soft %>%
  mutate(SowingD = dmy(SowingD)) %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  #filter(Round == 14) %>%
  group_by(Cultivar,SowingD, SowTreat, Depth,Round) %>%
  dplyr::select(HardAccum) %>%
  summarise_all(funs(mean,sd)) %>%
  ggplot(aes(x=Round, y=mean, colour=Cultivar, shape=Cultivar)) +
  geom_point(size=3) +
  geom_line() +
 facet_grid(Depth~SowTreat) +
  labs(x="Days",y=" Percentage of LiveHardseeds") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=mean-sd/3.46,
                    ymax=mean+sd/3.46))+
  theme_bw()+
  ylim(0,100)+
  xlim(0,100)+
  ylab(expression(Percentage~of~Hardseeds~"(%)"))+
  #theme(text = element_text(size=12))+
  #xlab(expression(Days))+
  theme(axis.text.x=element_text(angle = 45, hjust = 0.5, size= 11))+
   theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 16))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 12))+
   theme(axis.title.y=element_text(angle = 90, hjust = 0.5, size= 16))



```


```{r}
write.table(df_cum_soft, "dfHard_break.txt") #this will be used in seed breakdown stats slopes scripts


write.table(df_hard_live_max, "MaxHardness.txt") #this will be used in scripts which need max hardness 

```



end of this script . 



```{r}

#markdown::render("<C:\\GitHubRepos\\SubCloverPhD\\SubClover\\HardseedsProject1Read.Rmd>") 
```


