---
title: "Multiple scatter plots regressions"
author: "CT"
date: "17.04.2020"
output:
  word_document: default
  pdf_document: default
  html_document: default
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(gridExtra)

```
Objective 
_Create a fake data frame for Xiumei test her own dataset 
-Attempt to establish correlation between the different variates 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
df_all <- read.table("TestRawData.txt",header=TRUE)
head(df_all)
# change format 


```




Now plot variates to find  ...any correlation? 




```{r, fig.height=5, fig.width=10}

str(df_all)

pairs(~Percent+Rain+RH+SoilTemp+PET+AirTemp,data=df_all, main="Simple Scatterplot Matrix")
  


```

## then select columns of interest : here stats for overall means 

```{r}

#find coefficients 

cor (df_all[,-c(1,2)])
# cor (dfD[,-c(1,2)])
```




## Overall correlation:  inspect for all  variables 

##note lm= linear model


```{r}

summary(lm(Percent ~ Rain+RH+PET+AirTemp+SoilTemp, df_all))


```

## Select significant variables PR= *,**...in this case only AirTemp and SoilTEmp

```{r}

summary(lm(Percent ~ AirTemp+SoilTemp, df_all))

```



If needed : subset for individual cultivars  

```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_all$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_all %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required based on previous chunk (select Pr **, * )
  
   
    summary(lm(Percent ~ AirTemp, df_subset))
  #print
    
print(summary(lm(Percent ~ SoilTemp, df_subset)))


  } 


```


