---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "Thursday, 22 September , 2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(markdown)
#install.packages(markdown)

```
Here calculate the total percentage off dead seeds for cultivars and sow treat 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
df_seed <- read.table("HardseedsLiveData.txt",header=TRUE)
head(df_seed)
# change format 
df_seed$Date <- dmy(df_seed$Date)

# jeito 2 de trocar formato (usando dplyr)
df_seed <- df_seed %>%
  mutate(Plot = as.factor(Plot), 
         Block = as.factor(Block),
        Depth = as.factor(Depth),
        Soft = as.numeric(Soft),
         SoftDead = as.numeric(SoftDead),
         SoftGerm = as.numeric (SoftGerm),
         SoftAbn = as.numeric (SoftAbn),
         SoftUngerm = as.numeric (SoftUngerm),
       HardUngermFinal = as.numeric (HardUngermFinal)) 
  

summary(df_seed) # explore values
str(df_seed) # check formats
head(df_seed) # see to rows
tail(df_seed)



```



```{r CreatePercentSoft}
#Create a column that is the Accumulated Dead this is to calculate the Maximum percentage of dead seeds  


df_dead <- df_seed %>%
  mutate(Depth = factor(Depth,levels=c( "Above","Below")))%>%
  group_by(Plot,Depth) %>% 
  dplyr::select(-Date) %>% # 
  arrange(Round) %>% # need to tell which factor to accumulate within
  mutate(CumSoftDead = cumsum(SoftDead)) %>%
  #calculate the percentage of dead at the end of the experiment (119days) 
  filter(Round==119) %>%
  mutate(dead_perc = round((CumSoftDead/InitialSeedlotR1Number*100),2))

  
str (df_dead)





```


graph the total percentage of dead seeds 

```{r, fig.height=6, fig.width=10}

df_dead %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  filter(Round == 119) %>%
  group_by(Cultivar,SowTreat, Depth) %>%
  dplyr::select(dead_perc) %>%
  summarise_all(funs(mean,sd)) %>%
  ggplot(aes(x=Cultivar, y=mean, colour=Cultivar, shape=Cultivar)) +
  geom_point() +
  #geom_line() +
 facet_grid(Depth~SowTreat) +
  #facet_wrap(Depth~SowTreat)+
  labs(x="Sowing Date",y=" Percentage of dead seeds (%)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=mean-sd/3.46,
                    ymax=mean+sd/3.46))+
  theme_bw()+
  ylim(0,30)+
  theme(axis.text.x=element_text(angle = 90, hjust = 0.5, size= 12))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 12))


```






then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

file <- df_dead %>%
  dplyr::select(Block, Cultivar,SowTreat,Plot,Depth,dead_perc)

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(dead_perc ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
my.anova <- aov(dead_perc ~ Depth + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

The lowest percentage os dead seeds was observed in S1 and S1. In S4, S5 and S6 the percentage of dead seeds was threefold higher. 

Then test each sowing date individually 
S1


```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S1")

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(dead_perc ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



S2

```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S2")

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(dead_perc ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S3


```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S3")

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(dead_perc ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



S4

```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S4")

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(dead_perc ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S6


```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S6")

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(dead_perc ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



S7

```{r}
#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file %>%
  filter(SowTreat=="S7")

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(dead_perc ~ Cultivar*SowTreat + Block, data = file.subset)
my.anova <- aov(dead_perc ~ Cultivar + Block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```




