---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "22.09.2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)


```

This script reads the HardseedsLiveData (from raw data excel) with all catergories of seeds (germ, abnormal, dead). 
Runs ANOVA on the max percentage of hardseeds 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
df_seed <- read.table("HardseedsLiveData.txt",header=TRUE)
head(df_seed)
# change format 
df_seed$Date <- dmy(df_seed$Date)

# jeito 2 de trocar formato (usando dplyr)
df_seed <- df_seed %>%
  mutate(Plot = as.factor(Plot), 
         Block = as.factor(Block),
        Depth = as.factor(Depth),
        Soft = as.numeric(Soft),
         SoftDead = as.numeric(SoftDead),
         SoftGerm = as.numeric (SoftGerm),
         SoftAbn = as.numeric (SoftAbn),
         SoftUngerm = as.numeric (SoftUngerm),
       HardUngermFinal = as.numeric (HardUngermFinal)) 
  

summary(df_seed) # explore values
str(df_seed) # check formats
head(df_seed) # see to rows
tail(df_seed)



```


```{r}



# create an ID of each chunk
df_temp <- df_seed %>%
  dplyr::select(-Date) %>%
  mutate(codeID = as.factor(paste0(Plot,"_",Depth)))

# define unique factors to loop around
codesNames <- unique(df_temp$codeID)

# prepare final df to store data
df_final <- data.frame()

# loop
for(i in 1:length(codesNames)) {
  
  df_sub <- data.frame() # empty df
  
  df_sub <- df_temp %>%
    subset(codeID == codesNames[i]) %>% # segment one unique combination
    mutate(codeID = factor(codeID)) %>%
    arrange(Round) %>%
    mutate(SoftDead_cum = cumsum(SoftDead)) %>%
    mutate(Total_live = InitialSeedlotR1Number-max(SoftDead_cum)) %>%
    mutate(Soft_live = SoftGerm + SoftUngerm + SoftAbn) %>%
    #mutate(Hard_perc = HardUngermFinal_cum/max(InitialSeedlotR1Number)*100)
  filter(Round==min(Round)) %>% 
  mutate(Hard_perc = round(100-(Soft_live/Total_live*100),2))
  df_final <- rbind(df_final,df_sub)
  
}

summary(df_final)
```






```{r, fig.height=5, fig.width=10}

#Graph the maximum percentage of Live hardseeds!!! Here graph already show SE sd/3,.46 n = 3.
df_hard_live_max <- df_final

  df_hard_live_max %>%
  mutate(SowingD = dmy(SowingD)) %>%
  
  filter(Round == 14) %>%
  group_by(Cultivar,SowingD, Depth) %>%
  dplyr::select(Hard_perc) %>%
  summarise_each(funs(mean,sd)) %>%
  ggplot(aes(x=SowingD, y=mean, colour=Cultivar, shape=Cultivar)) +
  geom_point() +
  geom_line() +
 facet_grid(Depth~Cultivar) +
  labs(x="Sowing Date",y="Maximum Percentage of LiveHardseeds") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=mean-sd/3.46,
                    ymax=mean+sd/3.46))+
  theme_bw()+
  ylim(0,100)








```

Data Transformation :Hard_perc


```{r}

##rename dataframe 

file <-df_hard_live_max
  #filter(SowTreat=="S1")
 #filter(SowTreat=="S2")
 #filter(SowTreat=="S3") 
 #filter(SowTreat=="S4")
 #filter(SowTreat=="S6")
 #filter(SowTreat=="S7")




#data transformation
file$transf_sqr <- sqrt(file$Hard_perc)
file$transf_log <- log(file$Hard_perc)
file$transf_not <- 1*(file$Hard_perc/1)
file$transf_acos <- acos(file$Hard_perc/100)
file$transf_sqrx <- (file$Hard_perc^2)
#mutate(mydata, sqr.x = x^2)


head(file)

x <- c("transf_sqr", "transf_log","transf_acos","transf_not", "transf_sqrx" )
colsSelec <- match(x,colnames(file))




```


```{r, fig.height=7, fig.widht=8}


file %>%
  tidyr::gather("transformation","value",colsSelec) %>%
  ggplot(aes(value)) + 
  geom_histogram() +
  facet_grid(.~transformation, scales="free")+
  theme_bw()



```


check normality shapiro test +QQplots

```{r}

#normality test
shapiro.test(file$transf_acos)
shapiro.test(file$transf_not)
shapiro.test(file$transf_sqr)
shapiro.test(file$transf_log)
shapiro.test(file$transf_sqrx)




##QQplot
var<-file$transf_acos

#var<-file$transf_not
#var<-file$transf_sqr
#var<-file$transf_log
#var<-file$transf_sqrx

qqnorm(var)
qqline(var, col = 2)
qqplot(var, rt(300, df = 5))



```


then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

file <- df_final %>%
  dplyr::select(Block, Cultivar,SowTreat,Plot,Depth,Hard_perc)
  #filter(SowTreat=="S1")

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)

my.anova <- aov(Hard_perc ~ Cultivar*SowTreat*Depth + Block, data = file.subset)
#my.anova <- aov(Hard_perc ~ Cultivar*SowTreat + Block, data = file.subset)
#my.anova <- aov(Hard_perc ~ SowTreat + Block, data = file.subset)
#my.anova <- aov(Hard_perc ~ Cultivar + Block, data = file.subset)

```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among sowing dates 
```{r}
#Means separation 
#(LSD.test(my.anova, c("Cultivar","SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```


Kruskal-Wallis test by ranks

```{r}


#wilcox.test(Hard_perc ~ Cultivar, data = file)


kruskal.test (Hard_perc ~ Cultivar, data = file)

kruskal.test (Hard_perc ~ SowTreat, data = file)

#find medians 



## Interaction

interCvSow<-interaction(file$Cultivar, file$SowTreat)
kruskal.test(Hard_perc ~ interCvSow, data = file)



## Interaction

interCvSowDepth<-interaction(file$Cultivar, file$SowTreat, file$Depth )
kruskal.test(Hard_perc ~ interCvSowDepth, data = file)

```



```{r}

Mean <-file %>% 
  group_by(Cultivar) %>% 
  summarise(Mean = mean(Hard_perc))



```


############################################################


Then select for individual sowing dates 
S1 


```{r}

file <- df_hard_live_max %>%
  dplyr::select(Block, Cultivar,SowTreat,Plot,Depth,Hard_perc)%>%
  filter(SowTreat=="S1")

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(Hard_perc ~ Cultivar*Depth + Block, data = file.subset)

```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S1: S1 no effect of depth. cultivar had significant effect (P=0.0373, LSD=12.67). Only 'Leura' had fewer hardseeds (70 +- 11.5)than the other cvs (average of 86.5 +-3.5).




```{r}


#wilcox.test(Hard_perc ~ Cultivar, data = file)


kruskal.test (Hard_perc ~ Cultivar, data = file)

kruskal.test (Hard_perc ~ SowTreat, data = file)

#find medians 



## Interaction

interCvSow<-interaction(file$Cultivar, file$SowTreat)
kruskal.test(Hard_perc ~ interCvSow, data = file)



## Interaction

interCvSowDepth<-interaction(file$Cultivar, file$SowTreat, file$Depth )
kruskal.test(Hard_perc ~ interCvSowDepth, data = file)

```


S2

```{r}

file <- df_hard_live_max %>%
  dplyr::select(Block, Cultivar,SowTreat,Plot,Depth,Hard_perc)%>%
  filter(SowTreat=="S2")

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(Hard_perc ~ Cultivar*Depth + Block, data = file.subset)

```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```



S2. No effect of depth (P=0.43). Cultivar had effect (0.0088, LSD= 22.0)
```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



S2 no effect of depth. cultivar had significant effect (P=0.0088, LSD=22.0). Monti (87.4 +- 2.7) and Narrikup (47+ - 7.5) were the most contrasting cultivars. 


then for 
S3


```{r}

file <- df_hard_live_max %>%
  dplyr::select(Block, Cultivar,SowTreat,Plot,Depth,Hard_perc)%>%
  filter(SowTreat=="S2")

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(Hard_perc ~ Cultivar*Depth + Block, data = file.subset)

```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```




```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))

```

 

```{r}
#Means separation 
(LSD.test(my.anova, c("Depth"), alpha= 0.05, p.adj="none"))
```
 
 
S3 Main cultivar effect . Cultivar had effect (p<0.001, LSD= 9.44). Monti had sign more hardseeds (89 +-2.56)than Woogenellup (77 +-4.1 ) and Antas (58.5 +-9.35). Seeds above ground were sig (84.6 +-6.0 , P=0.002 harder than below ground seeds (75. 6 +-9).  


ANOVA S4 


```{r}

file <- df_hard_live_max %>%
  dplyr::select(Block, Cultivar,SowTreat,Plot,Depth,Hard_perc)%>%
  filter(SowTreat=="S4")

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(Hard_perc ~ Cultivar*Depth + Block, data = file.subset)

```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```




```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S4: Cultivar had an sig effect (P<0.001, LSD = 12.96) .Only Antas had sig fewer hard seeds (52.7 +- 24) than the other cvs (mean 80.3 +- 6.45)
 Depth had no effect.
 
 
Anova S6



```{r}

file <- df_hard_live_max %>%
  dplyr::select(Block, Cultivar,SowTreat,Plot,Depth,Hard_perc)%>%
  filter(SowTreat=="S6")

#-------------------------------------------------

# Chosen transform log to do anova 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(Hard_perc ~ Cultivar*Depth + Block, data = file.subset)

```
S6 

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```




```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```



S6: depth had no effect.  Cultivar (P=0.011, LSD 20.75) the two most contrasting cultivars were Monti (78.17 +- 3.02) differed from Antas and Woogenellup (mean of 42.5 +-12.0).



S7


```{r}

file <- df_hard_live_max %>%
  dplyr::select(Block, Cultivar,SowTreat,Plot,Depth,Hard_perc)%>%
  filter(SowTreat=="S7")

#-------------------------------------------------

# 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(Hard_perc ~ Cultivar*Depth + Block, data = file.subset)

```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```




```{r}
#Means separation 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```

S7: no effect of depth but cultivar ws significant (P<0.001, LSD = 15.63). most contasting cultivars were monti (95.4 +- 2.7) and Denmark (86.5 +-2.83)Wooge (54.7 +- 8.8) and  Antas (42.6 +-14.7). 

```{r}

#markdown::render("<C:\\GitHubRepos\\SubCloverPhD\\SubClover\\HardseedsProject1Read.Rmd>") 
```


