---
title: "Hardseeds Slopes 6CV"
author: "CT"
date: "Tuesday, July 19, 2016"
output:
  word_document: default
  pdf_document: default
---
Purpose: this script calculates the slopes of hardseed breakdown based on days and thermal-time sum of test

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(markdown)

```

Get the dataframe 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")

#create file
df_seed <- read.table("dfHard_break.txt",header=TRUE)
head(df_seed)



```

```{r}
# get TT at each  day
#create file
df_Tt <- read.table("dfHard_breakTT.txt",header=TRUE) %>% dplyr::select(Days,TtSum) %>% unique()
head(df_Tt)


```

```{r}
plot(df_Tt)
```



Just change name of dataframe and select columns to work 
```{r}
#Select depth of interest start with above seeds 

df_temp <- df_seed %>%
 mutate(Days=Round) %>%
 dplyr::select(Plot, Cultivar, Block, SowingD, SowTreat, Days, Depth, HardAccum, Round) 

dfSubSet <- merge(df_temp, df_Tt, by="Days")

dfSubSet$LoopIndex <- as.factor(paste0(dfSubSet$Plot,"_",dfSubSet$Depth)) # prepare for loop below

summary(dfSubSet)
  
```


graph hardseed decay with thermal time for ESA 2018 - data exploration

```{r}
 
df_graf <-dfSubSet %>%
  group_by(Cultivar,SowingD, SowTreat, TtSum) %>%
  dplyr::select(HardAccum) %>%
  summarise_all(funs(mean,sd)) 


df_graf %>%
  filter(SowTreat=="S2")%>%
  filter(Cultivar=="Antas"| Cultivar=="Monti" )%>%
ggplot(aes(x=TtSum , y=mean, colour=Cultivar, shape=Cultivar)) +
  geom_point(size=5) +
  geom_line() +
 #facet_grid(Depth~SowTreat) +
  labs(x="TT",y=" Percentage of LiveHardseeds") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
                  geom_errorbar(aes(ymin=mean-sd/3.46,
                    ymax=mean+sd/3.46),width=1,
                      size=0.4)+
  theme_bw()+
  ylim(0,100)+
  xlim(0,1900)+
  ylab(expression(Percentage~of~Hardseeds~"(%)"))+
  #theme(text = element_text(size=12))+
  xlab(expression(Thermal~time ~"("^"o"*"Cd)"))+
  theme(axis.text.x=element_text(angle = 45, hjust = 0.5, size= 11))+
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 16))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 12))+
  theme(axis.title.y=element_text(angle = 90, hjust = 0.5, size= 16))

```





then loop every plot and depth to find the linear equation and print a list of the coefficients and R2. 
```{r}
all.data<-data.frame()
counter<-0
# plots<-unique(dfSubSet$Plot)
# depth<-unique(dfSubSet$Depth)

li<- unique(dfSubSet$LoopIndex)
slopeType <- c("perDay","perTt")

#length(plots)*length(depth)

#p=d=1
for(p in 1:length(slopeType)) {
  for(d in 1:length(li)) {
  df_sub <- data.frame()  
   # print(paste0(plots[p],"_",depth[d]))
  #  counter<-counter+1
    
 # df_sub <- dfSubSet %>% filter(Plot==plots[p] & Depth == depth[d])
  df_sub <- dfSubSet %>% filter(LoopIndex==li[d])
  
  # Linear fit
  
# select type of slope calculated  
if(slopeType[p]=="Days") {
  x <- df_sub$Days
} else {
    x <- df_sub$TtSum
}
  
 # x <- df_sub$Days
 # x <- df_sub$TtSum
  y <- df_sub$HardAccum
  
  #print(data.frame(x=x,y=y))
  
  fit <- NULL
  fit <- lm(y ~ x)
  
  intercept <- round(fit$coefficients[[1]],2)
  slope <- round(fit$coefficients[[2]],3)
  r2 <- round(summary(fit)$r.squared * 100,2)
  # summary(fit)$adj.r.squared
  cv <- as.character(df_sub$Cultivar[1])
  block <- as.character(df_sub$Block[1])
  sow <- as.character(df_sub$SowTreat[1])
  sd <- dmy(df_sub$SowingD[1])
  slopeType <- factor(slopeType) 
  plot<- as.character(df_sub$Plot[1])
  depth<- as.character(df_sub$Depth[1])
  
  
  buf <- data.frame(slopeType=slopeType[p], sow=sow,cv=cv, block=block, plot=plot,depth=depth, int=intercept, slope=slope, r2=r2, n=nrow(df_sub))
  
  all.data <- rbind(buf, all.data)
  
 # print(buf)
  
  #print(nrow(df_sub))
    
  #subset(dfSubSet, (dfSubSet$Plot==plots[p] & Depth == depth[d]))
    
  }
  
}

summary(all.data)

```
write the datafram as txt to use in the next script (STats on slopes )
```{r}
write.table(all.data, "df_slopesBreak.txt")
```



