---
title: "Hardseeds Live_compare hardseed and normal germ"
author: "CT"
date: "09.01.2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
##this script reads

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)


```

This script reads the 'MeanSlope.txt " and the normal germ txt 
Combine the two dataframes with the objective to compare hardseedbreakdown rate and normal germination (is there a relationship?)


```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
#df_seed <- read.table("MeanSlope.txt",header=TRUE) 
df_seed <- read.table("MaxHardAndRate_Diff.txt",header=TRUE) 
#MaxHardAndRate_Diff.txt

str(df_seed)

##select columns

df_seed <-df_seed %>%
  
  dplyr::select(Plot,Cultivar,SowTreat, RateDecreasePerTTunit)
  
#make means

df_seed <- df_seed %>%
group_by(Cultivar, SowTreat)%>%
  dplyr::select( RateDecreasePerTTunit)%>%
  summarise_all(funs(mean))

```


then enter in the other folder 

C:\GitHubRepos\SubCloverPhD\SubClover\DeadAbnSeeds
```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\DeadAbnSeeds")
getwd()

#create file
df_norm<- read.table("MeanGermination.txt",header=TRUE) 

str(df_norm)


```


adjust data frames 

combine the two dataframes 


```{r}
str(df_seed)

df_seed <- df_seed%>%
  mutate( slope= 1*RateDecreasePerTTunit) 
  #ungroup()%>%
  #mutate(Cultivar=cv, SowTreat=sow, slope= -1*RateDecreasePerTTunit) %>%
  #select(-cv,-sow)



```


```{r}



dfMerge <-merge(df_seed, df_norm, by=c("Cultivar","SowTreat"))

#then rename column mean and slope

dfMerge<-dfMerge %>%
  mutate(Germination=mean)


```

then plot one against the other (x= slope, y = germination)


```{r, fig.height=7, fig.width=15}
str(dfMerge)

dfMerge %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6", "S7"),labels=c("Jun", "Jul", "Sept", "Nov", "Feb", "Mar")))%>%
  ggplot(aes(x=slope, y= Germination))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.2)+
  theme_bw() +
  xlab(expression(Mean~SDbreak~"( %/"^"o"*"Cd)"))+ 
  ylab(expression(Mean~Germination~"( %)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
  #theme(title =  element_text(size=14))


#remove grid lines 
     theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
  #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
   theme(text = element_text(size = 24))



  # annotate("text", x = 0.005, y = 110, label = "r= 0.37",size=6)+
  # annotate("text", x = 0.025, y = 15, label = "Soft",size=6 )+
  # annotate("text", x = 0.005, y = 15, label = "Medium",size=6)+
  # annotate("text", x = 0.025, y = 110, label = "Medium",size=6 )

  
  ggsave("plot_MeanGermVersus.png", width=12, height=6, dpi=400)
```




get a summary of the lm of the geom method (general)

equation is y = a(intercept) +b (slope) x
```{r}
summary(lm(Germination ~ slope, dfMerge))

```

Plug a loop to generate summary by cultivar 

```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(dfMerge$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- dfMerge %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required 
  
    summary(lm(Germination ~ slope, df_subset))  
    
  #print
    
print(summary(lm(Germination ~ slope, df_subset)))


  } 



```

