---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "11.01.2018"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(gridExtra)

```

-This script reads the weather conditions ten days before harvest (RH, TEMP, Rain) : EnviroBeforeHarvest.txt
-Combines the info about the max hardness and slope hardseed breakdown 
-Attempt to establish correlation between the different variates 


Mehtods and Interpretation here : 
http://www.sthda.com/english/articles/40-regression-analysis/168-multiple-linear-regression-in-r/

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
df_BefHvst <- read.table("EnviroBeforeHarvest.txt",header=TRUE)
head(df_BefHvst)
# change format 


```

now gather and create SowTreat column


```{r}

df_BefHvst <-df_BefHvst %>%
  gather(key= "SowTreat" , value = "Value" , S1:S7)
  

```


bring data frame with max hardseeds


```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
#df_Slope <- read.table("MeanSlope.txt",header=TRUE)
##use the other file with the differential rate 
df_Slope <- read.table("MaxHardAndRate_Diff.txt",header=TRUE)

head(df_Slope)


# df_Slope <- df_Slope %>%
#   mutate(SowTreat=sow, Cultivar=cv)%>%
#   dplyr::select (-sow,-cv)

str(df_Slope)

```

bring data with max hardseed

```{r}

# df_seed <- read.table("dfHard_break.txt",header=TRUE)
# 
# str(df_seed)
# 
# df_seed <- df_seed %>%
#   
# dplyr::select(Block:Round,HardAccum)  
# 
# str(df_seed)

##find means cultivar sowing date 
df_Slope <-df_Slope %>%
  group_by(Cultivar,SowTreat)%>%
   dplyr:: select(RateDecreasePerTTunit,HardPerc_Initial14)%>%
   summarise_all(funs(mean))

```

make the mean by cultivar and sowTreat

```{r}
# df_seed <- df_seed %>%
#  filter(Round==14)%>% 
#   group_by(Cultivar,SowTreat)%>%
#   dplyr:: select(HardAccum)%>%
#   summarise_all(funs(mean))

```

merge first the dataframes with max and hardseed breakdown


```{r}

# str(df_seed)
# str(df_Slope)
# df_MaxBreak <- merge(df_seed, df_Slope, by=c("Cultivar","SowTreat"))


```

then merge with the weather data ...need t spread variables RH, Temp and Rain first to create same number of rows  

```{r}

str(df_BefHvst)

##first spread 
df_BefHvst1 <-df_BefHvst %>%
  spread(Variable, Value)

# then merge 
df_All <- merge(df_Slope, df_BefHvst1, by=c("Cultivar","SowTreat"))

# then make slopes without minus sign 
#df_All <-df_All %>%
  #mutate (slope=-1*(slope))

##make the means by cultivar and sowing date


```


##Now include the days from sowing to harvest the seeds (DAS)


```{r}

df_seedHvst <- read.table("df_DaysToSeedHvst.txt",header=TRUE)

str(df_seedHvst)

# then merge 
df_All2 <- merge(df_All, df_seedHvst, by=c("Cultivar","SowTreat"))

```


##Now include also the duration of blooming (from FlowerIversen scripts: test the hypothesis that the longer the bloom period the lower the max hardness)file is :AverageBudDuration.txt


```{r}

df_BudDuration <- read.table("AverageBudDuration.txt",header=TRUE)

str(df_BudDuration)

# then merge 
df_All3 <- merge(df_All2, df_BudDuration, by=c("Cultivar","SowTreat"))

write.table(df_All3, "DataCompilation_Hardseed.txt")

```


##Now include flowering time ! Any correlation 
## use this file : df_tt_50p_flow

```{r}



df_DaysToFlow <- read.table("df_tt_50p_flow.txt",header=TRUE)

str(df_DaysToFlow)

# then create means 
df_DaysToFlow <-df_DaysToFlow %>%
  filter (Variable=="Flowering")%>%
  group_by(Cultivar,SowTreat)%>%
  dplyr::select(DAS50F)%>%
  summarise_all(funs(mean))
  
  # then merge 
df_All4 <- merge(df_All3, df_DaysToFlow, by=c("Cultivar","SowTreat"))%>%
  mutate(SumRHSoiltemp=RH+SoilTemp)
  
  
  
  #merge(df_All2, df_BudDuration, by=c("Cultivar","SowTreat"))

write.table(df_All4, "DataCompilation_Hardseed.txt")


```

Add Noraml germination Percentage data 

```{r}

df_Germination <- read.table("MeanGermination.txt",header=TRUE)

str(df_Germination)

 # then merge 
df_All5 <- merge(df_All4, df_Germination , by=c("Cultivar","SowTreat"))
 
str(df_All5)


  


```

```{r}

df_All5 <-df_All5 %>%
  mutate(HardAccum=HardPerc_Initial14,
         slope=RateDecreasePerTTunit,
         Germination=mean)

```




##Now plot variates to find  ...any correlation? 




```{r, fig.height=5, fig.width=10}

str(df_All5)


#pairs(~HardAccum+slope+Rain+RH+Temp,data=df_All, main="Simple Scatterplot Matrix")
  #pairs(~HardAccum+slope+Rain+RH+Temp+DaysToSeedharvest,data=df_All2, main="Simple Scatterplot Matrix")
 ##this is for df All2 
#pairs(~HardPerc_Initial14 +RateDecreasePerTTunit+Rain+RH+Temp+DaysToSeedharvest,data=df_All2, main="Simple Scatterplot Matrix")

##this is for df All3

pairs(~HardPerc_Initial14 +RateDecreasePerTTunit+Rain+RH+Temp+SoilTemp+DaysToSeedharvest+DaysBudDuration+DAS50F+SumRHSoiltemp,data=df_All5, main="Simple Scatterplot Matrix")

# dfD <- df_All%>%
#   filter(Cultivar=="Denmark")
# pairs(~HardAccum+slope+Rain+RH+Temp,data=dfD, main="Simple Scatterplot Matrix Denmark")

```



then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

#find coefficients 

#cor (df_All[,-c(1,2)])
cor (df_All4[,-c(1,2)])
# cor (dfD[,-c(1,2)])

#just change variable name to keep graphs same 




```

###Plot Weather variables with Maximum Percentage of Hardseeds 


```{r, fig.height=5, fig.width=10}

g1 <-df_All2 %>%
  ggplot(aes(x=DaysToSeedharvest, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Days~to~Harvest~"(n)"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)

grid.arrange(g1)

```




```{r, fig.height=8, fig.width=10}


MHard<-mean(df_All3$HardAccum)

Mslope<-mean(df_All3$slope)


g10 <-df_All3 %>%
  #ggplot(aes(x=DaysBudDuration, y= HardAccum))  +
  ggplot(aes(y=HardAccum, x= slope))  +
 # geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(colour=SowTreat,  shape=Cultivar),size=7)+
#   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  #xlab(expression(Days~to~BudDuration~"(n)"))+ 
  xlab(expression(SDbreak~"(n)"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  geom_abline(slope=0, intercept=MHard) +
  geom_vline(slope=0, xintercept=Mslope) + 
  xlim(0,0.028)+
  ylim(0,108)+
  theme(text = element_text(size=20))# +
#  facet_wrap(~SowTreat)

grid.arrange(g10)

```



```{r, fig.height=10, fig.width=15}

#hardAccum vs DaysToSeed Harvest 

 # g1 <-df_All2 %>%
 #  ggplot(aes(x=DaysToSeedharvest, y= HardAccum))  +
 #  geom_point(colour= "black", alpha=0.2) +
 #  geom_point(aes(shape=SowTreat),size=5)+
 #   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
 #  theme_bw() +
 #  xlab(expression(Days~to~Harvest~"(n)"))+ 
 #  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
 #  theme(text = element_text(size=20))+
 #  facet_wrap(~Cultivar)


#hardAccum vs Rain 

g2 <-df_All4 %>%
 mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
    ggplot(aes(x=Rain, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=5)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Rain~"("*"mm"*")"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#hardAccum vs RH
g3 <-df_All4 %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=5)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  
#hardAccum vs Temp

 g4 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Temp, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=5)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 
 
 g5 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=5)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 
 
  
#grid.arrange(g1, g2, g3, g4)
grid.arrange(g2, g3, g4,g5 )
# Save
#ggsave("plot_MaxHard_WeatherTendays.png", width=12, height=6, dpi=400)


```

new graph 
```{r, fig.height=12, fig.width=15}
#hardAccum vs Rain 

g11 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Rain, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
  #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  #geom_text(aes(label=SowTreat),hjust=0, vjust=0,size=7) +
  xlab(expression(Rain+Irrigation~"("*"mm"*")"))+
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  
#hardAccum vs RH
g12 <-df_All4 %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  
 g13 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Temp, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
  # geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) +
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 g14 <-df_All4 %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 g15 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=PET, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
 xlab(expression(PET~"("*"mm"*")"))+  
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 
 # g42 <-df_All %>%
 #   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
 #  ggplot(aes(x=DiffRainPET , y= HardAccum))  +
 #  geom_point(colour= "black", alpha=0.2) +
 #  geom_point(aes(shape=SowTreat),size=4)+
 #   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
 #  theme_bw() +
 # xlab(expression(Water~balance~"("*"mm"*")"))+  
 #  ylab(expression(SDmax~"("*"%"*")"))+
 #  theme(text = element_text(size=20))+
 #  facet_wrap(~Cultivar)
  
grid.arrange(g11, g12, g13,g14,g15)
# Save
#ggsave(file="whatever.pdf", g1, g2, g3,g4,g41)
#ggsave("plot_MaxHard_EnviroTSowHvst.png", width=14, height=7, dpi=400)


```


Mean Correlation coefficients for linear regressions (SHbreak =a+ bx) are :r Rain+Irrigation =0.24 (P=0.14);  rRH (%)  = 0.26 (P=0.09), rAirTemp =0.2 (P=0.23), rSoilTemp =0.0.24 (P=0.01),

Inspect overall Lm for variable HardACcum (SDmax) and all weatehr variables!

```{r}

str(df_All5)

#summary(lm(HardAccum ~ Rain+RH+ PET+Temp+SoilTemp,df_All5))
#summary(lm(HardAccum ~ RH+Rain,  df_All5))

summary(lm(HardAccum ~ Rain, df_All5)) 
#summary(lm(HardAccum ~ RH, df_All5)) 
#summary(lm(HardAccum ~ Temp, df_All4)) 
#summary(lm(HardAccum ~ SoilTemp, df_All4))
#summary(lm(HardAccum ~ PET, df_All4))
#summary(lm(HardAccum ~ SumRHSoiltemp, df_All4))

#summary(lm(HardAccum ~ DaysToSeedharvest, df_All2))
#summary(lm(HardAccum ~ DaysBudDuration, df_All3))
#summary(lm(HardAccum ~ slope, df_All3))
#summary(lm(HardAccum ~ DAS50F, df_All4))





```



This loop checks the lm 

```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_All2$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_All2 %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required 
  
    summary(lm(HardAccum ~ Rain, df_subset))  
    
  #print
    
print(summary(lm(HardAccum ~ Rain, df_subset)))


  } 


```

##Plot Days to harvest  with RAte of Hardseed breakdown 



```{r, fig.height=5, fig.width=10}
g4 <-df_All2 %>%
  ggplot(aes(x=DaysToSeedharvest, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Days~to~Harvest~"(n)"))+ 
 ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)

grid.arrange(g4)

```


####################### Sd break #########################

##Plot Weather variables with RAte of Hardseed breakdown  


```{r, fig.height=10, fig.width=15}
#Hardbreak vs Rain 


# g6 <-df_All2 %>%
#    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
#   ggplot(aes(x=DaysToSeedharvest, y= slope))  +
#   geom_point(colour= "black", alpha=0.2) +
#   geom_point(aes(shape=SowTreat),size=5)+
#    geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
#   theme_bw() +
#   xlab(expression(Days~to~Harvest~"(n)"))+
#  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
#   theme(text = element_text(size=20))+
#   facet_wrap(~Cultivar)



g6 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Rain, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Rain~"("*"mm"*")"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#hardAccum vs RH
g7 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)

 g8 <-df_All4 %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Temp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 


  
 g9 <-df_All4 %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 
  
#grid.arrange(g4, g5, g6, g7)
grid.arrange( g6, g7, g8,g9)
# Save
# ggsave(file="Fig_weather.tiff", dpi = 300)

#ggsave("plot_CumulativeGerm.png", width=12, height=6, dpi=400)


```

New Graph


new graph 
```{r, fig.height=12, fig.width=15}
#hardAccum vs Rain 

g21 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Rain, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
  #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  #geom_text(aes(label=SowTreat),hjust=0, vjust=0,size=7) +
  xlab(expression(Rain+Irrigation~"("*"mm"*")"))+
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
 
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  
#hardAccum vs RH
g22 <-df_All4 %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  
 g23 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Temp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
  # geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) +
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 g24 <-df_All4 %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 g25 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=PET, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
 xlab(expression(PET~"("*"mm"*")"))+  
 ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 
 # g42 <-df_All %>%
 #   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
 #  ggplot(aes(x=DiffRainPET , y= HardAccum))  +
 #  geom_point(colour= "black", alpha=0.2) +
 #  geom_point(aes(shape=SowTreat),size=4)+
 #   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
 #  theme_bw() +
 # xlab(expression(Water~balance~"("*"mm"*")"))+  
 #  ylab(expression(SDmax~"("*"%"*")"))+
 #  theme(text = element_text(size=20))+
 #  facet_wrap(~Cultivar)
  
grid.arrange(g21, g22, g23,g24,g25)
# Save
#ggsave(file="whatever.pdf", g1, g2, g3,g4,g41)
#ggsave("plot_MaxHard_EnviroTSowHvst.png", width=14, height=7, dpi=400)


```




########Enviro variables #########################


```{r}

#summary(lm(slope ~ Rain+RH+PET+Temp+SoilTemp, df_All5))
summary(lm(slope ~ Rain+PET+SoilTemp, df_All5))
#summary(lm(slope ~ Rain, df_All5)) 
#summary(lm(slope ~ RH, df_All5)) 
#summary(lm(slope ~ SoilTemp+PET, df_All5)) 
#summary(lm(slope ~ DaysToSeedharvest, df_All2))

#summary(lm(slope ~ SoilTemp, df_All4))


##DaysBudDuration
#summary(lm(slope ~ DaysBudDuration, df_All3))
##days to flower 
# summary(lm(slope ~ DAS50F, df_All4))
```

################## Germination vs weather #################

```{r}

#summary(lm(Germination ~ Rain+RH+PET+Temp+SoilTemp, df_All5))

summary(lm(Germination ~ Rain+Temp+SoilTemp, df_All5))
#summary(lm(Germination ~ Rain, df_All5))

```


```{r}


write.table(df_All5, "AllDataBeforeHarvest.txt")


```


####################Phenological Traits ################



```{r}


##Growing Days
#summary(lm(HardAccum ~ DaysToSeedharvest, df_All4))


##DaysBudDuration
 #summary(lm(HardAccum ~ DaysBudDuration, df_All4))
##days to flower 
#summary(lm(HardAccum ~ DAS50F, df_All4))



##Growing Days
#summary(lm(slope ~ DaysToSeedharvest, df_All4))


##DaysBudDuration
#summary(lm(slope ~ DaysBudDuration, df_All4))
##days to flower 
 summary(lm(slope ~ DAS50F, df_All4))


```

Do similar graphs with the phenological traits : Growing days, bud duration and time to flower 


Mean Correlation coefficients for linear regressions (SHmax =a+ bx) are :rGrowingDays =0.20 (P=0.23);  rBloomingPeriod =0.006 (P=0.97); rFloweringTime =0.2 (P=0.21),  




```{r, fig.height=15, fig.width=15}
#Hardbreak vs Rain 

str(df_All4)
 
##Growing Days vs slope
g111 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=DaysToSeedharvest , y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Growing~Period~"("*"days"*")"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#Days of blooming vs slope 
g112 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=DaysBudDuration, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Blooming~Period~"("*"days"*")"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)

#Time to flower 
 g113 <-df_All4 %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=DAS50F, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Days~to~Flower~"("*"n"*")"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 


  
  
#grid.arrange(g4, g5, g6, g7)
grid.arrange( g111, g112, g113)
# Save
# ggsave(file="Fig_weather.tiff", dpi = 300)

#ggsave("plot_CumulativeGerm.png", width=12, height=6, dpi=400)


```



```{r, fig.height=15, fig.width=15}
#Hardbreak vs Rain 

str(df_All4)
 
##Growing Days vs slope
g11 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=DaysToSeedharvest , y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Growing~Period~"("*"days"*")"))+ 
  ylab(expression(SDbreak"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#Days of blooming vs slope 
g12 <-df_All4 %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=DaysBudDuration, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Blooming~Period~"("*"days"*")"))+ 
  ylab(expression(SDbreak"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)

#Time to flower 
 g13 <-df_All4 %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=DAS50F, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Days~to~Flower~"("*"n"*")"))+ 
  ylab(expression(SDbreak"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 


  
  
#grid.arrange(g4, g5, g6, g7)
grid.arrange( g11, g12, g13)
# Save
# ggsave(file="Fig_weather.tiff", dpi = 300)

#ggsave("plot_CumulativeGerm.png", width=12, height=6, dpi=400)


```


Mean Correlation coefficients for linear regressions (SHmax =a+ bx) are :rGrowingDays =0.20 (P=0.23);  rBloomingPeriod =0.006 (P=0.97); rFloweringTime =0.2 (P=0.21),  


Plot Weather variables with SDmax  in R12 prior harvest  which were  significant : RH and Soil temp


```{r}

   df_All4 %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
  #geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  #ylab(expression(SDmax~"("*"%"*")"))+
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=22))+
   scale_x_continuous(limits = c(60,87),breaks=c(60,65,70,75, 80, 85))+
  scale_y_continuous(limits = c(0,0.03),breaks=c(0,0.01,0.015,0.02,0.025,0.03))+
  #facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  #theme(title =  element_text(size=14))

  ggsave("plot_Prjt7_Regression_SDbreakVsRHBeforeHarvest.tiff", width=12, height=6, dpi=400)

```




```{r}

   df_All4 %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
  #geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  #ylab(expression(SDmax~"("*"%"*")"))+
   ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=22))+
   scale_x_continuous(limits = c(14,22),breaks=c(10,12,14,16,18,20,22))+
 scale_y_continuous(limits = c(0,0.03),breaks=c(0,0.01,0.015,0.02,0.025,0.03))+
  #facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  #theme(title =  element_text(size=14))

  ggsave("plot_Prjt7_Regression_SDbreakVsSoilTemp_BeforeHarvest.tiff", width=12, height=6, dpi=400)

```





```{r}

#markdown::render("<C:\\GitHubRepos\\SubCloverPhD\\SubClover\\HardseedsProject1Read.Rmd>") 
```


