---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "22.09.2016"
output: pdf_document
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)


```

This script reads the df_slopesBreak.txt produced in script number 4 and run anova in the slopes as indicator of hardseedbreakdown 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
df_seed <- read.table("df_slopesBreakTT.txt",header=TRUE)


str(df_seed)





```



then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

file <- df_seed %>%
  dplyr::select(block, cv,sow,plot,depth,slope,r2)
 

#-------------------------------------------------

```


Then analyse overall slopes among cultivars 
```{r}
# select variable 
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(slope~ cv*depth + block, data = file.subset)
my.anova <- aov(slope~ cv*sow + block, data = file.subset)
```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among cultivars 
```{r}
#Means separation 
#(LSD.test(my.anova, c("depth"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("sow"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```





Then select for individual sowing dates 
S1 


```{r}
# select variable 
file.subset <- file %>%
  filter(sow=="S1")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(slope~ cv + block, data = file.subset)

```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among cultivars 
```{r}
#Means separation 
#(LSD.test(my.anova, c("depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("sow"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```


get the R2 

```{r}
# select variable 
file.subset <- file %>%
  filter(sow=="S1")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(r2~ cv*depth + block, data = file.subset)

(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```


Then do S2 



```{r}
# select variable 
file.subset <- file %>%
  filter(sow=="S2")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(slope~ cv*depth + block, data = file.subset)

```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among cultivars 
```{r}
#Means separation 
#(LSD.test(my.anova, c("depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("sow"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```


get the R2 

```{r}
# select variable 
file.subset <- file %>%
  filter(sow=="S2")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(r2~ cv*depth + block, data = file.subset)

(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```

Then run for S3 


```{r}
# select variable 
file.subset <- file %>%
  filter(sow=="S3")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(slope~ cv + block, data = file.subset)

```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among cultivars 
```{r}
#Means separation 
#(LSD.test(my.anova, c("depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("sow"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```


get the R2 for S3  

```{r}
# select variable 
file.subset <- file %>%
  filter(sow=="S3")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(r2~ cv + block, data = file.subset)

(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```

S4

```{r}
# select variable 
file.subset <- file %>%
  filter(sow=="S4")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(slope~ cv + block, data = file.subset)

```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among cultivars 
```{r}
#Means separation 
#(LSD.test(my.anova, c("depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("sow"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```


get the R2 for S4  

```{r}
# select variable 
file.subset <- file %>%
  filter(sow=="S4")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(r2~ cv*depth + block, data = file.subset)

(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```


Then do ANOVA for S6 

```{r}
# select variable 
file.subset <- file %>%
  filter(sow=="S6")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(slope~ cv+ block, data = file.subset)

```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among cultivars 
```{r}
#Means separation 
#(LSD.test(my.anova, c("depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("sow"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```


get the R2 for S6  

```{r}
# select variable 
file.subset <- file %>%
  filter(sow=="S6")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(r2~ cv*depth + block, data = file.subset)

(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```
 then S7 
 
 
```{r}
# select variable 
file.subset <- file %>%
  filter(sow=="S7")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(slope~ cv + block, data = file.subset)

```

```{r}
summary(my.anova)
#TukeyHSD(my.anova)


```

Check means among cultivars 
```{r}
#Means separation 
#(LSD.test(my.anova, c("depth"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("sow"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```


get the R2 for S7  

```{r}
# select variable 
file.subset <- file %>%
  filter(sow=="S7")

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(r2~ cv*depth + block, data = file.subset)

(LSD.test(my.anova, c("cv"), alpha= 0.05, p.adj="none"))
```
 













