---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "11.01.2018"
output: pdf_document
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(gridExtra)

```
sow
-This script reads the weather conditions for thw whole growing period (from sowing to  harvest (RH, TEMP, RainIrrig) : EnviroSowToHarvest.txt
-Combines the info about the max hardness and slope hardseed breakdown 
-Attempt to establish correlation between the different variates 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
df_SowHvst <- read.table("EnviroSowToHarvest.txt",header=TRUE)
head(df_SowHvst)
# change format 


```

now gather and create SowTreat column


```{r}

df_SowHvst <-df_SowHvst %>%
  gather(key= "SowTreat" , value = "Value" , S1:S7)
  

```


bring data frame with max hardseeds


```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
df_Slope <- read.table("MeanSlope.txt",header=TRUE)
head(df_Slope)


df_Slope <- df_Slope %>%
  mutate(SowTreat=sow, Cultivar=cv)%>%
  dplyr::select(-sow,-cv)

str(df_Slope)

```

bring data with max hardseed

```{r}

df_seed <- read.table("dfHard_break.txt",header=TRUE)

str(df_seed)

df_seed <- df_seed %>%
  
dplyr::select(Block:Round,HardAccum)  

str(df_seed)

```

make the mean by cultivar and sowTreat

```{r}
df_seed <- df_seed %>%
 filter(Round==14)%>% 
  group_by(Cultivar,SowTreat)%>%
  dplyr:: select(HardAccum)%>%
  summarise_all(funs(mean))

```

merge first the dataframes with max and hardseed breakdown


```{r}

str(df_seed)
str(df_Slope)
df_MaxBreak <- merge(df_seed, df_Slope, by=c("Cultivar","SowTreat"))


```

then merge with the weather data ...need t spread variables RH, Temp and Rain first to create same number of rows  

```{r}

str(df_SowHvst)

##first spread 
df_SowHvst1 <-df_SowHvst %>%
  spread(Variable, Value)

# then merge 
df_All <- merge(df_MaxBreak, df_SowHvst1, by=c("Cultivar","SowTreat"))

# then make slopes without minus sign 
df_All <-df_All %>%
  mutate (slope=-1*(slope))


```


Now plot variates to find  ...any correlation? 




```{r, fig.height=5, fig.width=10}

str(df_All)

pairs(~HardAccum+slope+RainIrrig+RH+Temp,data=df_All, main="Simple Scatterplot Matrix")
  
# dfD <- df_All%>%
#   filter(Cultivar=="Denmark")
# pairs(~HardAccum+slope+Rain+RH+Temp,data=dfD, main="Simple Scatterplot Matrix Denmark")

```

then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

#find coefficients 

cor (df_All[,-c(1,2)])
# cor (dfD[,-c(1,2)])
```

Plot Weather variables with Maximum Percentage of Hardseeds 


```{r, fig.height=15, fig.width=15}
#hardAccum vs Rain 

g1 <-df_All %>%
  ggplot(aes(x=RainIrrig, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Rain+Irrigation~"("*"mm"*")"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#hardAccum vs RH
g2 <-df_All %>%
  ggplot(aes(x=RH, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  
 g3 <-df_All %>%
  ggplot(aes(x=Temp, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(Maximum~Hardseeds~Percent~"(%)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 
  
grid.arrange(g1, g2, g3)
# Save
#ggsave("plot_MaxHard_WeatherTSowHvst.png", width=12, height=6, dpi=400)


```
This loop checks the lm 

```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_All$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_All %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required 
  
    #summary(lm(HardAccum ~ RainIrrig, df_subset))  
    #summary(lm(HardAccum ~ RH, df_subset))
    summary(lm(HardAccum ~ Temp, df_subset))
  #print
    
#print(summary(lm(HardAccum ~ RainIrrig, df_subset)))
#print(summary(lm(HardAccum ~ RH, df_subset)))
    print(summary(lm(HardAccum ~ Temp, df_subset)))

  } 


```



Plot Weather variables with RAte of Hardseed breakdown  


```{r, fig.height=15, fig.width=15}
#Hardbreak vs Rain 

g4 <-df_All %>%
  ggplot(aes(x=RainIrrig, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RainIrrig~"("*"mm"*")"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#hardAccum vs RH
g5 <-df_All %>%
  ggplot(aes(x=RH, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  
 g6 <-df_All %>%
  ggplot(aes(x=Temp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(Hardseed~breakdown~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 
  
grid.arrange(g4, g5, g6)
# Save
# ggsave(file="Fig_weather.tiff", dpi = 300)

#ggsave("plot_HardBreak_WeatherTSowHvst.png", width=12, height=6, dpi=400)


```


```{r}

#markdown::render("<C:\\GitHubRepos\\SubCloverPhD\\SubClover\\HardseedsProject1Read.Rmd>") 
```


