---
title: "Hardseeds Live Max 6CV"
author: "CT"
date: "11.01.2018"
output:
  word_document: default
  pdf_document: default
  html_document: default
---


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(gridExtra)

```
sow
-This script reads the weather conditions for the  seed filling period (R7-R12)   EnviroSeedFillingR7_R12.txt
-Combines the info about the max hardness and slope hardseed breakdown 
-Attempt to establish correlation between the different variates 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
df_SowHvst <- read.table("EnviroSeedFillingR7_R12.txt",header=TRUE)
head(df_SowHvst)
# change format 


```

now gather and create SowTreat column


```{r}

df_SowHvst <-df_SowHvst %>%
  gather(key= "SowTreat" , value = "Value" , S1:S7)
  

```


bring data frame with max hardseeds


```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Hardseeds")
getwd()

#create file
#df_Slope <- read.table("MeanSlope.txt",header=TRUE)

df_Slope <- read.table("MaxHardAndRate_Diff.txt",header=TRUE)
head(df_Slope)


# df_Slope <- df_Slope %>%
#   mutate(SowTreat=sow, Cultivar=cv)%>%
#   dplyr::select(-sow,-cv)

str(df_Slope)

```



```{r}

# str(df_seed)
# str(df_Slope)
 df_AllPlots<- merge( df_Slope, df_SowHvst, by=c("Cultivar","SowTreat"))

df_AllPlotsSpread<-df_AllPlots%>% 
  spread(Variable, Value)%>%
  group_by(Plot,Block,SowTreat,Cultivar,SowingD)%>%
  summarise_all(funs(mean))
  
 #write.table(to use in scatter plot and decisio tree analysis )

write.table(df_AllPlotsSpread, "AllPlotsHardWeatR7R12.txt")



```



bring data with max hardseed

```{r}

# df_seed <- read.table("dfHard_break.txt",header=TRUE)
# 
# str(df_seed)
# 
# df_seed <- df_seed %>%
#   
# dplyr::select(Block:Round,HardAccum)  
# 
# str(df_seed)

```

make the mean by cultivar and sowTreat

```{r}
df_Slope <- df_Slope %>%
 #filter(Round==14)%>% 
  group_by(Cultivar,SowTreat)%>%
  dplyr:: select(RateDecreasePerTTunit, HardPerc_Initial14 )%>%
  summarise_all(funs(mean))%>%
  mutate(HardAccum=HardPerc_Initial14,slope=RateDecreasePerTTunit)

write.table(df_Slope, "meanSDhardSDbreak.txt")


```

merge first the dataframes with max and hardseed breakdown

then merge with the weather data ...need t spread variables RH, Temp and Rain first to create same number of rows  

```{r}

str(df_SowHvst)

##first spread 
df_SowHvst1 <-df_SowHvst %>%
  spread(Variable, Value)

# then merge 
df_All <- merge(df_Slope, df_SowHvst1, by=c("Cultivar","SowTreat"))%>%
  mutate(SumRainRH=RainIrrig+RH)%>%
  mutate(SumRHSoil=RH+SoilTemp)

# then make slopes without minus sign 
# df_All <-df_All %>%
#   mutate (slope=-1*(slope))

str(df_All)

```


select columns to send statistician 

```{r}

Selection<-df_All%>%
  dplyr::select(Cultivar, SowTreat, HardPerc_Initial14, RateDecreasePerTTunit,RainIrrig,RH ,PET , SoilTemp,Temp )%>%
  mutate ( TreatCultivar = Cultivar,
           TreatSow= SowTreat,
           SDmax=HardPerc_Initial14,
           SDbreak=RateDecreasePerTTunit,
           AirTemp=Temp)
  
  
write.table (Selection, "MeanDataSelected.csv")


```


```{r}


##Transform the data 
##HSmax = asin(sqrt(file$Hard_perc/100))
##HSbreak = sqrt(slope)

df_All6 <-df_All %>%
  mutate(HSmaxtrans=asin(sqrt(HardAccum/100)),
         HSBreaktrans=sqrt(slope))



```




Now plot variates to find  ...any correlation? 




```{r, fig.height=5, fig.width=10}

str(df_All)

pairs(~HardAccum+slope+RainIrrig+RH+Temp+SoilTemp+PET+DiffRainPET,data=df_All, main="Simple Scatterplot Matrix")
  
# dfD <- df_All%>%
#   filter(Cultivar=="Denmark")
# pairs(~HardAccum+slope+Rain+RH+Temp,data=dfD, main="Simple Scatterplot Matrix Denmark")

```

then select columns of interest : here stats for overall means (SowTreat and Cultivar)

```{r}

#find coefficients 

cor (df_All[,-c(1,2)])
# cor (dfD[,-c(1,2)])
```

Plot Weather variables with Maximum Percentage of Hardseeds 


```{r, fig.height=10, fig.width=15}
#hardAccum vs Rain 

g1 <-df_All %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RainIrrig, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Rain+Irrigation~"("*"mm"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#hardAccum vs RH
g2 <-df_All %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  
 g3 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Temp, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 
 
 g4 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
 
 g41 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=PET, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
 xlab(expression(PET~"("*"mm"*")"))+  
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  
grid.arrange(g1, g2, g3,g4,g41)
# Save
#ggsave("plot_MaxHard_WeatherTSowHvst.png", width=12, height=6, dpi=400)


```



```{r, fig.height=12, fig.width=15}
#hardAccum vs Rain 

g1 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RainIrrig, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
  #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  #geom_text(aes(label=SowTreat),hjust=0, vjust=0,size=7) +
  xlab(expression(Rain+Irrigation~"("*"mm"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  
#hardAccum vs RH
g2 <-df_All %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  
 g3 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Temp, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
  # geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) +
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 g4 <-df_All %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 g41 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=PET, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
 xlab(expression(PET~"("*"mm"*")"))+  
  ylab(expression(SDmax~"("*"%"*")"))+
   
    theme(text = element_text(size=20))+
   theme(axis.text.x = element_text( 
                           size=12, angle=45, ))+
  facet_wrap(~Cultivar)+
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 
 # g42 <-df_All %>%
 #   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
 #  ggplot(aes(x=DiffRainPET , y= HardAccum))  +
 #  geom_point(colour= "black", alpha=0.2) +
 #  geom_point(aes(shape=SowTreat),size=4)+
 #   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
 #  theme_bw() +
 # xlab(expression(Water~balance~"("*"mm"*")"))+  
 #  ylab(expression(SDmax~"("*"%"*")"))+
 #  theme(text = element_text(size=20))+
 #  facet_wrap(~Cultivar)
  
grid.arrange(g1, g2, g3,g4,g41)
# Save
#ggsave(file="whatever.pdf", g1, g2, g3,g4,g41)
#ggsave("plot_MaxHard_EnviroTSowHvst.png", width=14, height=7, dpi=400)


```


overall correlation inspect for all 3 variables 


##Linear regression with weather parameters between phenophase R8-R12 and SDmax (SDmax=a+bx) are:  r Rain+Irrigation =0.34 (P=0.03);  rRH (%)  = 0.26 (P=0.10) and rAirTemp =0.22 (P=0.17), rsoilTemp =0.14 (P=0.4), rPET =0.08 (P=0.6).   

```{r}

summary(lm(HardAccum ~ RainIrrig+RH+PET+Temp+SoilTemp, df_All))

#summary(lm(HardAccum ~ RainIrrig, df_All))
#summary(lm(HardAccum ~ RH, df_All))
#summary(lm(HardAccum ~ Temp, df_All))
#summary(lm(HardAccum ~ SoilTemp, df_All))
#summary(lm(HardAccum ~ PET, df_All))
#summary(lm(HardAccum ~ DiffRainPET, df_All))

#summary(lm(HardAccum ~ SumRainRH, df_All))





```


This loop checks the lm for all cultivars 

```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_All$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_All %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required 
  
    #summary(lm(HardAccum ~ RainIrrig, df_subset))  
    #summary(lm(HardAccum ~ RH, df_subset))
    summary(lm(HardAccum ~ Temp, df_subset))
  #print
    
print(summary(lm(HardAccum ~ RainIrrig, df_subset)))
#print(summary(lm(HardAccum ~ RH, df_subset)))
   # print(summary(lm(HardAccum ~ Temp, df_subset)))

  } 


```



Plot Weather variables with RAte of Hardseed breakdown  during R8-R12 : Rain and Irrigation wer significant 


```{r}

   df_All %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RainIrrig, y= HardAccum))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
  #geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Rain+Irrigation~"("*"mm"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  ylab(expression(SDmax~"("*"%"*")"))+
  theme(text = element_text(size=22))+
   scale_x_continuous(limits = c(0,150),breaks=c(0,25,50,75, 100, 125,150))+
  scale_y_continuous(limits = c(0,100),breaks=c(0,20,40,60,80,100))+
  #facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  #theme(title =  element_text(size=14))

  ggsave("plot_Regression_SDmaxVsRainIrrig_R7_R11.tiff", width=12, height=6, dpi=400)

```



```{r, fig.height=12, fig.width=15}
#hardAccum vs Rain 

g11 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RainIrrig, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
  #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  #geom_text(aes(label=SowTreat),hjust=0, vjust=0,size=7) +
  xlab(expression(Rain+Irrigation~"("*"mm"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
 ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  
#slope vs RH
g12 <-df_All %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  
 g13 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Temp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
  # geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) +
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 g14 <-df_All %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)+
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 g15 <-df_All %>%
   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=PET, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   #geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
 xlab(expression(PET~"("*"mm"*")"))+  
 ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
   
    theme(text = element_text(size=20))+
   theme(axis.text.x = element_text( 
                           size=12, angle=45 ))+
  facet_wrap(~Cultivar)+
   #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
 
 
 # g42 <-df_All %>%
 #   mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
 #  ggplot(aes(x=DiffRainPET , y= slope))  +
 #  geom_point(colour= "black", alpha=0.2) +
 #  geom_point(aes(shape=SowTreat),size=4)+
 #   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
 #  theme_bw() +
 # xlab(expression(Water~balance~"("*"mm"*")"))+  
 #  ylab(expression(SDmax~"("*"%"*")"))+
 #  theme(text = element_text(size=20))+
 #  facet_wrap(~Cultivar)
  
grid.arrange(g11, g12, g13,g14,g15)
# Save
#ggsave(file="whatever.pdf", g1, g2, g3,g4,g41)
#ggsave("plot_MaxHard_EnviroTSowHvst.png", width=14, height=7, dpi=400)


```



old graph




```{r, fig.height=10, fig.width=15}
#Hardbreak vs Rain 

g4 <-df_All %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RainIrrig, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RainIrrig~"("*"mm"*")"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
  
#hardAccum vs RH
g5 <-df_All %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=RH, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(RH~"("*"%"*")"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  
 g6 <-df_All %>%
     mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=Temp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Air~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 
 
 g7 <-df_All %>%
     mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(Soil~temperature~"( "^"o"*"C)"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar) 
 
 
 g8 <-df_All %>%
    mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=PET, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(PET~"("*"mm"*")"))+ 
  ylab(expression(SDbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=20))+
  facet_wrap(~Cultivar)
  #theme(title =  element_text(size=14))
 
  
grid.arrange(g4, g5, g6, g7,g8)
# Save
# ggsave(file="Fig_weather.tiff", dpi = 300)

#ggsave("plot_HardBreak_WeatherTSowHvst.png", width=12, height=6, dpi=400)


```
 Inspect correlation overall 
 
 overall correlation inspect for all 3 variables ; remember here slope is the decrease in percentage units 
 
 data generated was : Linear regression with weather parameters between phenophase R8-R12 and SDmax (SDmax=a+bx) are:  r Rain+Irrigation =0.26 (P=0.1);  rRH (%)  = 0.37 (P=0.02) and rAirTemp =0.22 (P=0.18), rsoilTemp =0.39 (P=0.02), rPET =0.31(P=0.06).   

```{r}

#summary(lm(slope ~ RainIrrig+RH+PET+Temp+SoilTemp, df_All))

summary(lm(slope ~ PET+SoilTemp, df_All))

#summary(lm(slope ~ RainIrrig, df_All))
#summary(lm(slope ~ RH, df_All))
#summary(lm(slope ~ Temp, df_All))

#summary(lm(slope ~ PET, df_All))
#summary(lm(slope ~ SumRHSoil, df_All))



################ transformed data ####################

##summary(lm(HardAccum ~ RainIrrig+RH+PET+Temp+SoilTemp, df_All))
##HSmaxtrans=asin(sqrt(HardAccum/100)),
         ##HSBreaktrans=sqrt(slope))

summary(lm(HSBreaktrans ~ RainIrrig+RH+PET+SoilTemp, df_All6))
#summary(lm(HSBreaktrans ~ SoilTemp, df_All6))

```


##Bring data Germination 

```{r}

## bring data germination 


df_Germination <- read.table("MeanGermination.txt",header=TRUE)

str(df_Germination)

 # then merge 
df_All5 <- merge(df_All, df_Germination , by=c("Cultivar","SowTreat"))%>%
mutate(Germination=mean)
 
str(df_All5)


write.table(df_All5, "AllDataSeedFilling.txt")


```


see regressions 


```{r}


#summary(lm(Germination ~ RainIrrig+RH+PET+Temp+SoilTemp, df_All5))
summary(lm(Germination ~ RH+PET+SoilTemp, df_All5))




```




This loop checks the lm for all cultivars 

```{r}

#create a vector that holds names of all possible cultivars
cv.unique <- unique(df_All$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_All %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required 
  
    #summary(lm(HardAccum ~ RainIrrig, df_subset))  
    #summary(lm(HardAccum ~ RH, df_subset))
    summary(lm(slope ~ RH, df_subset))
  #print
    
print(summary(lm(slope ~ RH, df_subset)))
#print(summary(lm(HardAccum ~ RH, df_subset)))
   # print(summary(lm(HardAccum ~ Temp, df_subset)))

  } 


```



Plot Weather variables with SDbreak  in R12 prior harvest  which were  significant : RH and Soil temp


```{r}

   df_All %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=PET, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
  #geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
  xlab(expression(PET~"("*"mm"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  #ylab(expression(SDmax~"("*"%"*")"))+
  ylab(expression(HSbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=22))+
   #scale_x_continuous(limits = c(72,82),breaks=c(72,74,76,78, 80, 82))+
  scale_x_continuous(limits = c(120,300),breaks=c(150,175,200,225, 250, 275,300))+
  scale_y_continuous(limits = c(0,0.03),breaks=c(0,0.005, 0.01,0.015,0.02,0.025,0.03))+
  #facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  #theme(title =  element_text(size=14))

  ggsave("plot_Prjt9_Regression_SDbreakVsPET_SeedFilling.tiff", width=12, height=6, dpi=400)

```


Soil Temp 



```{r}

   df_All %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S6","S7"),labels=c("June", "July", "September", "November", "February","March")))%>%
  ggplot(aes(x=SoilTemp, y= slope))  +
  geom_point(colour= "black", alpha=0.2) +
  geom_point(aes(shape=SowTreat),size=6)+
  #geom_point(aes(shape=SowTreat),size=4)+
   geom_smooth(method='lm',formula=y~x, colour="grey",alpha=0.1)+
  theme_bw() +
 xlab(expression(Soil~temperature~"( "^"o"*"C)"))+  
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  #ylab(expression(SDmax~"("*"%"*")"))+
  ylab(expression(HSbreak~"( % /"^"o"*"Cd)"))+
  theme(text = element_text(size=22))+
   scale_x_continuous(limits = c(12,20),breaks=c(12,14,16,18, 20))+
  scale_y_continuous(limits = c(0,0.03),breaks=c(0,0.005, 0.01,0.015,0.02,0.025,0.03))+
  #facet_wrap(~Cultivar)+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 1), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  #theme(title =  element_text(size=14))
  #theme(title =  element_text(size=14))

  ggsave("plot_Prjt9_Regression_SDbreakVsSoilTempSeedFilling.tiff", width=12, height=6, dpi=400)

```





```{r}

#markdown::render("<C:\\GitHubRepos\\SubCloverPhD\\SubClover\\HardseedsProject1Read.Rmd>") 
```


