---
title: "Pok Vigour visuals  Analysis"
author: "CT"
date: "March  18, 2018"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---
Purpose : 
calculations of visual  scores for Poukawas plots : 
Subclover vigour, weed Percentage and fungal damage  
 
ANOVA for the variates

```{r, warning=FALSE}
#Load libraries 
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(lubridate)
library(knitr)
```

Read File 


```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\PokVigour")
getwd()
file <- read.table("PokVigour.txt",header=TRUE)

head (file)
```



parei aqui 

Define the formats  

```{r}

# define factors and formats
file <- file %>%
  mutate(
    Plot = as.factor(Plot),
    Block = as.factor(Block),
    Cultivar = as.factor(Cultivar),
    SowTreat = as.factor(SowTreat),
    Date = dmy(Date),
   SubVigour= as.numeric(SubVigour),
   WeedPerc= as.numeric(WeedPerc)
  )

str(file)
summary(file)

```



Here calculates prepare dodge positions and graph with SE directly

```{r, fig.height= 5, fig.width=10 , warning=FALSE}

#barplot 
#The palette with grey:cbPalette <- c("999999"),"666666", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#999999", "#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9", "#009E73")

#cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#D55E00", "#0072B2","#56B4E9")


# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)

# splitting and df due bug in tidyr (https://github.com/hadley/tidyr/issues/32)

 
  


```

Graph the pop score . To get the SE use /1.73 x 2 

```{r, fig.height= 5, fig.width=10 , warning=FALSE}
file %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_each(funs(mean,sd))%>%
  #filter(SowTreat=="S6")%>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=( SubVigour_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin= SubVigour_mean- SubVigour_sd/3.46, ymax= SubVigour_mean+ SubVigour_sd/3.46),
                width=0.25, size=0.3,position=dodge_x)   +
   scale_fill_brewer(palette="Blues")+
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
    labs(y="Vigour") +
  theme_bw()+
theme(axis.text.y = element_text( size = 16))+
theme(axis.title.y = element_text(face="bold", size=16))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 18))

#head(df_file)
```


## Create index to filter for loop ANOVA

```{r}
y <- c("S6","S7","S8")

sdIndex <- unique(file$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```


then loop anova if significant 

## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- file %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov( SubVigour ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


 if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
   print("***Sig Cultivar***") 
   print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```

Here analysis of variate weed percentage 


```{r, fig.height= 5, fig.width=10 , warning=FALSE}
file %>%
  #dplyr::select()
  group_by(Cultivar, SowTreat) %>%
  summarise_each(funs(mean,sd))%>%
  #filter(SowTreat=="S6")%>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=( WeedPerc_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin= WeedPerc_mean- WeedPerc_sd/3.46, ymax= WeedPerc_mean+ WeedPerc_sd/3.46),
                width=0.25, size=0.3,position=dodge_x)   +
   scale_fill_brewer(palette="Blues")+
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
    labs(y="Weed Percentage ") +
  theme_bw()+
theme(axis.text.y = element_text( size = 16))+
theme(axis.title.y = element_text(face="bold", size=16))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 18))

#head(df_file)
```


ANOVA for percenatge of weeds 

## Create index to filter for loop ANOVA

```{r}
y <- c("S6","S7","S8")

sdIndex <- unique(file$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```


then loop anova if significant 

## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- file %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov( WeedPerc ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


 if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
   print("***Sig Cultivar***") 
   print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```

Fungal damage 


Here analysis of variate weed percentage 


```{r, fig.height= 5, fig.width=10 , warning=FALSE}
fungi <-file %>%
  #dplyr::select()
  group_by(Cultivar, SowTreat) %>%
  summarise_all(funs(mean,sd))



```


```{r, fig.height=6,fig.width=12}

fungi %>%
  #filter(SowTreat=="S6")%>%
  #mutate(colPal = ifelse(Cultivar=="Antas","Brachy",ifelse(Cultivar=="Monti","Brachy","Yanny"))) %>%
  #ggplot(aes(x=Cultivar, y=(PropBurrBuried_mean),fill=colPal)) +
  ggplot(aes(x=Cultivar, y=( FungiDamage_mean),fill=Cultivar))+
   geom_bar(stat="identity", position = dodge_x) +
  geom_errorbar(aes(ymin= FungiDamage_mean- FungiDamage_sd/3.46, ymax= FungiDamage_mean+ FungiDamage_sd/3.46),
                width=0.25, size=0.3,position=dodge_x)   +
   scale_fill_brewer(palette="Blues")+
  theme_grey(base_size = 16) +
    facet_grid(.~SowTreat) +
    labs(y="Visual Score Foliar Fungi Damage ") +
  theme_bw()+
theme(axis.text.y = element_text( size = 16))+
theme(axis.title.y = element_text(face="bold", size=16))+
theme(axis.text.x=element_text(angle = 90, hjust=0.95,vjust=0.2,size = 18))

#head(df_file)

```



ANOVA for percenatge of weeds 

## Create index to filter for loop ANOVA

```{r}
y <- c("S6","S7","S8")

sdIndex <- unique(file$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```


then loop anova if significant 

## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- file %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov( FungiDamage ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


 if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
   print("***Sig Cultivar***") 
   print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```



