---
title: "Fitting  relationships rate of flowering, mean temperature and mean Pp for Reanalysis dataset  "
author: "CT"
date: "30.07.2018"
output:
  pdf_document: default
  html_document: default
  word_document: default

note: build linear relattionships between rate flowering , Temp and Pp as per Evans 1992 and Nori 2014.
  
 ## Grab dataframe with TT to start (see script 8)


 
---

```{r loadLibraries, echo=FALSE, include=FALSE}
#1
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library (segmented)
library(hydroGOF)
library(plot3D)

```
 
AIM:
- Estimate build relationship between rate of  flowering (1/days)  in relation to mean temperature and mean Pp for NZ and Australia data 
-Use this dataframe #df_Pptargets_TT50FFromEmergencePok.txt

```{r   loadFile}
#2
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\Reanalysis")

getwd()


```

## Bring dataframe ; remember this dataset compares Mean Pp from sowing and not from emergence 

```{r}


#use this file : df_DaysToFlower
df_tt_Pp <- read.table("df_DaysToFlower.txt",header=TRUE)

str(df_tt_Pp)
##then select only columns of interest 

df_tt_Pp <- df_tt_Pp %>%
dplyr::select(Location,Country,Treatcultivar, SowingDate,StartFlowering,DaysToFlower,AuthorYear )

##then rename column names 

df_tt_Pp  <- df_tt_Pp %>%
  mutate(Cultivar=as.factor(Treatcultivar),
         SowingD=as.Date (SowingDate),
         DAS50F=as.numeric(DaysToFlower), 
         Date=as.Date(StartFlowering))%>%
  dplyr::select(-SowingDate, -StartFlowering,-Treatcultivar, -DaysToFlower)
  
```


## Change formats 

```{r}
#3 get dataframe created similar to ReAnalysis4 which is Rea6 - use Iversen DAS50Flwoering data
#this is Iversen data: df_tt_Pp <- read.table("df_Pptargets_TT50F.txt",header=TRUE) 

#df_Pptargets_TT50FFromEmergence
#df_tt_Pp <- read.table("df_Pptargets_TT50FFromEmergencePok.txt",header=TRUE)

str(df_tt_Pp)

# force date format
df_tt_Pp$SowingD <- ymd(df_tt_Pp$SowingD)
df_tt_Pp$Date <- ymd (df_tt_Pp$Date)
#df_tt_Pp$Block <- as.factor(df_tt_Pp$Block)
#df_tt_Pp$TT_target <- as.factor(df_tt_Pp$TT_target)

str(df_tt_Pp)


```


## Now prepare the data frame to include the date of flowering and the rate (1/days)
## consider DAE (after emergence) ! ! 

```{r}
#4
#select columns of interest 

df_Prep <- df_tt_Pp %>%
  mutate(RateFlow=1/DAS50F )

  str(df_Prep)


```

## Read the  Air temp data and  adjust formats 

```{r}

#create file
#For Air temperature
df_A <- read.table("RawWeather.txt",header=TRUE)


```


##Now Add the accumulation of of soil temperatures to calculate the average temperature during the desired process (here 50% plants with first runner ). 


```{r}
#cumulate air; 
df_B <- df_A %>%
  mutate(AirTt=Tx+Tm/2)%>%
  mutate(SumAir = cumsum(AirTt)) %>%
  mutate(Date=dmy(Date))%>%
  dplyr::select(-AirTt)
str(df_B)

```


check data with graph

```{r}

#Air

df_B%>%
  ggplot(aes(x=Date,y=SumAir)) +
  geom_point()


str(df_B)

```


Merge dataframes by date

```{r}

# this step is used just to change the dataframe name similar (used to first merge the soil and air temperature dataframes in other script)  


df_Temp <- df_B%>%
  dplyr:: select(-Tx, -Tm)

str(df_Temp)

#Merge the two dataframes by Date
df1 <- merge(df_Prep,df_Temp, by.x="SowingD",by.y="Date") %>%
  #mutate(soilTempAcc_sow = SumTempSo) %>% 
  mutate(airTempAcc_sow=SumAir)%>%
dplyr::select(-SumAir)

str(df1)

 
```


##-----------------------

Include the mean temperature during flowering using the already calculated data in Reanalysis folder ("df_MeanTFlo2.txt")


```{r}

df_TempFlower <- read.table("df_MeanTFlo2.txt",header=TRUE)


str(df_TempFlower)


df_TempFlower<-df_TempFlower %>%
  dplyr::select(AuthorYear,TmeanSowFlow,Pp)%>%
  mutate(PpAtSow=Pp)%>%
  dplyr::select(-Pp)
  
str(df_TempFlower)
```

merge dataframes by AuthorYear column

```{r}

#then repeat same procedure done for the sowing date but use the date for Flowering 
  df_merge <- merge(df_Prep, df_TempFlower , by="AuthorYear") 


```


Turn off this script : not needed .
Need to force a date for 50 % of plants with runners  (round) to calculate the average temperature during this phase  

Save dataframe as txt file


```{r}

# str(df1)
# 
# # force formats of dates
# df1$Date <- round(df1$Date,0)
# df_Temp$Date <- round(df_Temp$Date,0)
# 
# #then repeat same procedure done for the sowing date but use the date for Flowering 
#   df_merge <- merge(df1, df_Temp, by="Date") %>%
#   #mutate(soilTempAcc_50F = SumTempSo) %>%
#   mutate(airTempAcc_50F=SumAir)%>%
#   dplyr::select( -SumAir) %>%
#  
#   #subtract accumulate temperature das1T from sowing 
#   #mutate(meanTempSoil_50F = (soilTempAcc_50F-soilTempAcc_sow)/DAS50F) %>% 
#   mutate(meanTempAir_50F = (airTempAcc_50F-airTempAcc_sow)/DAS50F)
#   
#   summary(df_merge)
#   
#   df_merge <-df_merge %>%
#     #eliminate repeat columns
#     dplyr::select(-Pp.x, -Pp.y)
# 
#   str(df_merge)
#   
#   ##Use this dataframe to build graph in script 4 
# #write.table(df_merge, "df_MeanTempTo50FlowerPok.txt") 



```

 

##Incorporate the mean Pp as well 


## Read the daily Pp and  adjust formats 

```{r}

#create file
##this is Iversen data df_P <- read.table("df_CumTTiv.txt",header=TRUE)
#bring back the df_A with the formated "Pok_Weat.txt" - they have same dataset 


df_C <- df_A %>%
  #mutate(AirTt=Tx+Tm/2)%>%
 # mutate(SumAir = cumsum(AirTt)) %>%
  mutate(Date=dmy(Date))%>%
  dplyr::select(-Tx,-Tm)

str(df_C)

#adjust formats and change dataframe name justto harmonise with following codes 
df_P<-df_C%>%
 #mutate(Date=dmy(Date))%>%
  dplyr:: select(Date,Pp)

str(df_P)

```

# Now need to calculate the mean Pp


#Till here all good ! 

Need to force a date for 50 % of plants with flowers  (round) to calculate the average Pp during this phase  

Save dataframe as txt file.


```{r}


# force formats of dates
#df_merge$Date <- round(df_merge$Date50FF ,0)
#df_P$Date <- round(df_P$Date,0)

#then repeat same procedure 
  df_mergePp <- merge(df_merge, df_P, by="Date") 
  
  str(df_mergePp)


```


Calculate the mean photoperiod for the flowering period

```{r}

  df_Pp50FmeanTPp <-df_mergePp %>%
    mutate(meanPp50F = (Pp+PpAtSow)/2) %>%
  mutate(meanTempAir_50F=TmeanSowFlow)
  ##calculate the rate to Flowering 1/DAS50FFromEmerg
  #mutate(RateFlow= 1/DAS50FFromEmerg)

str(df_Pp50FmeanTPp)

```

then select columns of interest and clean data frame for just AuthorYear  dataset  

```{r}

aRe <-df_Pp50FmeanTPp %>%
  #select(SowingD:Block,meanTempSoil_50F,meanTempAir_50F,meanPp50F,RateFlow  )%>%
  group_by(AuthorYear ,Cultivar,Location)%>%
  dplyr::select(meanPp50F, meanTempAir_50F,RateFlow)%>%
  summarise_all(funs(mean))
  
summary (aRe)
```

##That's Super  store this dataframe as txt table 
```{r}

##Select only cultivars with several observations
aRe_Cv <-aRe %>%
  filter(Cultivar=="MtBarker"|
          Cultivar=="SeatonPark"|
          Cultivar=="Trikkala"|
          Cultivar=="Woogenellup"|
          Cultivar== "Tallarook"|
         Cultivar=="Clare"
           )

#Save as table 
write.table(aRe_Cv, "df_MeanRateFlower50F_TempsPhotop_ReAnalysis.txt")


```



End of this script  (move for graphs  in script 13) 
