---
title: "ReAnalysis Table"
author: "CT"
date: "Thursday, December  05, 2016"
output: html_document
note: Re analysis data and weather files : merge .
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```
 


```{r   loadFile}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\ReAnalysis")
getwd()


#get dataframe created in ReAnalysis1
df_Rea3 <- read.table("df_Rea3.txt",header=TRUE)


#head(df_Data)

summary(df_Rea3)

```

Use slope values (Rea3) to normalise TT flowering 

```{r}
#Flowering reference = Floref
floref <- 50

TTpercflo <- 2.6 # degree days from 5 to 100 flowering (value calculated from DearEtAL1993_Reanalysis3 script)

df_Rea4 <- df_Rea3 %>%
  mutate(TTFloAdj=((floref-PercentFlower)*TTpercflo )+TTtoFlower)

summary(df_Rea4)

  
```


```{r}
#graph TTtoFlower vs TTFloAdj
#Check TT 
df_Rea4  %>% 
ggplot(aes(x=TTtoFlower, y= TTFloAdj)) +
    geom_point(shape=21)+
  geom_abline(intercept = 0, slope = 1)

```

Analysis of TTFlowerAdj vs T5-100. Is there any relationship between Time to flower and period (short orlong) for flower duration (5 to 100 %)? use DearEtAl1993 dataset to check.


```{r}
df_Rea4  %>% 
  filter(LocationYear=="Waggawagga1985") %>%
  #tidyr::gather("Variable", "Value",PercentFlower,TTFloAdj) %>%
    ggplot(aes(x=PercentFlower, y= TTFloAdj, colour=Treatcultivar)) +
  geom_point(shape=21) 
 #theme(legend.position="none")
  #facet_grid(), scales = "free")
 
```




plot TTadj vs. sowing date

```{r , fig.height=5, fig.width=10}
df_Rea4  %>% 
  filter(Treatcultivar=="Woogenellup") %>%
ggplot(aes(x=month(SowingDate), y= TTFloAdj, colour=Treatcultivar)) +
    geom_point(shape=21) +
  scale_x_continuous(breaks = c(2,4,6,8,10,12))+
 # geom_smooth()+
  facet_grid(Country~.)


```

```{r,fig.height=5, fig.width=10}
library(scales)

df_Rea4  %>% 
  tidyr::gather("Variable", "Value",DaysToFlower,TTFloAdj) %>%
  ggplot(aes(x=month(SowingDate), y= Value, colour=Treatcultivar)) +
  geom_point(shape=21) +
 theme(legend.position="none")+
  facet_grid(Variable~Country, scales = "free")

```

Then, select datasets with more than one sowing date in different months:

Condobolin1986
Katanning1990
Launceston1987
Melbourne1969
Waggawagga1985

```{r,fig.height=5, fig.width=10,warning=FALSE}
library(scales)
df_Rea4  %>% 
  filter(LocationYear=="Condobolin1986"| 
           LocationYear=="Katanning1990"|
           LocationYear=="Launceston1987"|
           LocationYear=="Melbourne1969"|
           LocationYear=="Waggawagga1985") %>%
  tidyr::gather("Variable", "Value",DaysToFlower,TTFloAdj) %>%
  ggplot(aes(x=month(SowingDate), y= Value, colour=Treatcultivar)) +
  geom_point(shape=21) +
 geom_smooth(se=FALSE)+
  #theme(legend.position="none")+
  facet_grid(Variable~Country, scales = "free")

#fixme makes month _number into date in month name (Apr, May etc ) 

  

```

Then, select contrasting cultivars : MtBarker, Trikala, Woogenelup 


```{r,fig.height=5, fig.width=10,warning=FALSE}
library(scales)
df_Rea4  %>% 
  filter(LocationYear=="Condobolin1986"| 
           LocationYear=="Katanning1990"|
           LocationYear=="Launceston1987"|
           LocationYear=="Melbourne1969"|
           LocationYear=="Waggawagga1985") %>%
  filter(Treatcultivar=="MtBarker"|
          Treatcultivar=="Trikkala"| 
           Treatcultivar=="Woogenellup"|
           Treatcultivar=="Nungarin")%>%
  tidyr::gather("Variable", "Value",DaysToFlower,TTFloAdj) %>%
  ggplot(aes(x=month(SowingDate), y= Value, colour=Treatcultivar)) +
  geom_point(shape=21) +
 geom_smooth(se=FALSE)+
  #theme(legend.position="none")+
  facet_grid(Variable~Country, scales = "free")


```




plot TTadjst vs. LocationYear

```{r, fig.height=5, fig.width=10}
df_Rea4  %>% 
  #filter(Treatcultivar=="Woogenellup") %>%
ggplot(aes(x=LocationYear, y= TTFloAdj, colour=Treatcultivar)) +
    geom_point(shape=21) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  theme(legend.position="none")+
  facet_grid(Country~.)
```






plot TTAdjs vs DaysToFlower

```{r, fig.height=5, fig.width=10}
df_Rea4  %>% 
  #filter(Treatcultivar=="Woogenellup") %>%
ggplot(aes(x=DaysToFlower, y= TTFloAdj)) +
  geom_point(shape=21,alpha=0.5)+
  facet_grid(Country~.)

```



Photoperiod at sowing 

```{r, fig.height=5, fig.width=10}

#Check TT 
df_Rea4  %>% 
ggplot(aes(x=Pp, y= TTFloAdj, colour=Treatcultivar)) +
    geom_point(shape=21) +
  facet_grid(Country~.)

```





