---
title: "ReAnalysis Table"
author: "CT"
date: "Thursday, December  05, 2016"
output:
  word_document: default
  html_document: default
note: Re analysis after  merged weather, calculated Tt, re calculate the TT for mid
  flowering .
---

AIM:

_this script reads the file created in previous script (script 3 where the TT to flower was adjusted to 50% ). Normalisation of TT to flower.
- graph the days and TTAdj50Flo(TT adjusted to 50% Flowering) by location and cultivar (explore location and cultivar effects )


```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```
 


```{r   loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\ReAnalysis")
getwd()


#get dataframe created in ReAnalysis1
df_Rea3 <- read.table("df_Rea3.txt",header=TRUE)


#head(df_Data)

summary(df_Rea3)

```

Use slope values (Rea3) to normalise TT flowering 

```{r}
#Flowering reference = Floref
floref <- 50

TTpercflo <- 2.2 # degree days from 5 to full (100) flowering (value calculated from DearEtAL1993_Reanalysis3 script 1/0.45)

df_Rea4 <- df_Rea3 %>%
  mutate(TTFloAdj=((floref-PercentFlower)*TTpercflo )+TTtoFlower)

summary(df_Rea4)

  
```


```{r}
#graph TTtoFlower vs TTFloAdj
#Check TT 
df_Rea4  %>% 
ggplot(aes(x=TTtoFlower, y= TTFloAdj)) +
    geom_point(shape=21)+
  xlim(500,2800)+
  geom_abline(intercept = 0, slope = 1)

```

Analysis of TTFlowerAdj vs T5-100. Is there any relationship between Time to flower and period (short orlong) for flower duration (5 to 100 %)? use DearEtAl1993 dataset to check.



```{r}
df_Rea4  %>% 
  filter(LocationYear=="Waggawagga1985"& AuthorYear=="DearEtal1993") %>%
  #tidyr::gather("Variable", "Value",PercentFlower,TTFloAdj) %>%
    ggplot(aes(x=PercentFlower, y= TTFloAdj, colour=Treatcultivar)) +
  geom_point(shape=21) 
 #theme(legend.position="none")
  #facet_grid(), scales = "free")
 
```




plot TTadj vs. sowing date

```{r , fig.height=5, fig.width=10}
df_Rea4  %>% 
  filter(Treatcultivar=="Trikkala"|
         Treatcultivar=="Dalkeith"|
           Treatcultivar=="Woogenellup"| 
           Treatcultivar=="MtBarker") %>%
ggplot(aes(x=month(SowingDate), y= TTFloAdj, colour=Treatcultivar)) +
    geom_point(shape=21) +
  scale_x_continuous(breaks = c(2,4,6,8,10,12) )+
  #scale_x_date(date_breaks = "1 month", date_labels =  "%b %Y") 
  geom_smooth()
  #facet_grid(Country~.)


```


Graph days to Flower and TTAdj vs. Location 


```{r,fig.height=5, fig.width=10}
library(scales)
df_Rea4  %>% 
  tidyr::gather("Variable", "Value",DaysToFlower,TTFloAdj) %>%
  #use this filter to analyse single locations
  #filter (Location=="Whatawhata")%>%
  ggplot(aes(x=Location, y= Value, colour=Treatcultivar)) +
  geom_point(shape=21) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
 theme(legend.position="none")+
  facet_grid(Variable~Country, scales = "free")


```

Explore the effect of sowing date 

```{r, fig.height=8 , fig.width= 20}
df_Rea4 %>%
  dplyr::select(LocationYear:Treatcultivar,DaysToFlower,TTtoFlower,Country) %>%
  gather("VarName","VarValue",DaysToFlower:TTtoFlower)  %>%
  mutate(VarName=factor(VarName, level=c("DaysToFlower","TTtoFlower"),labels=c("Days to flower","Thermal-time to flowering (oCd)"))) %>%
    mutate(Month=format(as.Date(ymd(SowingDate)),"%b")) %>%
#  ggplot(aes(x=reorder(Month,month(SowingDate)), y=DaysToFlower)) +
  #filter(Treatcultivar=="MtBarker") %>%
  ggplot(aes(x= reorder(Location,VarValue), y=VarValue))+
  geom_boxplot(alpha=0.2)+
  #geom_jitter(size=3,alpha=0.7,width = 0.1, aes(colour=reorder(Month,month(SowingDate)),shape=reorder(Month,month(SowingDate))))+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14))+
  geom_jitter(size=3,alpha=0.7,width = 0.1, aes(shape= Country, colour=reorder(Month,month(SowingDate))))+
  #theme(legend.position="none")+
  labs(x="Experiment location", y="Time to flower")+
  theme(axis.text.x=element_text(angle = 0, hjust = 0, size= 9))+
  theme(axis.text.y=element_text(size= 20))+
  theme_bw(base_size=20)+
    facet_grid(Country~VarName, scales="free") +
 # facet_wrap(~VarName, scales="free") +
  coord_flip() + theme(legend.position="top") + guides(colour=guide_legend(title="Sowing month"))+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  theme(text = element_text(size=26))+
   
   
   #make TT target labels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
theme(axis.text.x = element_text(26))
  
ggsave("plot_DaysTTFlowerLocation.png", width=16, height=8, dpi=500)
```


RE do black and white 

Explore the effect of sowing date 

```{r, fig.height=8 , fig.width= 20}
df_Rea4 %>%
  dplyr::select(LocationYear:Treatcultivar,DaysToFlower,TTtoFlower,Country) %>%
  gather("VarName","VarValue",DaysToFlower:TTtoFlower)  %>%
  mutate(VarName=factor(VarName, level=c("DaysToFlower","TTtoFlower"),labels=c("Days to flower","Thermal-time to flowering (oCd)"))) %>%
    mutate(Month=format(as.Date(ymd(SowingDate)),"%b")) %>%
#  ggplot(aes(x=reorder(Month,month(SowingDate)), y=DaysToFlower)) +
  #filter(Treatcultivar=="MtBarker") %>%
  ggplot(aes(x= reorder(Location,VarValue), y=VarValue))+
  geom_boxplot(alpha=0.2)+
  #geom_jitter(size=3,alpha=0.7,width = 0.1, aes(colour=reorder(Month,month(SowingDate)),shape=reorder(Month,month(SowingDate))))+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14))+
  #geom_jitter(size=3,alpha=0.7,width = 0.1, aes(shape= Country, colour=reorder(Month,month(SowingDate))))+
  
  
  geom_jitter(size=3,alpha=0.7,width = 0.1, aes(shape= reorder(Month,month(SowingDate), colour=Country)))+
  #theme(legend.position="none")+
  labs(x="Experiment location", y="Time to flower")+
  theme(axis.text.x=element_text(angle = 0, hjust = 0, size= 9))+
  theme(axis.text.y=element_text(size= 20))+
  theme_bw(base_size=20)+
    facet_grid(Country~VarName, scales="free") +
 # facet_wrap(~VarName, scales="free") +
  coord_flip() + theme(legend.position="top") + guides(colour=guide_legend(title="Sowing month"))+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  theme(text = element_text(size=26))+
   
   
   #make TT target labels  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
theme(axis.text.x = element_text(26))
  
#ggsave("plot_DaysTTFlowerLocation.png", width=16, height=8, dpi=500)
```




Then select Contrasting cultivars to compare : eg: Trikkala, Tallarook, MtBarker

```{r,fig.height=5, fig.width=10}

library(scales)
df_Rea4  %>% 
  tidyr::gather("Variable", "Value",DaysToFlower,TTFloAdj) %>%
  filter(Treatcultivar=="Trikkala"| 
           Treatcultivar=="Nungarin"|
           Treatcultivar=="Denmark"|
           Treatcultivar=="MtBarker"|
           Treatcultivar=="Bena"|
           Treatcultivar=="Tallarook"|
           Treatcultivar=="Dalkeith") %>%
  ggplot(aes(x=Location, y= Value, colour=Treatcultivar)) +
  geom_boxplot(alpha=0.2)+
  geom_jitter(width = 0.1, aes(colour=Treatcultivar))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
 #theme(legend.position="none")+
  labs(x=" Location", y="    oCd        Days")+
  facet_grid(Variable~Country, scales = "free")

summary (df_Rea4)

```

##This graph displays the TTAdjo50Flo!! 

```{r, fig.height=8 , fig.width= 20}

str(df_Rea4)

df_Rea4 %>%
  dplyr::select(LocationYear:Treatcultivar,DaysToFlower,TTtoFlower,Country) %>%
  filter(Treatcultivar=="Trikkala"| 
           Treatcultivar=="Nungarin"|
           Treatcultivar=="Denmark"|
           Treatcultivar=="MtBarker"|
           Treatcultivar=="Bena"|
           Treatcultivar=="Tallarook"|
           Treatcultivar=="Woogenellup"|
           Treatcultivar=="Dalkeith")%>%


  
  gather("VarName","VarValue",DaysToFlower:TTtoFlower)  %>%
  mutate(VarName=factor(VarName, level=c("DaysToFlower","TTtoFlower"),labels=c("Days to flower","Thermal-time to flowering (oCd)"))) %>%
    mutate(Month=format(as.Date(ymd(SowingDate)),"%b")) %>%
#  ggplot(aes(x=reorder(Month,month(SowingDate)), y=DaysToFlower)) +
  #filter(Treatcultivar=="MtBarker") %>%
  ggplot(aes(x= reorder(Location,VarValue), y=VarValue))+
  geom_boxplot(alpha=0.2)+
  #geom_jitter(size=3,alpha=0.7,width = 0.1, aes(colour=reorder(Month,month(SowingDate)),shape=reorder(Month,month(SowingDate))))+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11,12,13,14))+
  geom_jitter(size=3,alpha=0.7,width = 0.1, aes(shape= Country, colour=Treatcultivar))+
  #theme(legend.position="none")+
  labs(x="Experiment location", y="Time to flower")+
  theme(axis.text.x=element_text(angle = 0, hjust = 0, size= 9))+
  theme(axis.text.y=element_text(size= 18))+
  theme_bw(base_size=18)+
    facet_grid(.~VarName, scales="free") +
 # facet_wrap(~VarName, scales="free") +
  coord_flip() + theme(legend.position="top") + guides(colour=guide_legend(title="Cultivar "))

ggsave("plot_DaysTTFlowerCultivar.png", width=12, height=6, dpi=400)
```





Show genotype effect (need to fix it)


```{r,fig.height=5, fig.width=10}

library(scales)
df_Rea41 <- df_Rea4  %>% 
  mutate(Month=format(as.Date(ymd(SowingDate)),"%b")) %>%
  tidyr::gather("Variable", "Value",DaysToFlower,TTFloAdj) %>%
  filter(Treatcultivar=="Trikkala"| 
           Treatcultivar=="Dalkeith"|
           Treatcultivar=="Karridale"|
           Treatcultivar=="Nungarin"|
           Treatcultivar=="Denmark"|
           Treatcultivar=="MtBarker"|
           Treatcultivar=="Bena"|
           Treatcultivar=="Woogenellup"|
           Treatcultivar=="Tallarook"|
           Treatcultivar=="Larisa") 
  df_Rea41 %>%
  ggplot(aes(x=Location, y= Value, colour=Treatcultivar)) +
  geom_boxplot(alpha=0.2)+
  geom_jitter(width = 0.1, aes(colour=Treatcultivar))+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))+
 #theme(legend.position="none")+
    ylim(0, 2500)+
  labs(x=" Location", y="    oCd  ")+
    theme(text = element_text(size = 12))+
  facet_wrap(~Month, ncol= 5, scales = "free")
#facet_grid(Variable~.,scale="free") 



#summary (df_Rea4)
```





```{r, fig.height=5, fig.width=10}
df_Rea4  %>% 
  tidyr::gather("Variable", "Value",DaysToFlower,TTFloAdj) %>%
  mutate(Month=format(as.Date(ymd(SowingDate)),"%b")) %>%
  
  ggplot(aes(x=reorder(Month,month(SowingDate)), y= Value)) +
  labs(x=" Sowing Month", y="   oCd      Days  ")+
  #geom_boxplot(alpha=0.2)+
  geom_point(alpha=0.2)+
  geom_boxplot(alpha=0.2)+
  geom_jitter(alpha=0.2,width = 0.3, aes(colour=Location))+
  labs(x=" Sowing Month", y="                oCd                Days ")
  #facet_wrap(~Country)
  #geom_point(shape=21) +
# theme(legend.position="none")+
 # facet_grid(Variable~SowTreat, scales = "free")

```

```{r}
summary (df_Rea4)
```




```{r, fig.height=5, fig.width=10}
# df_Rea4  %>% 
#   tidyr::gather("Variable", "Value",DaysToFlower,TTFloAdj) %>%
#   filter(Treatcultivar=="MtBarker")%>%
#   mutate(Month=format(as.Date(ymd(SowingDate)),"%b")) %>%
#   ggplot(aes(x=reorder(Month,month(SowingDate)), y= Value, colour=Location)) +
#   labs(x=" Sowing Month", y="   oCd      Days  ")+
#   geom_boxplot(alpha=0.2)+
#   geom_jitter(alpha=0.2,width = 0.3, aes(colour=Location))+
#   labs(x=" Sowing Month", y="Days to flower")+
#   
#   #facet_wrap(~Country)
#   #geom_point(shape=21) +
# # theme(legend.position="none")+
#   facet_grid(Variable~Country, scales = "free")

```




Then, select datasets with more than one sowing date in different months:

Condobolin1986
Katanning1990
Launceston1987
Melbourne1969
Waggawagga1985

This df will be df_Rea5

```{r,fig.height=5, fig.width=10,warning=FALSE}
library(scales)
df_Rea5 <-df_Rea4  %>% 
  filter(LocationYear=="Condobolin1986"| 
           LocationYear=="Katanning1990"|
           LocationYear=="Launceston1987"|
           LocationYear=="Melbourne1969"|
           LocationYear=="Waggawagga1985") %>%
  tidyr::gather("Variable", "Value",DaysToFlower,TTFloAdj)

  df_Rea5 %>% 
  ggplot(aes(x=Pp, y= Value, colour=Treatcultivar)) +
  geom_point(shape=21) +
 geom_smooth(se=FALSE)+
  #theme(legend.position="none")+
  facet_grid(Variable~Country, scales = "free")

#fixme makes month _number into date in month name (Apr, May etc ) 

  

```


Then, select Location year with different cultivars in a range of Pp. This will be df_Rea6.
indexLocCult = combination of LocationYear and cultivar.


```{r,fig.height=5, fig.width=10,warning=FALSE}

df_Rea6 <- df_Rea5 %>% 
  filter(LocationYear!="Waggawagga1985") %>%
  mutate(indexLocCult=paste0(LocationYear,"_",Treatcultivar))
  
  df_Rea6 %>%
  ggplot(aes(x=month(SowingDate), y= Value, colour=indexLocCult)) +
  geom_point(shape=21) +
 geom_smooth(se=FALSE)+
  #theme(legend.position="none")+
  facet_grid(Variable~Country, scales = "free")

summary(df_Rea6)
```


```{r}

#Next step include Pp (next script Reanalysis 5). Use table created here! 


write.table(df_Rea6, "df_Rea6.txt")

```

