---
title: "Germination Seeds different Temperatures  4Cultivar"
author: "CT"
date: " September  , 2015"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)  
library(agricolae)
library(knitr)
library (lubridate)

```

This script reads the file created in script 1  -  df_SeedGermCum.txt


```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedGermTemp")
getwd()

#create file
df_seed <- read.table("df_SeedGermCum.txt",header=TRUE)
str(df_seed)
# change format with  base R)
#df_seed$Date <- dmy(df_seed$Date)

# jeito 2 de trocar formato (usando dplyr)
df_seed <- df_seed %>%
  mutate(Temp = as.numeric(Temp), 
         Block = as.factor(Block),
         PercGerm_cum= as.numeric(PercGerm_cum))


summary(df_seed) # explore values
str(df_seed) # check formats
head(df_seed) # see to rows
tail(df_seed)

```

#Need to add the ActTemp  (this step also in Script 2)


```{r}
df_seed <- df_seed %>%
  mutate(ActTemp=Temp*1)%>%
  mutate(ActTemp=as.factor(ActTemp))%>%
  #convert ActTemp in factor and then replace labels 
  mutate (ActTemp= factor(ActTemp, levels=c("2.5", "5", "7.5", "10", "12.5","15", "17.5", "20", "25", "30","35" ),labels=c("2", "5", "7", "9", "12.5","15", "17", "20", "25", "30","35" )))


  
  str(df_seed)
  
  #then reconvert ActTemp in numerical 
  
  df_seed<-df_seed%>%
    mutate(ActTemp=as.character(ActTemp))%>%
    mutate(ActTemp=as.numeric(ActTemp))
  
  str(df_seed)



```



Calculate the maximum germination in each temperature 

```{r}

 dMax<- df_seed %>%
  group_by(Temp,Cultivar,ActTemp) %>% 
dplyr::select(Temp,Cultivar,PercGerm_cum) %>%
  group_by(Cultivar,Temp) %>%
  summarise_all(funs(max,sd))%>%
  mutate(max=as.numeric(PercGerm_cum_max),
         sd=as.numeric(PercGerm_cum_sd))
  



```

Create a dataframe with max germ also per block to add to dataframe by cultivar origin. 


```{r}

 dMaxBlock<- df_seed %>%
  group_by(Temp,Cultivar,ActTemp) %>% 
dplyr::select(Temp,Cultivar,PercGerm_cum, Block) %>%
  group_by(Cultivar,Temp, Block) %>%
  summarise_all(funs(max,sd))%>%
  mutate(max=as.numeric(PercGerm_cum_max),
         sd=as.numeric(PercGerm_cum_sd))
 
#write table to combine cultivars by origin in new dataframe 

write.table(dMaxBlock, "df_SeedGermMaxBlock.txt")


```





This graph uses the set Temperature (Temp)! 

```{r, fig.height=5, fig.width=10}
#check format
str(dMax)

#graph it here error bars already represent the SE (std/sqrtn = 4)
dMax %>%
  
  ggplot(aes(x=Temp, y=max, colour=Cultivar, shape=Cultivar  ))+  # do percentage here
  geom_point(size =4)+
  #geom_smooth()+
  geom_line()+
  geom_errorbar(aes(ymin=max-sd/4,
  ymax=max+sd/4))+
     theme_bw(base_size=20)+
#   #facet_wrap (~SowTreat,ncol=4, scales = "free")+
#   ylim(0,100)+
#   #labs(x="Hours",y="Cummulative Germination Percnet(%)")+
#   #facet_grid(.~Temp)
#   #facet_wrap(.~Temp, ncol=6)
facet_wrap(~Cultivar,ncol=2, scales = "free")+
#   theme_bw()+
  #scale_x_continuous(breaks = c(5,10,15,20,25,30,35))+
  ylim(0, 120)+
  ylab(expression(Maximum~Germination~"(%)"))+
  theme(text = element_text(size=18))+
  xlab(expression(Temperature~"("^"o"*"C)"))+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 11))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 12))+
  #xlim(0, 40)+
  #labs(y="Maximum germination Percent (%)",x="Temperature")+ 
  geom_abline(intercept = 100, slope = 0, linetype=2)

#ggsave("plot_MaxGerm.png", width=12, height=6, dpi=400)

```

produce the graph with the max error bar (this is just a draft ...the real one in the next chunck)


```{r, fig.height=5, fig.width=10}

#then create the error bar position
#Here how to create the end error bar with max Sd 
# find size of bar per cultivar and temp
# find single position of x y to put the bar

#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.1 # extra position for single error bar
x_max<-max(dMax$Temp)
y_max<-max(dMax$max)


sd_df <- dMax %>% 
  group_by(Cultivar) %>%
  dplyr::select(sd)%>%
  summarise_all(funs(max))%>%
  #summarise(max_sd = max(sd)) %>% 
  ungroup() %>%
  rowwise() %>%
  mutate(Temp = x_max*extraPos, max = y_max*extraPos, max_sd=sd)

summary(sd_df)


#make a graph 
#then graph remember sd/2 because of 4 replicates 


dMax %>% 
  #select( Variable, Cultivar, Temp, mean,sd) %>%
  ggplot(aes(x=Temp, y=max)) + 
#  geom_point(data=sd_df,aes(x=DAS,y=NumberRun_mean)) +
  geom_point(aes(shape=Cultivar), size=6) +
  scale_shape_manual(values = c(1,2,0,7)) +
  geom_errorbar(data=sd_df, aes(ymin=max-max_sd/2,
                    ymax=max+max_sd/2), width=5)+
  facet_wrap (~Cultivar,ncol=2)+
  ylim(0,140 ) +
  ylab(expression(Maximum~Germination~"(%)"))+
  theme(text = element_text(size=20))+
  xlab(expression(Temperature~"("^"o"*"C)"))+
  #labs(y="Maximum ",x="Temperature")+
  theme_grey(base_size = 20) +
  theme_bw()+
  # geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 100,  slope = 0, linetype=2)+
   #geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
  
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   
  #label sizes 
theme(text = element_text(size = 22))

#ggsave("plot_MaxGerm.png", width=12, height=6, dpi=400)

```



Make the graph using actual temperature data  (Act Temp) as well.Saved graph!  


```{r, fig.height=5, fig.width=10}

#then create the error bar position
#Here how to create the end error bar with max Sd 
# find size of bar per cultivar and temp
# find single position of x y to put the bar

#check name columns 

str(dMax)



#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.1 # extra position for single error bar
x_max<-max(dMax$ActTemp_max)
y_max<-max(dMax$max)


sd_df <- dMax %>% 
  group_by(Cultivar) %>%
  dplyr::select(sd)%>%
  summarise_all(funs(max))%>%
  #summarise(max_sd = max(sd)) %>% 
  ungroup() %>%
  rowwise() %>%
  mutate(ActTemp_max = x_max*extraPos, max = y_max*extraPos, max_sd=sd)

summary(sd_df)


#make a graph 
#then graph remember sd/2 because of 4 replicates 


dMax %>% 
  #select( Variable, Cultivar, Temp, mean,sd) %>%
  ggplot(aes(x=ActTemp_max, y=max)) + 
#  geom_point(data=sd_df,aes(x=DAS,y=NumberRun_mean)) +
  geom_point(aes(shape=Cultivar), size=6) +
  scale_shape_manual(values = c(1,2,0,7)) +
  geom_errorbar(data=sd_df, aes(ymin=max-max_sd/2,
                    ymax=max+max_sd/2), size=1)+
  facet_wrap (~Cultivar,ncol=2)+
  ylim(0,140 ) +
  ylab(expression(Maximum~Germination~"(%)"))+
  theme(text = element_text(size=20))+
  xlab(expression(Temperature~"("^"o"*"C)"))+
  #labs(y="Maximum ",x="Temperature")+
  theme_grey(base_size = 20) +
  theme_bw()+
  # geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 100,  slope = 0, linetype=2)+
   #geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
  
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
   
  #label sizes 
theme(text = element_text(size = 24))

ggsave("plot_MaxGerm.png", width=12, height=6, dpi=500)

```




```{r, fig.height=5, fig.width=10}

#then create the error bar position
#Here how to create the end error bar with max Sd 
# find size of bar per cultivar and temp
# find single position of x y to put the bar

#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.1 # extra position for single error bar
x_max<-max(dMax$ActTemp)
y_max<-max(dMax$max)


sd_df <- dMax %>% 
  group_by(Cultivar) %>%
  dplyr::select(sd)%>%
  summarise_all(funs(max))%>%
  #summarise(max_sd = max(sd)) %>% 
  ungroup() %>%
  rowwise() %>%
  mutate(ActTemp = x_max*extraPos, max = y_max*extraPos, max_sd=sd)

summary(sd_df)


#make a graph 
#then graph remember sd/2 because of 4 replicates 


dMax %>% 
  #select( Variable, Cultivar, Temp, mean,sd) %>%
  ggplot(aes(x=ActTemp, y=max)) + 
#  geom_point(data=sd_df,aes(x=DAS,y=NumberRun_mean)) +
  geom_point(aes(shape=Cultivar), size=4) +
  scale_shape_manual(values = c(1,2,0,7)) +
  geom_errorbar(data=sd_df, aes(ymin=max-max_sd/2,
                    ymax=max+max_sd/2), width=4)+
  facet_wrap (~Cultivar,ncol=2)+
  ylim(0,160 ) +
  ylab(expression(Maximum~Germination~"(%)"))+
  theme(text = element_text(size=18))+
  xlab(expression(Temperature~"("^"o"*"C)"))+
  #labs(y="Maximum ",x="Temperature")+
  theme_grey(base_size = 16) +
  theme_bw()+
  
  # geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 100,  slope = 0, linetype=2)+
   #geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
  #remove grid lines 
    theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
  
  
theme(text = element_text(size = 20))

ggsave("plot_MaxGerm.png", width=12, height=6, dpi=400)

```








Get the means/stats  for temperature and cultivar 
Variable : Max Germination 

```{r}
  #Prepare data frame for ANOVA
df_s<- df_seed %>%
  group_by(Temp,Cultivar,Block,Plot) %>% # 
dplyr::select(Temp,Cultivar,PercGerm_cum) %>%
  summarise_all(funs(max(PercGerm_cum)))


#-------------------------------------------------
# anova 
file <- df_s

file.subset <- file 

head(file.subset)
summary(file.subset)

```



```{r}

#ANOVA
my.anova <- aov(PercGerm_cum~ Cultivar*Temp + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
summary(my.anova)
```

```{r}

#(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "Temp"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar", "Temp"), alpha= 0.05, p.adj="none"))
```



```{r}

(LSD.test(my.anova, c( "Temp"), alpha= 0.05, p.adj="none"))
```



Get the means/stats  for temperature equals 2.5 (filter only this temperature ) and cultivar 
Variable : Max Germination 

```{r}
  #Prepare data frame for ANOVA
df_2.5<- df_seed %>%
  filter(Temp==2.5)%>%
  group_by(Cultivar,Block,Plot) %>% 
dplyr::select(Temp,Cultivar,PercGerm_cum) %>%
  summarise_all(funs(max(PercGerm_cum)))


df_3035<- df_seed %>%
  filter(Temp==30|Temp==35)%>%
  group_by(Cultivar,Block,Plot) %>% 
dplyr::select(Temp,Cultivar,PercGerm_cum) %>%
  summarise_all(funs(max(PercGerm_cum)))


#-------------------------------------------------
# anova 
#file <- df_2.5
file <- df_3035

file.subset <- file 

head(file.subset)
summary(file.subset)

```



```{r}

#ANOVA
my.anova <- aov(PercGerm_cum~ Cultivar + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
summary(my.anova)
```

```{r}

(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c( "Temp"), alpha= 0.05, p.adj="none"))
#(LSD.test(my.anova, c("Cultivar", "Temp"), alpha= 0.05, p.adj="none"))
```
