---
title: "Germination Seeds different Temperatures  4Cultivar"
author: "CT"
date: " September  2017"
output: html_document
---
# this script calculates the TT based on Tb and T suboptimal for each cultivar 

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)  
library(agricolae)
library(knitr)
library (lubridate)

```


```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedGermTemp")
getwd()

#create file Use here df_RAteGErm2 as it has the zeros to include in graphics 
df_seed <- read.table("df_RateGerm.txt",header=TRUE)
str(df_seed)
# change format with  base R)
#df_seed$Date <- dmy(df_seed$Date)

# jeito 2 de trocar formato (usando dplyr)
df_seed <- df_seed %>%
  mutate(Temp = as.numeric(Temp), 
         Block = as.factor(Block),
         Rate= as.numeric(Rate))


summary(df_seed) # explore values
str(df_seed) # check formats
```

 Ttsub= from Tb to Topt; Ttsup= from Topt to Tmax.
 Here select first cultivar Antas range of suboptimal is Tb= -2.7
 
 
```{r}
dfTT <-df_seed %>%
  dplyr:: select(-Rate,-PercentRelative)%>%
  filter(Cultivar=="Antas")%>%
  subset(DAS50E>0.7 )%>%
  subset(Temp>0.05 & Temp<19.7)%>%
  mutate(TTzero=(Temp*DAS50E))%>%
  mutate(TTbased=((Temp-(-2.7))*DAS50E))

dfTTAntasTTsub <- dfTT %>%
  group_by( Cultivar) %>%
  dplyr::select( TTbased) %>%
  summarise_all(funs(mean,sd))%>%
  mutate(SE=sd/2)
  


```
 
 for Denmark : Tb = 1.7

```{r}

dfTTD <-df_seed %>%
  dplyr:: select(-Rate,-PercentRelative)%>%
  filter(Cultivar=="Denmark")%>%
  subset(DAS50E>0.7 )%>%
  subset(Temp>0.05 & Temp<19.7)%>%
  mutate(TTzero=(Temp*DAS50E))%>%
  mutate(TTbased=((Temp-1.7)*DAS50E))

dfTTDenmarkTTsub <- dfTTD %>%
  group_by( Cultivar) %>%
  dplyr::select( TTbased) %>%
  summarise_all(funs(mean,sd))%>%
  mutate(SE=sd/2)
```


Monti, Tb= -0.7

```{r}
dfTTM <-df_seed %>%
  dplyr:: select(-Rate,-PercentRelative)%>%
  filter(Cultivar=="Monti")%>%
  subset(DAS50E>0.7 )%>%
  subset(Temp>0.05 & Temp<19.7)%>%
  mutate(TTzero=(Temp*DAS50E))%>%
  mutate(TTbased=((Temp-(-0.7))*DAS50E))

dfTTMontiTTsub <- dfTTM %>%
  group_by( Cultivar) %>%
  dplyr::select( TTbased) %>%
  summarise_all(funs(mean,sd))%>%
  mutate(SE=sd/2)


```


Narrikup, Tb= 0.8

```{r}

dfTTN <-df_seed %>%
  dplyr:: select(-Rate,-PercentRelative)%>%
  filter(Cultivar=="Narrikup")%>%
  subset(DAS50E>0.7 )%>%
  subset(Temp>0.05 & Temp<19.7)%>%
  mutate(TTzero=((Temp-0.8)*DAS50E))%>%
  mutate(TTbased=((Temp-1.7)*DAS50E))

dfTTNarrikupTTsub <- dfTTN %>%
  group_by( Cultivar) %>%
  dplyr::select( TTbased) %>%
  summarise_all(funs(mean,sd))%>%
  mutate(SE=sd/2)

```

then bind all df with all plots to perform anova with the TT calculated with the estimated base temperatures 
dfTT; dfTTD; dfTTM, dfTTN


```{r}


totalTT <- rbind(dfTT, dfTTD, dfTTM, dfTTN)

```

then ANOVA 

```{r}


#prepare for  anova 
file <- totalTT

file.subset <- file 

head(file.subset)
summary(file.subset)

```


```{r}

#ANOVA
my.anova <- aov(TTbased~ Cultivar + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
summary(my.anova)

```


```{r}

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
```


summary of linear regressions :

Appendix ZZ. Table XX. Segmented linear regressions and coefficients applied to estimate cardinal temperatures for germination of sub clover cultivars 'Antas', 'Denmark', 'Monti' and 'Narrikup' under constant temperatures. 
Cultivar	Regression 	intercept	slope	R2	P value
'Antas'	ascending	0.08 (±0.04)	0.03 (±0.002) 	93	<0.001
'Antas'	descending	1.8 (±0.6)	-0.05 (±0.02)	84	0.3
Denmark'	ascending	-0.07 (±0.04)	0.042 (±0.004)	95	<0.001
Denmark'	descending	1.7 (±0.9)	-0.043(±0.04)	79	0.11
Monti'
ascending
0.02(±0.04)
0.03(±0.002)
94
<0.001
Monti'
descending
1.0 (±0.34)
-0.03(±0.006)
84
0.3
Narrikup'
ascending
-0.025(±0.06)
0.03(±0.006)
85
0.003
Narrikup'
descending
0.9(±0.24)
-0.02(±0.008)
83
0.3




Calculations Ttsub and Ttsup

1/t75=bo+b1T (for the positive linear portion) (1)
1 /t75 = b2+b3T (for the negative linear portion) (2) 
The regression coefficient can then be related to Tb, Tmax and Tt as:
and
(3) (4)
Ttsub=1/b1 (5) 
Ttsub = -1/b3



```{r}





```


Graph DAS 50 vs temperature 


```{r, fig.height=5, fig.width=10}
#check format
#str(dMax)

# #graph it here error bars already represent the SE (std/sqrtn = 4)
a <- dfTT %>%
#   #ungroup()%>%
#   #mutate(Temp=as.numeric(Temp))%>%
group_by( Cultivar) %>%
  dplyr::select(TT)%>%
  summarise_all(funs(mean,sd)) 
  
# define position of bar and errorbar
dodge_x <- position_dodge(width = 0.9)
  # here sd/4 correspond to standard error 
  a %>%
  ggplot(aes(x=Cultivar, y=(mean), fill=Cultivar)) +
  geom_bar(stat="identity",position = dodge_x) +
  geom_errorbar(aes(ymin=mean-sd/4,
                    ymax=mean+sd/4),
                width=0.25, size=0.3,position=dodge_x)   +
  theme_grey(base_size = 16) +
    theme_bw()+
   theme(text = element_text(size=16))+
  ylab(expression(Thermal~time ~"("^"o"*"Cd)"))+
  theme(axis.text.x=element_text(angle = +0, hjust = 0, size= 16))+
  theme(axis.text.y=element_text(angle = +0, hjust = 0, size= 16))
  
   
  

```

Get the means/stats  for  cultivar 
Vaariable : TT

```{r}
  #Prepare data frame for ANOVA
df_s<- dfTT
  
  


#-------------------------------------------------
# anova 
file <- df_s

file.subset <- file 

head(file.subset)
summary(file.subset)

```

```{r}

#ANOVA
my.anova <- aov(TT~ Cultivar + Block, data = file.subset)
#my.anova <- aov(TSW ~ Cultivar*Depth + Block, data = file.subset)
summary(my.anova)
```

```{r}

#(LSD.test(my.anova, c( "Cultivar"), alpha= 0.05, p.adj="none"))

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
#Note LSD interaction from Genstat was calculated as 0.7029 



#(LSD.test(my.anova, c( "Temp"), alpha= 0.05, p.adj="none"))

```



```{r}

(LSD.test(my.anova, c( "Temp"), alpha= 0.05, p.adj="none"))
```




 

