---
title: "Germination Seeds lab many temps 4 cultivars "
author: "CT"
date: "01.10.2017"
output: html_document
---

This script does this:

- get the dataframe produced in Calc1  
- Calculate the DAS and TT for the 50% emergence by a loop interpolating points
- Calculate the rate of emergence (1/Days)
_Graph results  


```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
```


```{r loadFile}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergenceIv2")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedGermTemp")
getwd()

#create file
df_emerg1 <- read.table("df_SeedGermCum.txt",header=TRUE)


str(df_emerg1)
```

Format changes 
```{r}
#change formats 

df_emerg1$DAS <- as.numeric(df_emerg1$DAS )
df_emerg1$Block <- as.factor(df_emerg1$Block)
df_emerg1$Plot <- as.factor(df_emerg1$Plot)
df_emerg1$Temp <- as.factor(df_emerg1$Temp)

str(df_emerg1)

```

Calculate 50 PercentEmergence  

```{r SummariseDf}

# This step is now unnecessary as we want Plot values anyway (FIXME)
df_50_Perc <- df_emerg1 %>%
  mutate(PercEmerg = as.numeric(PercGerm_cum)) %>%
  group_by(Plot, Block,Cultivar,Temp, PercEmerg) %>%
  summarise(av_Perc = mean(PercEmerg), 
            #av_TT = mean(TT_to_emerg),
            av_DAS = mean(DAS)
            )

str(df_50_Perc)
summary(df_50_Perc)
head(df_50_Perc)

# try to subset abd see if loop works 

#df15<- df_50_Perc %>%
  #subset(Temp == 15)

# write.table(df_50_Perc, "df_50_PercEmerg.txt") # FIXME: this file is not yet 50%

#  loop to calculate tt_50p_flow for each var x sd x cv
#cv <- unique(df_50_Perc$Cultivar)
#var <- unique(df_50_Perc$PercEmerg)
#sow <- unique(df_50_Perc$SowTreat)
#sowd <- unique(df_50_Perc$SowingDate)
plots <- unique(df_50_Perc$Plot)
 

 #create empty df
# df_tt_50p_emerg <- data.frame(Plot = NULL,
#                               Block = NULL,
#                              SowingD = NULL,
#                              Cultivar = NULL, 
#                              SowTreat = NULL,
#                              PercEmerg = NULL, 
#                              TT50Em = NULL)

#loop trough each combination of factor levels

for(p in 1:length(plots)) {
#  for(j in 1:length(var)){
 #   for(k in 1:length(sow)){
      
      # clean value holders
      DAS_50p_emerg <- 0
      #tt_50p_emerg <- 0
      
      #FIX ME Partially set 
    
     # print(paste0(cv[i]," ",var[j]," ", sow[k]))
      # filter for each combination

  df_sub <- df_50_Perc %>%
    # subset(Cultivar == as.character(cv[i]) &
    # Plot == as.character(var[j]) &
    # Block == as.character(var[b]) &
    # SowTreat == as.character(sow[k])) %>%
    subset(Plot == plots[p]) %>%
    arrange(PercEmerg)
  
  df_sub
  head(df_sub)
  # create percentage with maximum value recorded 
  # to avoid crossing the 50% line twice
  
  df_sub$av_Perc_max <- 0 # create new col
  
  for(z in 1:nrow(df_sub)) {
    
    df_sub$av_Perc_max[z] <- max(df_sub$av_Perc[z],
                                 df_sub$av_Perc_max[z-1])
    
  }
  
  df_sub
  head(df_sub)
  tail(df_sub)

  # Interpolate 
  y_ref <- 50 # y value where we want to find x by interpolation
  
  # interpolate
  #find DAS at 50 Pecent Emergence 

  tryCatch(  
  DAS_50p_emerg <- approx(df_sub$PercEmerg, 
  df_sub$av_DAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  DAS_50p_emerg <- NA
  }
)
#   #find TT at 50 Pecent Emergence
#   tryCatch(  
#   tt_50p_emerg <- approx(df_sub$av_Perc, 
#   df_sub$av_TT , xout = y_ref, rule = 1)$y,
#   error = function(e) 
#   {
#   tt_50p_emerg <- NA
#   }
# )

  df_temp <- NULL
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             PercEmerg = df_sub$PercEmerg[1], 
                             Temp = df_sub$Temp[1],
                             Plot = df_sub$Plot[1],
                             Block = df_sub$Block[1],
                             DAS50E = DAS_50p_emerg)
  
                          print(p)
  
  if(p == 1) {
    df_tt_50p_emerg <- df_temp
  } else {
   df_tt_50p_emerg <- rbind(df_tt_50p_emerg,df_temp) 
  }                     
  
#    } 
  } # end plot loop




```

```{r}
summary(df_tt_50p_emerg)

write.table(df_tt_50p_emerg,"df_tt_50p_emerg.txt")

summary(df_tt_50p_emerg)
```

Graph results:  


Data visualisation and means check.
```{r, fig.height=5, fig.width=10}

#Here just to check means 
# mean <-df_tt_50p_emerg %>%
#   group_by(SowTreat, SowingDate, Cultivar,DAS50E) %>%
#   summarise_each(funs(mean,sd))
# summary (mean)


df_tt_50p_emerg %>%
  group_by(Temp, Cultivar) %>%
  dplyr::select(DAS50E) %>%
  summarise_each(funs(mean,sd)) %>%
  
  # if needed to exclude cultivars for analysis use filter 
  # filter( Cultivar != "Woogenellup" &
  #        Cultivar != "Monti" &
  #        Cultivar != "Antas" &
  #        Cultivar != "Denmark" &
  #        Cultivar != "Leura") %>%
         
  
ggplot(aes(x=Temp, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Temperature",y="Days to 50% emergence ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 12))+
  theme(axis.text.y = element_text(angle = 0, hjust = 1, size = 12))+
  geom_errorbar(aes(ymin=mean-(sd/2)/2,
  ymax=mean+(sd/2)/2))+
  facet_wrap(~Cultivar,ncol=2, scales = "free")+
  theme_bw()
 


```

Calculate the rate of emergence (1/Days to 50% emergence)

```{r}

#try 1/DAS50% = Rate

df_RateEmerg <- df_tt_50p_emerg %>%
  mutate(Rate=1/DAS50E)

  summary(df_RateEmerg)
  
  
  
```

graph and save a dataframe as txt .Here data shows SE as sd/2/2
```{r, fig.height=5, fig.width=10}
df_RateEmerg %>%
  group_by(Temp, Cultivar) %>%
  #filter(Cultivar=="Woogenellup")%>%
 # filter (SowTreat== "S2"| SowTreat== "S2"|SowTreat== "S2"|)
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=Temp, y=mean, colour=Cultivar, shape=Cultivar)) +
  geom_point() +
  geom_line() +
  labs(x="Temperature",y="1/ Days to 50% emergence ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size =14 ))+
  theme(axis.text.y = element_text(angle = 0,  size =16 ))+
  geom_errorbar(aes(ymin=mean-(sd/2)/2,
  ymax=mean+(sd/2)/2))+
  facet_wrap(~Cultivar,ncol=2, scales = "free")+
  theme_bw()
  
  write.table(df_RateEmerg, "df_RateGerm.txt")
```



End of this script 

