---
title: "Germination Seeds lab many temps 4 cultivars "
author: "CT"
date: "01.10.2017"
output: html_document
---

This script does this:

- get the dataframe produced in Calc1  
- Calculate the DAS and TT for the 50% emergence by a loop interpolating points
- Calculate the rate of emergence (1/Days)
_Graph results  


```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
library(gridExtra)
```


```{r loadFile}

setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\SeedGermTemp")
getwd()

#create file
df_emerg1 <- read.table("df_SeedGermCum.txt",header=TRUE)


str(df_emerg1)
```

Format changes 
```{r}
#change formats 

df_emerg1$DAS <- as.numeric(df_emerg1$DAS )
df_emerg1$Block <- as.factor(df_emerg1$Block)
df_emerg1$Plot <- as.factor(df_emerg1$Plot)
#df_emerg1$Temp <- as.factor(df_emerg1$Temp)

str(df_emerg1)

```

Calculate the maximum germination percentage observed in each plot 

```{r}

df_emerg2 <-df_emerg1 %>%
group_by(Plot)%>%
  dplyr::select(PercGerm_cum)%>%
  summarise_all(funs(max))%>%
  mutate(MaxGermPerc=PercGerm_cum)%>%
  select(-PercGerm_cum)
  


```

now merge the two dataframes by plot calculate the Percentage in relation to the maximum germination observed (do as PercGerm_cum/*100)

```{r}
df_3<-merge(df_emerg1,df_emerg2, by="Plot")

str (df_3)

df_3 <-df_3%>%
  mutate(PercentRelative=(PercGerm_cum/MaxGermPerc*100))

```


#Add here a column with the actual temperatures (ActTemp) instead of using the Set temperature (Temp)



```{r}

df_3a <- df_3 %>%
  mutate(ActTemp=Temp*1)%>%
  mutate(ActTemp=as.factor(ActTemp))%>%
  #convert ActTemp in factor and then replace labels 
  mutate (ActTemp= factor(ActTemp, levels=c("2.5", "5", "7.5", "10", "12.5","15", "17.5", "20", "25", "30","35" ),labels=c("2", "5", "7", "9", "12.5","15", "17", "20", "25", "30","35" )))

 #mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5"),labels=c("February", "March", "May", "July", "August")))%>%
  
  str(df_3a)
  
  #then reconvert ActTemp in numerical 
  
  df_3b<-df_3a%>%
    mutate(ActTemp=as.character(ActTemp))%>%
    mutate(ActTemp=as.numeric(ActTemp))
  
  str(df_3b)
  
```





Graph the absolute cumulative germination of the seeds . Select Narrikup 10 degrees and 35 degrees (Plots 13 and 173)




```{r, fig.height=6, fig.width=14}

df_Nar <-df_3 %>%
#filter(Plot=="13"|Plot=="93")%>%
  filter(Cultivar=="Narrikup")%>%
  filter(Temp== "10"|Temp=="2.5")%>%
  group_by( DAS,Temp)%>%
  dplyr::select(PercGerm_cum)%>%
  summarise_all(funs(mean,sd))
  

str(df_Nar)

df_Nar %>%
  mutate(Temp=as.factor(Temp))%>%
ggplot(aes(x=DAS, y=mean, shape=Temp))+  # do percentage here
  #geom_point(size =4 )+
  geom_line(aes(), linetype= 5, colour="dark grey", size = 2)+
  geom_point(aes(shape=Temp), size=7) +
 # scale_shape_manual(values = c(2)) +
  geom_errorbar(aes(ymin=mean-sd/4,
  ymax=mean+sd/4))+
  #facet_wrap (~Plot,ncol=2)+
  ylim(0,110 ) +
   xlim(0,20) +
  labs(y="Cumulative germination (%)",x="Days")+
  #theme_grey(base_size = 16) +
  theme_bw()+
  
theme(axis.text.x=element_text(angle = 0, hjust = 0,size = 26))+
theme(axis.text.y=element_text(angle = 0, hjust = 0,size = 26))+
theme(axis.title.x=element_text(angle = 0, hjust = 0.5,size = 26))+
theme(axis.title.y=element_text(angle = 90, hjust = 0.5,size = 26))+
  #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black"  , size = 3.0), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+

theme(text = element_text(size = 40))


 ggsave("plot_Example_Narrikup_DAS50Perc_Germ.png", width=14, height=6, dpi=400)


```


Now make the same graph but using the Actual Temperature (ActTemp)



```{r, fig.height=6, fig.width=14}

df_Nar1 <-df_3b %>%
#filter(Plot=="13"|Plot=="93")%>%
  filter(Cultivar=="Narrikup")%>%
  filter(Temp== "10"|Temp=="2.5")%>%
  group_by(DAS,Temp,ActTemp)%>%
  dplyr::select(PercGerm_cum)%>%
  summarise_all(funs(mean,sd))
  

str(df_Nar1)

df_Nar1 %>%
  mutate(ActTemp=as.factor(ActTemp))%>%
ggplot(aes(x=DAS, y=mean, shape=ActTemp))+  # do percentage here
  #geom_point(size =4 )+
  geom_line(aes(), linetype= 2, colour="grey")+
  geom_point(aes(shape=ActTemp), size=5) +
 # scale_shape_manual(values = c(2)) +
  geom_errorbar(aes(ymin=mean-sd/4,
  ymax=mean+sd/4))+
  #facet_wrap (~Plot,ncol=2)+
  ylim(0,100 ) +
   xlim(0,20) +
  labs(y="Cumulative germination %",x="Days")+
  #theme_grey(base_size = 16) +
  theme_bw()+
  
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
  
  #remove grid lines 
     theme(
     #panel.border = element_rect(colour = "black"  , size = 2.0), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+

theme(text = element_text(size = 24))


 #ggsave("plot_Example_Narrikup_DAS50Perc_Germ.png", width=14, height=6, dpi=400)


```


Now calculate the 50 percent emerge relative 

```{r}

str(df_3)

df_50_Perc <- df_3b %>%
  #change name variable
  mutate(av_Perc=PercentRelative)%>%
mutate(av_DAS=DAS)%>%
  select(-PercGerm_cum, -MaxGermPerc)

str(df_50_Perc)

write.table(df_50_Perc,"dataToCurveFitGerm.txt")


```


graph the data of one plot to add in material and methods (compare with gompertz ). use Narrikup at 10 oC as example (done above)



```{r, fig.height=5, fig.width=8}

# df_N <-df_50_Perc %>%
# filter(Plot=="13"|Plot=="173")%>%
#   #filter(Cultivar=="Narrikup")%>%
#   #filter(Temp==10.0)%>%
#   group_by(Plot, DAS,Cultivar)%>%
#   dplyr::select(PercentRelative)%>%
#   summarise_all(funs(mean,sd))
#   
# 
# 
# df_N %>%
# ggplot(aes(x=DAS, y=mean, shape=Cultivar))+  # do percentage here
#   #geom_point(size =4 )+
#   geom_line(aes(), linetype= 2, colour="grey")+
#   geom_point(aes(shape=Cultivar), size=5) +
#   scale_shape_manual(values = c(7)) +
#   geom_errorbar(aes(ymin=mean-sd/4,
#   ymax=mean+sd/4))+
#   #facet_wrap (~Plot,ncol=2)+
#   ylim(0,110 ) +
#    xlim(0,16 ) +
#   labs(y="Cumulative germination %",x="Days")+
#   #theme_grey(base_size = 16) +
#   theme_bw()+
#   # geom_abline(intercept = 1, slope = 0, linetype=2)+
#    #geom_abline(intercept = 5,  slope = 0, linetype=2)+
#    geom_abline(intercept = 50,  slope = 0, linetype=2)+
# theme(axis.text.x=element_text(angle = 0, hjust = 0))+
# theme(text = element_text(size = 20))
# 

 #ggsave("plot_Example_Narrikup_DAS50Perc_Germ.png", width=12, height=6, dpi=400)


```



use PercRelative to calculate 50 Perc of germ.Already added the Actual temperature 

```{r}
plots <- unique(df_50_Perc$Plot)

#loop trough each combination of factor levels

 for(p in 1:length(plots)) {
#  for(j in 1:length(var)){
 #   for(k in 1:length(sow)){
      
      # clean value holders
      DAS_50p_emerg <- 0
      #tt_50p_emerg <- 0
      
      #FIX ME Partially set 
    
     # print(paste0(cv[i]," ",var[j]," ", sow[k]))
      # filter for each combination

  df_sub <- df_50_Perc %>%
    # subset(Cultivar == as.character(cv[i]) &
    # Plot == as.character(var[j]) &
    #   Block == as.character(var[b]) &
    # SowTreat == as.character(sow[k])) %>%
    subset(Plot == plots[p]) %>%
    arrange(PercentRelative)
  
  df_sub
  head(df_sub)
  # create percentage with maximum value recorded 
  # to avoid crossing the 50% line twice
  
  df_sub$av_Perc_max <- 0 # create new col
  
  for(z in 1:nrow(df_sub)) {
    
    df_sub$av_Perc_max[z] <- max(df_sub$av_Perc[z],
                                 df_sub$av_Perc_max[z-1])
    
  }
  
  df_sub
  head(df_sub)
  tail(df_sub)

  # Interpolate 
  y_ref <- 50 # y value where we want to find x by interpolation
  
  # interpolate
  #find DAS at 50 Pecent Emergence 

  tryCatch(  
  DAS_50p_emerg <- approx(df_sub$PercentRelative, 
  df_sub$av_DAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  DAS_50p_emerg <- NA
  }
)
  #find TT at 50 Pecent Emergence
#   tryCatch(  
#   tt_50p_emerg <- approx(df_sub$av_Perc, 
#   df_sub$av_TT , xout = y_ref, rule = 1)$y,
#   error = function(e) 
#   {
#   tt_50p_emerg <- NA
#   }
# )

  # #----------------------------
df_temp <- NULL 
   df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             Temp = df_sub$Temp[1],
                              PercentRelative = df_sub$PercentRelative[1],
                              ActTemp = df_sub$ActTemp[1],
                              Plot = df_sub$Plot[1],
                              Block = df_sub$Block[1],
                              DAS50E = DAS_50p_emerg)
                              #TT50E = tt_50p_emerg)

  
  
  
  print(p)
  
  if(p == 1) {
    df_tt_50p_emerg <- df_temp
  } else {
   df_tt_50p_emerg <- rbind(df_tt_50p_emerg,df_temp) 
  }                     
  
#    } 
  } # end plot loop





```




```{r}
summary(df_tt_50p_emerg)

write.table(df_tt_50p_emerg,"df_tt_50p_germination.txt")

#summary(df_tt_50p_emerg)
```

Graph results:  


Data visualisation and means check.
```{r, fig.height=5, fig.width=10}

#Here just to check means 
# mean <-df_tt_50p_emerg %>%
#   group_by(SowTreat, SowingDate, Cultivar,DAS50E) %>%
#   summarise_each(funs(mean,sd))
# summary (mean)


df_tt_50p_emerg %>%
  group_by(Temp, Cultivar,ActTemp) %>%
  dplyr::select(DAS50E) %>%
  summarise_each(funs(mean,sd)) %>%
  
  # if needed to exclude cultivars for analysis use filter 
  # filter( Cultivar != "Woogenellup" &
  #        Cultivar != "Monti" &
  #        Cultivar != "Antas" &
  #        Cultivar != "Denmark" &
  #        Cultivar != "Leura") %>%
         
  
ggplot(aes(x=ActTemp, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point(size=3) +
  geom_line() +
  labs(x="Temperature",y="Days to 50% emergence ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 14))+
  theme(axis.text.y = element_text(angle = 0, hjust = 1, size = 14))+
  geom_errorbar(aes(ymin=mean-(sd/2)/2,
  ymax=mean+(sd/2)/2))+
  facet_wrap(~Cultivar,ncol=2, scales = "free")+
  theme_bw(base_size = 16)
 
#ggsave("plot_.png", width=10, height=6, dpi=400)

```

Calculate the rate of emergence (1/Days to 50% emergence)

```{r}

#try 1/DAS50% = Rate

df_RateEmerg <- df_tt_50p_emerg %>%
  mutate(Rate=1/DAS50E)

  str(df_RateEmerg)
  
  write.table(df_RateEmerg, "df_RateGerm.txt")
  
```

Make graph with DAS50E

```{r, fig.height=5, fig.width=10}

#select the variable and find mean and sd 
df_Rate_MeanD <-df_RateEmerg%>%
  group_by(Cultivar, Temp, ActTemp ) %>%
    dplyr::select(DAS50E)%>%
  summarise_all(funs(mean,sd))

#then create the error bar position
#Here how to create the end error bar with max Sd 
# find size of bar per cultivar and temp
# find single position of x y to put the bar

#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.2 # extra position for single error bar
x_max<-max(df_Rate_MeanD$ ActTemp)
y_max<-max(df_Rate_MeanD$mean)

# find largest standard error for each cultivar 
sd_df <- df_Rate_MeanD %>% 
  group_by(Cultivar) %>%
  dplyr:: select(sd)%>%
  summarise_all(funs(max))%>% 
  ungroup() %>%
  rowwise() %>%
  mutate(ActTemp = x_max*extraPos, mean = y_max*extraPos, max_sd=sd)

summary(sd_df)


#make a graph 
#then graph 


df_Rate_MeanD %>% 
  #select( Variable, Cultivar, Temp, mean,sd) %>%
  ggplot(aes(x= ActTemp, y=mean)) + 
#  geom_point(data=sd_df,aes(x=DAS,y=NumberRun_mean)) +
  geom_point(aes(shape=Cultivar), size=6) +
  scale_shape_manual(values = c(1,2,0,7)) +
  geom_errorbar(data=sd_df, aes(ymin=mean-max_sd/2,
                    ymax=mean+max_sd/2), width=3, size=1.5)+
  facet_wrap (~Cultivar,ncol=2)+
  ylim(0,20 ) +
  #labs(y="Time to 50% final germination",x="Temperature")+
  #ylab(expression(Time~to~T~"%"~final~Germination~"(days)"))+
  ylab(expression(Time~to~T50~"(days)"))+
  xlab(expression(Temperature~"("^"o"*"C)"))+
  theme_grey(base_size = 22) +
  theme_bw()+
  # geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 5,  slope = 0, linetype=2)+
   #geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
  
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   theme(text = element_text(size = 24))+
   
  theme(axis.title.y = element_text(face="bold", size=24))


 ggsave("plot_DAS50Perc_Germ.png", width=12, height=6, dpi=400)


```






make the same graph with rate 

```{r , fig.height=5, fig.width=10}

#select the variable and find mean and sd 
df_Rate_MeanR <-df_RateEmerg%>%
  group_by(Cultivar, Temp, ActTemp  ) %>%
    dplyr::select(Rate)%>%
  summarise_all(funs(mean,sd))

#then create the error bar position
#Here how to create the end error bar with max Sd 
# find size of bar per cultivar and temp
# find single position of x y to put the bar

#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.1 # extra position for single error bar
x_max<-max(df_Rate_MeanR$ActTemp)
y_max<-max(df_Rate_MeanR$mean)

# find largest standard error
sd_df1 <- df_Rate_MeanR %>% 
  group_by(Cultivar) %>%
  dplyr:: select(sd)%>%
  summarise_all(funs(max))%>%
  ungroup() %>%
  rowwise() %>%
  mutate(ActTemp = x_max*extraPos, mean = y_max*extraPos, max_sd=sd)

summary(sd_df1)

#make a graph 
#then graph and remember to divide the sd /2 because of the 4 replicates 


df_Rate_MeanR %>% 
  #select( Variable, Cultivar, Temp, mean,sd) %>%
  ggplot(aes(x=ActTemp, y=mean)) + 
#  geom_point(data=sd_df,aes(x=DAS,y=NumberRun_mean)) +
  geom_point(aes(shape=Cultivar), size=6) +
  scale_shape_manual(values = c(1,2,0,7)) +
  geom_errorbar(data=sd_df1, aes(ymin=mean-max_sd/2,
                    ymax=mean+max_sd/2), width=4,size=1.5)+
  facet_wrap (~Cultivar,ncol=2)+
  ylim(0,1.4) +
  ylab(expression(Germination~Rate~"(1/Days)"))+
  xlab(expression(Temperature~"("^"o"*"C)"))+
  #labs(y="Germination rate (1/days)",x="Temperature")+
  theme_grey(base_size = 22) +
  theme_bw()+
  # geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 5,  slope = 0, linetype=2)+
   #geom_abline(intercept = 9,  slope = 0, linetype=2)+
   theme(axis.text.x=element_text(angle = 0, hjust = 0))+
  #remove grid lines 
    theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
  
theme(text = element_text(size = 24))


ggsave("plot_RatePerc_Germ.png", width=12, height=6, dpi=400)


```


This chunck is not in use graph (GRID ) and save a dataframe as txt .Here data shows SE as sd/2/2

```{r, fig.height=8, fig.width=15}

#Here how to create the end error bar with max Sd 
# find size of bar per month
# find single position of x y to put the bar

#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.1 # extra position for single error bar
x_max<-max(df_Rate_Mean$Temp)
y_max<-max(df_Rate_Mean$mean)

# find largest standard error
sd_df <- df_Rate_Mean %>% 
  group_by(Cultivar) %>%
  summarise(max_sd = max(sd)) %>% 
  ungroup() %>%
  rowwise() %>%
  mutate(Temp = x_max*extraPos, mean = y_max*extraPos)

summary(sd_df)

#DAS 50% germ 

g1 <-df_RateEmerg %>%
  group_by(Temp, Cultivar) %>%
  #filter(Cultivar=="Woogenellup")%>%
 # filter (SowTreat== "S2"| SowTreat== "S2"|SowTreat== "S2"|)
  dplyr::select(DAS50E) %>%
  summarise_all(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=Temp, y=mean,  shape=Cultivar)) +
  #geom_point(aes(shape)) +
  geom_point(aes(shape=Cultivar),size=4)+
  geom_errorbar(data=sd_df, aes(ymin=mean-max_sd,
                    ymax=mean+max_sd), width=4)+
  #scale_shape_manual(values = c(0,1,2,3,4))+
  scale_shape_manual(values = c(1,2,4,7))+
  labs(x="Temperature",y="Days to 50% germination ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size =14 ))+
  theme(axis.text.y = element_text(angle = 0,  size =16 ))+
  #geom_errorbar(aes(ymin=mean-(sd/2)/2,
  #ymax=mean+(sd/2)/2))+
  #facet_wrap(~Cultivar,ncol=2, scales = "free")+
  facet_wrap(~Cultivar,ncol=2)+
  #theme_bw()+
  theme_bw(base_size = 16) +
  ylim(0,25)

#Rate to Germ 
g2 <- df_RateEmerg %>%
  group_by(Temp, Cultivar) %>%
  #filter(Cultivar=="Woogenellup")%>%
 # filter (SowTreat== "S2"| SowTreat== "S2"|SowTreat== "S2"|)
  dplyr::select(Rate) %>%
  summarise_all(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=Temp, y=mean,  shape=Cultivar)) +
  #geom_point(aes(shape)) +
  geom_point(aes(shape=Cultivar),size=4)+
  geom_errorbar(data=sd_df, aes(ymin=mean-max_sd,
                    ymax=mean+max_sd), width=4)+
  #scale_shape_manual(values = c(0,1,2,3,4))+
  scale_shape_manual(values = c(1,2,4,7))+
  labs(x="Temperature",y="Rate 50% germination ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size =14 ))+
  theme(axis.text.y = element_text(angle = 0,  size =16 ))+
  #geom_errorbar(aes(ymin=mean-(sd/2)/2,
  #ymax=mean+(sd/2)/2))+
  #facet_wrap(~Cultivar,ncol=2, scales = "free")+
  facet_wrap(~Cultivar,ncol=2)+
  #theme_bw()+
  theme_bw(base_size = 16) +
  ylim(0,30)
  


g <-grid.arrange(g1, g2)
  
  #ggsave(file="plot_DAS50E_Rate_Germination.png", width=12, height=6, dpi=400,g)


  
```



End of this script 

