---
title: 'Seed Germination Cardinal Temperatures Stats summary  '
author: "CT"
date: "09.06..2018"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

This script does this:

-get dataframe produced with previous scripts (organized in excel _ AnalysisSeed GermTemps - folder PhD Analysis) for each cultivar and block
- Calculates the SE and Ci for each.     



```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
library (gridExtra)
library (rcompanion)
library(knitr) 

```

get file 

```{r loadFile}
# Get dataframe from previous script (written table )
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedGermTemp")
getwd()

#create file
#df_G <- read.table("df_RateGerm2.txt",header=TRUE)
df_Card <- read.table("TempCardCalc.txt",header=TRUE)

str(df_Card)
```

select columns of interest and Adjust formats 
```{r}

#change formats
df_Card$Cultivar <- as.factor(df_Card$Cultivar)
df_Card$Block <- as.factor(df_Card$Block)
#df_Card$Plot <- as.factor(df_Card$Plot)
df_Card$Variate <- as.factor(df_Card$Variate)#note Temp here needs to be numeric for subseting 
df_Card$Value <- as.numeric(df_Card$Value)#note Temp here needs to be numeric for subseting


# this is to "clean previous dfs : df_emerg4 <- NULL
```

Get overall means and se 

```{r}

df_Allmeans<- df_Card%>%
  group_by( Variate) %>%
  dplyr::select( Variate, Value)%>%
  summarise_all(funs(mean(Value), sd))%>%
  mutate(SE=sd/2)




```



Create a Loop ANOVA for variate 


## Create index to filter for loop ANOVA

```{r}
y <- c("Tb","Tmax","Topt")

sdIndex <- unique(df_Card$Variate)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```

Loop Anova 


## Then loop anova for each individual variate  

```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_Card %>%
  filter(Variate==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(Value ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))



if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}


```


then explore data of Tb  to get the Ci ; exampleplant.mod1 = lm(weight ~ group, data = plant.df). Filter the Tb first 



```{r}
df_Tb<-df_Card %>%
  filter(Variate=="Tb")
  

#then do the lm 

plant.mod1 = lm(Value ~ Cultivar, data = df_Tb)

#call first summary 
summary(plant.mod1)

```

Visualise  with the t.test the overall confidence interval for Tb, Tmax and Topt 

```{r}
#this gives an overview of all values 
#t.test(df_Tb$Value,conf.level = 0.95)
 

#here only for Tb :

groupwiseMean(Value~Cultivar,
              data=df_Tb,
              conf= 0.95,
              digits=3)

```



```{r}

#t.test(df_Tb$Value,conf.level = 0.95)
 
#here for Tmax

groupwiseMean(Value~Cultivar,
              data=df_Tmax,
              conf= 0.95,
              digits=3)

```


```{r}

#t.test(df_Tb$Value,conf.level = 0.95)
 
#here for Topt 

groupwiseMean(Value~Cultivar,
              data=df_Topt,
              conf= 0.95,
              digits=3)

```



Other data explorations  using confit but is outdated as R companion library was installed! 


```{r}

#anova lm 
anova(plant.mod1)


```



```{r}

confint(plant.mod1)

```


```{r}

ggplot(df_Tb, aes(x = Cultivar, y = Value)) +
  geom_boxplot(fill = "grey80", colour = "black") +
  scale_x_discrete() +
  #ylim(-8,10)+
  xlab("Cultivar") +
  ylab("Temperature")


```




Now do the same with the Tmax 


```{r}
df_Tmax<-df_Card %>%
  filter(Variate=="Tmax")
  

#then do the lm 

plant.mod2 = lm(Value ~ Cultivar, data = df_Tmax)

#call first summary 
summary(plant.mod2)

```



```{r}

#anova lm 
anova(plant.mod2)


```



```{r}

confint(plant.mod2)

```



```{r}

ggplot(df_Tmax, aes(x = Cultivar, y = Value)) +
  geom_boxplot(fill = "grey80", colour = "black") +
  scale_x_discrete() +
  #ylim(-8,3)+
  xlab("Cultivar") +
  ylab("Temperature")

```





Now Run analysis for the Topt 




```{r}
df_Topt<-df_Card %>%
  filter(Variate=="Topt")
  

#then do the lm 

plant.mod3 = lm(Value ~ Cultivar, data = df_Topt)

#call first summary 
summary(plant.mod3)

```



```{r}

#anova lm 
anova(plant.mod3)


```



```{r}

confint(plant.mod3)

```



```{r}

ggplot(df_Tmax, aes(x = Cultivar, y = Value)) +
  geom_boxplot(fill = "grey80", colour = "black") +
  scale_x_discrete() +
  #ylim(-8,3)+
  xlab("Cultivar") +
  ylab("Temperature")

```





End of this script
next script generate equations for each cultivar separately from 5 to 15.4-5 degrees. 