---
title: "Seed Germination rate for Narrikup "
author: "CT"
date: "09.10.2017"
output: html_document
---

This script does this:

-get dataframe produced in script script 5 for Narrikup only between 2.5 and 17.5 degrees Used dataframe Rate2. 
- had excluded 35 degrees as deviates from the curve    



```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
library (gridExtra)
```

get file 

```{r loadFile}
# Get dataframe from previous script (written table )
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedGermTemp")
getwd()

#create file
df_G <- read.table("df_RateGerm.txt",header=TRUE)



```

select columns of interest and Adjust formats. Add ActTemp. 
```{r}

#change formats
df_G$Cultivar <- as.factor(df_G$Cultivar)
df_G$Block <- as.factor(df_G$Block)
df_G$Plot <- as.factor(df_G$Plot)
df_G$Temp <- as.numeric(df_G$Temp)#note Temp here needs to be numeric for subseting 
df_G$ActTemp <- as.numeric(df_G$ActTemp)#note Temp here needs to be numeric for subseting
#select columns 
df_G <-df_G %>%
dplyr:: select(Plot,Block,Cultivar,ActTemp,Rate)


str(df_G)

# this is to "clean previous dfs : df_emerg4 <- NULL
```

Subset cultivars Narrikup between temperature 2.5 to max 20 

```{r}

#subset Cultivar

df_N <-df_G %>%
subset(Cultivar=="Narrikup")

#subset Temperature range 
df_N1 <-df_N %>%
  subset (ActTemp>1.5 & ActTemp<18)


#remove data if needed
df_N2 <- df_N1 

```

work dataframe for narrikup

```{r}


df_N3 <-df_N2 %>%
  dplyr::select(ActTemp,Cultivar, Plot, Rate) %>%
  group_by(ActTemp,Cultivar) %>%
  summarise_all(funs(mean)) %>%
  mutate(y=Rate,x=ActTemp) %>%
  dplyr::select(-ActTemp, -Rate, -Plot)

str(df_N2)

```

got the means here ... and graph it

```{r, fig.height=5, fig.width=10, echo = FALSE}
df_N3%>%
ggplot(aes(x=x, y=y))  +
  geom_point(alpha=0.8, size= 3) +
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Temperature~~"("^"o"*"C)")) + 
  ylab(" Mean Rate (1/ Days) to 50% germination") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=12))+
 scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.8))


# 

```



here get the equations for the Antas subset (min to optimum)  

```{r, fig.height=5,fig.width=10}
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}

#use all datapoints 
df <- df_N2 %>%
  dplyr::select(ActTemp,Cultivar, Plot, Rate) %>%
  group_by(ActTemp,Cultivar)%>%
  summarise_all(funs(mean)) %>%
  mutate(y=Rate,x=ActTemp) %>%
  dplyr::select(-ActTemp, -Rate)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_point(aes(colour = factor(ActTemp)), size=5) + scale_shape(solid = FALSE)+ 
  
  theme_bw()+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.8))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE) + 
  facet_grid(Cultivar~.,scales="free")
  
p1
```


```{r}
#get statistical summary here 
summary(lm(y ~ x, df))
```


```{r}

 
confint(lm(y ~ x, df))


```





do for individual blocks loop



```{r}

#get the dataframe and rename it 

dfSubSet <- df_N2
str(dfSubSet)

all.data<-data.frame()
counter<-0
blocks<-unique(dfSubSet$Block)

length(blocks)#*length(depth)
#p=d=1
for(p in 1:length(blocks)) {
  #for(d in 1:length(depth)) {
  df_sub <- data.frame()  
   # print(paste0(plots[p],"_",depth[d]))
  #  counter<-counter+1
    
  df_sub <- dfSubSet %>% filter(Block==blocks[p])

# Linear fit
  x <- df_sub$Temp
  y <- df_sub$Rate
  
  #print(data.frame(x=x,y=y))
  
  fit <- NULL
  fit <- lm(y ~ x)

intercept <- round(fit$coefficients[[1]],2)
  slope <- round(fit$coefficients[[2]],3)
  r2 <- round(summary(fit)$r.squared * 100,2)
  # summary(fit)$adj.r.squared
  cv <- as.character(df_sub$Cultivar[1])
  block <- as.character(df_sub$Block[1])
  #sow <- as.character(df_sub$SowTreat[1])
  #sd <- dmy(df_sub$SowingD[1])
  
  
  buf <- data.frame(cv=cv, block=block[p], int=intercept, slope=slope, r2=r2, n=nrow(df_sub))
  
  all.data <- rbind(buf, all.data)
  
 # print(buf)
  
  #print(nrow(df_sub))
    
  #subset(dfSubSet, (dfSubSet$Plot==plots[p] & Depth == depth[d]))
    
  }
  


summary(all.data)



```







Now run same linear equation for linear decrease 

Subset cultivars Narrikup between temperature >21 to max of 30. Excluded 35 as deviates from the curve  

```{r}

#subset Cultivar

df_Z <-df_G %>%
subset(Cultivar=="Narrikup")

#subset Temperature range 
df_Z1 <-df_Z %>%
  subset (ActTemp>18 & ActTemp<36)


#remove data if needed
df_Z2 <- df_Z1 

```



```{r}


df_Z3 <-df_Z2 %>%
  dplyr::select(ActTemp,Cultivar, Plot, Rate) %>%
  group_by(ActTemp,Cultivar) %>%
  summarise_all(funs(mean)) %>%
  mutate(y=Rate,x=ActTemp) %>%
  dplyr::select(-ActTemp, -Rate, -Plot)

str(df_Z2)

```

got the means here ... and graph it

```{r, fig.height=5, fig.width=10, echo = FALSE}
df_Z3%>%
ggplot(aes(x=x, y=y))  +
  geom_point(alpha=0.8, size= 3) +
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Temperature~~"("^"o"*"C)")) + 
  ylab(" Mean Rate (1/ Days) to 50% germination") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=12))+
 scale_x_continuous(limits = c(0,40))+
  scale_y_continuous(limits = c(0,0.8))


# 

```



here get the equations for the narrikup subset (min to optimum)  

```{r, fig.height=5,fig.width=10}
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}

#use all datapoints 
df <- df_Z2 %>%
  dplyr::select(ActTemp,Cultivar, Plot, Rate) %>%
  group_by(ActTemp,Cultivar)%>%
  summarise_all(funs(mean)) %>%
  mutate(y=Rate,x=ActTemp) %>%
  dplyr::select(-ActTemp, -Rate)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x,linetype=2) +
  geom_point(aes(colour = factor(ActTemp)), size=5) + scale_shape(solid = FALSE)+ 
  
  theme_bw()+
  scale_x_continuous(limits = c(0,40))+
  scale_y_continuous(limits = c(0,0.8))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE) + 
  facet_grid(Cultivar~.,scales="free")
  
p1
```


```{r}
#get statistical summary here 
summary(lm(y ~ x, df))
```


```{r}

 
confint(lm(y ~ x, df))


```




```{r}

#get the dataframe and rename it 

dfSubSet <- df_Z2
str(dfSubSet)

all.data<-data.frame()
counter<-0
blocks<-unique(dfSubSet$Block)

length(blocks)#*length(depth)
#p=d=1
for(p in 1:length(blocks)) {
  #for(d in 1:length(depth)) {
  df_sub <- data.frame()  
   # print(paste0(plots[p],"_",depth[d]))
  #  counter<-counter+1
    
  df_sub <- dfSubSet %>% filter(Block==blocks[p])

# Linear fit
  x <- df_sub$ActTemp
  y <- df_sub$Rate
  
  #print(data.frame(x=x,y=y))
  
  fit <- NULL
  fit <- lm(y ~ x)

intercept <- round(fit$coefficients[[1]],2)
  slope <- round(fit$coefficients[[2]],3)
  r2 <- round(summary(fit)$r.squared * 100,2)
  # summary(fit)$adj.r.squared
  cv <- as.character(df_sub$Cultivar[1])
  block <- as.character(df_sub$Block[1])
  #sow <- as.character(df_sub$SowTreat[1])
  #sd <- dmy(df_sub$SowingD[1])
  
  
  buf <- data.frame(cv=cv, block=block[p], int=intercept, slope=slope, r2=r2, n=nrow(df_sub))
  
  all.data <- rbind(buf, all.data)
  
 # print(buf)
  
  #print(nrow(df_sub))
    
  #subset(dfSubSet, (dfSubSet$Plot==plots[p] & Depth == depth[d]))
    
  }
  


summary(all.data)



```



End of this script
