---
title: "Compare results of Gompertz Sigmaplot and  "
author: "CT"
date: "07.10..2017"
output: html_document
---

This script does this:

-get dataframe produced in by comparing Gompertz sigmaplot(GermDataFitSigma.xls) with approx values produced in script 2 




```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
library (gridExtra)
```

get file 

```{r loadFile}
# Get dataframe from previous script (written table )
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedGermTemp")
getwd()

#create file
df_GAprox <- read.table("CompareGompertzApproxFunction.txt",header=TRUE)


str(df_GAprox)


```

select columns of interest and Adjust formats 
```{r}

#change formats
df_GAprox$Cultivar <- as.factor(df_GAprox$Cultivar)
df_GAprox$Block <- as.factor(df_GAprox$Block)
df_GAprox$Plot <- as.factor(df_GAprox$Plot)
df_GAprox$Temp <- as.numeric(df_GAprox$Temp)#note Temp here needs to be numeric for subseting 


str(df_GAprox)

# this is to "clean previous dfs : df_emerg4 <- NULL
```

rename variables



```{r}


df_graph <-df_GAprox %>%
  mutate(y=DAS50Germ_Gompertz,x=DAS50Germ_Approx) %>%
  dplyr::select(-DAS50Germ_Approx, -DAS50Germ_Gompertz,-Plot)

str(df_graph)

```

got the means here ... and graph it

```{r, fig.height=5, fig.width=15, echo = FALSE}
df_graph%>%
ggplot(aes(x=x, y=y))  +
  geom_point(aes(shape=Cultivar), size=4) +
  scale_shape_manual(values = c(1,2,0,7)) +
  #geom_line(colour="grey", linetype=2)+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
 # xlab(expression(Gompertz~estimated~days"("*"DAS50"*")")) + 
  ylab("  Days to 50% germination-Gompertz ")+
  xlab(" Days to 50% germination -Approx") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=12))+
 scale_x_continuous(limits = c(0,16))+
  scale_y_continuous(limits = c(0,16))+
   geom_abline(intercept = 5,  slope = 0, linetype=2)


ggsave("plot_GompertzApprox.png", width=12, height=6, dpi=400)

```



here get the equations for the Antas subset (min to optimum)  

```{r, fig.height=5,fig.width=10}
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}

#use all datapoints 
df <- df_graph
  #dplyr::select(Temp,Cultivar, Plot) %>%
  #group_by(Temp)%>%
  #summarise_all(funs(mean)) 
  #mutate(y=Rate,x=Temp) %>%
  #dplyr::select(-Temp, -Rate)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_point(aes(colour = factor(Temp)), size=5) + scale_shape(solid = FALSE)+ 
  
  theme_bw()+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,25))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE)  +
  facet_grid(Cultivar~.,scales="free")
  
p1
```
(parei aqui ..update table )

```{r}
#get statistical summary here 
summary(lm(y ~ x, df))
```



get confidential intervals 

```{r}

 
confint(lm(y ~ x, df))


```

now perform anova with the two values as factor (Temp, cultivar, ValueDAS) compare if they are stts differnet 

```{r}

#transform Gompertz and Approx values as variables. Prepare dataframe

str(df_GAprox)

df_gathered <-df_GAprox%>%
  gather(key= "Method" , value = "DAS50" , DAS50Germ_Gompertz,DAS50Germ_Approx)%>%
  mutate(Method=as.factor(Method), 
         DAS50=as.numeric(DAS50),
         Temp=as.factor(Temp)
         )
  str(df_gathered)

```

Anova
```{r}


# anova 

file.subset <- df_gathered

head(file.subset)
str(file.subset)
```

Check if method has any significant difference! 

```{r}

#ANOVA


my.anova <- aov(DAS50 ~ Method*Temp + Cultivar, data = file.subset)
summary(my.anova)

```

There is no significant differencesbetween the methods !!!! P= 0.4!! Now do the mean separation to confirm

```{r}

#(LSD.test(my.anova, c("Method", "Cultivar"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Method", "Temp"), alpha= 0.05, p.adj="none")) 

```


conclusion : o differences between the methods!!! 

End of this script
