---
title: 'Seed Germination Max_DAS50 and rate _Stats summary  '
author: "CT"
date: "09.10.2018"
output
  pdf_document: default
  html_document: default
  word_document: default
---

This script does this:

-get dataframe produced with previous scripts (organized in excel _ AnalysisSeed GermTemps - folder PhD Analysis_DataAnalysisOrigin) for each cultivar and block
- created file is : DataOriginCv_MaxDAS50Rate.txt
- Calculates the SE and Ci for each.  run anova   



```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
library (gridExtra)
library (rcompanion)
library(knitr) 

```

get file 

```{r loadFile}
# Get dataframe from previous script (written table )
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedGermTemp")
getwd()

#create file
#df_G <- read.table("df_RateGerm2.txt",header=TRUE)
df_Data <- read.table("DataOriginCv_MaxDAS50Rate.txt",header=TRUE)


str(df_Data)
summary (df_Data)

```

select columns of interest and Adjust formats 
```{r}

#change formats
df_Data$Cultivar <- as.factor(df_Data$Cultivar)
df_Data$Block <- as.factor(df_Data$Block)
df_Data$Origin <- as.factor(df_Data$Origin)
df_Data$Temp <- as.numeric(df_Data$Temp)
df_Data$Variate <- as.factor(df_Data$Variate)#note Temp here needs to be numeric for subseting 
df_Data$Value <- as.numeric(df_Data$Value)#note Temp here needs to be numeric for subseting


# this is to "clean previous dfs : df_emerg4 <- NULL
```

Get overall means and se 

```{r}

df_Allmeans<- df_Data%>%
  group_by(Origin,Variate,Temp) %>%
  dplyr::select( Variate, Value)%>%
  summarise_all(funs(mean(Value),sd))%>%
  mutate(SE=sd/2)




```

Plot Temp in x axis and variate in y axis. Create symbols per origin. 


```{r, fig.height=7, fig.width=15}


#Here how to create the end error bar with max Sd 
# find size of bar per month
# find single position of x y to put the bar

str(df_Allmeans)

extraPos<- 1.10 # extra position for single error bar
 #extraPos<- 0.5 # extra position for single error bar
  #x_max<-max(df_Allmeans$Temp)
  #y_max<-max(df_Allmeans$mean)
 #try min to visualise bars in graph 
 x_min<-min(df_Allmeans$Temp)
 y_min <-min(df_Allmeans$mean)

# find largest standard error
 sd_df2 <- df_Allmeans %>% 
#   #group_by(Temp) # 
   group_by(Origin,Variate) %>%
   dplyr::select(sd) %>%
   summarise_all(max) %>%
#summarise(max_sd = max(sd)) %>% 
   ungroup() %>%
   rowwise() %>%
#   #rename variables
   #mutate(Temp = x_max*extraPos, mean = y_max*extraPos,max_sd=sd )
 mutate(Temp = x_min*extraPos, mean = y_min*extraPos,max_sd=sd )
# 
 str(sd_df2)

#divide sd/2 as number of replicates were 4 

df_graphic<-df_Allmeans
 
  
df_graphic%>%
ggplot(aes(x=Temp, y=mean)) + 
  geom_point(aes(shape= Origin), size=5)+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11))+
  geom_line(aes(width=Origin))+
  #geom_point(aes(shape=Temp),size=4)+
  #scale_shape_manu(al(values = c(0,1,2,3,4))+
   #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10)) +
  #scale_shape_manual(values = c(1,2,4,7))+
  #geom_line()+
  geom_errorbar(data=sd_df2, aes(ymin=mean-max_sd/4,
                    ymax=mean+max_sd/4), size=2)+
  
  #geom_errorbar(data=sd_df2, aes(ymin=mean-(sd/4),
                    #ymax=mean+(sd/4)))+
  facet_wrap(~Variate,ncol=3, scales = "free")+
  #facet_grid(Variate~., scales = "free")+
   #facet_wrap(~Variate,ncol=3)+
  theme_bw()+
  #scale_x_continuous(breaks = c(5,10,15,20,30))+
  #ylim(0, 145)+
  #scale_y_continuous(breaks = c(0,25,50,75,100))+
  #xlim(0, 23)+
  #labs(y="Mean cumulative germination (%)")+ 
  xlab(expression(Temperature~"("^"o"*"C)"))+
  #theme(axis.title.x = element_text( size=24)) + scale_x_continuous(breaks = c(0:6))+
  theme(text=element_text(size=22 ))+
  theme(title=element_text(size=22, face="bold"))+
  theme(title=element_text(size=22,  face="bold"))+
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black"  , size = 2.0), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     
     axis.line = element_line(colour = "black", size= 1))+

#make Cultivars  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
  
  #label sizes 
theme(text = element_text(size = 26))
  
  #geom_abline(intercept = 50, slope = 0)


#ggsave("plot_CumulativeGermCv.png", width=12, height=10, dpi=500)




```



try as facet wrap (can not add distinct error bars )



```{r, fig.height=7, fig.width=20}

#  df_graphic1%>%
#   
#                            
# df_graphic$ Variate <- as.factor(rep(c("A","B","C"), each = length (Temp))) 
 
df_graphic%>% 
ggplot(aes(x=Temp, y=mean)) + 
  geom_point(aes(shape= Origin), size=8)+
  scale_shape_manual(values = c(1,19))+
  geom_line(aes(width=Origin))+
   #scale_shape_manual(values = c(0,1,))+
   #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10)) +
  #scale_shape_manual(values = c(1,2,4,7))+
  #geom_line()+
  # geom_errorbar(data=sd_df2, aes(ymin=mean-max_sd/4,
                     #ymax=mean+max_sd/4), size=2) +
    geom_errorbar (aes(ymin=mean-SE/2,
                     ymax=mean+SE/2), size=0.8) +
  
  #facet_grid(Variate~., scales = "free")+
   #facet_wrap(~Variate,ncol=3)+
  theme_bw()+
  #scale_x_continuous(breaks = c(5,10,15,20,30,40))+
  #ylim(0, 145)+
  #scale_y_continuous(breaks = c(0,25,50,75,100))+
  #xlim(0, 23) +
  
  
  facet_wrap(~Variate,ncol=3, scales = "free_y", strip.position = "left", 
             labeller= as_labeller(c(DAS50E="Time to T50 (days)", MaxGerm = "Maximum Germination (%)", Rate ="Rate (1/days)" ))) +
  ylab(NULL)+
  expand_limits (x=0,y=0)+ 
  #scale_x_continuous(expand= c(0,0)) + scale_y_continuous(expand= c(0,0))+
  #xlim(0, 40) +
  
  #labs(y="Mean cumulative germination (%)")+ 
  xlab(expression(Temperature~"("^"o"*"C)"))+
  #theme(axis.title.x = element_text( size=24)) + scale_x_continuous(breaks = c(0:6))+
  theme(text=element_text(size=22 ))+
  theme(title=element_text(size=22, face="bold"))+
  theme(title=element_text(size=22,  face="bold"))+
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black"  , size = 2.0), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     
     axis.line = element_line(colour = "black", size= 1))+

#make Cultivars  white  
   theme(strip.background = element_rect(colour = "white", fill = "white",size=2), strip.placement = "outside")+
  
  #label sizes 
theme(text = element_text(size = 26))
  
  #geom_abline(intercept = 50, slope = 0)


ggsave("plot_Panel_Origin_DASMaxGerm_Rate.png", width=18, height=8, dpi=500)



```


Here do by individual variate (error bar inclusion issue)

```{r, fig.height=7, fig.width=15}



df_graphDAS <-df_Allmeans%>%
  filter(Variate=="DAS50E")
 

#Here how to create the end error bar with max Sd 
# find size of bar per month
# find single position of x y to put the bar

#str(df_Allmeans)

extraPos<- 1.10 # extra position for single error bar
 #extraPos<- 0.5 # extra position for single error bar
  x_max<-max(df_graphDAS$Temp)
  y_max<-max(df_graphDAS$mean)
 #try min to visualise bars in graph 
 #x_min<-min(df_graphDAS$Temp)
 #y_min <-min(df_graphDAS$mean)

# find largest standard error
 sd_df3 <- df_graphDAS %>% 
#   #group_by(Temp) # 
   group_by(Origin) %>%
   dplyr::select(sd) %>%
   summarise_all(max) %>%
#summarise(max_sd = max(sd)) %>% 
   ungroup() %>%
   rowwise() %>%
#   #rename variables
   #mutate(Temp = x_max*extraPos, mean = y_max*extraPos,max_sd=sd )
 mutate(Temp = x_max*extraPos, mean = y_max*extraPos,max_sd=sd )
# 
 str(sd_df3)

#divide sd/2 as number of replicates were 4 to get SE then divide / 2 to split SE

 ###########################

df_graphDAS %>%
ggplot(aes(x=Temp, y=mean)) + 
  geom_point(aes(shape= Origin), size=5)+
  #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11))+
  geom_line(aes(width=Origin))+
  #geom_point(aes(shape=Temp),size=4)+
  #scale_shape_manu(al(values = c(0,1,2,3,4))+
   #scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10)) +
  #scale_shape_manual(values = c(1,2,4,7))+
  #geom_line()+
  geom_errorbar(data=sd_df3, aes(ymin=mean-max_sd/4,
                    ymax=mean+max_sd/4), size=2)+
  
  #geom_errorbar(data=sd_df2, aes(ymin=mean-(sd/4),
                    #ymax=mean+(sd/4)))+
  #facet_wrap(~ Origin,ncol=1, scales = "free")+
  #facet_grid(Variate~., scales = "free")+
   #facet_wrap(~Variate,ncol=3)+
  theme_bw()+
  #scale_x_continuous(breaks = c(5,10,15,20,30))+
  #ylim(0, 145)+
  #scale_y_continuous(breaks = c(0,25,50,75,100))+
  #xlim(0, 23)+
  #labs(y="Mean cumulative germination (%)")+ 
  xlab(expression(Temperature~"("^"o"*"C)"))+
  #theme(axis.title.x = element_text( size=24)) + scale_x_continuous(breaks = c(0:6))+
  theme(text=element_text(size=22 ))+
  theme(title=element_text(size=22, face="bold"))+
  theme(title=element_text(size=22,  face="bold"))+
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black"  , size = 2.0), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     
     axis.line = element_line(colour = "black", size= 1))+

#make Cultivars  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
  
  #label sizes 
theme(text = element_text(size = 26))
  
  #geom_abline(intercept = 50, slope = 0)


#ggsave("plot_CumulativeGermCv.png", width=12, height=10, dpi=500)




```



```{r}




## Create a Loop ANOVA for variate 


## Create index to filter for loop ANOVA

y <- c("DAS50E","MaxGerm", "Rate")

sdIndex <- unique(df_Data$Variate)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex


```



Loop Anova 


## Then loop anova for each individual variate xplore effect of Origin  

```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_Data %>%
  filter(Variate==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(Value ~ Origin + Block, data = file.subset)
print(summary(my.anova))



if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Origin***") 
  print((LSD.test(my.anova, c("Origin"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig  Origin***") 
  print((LSD.test(my.anova, c("Origin"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Origin"), alpha= 0.05, p.adj="none"))
  
}


```




## Then loop anova for each individual variate xplore effect of Origin  

```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_Data %>%
  filter(Variate==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(Value ~ Origin*Temp + Block, data = file.subset)
print(summary(my.anova))



if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Origin***") 
  print((LSD.test(my.anova, c("Origin","Temp"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig  Origin***") 
  print((LSD.test(my.anova, c("Origin","Temp"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Origin","Temp"), alpha= 0.05, p.adj="none"))
  
}


```


then explore data of Tb  to get the Ci ; exampleplant.mod1 = lm(weight ~ group, data = plant.df). Filter the Tb first 



```{r}
df_Tb<-df_Data %>%
  filter(Variate=="Tb")
  

#then do the lm 

plant.mod1 = lm(Value ~ Cultivar, data = df_Tb)

#call first summary 
summary(plant.mod1)

```

Visualise  with the t.test the overall confidence interval for Tb, Tmax and Topt 

```{r}
#this gives an overview of all values 
#t.test(df_Tb$Value,conf.level = 0.95)
 

#here only for Tb :

groupwiseMean(Value~Cultivar,
              data=df_Tb,
              conf= 0.95,
              digits=3)

```



```{r}

#t.test(df_Tb$Value,conf.level = 0.95)
 
#here for Tmax

groupwiseMean(Value~Cultivar,
              data=df_Tmax,
              conf= 0.95,
              digits=3)

```


```{r}

#t.test(df_Tb$Value,conf.level = 0.95)
 
#here for Topt 

groupwiseMean(Value~Cultivar,
              data=df_Topt,
              conf= 0.95,
              digits=3)

```



Other data explorations  using confit but is outdated as R companion library was installed! 


```{r}

#anova lm 
anova(plant.mod1)


```



```{r}

confint(plant.mod1)

```


```{r}

ggplot(df_Tb, aes(x = Cultivar, y = Value)) +
  geom_boxplot(fill = "grey80", colour = "black") +
  scale_x_discrete() +
  #ylim(-8,10)+
  xlab("Cultivar") +
  ylab("Temperature")


```




Now do the same with the Tmax 


```{r}
df_Tmax<-df_Data %>%
  filter(Variate=="Tmax")
  

#then do the lm 

plant.mod2 = lm(Value ~ Cultivar, data = df_Tmax)

#call first summary 
summary(plant.mod2)

```



```{r}

#anova lm 
anova(plant.mod2)


```



```{r}

confint(plant.mod2)

```



```{r}

ggplot(df_Tmax, aes(x = Cultivar, y = Value)) +
  geom_boxplot(fill = "grey80", colour = "black") +
  scale_x_discrete() +
  #ylim(-8,3)+
  xlab("Cultivar") +
  ylab("Temperature")

```





Now Run analysis for the Topt 




```{r}
df_Topt<-df_Data %>%
  filter(Variate=="Topt")
  

#then do the lm 

plant.mod3 = lm(Value ~ Cultivar, data = df_Topt)

#call first summary 
summary(plant.mod3)

```



```{r}

#anova lm 
anova(plant.mod3)


```



```{r}

confint(plant.mod3)

```



```{r}

ggplot(df_Tmax, aes(x = Cultivar, y = Value)) +
  geom_boxplot(fill = "grey80", colour = "black") +
  scale_x_discrete() +
  #ylim(-8,3)+
  xlab("Cultivar") +
  ylab("Temperature")

```





End of this script
next script generate equations for each cultivar separately from 5 to 15.4-5 degrees. 