
---
title: 'Incubator temperatures '
author: "CT"
date: "12.2.2018"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

This script calculates the Thermal time using the incubator temperatures : 
1. hourly as average of the 30minutes  measurements 
2. simple bilinear method ;consider tb, topt and tmax estimated 
3. use all datapoints  datapoints for each linear ascending equation (2.5-35)




```{r}
library(tidyr)
library (dplyr)
library (ggplot2)
library (lubridate)
library (scales)
library(gridExtra)
library(knitr)
```



## 
# ATTENTION HERE ; select the Tb according to Cultivar 

Cultivar	Tb 	Topt 	Tmax
		(oC)	
'Antas'	-2.7 (±0.9)	22.0 (±1.4)	36.0 (±0.4)
'Denmark'	 1.7 (±0.3)	24.0 (±0.4)	35.0 (±0.3)
'Monti'	-0.7 (±0.3)	19.0 (±1.7)	37.0 (±0.7)
'Narrikup'	 0.9 (±0.6)	16.0 (±1.0)	39.0 (±0.3)

							
```{r}
#Antas
#tt_card <- data.frame(temp=c(-2.7,22,22,36),TT=c(0,22,22,0))
#Denmark
#tt_card <- data.frame(temp=c(1.7,24,24,35),TT=c(0,24,24,0))

#Monti
tt_card <- data.frame(temp=c(-0.7,19,19,37),TT=c(0,19,19,0))

#Narrikup
#tt_card <- data.frame(temp=c(0.9,16,16,39),TT=c(0,19,19,0))


#tt_card <- data.frame(temp=c(0,40,40,40),TT=c(0,40,40,40))
tt_card %>%
  ggplot(aes(x=temp, y=TT))+
  #labs(x="Temperature (degree Celsius)")+
  labs(y="Thermal Time (degree days)") +
  xlab(expression(Temperature~~"("^"o"*"C)"))+
  ylab(expression(Thermal~time~~"("^"o"*"Cd)"))+
  theme_bw()+
  geom_line()
  

```



```{r}

 

#Create and test interpolation function - Test if works 

temp_ref  <- 20 # x-axes reference
temp <- tt_card$temp # x-axes
TT <- tt_card$TT # y-axes


int_func <- function(temp,TT,temp_ref){

  # if temp is too low or too high give extreme TT values
 if(temp_ref>temp[length(temp)]) {
   
   out <- TT[length(TT)] 
   # FIXME: approx functions seems to do that - need param
   
 } else if (temp_ref<temp[1]) {
   
   out <- TT[1]
   
 } else {
   
   # else interpolate
   
   tryCatch(  
   
  out <- approx(temp, TT, xout = temp_ref, 
         method="linear", 
         rule = 2)$y,
  error = function(e) 
  {
  out <- NA
  }
) 
  
} # end if check

  return(out)  
  
 }
  
int_func(temp,TT,temp_ref)


```




Note: this file produces the graphs for recorded temperatues i incubators  

```{r, load file}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedGermTemp")
getwd()
#read data , use row.names=NULL to delete Error message 

df_file <- read.table("TempIncub.txt",header =TRUE,row.names= NULL )

```

```{r}
summary(df_file)
```

##Method 1. TT calculate hourly from measurements every 30 minutes!!!  

```{r}

#Average the Temp per Hour

df_file_Hourly<- df_file %>%
  mutate(Date=dmy(Date)) %>%
  group_by(Date, Hour)%>%
  dplyr::select(RecTemp )%>%
  summarise_all(funs(mean))
  
str(df_file_Hourly)
```

`

Connect function TT calculation 


```{r}


df_H <- df_file_Hourly %>%
  #dplyr::select(Date:RecTemp) %>%
    rowwise() %>%
  mutate(TThour=int_func(temp,TT,RecTemp)) %>%
   group_by(Date) %>%
    dplyr::select(TThour)%>%
   summarise_all(funs(mean))%>% 
    mutate(TTday=TThour)%>%
  dplyr::select(-TThour)%>%
    mutate(SumTTday = cumsum(TTday))

summary(df_H)
str(df_H)
#write.table(df_H, "SumTTHourGC.txt")


```


Now merge with the dates of start (sowing) and the dates to reach 50% germination
1. Bring data frame with relevant info with dates 
2. Select the cultivar and temperature range to work in this case all datapoints  as using the two regressions !



```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedGermTemp")
getwd()
#read data , use row.names=NULL to delete Error message 

df_GDates <- read.table("SeedGerm1.txt",header =TRUE,row.names= NULL )
str(df_GDates)

# select cultivars of interest , temperatures of interest and then only Plot and StartDate

D<-df_GDates %>%
  ###ATTENTION HERE - no select only cultivar ! 
  #subset(Temp>2 & Temp<17.7)%>%
  filter(Cultivar=="Narrikup") %>%
  dplyr::select(Plot,startDate)%>%
  mutate(startDate=dmy(startDate))
  
  

str(D)

```


Then bring dataframe with the number of days to DAS50



```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\SeedGermTemp")
getwd()
#read data , use row.names=NULL to delete Error message 

df_germ <- read.table("df_RateGerm.txt",header =TRUE,row.names= NULL )
str(df_germ)

```

Select

							
```{r}

E <-df_germ %>%
dplyr::select(Cultivar, Block,Plot,DAS50E)

summary(E)

df_germ <- NULL



```

merge the dataframes by Plot 
```{r}


#Merge the two dataframes by plot


df_M <- merge(D,E,by ="Plot")
str(df_M)
head(df_M)

#Then calculate the date to 50% Emergence sum the date or sowing + DAS50E
#Note df_Md has duplicated rows - fix it!! 

df_MD <- df_M %>%
  mutate(Date50E=startDate+DAS50E) %>%
  group_by(Plot, DAS50E) %>% 
  dplyr::filter(row_number() == 1)

str(df_MD)
#Here DAte50E is included no need to change format 

# mutate(Date50E = dmy(Date50E)

E <- D <- df_M <- NULL



```



figure out how to calculate tt at sow (start) then tt at the date of 50 emergence make one minus another to find TT emerg 

```{r}
df1 <- merge(df_MD,df_H, by.x="startDate",by.y="Date") %>%
  mutate(SumTT_sow = SumTTday) %>%
  dplyr::select(-SumTTday)
 

str(df1)
```
then subtract from the SummTT at the date of 50% germ 

```{r}


# force formats of dates
df1$Date <- round(df1$Date50E,0)
df_H$Date <- round(df_H$Date,0)

df2 <-  merge(df1,df_H, by="Date") %>%
  mutate(SumTT_DAS50Germ = SumTTday) %>%
  dplyr::select(-SumTTday)%>%
  mutate(SumTTGerm = SumTT_DAS50Germ-SumTT_sow)

str(df2)


```
get the means for each cultivar 

```{r}

dfMean_Allcv<- df2 %>%
  #group_by(Cultivar)%>%
  dplyr::select(SumTTGerm)%>%
  summarise_all(funs(mean,sd))%>%
  mutate(SE=sd/2)




```


