---
title: "thermal time to flower versus Mean Photoperiod analysis "
author: "CT"
date: "09.07.2018"
output:
  pdf_document: default
  html_document: default
  word_document: default

note: include Pp analysis using the mean photoperiod to compare with the results from the re analysis. 
  Iversen 2 collected data; this script is a continuation of script 9 .
  This script use the thermal time from emergence (TT50FromEmerg)
  
  Next scrip 8b contains all the Photoperiods!!! 
  
---

```{r loadLibraries, echo=FALSE, include=FALSE}
#1
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
#library (segmented)
#library(hydroGOF)

```
 
AIM:
- Check the reanalisys data 
Ch03_05_MeanPpToFlowerReanalysis

```{r   loadFile}
#2
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\PredictFlowerTime")

getwd()


```
## Change formats

##file is : TT50FloAndMeanPhotoperiod 

```{r}
#3 get dataframe created similar to ReAnalysis4 which contains the mean photoperiod 
df_tt_MeanPp <- read.table("Ch03_05_MeanPpToFlowerReanalysis.txt",header=TRUE) 


# force date format
#df_tt_MeanPp$SowingD <- dmy(df_tt_MeanPp$SowingD)
str(df_tt_MeanPp)


```

```{r}
#4
summary(df_tt_MeanPp)
```



simply plot the TT50FromEmerg in y and Mean Pp in x 



```{r}

df_FP_all_mean <- df_tt_MeanPp  %>%
  mutate(Variable2=factor(Variable, level=c("DAS50F","TT50F"),
                         labels=c("Days to flower","Thermal-time (degree days)"))) %>%
  mutate(SensGroup2=factor(SensGroup, level=c("E","L"),
                         labels=c("Early","Late"))) %>%
  mutate(Pp_direction=factor(PpDir, level=c("D","I"),
                         labels=c("Decreasing","Increasing")))  %>%
  mutate(Trial=factor(Experiment, level=c("ReAnalysis","Iversen","GC"),
                         labels=c("ReAnalysis","Field","GrowthChamber")))  %>%
  group_by(Experiment,Trial, Cultivar, Variable,Variable2, SensGroup,SensGroup2, PpMean, PpDir,Pp_direction) %>%
   dplyr::select(Experiment,Trial, Cultivar, Variable,Variable2, SensGroup,SensGroup2, PpMean, PpDir,Pp_direction, Value) %>%
   summarise_all(funs(mean,sd))  %>%
  ungroup()
# 
 summary (df_FP_all_mean)

```
Make draft graph 
```{r, fig.width=15, fig.height=10}

 df_FP_all_mean %>%
  filter(Experiment!="GC") %>%
  filter(Variable=="TT50F") %>%
    #filter(Experiment!="ReAnalysis") %>%
 ggplot(aes(x=PpMean,y=mean, colour=SensGroup2, fill=SensGroup2, linetype=Pp_direction) )+
# ggplot(aes(x=PpMean,y=mean, colour=Pp_direction, fill=Pp_direction) )+
  geom_point(size=4, aes(shape=Trial)) +
  ylim(0,NA) +
  geom_vline(xintercept = 13.5, linetype=2, colour='darkgrey') +
 geom_smooth(method = "lm",se=TRUE, alpha=0.2) 

```


Make a final  graph  as per reanalysis

```{r, fig.width=15, fig.height=10}

 df_FP_all_mean %>%
  filter(Experiment!="GC") %>%
  filter(Variable=="TT50F") %>%
  
 ggplot(aes(x=PpMean,y=mean, colour=SensGroup2, fill=SensGroup2, linetype=Pp_direction) )+
# ggplot(aes(x=PpMean,y=mean, colour=Pp_direction, fill=Pp_direction) )+
  geom_point(size=6, aes(shape=Trial)) +
  ylim(0,NA) +
  geom_vline(xintercept = 13.5, linetype=2, colour='darkgrey') +
 geom_smooth(method = "lm",se=TRUE, alpha=0.2) +
theme_bw(base_size = 26) +
  labs(x="Mean photoperiod (hours)", y="Time to 50% flowering ") +
 ylim(0,NA)+
theme(
   #  panel.border = element_rect(colour = "black", size = 3),
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  

  
  #make sowing dates white  
  theme(strip.background = element_rect(colour = "black", fill = "white",size=1.5))


ggsave("plot_2_TT50FlowversusMeanPp_ThermalTimeFlo_FieldReanalysis.tiff", width=14, height=12, dpi=600)

```

for the whole dataset REalsysis + field
```{r}
library(broom)
options(scipen=999)

#Select the Pp you want to regress against PT50


# create the linear fits by groups o variables

  #dfregCv <- temp_A %>% group_by(Cultivar,Pp_dir) %>%
  dfregGroup <- df_FP_all_mean %>% group_by(SensGroup, PpDir) %>%
##For emergence use PpEmerg,
  ##do(fitreg = lm(PhoTherm ~ meanPp50F, data = .))
  do(fitreg = lm(mean  ~  PpMean , data = .))
  ##do(fitreg = lm(PhoTherm ~ Pp1Trifo, data = .))
  
  ##For First Trifo use  Pp1Trifo_mean
 #do(fitreg = lm(PhylC_mean ~ Pp1Trifo_mean, data = .))

## get the linear coefficients by group in a tidy data_frame
dfCoef <- tidy(dfregGroup, fitreg)
dfCoef






#write.table(dfCoefInc, "CoefficientsregressionPT50AgainstPp1Trifo.csv")

```




```{r}

dfCoefInc = glance(dfregGroup, fitreg)
dfCoefInc



```

###################################################################################################################################

Do fit only for Iversen

```{r}

Iversen <- df_FP_all_mean %>%
  filter(Experiment=="Iversen") 
  #filter(Variable=="TT50F")


```




Just for Iversen
```{r}
library(broom)
options(scipen=999)

#Select the Pp you want to regress against PT50


# create the linear fits by groups o variables

  #dfregCv <- temp_A %>% group_by(Cultivar,Pp_dir) %>%
  dfregGroup <-Iversen  %>% group_by(SensGroup, PpDir) %>%
##For emergence use PpEmerg,
  ##do(fitreg = lm(PhoTherm ~ meanPp50F, data = .))
  do(fitreg = lm(mean  ~  PpMean , data = .))
  ##do(fitreg = lm(PhoTherm ~ Pp1Trifo, data = .))
  
  ##For First Trifo use  Pp1Trifo_mean
 #do(fitreg = lm(PhylC_mean ~ Pp1Trifo_mean, data = .))

## get the linear coefficients by group in a tidy data_frame
dfCoef <- tidy(dfregGroup, fitreg)
dfCoef



#write.table(dfCoefInc, "CoefficientsregressionPT50AgainstPp1Trifo.csv")

```




```{r}

dfCoefInc = glance(dfregGroup, fitreg)
dfCoefInc



```


###################################################################################################################################

Do fit only for REanalysis

```{r}

ReAnalysis <- df_FP_all_mean %>%
  filter(Experiment=="ReAnalysis")
  #filter(Variable=="TT50F")


```




Just for Iversen
```{r}
library(broom)
options(scipen=999)

#Select the Pp you want to regress against PT50


# create the linear fits by groups o variables

  #dfregCv <- temp_A %>% group_by(Cultivar,Pp_dir) %>%
  dfregGroup <-ReAnalysis  %>% group_by(SensGroup, PpDir) %>%
##For emergence use PpEmerg,
  ##do(fitreg = lm(PhoTherm ~ meanPp50F, data = .))
  do(fitreg = lm(mean  ~  PpMean , data = .))
  ##do(fitreg = lm(PhoTherm ~ Pp1Trifo, data = .))
  
  ##For First Trifo use  Pp1Trifo_mean
 #do(fitreg = lm(PhylC_mean ~ Pp1Trifo_mean, data = .))

## get the linear coefficients by group in a tidy data_frame
dfCoef <- tidy(dfregGroup, fitreg)
dfCoef



#write.table(dfCoefInc, "CoefficientsregressionPT50AgainstPp1Trifo.csv")

```




```{r}

dfCoefInc = glance(dfregGroup, fitreg)
dfCoefInc



```






######################################################################################################################################


Make a final  graph  for Woogenellup

```{r, fig.width=15, fig.height=10}

 Wooge <-df_FP_all_mean %>%
  filter(Experiment!="GC") %>%
  filter(Variable=="TT50F") %>%
  filter(Cultivar=="Woogenellup") 
filter(Cultivar=="Woogenellup")
Wooge%>%

 ggplot(aes(x=PpMean,y=mean, colour=SensGroup2, fill=SensGroup2, linetype=Pp_direction) )+
# ggplot(aes(x=PpMean,y=mean, colour=Pp_direction, fill=Pp_direction) )+
  geom_point(size=6, aes(shape=Trial)) +
 #ylim(0,NA) +
  geom_vline(xintercept = 13.5, linetype=2, colour='black') +
 geom_smooth(method = "lm",se=TRUE, alpha=0.2) +
theme_bw(base_size = 26) +
  labs(x="Mean photoperiod (hours)", y="Time to 50% flowering ") +
 ylim(0,NA)+
theme(
   #  panel.border = element_rect(colour = "black", size = 3),
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  

  #make sowing dates white  
  theme(strip.background = element_rect(colour = "black", fill = "white",size=1.5))


##ggsave("plot_2_TT50FlowversusMeanPp_ThermalTimeFlo_FieldReanalysis.tiff", width=14, height=12, dpi=600)

```

```{r}

str(Wooge)
```

equations for woogenellup


# Get linear coefficients of equations above
##check what are these P values lonly for the decreasing Photoperiod 

Just for woogenellup
```{r}
library(broom)
options(scipen=999)

#Select the Pp you want to regress against PT50


# create the linear fits by groups o variables

  #dfregCv <- temp_A %>% group_by(Cultivar,Pp_dir) %>%
  dfregGroup <- Wooge %>% group_by(PpDir) %>%
##For emergence use PpEmerg,
  ##do(fitreg = lm(PhoTherm ~ meanPp50F, data = .))
  do(fitreg = lm(mean  ~  PpMean , data = .))
  ##do(fitreg = lm(PhoTherm ~ Pp1Trifo, data = .))
  
  ##For First Trifo use  Pp1Trifo_mean
 #do(fitreg = lm(PhylC_mean ~ Pp1Trifo_mean, data = .))

## get the linear coefficients by group in a tidy data_frame
dfCoef <- tidy(dfregGroup, fitreg)
dfCoef






#write.table(dfCoefInc, "CoefficientsregressionPT50AgainstPp1Trifo.csv")

```




```{r}

dfCoefInc = glance(dfregGroup, fitreg)
dfCoefInc



```


