---
title: "TPredict time to flower in Lincoln and H Bay"
author: "CT"
date: "14 Oct 2020"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE, loadlibraires}
#knitr::opts_chunk$set(echo = TRUE)
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)

```

C:\GitHubRepos\SubcloverPhD\SubClover\PredictFlowerTime

##Justbring the mean Das ttf50 OF All experiemtns 

```{r readData}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\PredictFlowerTime")
getwd()

#create file
df_HBay <- read.table("df_CumTT_HBay_Hastings.txt", header=TRUE)

df_Lincoln <- read.table("df_CumTT_LincolnHistorical.txt", header=TRUE)
#head(df_We)

#summary(df_Weiv)
```


Format dates 

```{r}


df_HBay$Date<-ymd(df_HBay$Date)
str(df_HBay)


df_Lincoln$Date<-ymd(df_Lincoln$Date)
str(df_HBay)


str(df_Lincoln)






```




```{r}

dfLocations<- rbind(df_Lincoln,df_HBay )
summary(dfLocations)

```





Get the day of the year from date 
remove the SumTTday to recalculate by location


Use equation from chapter 7 only for the Decreasing Pp 

Chapter 7 
TT50F = -3237(±275.8)+369(±22.1)Pp, R2=0.8,

Chapter 4 dsubdata : Updated after Derricks review: use only Iversen equation - late cvs 

TT50F = -5040(±225.9.8) + 487(±16.0Pp, R2=0.99 p<0.001. 


```{r}

##(Indicate the sowing date inDOY)

##Sow (sow in February 1)
#DOY_sow <-32

##Sow (sow in February 15)
#DOY_sow <-46

##Sow (sow in March 1)
#DOY_sow <-61 

## Sow in March 15
#DOY_sow <-75

##Sow in 01 April 
#DOY_sow <- 92

##Sow in 15 April 
#DOY_sow <- 106

##Sow in 01 May
DOY_sow <- 122

##Sow in 15 May
#DOY_sow <- 137

# df_flow_date <- dfLocations %>%
#     mutate(DOY=yday(Date)) %>%
#   mutate(TT_sum_window = ifelse(DOY >DOY_sow,"PostSow","BeforeSow")) %>%  
#   dplyr::rename(Location=LocationYear) %>%
# 
#   dplyr::select(-SumTTday) %>%
#   mutate(Year=year(Date)) %>%
#   mutate(LocationYear=paste0(Location,"_",Year)) %>%
#   mutate(LocationYear=factor(LocationYear)) %>%
#   mutate(PeriodLabel=paste0(LocationYear,"_",TT_sum_window)) %>%
#   group_by(PeriodLabel) %>%
#   arrange(Date) %>%
#   mutate(AcumTTday = cumsum(TTday)) %>%
#   mutate(Pp_sum = cumsum(Pp)) %>%
#   mutate(Pp_mean=Pp_sum/(DOY-DOY_sow)) %>%
#   # mutate(Ppmean=Pp) %>%
#   # mutate(lag_Pp_mean=lag(Ppmean),
#   #                 Pp_mean=(Pp+lag_Pp_mean)/2) %>%
#   ##Use for chapter 7# mutate(
#     mutate(TT50_D_E = max(-3237 + 369*Pp_mean,565),
#     TT50_D_L = max(-4831 + 458*Pp_mean,770))  %>%
#  ##Use equatios chapter 3 
#    # mutate(
#    #   TT50_I_E = 1275 + (-41)*Pp_mean,
#    #   TT50_I_L = 722 + (27)*Pp_mean,
#    #   TT50_D_E = -8739 + 831*Pp_mean,
#    #   TT50_D_L =  -10721 + 977*Pp_mean)  %>%
#   
#   filter(TT_sum_window == "PostSow") %>%
#   mutate(DateTT50_D_E = ifelse(AcumTTday>TT50_D_E,"F","V"),
#     DateTT50_D_L =  ifelse(AcumTTday>TT50_D_L,"F","V")) %>%
#     mutate(Pp_diff = Pp - lag(Pp, default = Pp[1])) %>%
#     ungroup()
# 
# summary(df_flow_date)

```
Use data for combining equations reanalysis and field (Chapter 7)

```{r}

df_flow_date <- dfLocations %>%
    mutate(DOY=yday(Date)) %>%
  mutate(TT_sum_window = ifelse(DOY >DOY_sow,"PostSow","BeforeSow")) %>%  
  dplyr::rename(Location=LocationYear) %>%

  dplyr::select(-SumTTday) %>%
  mutate(Year=year(Date)) %>%
  mutate(LocationYear=paste0(Location,"_",Year)) %>%
  mutate(LocationYear=factor(LocationYear)) %>%
  mutate(PeriodLabel=paste0(LocationYear,"_",TT_sum_window)) %>%
  group_by(PeriodLabel) %>%
  arrange(Date) %>%
  mutate(AcumTTday = cumsum(TTday)) %>%
  mutate(Pp_sum = cumsum(Pp)) %>%
  mutate(Pp_mean=Pp_sum/(DOY-DOY_sow)) %>%
  # mutate(Ppmean=Pp) %>%
  # mutate(lag_Pp_mean=lag(Ppmean),
  #                 Pp_mean=(Pp+lag_Pp_mean)/2) %>%
  ##Use for chapter 4# mutate(
    # mutate(TT50_I_E = 774,
    # TT50_I_L = 1090,
    # TT50_D_E = min(max(-3237 + 369*Pp_mean,808),1716),
    # TT50_D_L = min(max(-3237 + 369*Pp_mean,1062)),2328)  %>%
  ##Use for chapter 4 only field experiment and late cvs # 
  ##TT50F = -5040(±225.9.8) + 487(±16.0Pp, R2=0.99 p<0.001
    mutate(TT50_I_E = 774,
    TT50_I_L = 1090,
    TT50_D_E = min(max(-5040 +487*Pp_mean,800),1750),
    TT50_D_L = min(max(-5040 + 487*Pp_mean,1000)),2400)  %>%
  
  
 ##Use equatios chapter 3 
   # mutate(
   #   TT50_I_E = 1275 + (-41)*Pp_mean,
   #   TT50_I_L = 722 + (27)*Pp_mean,
   #   TT50_D_E = -8739 + 831*Pp_mean,
   #   TT50_D_L =  -10721 + 977*Pp_mean)  %>%
  
  filter(TT_sum_window == "PostSow") %>%
  mutate(
    DateTT50_I_E = ifelse(AcumTTday>TT50_I_E,"F","V"),
    DateTT50_I_L =ifelse(AcumTTday>TT50_I_L,"F","V"),
    DateTT50_D_E = ifelse(AcumTTday>TT50_D_E,"F","V"),
    DateTT50_D_L =  ifelse(AcumTTday>TT50_D_L,"F","V")) %>%
    mutate(Pp_diff = Pp - lag(Pp, default = Pp[1])) %>%
    ungroup()

summary(df_flow_date)
```


group by location 

```{r, fig.width=12}

  df_flow_date%>%
  ggplot(aes(x=Date, y=AcumTTday)) +
  geom_line()+
  facet_grid(Location~.)
  
  
```

Do for early in decreasing Pp

```{r}
df_flow_date_D_E <- df_flow_date %>%
  
  filter(DateTT50_D_E =="F") %>%
  group_by(LocationYear) %>%
 # filter(AcumTTday > 1000)
  #filter(Pp_mean >13)
  filter(Date==min(Date))
         
```


```{r}
ref<-ymd("1900-01-01")

df_flow_date_D_E %>%
  ggplot(aes(x=DOY+ref, y=..scaled..,fill=Location)) +
  geom_density(alpha=0.2) 
#    scale_x_date(date_breaks = "1 month",
# labels=date_format("%b-%Y"),
# limits = as.Date(c('1999-11-01','2000-03-01')))
```


```{r}
df_gather <- df_flow_date %>%
 gather(VarName,VarValue,DateTT50_D_E:DateTT50_D_L) %>%
 mutate(VarName=factor(VarName), VarValue=factor(VarValue)) %>%
 group_by(VarName, LocationYear) %>%
  filter(VarValue=="F") %>%
  filter(DOY==min(DOY)) %>%
  ungroup() 

summary(df_gather)
```

```{r, fig.width=12}
ref<-ymd("2000-01-01")

library(scales)

df_gather %>%
  filter(VarName!="DateTT50_I_E") %>%
  filter(VarName!="DateTT50_I_L") %>%
  filter(VarName!="DateTT50_D_E") %>%
#  mutate(VarName=factor(VarName,levels=c(,labels=c()))) %>%
  ggplot(aes(x=DOY+ref, y=..scaled.., fill=VarName)) +
  
 #  ggplot(aes(x=DOY+ref, fill=VarName)) +
  geom_density(alpha=0.3)  +
  facet_grid(Location~., scales='free') +
  ylab("Probability of flowering (dimentionsless)") +
  xlab("Flowering month") + theme_bw()+
  theme(text = element_text(size=20)) + 
    scale_x_date(date_breaks = "1 month", 
                 labels=date_format("%b"),
                 limits = as.Date(c('2000-06-01','2000-11-15')))+
  
  
  theme(
     panel.background = element_rect(fill = "white", colour = "black", size = 2, linetype = "solid"), 
     panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "grey"), 
     panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "grey"),
     axis.line = element_line(colour = "black"))+
     theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  
  #theme(strip.background = element_rect(colour = "black", fill = "white",size=1)) 

 #ggsave("plot_1_PredictFlowering.tiff", width=12, height=10, dpi=600)
 
```



```{r, fig.width=12}
ref<-ymd("2000-01-01")

library(scales)

df_gather %>%
  filter(VarName!="DateTT50_I_E") %>%
  filter(VarName!="DateTT50_I_L") %>%
   filter(VarName!="DateTT50_D_E") %>%
#  mutate(VarName=factor(VarName,levels=c(,labels=c()))) %>%
  ggplot(aes(x=DOY+ref, y=..scaled.., fill=VarName)) +
 #  ggplot(aes(x=DOY+ref, fill=VarName)) +
  geom_density(alpha=0.3)  +
  facet_grid(Location~., scales='free') +
   geom_abline(xintercept = 0.5, linetype=2, colour='darkgrey') +
  ylab("Probability of flowering (dimentionsless)") +
  xlab("Flowering month") + theme_bw()+
  theme(text = element_text(size=20)) + 
    scale_x_date(date_breaks = "1 month", 
                 labels=date_format("%b"),
                 limits = as.Date(c('2000-06-01','2000-11-15')))+
  
  
  theme(
     panel.background = element_rect(fill = "white", colour = "black", size = 2, linetype = "solid"), 
     panel.grid.major = element_line(size = 0.5, linetype = 'solid', colour = "white"), 
     panel.grid.minor = element_line(size = 0.25, linetype = 'solid', colour = "white"),
     axis.line = element_line(colour = "black"))+
     theme(strip.background = element_rect(colour = "black", fill = "white",size=1))
  
  #theme(strip.background = element_rect(colour = "black", fill = "white",size=1)) 

 #ggsave("plot_1_PredictFlowering_Version2.tiff", width=12, height=10, dpi=600)
 
```








