---
title: "Runners Poukawa "
author: "CT"
date: "17.08.2017"
output: html_document
---

Purpose:

-Analysis of runner elongation for Poukawa from previous script (use Runner)
- Calculate the time to reach 50% plants with runner (5 plants as all 10 plants had produced runners )
- Calculate rate of leaf appearance (1/Days) 
 - variable Runner is already in percentage!!! 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
```



```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\RunnersPok")
getwd()
#create file
#df_Runner <- read.table("Number_Runner.txt",header=TRUE)

df_Runner <- read.table("Number_RunnerPok.txt",header=TRUE)

str(df_Runner)


```


Define formats 

```{r loadFile}


# define factors for the ones that "look like" values

df_run_worked <- df_Runner %>%
  mutate(SowingDate = ymd(SowingDate), 
         ReadingDate = ymd(ReadingDate),
         DAS = as.numeric(DAS),
         Plot= as.factor(Plot),
         Block=as.factor(Block),
         Cultivar=as.factor(Cultivar),
         SowTreat=as.factor(SowTreat))%>%
  dplyr::select(-s1,-s2,-s3,-s4,-s5,-s6,-s7,-s8,-s9,-s10)

 

```


```{r}

str(df_run_worked)

```





#Try another loop





Calculate 50 PercentEmergence  

```{r SummariseDf}



#  loop to calculate tt_50p_flow for each plot 

#sowd <- unique(df_50_Perc$SowingDate)
plots <- unique(df_run_worked$Plot)
 


#loop trough each combination of factor levels

for(p in 1:length(plots)) {
#  for(j in 1:length(var)){
 #   for(k in 1:length(sow)){
      
      # clean value holders
      #DAS_50p_emerg <- 0
      #tt_50p_emerg <- 0
      # clean value holders
      DAS_50_run <- 0
     
      # filter for each combination

  df_sub <- df_run_worked %>%
    # subset(Cultivar == as.character(cv[i]) &
    # Plot == as.character(var[j]) &
    #   Block == as.character(var[b]) &
    # SowTreat == as.character(sow[k])) %>%
    subset(Plot == plots[p]) %>%
    arrange(Runner)
    #arrange(DAS)
    
  df_sub
  head(df_sub)
  # create percentage with maximum value recorded 
  # to avoid crossing the 50% line twice
  
  df_sub$av_Run_max <- 0 # create new col
  
  for(z in 1:nrow(df_sub)) {
    
    df_sub$av_Run_max[z] <- max(df_sub$Runner[z],
                                 df_sub$Runner [z-1])
    
  }
  
  df_sub
  head(df_sub)
  tail(df_sub)

  
  # Interpolate 
  y_ref <- 0.5 # y value where we want to find x by interpolation note that here I used 0.5 because used pure runner count number! 
  
  # interpolate
  #find DAS at 50 Pecent Emergence 

  tryCatch(  
  DAS_50_run <- approx(df_sub$Runner, 
  df_sub$DAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
 DAS_50_run <- NA
  }
)
#   #find TT at 50 Pecent Emergence
#   tryCatch(  
#   tt_50p_emerg <- approx(df_sub$Runner, 
#   df_sub$TT_to_emerg , xout = y_ref, rule = 1)$y,
#   error = function(e) 
#   {
#   tt_50p_emerg <- NA
#   }
# )

  df_temp <- NULL
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             Runner = df_sub$Runner[1], 
                             SowTreat = df_sub$SowTreat[1],
                             Plot = df_sub$Plot[1],
                             Block = df_sub$Block[1],
                             DAS50E = DAS_50_run)
                             
  print(p)
  
  if(p == 1) {
    df_tt_50p_emerg <- df_temp
  } else {
   df_tt_50p_emerg <- rbind(df_tt_50p_emerg,df_temp) 
  }                     
  
#    } 
  } # end plot loop


```

```{r}
##rename dataframe


df_all <- df_tt_50p_emerg 

```





Include dates of sowing again in dataframe  
```{r}
sdLookup <- data.frame (
  SowTreat = c("S1","S2","S3","S4","S5","S6","S7","S8"),
  SowingDate = c("19/02/2016", 
                 "30/03/2016" ,
                 "30/05/2016" ,
                 "5/07/2016" ,
                 "24/08/2016" ,
                 "11/10/2016" ,
                 "24/11/2016",
                 "05/01/2017"))

sdLookup$SowingDate <- dmy(sdLookup$SowingDate)

df_50Run <- merge(df_all, sdLookup, by="SowTreat")
summary(df_50Run)


```



Now correct column names after loop not to mix with other generated tables

```{r}

df_50R<-df_50Run%>%
  mutate(DAS=as.numeric(DAS50E))%>%
  dplyr::select(-DAS50E)


str(df_50R)
 


```



```{r}

write.table(df_50R,"df_DAS_50toRunnerPok.txt")
```




Calculate RAte (1/days to 50%) 


```{r}

#try 1/DAS50% = Rate

df_RateRunner <- df_50R %>%
  mutate(Rate=1/ DAS)

  summary(df_RateRunner)
  
  write.table(df_RateRunner,"RateRunnerPok.txt")

```



Graph rate and SowTreat

```{r}
#Graph 

  df_RateRunner %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(DAS)%>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 9 trifoliates  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

df_RateRunner %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 9 trifoliates  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

```




End of this script Calc 2. 
Move to script 3 to include temperatures  
