---
title: "Emergence seedlings I2"
author: "CT"
date: "Thursday, December 31, 2015"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

Purpose:

-Analysis of plant population 
-calculate the percentage of emergence 



```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(mosaic)
library(lattice)
```


```{r loadFile}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergenceIv2")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\EmergenceIv2")
getwd()

#create file
df_emerg <- read.table("PlantPop.txt",header=TRUE)



# define factors for the ones that "look like" values
df_emerg$Plot <- as.factor(df_emerg$Plot)
df_emerg$Block <- as.factor(df_emerg$Block)

 df_emerg <- df_emerg %>%
  mutate(SowingDate = dmy(SowingDate), 
         ReadingDate = dmy(ReadingDate),
         PlantPop = (Sub1+Sub2+Sub3)/3/0.01)

str(df_emerg)
head(df_emerg)
tail(df_emerg)


df_emerg %>% filter(Plot ==1) %>% summary()


```

```{r, fig.height= 5, fig.width= 15}
# Graph it 


#Graph         
  df_emerg %>% 
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),labels=c("June", "July", "September", "November", "December", "February","March", "May")))%>%
  group_by(Cultivar, SowTreat, DAS) %>%
  #filter(SowTreat =="March"| SowTreat =="May" )%>%
  #filter(Cultivar =="Antas"|Cultivar =="Monti")%>%
  #dplyr::select(-SowingDate, - ReadingDate) %>%
  summarise_all(funs(mean,sd)) %>%
  ggplot(aes(x=DAS, y=PlantPop_mean))+ 
  #geom_point(aes(colour=Cultivar,shape=Cultivar))+
  geom_point(aes(shape=Cultivar),size=4)+
  #geom_line(aes(colour=Cultivar))+
  #geom_smooth(aes(alpha=0.3))+
  #add error bar
  #geom_errorbar(aes(ymin=PlantPop_mean-PlantPop_sd/1.73,
                    #ymax=PlantPop_mean+PlantPop_sd/1.73))+
  theme_bw()+
  #geom_errorbar(aes(x=20,ymin=200,ymax=300,width=0.2))+
  facet_wrap(~SowTreat,ncol=4, scales = "free")+
  theme_bw()+
  ylim(0, 2400)+
  labs(y="Population (m2)",x="Days after sowing") 
  #+geom_abline(intercept = 50, slope = 0)

#save image 
 ggsave("plot_Population.png", width=12, height=6, dpi=400)
```

This section calculates the Percentage Emergence in relation to the maximum plant population observed (which was 2400!)


```{r CalculatePercentageEmergence }

df_emerg_perc <- df_emerg %>%
group_by(Plot) %>%
mutate(PercEmerg = round(PlantPop/max(PlantPop)*100,digits=2))

# Check
summary(df_emerg_perc)
tail(df_emerg_perc)
df_emerg_perc %>%  filter(Plot=="2")


```

Graph the percentage of seedlings were established based on max overall emergence (~ 2200)
```{r, fig.width= 10, fig.height=6}
#Graph         
  df_emerg_perc %>%  group_by(Cultivar, SowTreat, DAS) %>%
#  filter(Cultivar =="Monti") %>%
  dplyr::select(-SowingDate, - ReadingDate) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=PercEmerg)) + 
  geom_point(aes(colour=Cultivar,shape=Cultivar)) +
  geom_line(aes(colour=Cultivar)) +
     theme_bw()+
  facet_wrap (~SowTreat,ncol=4, scales = "free")+
  labs(y="Percentage  of Seedling emergence",x="Days after sowing") +
  #geom_abline(intercept = 50, slope = 0)
```

Now Calculate the Percentage of Emergence in relation to the final emergence. Need to calculate the final population first and then estimate the percentage. all  plots have to end up with 100% !! 


```{r}

df_FinalPop<-df_emerg %>%
group_by(Plot) %>%
  filter(DAS==max(DAS))%>%
  dplyr::select(PlantPop)%>%
  summarise_all(funs(max))%>%
  mutate(FinalPop=round((PlantPop)*1,digits=2))%>%
  dplyr::select(-PlantPop)

#Now merge the two dataframes to calculate the percentage of emergence relative to the final pop 

df_merged1 <- merge(df_FinalPop,df_emerg,by="Plot")%>%
  mutate(PercFinalEmerg=PlantPop/FinalPop*100)

```



select only data for Woogenellup 
```{r, fig.height=5, fig.width=10}


#Graph         
  W <- df_merged1 %>%  
  group_by(Cultivar, SowTreat, DAS) %>%
  filter(Cultivar =="Woogenellup") %>%
  filter (SowTreat== "S2"| SowTreat== "S3"|SowTreat== "S4"|SowTreat== "S6")%>%
  dplyr::select(-SowingDate, - ReadingDate) %>%
  dplyr::select(PercFinalEmerg) %>%
  summarise_all(funs(mean,sd))

W %>%
  ggplot(aes(x=DAS, y=mean)) + 
  geom_point() +
  #here if only need a line
  #geom_line() +
  #or added a sigmoid fit 
  geom_smooth(method="nls", formula=y~1+Vmax* (1-exp(-x/tau)), start= c(tau=0.2,Vmax=2),se=FALSE)+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
     theme_bw()+
  facet_wrap (~SowTreat,ncol=4, scales = "free")+
  ylim(0,140)+
  labs(y="Percentage  of Seedling emergence",x="Days after sowing") +
  geom_abline(intercept = 50, slope = 0)



```


try graph 2 updated code 

```{r}




#Graph         
  W <- df_merged1 %>%  
  group_by(Cultivar, SowTreat, DAS) %>%
  filter(Cultivar =="Woogenellup") %>%
  filter (SowTreat== "S2"| SowTreat== "S3"|SowTreat== "S4"|SowTreat== "S6")%>%
  dplyr::select(-SowingDate, - ReadingDate) %>%
  dplyr::select(PercFinalEmerg) %>%
  summarise_all(funs(mean,sd))

W %>%
  ggplot(aes(x=DAS, y=mean)) + 
  geom_point() +
  #geom_line() +
  geom_smooth(method="nls", formula=y~1+Vmax* (1-exp(-x/tau)), 
              
              method.args= list(start=c(tau=0.2,Vmax=2)))+
  
  #stat_smooth()+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
     theme_bw()+
  facet_wrap (~SowTreat,ncol=4, scales = "free")+
  ylim(0,180)+
  labs(y="Percentage  of Seedling emergence",x="Days after sowing") +
  geom_abline(intercept = 50, slope = 0)

```





```{r ANOVAMaxPlantPop}

#compare max plant population among Sowing dates and cultivars. get the last DAS because sometimes plants died

df_emerg_perc3 <- df_emerg %>%
group_by(SowTreat,Cultivar,Block,Plot) %>%
  filter(DAS==max(DAS))%>%
  dplyr::select(PlantPop)%>%
  summarise_all(funs(max))%>%
  mutate(FinalPop=round((PlantPop)*1,digits=2))

head(df_emerg_perc3)
summary (df_emerg_perc3)

write.table(df_emerg_perc3, "df_emerg_perc3.txt")

```


Transform 

```{r}

#normality test
shapiro.test(df_emerg_perc3$FinalPop)


#data transformation
file <- df_emerg_perc3

# file$transf_sqr <- sqrt(df_emerg_perc3$FinalPop)
# file$transf_log <- log(df_emerg_perc3$FinalPop)
# file$transf_log1 <- log(df_emerg_perc3$FinalPop+1)
file$transf_no <- 1*(df_emerg_perc3$FinalPop)
file$transf_logit <- logit(df_emerg_perc3$FinalPop/10000)
head(file)

shapiro.test(file$transf_logit)

x <- c("transf_logit", "transf_no")
colsSelec <- match(x,colnames(file))

file %>%
  tidyr::gather("transformation","value",colsSelec) %>%
  ggplot(aes(value)) + 
  geom_histogram() +
 # facet_wrap(SowTreat~transformation, scales="free", ncol=4) +
  facet_grid(transformation~SowTreat, scales="free")

head(file)


#QQplot
var<-file$transf_no
qqnorm(var)
qqline(var, col = 2)
qqplot(var, rt(3000))

#-------------------------------------------------
# ANOVA (selecing by hand FIXME: do loop)
# file.subset <- file %>% subset(SowTreat == "S2" & round==1)
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar*SowTreat + Block, 
                data = file.subset)

summary(my.anova)

TukeyHSD(my.anova)

#Means separation 
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none") ) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
(LSD.test(my.anova, c("SowTreat","Cultivar"), alpha= 0.05, p.adj="none"))

```



Create Graph Percent emergence with Mean Soil Temperature 
```{r}

#("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergenceIv2")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\EmergenceIv2")
getwd()


df_fileSo <- read.table("SoilTemp.txt", header=TRUE)

head(df_fileSo)

df_fileSo <- df_fileSo %>%
mutate(ReadingDate = dmy(Date)) %>%
dplyr:: select(-Date)
str(df_fileSo)

#
head(df_merged1)
head(df_fileSo)

 
# Merge SoilTemp and Emergence  at measurement date
df_emerg_perc_SoilT <- NULL
df_emerg_perc_SoilT <- merge(df_merged1,df_fileSo,by="ReadingDate")
head(df_emerg_perc_SoilT)


```

Bring data ThermalSumSoil

```{r SoilTemp}
# include soil  temperature before 30 June_lysimeter  

df_SoilTT <- read.table("ThermalSumSoil.txt",header=TRUE)
head(df_SoilTT)

# convert to date format
df_SoilTT <- as.data.frame(df_SoilTT) %>%
 mutate(Date=ymd(Date))


# check
head(df_SoilTT)
summary (df_SoilTT)

```

Merge the dataframes 

```{r}

# Merge Tt at measurement date
df_emerg_perc_TT <- NULL
df_emerg_perc_TT <- merge(df_merged1,df_SoilTT,by.x="ReadingDate",by.y="Date")
df_emerg_perc_TT <- merge(df_emerg_perc_TT,df_SoilTT,by.x="SowingDate",by.y="Date")
df_emerg_perc_TT$TT_to_emerg <- df_emerg_perc_TT$TT.x-df_emerg_perc_TT$TT.y
summary(df_emerg_perc_TT)

#save as table 
write.table(df_emerg_perc_TT, "df_emerg_perc_soilTT.txt")


head(df_emerg_perc_TT )


  


```
Then graph the percentage of emergence relative to the final palnt population

```{r, fig.width=10, fig.height=6}
# graph emerg x tt
df_emerg_perc_TT %>%
  group_by(Cultivar, SowTreat, TT_to_emerg) %>%
  #dplyr::select(-SowingDate, - ReadingDate) %>%
#  filter(Cultivar =="Narrikup") %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=TT_to_emerg, y=PercFinalEmerg,colour=Cultivar)) + 
  geom_point() +
  geom_line() +
  #facet_grid (Cultivar~., scales = "free")+
  geom_abline(intercept = 50, slope = 0) +
  facet_wrap (~SowTreat,ncol=4, scales = "free")+
  theme_bw() +
  theme(text = element_text(size = 10))+
  xlab("Thermal-time from sowing") +
  ylab("Percentage emergence")
```

