---
title: "Emergence seedlings I2"
author: "CT"
date: "01.01.2016"
output: html_document
---

This script does this:

-Reads the table "df_tt_50p_emerg.txt"
- Run the anova on DAS and TT to 50 % Emergence for Sowind dates and cultivars 
- Do it overall and then each SowTreat individually (Saville)

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(mosaic)
library(lattice)

```
Read file 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergenceIv2")
getwd()

#create file
df_emerg1 <- read.table("df_tt_50p_emerg.txt",header=TRUE)

head(df_emerg1)



```
Check formats 
```{r}
df_emerg1$SowTreat <- as.factor(df_emerg1$SowTreat)
df_emerg1$Cultivar <- as.factor(df_emerg1$Cultivar)
df_emerg1$Block <- as.factor(df_emerg1$Block)
df_emerg1$Plot <- as.factor(df_emerg1$Plot)

str(df_emerg1)
head(df_emerg1)
summary(df_emerg1)
```

Check data for normality  
Transformations are : sqrt, log, log+1 and no transformation (transf_no)

```{r DataCheckANOVADf}

# This step is now check for data Normality 

#normality test
shapiro.test(df_emerg1$DAS50E)
shapiro.test(df_emerg1$TT50E)

#data transformation
file <- df_emerg1

file$transf_sqr <- sqrt(df_emerg1$DAS50E)
file$transf_log <- log(df_emerg1$DAS50E)
file$transf_log1 <- log(df_emerg1$DAS50E+1)
file$transf_no <- 1*(df_emerg1$DAS50E)
head(file)


x <- c("transf_sqr", "transf_log","transf_log1", "transf_no")
colsSelec <- match(x,colnames(file))


```

histogram of residuals 
```{r}
file %>%
  tidyr::gather("transformation","value",colsSelec) %>%
  ggplot(aes(value)) + 
  geom_histogram() +
 # facet_wrap(SowTreat~transformation, scales="free", ncol=4) +
  facet_grid(transformation~SowTreat, scales="free")

head(file)

#normality test
#shapiro.test(file$transf_ln)


```

then check QQ plot

```{r}
#QQplot
var<-file$transf_no
qqnorm(var)
qqline(var, col = 2)
# qqplot(var, rt(3000))

#-------------------------------------------------

```

 
 Here general data overview 
```{r}

# ANOVA (selecing by hand FIXME: do loop)
file.subset <- file %>% subset(SowTreat == "S7" )
#file.subset <- file 

head(file.subset, 50)
summary(file.subset)
#my.anova <- aov(transf_no ~ Cultivar*SowTreat + Block, 
                #data = file.subset)

my.anova <- aov(transf_no ~ Cultivar+ Block, 
                data = file.subset)
summary(my.anova)

#TukeyHSD(my.anova)

#Means separation 
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none")) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
#(LSD.test(my.anova, c("SowTreat","Cultivar"), alpha= 0.05, p.adj="none"))

#loop trough each combination of factor levels
```


make an ANOVA loop here 
Then make anova for DAS50E 
get mean separation when P <0.05

```{r}

y <- c("S1","S2","S3","S4","S5","S6","S7", "S8")

sdIndex <- unique(df_emerg1$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex


for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_emerg1 %>%
    #dplyr::select(Plot, Cultivar, Block, SowTreat, DAS50E)
  filter(SowTreat==sdIndex[i])

  head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(DAS50E~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig CV***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } # do if

if ((summary(my.anova)[[1]][["Pr(>F)"]][2])>0.05) {print("***Not Signfican CV***")
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none")))
  } 
if ((summary(my.anova)[[1]][["Pr(>F)"]][2])<0.05) {print("***Sig Block***")
  print((LSD.test(my.anova, c("Block"), alpha= 0.05, p.adj="none")))
  } 
#if ((summary(my.anova)[[1]][["Pr(>F)"]][4])<0.05) {print("***Sig CV:Depth Int***")
  #print((LSD.test(my.anova, c("cv:depth"), alpha= 0.05, p.adj="none")))
  #} 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}



```

Now get mean values of TT50E when significant P<0.05

```{r}

y <- c("S1","S2","S3","S4","S5","S6","S7", "S8")

sdIndex <- unique(df_emerg1$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex


for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- df_emerg1 %>%
    #dplyr::select(Plot, Cultivar, Block, SowTreat, DAS50E)
  filter(SowTreat==sdIndex[i])

  head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(TT50E~Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig CV***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } # do if

#if ((summary(my.anova)[[1]][["Pr(>F)"]][2])<0.05) {print("***Sig Depth***")
  #print((LSD.test(my.anova, c("depth"), alpha= 0.05, p.adj="none")))
  #} 
if ((summary(my.anova)[[1]][["Pr(>F)"]][2])<0.05) {print("***Sig Block***")
  print((LSD.test(my.anova, c("Block"), alpha= 0.05, p.adj="none")))
  } 
#if ((summary(my.anova)[[1]][["Pr(>F)"]][4])<0.05) {print("***Sig CV:Depth Int***")
  #print((LSD.test(my.anova, c("cv:depth"), alpha= 0.05, p.adj="none")))
  #} 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```










