---
title: "Emergence seedlings Iversen 2"
author: "CT"
date: "01.01.2016"
output: html_document
---

This script does this:

- get the dataframe produced in Calc1  
- Calculate the DAS and TT for the 50% emergence by a loop interpolating points
- Calculate the rate of emergence (1/Days)
_Graph results  


```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
library (gridExtra)
```


```{r loadFile}
#setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergenceIv2")
setwd("C:\\GitHubRepos\\SubcloverPhD\\Subclover\\EmergenceIv2")
getwd()

#create file
df_emerg1 <- read.table("df_emerg_perc_soilTT.txt",header=TRUE)



```

Format changes 
```{r}
#change formats 
df_emerg1$ReadingDate <- ymd(df_emerg1$ReadingDate )
df_emerg1$SowingDate <- ymd(df_emerg1$SowingDate )
df_emerg1$Block <- as.factor(df_emerg1$Block)
df_emerg1$Plot <- as.factor(df_emerg1$Plot)
str(df_emerg1)
head(df_emerg1)



#clean not needed columns 
df_emerg1<-df_emerg1%>%
  dplyr::select(-Sub1, -Sub2, -Sub3,-TT.y)
str(df_emerg1)
```


Need to subset only DAS with less than 100 % emergence (above 100% means seedlings had died and need the 50% of emergence based on final plant population!!! )
```{r}
df_emerg1 <- df_emerg1%>%
  subset(PercFinalEmerg>0 & PercFinalEmerg<101 )


```



Calculate 50 PercentEmergence  

```{r SummariseDf}



#  loop to calculate tt_50p_flow for each plot 

#sowd <- unique(df_50_Perc$SowingDate)
plots <- unique(df_emerg1$Plot)
 


#loop trough each combination of factor levels

for(p in 1:length(plots)) {
#  for(j in 1:length(var)){
 #   for(k in 1:length(sow)){
      
      # clean value holders
      DAS_50p_emerg <- 0
      tt_50p_emerg <- 0
      
     
      # filter for each combination

  df_sub <- df_emerg1 %>%
    # subset(Cultivar == as.character(cv[i]) &
    # Plot == as.character(var[j]) &
    #   Block == as.character(var[b]) &
    # SowTreat == as.character(sow[k])) %>%
    subset(Plot == plots[p]) %>%
    arrange(PercFinalEmerg)
    #arrange(DAS)
    
  df_sub
  head(df_sub)
  # create percentage with maximum value recorded 
  # to avoid crossing the 50% line twice
  
  df_sub$av_Perc_max <- 0 # create new col
  
  for(z in 1:nrow(df_sub)) {
    
    df_sub$av_Perc_max[z] <- max(df_sub$PercFinalEmerg[z],
                                 df_sub$PercFinalEmerg[z-1])
    
  }
  
  df_sub
  head(df_sub)
  tail(df_sub)

  # Interpolate 
  y_ref <- 50 # y value where we want to find x by interpolation
  
  # interpolate
  #find DAS at 50 Pecent Emergence 

  tryCatch(  
  DAS_50p_emerg <- approx(df_sub$PercFinalEmerg, 
  df_sub$DAS , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  DAS_50p_emerg <- NA
  }
)
  #find TT at 50 Pecent Emergence
  tryCatch(  
  tt_50p_emerg <- approx(df_sub$PercFinalEmerg, 
  df_sub$TT_to_emerg , xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  tt_50p_emerg <- NA
  }
)

  df_temp <- NULL
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             PercFinalEmerg = df_sub$PercFinalEmerg[1], 
                             SowTreat = df_sub$SowTreat[1],
                             Plot = df_sub$Plot[1],
                             Block = df_sub$Block[1],
                             DAS50E = DAS_50p_emerg,
                             TT50E = tt_50p_emerg)
  print(p)
  
  if(p == 1) {
    df_tt_50p_emerg <- df_temp
  } else {
   df_tt_50p_emerg <- rbind(df_tt_50p_emerg,df_temp) 
  }                     
  
#    } 
  } # end plot loop


```



```{r}

head(df_tt_50p_emerg)

write.table(df_tt_50p_emerg,"df_tt_50p_emerg.txt")
#write.table(df_tt_50p_emerg,"df_tt_50p_emerg_2.txt")

summary(df_tt_50p_emerg)


```



Graph results: include the sowing treatments again. 


```{r GraphResults}

sdLookup <- data.frame (
  SowTreat = c("S1","S2","S3","S4","S5","S6","S7","S8"),
  SowingDate = c("24/06/2015", 
                 "28/07/2015" ,
                 "15/09/2015" ,
                 "5/11/2015" ,
                 "15/12/2015" ,
                 "17/02/2016" ,
                 "15/03/2016",
                 "4/05/2016"))

sdLookup$SowingDate <- dmy(sdLookup$SowingDate)

df_tt_50p_emerg <- merge(df_tt_50p_emerg, sdLookup, by="SowTreat")
summary(df_tt_50p_emerg)


```





Data visualisation and means check.With standard deviation 
```{r, fig.height=5, fig.width=10}

#Here just to check means 
# mean <-df_tt_50p_emerg %>%
#   group_by(SowTreat, SowingDate, Cultivar,DAS50E) %>%
#   summarise_each(funs(mean,sd))
# summary (mean)


df_tt_50p_emerg %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(DAS50E) %>%
  summarise_each(funs(mean,sd)) %>%
  
  # if needed to exclude cultivars for analysis use filter 
  # filter( Cultivar != "Woogenellup" &
  #        Cultivar != "Monti" &
  #        Cultivar != "Antas" &
  #        Cultivar != "Denmark" &
  #        Cultivar != "Leura") %>%
         
  
ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="Days to 50% emergence ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 12))+
  theme(axis.text.y = element_text(angle = 0, hjust = 1, size = 12))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()
 


```

Do new graph with the standard error 

```{r, fig.height=8, fig.width=12}

#Work dataframe with DAS50
df_Graph1 <-df_tt_50p_emerg %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(DAS50E) %>%
  summarise_each(funs(mean,sd)) %>%
  mutate(SE=sd/1.73)

g1<-df_Graph1%>%
ggplot(aes(x=SowingDate, y=mean)) +
  geom_point(aes(shape=Cultivar),size=4) +
  #geom_line() +
  labs(x="Sowing Date") +
  ylab(expression(Time~to~Emergennce~"("*"days"*")"))+
  geom_errorbar(aes(ymin=mean-SE/2,
  ymax=mean+SE/2))+
  theme_bw()+
  scale_x_date(date_breaks = "1 month",
               labels=date_format("%b-%Y"),
               limits = as.Date(c("2015-06-01", "2016-06-01")))+
  ylim(0,45)+
  #theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 14))+
  theme(axis.text.x = element_blank())+
  theme(axis.title.x = element_blank())+
  theme(axis.text.y = element_text(angle = 0, hjust = 1, size = 14))+
  theme(axis.title.y = element_text(angle = 90, hjust = 0.5, size = 14))

#work dataframe for TT50

df_Graph2 <-df_tt_50p_emerg %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(TT50E) %>%
  summarise_each(funs(mean,sd)) %>%
  mutate(SE=sd/1.73)

g2<-df_Graph2%>%
ggplot(aes(x=SowingDate, y=mean)) +
  geom_point(aes(shape=Cultivar),size=4) +
  #geom_line() +
  labs(x="Sowing Date") +
  ylab(expression(Thermal~time ~"("^"o"*"Cd)"))+
  geom_errorbar(aes(ymin=mean-SE/2,
  ymax=mean+SE/2))+
  theme_bw()+
  scale_x_date(date_breaks = "1 month",
               labels=date_format("%b-%Y"),
               limits = as.Date(c("2015-06-01", "2016-06-01")))+
  ylim(0,250)+
  
  theme(axis.text.x = element_text(angle = 45, hjust = 1, size = 14))+
  theme(axis.text.y = element_text(angle = 0, hjust = 1, size = 14))+
  theme(axis.title.y = element_text(angle = 90, hjust = 0.5, size = 14))

#align the vertical axes using maxWidths
gA <- ggplotGrob(g1)
gB <- ggplotGrob(g2)
 maxWidth=grid::unit.pmax(gA$widths[2:5],gB$widths[2:5])
 gA$widths[2:5] <-as.list(maxWidth)
 gB$widths[2:5] <-as.list(maxWidth)
 g <- grid.arrange(gA,gB, ncol=1)
 
 #save graph - to save a grid need to atribute to "g" 
 
 ggsave(file="DAS50E&TTAS50E.png", width=12, height=6, dpi=400,g)
 
```





Calculate the rate of emergence (1/Days to 50% emergence)

```{r}

#try 1/DAS50% = Rate

df_RateEmerg <- df_tt_50p_emerg %>%
  mutate(Rate=1/DAS50E)

  summary(df_RateEmerg)
  
  
  
```

graph and save a dataframe as txt
```{r}
df_RateEmerg %>%
  group_by(SowingDate, Cultivar) %>%
  #filter(Cultivar=="Woogenellup")%>%
 # filter (SowTreat== "S2"| SowTreat== "S2"|SowTreat== "S2"|)
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 50% emergence ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()
  
  write.table(df_RateEmerg, "df_RateEmerg.txt")

  
```

Graph here only for "Woogenellup (draft paper") . Here alread with Stanard error (1.73)

```{r}

df_RateEmerg %>%
  group_by(SowingDate, Cultivar) %>%
  filter(Cultivar=="Antas")%>%
  filter (SowTreat== "S2"| SowTreat== "S3"|SowTreat== "S4"|SowTreat== "S6")%>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 50% emergence ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-(sd/1.73)/2,
  ymax=mean+(sd/1.73)/2))+
  theme_bw()









```




graph with rate and thermal time to 50% 

```{r, fig.height=5, fig.width=10}


df_tt_50p_emerg %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(TT50E) %>%
  summarise_each(funs(mean,sd)) %>%
  
  # if needed to exclude cultivars for analysis use filter 
  # filter( Cultivar != "Woogenellup" &
  #        Cultivar != "Monti" &
  #        Cultivar != "Antas" &
  #        Cultivar != "Denmark" &
  #        Cultivar != "Leura") %>%
         
 
  
ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  #geom_line() +
  
  labs(x="Sowing Date",y="Thermal time to 50% emergence ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()
 

```



```{r}
#empty

```

End of this script 

