---
title: "Emergence seedlings I2 graphs with Mean Soil Temp"
author: "CT"
date: "10.01 2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

This script does this:
-get dataframe produced in Calc4EmergSoilT (df3; df_MeanSoilTemp50Emerg.txt)
-graph y=Days to 50% emergence ; x= mean soil Temp
-graph y= 1/days to 50% emergence ; x= mean soil Temp
-produces the linear equations emergence as a function of temperature 



```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
library (gridExtra)
```

Read file and correct formats 
```{r loadFile}
# Get dataframe from previous script (written table )
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergenceIv2")
getwd()

#create file
#df_G <- read.table("df_MeanSoilTemp50Emerg.txt",header=TRUE)
df_G <- read.table("df_MeanSoilTemp50Emerg_2.txt",header=TRUE)

df_G$Date50E <- ymd(df_G$Date50E)
df_G$SowingDate <- ymd(df_G$SowingDate )
df_G$Cultivar <- as.factor(df_G$Cultivar)
df_G$Plot <- as.factor(df_G$Plot)

#check data 
summary(df_G)

# this is to "clean previous dfs : df_emerg4 <- NULL

```

calculate and include column 1/DAS50E 


```{r}

df_H <- df_G %>%
  mutate(InvDAS50E= 1/ DAS50E)

```

Graph DAS50 Emergence and rate against meanTemp at emergence 

```{r, fig.height=5, fig.width=12 echo = FALSE}



fontSize <- 12.0

 

  g1 <- df_H %>%
 # filter(Cultivar=="Antas"|Cultivar=="Monti") %>%
  ggplot(aes(x=meanTemp_Em, y=DAS50E, colour=SowTreat))  +
  geom_point(alpha=0.8, size=3) +
  #geom_smooth()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Soil~temperature~~"("^"o"*"C)")) +  
  ylab("Days to 50% emergence  (days)") +
    facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=11))+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,60))

# 1/DAS50E
  g2 <- df_H %>%
   # filter(Cultivar=="Antas"|Cultivar=="Monti") %>%
  ggplot(aes(x=meanTemp_Em, y=InvDAS50E, colour=SowTreat))  +
  geom_point(alpha=0.8, size=3) +
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Soil~temperature~~"("^"o"*"C)")) + 
  ylab(" Rate (1/ Days) to 50% emergence") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=11))+
 scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.25))
  grid.arrange(g1, g2)
# 

# 

```


calculate mean values for each cultivar and sow Treat

```{r}
df_mean<-df_H%>%
  mutate(SowMonth= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),
                           labels=c("June", "July", "September", "November", "December", "February","March", "May")))%>%
  group_by(Cultivar,SowTreat,SowMonth)%>%
   summarise_all(funs(mean))
```


```{r, fig.height=6, fig.width=12}

fontSize <- 16.0



#DAS50E
#
  g3 <- df_mean %>%
  #filter(Cultivar=="Monti"| Cultivar=="Antas")%>%
  #filter (SowTreat== "S2"| SowTreat== "S3"|SowTreat== "S4"|SowTreat== "S6")%>%
    #group_by(Cultivar,SowTreat)%>%
    #summarise_all(funs(mean))
  #ggplot(aes(x=meanTemp_Em, y=DAS50E, colour=SowTreat))  +
     ggplot(aes(x=meanTemp_Em, y=DAS50E))  +
    #geom_point(aes(shape= SowTreat), size=4)+
    geom_point(aes(shape= SowMonth), size=4)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
 # geom_point(alpha=0.8) +
  #geom_smooth()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Soil~temperature~~"("^"o"*"C)")) +  
  ylab("Days to 50% emergence  (days)") +
    facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=11))+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,40))

# 1/DAS50E
  g4 <- df_mean %>%
   #filter(Cultivar=="Monti"| Cultivar=="Antas")%>%
  #filter (SowTreat== "S2"| SowTreat== "S3"|SowTreat== "S4"|SowTreat== "S6")%>% 
    #ggplot(aes(x=meanTemp_Em, y=InvDAS50E, colour=SowTreat))  +
  ggplot(aes(x=meanTemp_Em, y=InvDAS50E))  +
    geom_point(aes(shape= SowMonth), size=4)+
    #geom_point(aes(shape= SowTreat), size=4)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8))+
  #geom_point(alpha=0.8) +
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab(expression(Soil~temperature~~"("^"o"*"C)")) + 
  ylab(" Rate (1/ Days) to 50% emergence") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=11))+
 scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.30))
  
  g <-grid.arrange(g3, g4)
  
  #ggsave(file="plot_DAS50E_Rate_Iv.png", width=12, height=6, dpi=400,g)

```
 

Graph only time 50% emergence and mean soil temp 

```{r, fig.height=15, fig.width=15}


df_seed1<-df_H%>%
  mutate(SowMonth= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),
                           labels=c("June", "July", "September", "November", "December", "February","March", "May")))%>%
  group_by(Cultivar,SowTreat,SowMonth)%>%
  dplyr::select(DAS50E, meanTemp_Em)%>%
   summarise_all(funs(mean,sd))

str(df_seed1)

##then rename for graphs


#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.1 # extra position for single error bar
x_max<-max(df_seed1$meanTemp_Em_mean)
y_max<-max(df_seed1$DAS50E_mean)

# find largest standard error
sd_df2 <- df_seed1 %>% 
  #group_by(Temp) %>%
  group_by(Cultivar) %>%
  dplyr::select(DAS50E_sd)%>%
  summarise_all(max)%>%
#summarise(max_sd = max(sd)) %>% 
  ungroup() %>%
  rowwise() %>%
  #rename variables
  mutate(meanTemp_Em_mean = x_max*extraPos, DAS50E_mean = y_max*extraPos,max_sd=DAS50E_sd )

summary(sd_df2)

#divide sd/2 as number of replicates were 4 

df_seed1%>%
ggplot(aes(x=meanTemp_Em_mean, y=DAS50E_mean)) + 
  geom_point(aes(shape= SowTreat), size=8)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11))+
  geom_line(aes(width=SowTreat))+
 
  geom_errorbar(data=sd_df2, aes(ymin=DAS50E_mean-max_sd/2,
                    ymax=DAS50E_mean+max_sd/2), size=1.5)+
  #facet_wrap(~Cultivar,ncol=2, scales = "free")+
   facet_wrap(~Cultivar,ncol=2)+
  theme_bw()+
  #scale_x_continuous(breaks = c(5,10,15,20,30))+
  #ylim(0, 145)+
  scale_y_continuous(breaks = c(0,10,20,30,40,50))+
  xlim(0, 24)+
  ylab("Time to 50% emergence  (days)") + 
  xlab(expression(Soil~temperature~~"("^"o"*"C)")) +
  #theme(axis.title.x = element_text( size=24)) + scale_x_continuous(breaks = c(0:6))+
  #theme(text=element_text(size=22 ))+
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5,size = 22,face="bold"))+
  theme(axis.title.y=element_text(angle = 90, hjust = 0.5,size = 22,face="bold"))+
  #theme(title=element_text(size=22, face="bold"))+
  #theme(title=element_text(size=22,  face="bold"))+
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black"  , size = 2.0), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     
     axis.line = element_line(colour = "black", size= 1))+
   ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))+

#make Cultivars  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
  
  #label sizes 
theme(text = element_text(size = 26))
  
  #geom_abline(intercept = 50, slope = 0)


ggsave("plot_5_DAS50Emerg_Vs_SoilTemp.tiff", width=14, height=16, dpi=600)



```

Graph only  emergence rate (1/das) and mean soil temp 

```{r, fig.height=6, fig.width=8}


df_seed2<-df_H%>%
  mutate(SowMonth= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),
                           labels=c("June", "July", "September", "November", "December", "February","March", "May")))%>%
  group_by(Cultivar,SowTreat,SowMonth)%>%
  dplyr::select(InvDAS50E, meanTemp_Em)%>%
   summarise_all(funs(mean,sd))

#str(df_seed2)

##then rename for graphs


#extraPos<- 1.10 # extra position for single error bar
extraPos<- 1.1 # extra position for single error bar
x_max<-max(df_seed2$meanTemp_Em_mean)
y_max<-max(df_seed2$InvDAS50E_mean)

# find largest standard error
sd_df2 <- df_seed2 %>% 
  #group_by(Temp) %>%
  #group_by(Cultivar) %>%
  dplyr::select(InvDAS50E_sd,InvDAS50E_mean)%>%
  #summarise_all(max)%>%
summarise(max_sd = max(InvDAS50E_sd), InvDAS50E_mean=mean(InvDAS50E_mean)) %>%

  #ungroup()
  #rowwise() %>%
  #rename variables
  mutate(meanTemp_Em_mean = x_max*extraPos, InvDAS50E_mean = y_max*extraPos,max_sd=max_sd )


summary(sd_df2)

#######create one single error bar (no panel max SE= (0.10/2) = 0.05



#divide sd/2 as number of replicates were 4 

df_seed2%>%
  
  #filter(SowTreat!="S1")%>%
ggplot(aes(x=meanTemp_Em_mean, y=InvDAS50E_mean)) + 
  geom_point(aes(shape= SowTreat,colour=Cultivar), size=8)+
  scale_shape_manual(values = c(0,1,2,3,4,5,6,7,8,9,10,11))+
  #geom_line(aes(width=SowTreat))+
 #geom_smooth(method = lm, fullrange=TRUE)+
  #geom_smooth(method = lm, SE=FALSE, alpha=0.2, linetype= 2)+
  geom_errorbar(data=sd_df2, aes(ymin=InvDAS50E_mean-max_sd/2,
                    ymax=InvDAS50E_mean+max_sd/2), size=1.5)+

  #facet_wrap(~Cultivar,ncol=2, scales = "free")+
   #facet_wrap(~Cultivar,ncol=2)+
  theme_bw()+
  scale_y_continuous(breaks = c(0,0.05,0.10,0.15,0.20,0.25,0.30))+
 # xlim(0, 24)+
 # ylim(0,0.3)+
  geom_abline(slope=0.01526,intercept = 0)+
  geom_abline(slope=0.0086,intercept = 0, linetype=2)+
  ylab("Emergence rate  (1/days)") + 
  xlab(expression(Soil~temperature~~"("^"o"*"C)")) +
  #theme(axis.title.x = element_text( size=24)) + scale_x_continuous(breaks = c(0:6))+
  #theme(text=element_text(size=22 ))+
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5,size = 22))+
  theme(axis.title.y=element_text(angle = 90, hjust = 0.5,size = 22))+
  #theme(title=element_text(size=22, face="bold"))+
  #theme(title=element_text(size=22,  face="bold"))+
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black"  , size = 2.0), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     
     axis.line = element_line(colour = "black", size= 1))+
   ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))+

#make Cultivars  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
  
  #label sizes 
theme(text = element_text(size = 22)) +
  ylim(0,NA)+
  xlim(0,NA)
  
  #geom_abline(intercept = 50, slope = 0)


ggsave("plot_5_RateEmerg_Vs_SoilTemp.tiff", width=12, height=12, dpi=600)



```


Then get the equations from the whole temperature range   

```{r, fig.height=7,fig.width=12}
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}


df <- df_H %>%
  dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E) %>%
  group_by(SowTreat,Cultivar) %>%
  summarise_all(funs(mean)) %>%
  mutate(y=InvDAS50E,x=meanTemp_Em) %>%
  dplyr::select(-meanTemp_Em, -InvDAS50E)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_point()+
  theme_bw()+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.45))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE) + 
  facet_grid(Cultivar~.,scales="free")
  
p1
```




Try to leave S1 out of that and see if it improves  

```{r fig.height=6, fig.width=12, echo = FALSE, warning=FALSE}

#graph S2-S8 



fontSize <- 12.0

#DAS50E
#g1 <- df_H %>%
  #filter(year %in% 1960:2000) %>%
  #group_by(day) %>%
 # summarise_each(funs(mean)) %>%
  g1 <- df_H %>%
    filter(SowTreat!="S1")%>%
  ggplot(aes(x=meanTemp_Em, y=DAS50E,shape=Cultivar))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  #geom_smooth()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
 xlab("Mean Soil Temp (oC)") + 
  ylab("Days to 50% emergence  (days)") +
    facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=10))+
  geom_smooth(method = "lm") # +
  # scale_x_continuous(limits = c(0,25))+
  # scale_y_continuous(limits = c(0,40))

# 1/DAS50E
  g2 <- df_H %>%
    filter(SowTreat!="S1")%>%
  ggplot(aes(x=meanTemp_Em, y=InvDAS50E, shape=Cultivar))  +
  geom_point(colour= "red", alpha=0.2) +
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  geom_smooth(method = "lm")+
  theme_bw() +
  xlab("Mean Soil Temp (oC)") + 
  ylab(" Rate (1/ Days) to 50% emergence") +
  facet_grid(.~Cultivar, scales="free")+
 theme(text = element_text(size=10)) #+
 # scale_x_continuous(limits = c(0,17))+
 #  scale_y_continuous(limits = c(0,0.25))
  grid.arrange(g1, g2)
# 

  
  grid.arrange(g1, g2)

```

Then get the equations for the interval between 5 - 17 degrees.
This is the portion of the data which is ascending.

```{r}

# 1/DAS50E (going up)
  require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}


df <- df_H %>%
  dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E) %>%
 # filter(SowTreat!="S1", SowTreat!="S8")%>%
  group_by(SowTreat,Cultivar) %>%
  summarise_all(funs(mean)) %>%
  mutate(y=InvDAS50E,x=meanTemp_Em) %>%
  dplyr::select(-meanTemp_Em, -InvDAS50E)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_point(aes(shape=SowTreat))+
  theme_bw()+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.45))

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE) + 
  facet_grid(Cultivar~.,scales="free")
  
p1




```


