---
title: "Emergence seedlings I2 graphs with Mean Soil Temp between 5-5"
author: "CT"
date: "01.08.2017"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

This script does this:
-get txt file produced in Calc5EmergSoilT (a sub set of  df_MeanSoilTemp50Emerg.txt)
-graph y=Days to 50% emergence ; x= mean soil Temp between 5 -18 
-graph y= 1/days to 50% emergence ; x= mean soil Temp subset 5-18 
-eliminated S1 and S8 bad establishment 
-best R2 from 5 to 15 


```{r loadLibraries, warning=FALSE}
library(tidyr)
library(dplyr)
library(ggplot2)
library(agricolae)
library(knitr)
library(lubridate)
library(mosaic)
library(lattice)
library (gridExtra)
```

Read file and adjust formats 
```{r loadFile}
# Get dataframe from previous script (written table )
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\EmergenceIv2")
getwd()

#create file. This file is created in Excel from df_MeanSoilTemp.txt
df_G <- read.table("SubsetS2_S7.txt",header=TRUE)


df_G$Date50E <- ymd(df_G$Date50E)
df_G$SowingDate <- ymd(df_G$SowingDate )
df_G$Cultivar <- as.factor(df_G$Cultivar)
df_G$Plot <- as.factor(df_G$Plot)

summary(df_G)

# this is to "clean previous dfs : df_emerg4 <- NULL

```

Include a column with 1/DAS50E 


```{r}

df_H <- df_G %>%
  mutate(InvDAS50E= 1/ DAS50E)

```

Graph and check data 
```{r, fig.height=5, fig.width=10, echo = FALSE}



fontSize <- 12.0

#DAS50E
#g1 <- df_H %>%
  #filter(year %in% 1960:2000) %>%
  #group_by(day) %>%
 # summarise_each(funs(mean)) %>%
  g1 <- df_H %>%
  ggplot(aes(x=meanTemp_Em, y=DAS50E,shape=Cultivar))  +
  geom_point(colour= "darkblue", alpha=0.2) +
  geom_smooth()+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
 xlab("Mean Soil Temp (oC)") + 
  ylab("Days to 50% emergence  (days)") +
    facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=10))+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,30))

# 1/DAS50E
  g2 <- df_H %>%
  ggplot(aes(x=meanTemp_Em, y=InvDAS50E, shape=Cultivar))  +
  geom_point(colour= "red", alpha=0.9) +
  #geom_smooth(colour="red")+
  #stat_smooth(level = 0.9, size = 1, colour="white") + 
  theme_bw() +
  xlab("Mean Soil Temp (oC)") + 
  ylab(" Rate (1/ Days) to 50% emergence") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=10))+
 scale_x_continuous(limits = c(0,25))+
  scale_y_continuous(limits = c(0,0.25))
  grid.arrange(g1, g2)
# 

# 

```


here get the equations from all temperatures  

```{r}

df_All<-df_H%>%
  group_by(Cultivar,SowTreat)%>%
  dplyr::select(InvDAS50E, meanTemp_Em)%>%
   summarise_all(funs(mean))

  #dplyr::select(-InvDAS50E,-meanTemp_Em)
  
#create a vector that holds names of all possible cultivars
#cv.unique <- unique(df_All$Cultivar)
cv.unique <- unique(df_All$Cultivar)

summary(cv.unique )


for (i in 1:length(cv.unique)) {
  
 #print(i)
 print(paste0(cv.unique[i],"--------------------------------"))
  
  #then make it subset 
  
  df_subset <- df_All %>%
    subset(Cultivar==cv.unique[i])
  
  #add the function or calculation required 
  
    summary(lm(InvDAS50E ~ meanTemp_Em, df_subset))
  #print
    
    print(summary(lm(InvDAS50E ~ meanTemp_Em, df_subset)))


  } 





```









```{r, fig.height=7,fig.width=12}
require(ggplot2)
require(plyr)
require(dplyr)

lm_eqn = function(df){
  m = lm(y ~ x, df);
  eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2, 
                   list(a = format(coef(m)[1], digits = 2), 
                        b = format(coef(m)[2], digits = 2), 
                        r2 = format(summary(m)$r.squared, digits = 3)))
  as.character(as.expression(eq));                 
}


df <- df_H %>%
  dplyr::select(SowTreat,Cultivar, Plot, meanTemp_Em, InvDAS50E) %>%
  group_by(SowTreat,Cultivar) %>%
  summarise_each(funs(mean)) %>%
  mutate(y=InvDAS50E,x=meanTemp_Em) %>%
  dplyr::select(-meanTemp_Em, -InvDAS50E)

eq <- ddply(df,.(Cultivar),lm_eqn)

yx<-quantile(df$y,0.75)
xn<- quantile(df$x,0.25)

p <- ggplot(data = df, aes(x = x, y = y)) +
  geom_smooth(method = "lm", se=FALSE, color="black", formula = y ~ x) +
  geom_point()+
  theme_bw()+
  scale_x_continuous(limits = c(0,25))+
  scale_y_continuous (limits = c(0, 0.3))+
  xlab("Mean Soil Temp (oC)") + 
  ylab(" Rate (1/ Days) to 50% emergence") 

p1 <- p + geom_text(data=eq,aes(x = xn, y = yx,label=V1), parse = TRUE, inherit.aes=FALSE) + 
  facet_grid(Cultivar~.,scales="free")
  
p1
```

End of this script. 
continue in Calc7 (subset data)