---
title: "Emergence seedlings Iversen 2"
author: "CT"
date: "31.12. 2015"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

Purpose:

-Analysis of plant population 
-calculate the percentage of emergence 



```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library(mosaic)
library(lattice)
```
Read raw data 

```{r loadFile}
setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\EmergenceIv2")
getwd()

#create file
df_emerg <- read.table("PlantPop.txt",header=TRUE)


```

Define formats and calculate Plant Population

```{r}
# define factors for the ones that "look like" values
df_emerg$Plot <- as.factor(df_emerg$Plot)
df_emerg$Block <- as.factor(df_emerg$Block)

# calculate plant population
 df_emerg <- df_emerg %>%
  mutate(SowingDate = dmy(SowingDate), 
         ReadingDate = dmy(ReadingDate),
         PlantPop = (Sub1+Sub2+Sub3)/3/0.01)

str(df_emerg)
head(df_emerg)
tail(df_emerg)

#check data
df_emerg %>% filter(Plot ==2) %>% summary()
```
Data visualisation and check of plant population counts (seedlings per m2).

```{r, fig.height= 6, fig.width= 10}


#Graph         
  df_emerg %>%  group_by(Cultivar, SowTreat, DAS) %>%
  #filter(SowTreat =="S2"& SowTreat =="S4")%>%
  #dplyr::select(-SowingDate, - ReadingDate) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=PlantPop)) + 
  geom_point(aes(colour=Cultivar,shape=Cultivar)) +
  geom_line(aes(colour=Cultivar)) +
  #add error bar
  geom_errorbar(aes(x=20,ymin=200,ymax=300,width=0.2))+
  facet_wrap(~SowTreat,ncol=4, scales = "free")+
  theme_bw()+
  ylim(0, 2200)+
  labs(y="Number of seedlings per m2",x="Days after sowing") 
  #+geom_abline(intercept = 50, slope = 0)



```


Calculation of the percentage of emergence based on the maximum plant population in each plot.



```{r CalculatePercentageEmergence }

df_emerg_perc <- df_emerg %>%
group_by(Plot) %>%
mutate(PercEmerg = round(PlantPop/max(PlantPop)*100,digits=2))

# Check
summary(df_emerg_perc)
tail(df_emerg_perc)
df_emerg_perc %>%  filter(Plot=="2")


```

Graph the percentage of emergence 

```{r, fig.width= 10, fig.height=6}
#Graph         
  df_emerg_perc %>%  group_by(Cultivar, SowTreat, DAS) %>%
  #filter(SowTreat =="S3", Cultivar == "Leura") %>%
  dplyr::select(-SowingDate, - ReadingDate) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=PercEmerg)) + 
  geom_point(aes(colour=Cultivar,shape=Cultivar)) +
  geom_line(aes(colour=Cultivar)) +
    theme_bw()+
  #add error bar
  geom_errorbar(aes(x=20,ymin=20,ymax=30,width=0.2))+
  facet_wrap (~SowTreat,ncol=4, scales = "free")+
  labs(y="Percentage  of Seedling emergence",x="Days after sowing") +
  geom_abline(intercept = 50, slope = 0)
```

Create a column that has the value of maximum final plant population. 


```{r }

#compare max plant population among Sowing dates and cultivars

df_emerg_perc3 <- df_emerg %>%
group_by(Plot) %>%
mutate(FinalPop= round(max(PlantPop)*1,digits=2))

head(df_emerg_perc3)
summary (df_emerg_perc3)

write.table(df_emerg_perc3, "df_emerg_perc3.txt")
```


Transformation option for datasets 

```{r}

#normality test
shapiro.test(df_emerg_perc3$FinalPop)


#data transformation
file <- df_emerg_perc3

# file$transf_sqr <- sqrt(df_emerg_perc3$FinalPop)
# file$transf_log <- log(df_emerg_perc3$FinalPop)
# file$transf_log1 <- log(df_emerg_perc3$FinalPop+1)
file$transf_no <- 1*(df_emerg_perc3$FinalPop)
file$transf_logit <- logit(df_emerg_perc3$FinalPop/10000)
head(file)



file %>%
  tidyr::gather("transformation","value",colsSelec) %>%
  ggplot(aes(value)) + 
  geom_histogram() +
 # facet_wrap(SowTreat~transformation, scales="free", ncol=4) +
  facet_grid(transformation~SowTreat, scales="free")

head(file)


#QQplot
var<-file$transf_no
qqnorm(var)
qqline(var, col = 2)
qqplot(var, rt(3000))

#-------------------------------------------------
# ANOVA overview 
# file.subset <- file %>% subset(SowTreat == "S2" & round==1)
file.subset <- file 

head(file.subset, 50)
summary(file.subset)
my.anova <- aov(transf_no ~ Cultivar*SowTreat + Block, 
                data = file.subset)

summary(my.anova)

TukeyHSD(my.anova)

#Means separation 
(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none") ) 
(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none") )
(LSD.test(my.anova, c("SowTreat","Cultivar"), alpha= 0.05, p.adj="none"))

```
Shapiro Test

```{r}
shapiro.test(file$transf_logit)

x <- c("transf_logit", "transf_no")
colsSelec <- match(x,colnames(file))
```



Combine Soil Temperature data.
Create Graph Percent emergence with Mean Soil Temperature 
```{r}

setwd("C:\\Users\\EdCarmen\\Documents\\CarmenProjects2016\\GitSubclover\\EmergenceIv2")
getwd()


df_fileSo <- read.table("SoilTemp.txt", header=TRUE)

head(df_fileSo)

df_fileSo <- df_fileSo %>%
mutate(ReadingDate = dmy(Date)) %>%
dplyr:: select(-Date)
str(df_fileSo)

head(df_emerg_perc)
head(df_fileSo)

 


```

Merge the two dataframes 

```{r}

# Merge SoilTemp and Emergence  at measurement date
df_emerg_perc_SoilT <- NULL
df_emerg_perc_SoilT <- merge(df_emerg_perc,df_fileSo,by="ReadingDate")
head(df_emerg_perc_SoilT)
```

Include the Thermal time accumulation using the soil temperature 
ThermalSum soil. txt is generated in another script. 

```{r SoilTemp}
# include soil  temperature before 30 June_lysimeter  

df_SoilTT <- read.table("ThermalSumSoil.txt",header=TRUE)
head(df_SoilTT)

# convert to date format
df_SoilTT <- as.data.frame(df_SoilTT) %>%
 mutate(Date=ymd(Date))


# check
head(df_SoilTT)
summary (df_SoilTT)

```

Merge the dataframes 

```{r}

# Merge Tt at measurement date
df_emerg_perc_TT <- NULL
df_emerg_perc_TT <- merge(df_emerg_perc,df_SoilTT,by.x="ReadingDate",by.y="Date")
df_emerg_perc_TT <- merge(df_emerg_perc_TT,df_SoilTT,by.x="SowingDate",by.y="Date")
df_emerg_perc_TT$TT_to_emerg <- df_emerg_perc_TT$TT.x-df_emerg_perc_TT$TT.y
summary(df_emerg_perc_TT)

#save as table 
write.table(df_emerg_perc_TT, "df_emerg_perc_soilTT.txt")
head(df_emerg_perc_TT )


  


```
GRaph the thermal time from sowing and percentage of emergence

```{r, fig.width=10, fig.height=6}
# graph emerg x tt
df_emerg_perc_TT %>%
  group_by(Cultivar, SowTreat, TT_to_emerg) %>%
  #dplyr::select(-SowingDate, - ReadingDate) %>%
#  filter(Cultivar =="Narrikup") %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=TT_to_emerg, y=PercEmerg,colour=Cultivar)) + 
  geom_point() +
  geom_line() +
  #facet_grid (Cultivar~., scales = "free")+
  geom_abline(intercept = 50, slope = 0) +
  facet_wrap (~SowTreat,ncol=4, scales = "free")+
  theme_bw() +
  theme(text = element_text(size = 10))+
  xlab("Thermal-time from sowing") +
  ylab("Percentage emergence")
```

End of this script. 
More analysis in EmergenceI2_Calc2.Rmd file. 