---
title: "Flowering 6CV"
author: "CT"
date: "Thursday, December 31, 2015"
output: html_document
---

```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
```

This script reads the dataframe ( df_tt_50p_flow) created in previous script 3 and makes graphs 

```{r loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\FlowIv2")
getwd()

#create file ; this file was generated in the previous script FlowerProject2

df_tt_50p_flow <- read.table("df_tt_50p_flow.txt",header=TRUE)

#head(df_bud_flow_bur_simple)
# change formats
df_tt_50p_flow <- df_tt_50p_flow %>%
mutate (SowingD=ymd(SowingD))

summary(df_tt_50p_flow)
#tail(df_bud_flow_bur_simple)
```



Use this chunk to generate TT50 for bud, flowering(fertilization) and seed mature

```{r GraphResults, fig.width=12}

#Here need to create Variable2 to make a graph with the DAS50F and TT50F 

  df_tt_50p_flow %>%
  #use filter to check single variables -Bud, Flowering and Bur
  filter( Variable== "Bud") %>%
  mutate(TT50F=ifelse(TT50F==0,NA,as.numeric(TT50F)))%>%
  mutate(DAS50F=ifelse(DAS50F==0,NA,as.numeric(DAS50F)))%>%
  tidyr::gather("Variable2","Value",DAS50F:TT50F) %>%
  mutate(Variable2=as.factor(Variable2))%>%

  ggplot(aes(x=SowingD,y=Value,colour=Cultivar, shape=Cultivar))+
  geom_point()+
  geom_line()+
  facet_grid(Variable2~Block, scales="free")+
  theme_bw()+
  #theme(axis.text.x = element_text(angle = 0, hjust = 1.0))+
  scale_x_date(date_breaks = "1 month",date_labels =  "%b")+
labs(x="Sowing Month")+
ylab(expression(Tt~"("^"o"*"Cd)"~~~~~~~~~~~~~~~~Days)) 
  


```


Build graph grid with DAS and TT as per vegetative stage 


```{r}






```



```{r}

dfN <-  df_tt_50p_flow %>%
  filter(Cultivar=="Narrikup")%>%
  filter(SowTreat=="S7")%>% 
  group_by(Variable)%>%
  summarise_all(funs(mean))




```




stopped here .. need to check why there are zeros !!! 


```{r}
df_tt_50p_flow %>%
  na.omit() %>%
    #filter( SowTreat != "S6" & SowTreat != "S7")%>%
  ggplot(aes(x=SowingD,y=TT50F,colour=Cultivar, shape=Cultivar))+
  geom_point()+
  facet_grid(Variable~Block)+
  theme_bw()+
  geom_line()

```
Now 

```{r,  warning =FALSE }

#CalculateDAys from bud to bur phases,
df_tt_50p_flow %>%
  dplyr::select(-TT50F)  %>%
  tidyr::spread(Variable,DAS50F) %>%
  mutate(DAS50Bud2Bur = Bur - Bud) %>%
ggplot(aes(x=SowingD, y=DAS50Bud2Bur)) + 
  geom_line(aes(colour=Cultivar)) +
  geom_point(aes(shape=Cultivar,colour=Cultivar))+
  #facet_grid(Cultivar~SowTreat, scales = "free") +
  facet_grid(.~Block, scales = "free") +
  geom_abline(intercept = 50, slope = 0) +
  #ylab("Percent of Flowering (%)") +
  #xlab("Thermal-time from sowing (oCd)")+
theme(axis.text.x = element_text(angle = 60, hjust = 1))

# save final DF
#write.table(df_tt_50p_flow, "df_tt_50p_flow.txt")






```

Graph thermal time required from bud to bur phase 

```{r}
df_tt_50p_flow %>%
  dplyr::select(-DAS50F)  %>%
  tidyr::spread(Variable,TT50F) %>%
  mutate(TT50Bud2Bur = Bur - Bud) %>%
  #graph it
ggplot(aes(x=SowingD, y=TT50Bud2Bur)) + 
  geom_line(aes(colour=Cultivar)) +
  geom_point(aes(shape=Cultivar,colour=Cultivar))+
  #facet_grid(Cultivar~SowTreat, scales = "free") +
  facet_grid(SowTreat~Cultivar, scales = "free") +
  geom_abline(intercept = 50, slope = 0) +
  #ylab("Percent of Flowering (%)") +
  #xlab("Thermal-time from sowing (oCd)")+
theme(axis.text.x = element_text(angle = 60, hjust = 1))
```



Now take the dataframe with 50 to flower and combine with photoperiod at sowing 

```{r}

df_Photo <- read.table("Photoperiod.txt",header=T)
df_Photo$Date <- dmy(df_Photo$Date)
df_Photo$SowingD <- df_Photo$Date
head(df_Photo)
head(df_tt_50p_flow)
df_tt_50p_flow$SowingD <- ymd(df_tt_50p_flow$SowingD)

#merge two data frames by ID
df_photoTT <- merge(df_tt_50p_flow,df_Photo, by="SowingD")
#head(df_photoTT)
summary(df_photoTT)




```

```{r}
#graph
df_photoTT %>%
  ggplot(aes(x=Pp, y=TT50F,color=factor(Cultivar)))  +
  geom_point()+
  geom_line() +
 # geom_smooth(aes(color=Cultivar))+
  facet_grid(Variable~Block, scales = "free")
```


next step: join early_open and petal categories to create " flower" 

Graph TTAS and Photoperiod 

```{r GraphPhoto}

# graph it
#head (df_bur_simple)
df_bud_flow_bur_simple %>%
  filter(Variable == "Bud" |
           Variable =="Flowering"| 
           Variable =="Bur")  %>%
  mutate(Variable = 
  factor(Variable,levels = c("Bud","Flowering",
                             "Bur"))) %>%
  group_by(TT50F,Cultivar,SowTreat,Variable,Pp_sow) %>%
  summarise_each(funs(mean)) %>%
  #select(Variable,Percent, Cultivar,TTAS,SowTreat,Pp_sow) %>%
  #filter(Cultivar == "Monti" | Cultivar == "Leura" ) %>%
  #filter(Variable == "Bud") %>%
  ggplot(aes(x=TT50F, y=Percent)) + 
  geom_line(aes(colour=Cultivar)) +
  geom_point(aes(shape=Cultivar,colour=Cultivar))+
  facet_grid(SowTreat~Variable, scales = "free") +
  geom_abline(intercept = 50, slope = 0)+
theme(axis.text.x = element_text(angle = 60, hjust = 1))

unique(df_bur_simple$Variable)


```


