---
title: "Include the mean Photoperiod ""
author: "CT"
date: "16.07.2017"
output:
  pdf_document: default
  html_document: default
  word_document: default
note: This is for DAE and TT from Emergence  to 9 Trifos. Include the mean Pp. 
---

```{r loadLibraries, echo=FALSE, include=FALSE}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library(knitr)
library (lubridate)
library (segmented)
library(hydroGOF)
library (markdown)
library (knitr)

```
 
AIM:

- Calculates the Mean Photoperiod 
- Plot TT to 50% plants  with 9 trifoliates  and plot against Mean Photoperiod

```{r   loadFile}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifosNineI2")

getwd()


```
 
```{r}
#get dataframe created similar to ReAnalysis4 which is Rea6 - use here the dataframe with the emergence info : DaysTT9TFromEmergence
#df_tt_flow <- read.table("df_tt_50p_flow.txt",header=TRUE) 

df_tt_9T <- read.table("df_Pptargets_TT9Trifos.txt",header=TRUE) 

# force date format
df_tt_9T$SowingDate <- ymd(df_tt_9T$SowingDate)
str(df_tt_9T)


```

Clean table with selected columns

```{r}
#summary(df_tt_9T)
df_Select <-df_tt_9T %>%
  ##Calculate Date when 9 Trifos occurred 
  mutate(DateTo9Trifo= SowingDate+DAS9T )%>%

  dplyr::select(SowingDate:Block,DAS9TFromEmerg,TT9TFromEmerg,Pp_sow,SowingD,DateTo9Trifo)

```


#Incorporate the mean Pp as well 


## Read the daily Pp and  adjust formats 

```{r}

#create file
df_P <- read.table("df_CumTTiv.txt",header=TRUE)

#
str(df_P)
df_P$Date<-as.Date(df_P$Date)
str(df_P)

#adjust formats
df_P<-df_P%>%
 #mutate(Date=dmy(Date))%>%
  select(Date,Pp)

str(df_P)

```
 
# Now need to calculate the mean Pp

#Till here all good ! 

Need to force a date for 50 % of plants with flowers  (round) to calculate the average Pp during this phase  

Save dataframe as txt file.


```{r}


# force formats of dates
df_Select$Date <- round(df_Select$DateTo9Trifo ,0)
df_P$Date <- round(df_P $Date,0)

#then repeat same procedure done for the soing date but use the dat for 1 Trifoliate
  df_mergePp <- merge(df_Select, df_P, by="Date") 
  
  str(df_mergePp)


```




Calculate the mean photoperiod for the 9 trifos  period

```{r}


  df_Pp509TmeanTPp <-df_mergePp %>%
    mutate(meanPp509T = (Pp+Pp_sow)/2) %>%
  ##calculate the rate to Flowering 1/DAS50FFromEmerg
  mutate(Rate9T= 1/DAS9TFromEmerg)

str(df_Pp509TmeanTPp)

```


then select columns of interest and clean data frame for just 144 plots dataset  

```{r}

b <-df_Pp509TmeanTPp %>%
  select(SowingDate:Block,TT9TFromEmerg,Rate9T,meanPp509T )%>%
  group_by(SowTreat,Plot,Cultivar,Block)%>%
  dplyr::select(meanPp509T, TT9TFromEmerg,Rate9T)%>%
  summarise_all(funs(mean))
  

```


Merge and calculate the two datasets 

- SumTT is value at sowing from 24 Jun 2015 
- TT50F_run (at flowering time) sets a limit for juvenile period - why? 

```{r}
# get TTsum at sowing
# estimates Tt with running TT sum from weather file

str( df_tt_9T)

df_Iv <- merge(df_tt_9T, df_weather,
               by.x=c("SowingDate"), 
               by.y=c("Date")) %>%
  ungroup()%>%
 # na.omit() %>%
  mutate(Pp_sow = Pp) %>%
  mutate(TtAtSowing_run = SumTTday) %>%
  dplyr::select(-SumTTday, -Pp) %>%
  mutate(TT50F_run = SummTT9Trifo + TtAtSowing_run) %>% # Tt running at flowering
  mutate(cv_block_index = as.factor(paste0(Cultivar,"_",Block)))  %>%
  mutate(SowingD=ymd(SowingDate))
 
str(df_Iv)

```


```{r}
summary(df_Iv)
```


##now here include the Pp function


Now assemble the Pp targets !!! 

##These chunks below need revision !!! why TT 50 run is added not sure if it is necessary now (26.06.2018) ? That is fixed now (01.07)


## calc

Find running sumTT for each sowing date at sowing

- only to have a small df for function below

- Obs: lebel tt as "_run" when using running sum of Tt across all sow dates

```{r}
sumTTatSow <- df_Iv %>%
  dplyr::select(SowTreat, TtAtSowing_run) %>%
  unique() %>%
  as.data.frame()

head(sumTTatSow)

```



Create function for retrieving photoperiod as a function of TT after sowing and Sowing date  treatment

- finds running TT at sowing
- adds target to that and finds pp at that TT moment
- tt_target is oCd after sowing when Pp is retrieved
- sowT is the sowing treatment (S1...)

```{r}

Pp_finder_func <- function(sowT, tt_target){
  
  #isolate the experiment and cultivar 
   sTT <- sumTTatSow %>% dplyr::filter(SowTreat == sowT) %>% dplyr::select(TtAtSowing_run)
   
   # sum target to sumTT at time of sowing for this spesific sd
   tt_target_adj <- tt_target + sTT 
   
  # lookup for Pp at new tt sum in weather file
  tryCatch(  
  Pp_target <- approx(df_weather$SumTTday, 
  df_weather$Pp, xout = tt_target_adj, rule = 1)$y,
  error = function(e) 
  {
  Pp_target <- NA
  }
)
 
  return(Pp_target)
  
}

```

## Test function

```{r}
st <- "S1"

#test
tt_target <- 0 
#TTsum estimated to reach 1st trifoliate 

#test if function is working : example : 
Pp_finder_func(st, tt_target)
```




# Find Pp at a given Tt sum after sowing

- Sums ftxed Tt to sowing Tt and see what Pp is there
- Plots this Pp against TT to flowering
- See if there is a stronger relationship beteen Pp and Tt

## Segment df by Cv and block 

##Parei aqui!!! review 

```{r}

# FIXME: This logic is corrupted as graph for target ==0 is not as above. Yes that is sure thing !!!! 

cv_block <- (unique(df_Iv$cv_block_index))

df_Iv_9Trif <- df_Iv 
  #dplyr::filter(Variable=="Flowering") %>%
  #subset(TT50F>0.5)
#na.omit()
  #Need to remove Denmark and Leura S5 ! no flowering 
  

# Loop 
df_pp_all <- data.frame()

for(p in 1:length(cv_block)) {
  
  CBI <- cv_block[p]
  
  # segment plot of interesst
  df_sub <- df_Iv_9Trif %>% 
    dplyr::filter(cv_block_index==cv_block[p])
  
  # loop through Tt chuncks after sowing
  # t is tt from sowing to the point where Pp is retrieved
    for(t in seq(from=0, to=min(df_sub$ TT50F ), by=100)){
    
 #   TT_target <- t # tt from sowing to the point where Pp is retrieved
  
    # Calculate Pp at this Tt sum after sowing
    df_sub_pp <- df_sub %>%
    rowwise() %>%
    mutate(TT_target = t)  %>%
    mutate(Pp_target=Pp_finder_func(SowTreat,TT_target))
    
    # Bind all results
    df_pp_all <- rbind(df_pp_all,df_sub_pp)
   
    }
}

summary(df_pp_all)

# FIXME: The extreme value of Tt target goes beyond current weather, need to expand it a bit

```


# Plot TT9TFromEmerg  vs Pp at sowing - data Visualisation


```{r, fig.width=12}

 dfGraph1 <- df_pp_all

dfGraph1 %>%
  na.omit() %>%
  dplyr::select(Cultivar, SowTreat, TT9TFromEmerg, Pp_sow) %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_all(funs(mean,sd)) %>%
  ggplot(aes(x=Pp_sow_mean,y=TT9TFromEmerg_mean, colour=Cultivar)) +
  theme_bw()+
  ylim(0,700)+
  geom_point()+
  geom_line()+
  facet_grid(Cultivar~.)



```



get all graphs in appendix then. 


## Check data with specific TT targets

```{r, fig.height= 10 , fig.width=15}

df_pp_all %>%
  #dplyr::select(Cultivar, SowTreat, TT9TFromEmerg, Pp_sow) %>%
  filter(TT_target==100) %>%
  ggplot(aes(x=Pp_target,y=TT9TFromEmerg,colour=factor(Cultivar),shape=factor(SowTreat),size=3 )) +
  geom_point() +
  geom_line() +
  facet_grid(Cultivar~.)

```


## Data Visualisation

```{r, fig.height=5, fig.width=15}


dfGraph2 <- dfGraph1 %>%
  na.omit() %>%
  dplyr::select(Cultivar, SowTreat, TT9TFromEmerg, Pp_sow) %>%
  group_by(Cultivar, SowTreat) %>%
  summarise_all(funs(mean,sd))


dfGraph2 %>%
mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May")))%>%
   #filter(Cultivar=="Monti"| Cultivar=="Antas")%>%
  #filter (SowTreat== "S3"| SowTreat== "S4"|SowTreat== "S5"|SowTreat== "S6")%>%
  #ggplot(aes(x=Pp_sow,y=TT50F,colour=factor(Cultivar)))   +
   #ggplot(aes(x=Pp_sow,y=TT9TFromEmerg))+
ggplot(aes(x=Pp_sow_mean,y=TT9TFromEmerg_mean)) +
  #  geom_point(aes(shape= SowTreat), size=4)+
  
  geom_text(aes(label=SowTreat),hjust=0, vjust=0,size=5) +
  theme_bw()+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
  ylab(expression(Mean~Thermal~time~to~Nine~Trifoliates~"("^"o"*"Cd)")) + 
  xlab(" Photoperiod at Sowing") +
  facet_grid(.~Cultivar, scales="free")+
  theme(text = element_text(size=18))+
 scale_x_continuous(limits = c(9,20))+
  scale_y_continuous(limits = c(0,900))
#theme(axis.title.y = element_text(face="bold", size=16))+
   

#ggsave("plot_PhotoperiodSowing.png", width=16, height=6, dpi=400)

```



##Now write a table to use to calculte the and Plot TT9 Trifo emergence against mean Photoperiod



```{r, fig.height= 5 , fig.width=10}

str(df_pp_all)

df_pp_all 
  
#Save as table 
write.table(df_pp_all, "df_Pptargets_TT9Trifos.txt")

```


End of this script 
