---
title: "Trifoliates Iversen "
author: "CT"
date: "31.08.2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Analysis of trifoliates expansion for Iversen with focus on first Trifoliate 
- Graph the main dataset 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```

#Bring TT Emergence
```{r}
df_TTEmerg <- read.table("DaysTT9TFromEmergence_v2.txt",header=TRUE) %>%
  dplyr::select(Plot, TT50E)

summary(df_TTEmerg)
```

# Bring Pp 
```{r}
df_Photo <- read.table("Photoperiod.txt",header=TRUE) %>%
  mutate(Date=dmy(Date))

summary(df_Photo)
```

```{r ReadThermalSumData}
# read raw data

#Temperatures from 24 June to 29 June included from Broadfield Niwa in excel Datalogger folder  Thermal Sum is created  in the the Thermal time project_TTCalc (R script_file)

#The df_CumTTiv.txt comes from the TTCalc script in the main Gitsubclover folder! Need to produce the file and add to the FlowIv2 folder for calculations. 

#the file df_CumTTiv2.txt contains the thermal sum hourly from Iversen. 
 
df_TTSum <- read.table("df_CumTTiv2.txt",header=TRUE)

# remove extra columns
df_TTSum <- df_TTSum %>%
dplyr::select(Date,SumTTday) %>%
mutate(Date = ymd(Date))
 
#check
summary(df_TTSum)

```

# Read main data
```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifosNineI2")
getwd()
#create file
#df_trifo <- read.table("TrifoCountall.txt",header=TRUE)%>%
df_trifo_raw <- read.table("TrifoCountall.txt",header=TRUE) 

summary(df_trifo_raw)

```


# create working df

Define formats and calculate the mean number of trifoliates considering the sub samples (S1-S10)

```{r}
df_trifo <- df_trifo_raw %>%
  mutate(SowingDate = dmy(SowingDate), 
         ReadingDate = dmy(ReadingDate),
         Trifo = (s1+s2+s3+s4+s5+s6+s7+s8+s9+s10)/10,
         Plot = as.factor(Plot),
         Block = as.factor(Block),
         Cultivar = as.factor(Cultivar),
         SowTreat = as.factor(SowTreat)
         ) %>%
  dplyr::select(-s1,-s2,-s3,-s4,-s5,-s6,-s6,-s7,-s8,-s9,-s10) %>%
  merge(df_TTSum, by.x = "ReadingDate", by.y = "Date") %>%
  dplyr::rename(SumTT_Reading = SumTTday) %>%
  merge(df_TTSum, by.x = "SowingDate", by.y = "Date") %>%
  dplyr::rename(SumTT_Sowing = SumTTday) %>%
  mutate(TTAS = SumTT_Reading-SumTT_Sowing) %>%
  merge(df_Photo, by.x="SowingDate", by.y = "Date") %>%
  dplyr::rename(Pp_Sowing = Pp)  %>%
  merge(df_TTEmerg, by = "Plot")  %>%
  mutate(TTAE = TTAS-TT50E) %>%  
  mutate (SowMonth = factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),labels=c("June", "July", "September", "November", "December", "February","March", "May")))

str(df_trifo)
```


```{r}
summary(df_trifo)
```

```{r}
tail(df_trifo)
```


```{r}
summary(df_trifo)
```

```{r loadFile}
df_trifo %>% filter(Plot ==1) %>% summary()
```


Graph the results : DAS and number of trifoliates 

```{r, fig.height=8, fig.width=15}
#Graph 1        
  df_trifo %>%
  filter(Cultivar=="Antas"|Cultivar=="Denmark"|Cultivar=="Leura")%>%
  group_by(Cultivar, SowMonth, DAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=Trifo)) + 
  #geom_point(aes(colour=Cultivar, shape=Cultivar), size=4) +
  geom_point(aes(shape=Cultivar), size=5) +
  #scale_shape_manual(values = c(0,1,2, 3,4,5,6,7,8,9,10,11))+
  scale_shape_manual(values = c(1,2,0)) +
  #geom_line(aes(colour=Cultivar)) +
  #geom_line()+
  #facet_wrap(~SowTreat,ncol=4, scales = "free") +
  facet_wrap (~SowMonth,ncol=4)+
  ylim(0,16)+
  labs(y="Number of trifoliate leaves (n)",x="Days after sowing")+
  #theme_grey(base_size = 16) +
  theme_bw(base_size = 24)+
  
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
    geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 5,  slope = 0, linetype=2)+
   geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
theme(text = element_text(size = 24))


#save
   
   #ggsave("plot_NumberOfTrifoliateLeavesA.png", width=16, height=8, dpi=400)




```


Graph the results: DAS and number of trifoliates 

```{r, fig.height=8, fig.width=15}
#Graph 1        
  df_trifo %>%
  filter(Cultivar=="Monti"|Cultivar=="Narrikup"|Cultivar=="Woogenellup")%>%
  group_by(Cultivar, SowMonth, DAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=Trifo)) + 
  #geom_point(aes(colour=Cultivar, shape=Cultivar), size=4) +
  geom_point(aes(shape=Cultivar), size=5) +
  #scale_shape_manual(values = c(0,1,2, 3,4,5,6,7,8,9,10,11))+
  scale_shape_manual(values = c(4,7,8)) +
  #geom_line(aes(colour=Cultivar)) +
  #geom_line()+
  #facet_wrap(~SowTreat,ncol=4, scales = "free") +
  facet_wrap (~SowMonth,ncol=4)+
  ylim(0,16)+
  labs(y="Number of trifoliate leaves (n)",x="Days after sowing")+
  
  theme_bw(base_size = 24)+
  
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
    geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 5,  slope = 0, linetype=2)+
   geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
theme(text = element_text(size = 24))

#save
   
   #ggsave("plot_NumberOfTrifoliateLeavesB.png", width=16, height=8, dpi=400)
 

```

Other graphics with same dat 
```{r, fig.height=5, fig.width=8}
#Graph         
  df_trifo %>%  
  group_by(Cultivar, SowMonth, DAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=Trifo)) + 
  geom_point(aes(colour=Cultivar, shape=Cultivar)) +
  geom_line(aes(colour=Cultivar)) +
  facet_wrap (SowMonth~., scales = "free")+
  labs(y="Number of trifoliates",x="Days after sowing")+
    #geom_abline(intercept = 6, slope = 0)
   geom_abline(intercept = 4:6, slope = 0)

```


get the standard  error values for the final trifoliate numbers 
```{r}
#str(df_trifo)
dfMaxTrifo <- df_trifo %>% 
  group_by( Cultivar, SowTreat,SowMonth ) %>%
  dplyr::select(Trifo)%>%
  summarise_all(funs(max,sd))%>%
  mutate(SE=sd/1.73)

summary(dfMaxTrifo)
```

Then include the TT calculated !!! TT cum 

Read Thermal Sum data. Need to include  values before 30 06 : 

Country	LocationYear	Date	DOY	Tx	Tm	MeanTt	Pp
NZ	Iversen2_2015	24/06/2015	175	7.30	-1.80	2.75	10.03173957
NZ	Iversen2_2015	25/06/2015	176	6.90	-3.90	1.50	10.033705
NZ	Iversen2_2015	26/06/2015	177	12.80	-0.70	6.05	10.03668323
NZ	Iversen2_2015	27/06/2015	178	17.40	-1.30	8.05	10.04067231
NZ	Iversen2_2015	28/06/2015	179	10.30	-1.70	4.30	10.04566961
NZ	Iversen2_2015	29/06/2015	180	17.30	3.70	10.50	10.05167184
NZ	Iversen2_2015	30/06/2015	181	18.50	1.30	9.90	10.05867507
"
#Merge dfs TTSum at Measurement and Sowing Date and Pp.
#Calculate the TTSum after emegence (TTAE) 
```{r}
# # Add Tt at measurement date
# df_trifo2 <- df_trifo %>%
#   ungroup() %>%
#   dplyr::select(-s1,-s2,-s3,-s4,-s5,-s6,-s6,-s7,-s8,-s9,-s10) %>%
#   merge(df_TTSum, by.x = "ReadingDate", by.y = "Date") %>%
#   dplyr::rename(SumTT_Reading = SumTTday) %>%
#   merge(df_TTSum, by.x = "SowingDate", by.y = "Date") %>%
#   dplyr::rename(SumTT_Sowing = SumTTday) %>%
#   mutate(TTAS = SumTT_Reading-SumTT_Sowing) %>%
#   merge(df_Photo, by.x="SowingDate", by.y = "Date") %>%
#   dplyr::rename(Pp_Sowing = Pp)  %>%
#   merge(df_TTEmerg, by = "Plot")  %>%
#   mutate(TTAE = TTAS-TT50E)
#   
# summary(df_trifo2)
```

Graphic

```{r MergeTTSumDate}

df_trifo %>%
  #filter(SowTreat != "S6" & SowTreat != "S7")%>%
  group_by(DAS,Cultivar,SowTreat) %>%
  summarise_each(funs(mean)) %>%
  #select(Variable,Percent, Cultivar,SowTreat) %>%
  filter(Cultivar == "Narrikup" | Cultivar =="Denmark") %>%
  ggplot(aes(x=DAS, y=Trifo, colour=SowTreat)) + 
  #geom_bar(shape=1, stat="identity")
  geom_point(aes(shape=Cultivar)) +
 # facet_wrap(SowTreat~., scales = "free") +
  geom_abline(intercept = 50, slope = 0)+
theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

## save df

```{r}
# save final DF"
write.table(df_trifo, "df_TrifoLeavesTT.txt")

```

Graphics 

```{r}
# graph
df_trifo %>%
  # mutate(Variable = 
  # factor(Variable,levels = c("Bud","Early","Open",
  #         "Petal","Bur1","Bur2","Bur3","Bur4" ))) %>%
  filter(Cultivar=="Narrikup")%>%
  group_by(TTAS,Cultivar,SowTreat,DAS) %>%
  summarise_each(funs(mean)) %>%
  #select(Variable,Percent, Cultivar,TTAS,SowTreat,SowingD,DAS) %>%
  #filter(Variable == "Bud"| Variable == "Open" ) %>%
  #filter(Variable == "Bud"| Variable == "Bur3" ) %>%
  #ggplot(aes(x=TTAS, y=Percent)) + 
  ggplot(aes(x=TTAS, y=Trifo)) +
  geom_line(aes(colour=SowTreat)) +
 # facet_wrap(SowTreat~Cultivar, scales = "free") +
  geom_abline(intercept = 50, slope = 0)+
   theme_bw()+
theme(axis.text.x = element_text(angle = 60, hjust = 1))+
labs(y="Percent of Plants with Floral bud ")+
xlab(expression(Thermal~time~~"("^"o"*"Cd)"))
 
```

Regraph

Graph the results : DAS and number of trifoliates 

```{r, fig.height=8, fig.width=15}
#Graph 1        
  df_trifo %>%
  filter(Cultivar=="Monti"|Cultivar=="Narrikup"|Cultivar=="Woogenellup")%>%
  group_by(Cultivar, SowTreat, SowMonth, DAS,TTAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=TTAS, y=Trifo)) + 
  #geom_point(aes(colour=Cultivar, shape=Cultivar), size=4) +
  geom_point(aes(shape=Cultivar), size=5) +
  #scale_shape_manual(values = c(0,1,2, 3,4,5,6,7,8,9,10,11))+
  scale_shape_manual(values = c(4,7,8)) +
  #geom_line(aes(colour=Cultivar)) +
  #geom_line()+
  #facet_wrap(~SowTreat,ncol=4, scales = "free") +
  facet_wrap (~SowMonth,ncol=4)+
  ylim(0,16)+
  labs(y="Number of trifoliate leaves (n)")+
  xlab(expression(Thermal~time~Sowing~"("^"o"*"Cd)"))+
  theme_bw(base_size = 24)+
  
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
    geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 5,  slope = 0, linetype=2)+
   geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
theme(text = element_text(size = 24))

#save
   
   #ggsave("plot_NumberOfTrifoliateLeavesB.png", width=16, height=8, dpi=400)
 

```

bring dataframe with TTEmergence to calculate number leaves from emergence

Select only data needed for regressions and stats 
```{r}
##this will be used to calculate the slope (phyllochron)
DataPhyllo <- df_trifo %>%
filter(Trifo>=1) %>%
mutate(phylloStage=as.factor(ifelse(TTAE<=400,"P1","P2")))

summary(DataPhyllo)

write.table(DataPhyllo, "DataPhyllo.txt")
```
```{r}
DataPhyllo %>% filter(phylloStage=="P1")%>% summary()
```

```{r}
DataPhyllo %>% filter(phylloStage=="P2")%>% summary()
```

# Mean and sd for graph
```{r, Warning=FALSE}
df_trifo_mean <- df_trifo %>%
  dplyr::select(Cultivar, SowMonth, SowTreat, DAS, Trifo, TTAE) %>%
  subset(TTAE>0) %>% 
  group_by(Cultivar, SowMonth, SowTreat, DAS) %>%
  summarise_all(funs(mean, sd)) %>%
  na.omit()

  summary(df_trifo_mean)
```
Just check the values for V11 and write on text 
```{r}

NineTrif<-df_trifo_mean %>%
 subset(Trifo_mean>8.9,Trifo_mean<10 )%>%
  group_by(Cultivar)%>%
  dplyr::select(TTAE_mean, TTAE_sd )%>%
  summarise_all(funs(mean))
  

```



```{r}
df_phyllo_mean <- df_trifo_mean %>%
  ungroup() %>%
  filter(Trifo_mean>=1) %>%
   mutate(phylloStage=as.factor(ifelse(TTAE_mean<=400,"P1","P2")))
  summary(df_phyllo_mean)
```
Prepare graphic elements
```{r}
bar_x <- max(df_trifo_mean$TTAE_mean) *1.1
bar_y <- max(df_trifo_mean$Trifo_mean) *1.1

bar_x 
bar_y
```


```{r}
##Get sd at max trifo position
dfError <- df_trifo_mean %>%
  ungroup() %>%
  dplyr::select(SowMonth, SowTreat,TTAE_mean, Trifo_mean, Trifo_sd)%>%
  group_by(SowTreat, SowMonth) %>%
  filter(Trifo_mean==max(Trifo_mean)) %>%
  summarise_all(funs(mean)) %>%
  mutate(SE=Trifo_sd/1.73) %>%
  mutate(TTAE_mean=bar_x, Trifo_mean=bar_y)

summary(dfError)
```

```{r}
df_phyllo_mean %>%
  ggplot(aes(x=TTAE_mean, y=Trifo_mean)) +
  geom_point(aes(shape=Cultivar), size=5)
```



#Graph 1  
```{r, fig.height=20, fig.width=10}

# select
p1 <- df_phyllo_mean %>% filter(phylloStage=="P1") 
p2 <- df_phyllo_mean %>% filter(phylloStage=="P2")

df_trifo_mean %>%
    ungroup()%>%
    subset(Trifo_mean>0.90)%>%
  #filter(Cultivar=="Antas"|Cultivar=="Denmark"|Cultivar=="Leura")%>%
  #group_by(Cultivar, SowTreat, DAS) %>%
  #summarise_each(funs(mean)) %>%
  ggplot(aes(x=TTAE_mean, y=Trifo_mean)) + 
 # geom_smooth(data=TrifoSubset,method='lm',formula=y~x, colour="grey",alpha=0.1, size=2)+
  geom_smooth(data=p1, method='lm', linetype=1,
              size=2, fill="grey", colour="black", alpha=0.2) +
 # geom_smooth(data=p2, method='lm', size=2, fill="darkgrey",colour="grey", alpha=0.2) +
  geom_point(aes(shape=Cultivar), size=8, alpha=0.5, stroke= 1.5) +
  #scale_shape_manual(values = c(0,1,2, 3,4,5,6,7,8,9,10,11))+
  scale_shape_manual(values = c(0,1,2,4,7,8)) +
  geom_errorbar(data=dfError, aes(ymin=Trifo_mean-SE,
                                  ymax=Trifo_mean+SE), width=50) +
  #geom_line(aes(colour=Cultivar)) +
  #geom_line()+
  #facet_wrap(~SowTreat,ncol=4, scales = "free") +
  facet_wrap (~SowMonth,ncol=2)+
 # ylim(0,18)+
 # xlim(0,700)+
  labs(y="Number of trifoliate leaves (n)")+
  #xlab(expression(Thermal~time~Emergence~"("^"o"*"Cd)"))+
  xlab(expression(Thermal~time~"("^"o"*"Cd)"))+
  theme_bw(base_size = 30)+
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  geom_vline(xintercept = 400, linetype=2)+
  #  geom_abline(intercept = 1, slope = 0, linetype=2)+
  # geom_abline(intercept = 5,  slope = 0, linetype=2)+
   #geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0.5))+
theme(text = element_text(size = 30))+
    ##thicks in axis
  theme(axis.ticks.length=unit(.3, "cm"))+
    #make Cultivars  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
  #label sizes 
theme(text = element_text(size = 30)) + theme(legend.position="top")

#save
   
   ggsave("plot_11_AllCVS_Number_TrifoliateLeavesThermalT.tiff", width=20, height=24, dpi=400)
 

```

#Calculate phyllochron
```{r}
library(broom)

p1<-DataPhyllo %>% filter(phylloStage=="P1")  %>% na.omit() %>% ungroup() 
#dplyr::select(-phylloStage)

phylloReg <- p1 %>%
 group_by(phylloStage, SowTreat, Cultivar, Block) %>%
    group_by(SowTreat, Cultivar,Block) %>%
 do(fit = lm(Trifo ~ TTAE, data = .))

head(phylloReg)
summary(phylloReg)
```


```{r}
phylloRegTable <- tidy(phylloReg, fit) %>% filter(term=="TTAE") %>%
mutate(Phyllocron=1/estimate)

summary(phylloRegTable)

dfCoef = glance(phylloReg, fit)
dfCoef

write.table(phylloRegTable, "Phyllochron.txt")

```

Get the means to build table (by SowTreat as per ANOVA )

```{r}
phylloRegTableMean <- phylloRegTable %>%
#filter(phylloStage=="P1")%>%
group_by(SowTreat) %>%
  dplyr::select(SowTreat, estimate, std.error, p.value)%>%
  summarise_all(funs(mean))

head(phylloRegTableMean)
```


```{r}
dfCoefMean<-dfCoef %>%
  #filter(phylloStage=="P1")%>%
  group_by(SowTreat)%>%
  dplyr::select(SowTreat, r.squared)%>%
  summarise_all(funs(mean))


head(dfCoefMean)
```
#Compare cultivars
```{r, fig.height=10}
phylloRegTable %>%
  ungroup() %>%
  #filter(Phyllocron==max(Phyllocron)) %>%
  ggplot(aes(x=SowTreat,y=Phyllocron)) +
  geom_point(aes(colour=Block)) +
  geom_boxplot(alpha=0.2) +
  facet_wrap(.~Cultivar, scales='free')
```

# Compare sowing dates
```{r, fig.height=10}
phylloRegTable %>%
  ungroup() %>%
  #filter(Phyllocron==max(Phyllocron)) %>%
  ggplot(aes(x=Cultivar,y=Phyllocron)) +
  geom_point(aes(colour=Block)) +
  geom_boxplot(alpha=0.2) +
  facet_wrap(.~SowTreat, scales='free')
```

##ANOVA Phyllochron

```{r}
my.anova <- aov(Phyllocron ~ SowTreat*Cultivar, data = phylloRegTable)

summary(my.anova)
```

## Mean separation 

```{r}
#(LSD.test(my.anova, c("SowTreat"), alpha= 0.05, p.adj="none"))
(LSD.test(my.anova, c("Cultivar", "SowTreat"), alpha= 0.05, p.adj="none"))
```


Do by SowTreat



## Create index to filter for loop ANOVA

```{r}
y <- c("S1","S2","S3","S4","S5","S6","S7","S8")

sdIndex <- unique(phylloRegTable$SowTreat)

sdIndex[order(match(sdIndex,y))]

length(sdIndex)
sdIndex
```
## Then loop anova for each individual sowing date 
```{r}
for (i in 1:length(sdIndex)) {
  
 #print(i)
 print(paste0(sdIndex[i],"--------------------------------"))
  
  file.subset <- phylloRegTable %>%
  filter(SowTreat==sdIndex[i])
  
 
head(file.subset, 50)
   summary(file.subset)
my.anova <- aov(Phyllocron ~ Cultivar + Block, data = file.subset)
print(summary(my.anova))

if ((summary(my.anova)[[1]][["Pr(>F)"]][1])<0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 


if ((summary(my.anova)[[1]][["Pr(>F)"]][1])>0.05) {
  print("***Sig Cultivar***") 
  print((LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))) } 

# make mean separation if significant

(LSD.test(my.anova, c("Cultivar"), alpha= 0.05, p.adj="none"))
  
}

```

