---
title: "Trifoliates Iversen Phyllochron  "
author: "CT"
date: "04.07.2018" 
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Plot Phyllochron agains PP emergence and First trifo 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```

Read document generated in script "3" 5Trifo_rate

```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifosNineI2")
getwd()
#create file


df_Phyllo <- read.table("Phyllochron.txt",header=TRUE)



head(df_Phyllo)


```
Define formats 

```{r loadFile}


# define factors for the ones that "look like" values
#df_Phyllo$Plot <- as.factor(df_Phyllo$Plot)
df_Phyllo$Block <- as.factor(df_Phyllo$Block)
df_Phyllo$Cultivar <- as.factor(df_Phyllo$Cultivar)
df_Phyllo$SowTreat <- as.factor(df_Phyllo$SowTreat)

 #df_Phyllo <- df_Phyllo %>%
 # mutate(SowingDate = ymd(SowingDate)) 

str(df_Phyllo)

df_Phyllo<-df_Phyllo %>%
  dplyr::select(SowTreat,Cultivar,Block,Phyllocron)

```

Bring the photoperiod data 

```{r}

df_PhotoP <- read.table("PhotoperiodEmergAnd1trifo.txt",header=TRUE)

#str(df_PhotoP)

### then bring a dataframe with all variables (plot, block )

df_Exp <- read.table("DataPhyllo.txt",header=TRUE)

expStruc<-df_Exp %>%
  dplyr::select(Plot, Block, SowTreat, Cultivar) %>%
  unique()
##
df_ExpPp <- merge(df_PhotoP, expStruc, by= "Plot")

summary(df_ExpPp)

```

```{r}


df_merged <- merge(df_ExpPp, df_Phyllo, by= c("Block", "SowTreat", "Cultivar"))

summary(df_merged)

```

Graph it but select which Photoperiod is to be explored 
PpEmerg or Pp1Trifo

```{r}
MeanData<-df_merged %>%
  group_by(Cultivar, SowTreat)%>%
  dplyr::select(PpEmerg,Phyllocron, Cultivar, SowTreat,Pp1Trifo)%>%
  ##use this for FirstTrifo
  #dplyr::select(Pp1Trifo,PhylC)%>%
  summarise_all(funs(mean,sd)) %>%
  ungroup()  %>%
  mutate(SowMonth= factor(SowTreat, 
                           levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
                           labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May")))
  

summary(MeanData)
```

Plot Weather variables with Maximum Percentage of Hardseeds 
```{r}
str(MeanData)
```
Draft graph 1

```{r}
#check data
df_Photo_dir <- data.frame(
  SowTreat = c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
  Pp_dir = c("Pp increase", "Pp increase", "Pp increase", "Pp increase", "Pp decrease", "Pp decrease", "Pp decrease","Pp decrease")
)

head(df_Photo_dir)
```


```{r, fig.height=8, fig.width=15}

sm_n <- c(6,7,9,11,12,2,3,5)
sm <- unique(MeanData$SowMonth)

g1 <- MeanData %>%
  ungroup() %>%
  mutate(SowMonthNo = factor(SowMonth, levels = sm_n,labels = sm)) %>%
  left_join(df_Photo_dir, by="SowTreat") %>%
  ##For Ppemergence
  # ggplot(aes(x=PpEmerg_mean, y= Phyllocron_mean))  +
  ggplot(aes(x=SowMonth, y= Phyllocron_mean)) + 
 # geom_point(colour= "black", alpha=0.5) +
   geom_point(aes(colour=Cultivar, shape=Cultivar),size=6, stroke=1.7) +
scale_shape_manual(values = c(0,1,2,4,7,8)) +
  ylim(0,100)+
  theme_bw()+
   #label sizes 
theme(text = element_text(size = 24))+
  xlab("Sowing Month")+
ylab(expression(Mean~Phyllochron~"("^"o"*"Cd/leaf)"))+
  #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  ##create ablines to indicate the average 51 (S2,S6) and +- LSD 7.65 to indicate no differences
  geom_abline(intercept = 51, slope = 0, linetype=1, linecolour="black")+
   geom_abline(intercept = 44,  slope = 0, linetype=2, linecolour="darkgrey")+
   geom_abline(intercept = 59,  slope = 0, linetype=2, linecolour="darkgrey")+
   
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   
  #label sizes 
theme(text = element_text(size = 26))
  

grid.arrange(g1)


# Save

ggsave("plot_13TrifoIv2_Phyllochron_SowMonth.tiff", width=12, height=6, dpi=400)

```
##Find the standard error for each sowing date 


```{r, fig.height=8, fig.width=15}

SESowMonth<-MeanData %>%
  group_by(SowTreat)%>%
  summarise_all(funs(max(Phyllocron_sd/1.73)))

  

```


## Graph Phyllcron and Pp at first trifoliate 
Create a graph with max SE 



```{r, fig.height=8, fig.width=15}
#check data

##Create Sowing date an photoperiod direction labels
df_Photo_dir <- data.frame(
  SowTreat = c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
  Pp_dir = c("Pp increase", "Pp increase", "Pp increase", "Pp increase", "Pp decrease", "Pp decrease", "Pp decrease","Pp decrease")
)

str(MeanData)

##Create datapoint for error bar 
dfError<- MeanData%>%
  group_by(Cultivar)%>%
  dplyr::select(Cultivar, Phyllocron_sd)%>%
  summarise_all(funs(max(Phyllocron_sd)))%>%
  mutate(SE=Phyllocron_sd/1.73)%>%
  #summarise(SE=max(Phyllocron_sd)/1.73)%>%
  mutate(Pp1Trifo_mean=18,Phyllocron_mean=90) 
 



g1 <-MeanData %>%
  ungroup() %>%
  #mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4","S5", "S6","S7","S8"),labels=c("June", #"July", "September", "November","December", "February","March","May")))%>%
  mutate(SowMonth= factor(SowTreat, 
                           levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
                           labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May"))) %>%
  left_join(df_Photo_dir, by="SowTreat") %>%
  ##For Ppemergence
  ggplot(aes(x=Pp1Trifo_mean, y= Phyllocron_mean))  +
   facet_wrap(~Cultivar)+
  ##for fristtrifo (Pp1Trifo_mean)
 #ggplot(aes(x=Pp1Trifo_mean, y= PhylC_mean))  +
  geom_point(colour= "black", alpha=0.5) +
  geom_point(aes(shape=SowMonth),size=6, stroke=1.5)+
  scale_shape_manual(values = c(1,2,3,4,5,6,7,8)) +
  #geom_text(aes(label=SowMonth),hjust=0, vjust=0,size=7) +
  #geom_errorbar(aes(ymin=PhylC_mean-PhylC_sd/2,
                    #ymax=PhylC_mean+PhylC_sd/2), width=1.5)+
  geom_errorbar(data=dfError, aes(ymin=Phyllocron_mean-SE/2,ymax=Phyllocron_mean+SE/2), width=.9)+
 
  #geom_smooth(method='lm',formula=y~x,alpha=0.01, aes(linetype=Pp_dir,fill = Pp_dir, colour="black"))+
    geom_smooth(method='lm',formula=y~x,alpha=0.01, aes(linetype=Pp_dir,fill = Pp_dir),colour="black")+
  #geom_smooth(method='lm',formula=y~x,alpha=0.1,  linetype = "dashed", colour= "grey")+
  
  theme_bw() +
  xlab(expression(Photoperiod~"("*"hours"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  ylab(expression(Mean~Phyllochron~"("^"o"*"Cd/leaf)")) +
  theme(text = element_text(size=24))+
  xlim(9,20)+
  ylim(0,120)+
 #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   
  #label sizes 
theme(text = element_text(size = 24))
  

#grid.arrange(g1, g2, g3,g4,g41)
grid.arrange(g1)
# Save
#ggsave("plot_Phyllochron_PpEmergence.tiff", width=12, height=6, dpi=400)
ggsave("plot_Prjt13_Phyllochron_PpFirstTrifo.tiff", width=12, height=6, dpi=400)

```


##Need to  insert Pp direction 

# Get linear coefficients of equations above
##check what are these P values 

```{r}
library(broom)
options(scipen=999)

MeanData2<-merge(MeanData, df_Photo_dir, by="SowTreat")

# create the linear fits by groups o variables
dfreg <- MeanData2 %>% group_by(Cultivar, Pp_dir) %>%
  do(fitreg = lm(Phyllocron_mean ~ Pp1Trifo_mean, data = .))
  #do(fitreg = lm(PhylC_mean ~ Pp1Trifo_mean, data = .))
  #Pp1Trifo_mean

# get the linear coefficients by group in a tidy data_frame
dfCoef <- tidy(dfreg, fitreg)
dfCoef



```



```{r}


dfCoef = glance(dfreg, fitreg)
dfCoef

```

Select only The increase in Photoperiod S1-S4

```{r, fig.height=8, fig.width=15}
#check data


df_Photo_dir <- data.frame(
  SowTreat = c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
  Pp_dir = c("Pp increase", "Pp increase", "Pp increase", "Pp increase", "Pp decrease", "Pp decrease", "Pp decrease","Pp decrease")
)

g2 <-MeanData %>%
  ungroup() %>%
  #mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4","S5", "S6","S7","S8"),labels=c("June", #"July", "September", "November","December", "February","March","May")))%>%
  mutate(SowMonth= factor(SowTreat, 
                           levels=c("S1", "S2", "S3", "S4", "S5", "S6", "S7","S8"),
                           labels=c("June", "July", "Sept.", "Nov.", "Dec.", "Feb.", "March", "May"))) %>%
  left_join(df_Photo_dir, by="SowTreat") %>%
  #filter(SowTreat=="S1"| 
        # SowTreat=="S2"| 
         #SowTreat=="S3"|
         #SowTreat=="S4")%>%
  
  #ggplot(aes(x=PpEmerg_mean, y= PhylC_mean))  +
  #Pp1Trifo_mean
 ggplot(aes(x=Pp1Trifo_mean, y= PhylC_mean))  +
  geom_point(colour= "black", alpha=0.5) +
  geom_point(aes(shape=SowMonth),size=4)+
  scale_shape_manual(values = c(1,2,3,4,5,6,7,8)) +
  geom_text(aes(label=SowMonth),hjust=0, vjust=0,size=7) +
  geom_errorbar(aes(ymin=PhylC_mean-PhylC_sd/2,
                    ymax=PhylC_mean+PhylC_sd/2), width=1.5)+
 
  #geom_smooth(method='lm',formula=y~x,alpha=0.1, aes(colour=Pp_dir, fill = Pp_dir)) +
  geom_smooth(method='lm',formula=y~x,alpha=0.1,  linetype = "dashed", colour= "grey")+
  
  theme_bw() +
  xlab(expression(Photoperiod~"("*"hours"*")"))+ 
  #ylab(expression(Maximum~Hardseeds~Percent~"("*"%"*")"))+
  ylab(expression(Mean~Phyllochron~"("^"o"*"Cd/leaf)")) +
  theme(text = element_text(size=24))+
  facet_wrap((Pp_dir~Cultivar), ncol = 6)+
  xlim(9,20)+
 #remove grid lines 
   theme(
     panel.border = element_rect(colour = "black", size = 3), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
   #scale_fill_manual("legend", values = c("Antas" = "#660066", "Denmark" = "lightgrey","Leura" = "darkgrey", "Monti" = "#FF9933","Narrikup" = "blue",  "Woogenellup" = "#033333"))+
   
   #make sowing dates white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=1))+
   
  #label sizes 
theme(text = element_text(size = 24))
  

#grid.arrange(g1, g2, g3,g4,g41)
grid.arrange(g2)
# Save
#ggsave("plot_Phyllochron_PpEmergence.tiff", width=12, height=6, dpi=400)


```



# Get linear coefficients of equations above
##check what are these P values lonly for the decreasing Photoperiod 

```{r}
library(broom)
options(scipen=999)

IncreasePp <-MeanData %>%
  filter(SowTreat=="S1"| 
         SowTreat=="S2"| 
         SowTreat=="S3"|
         SowTreat=="S4")



# create the linear fits by groups o variables
dfregInc <- IncreasePp %>% group_by(Cultivar) %>%
##For emergence use PpEmerg_mean,
  do(fitreg = lm(PhylC_mean ~ PpEmerg_mean, data = .))

  ##For First Trifo use  Pp1Trifo_mean
 #do(fitreg = lm(PhylC_mean ~ Pp1Trifo_mean, data = .))

# get the linear coefficients by group in a tidy data_frame
dfCoefInc <- tidy(dfregInc, fitreg)
dfCoefInc


```


```{r}


dfCoefInc = glance(dfregInc, fitreg)
dfCoefInc

```


do the same with decreasing Pp 


```{r}
library(broom)
options(scipen=999)

DecreasePp <-MeanData %>%
  filter(SowTreat=="S5"| 
         SowTreat=="S6"| 
         SowTreat=="S7"|
         SowTreat=="S8")



# create the linear fits by groups o variables
dfregDec <- DecreasePp %>% group_by(Cultivar) %>%
  do(fitreg = lm(PhylC_mean ~ PpEmerg_mean, data = .))
  
  ##Pp1Trifo_mean
 # do(fitreg = lm(PhylC_mean ~ Pp1Trifo_mean, data = .))

# get the linear coefficients by group in a tidy data_frame
dfCoefDec <- tidy(dfregDec, fitreg)
dfCoefDec


```




```{r}


dfCoefDec = glance(dfregDec, fitreg)
dfCoefDec

```





try with Ppfirst trifo 

Graph it 
```{r}

MeanDataTrifo1<-df_merged%>%
  group_by(Cultivar, SowTreat)%>%
  select( Pp1Trifo,PhylC)%>%
  summarise_all(funs(mean,sd))


```










```





