---
title: "Trifoliates Iversen "
author: "CT"
date: "31.08.2016"
output: 
  word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Analysis of trifoliates expansion for Iversen with focus on first Trifoliate 
- Graph the main dataset 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```



```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifosNineI2")
getwd()
#create file
df_trifo <- read.table("TrifoCountall.txt",header=TRUE)
head(df_trifo)


```
Define formats and calculate the mean number of trifoliates considering the sub samples (S1-S10)

```{r loadFile}


# define factors for the ones that "look like" values
df_trifo$Plot <- as.factor(df_trifo$Plot)
df_trifo$Block <- as.factor(df_trifo$Block)
df_trifo$Cultivar <- as.factor(df_trifo$Cultivar)
df_trifo$SowTreat <- as.factor(df_trifo$SowTreat)

 df_trifo <- df_trifo %>%
  mutate(SowingDate = dmy(SowingDate), 
         ReadingDate = dmy(ReadingDate),
         Trifo = (s1+s2+s3+s4+s5+s6+s7+s8+s9+s10)/10)

str(df_trifo)
head(df_trifo)
tail(df_trifo)


df_trifo %>% filter(Plot ==1) %>% summary()



```

Graph the results : DAS and number of trifoliates 

```{r, fig.height=8, fig.width=15}
#Graph 1        
  df_trifo %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),labels=c("June", "July", "September", "November", "December", "February","March", "May")))%>%
  filter(Cultivar=="Antas"|Cultivar=="Denmark"|Cultivar=="Leura")%>%
  group_by(Cultivar, SowTreat, DAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=Trifo)) + 
  #geom_point(aes(colour=Cultivar, shape=Cultivar), size=4) +
  geom_point(aes(shape=Cultivar), size=5) +
  #scale_shape_manual(values = c(0,1,2, 3,4,5,6,7,8,9,10,11))+
  scale_shape_manual(values = c(1,2,0)) +
  #geom_line(aes(colour=Cultivar)) +
  #geom_line()+
  #facet_wrap(~SowTreat,ncol=4, scales = "free") +
  facet_wrap (~SowTreat,ncol=4)+
  ylim(0,16)+
  labs(y="Number of trifoliate leaves (n)",x="Days after sowing")+
  #theme_grey(base_size = 16) +
  theme_bw(base_size = 24)+
  
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
    geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 5,  slope = 0, linetype=2)+
   geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
theme(text = element_text(size = 24))+
  #make Cultivars  white  
   theme(strip.background = element_rect(colour = "black", fill = "white",size=2))+
  
  #label sizes 
theme(text = element_text(size = 26))
  


#save
   
   ggsave("plot_NumberOfTrifoliateLeavesA.png", width=16, height=8, dpi=400)




```


Graph the results : DAS and number of trifoliates 

```{r, fig.height=8, fig.width=15}
#Graph 1        
  df_trifo %>%
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),labels=c("June", "July", "September", "November", "December", "February","March", "May")))%>%
  filter(Cultivar=="Monti"|Cultivar=="Narrikup"|Cultivar=="Woogenellup")%>%
  group_by(Cultivar, SowTreat, DAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=Trifo)) + 
  #geom_point(aes(colour=Cultivar, shape=Cultivar), size=4) +
  geom_point(aes(shape=Cultivar), size=5) +
  #scale_shape_manual(values = c(0,1,2, 3,4,5,6,7,8,9,10,11))+
  scale_shape_manual(values = c(4,7,8)) +
  #geom_line(aes(colour=Cultivar)) +
  #geom_line()+
  #facet_wrap(~SowTreat,ncol=4, scales = "free") +
  facet_wrap (~SowTreat,ncol=4)+
  ylim(0,16)+
  labs(y="Number of trifoliate leaves (n)",x="Days after sowing")+
  
  theme_bw(base_size = 24)+
  
   #remove grid lines 
     theme(
     panel.border = element_rect(colour = "black", size = 2), 
     panel.grid.major = element_blank(),
     panel.grid.minor = element_blank(),
     axis.line = element_line(colour = "black"))+
  
    geom_abline(intercept = 1, slope = 0, linetype=2)+
   geom_abline(intercept = 5,  slope = 0, linetype=2)+
   geom_abline(intercept = 9,  slope = 0, linetype=2)+
theme(axis.text.x=element_text(angle = 0, hjust = 0))+
theme(text = element_text(size = 24))

#save
   
   ggsave("plot_NumberOfTrifoliateLeavesB.png", width=16, height=8, dpi=400)
 

```





Other graphics with same dat 
```{r, fig.height=5, fig.width=8}
#Graph         
  df_trifo %>%  
  mutate (SowTreat= factor(SowTreat, levels=c("S1", "S2", "S3", "S4", "S5", "S6","S7", "S8"),labels=c("June", "July", "September", "November", "December", "February","March", "May")))%>%
  group_by(Cultivar, SowTreat, DAS) %>%
  summarise_each(funs(mean)) %>%
  ggplot(aes(x=DAS, y=Trifo)) + 
  geom_point(aes(colour=Cultivar, shape=Cultivar)) +
  geom_line(aes(colour=Cultivar)) +
  facet_grid (SowTreat~., scales = "free")+
  labs(y="Number of trifoliates",x="Days after sowing")+
    #geom_abline(intercept = 6, slope = 0)
   geom_abline(intercept = 4:6, slope = 0)



```


get the standard  error values for the final trifoliate numbers 


```{r}
str(df_trifo)

dfMaxTrifo <- df_trifo %>% 

  group_by( Cultivar, SowTreat ) %>%
  dplyr::select(Trifo)%>%
  summarise_all(funs(max,sd))%>%
  mutate(SE=sd/1.73)
 

  



```





End of this script Calc 1. 
Move to script 2 to calculate percent and rate of leaf appearance 
