---
title: "Trifoliates Iversen "
author: "CT"
date: "17.08.2017"
output: html_document
---

Purpose:

-Analysis of trifoliates expansion for Iversen from previous script (use number Trifo)
- Calculate the time to reach 10 number of leaves
- Calculate rate of leaf appearance (1/Days) 
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
```



```{r}
setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifosNineI2")
getwd()
#create file
df_trif <- read.table("Number_Trifo.txt",header=TRUE)
str(df_trif)


```


Define formats 

```{r loadFile}


# define factors for the ones that "look like" values

df_trif_worked <- df_trif %>%
  mutate(SowingDate = ymd(SowingDate), 
         ReadingDate = ymd(ReadingDate),
         DAS = as.numeric(DAS),
         Plot= as.factor(Plot),
         Block=as.factor(Block),
         Cultivar=as.factor(Cultivar),
         SowTreat=as.factor(SowTreat))

 


```


```{r}

str(df_trif_worked)

```



update the loop

```{r}

plots <- unique(df_trif_worked$Plot)
 
df_all <- data.frame()

for(p in 1:length(plots)) {

      # clean value holders
      DAS_nine_trifos <- 0

  df_sub <- df_trif_worked %>%
    subset(Plot == plots[p]) %>%
    arrange(TrifoNumber)
  
  df_sub
  head(df_sub)
 
   # record maximum value recorded to avoid crossing- FIXME: Not needed here?
  max_trifo <- max(df_sub$TrifoNumber) # create new col
  
  # for(z in 1:nrow(df_sub)) {
  #   
  #   df_sub$max_run[z] <- max(df_sub$NumberRun[z],
  #                                df_sub$NumberRun[z-1])
  #   
  # }
  # 
  df_sub
  
  
  ##############################################
   # Interpolate 
  y_ref <- 9 # y value where we want to find x by interpolation in this case needed 9 
  
  # interpolate
  tryCatch(  
  DAS_nine_trifos <- approx(df_sub$TrifoNumber, 
  df_sub$DAS, xout = y_ref, rule = 1)$y,
  error = function(e) 
  {
  DAS_nine_trifos <- max_trifo # FIXME: This should give max but gives NA - quick fix below temporarily
  }
)
  
 # COMPACT SYNTHAX FOR IFELSE when plots had reachedmore than 8 but less than 9 trifoliates ! 
  
 DAS_nine_trifos <- ifelse(is.na(DAS_nine_trifos),max_trifo,DAS_nine_trifos) # FIXME: This should be unecessary if try catch gives max value
 
  df_temp <- NULL 
  df_temp <- data.frame(Cultivar = df_sub$Cultivar[1],
                             SowTreat = df_sub$SowTreat[1],
                             Plot = df_sub$Plot[1],
                             Block = df_sub$Block[1],
                             DAS_nine_trifos = DAS_nine_trifos,
                             TrifoNumber = min(y_ref,max_trifo))

#  print(p)
  
df_all <- rbind(df_all,df_temp)                 
  
  } # end plot loop

summary(df_all)


```




Include dates of sowing again in dataframe 
```{r}
sdLookup <- data.frame (
  SowTreat = c("S1","S2","S3","S4","S5","S6","S7","S8"),
  SowingDate = c("24/06/2015", 
                 "28/07/2015" ,
                 "15/09/2015" ,
                 "5/11/2015" ,
                 "15/12/2015" ,
                 "17/02/2016" ,
                 "15/03/2016",
                 "4/05/2016"))

sdLookup$SowingDate <- dmy(sdLookup$SowingDate)

df_509T <- merge(df_all, sdLookup, by="SowTreat")
summary(df_509T)


```



Now correct column names after loop not to mix with other generated tables

```{r}

df_9T<-df_509T%>%
  mutate(DAS9T=as.numeric(DAS_nine_trifos))%>%
  dplyr::select(-DAS_nine_trifos)

str(df_9T)
 


```



```{r}

write.table(df_9T,"df_DAS_9_Trifo.txt")
```




Calculate RAte (1/days to 50%) 


```{r}

#try 1/DAS50% = Rate

df_RateTrifo <- df_9T %>%
  mutate(Rate=1/DAS9T)

  summary(df_RateTrifo)
  
  write.table(df_RateTrifo,"RateTrifo.txt")

```



Graph rate and SowTreat

```{r}
#Graph 

  df_RateTrifo %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(DAS9T)%>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 9 trifoliates  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

df_RateTrifo %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 9 trifoliates  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

```




End of this script Calc 3. 
Move to script 4 to include temperatures  
