---
title: "Trifoliates Iversen "
author: "CT"
date: "17.08.2017"
output: word_document: default
  pdf_document: default
  html_document: default
---

Purpose:

-Combine the rate of trifoliate appearance fof 9 trifoliates and  Mean Air Temp during trifo appearance   
 
```{r loadLibraries}
library(tidyr)
library (dplyr)
library (ggplot2)
library(agricolae)
library (lubridate)
library(mosaic)
library(lattice)
library(knitr)
```

Get data from Emergence Folder, Daily Mean Air temperature and dates to combine in dataframe 


```{r}

setwd("C:\\GitHubRepos\\SubCloverPhD\\SubClover\\TrifosNineI2")
getwd()
#create file

df_trif <- read.table("RateTrifo.txt",header=TRUE)
#adjust formats 
df_trif$SowingDate <- ymd(df_trif$SowingDate )
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$DAS9T <- as.numeric(df_trif$DAS9T)

```

Create df_MD to workout dates to % trifoliates 
```{r}

  df_MD <- df_trif %>%
  mutate(Date9T=SowingDate+DAS9T) %>%
  group_by(Plot, DAS9T) %>% 
  dplyr::filter(row_number() == 1)

str(df_MD)

H <-df_MD %>%
 dplyr:: select (Plot, Date9T)

#save and store table 
write.table(H, "DateTo9Trifos.txt")

```



Read the soil Temp data and Air temp data and  adjust formats 

```{r}

#create file
df_A <- read.table("AirTemp.txt",header=TRUE)
df_Soil <-read.table("SoilTemp.txt",header=TRUE)

#adjust formats
df_A %>%
  mutate(Date=dmy(Date))

str(df_A)

#adjust formats
df_Soil <- df_Soil%>%
mutate(Date=dmy(Date))


```

Now 
Add the accumulation of of soil temperatures to calculate the average temperature during the desired process (here 5 trifos). 

```{r}
#cumulate air
df_B <- df_A %>%
  mutate(SumAir = cumsum(AirTt)) %>%
  mutate(Date=dmy(Date))%>%
  dplyr::select(-AirTt)

#cumulate soil

df_Soil1 <- df_Soil %>%
  mutate(SumTempSo = cumsum(TempSoil10mm)) %>%
  #mutate(Date=dmy(Date))%>%
  dplyr::select(-TempSoil10mm)


```

check data with graph

```{r}
df_Soil1 %>%
  ggplot(aes(x=Date,y=SumTempSo)) +
  geom_point()

df_B%>%
  ggplot(aes(x=Date,y=SumAir)) +
  geom_point()

```




Merge dataframes by date

```{r}

# first merge the soil and air temperature dataframes 

df_Temp <- merge(df_Soil1,df_B,by="Date") 


#Merge the two dataframes by Date
df1 <- merge(df_MD,df_Temp, by.x="SowingDate",by.y="Date") %>%
  mutate(soilTempAcc_sow = SumTempSo) %>% 
  mutate(airTempAcc_sow=SumAir)%>%
dplyr::select(-SumTempSo,-SumAir)

str(df1)


```

Need to force a date for 50 % of plants with five trifoliates  (round) to calculate the average temperature during this phase  

Save dataframe as txt file


```{r}


# force formats of dates
df1$Date <- round(df1$Date9T,0)
df_Temp$Date <- round(df_Temp$Date,0)

#then repeat same procedure done for the soing date but use the dat for 1 Trifoliate
  df_merge <- merge(df1, df_Temp, by="Date") %>%
  mutate(soilTempAcc_9T = SumTempSo) %>%
  mutate(airTempAcc_9T=SumAir)%>%
  dplyr::select(-SumTempSo, -SumAir) %>%
 
#subtract accumulate temperature das1T from sowing 
  mutate(meanTempSoil_9T = (soilTempAcc_9T-soilTempAcc_sow)/DAS9T ) %>% 
  mutate(meanTempAir_9T = (airTempAcc_9T-airTempAcc_sow)/DAS9T )
  
  summary(df_merge)

  ##Use this dataframe to build graph in script 5 
write.table(df_merge, "df_MeanTempNineTrifo.txt") 

```




get the simple TT and SE for all cultivars. exclude S1 . Consider Tb=0 for all cultivars. 

```{r}

df_TT9T <- df_merge%>%
  mutate(TTto9TSoil=soilTempAcc_9T -soilTempAcc_sow)%>%
  mutate(TTto9TAir=airTempAcc_9T -airTempAcc_sow)

#then select sow treat and means and se

df_TTAllcv <-df_TT9T%>%
  filter(SowTreat!= "S1")%>% 
  #group_by(Cultivar) %>%
  group_by(SowTreat)%>%
  dplyr::select(TTto9TSoil)%>%
#dplyr::select(TTto1TAir)
  summarise_all(funs(mean,sd))%>%
    mutate(SE=sd/1.73)

```


Graph results 

Then graph results  (remember that here each replicate has a different temperature set... need to average to get a simpler graph 
## complete graph 
```{r, fig.height=5, fig.width=8}
dGraph <-df_merge %>%
  group_by(SowTreat, Cultivar) %>%
  dplyr::select(Rate,meanTempSoil_9T) %>%
  summarise_all(funs(mean,sd)) 

```




Not using this part yet . Bring data from emergence folder 



```{r}
df_S <- read.table("DASSeedEmer.txt",header=TRUE)

#change formats 
df_S <- df_S %>%
  mutate(Plot=as.factor(Plot),
         DAS50SeedEm= as.numeric(DAS50SeedEm),
         Date50SeedEm= dmy(Date50SeedEm))

         
str(df_S)


```



```{r}


#create file
df_A <- read.table("AirTemp.txt",header=TRUE)

#adjust formats
df_A %>%
  mutate(Date=dmy(Date))

str(df_A)

df_B <- df_A %>%
  mutate(SumAir = cumsum(AirTt)) %>%
  mutate(Date=dmy(Date))%>%
  dplyr::select(-AirTt)


summary(df_B)
summary (df_S)


#then save table df_B with the ACcumulated Air Temperature and merge 

write.table(df_B, "AccumAir.txt")

df1 <- merge(df_S,df_B, by.x="Date50SeedEm",by.y="Date")%>%
mutate(AirTempAcc_emerg = SumAir) %>%
  dplyr::select(-SumAir)

str(df1)

write.table(df1,"AccAirEmerg9T.txt")
```

Re start from here : Bring the calculated Mean AirTrifo file and merge 

```{r}

#create file
df_trif <- read.table("RateTrifo.txt",header=TRUE)
df_MeanAir <- read.table("MeanAirTrifo.txt",header=TRUE)

str(df_trif)
str(df_MeanAir)


```

adjust formats and Calculate the date to 50%  
```{r}

#adjust formats 
df_trif$SowingDate <- ymd(df_trif$SowingDate )
df_trif$Block <- as.factor(df_trif$Block)
df_trif$Plot <- as.factor(df_trif$Plot)
df_trif$DAS5T <- as.numeric(df_trif$DAS5T)

df_MeanAir$Plot <- as.factor(df_MeanAir$Plot)



```


```{r}


dfok <- merge(df_trif,df_MeanAir, by="Plot")

str(dfok)
```

Then graph results  (remember that here each replicate has a different temperature set... need to average to get a simpler graph 
## complete graph 
```{r, fig.height=5, fig.width=8}
dfok %>%
  group_by(MeanAirTempTrifo, SowingDate, SowTreat, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  #ggplot(aes(x=MeanAirTempTrifo, y=mean, colour=(Cultivar), shape=factor(Cultivar) )) +
 ggplot(aes(x=MeanAirTempTrifo, y=mean,colour=SowTreat, shape=Cultivar)) +
  geom_point(size=5) +
  #geom_line() +
  
  labs(y="Rate to five trifoliate stage (1/days)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()+
  xlim(0,20)+
  ylim(0,0.04)+
  #facet_wrap(~Cultivar,ncol=3, scales = "free")+
  xlab(expression(Mean~Air~Temperature~"("^"o"*"C)"))+
  theme(axis.text.x=element_text(angle = 0, hjust = 0, size= 12))+
  theme(axis.text.y=element_text(angle = 0, hjust = 0, size= 12))+
  theme(axis.title.y=element_text(angle = 90, hjust = 0, size= 14))+
  theme(axis.title.x=element_text(angle = 0, hjust = 0.5, size= 14))+
  theme(legend.text=element_text(size=12))
  
# then merge the dataframes to find out the mean temperature 


```




Graph rate and SowTreat

```{r}
#Graph 

  dfok %>%
  group_by(SowingDate, Cultivar) %>%
  dplyr::select(Rate) %>%
  summarise_each(funs(mean,sd)) %>%
  #Graph
  ggplot(aes(x=SowingDate, y=mean, colour=factor(Cultivar), shape=factor(Cultivar))) +
  geom_point() +
  geom_line() +
  labs(x="Sowing Date",y="1/ Days to 50% leaf emergence  ") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))+
  geom_errorbar(aes(ymin=mean-sd/2,
  ymax=mean+sd/2))+
  theme_bw()

```




End of this script . 
Move to script 5.  
